### 2023-03-15 paper.tex

% Created 2023-03-15 Wed 11:50
% Intended LaTeX compiler: pdflatex
\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{breakcites}
\usepackage{apacite}
\usepackage{paralist}
\usepackage{biblatex}
\addbibresource{/home/dp/Documents/Research_paper_SFR/bibl/bibliography/bibliography.bib}
\usepackage{hyperref}
\let\itemize\compactitem
\let\description\compactdesc
\let\enumerate\compactenum
\addbibresource{/bibl/bibliography/bibliography.bib}
\author{Dimitrios Papachistopoulos}
\date{\today}
\title{Finding the normalization constant of \(SFR_{del}\) and the relations between the various masses of the Galaxies}
\hypersetup{
 pdfauthor={Dimitrios Papachistopoulos},
 pdftitle={Finding the normalization constant of \(SFR_{del}\) and the relations between the various masses of the Galaxies},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2 (Org mode 9.6.1)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents

\#\#+\LaTeX{}\textsubscript{HEADER}: \affiliation{Dr. Pavel Kroupa}
\begin{ABSTRACT}

\textbf{Abstract}

\noindent\rule{\textwidth}{0.5pt}
\end{ABSTRACT}
\tableofcontents

\section{The Galaxies in the Local Cosmological Volume (LCV)}
\label{sec:org776cf02}

The Catalogue of Neigbouring Galaxies (Karachentsev, Igor D. and Makarov  et al. 2013\autocite{karachentsevUPDATEDNEARBYGALAXY2013}) and its updated version from the ``Catalog \& Atlas of the LV galaxies'' database \cite{CatalogLVGalaxies} are used to extract the K-band luminosities, the types of the galaxies, the mass within the Holmberg radius (M26), the Hydrogen masses of the galaxies (\(M_{HI}\)) and the SFRs based on integrated  H and far-ultraviolet (FUV) measurments for galaxies within a distance of
\(\approx 11\) Mpc. The SFR values contain limit flags, which we exclude from our present analysis. This gives a sample of 793 galaxies from 1248. From the remaing galaxies we have

\begin{center}
\begin{tabular}{|l|l|}
\hline
Measurment & Number of Galaxies \\
\hline
Hydrogen-Mass & 643 \\
M26 & 643 \\
K-band lum. & 789 \\
Type & 793 \\
H \$$\backslash$alpha\$ -S & 566 \\
FUV-SFR & 688 \\
\hline
\end{tabular}
\end{center}

The K-band values are converted to the total Stellar Masses of each galaxy according to the mass-to-light ratio of 0.6 (\cite{lelliSPARCMASSMODELS2016}), and the \(M_{HI}\) can be converted to the total mass of the gas of the galaxy using the equation \(M_g=1.33\,M_{HI}\)

The total SFR of each galaxy can be calcuated by

$$
    SFR_o=\frac{SFR_{FUV}+SFR_{Ha}}{2}
$$

if both \(SFR_{H\alpha},SFR_{FUV}\) measurments are available. If only one only one of them is given, then the SFR is equal to the given SFR value

$$
    SFR_o=SFR_i,\ \text{if } SFR_j=0,\ i\neq j,\ i,j=SFR_{FUV},\, SFR_{Ha}
$$

The condition \(SFR_o\geq 10^{-3}M_\odot yr^{-1}\) leaves 579 galaxies. This condition is applied due to the reasons given in the P. Kroupa,M. Haslbauer, I. Banik, S. T. Nagesh and J. Pflamm-Altenburg et al. 2020 \cite{kroupaConstraintsStarFormation2020}

\section{Types of galaxies}
\label{sec:org3f06310}

Using the dataset of 1248 galaxies, do before using the condition and removing the galaxies with the flags, the below histograms can be plotted.

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./graphs/hist-Type.png}
\caption{\label{Types of galaxies}The classification by de Vaucouleurs et al. (1991) is used for the morphology of the galaxies}
\end{figure}

Most of the galaxies in the LCV are Higly Irregular galaxies followed by lenticular galaxies

Out of the 1248 galaxies the 1022 are dwarf galaxies

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./graphs/hist-Tdw1.png}
\caption{\label{Types of dwarf galaxies}Dwarf galaxy morphology}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./graphs/hist-Tdw2.png}
\caption{\label{Types of dwarf galaxies brightness}Dwarf galaxy surface brightness morphology, where: H = high; N = normal; L = low; X = extremely low.}
\end{figure}

Most dwarf galaxies have low brightness and are irregulars followed by Dwarf spheroidal.

\section{Calculation of the normalization constant}
\label{sec:orgbfb382e}

According to P. Kroupa et al. 2020 current star formation rates of galaxies can be described by the 'delayed-\(\tau\)' mode as

\begin{equation} \label{eq:SFR}
SFR_{0,del}=\frac{A_{del}xe^{-x}}{\tau},\text{ where } x=\frac{t_{sf}}{\tau}
\end{equation}

\(\tau\) is the star formation time-scale and \(t_{sf}\) is the real time of star formation in a given galaxy

The average SFR is

\begin{equation}\label{eq:av_SFR-x}
\overline{SFR_{del}}=\frac{A_{del}}{t_{sf}}[1-(1+x)e^{-x}]
\end{equation}
and can also be defined by the present day stellar mass

\begin{equation}\label{eq:av_SFR M*}
    \overline{SFR}=\frac{\zeta M_*}{t_{sf}}
\end{equation}
where \(\zeta\) accommodates for mass-loss through stella evolution and \(\zeta\approx 1.3\)

\subsection{Constant \(t_{sf}\)}
\label{sec:org4bfffb4}
The observed ages of galactic discs are \(t_{sf}\approx 12\) Gyr (e.g. Knox, Hawkins \& Hambly 1999), so assuming an approximation of \(t_{sf}=12.5\) Gyr, the \(\overline{SFR_{del}}\) can be calcuated, from the equation (\ref{eq:av_SFR M*}). After that the equation of ratio

\begin{equation} \label{eq:ratio}
    \frac{\overline{SFR_{del}}}{SFR_{0,del}}=\frac{e^x-x-1}{x^2}
\end{equation}

can be solved numerically for \(x\) and using the equations (\Ref{eq:SFR}) and (\Ref{eq:av_SFR-x}) the \(A_{del}\) and \(\tau\) of each galaxy are found

\begin{verbatim}
                x           tau         A_del
count  550.000000  5.500000e+02  5.500000e+02
mean     1.762321  1.126908e+11  2.600301e+12
std      1.388768  1.067717e+12  4.456457e+13
min      0.000559  2.198306e+09  2.477977e+07
50%      1.513139  8.260984e+09  6.446495e+08
max      5.686198  2.237735e+13  1.005083e+15
\end{verbatim}

\begin{center}
\includegraphics[width=.9\linewidth]{./graphs/x-A_3.png}
\end{center}

\subsection{Constant \(\tau\)}
\label{sec:org3e5bf87}
Assuming for an constant \(\tau=3.5\) Gyr, we cannot use the same \(\overline{SFR}\) and ratio. Using the equations\textasciitilde{}(\Ref{eq:av_SFR M*}) and (\Ref{eq:ratio})

$$
    \frac{\overline{SFR_{del}}}{SFR_{0,del}}=\frac{e^x-x-1}{x^2}\Leftrightarrow \frac{e^x-x-1}{x}=\frac{\zeta M_*}{SFR\cdot\tau}
$$

and \(x\) and \(A_{del}\) can be calcuated numerically.

\begin{verbatim}
                  A           tsf         x_i
count  5.500000e+02  5.500000e+02  550.000000
mean   4.192335e+09  8.727310e+09    2.493517
std    1.432226e+10  3.097809e+09    0.885088
min    9.870027e+06  2.323533e+09    0.663867
25%    6.466448e+07  6.441713e+09    1.840489
50%    2.234694e+08  8.383763e+09    2.395361
75%    1.034826e+09  1.077179e+10    3.077654
max    1.057699e+11  1.796414e+10    5.132611
\end{verbatim}

\begin{center}
\includegraphics[width=.9\linewidth]{./graphs/x-A_tau.png}
\end{center}

Comparing the two different results for x, we see that the \(x_i\) from the second solution has a lower \(\sigma\)
\begin{verbatim}
                x         x_i
count  550.000000  550.000000
mean     1.762321    2.493517
std      1.388768    0.885088
min      0.000559    0.663867
25%      0.558532    1.840489
50%      1.513139    2.395361
75%      2.789068    3.077654
max      5.686198    5.132611
\end{verbatim}

The \(x_i\) results are more inline with the expected values from Kroupa et al. 2020 \(2.7<x<3.4\)
\begin{center}
\includegraphics[width=.9\linewidth]{./graphs/x-x_i.png}
\end{center}

\begin{center}
\includegraphics[width=.9\linewidth]{./graphs/A-A_del.png}
\end{center}

The correlation between the 2 different \(x\) is good with an R-squared of 94\%

\subsubsection{{\bfseries\sffamily TODO} DO sigma clipping for x to see if the x's are in agreement with the theoritical values}
\label{sec:org33fabf5}

\section{Mass relations}
\label{sec:orgcb5272f}

The below graphs show the correlation that the masses of the galaxies have. To consider a correlation good we need a \(R^2>70\%\)

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./graphs/logStellarMass-logM26.png}
\caption{\label{Stellar Mass - Mass within Holmberg radius}Stellar Mass - Mass within Holmberg radius: \(R^2=0.8\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./graphs/logMg-logM26.png}
\caption{\label{Gas Mass - Mass within Holmberg radius}Gas Mass - Mass within Holmberg radius: \(R^2=0.77\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./graphs/logMg-logM26.png}
\caption{\label{Gas Mass - Mass within Holmberg radius}Gas Mass/Hydrogen Mass - Mass within Holmberg radius: \(R^2=0.77\)}
\end{figure}, \begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./graphs/logMHI-logM26.png}
\caption{\label{Gas Mass - Mass within Holmberg radius}Gas Mass/Hydrogen Mass - Mass within Holmberg radius: \(R^2=0.77\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./graphs/logStellarMass-logMt.png}
\caption{\label{Total Mass - Stellar Mass}Total Mass - Stellar Mass: \(R^2=0.93\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./graphs/logMg-logMt.png}
\caption{\label{Total Mass - Gas Mass}Total Mass - Gas Mass/Hydrogen Mass: \(R^2=0.87\)}
\end{figure},\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./graphs/logMHI-logMt.png}
\caption{\label{Total Mass - Gas Mass}Total Mass - Gas Mass/Hydrogen Mass: \(R^2=0.87\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./graphs/logM26-logMt.png}
\caption{\label{Total Mass - Mass within Holmberg radius}Total Mass - Mass within Holmberg radius: \(R^2=0.85\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./graphs/M-MHI-M26.png}
\caption{\label{Stellar Mass - Mass within Holmberg radius - Hydrogen Mass - Total Mass}Stellar Mass - Mass within Holmberg radius - Hydrogen Mass - Total Mass}
\end{figure}

\section{Calculate the gas depletion timescale \(\tau_g\)}
\label{sec:orgf5cea8c}

The gas depletion timescale τg measures the time taken by a galaxy to exhaust its gas content Mg given the current SFR (Pflamm-Altenburg \& Kroupa 2009).
$$
\tau_g=\frac{M_g}{\dot{M_*}}=\frac{M_g}{SFR}
$$
\end{document}

### 2023-03-23 paper.tex
first draft
- Added the hopefully final form of the project
- I have added almost all of the graphs
- i have created some scripts to automate writing in latex from python

@@
-% Created 2023-03-15 Wed 11:50
+% Created 2023-03-20 Mon 22:04
 % Intended LaTeX compiler: pdflatex
@@
 \let\enumerate\compactenum
-\addbibresource{/bibl/bibliography/bibliography.bib}
 \author{Dimitrios Papachistopoulos}
 \date{\today}
-\title{Finding the normalization constant of \(SFR_{del}\) and the relations between the various masses of the Galaxies}
+\title{Investigations of the galaxies of the LCV}
 \hypersetup{
  pdfauthor={Dimitrios Papachistopoulos},
- pdftitle={Finding the normalization constant of \(SFR_{del}\) and the relations between the various masses of the Galaxies},
+ pdftitle={Investigations of the galaxies of the LCV},
  pdfkeywords={},
@@
 \maketitle
-\tableofcontents
-
-\#\#+\LaTeX{}\textsubscript{HEADER}: \affiliation{Dr. Pavel Kroupa}
 \begin{ABSTRACT}
@@
 \end{ABSTRACT}
-\tableofcontents
 
 \section{The Galaxies in the Local Cosmological Volume (LCV)}
-\label{sec:org776cf02}
+\label{sec:org630e55f}
 
@@
 and Makarov  et al.
-2013\autocite{karachentsevUPDATEDNEARBYGALAXY2013}) and its updated version from the ``Catalog \& Atlas of the LV galaxies'' database \cite{CatalogLVGalaxies} are used to extract the K-band luminosities, the types of the galaxies, the mass within the Holmberg radius (M26), the Hydrogen masses of the galaxies (\(M_{HI}\)) and the SFRs based on integrated  H and far-ultraviolet (FUV) measurments for galaxies within a distance of
+2013\autocite{karachentsevUPDATEDNEARBYGALAXY2013}) and its updated version from the ``Catalog \& Atlas of the LV galaxies'' databas\autocite{CatalogLVGalaxies}  are used to extract the K-band luminosities, the types of the galaxies, the mass within the Holmberg radius (M26), the Hydrogen masses of the galaxies (\(M_{HI}\)) and the SFRs based on integrated  H and far-ultraviolet (FUV) measurments for galaxies within a distance of
 \(\approx 11\) Mpc. The SFR values contain limit flags, which we exclude from our present analysis. This gives a sample of 793 galaxies from 1248. From the remaing galaxies we have
@@
 \section{Types of galaxies}
-\label{sec:org3f06310}
+\label{sec:org6287ff6}
 
@@
 \section{Calculation of the normalization constant}
-\label{sec:orgbfb382e}
+\label{sec:orgbe376f2}
 
@@
 \subsection{Constant \(t_{sf}\)}
-\label{sec:org4bfffb4}
+\label{sec:org2e54374}
 The observed ages of galactic discs are \(t_{sf}\approx 12\) Gyr (e.g.
@@
 \subsection{Constant \(\tau\)}
-\label{sec:org3e5bf87}
+\label{sec:orgce62d74}
 Assuming for an constant \(\tau=3.5\) Gyr, we cannot use the same \(\overline{SFR}\) and ratio. Using the equations\textasciitilde{}(\Ref{eq:av_SFR M*}) and (\Ref{eq:ratio})
@@
 \begin{center}
-\includegraphics[width=.9\linewidth]{./graphs/x-x_i.png}
+\includegraphics[width=.9\linewidth]{./graphs/x-x_icolor_color.png}
 \end{center}
 
+The galaxies with low x and x\textsubscript{i}, have a lower color index (\(<B-V>\)) then galaxies with higher x, which means that they are younger galaxies, as expected by the x values.
+For example, if x has a value of 1 \(\Leftrightarrow x_i=2\) then
+
 \begin{center}
-\includegraphics[width=.9\linewidth]{./graphs/A-A_del.png}
+\includegraphics[width=.9\linewidth]{./graphs/log_A_del-log_A.png}
 \end{center}
@@
 \subsubsection{{\bfseries\sffamily TODO} DO sigma clipping for x to see if the x's are in agreement with the theoritical values}
-\label{sec:org33fabf5}
+\label{sec:org0b0321d}
 
 \section{Mass relations}
-\label{sec:orgcb5272f}
+\label{sec:org70c9aab}
 
@@
 \centering
-\includegraphics[width=.9\linewidth]{./graphs/logStellarMass-logMt.png}
+\includegraphics[width=.9\linewidth]{./graphs/logStellarMass-logMtcolor_log_Mass_ratio.png}
+\caption{\label{Total Mass - Stellar Mass}Total Mass - Stellar Mass: \(R^2=0.93\)}
+\end{figure}
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=.9\linewidth]{./graphs/logStellarMass-logMtcolor_log_SFR_0.png}
+\caption{\label{Total Mass - Stellar Mass}Total Mass - Stellar Mass: \(R^2=0.93\)}
+\end{figure}
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=.9\linewidth]{./graphs/logStellarMass-logMtcolor_log_tau_g.png}
 \caption{\label{Total Mass - Stellar Mass}Total Mass - Stellar Mass: \(R^2=0.93\)}
@@
 \section{Calculate the gas depletion timescale \(\tau_g\)}
-\label{sec:orgf5cea8c}
+\label{sec:orgaf32583}
 
@@
 $$
+
+\printbibliography
 \end{document}

### 2023-03-23 paper2.tex
first draft
- Added the hopefully final form of the project
- I have added almost all of the graphs
- i have created some scripts to automate writing in latex from python

% Created 2023-03-23 Thu 02:32
% Intended LaTeX compiler: pdflatex
\documentclass[a4paper,twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{breakcites}
\usepackage{paralist}
\usepackage{amsmath}
\usepackage{biblatex}
\addbibresource{/home/dp/Documents/Research_paper_SFR/bibl/bibliography/bibliography.bib}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{booktabs}
\usepackage[T1]{fontenc}
\usepackage{tgbonum}
\let\itemize\compactitem
\let\description\compactdesc
\let\enumerate\compactenum
\author{Dimitrios Papachistopoulos}
\date{\today}
\title{Investigations of the galaxies of the LCV}
\hypersetup{
 pdfauthor={Dimitrios Papachistopoulos},
 pdftitle={Investigations of the galaxies of the LCV},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2 (Org mode 9.6.1)}, 
 pdflang={English}}
\begin{document}

\maketitle

\section{The Galaxies in the Local Cosmological Volume (LCV)}
\label{sec:org50829b4}

The Catalogue of Neigbouring Galaxies (Karachentsev, Igor D. and Makarov  et al. 2013\autocite{karachentsevUPDATEDNEARBYGALAXY2013}) and its updated version from the ``Catalog \& Atlas of the LV galaxies'' databas\autocite{CatalogLVGalaxies}  are used to extract the K-band luminosities, the types of the galaxie\footnote{TType=Morphology type code according to the classification by de Vaucouleurs/ Tdw1=Dwarf galaxy morphology/ Tdw2=Dwarf galaxy surface brightness morphology}s, the mass within the Holmberg radius (M26), the Hydrogen masses of the galaxies (\(M_{HI}\)) and the SFRs based on integrated  H and far-ultraviolet (FUV) measurments for galaxies within a distance of
\(\approx 11\) Mpc. The SFR and MHI values contain limit flags, which we exclude from our present analysis. This gives a sample of 793 galaxies from 1248. From the remaing galaxies we have

\begin{table}[hc]
\centering
\begin{tabular}{lr}
\toprule
{} &    0 \\
\midrule
Name    &  793 \\
Kmag    &  321 \\
FUVmag  &  687 \\
TType   &  793 \\
Tdw1    &  580 \\
Tdw2    &  568 \\
Bmag    &  790 \\
SFR\_Ha  &  566 \\
SFR\_FUV &  688 \\
K       &  789 \\
MHI     &  643 \\
color   &  321 \\
\bottomrule
\end{tabular}
\end{table}

\begin{center}
\begin{tabular}{|l|l|}
\hline
Measurment & Number of Galaxies \\
\hline
\end{tabular}
\end{center}

The K-band values are converted to the total Stellar Masses of each galaxy according to the mass-to-light ratio of 0.6 (\cite{lelliSPARCMASSMODELS2016}), and the \(M_{HI}\) can be converted to the total mass of the gas of the galaxy using the equation \(M_g=1.33\,M_{HI}\)

The total SFR of each galaxy can be calcuated by

$$
    SFR_o=\frac{SFR_{FUV}+SFR_{Ha}}{2}
$$

if both \(SFR_{H\alpha},SFR_{FUV}\) measurments are available. If only one only one of them is given, then the SFR is equal to the given SFR value

$$
    SFR_o=SFR_i,\ \text{if } SFR_j=0,i\neq j,\ i,j=FUV, H_a
$$

The condition \(SFR_o\geq 10^{-3}M_\odot yr^{-1}\) leaves 579
galaxies. This condition is applied due to the reasons given in the P. Kroupa,M. Haslbauer, I. Banik, S. T. Nagesh and J. Pflamm-Altenburg et al. 2020 \cite{kroupaConstraintsStarFormation2020}

\section{Types of galaxies}
\label{sec:org54aef07}

Using the dataset of 1248 galaxies, do before using the condition and removing the galaxies with the flags, the below histograms can be plotted.

Most of the galaxies in the LCV are Higly Irregular galaxies followed by lenticular galaxies

Out of the 1248 galaxies the 1022 are dwarf galaxies

Most dwarf galaxies have low brightness and are irregulars followed by Dwarf spheroidal.

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figs/hist-Type.png}
\caption{\label{Types of galaxies}The classification by de Vaucouleurs et al. (1991) is used for the morphology of the galaxies}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figs/hist-Tdw1.png}
\caption{\label{Types of dwarf galaxies}Dwarf galaxy morphology}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figs/hist-Tdw2.png}
\caption{\label{Types of dwarf galaxies brightness}Dwarf galaxy surface brightness morphology, where: H = high; N = normal; L = low; X = extremely low.}
\end{figure}

\section{Delayed-\(\tau\) model}
\label{sec:org9d3ca76}

According to P. Kroupa et al. 2020\autocite{kroupaConstraintsStarFormation2020} current star formation rates of galaxies can be described by the 'delayed-\(\tau\)' mode as

\begin{equation} \label{eq:SFR}
SFR_{0,del}=\frac{A_{del}xe^{-x}}{\tau},\text{ where } x=\frac{t_{sf}}{\tau}
\end{equation}

where \(\tau\) is the star formation time-scale,  \(t_{sf}\) is the real time of star formation in a given galaxy and \(A_{del}\) a normalization constant.

The average SFR is

\begin{equation}\label{eq:av_SFR-x}
\overline{SFR_{del}}=\frac{A_{del}}{t_{sf}}[1-(1+x)e^{-x}]
\end{equation}
and can also be defined by the present day stellar mass

\begin{equation}\label{eq:av_SFR M*}
    \overline{SFR}=\frac{\zeta M_*}{t_{sf}}
\end{equation}
where \(\zeta\) accommodates for mass-loss through stella evolution and \(\zeta\approx 1.3\)

This is a system of 2 equations and 3 variables, since A\textsubscript{del} has never been calculated

\subsection{Constant \(t_{sf}\)}
\label{sec:orgb5e0687}
The observed ages of galactic discs are \(t_{sf}\approx 12\) Gyr\autocite{knoxSurveyCoolWhite1999}, so assuming an approximation of \(t_{sf}=12.5\) Gyr, the \(\overline{SFR_{del}}\) can be calcuated, from the equation (\ref{eq:av_SFR M*}).

After that the equation of ratio

\begin{equation} \label{eq:ratio}
    \frac{\overline{SFR_{del}}}{SFR_{0,del}}=\frac{e^x-x-1}{x^2}
\end{equation}

can be solved numerically for \(x\) and using the equations (\Ref{eq:SFR}) and (\Ref{eq:av_SFR-x}) the \(A_{del}\) and \(\tau\) of each galaxy are found.

\begin{table}[hc]
\centering
\begin{tabular}{lrrr}
\toprule
{} &    A\_tsf &      tau &    x\_tsf \\
\midrule
count & 5.78E+02 & 5.79E+02 & 5.79E+02 \\
mean  & 2.25E+12 & 1.09E+11 & 1.85E+00 \\
std   & 3.94E+13 & 1.04E+12 & 1.48E+00 \\
min   & 2.48E+07 & 1.93E+09 & 5.59E-04 \\
25\%   & 1.41E+08 & 4.18E+09 & 5.65E-01 \\
50\%   & 6.84E+08 & 7.79E+09 & 1.60E+00 \\
75\%   & 5.70E+09 & 2.21E+10 & 2.99E+00 \\
max   & 9.10E+14 & 2.24E+13 & 6.47E+00 \\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figs/x-A_tsf.png}
\caption{\label{fig:$A_{del} = f(x)$ for constant t_{sf}}\(A_{del} = f(x)\) for constant t\textsubscript{sf}}
\end{figure}

\begin{center}
\includegraphics[width=.9\linewidth]{figs/T-A_tsf.png}
\end{center}

\subsection{Constant \(\tau\)}
\label{sec:org4942cfd}

Assuming for an constant \(\tau=3.5\) Gyr, we cannot use the same \(\overline{SFR}\) since it depends on \(t_{sf}\). Using the equations\textasciitilde{}(\Ref{eq:av_SFR M*}) and (\Ref{eq:ratio})

$$
    \frac{\overline{SFR_{del}}}{SFR_{0,del}}=\frac{e^x-x-1}{x^2}\Leftrightarrow \frac{e^x-x-1}{x}=\frac{\zeta M_*}{SFR\cdot\tau}
$$

using this equation \(x\) and \(A_{del}\) can be calcuated numerically.

\begin{table}[hc]
\centering
\begin{tabular}{lrrr}
\toprule
{} &    A\_tau &    x\_tau &      tsf \\
\midrule
count & 5.79E+02 & 5.79E+02 & 5.79E+02 \\
mean  & 4.59E+09 & 2.54E+00 & 8.89E+09 \\
std   & 1.50E+10 & 9.57E-01 & 3.35E+09 \\
min   & 9.87E+06 & 4.07E-01 & 1.42E+09 \\
25\%   & 6.50E+07 & 1.87E+00 & 6.55E+09 \\
50\%   & 2.37E+08 & 2.44E+00 & 8.54E+09 \\
75\%   & 1.12E+09 & 3.08E+00 & 1.08E+10 \\
max   & 1.06E+11 & 5.77E+00 & 2.02E+10 \\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figs/x-A_tau.png}
\caption{\label{fig:$A_{del} = f(x)$ for constant $\tau$}\(A_{del} = f(x)\) for constant \(\tau\)}
\end{figure}

\begin{center}
\includegraphics[width=.9\linewidth]{figs/T-A_tau.png}
\end{center}

\subsection{Comparing the two results}
\label{sec:org2d98e85}

\subsubsection{Comparing the \(x\)'s}
\label{sec:org7c16f4c}

Comparing the two different results for x, we see that the \(x|_\tau\) has a lower \(\sigma\)

\begin{table}[hc]
\centering
\begin{tabular}{lrr}
\toprule
{} &    x\_tau &    x\_tsf \\
\midrule
count & 5.79E+02 & 5.79E+02 \\
mean  & 2.54E+00 & 1.85E+00 \\
std   & 9.57E-01 & 1.48E+00 \\
min   & 4.07E-01 & 5.59E-04 \\
25\%   & 1.87E+00 & 5.65E-01 \\
50\%   & 2.44E+00 & 1.60E+00 \\
75\%   & 3.08E+00 & 2.99E+00 \\
max   & 5.77E+00 & 6.47E+00 \\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figs/Comparing_the_x_Mt.png}
\caption{\label{fig:Comparing the two x's, According to their total masses}Comparing the two x's, According to their total masses}
\end{figure}
\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figs/x_tau-Mt-color.png}
\caption{\label{fig:$x|_\tau=f(M_t)$, with their color index}\(x|_\tau=f(M_t)\), with their color index}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figs/x_tsf-x_tau-color_logMt.png}
\caption{\label{fig:Comparing the two x, according to their total mass}Comparing the two x, according to their total mass}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figs/x_tsf-x_tau-color_TType.png}
\caption{\label{fig:Comparing the two x, according to their type}Comparing the two x, according to their type}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figs/x_tsf-x_tau-color_logcolor.png}
\caption{\label{fig:Comparing the two x, according to their color index}Comparing the two x, according to their color index}
\end{figure}

The two results are interrelated through the equation:
\begin{equation}\label{eq:x_tsf-x_tau}
\begin{align}
& x|_\tau = (6.30(6) \times 10^{-1})\cdot x|_{tsf} + (1.374(15) \times 10^{0}) \\ 
& \textrm{with correlation } R^2=94\%
\end{align}
\end{equation}

and from the plots the following conclusions can be drawn:

\begin{enumerate}
\item The galaxies with a higher total mass deviate less from the linear fit and are older.
\item The younger galaxies are mainly later types of galaxies
\item For lower x's, the galaxies have a lower color index which indicates that they are younger. So the values are inline with the experimental values.
\end{enumerate}

\subsubsection{Comparing the normalization constants}
\label{sec:orgcf339e2}

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figs/Comparing_the_A_x.png}
\caption{\label{fig:Comparing the two A_{del}}Comparing the two A\textsubscript{del}}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figs/A_tau-A_tsf_colo_X.png}
\caption{\label{fig:Comparison of the 2 A_{del}s according to their $x$}Comparison of the 2 A\textsubscript{del}s according to their \(x\)}
\end{figure}
\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figs/A_tau-A_tsf_Mt.png}
\caption{\label{fig:Comparison of the 2 A_{del}s according to their total masses}Comparison of the 2 A\textsubscript{del}s according to their total masses}
\end{figure}

For high \(x\) and high masses the two A\textsubscript{del}s have a high correlation. Specifically:
\begin{enumerate}
\item For high \(x\) the \(A_{del}|_{\tau}-A_{del}|_{t_{sf}}\) plot follows a \(y=x\) trend, which means that for older stars and stars with a low star formation timescale \(\tau\), the normalization constant is the same despite the method used to calculate it.
\item The same is true for more massive galaxies, since they deviate less from the \(y=x\) line
\end{enumerate}

\section{The gas depletion timescale \(\tau_g\)}
\label{sec:org33bc00a}

The gas depletion timescale \(\tau_g\) measures the time taken by a galaxy to exhaust its gas content Mg given the current SFR\autocites{nageshSimulationsStarformingMainsequence2023}[][]{pflamm-altenburgFundamentalGasDepletion2009}.
$$
\tau_g=\frac{M_g}{\dot{M_*}}=\frac{M_g}{SFR}
$$

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figs/tau_g-Mg-color_StellarMass.png}
\caption{\label{fig:$\tau_g = f(M_g)$, with the Stellar Mass of the galaxies}\(\tau_g = f(M_g)\), with the Stellar Mass of the galaxies}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figs/logStellarMass-log_tau_g-color_log_SFR_0.png}
\caption{\label{fig:Correlation of the $\tau_g$ with the SFR and the Stellar mass}Correlation of the \(\tau_g\) with the SFR and the Stellar mass}
\end{figure}

Even though the logarithmic correlation is low (\(R^2 = 21\%\)), there seems to be a pattern wherein the decrease of \(\tau_g\) corresponds to an increase in the values of the Stellar Mass and the current star formation \(SFR_0\).

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figs/logMt-log_tau_g-color_logMg.png}
\caption{\label{fig:Correlation of the $\tau_g$ with the total mass and the mass of the gas}Correlation of the \(\tau_g\) with the total mass and the mass of the gas}
\end{figure}

Again it can be observed that as the \(\tau_g\) decreases, the corresponding values of \(M_t\) and \(M_g\) increase, but the logarithmic correlation is again low (\(R^2 = 11\%\)).

There is a notable trend, wherein for high masses we have a shorter timescale

\section{Mass relations}
\label{sec:org630e948}

Many of the galaxies masses have a high correlation with each other, and also help us undarstand the previous calculations.

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figs/log_tsf-log_Mass_ratio-color_color.png}
\caption{\label{fig:None}None}
\end{figure}

As expected, the older the galaxy the mass ratio is higher, and the color index agrees ($\backslash$?)

\pagebreak
\printbibliography
\end{document}

### 2023-03-23 final.py

@@ -1,0 +1,323 @@
+import numpy as np
+import pandas as pd
+from scipy.optimize import fsolve
+import matplotlib.pyplot as plt
+import seaborn as sns
+import statsmodels.api as sm
+import statsmodels.formula.api as smf
+from tabulate import tabulate
+
+
+pd.set_option('display.float_format', lambda x: '%.2E' % x)
+######Print images with caption
+def caption(fname,caption,name = None):
+    if name == None:
+        name = caption
+    return "#+caption:{} \n#+name: fig:{} \n#+label: fig:{} \n[[./{}]]".format(caption,name,name,fname)
+
+def simple_regplot(data ,
+    X, Y, cap = None, name = None, n_std=2, n_pts=100, ax=None, scatter_kws=None, line_kws=None, ci_kws=None):
+    df=data
+    x=df[X]
+    y=df[Y]
+    """ Draw a regression line with error interval. """
+    ax = plt.gca() if ax is None else ax
+
+    # calculate best-fit line and interval
+    x_fit = sm.add_constant(x)
+    fit_results = sm.OLS(y, x_fit,missing='drop').fit()
+
+    xconst=f'{fit_results.params[1]:.3f}'
+    const=f'{fit_results.params[0]:.3f}'
+    eval_x = sm.add_constant(np.linspace(np.min(x), np.max(x), n_pts))
+    pred = fit_results.get_prediction(eval_x)
+
+    # draw the fit line and error interval
+    ci_kws = {} if ci_kws is None else ci_kws
+    ax.fill_between(
+        eval_x[:, 1],
+        pred.predicted_mean - n_std * pred.se_mean,
+        pred.predicted_mean + n_std * pred.se_mean,
+        facecolor ='red',
+        alpha=0.5,
+        **ci_kws,
+    )
+    line_kws = {} if line_kws is None else line_kws
+    h = ax.plot(eval_x[:, 1], pred.predicted_mean, **line_kws,color='red',linestyle='dashed',label= Y+"="+xconst+X+"+"+const)
+
+    # draw the scatterplot
[…]

### 2023-03-23 paper2.tex
html

@@
-% Created 2023-03-23 Thu 02:32
+% Created 2023-03-24 Fri 00:20
 % Intended LaTeX compiler: pdflatex
@@
 \maketitle
+\begin{abstract}
+The paper investigates the properties of galaxies in the Local Cosmological Volume (LCV), using the Catalogue of Neighboring Galaxies\autocite{karachentsevUPDATEDNEARBYGALAXY2013} and its updated version from the ``Catalog \& Atlas of the LV galaxies'' database\autocite{CatalogLVGalaxies}.
+The properties studied include the galaxy types, their various masses, the star formation rates (SFRs) and the star formation timescale \(\tau\), gas depletion timescale \(\tau_g\).
+The paper aims to understand the distribution and correlation of these properties in the sample of galaxies in the LCV, and how they relate to current astrophysical theories.
+Additionally, the paper discusses the conditions for star formation and the implications of the observed properties on galaxy evolution.
+\end{abstract}
 
 \section{The Galaxies in the Local Cosmological Volume (LCV)}
-\label{sec:org50829b4}
+\label{sec:org6580427}
 
@@
 and Makarov  et al.
-2013\autocite{karachentsevUPDATEDNEARBYGALAXY2013}) and its updated version from the ``Catalog \& Atlas of the LV galaxies'' databas\autocite{CatalogLVGalaxies}  are used to extract the K-band luminosities, the types of the galaxie\footnote{TType=Morphology type code according to the classification by de Vaucouleurs/ Tdw1=Dwarf galaxy morphology/ Tdw2=Dwarf galaxy surface brightness morphology}s, the mass within the Holmberg radius (M26), the Hydrogen masses of the galaxies (\(M_{HI}\)) and the SFRs based on integrated  H and far-ultraviolet (FUV) measurments for galaxies within a distance of
-\(\approx 11\) Mpc. The SFR and MHI values contain limit flags, which we exclude from our present analysis. This gives a sample of 793 galaxies from 1248. From the remaing galaxies we have
+2013\autocite{karachentsevUPDATEDNEARBYGALAXY2013}) and its updated version from the ``Catalog \& Atlas of the LV galaxies'' database\autocite{CatalogLVGalaxies}  are used to extract the B-band, FUV $\backslash$& K-band luminosities\footnote{We use the FUV and B measurments to calculate the B-FUV color index.} , the types of the galaxie\footnote{TType=Morphology type code according to the classification by de Vaucouleurs/ Tdw1=Dwarf galaxy morphology/ Tdw2=Dwarf galaxy surface brightness morphology}s, the mass within the Holmberg radius (M26), the Hydrogen masses of the galaxies (\(M_{HI}\)) and the SFRs based on integrated  H and far-ultraviolet (FUV) measurments for galaxies within a distance of
+\(\approx 11\) Mpc. Some of those values contain limit flags, which we exclude from our present analysis. This gives a sample of 793 galaxies from 1248. From the remaing galaxies we have
 
@@
 Name    &  793 \\
-Kmag    &  321 \\
 FUVmag  &  687 \\
@@
 MHI     &  643 \\
-color   &  321 \\
+color   &  686 \\
 \bottomrule
@@
 \section{Types of galaxies}
-\label{sec:org54aef07}
+\label{sec:org9a48829}
 
@@
 \section{Delayed-\(\tau\) model}
-\label{sec:org9d3ca76}
+\label{sec:org5bed0e8}
 
@@
 \subsection{Constant \(t_{sf}\)}
-\label{sec:orgb5e0687}
+\label{sec:org0892bf5}
 The observed ages of galactic discs are \(t_{sf}\approx 12\) Gyr\autocite{knoxSurveyCoolWhite1999}, so assuming an approximation of \(t_{sf}=12.5\) Gyr, the \(\overline{SFR_{del}}\) can be calcuated, from the equation (\ref{eq:av_SFR M*}).
@@
 
-\begin{figure}[htbp]
+\begin{figure}[!htpb]
 \centering
@@
 \subsection{Constant \(\tau\)}
-\label{sec:org4942cfd}
+\label{sec:org3a3fe8a}
 
@@
 \subsection{Comparing the two results}
-\label{sec:org2d98e85}
+\label{sec:org26db3cc}
 
 \subsubsection{Comparing the \(x\)'s}
-\label{sec:org7c16f4c}
+\label{sec:orga60f19a}
 
@@
 \end{figure}
-\begin{figure}[htbp]
+\begin{figure}[!htpb]
 \centering
@@
 
-\begin{figure}[htbp]
+\begin{figure}[!htpb]
 \centering
-\includegraphics[width=.9\linewidth]{./figs/x_tsf-x_tau-color_logcolor.png}
+\includegraphics[width=.9\linewidth]{./figs/x_tsf-x_tau-color_color.png}
 \caption{\label{fig:Comparing the two x, according to their color index}Comparing the two x, according to their color index}
@@
 \subsubsection{Comparing the normalization constants}
-\label{sec:orgcf339e2}
+\label{sec:org4dd08f6}
 
-\begin{figure}[htbp]
+\begin{figure}[!htpb]
 \centering
@@
 
-\section{The gas depletion timescale \(\tau_g\)}
-\label{sec:org33bc00a}
+\section{The gas depletion timescale \(\tau_g\) \label{SEC:tau_g}}
+\label{sec:orgc1cc7d3}
 
 The gas depletion timescale \(\tau_g\) measures the time taken by a galaxy to exhaust its gas content Mg given the current SFR\autocites{nageshSimulationsStarformingMainsequence2023}[][]{pflamm-altenburgFundamentalGasDepletion2009}.
-$$
+\begin{equation}\label{eq:tau_g}
 \tau_g=\frac{M_g}{\dot{M_*}}=\frac{M_g}{SFR}
-$$
+\end{equation}
 
-\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=.9\linewidth]{./figs/tau_g-Mg-color_SFR.png}
+\end{center}
+\begin{figure}[!htpb]
 \centering
-\includegraphics[width=.9\linewidth]{./figs/tau_g-Mg-color_StellarMass.png}
-\caption{\label{fig:$\tau_g = f(M_g)$, with the Stellar Mass of the galaxies}\(\tau_g = f(M_g)\), with the Stellar Mass of the galaxies}
+\includegraphics[width=.9\linewidth]{./figs/log_SFR_0-log_tau_g-color_logMg.png}
+\caption{\label{fig:Correlation of the $\tau_g$ with the SFR and the gas mass}Correlation of the \(\tau_g\) with the SFR and the gas mass}
 \end{figure}
 
-\begin{figure}[htbp]
+Despite a weak logarithmic correlation (as indicated by \(R^2 = 32\%\)), there is a noticeable trend of decreasing \(\tau_g\) with increasing SFR and \(M_g\).
+
+\begin{figure}[!htpb]
 \centering
-\includegraphics[width=.9\linewidth]{./figs/logStellarMass-log_tau_g-color_log_SFR_0.png}
+\includegraphics[width=.9\linewidth]{./figs/logStellarMass-log_tau_g-color_log_tau.png}
 \caption{\label{fig:Correlation of the $\tau_g$ with the SFR and the Stellar mass}Correlation of the \(\tau_g\) with the SFR and the Stellar mass}
@@
 
-Even though the logarithmic correlation is low (\(R^2 = 21\%\)), there seems to be a pattern wherein the decrease of \(\tau_g\) corresponds to an increase in the values of the Stellar Mass and the current star formation \(SFR_0\).
+The logarithmic correlation between \(\tau_g-M_*\) is low (\(R^2 = 21\%\)), there seems to be a pattern wherein the decrease of \(\tau_g\) corresponds to an increase in the values of the Stellar Mass, but there does not seem to be one for \(\tau_g-\tau\)
 
-\begin{figure}[htbp]
+\begin{figure}[!htpb]
 \centering
-\includegraphics[width=.9\linewidth]{./figs/logMt-log_tau_g-color_logMg.png}
+\includegraphics[width=.9\linewidth]{./figs/logMt-log_tau_g-color_log_tsf.png}
 \caption{\label{fig:Correlation of the $\tau_g$ with the total mass and the mass of the gas}Correlation of the \(\tau_g\) with the total mass and the mass of the gas}
@@
 
-Again it can be observed that as the \(\tau_g\) decreases, the corresponding values of \(M_t\) and \(M_g\) increase, but the logarithmic correlation is again low (\(R^2 = 11\%\)).
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/color-log_tau_g-color_log_Mass_ratio.png}
+\caption{\label{fig:Correlation of the $\tau_g$ with the color index}Correlation of the \(\tau_g\) with the color index}
+\end{figure}
 
-There is a notable trend, wherein for high masses we have a shorter timescale
+Again it can be observed that as the \(\tau_g\) decreases, the corresponding values of \(M_t\) increase, but the logarithmic correlation is again low (\(R^2 = 11\%\)), and there is no clear correlation between \(\tau_g-t_{sf}\)
+
+There is a notable trend, wherein for high masses we have a shorter timescale.
 
 \section{Mass relations}
-\label{sec:org630e948}
+\label{sec:org4c8a4bc}
 
-Many of the galaxies masses have a high correlation with each other, and also help us undarstand the previous calculations.
+Many of the galaxies masses have a high correlation with each other, and also help us understand the previous calculations.
 
-\begin{figure}[htbp]
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/logMg-logStellarMass-color_color.png}
+\caption{\label{fig:mg_SMass}mg\textsubscript{SMass}}
+\end{figure}
+
+For the plot \ref{fig:mg_SMass}:
+\begin{equation}\label{eq:logMg-logStellarMass}
+\begin{align}
+& $M_g$ = (1.098(35) \times 10^{0})\cdot $M_*$ + (-7.9(2.9) \times 10^{-1}) \\ 
+& \textrm{with correlation } R^2=64\%
+\end{align}
+\end{equation}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/logStellarMass-logM26-color_log_tau_g.png}
+\caption{\label{fig:SMass_m26}SMass\textsubscript{m26}}
+\end{figure}
+
+For the plot \ref{fig:SMass_m26}:
+
+\begin{equation}\label{eq:logStellarMass-logM26}
+\begin{align}
+& M26 = (1.076(23) \times 10^{0})\cdot M* + (-1.8(1.9) \times 10^{-1}) \\ 
+& \textrm{with correlation } R^2=80\%
+\end{align}
+\end{equation}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/logMg-logM26.png}
+\caption{\label{fig:mg_m26}mg\textsubscript{m26}}
+\end{figure}
+
+For the plot \ref{fig:mg_m26}:
+
+\begin{equation}\label{eq:logMg-logM26}
+\begin{align}
+& M26 = (1.41(4) \times 10^{0})\cdot Mg + (-2.92(30) \times 10^{0}) \\ 
+& \textrm{with correlation } R^2=74\%
+\end{align}
+\end{equation}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/logStellarMass-logMt-color_log_SFR_0.png}
+\caption{\label{fig:SMass_mt}SMass\textsubscript{mt}}
+\end{figure}
+
+For the plot \ref{fig:SMass_mt}:
+\begin{equation}\label{eq:logStellarMass-logMt}
+\begin{align}
+& $M_t$ = (8.41(9) \times 10^{-1})\cdot $M_*$ + (1.69(8) \times 10^{0}) \\ 
+& \textrm{with correlation } R^2=94\%
+\end{align}
+\end{equation}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/logMg-logMt-color_log_SFR_0.png}
+\caption{\label{fig:mg_mt}mg\textsubscript{mt}}
+\end{figure}
+
+For the plot \ref{fig:mg_mt}:
+\begin{equation}\label{eq:logMg-logMt-color_log_SFR_0}
+\begin{align}
+& $M_t$ = (1.065(23) \times 10^{0})\cdot $M_g$ + (-1.5(1.9) \times 10^{-1}) \\ 
+& \textrm{with correlation } R^2=81\%
+\end{align}
+\end{equation}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/logM26-logMt.png}
+\caption{\label{fig:m26_mt}m26\textsubscript{mt}}
+\end{figure}
+
+\begin{equation}\label{eq:logM26-logMt}
+\begin{align}
+& M26 = (6.64(12) \times 10^{-1})\cdot $M_t$ + (2.85(11) \times 10^{0}) \\ 
+& \textrm{with correlation } R^2=85\%
+\end{align}
+\end{equation}
+
+There are many plots exhibiting a correlation of \(R^2>80%\), indicating that we can utilize those functions to estimate the masses of the galaxies in the LCV with a high degree of confidence.
+
+The \(M_t-M_*\) (\ref{fig:SMass_mt}) plot is particularly noteworthy, displaying a correlation  of \(R^2 = 94\%\).
+This plot also indicates that galaxies with greater total and stellar masses tend to have higher SFR, consistent with the findings in section \ref{SEC:tau_g} where \(\tau_g\) decreases with increasing masses.
+
+This phenomenon is likely due to the fact that galaxies with higher masses possess greater potential energy, which accelerates the star formation process.
+The galaxies with a high Mass ratio \(M_r\) could also help the process due to their dense regions and the resulting strong local gravitational potential.
+
+\begin{figure}[!htpb]
 \centering
 \includegraphics[width=.9\linewidth]{./figs/log_tsf-log_Mass_ratio-color_color.png}
+\caption{\label{fig:tsf_mr}tsf\textsubscript{mr}}
+\end{figure}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/color-log_Mass_ratio-color_logMt.png}
+\caption{\label{fig:col_Mr}col\textsubscript{Mr}}
+\end{figure}
+
+From the \ref{fig:col_Mr}, we conclude that when the color index is higher the Mass ratio decreases, which is to be expected, since the higher the B-FUV the more active the star formation of the galaxy.
+
+\section{Variations in Star Formation Rate Across the Different Masses}
+\label{sec:orga487cc5}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/log_SFR_0-color.png}
 \caption{\label{fig:None}None}
@@
 
-As expected, the older the galaxy the mass ratio is higher, and the color index agrees ($\backslash$?)
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/log_SFR_0-logStellarMass-color_log_tau_g.png}
+\caption{\label{fig:None}None}
+\end{figure}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/log_SFR_0-log_tau_g-color_logStellarMass.png}
+\caption{\label{fig:None}None}
+\end{figure}
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/log_SFR_0-logMt-color_log_tau_g.png}
+\caption{\label{fig:None}None}
+\end{figure}
 

### 2023-04-07 final.py
fixing the latex figures in latex

@@ -6,6 +6,8 @@ import seaborn as sns
 import statsmodels.api as sm
 import statsmodels.formula.api as smf
 from tabulate import tabulate
+import uncertainties as unc
+
 
 
 pd.set_option('display.float_format', lambda x: '%.2E' % x)
@@ -13,7 +15,7 @@ pd.set_option('display.float_format', lambda x: '%.2E' % x)
 def caption(fname,caption,name = None):
     if name == None:
         name = caption
-    return "#+caption:{} \n#+name: fig:{} \n#+label: fig:{} \n[[./{}]]".format(caption,name,name,fname)
+    return "#+name: fig:{} \n#+label: fig:{} \n#+caption:{} \n#+ATTR_LaTeX: :placement [!htpb]\n[[./{}.png]]".format(caption,name,name,fname)
 
 def simple_regplot(data ,
     X, Y, cap = None, name = None, n_std=2, n_pts=100, ax=None, scatter_kws=None, line_kws=None, ci_kws=None):
@@ -56,7 +58,7 @@ def simple_regplot(data ,
     ax.legend(loc = "best")
     if scatter_kws == {}:
         lab = X+"-"+Y
-        fname = "graphs/"+lab
+        fname = "figs/"+lab
         plt.savefig(fname)
         plt.close()
     else:
@@ -64,14 +66,14 @@ def simple_regplot(data ,
         PCM=ax.get_children()[2] #get the mappable, the 1st and the 2nd are the x and y axes
         plt.colorbar(PCM, ax=ax).set_label(col)
         lab = X+"-"+Y+"-color_"+col
-        fname = "graphs/"+lab
+        fname = "figs/"+lab
         plt.savefig(fname)
         plt.close()
 
     if name == None:
         name = cap
 
-    Cap = "#+caption:{} \n#+name: fig:{} \n#+label: fig:{} \n[[./{}]]".format(cap,name,name,fname)
+    Cap = "#+name: fig:{} \n#+label: fig:{} \n#+caption:{}\n#+ATTR_LaTeX: :placement [!htpb] \n[[./{}.png]]".format(cap,name,name,fname)
[…]

### 2023-04-07 Finding_Adel.tex
First draft
I had already found something from the previous branch and I added a new pdf

% Created 2023-04-06 Thu 00:06
% Intended LaTeX compiler: pdflatex
\documentclass[a4paper,twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{tgbonum}
\usepackage{biblatex}
\addbibresource{/home/dp/Documents/Research_paper_SFR/bibl/bibliography/bibliography.bib}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{hyperref}
\let\description\compactdesc
\raggedbottom
\date{\today}
\title{Finding Adel}
\hypersetup{
 pdfauthor={},
 pdftitle={Finding Adel},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2 (Org mode 9.6.1)}, 
 pdflang={English}}
\begin{document}

\maketitle
According to P. Kroupa et al. 2020\autocite{kroupaConstraintsStarFormation2020} current star formation rates of galaxies can be described by the 'delayed-\(\tau\)' model as

\begin{equation} \label{eq:SFR}
SFR_{0,del}=\frac{A_{del}xe^{-x}}{\tau},\text{ where } x=\frac{t_{sf}}{\tau}
\end{equation}

\noindent
where \(\tau\) is the star formation time-scale,  \(t_{sf}\) is the real time of star formation in a given galaxy and \(A_{del}\) a normalization constant.

For a galaxy that forms stars from the time t\textsubscript{1} to t\textsubscript{2}=the pressent day (if the galaxy is still forming stars) the SFH can be written as \(SFR(t) = \overline{SFR}+\Delta SFR(t)\), such that the average SFR of the galaxy can be witten as

\begin{equation}\label{eq:int of av_SFR}
\overline{SFR} = \frac{1}{t_{sf}} \left(\int^{t_2}_{t_1}\overline{SFR}dt+ \int^{t_2}_{t_1}\Delta SFR(t)\right)
\end{equation}
with temporal deviations from \(\overline{SFR}\) satisfying:

$$\int^{t_2}_{t_1} \Delta SFR dt = 0M_\odot$$

So from the equations (\ref{eq:SFR}) and (\ref{eq:int of av_SFR}) we get the averge SFR:

\begin{equation}\label{eq:av_SFR-x}
\overline{SFR_{del}}=\frac{A_{del}}{t_{sf}}[1-(1+x)e^{-x}]
\end{equation}
and can also be defined by the present day stellar mass

\begin{equation}\label{eq:av_SFR M*}
    \overline{SFR}=\frac{\zeta M_*}{t_{sf}}
\end{equation}
\noindent where \(\zeta\) accommodates for mass-loss through stellar evolution and \(\zeta\approx 1.3\).

From the equations (\Ref{eq:int of av_SFR}) and (\ref{eq:av_SFR-x}) we can derive that the \(A_{del}\) must be independent from the time/ constant throughout the life of the galaxy.

Also from the equation (\ref{eq:SFR}) we can find the units of the \(A_{del}\)
\begin{equation} \label{eq:units}
\begin{align}
\left[SFR_{0,del}\right]&=\frac{\left[A_{del}\right]\left[x\right]\left[e^{-x}\right]}{\left[\tau\right]}\\
\frac{[M_*]}{[time]}& = \frac{[A_{del}]\cdot 1\cdot 1}{[time]}\\
[M_*]& = [A_{del}]
\end{align}
\end{equation}

So we can expect that the \(A_{del}\) can be expressed as
\begin{equation}\label{eq:A=f(M)}
A_{del}=c\cdot M \Leftrightarrow \log(A_{del})= log(M)+log(c)
\end{equation}
\noindent where c is a constant and M the stellar mass (\(M_*\)), the gas mass (\(M_g\)) or the total mass of galaxy(\(M_t = M_* + M_g\)).

The equations (\ref{eq:SFR}) and (\ref{eq:av_SFR-x}) create a system of 2 equations and 3 variables (the SFR and the stellar masses are given), since A\textsubscript{del} has never been calculated

\section{Constant \(t_{sf}\)}
\label{sec:orge82f914}

The observed ages of galactic discs are \(t_{sf}\approx 12\) Gyr\autocite{knoxSurveyCoolWhite1999}, so we assume an approximation of \(t_{sf}=12.5\) Gyr. Having one out of the three variables as a constant we can calculate the \(A_{del}|_{t_{sf}}\) and \(\tau|_{t_{sf}}\) and plot them (figures \ref{fig:A-x_tsf} and \ref{fig:A-tau_tsf}).

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/x-A_tsf.png}
\caption{\label{fig:A-x_tsf}\(A_{del} = f(x)\) for constant t\textsubscript{sf}}
\end{figure}

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/T-A_tsf.png}
\caption{\label{fig:A-tau_tsf}\(A_{del} = f(\tau)\) for constant t\textsubscript{sf}}
\end{figure}

\section{Constant \(\tau\)}
\label{sec:org8d5bda4}

Now assuming for a constant \(\tau = 3.5\) Gyr the system can again be solved numerically for each galaxy and the values of \(A_{del}|_{\tau}\) and \(t_{sf}|_{\tau}\) can be found and plotted (figures \ref{fig:A-x_tau} and \ref{fig:A-tsf_tau}).

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/x-A_tau.png}
\caption{\label{fig:A-x_tau}\(A_{del} = f(x)\) for constant \(\tau\)}
\end{figure}

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/T-A_tau.png}
\caption{\label{fig:A-tsf_tau}\(A_{del} = f(t_{sf})\) for constant \(\tau\)}
\end{figure}

\section{Finding the \(A_{del} = f(\text{Mass})\) relation}
\label{sec:orgb5ebed2}

If we plot the \(A_{del}\) with the 3 given masses of each galaxy, both for a constant \(\tau\) and a constant \(t_{sf}\), we observe that indeed there is a correlation in the form of:
$$
\log(A_{del}) = c_1\log(\text{Mass})+c_2
$$

\begin{enumerate}
\item For a constant \(t_{sf}\) the correlations are:
\begin{enumerate}
\item Total mass: \(R^2=48\%\) (Fig. \ref{fig:A_tsf_Mt})
\item Mass of the Gasses: \(R^2=43\%\) (Fig. \ref{fig:A_tsf_Mg})
\item Stellar Mass: \(R^2=44\%\) (Fig. \ref{fig:A_tsf_StellarMass})
\end{enumerate}

\item For a constant \(\tau\) the correlations are:
\begin{enumerate}
\item Total mass: \(R^2=91\%\) (Fig. \ref{fig:A_tau_Mt})
\item Mass of the Gasses: \(R^2=70\%\) (Fig. \ref{fig:A_tau_Mg})
\item Stellar Mass: \(R^2=90\%\) (Fig. \ref{fig:A_tau_StellarMass})
\end{enumerate}
\end{enumerate}

In both cases the best correlation is  \(A_{del} = f(M_t)\) and for \(\tau =\) const. the correlation is excelent.
\begin{equation}\label{eq:logMt-log_A_tsf-color_x_tsf}
\log(A_{del}|_t_{sf}) = (9.6(4) \times 10^{-1})\cdot \log(M_t) + (8(4) \times 10^{-1})
\end{equation}
\begin{equation}\label{eq:logMt-log_A_tau-color_x_tau}
\log(A_{del}|_\tau) = (1.025(14) \times 10^{0})\cdot \log(M_t) + (-3.0(1.2) \times 10^{-1})
\end{equation}

For both equations (\ref{eq:logMt-log_A_tsf-color_x_tsf}) and (\ref{eq:logMt-log_A_tau-color_x_tau}) \(c_1\approx 1\) so they fit the equation (\ref{eq:A=f(M)}).

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/logMt-log_A_tsf-color_x_tsf.png}
\caption{\label{fig:A_tsf_Mt}Total Mass \(M_t\) - \(A_{del}|_{t_{sf}}\)}
\end{figure}

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/logMg-log_A_tsf-color_x_tsf.png}
\caption{\label{fig:A_tsf_Mg}Mass of the gasses \(M_g\) - \(A_{del}|_{t_{sf}}\)}
\end{figure}

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/logStellarMass-log_A_tsf-color_x_tsf.png}
\caption{\label{fig:A_tsf_StellarMass}Stellar Mass \(M_*\) - \(A_{del}|_{t_{sf}}\)}
\end{figure}

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/logMt-log_A_tau-color_x_tau.png}
\caption{\label{fig:A_tau_Mt}Total Mass \(M_t\) - \(A_{del}|_{\tau}}\)}
\end{figure}

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/logMg-log_A_tau-color_x_tau.png}
\caption{\label{fig:A_tau_Mg}Mass of the gasses \(M_g\) - \(A_{del}|_{\tau}\)}
\end{figure}

\begin{figure}[!htpb]
\centering
\includegraphics[width=.9\linewidth]{./figs/logStellarMass-log_A_tau-color_x_tau.png}
\caption{\label{fig:A_tau_StellarMass}Stellar Mass \(M_*\) - \(A_{del}|_{\tau}}\)}
\end{figure}

\pagebreak
\printbibliography
\end{document}

### 2023-05-07 paper2.tex
before fedora update
-fixed the table,
-added some dataframes,
- started the presentation

@@
-% Created 2023-03-24 Fri 00:20
+% Created 2023-04-30 Sun 20:08
 % Intended LaTeX compiler: pdflatex
@@
 \maketitle
+
+\subsection{{\bfseries\sffamily TODO} no indent}
+\label{sec:org8d9b93a}
+\subsection{{\bfseries\sffamily TODO} fullstops}
+\label{sec:orgde0c807}
+\subsection{{\bfseries\sffamily TODO} Units in the plots}
+\label{sec:org1a3080c}
+
 \begin{abstract}
 The paper investigates the properties of galaxies in the Local Cosmological Volume (LCV), using the Catalogue of Neighboring Galaxies\autocite{karachentsevUPDATEDNEARBYGALAXY2013} and its updated version from the ``Catalog \& Atlas of the LV galaxies'' database\autocite{CatalogLVGalaxies}.
-The properties studied include the galaxy types, their various masses, the star formation rates (SFRs) and the star formation timescale \(\tau\), gas depletion timescale \(\tau_g\).
+The properties studied include the galaxy types, their various masses, the star formation rates (SFRs) and the star formation timescale \(\tau\), gas depletion timescale \(\tau_g\) and the star formation time \(t_{sf}\).
 The paper aims to understand the distribution and correlation of these properties in the sample of galaxies in the LCV, and how they relate to current astrophysical theories.
-Additionally, the paper discusses the conditions for star formation and the implications of the observed properties on galaxy evolution.
 \end{abstract}
@@
 \section{The Galaxies in the Local Cosmological Volume (LCV)}
-\label{sec:org6580427}
+\label{sec:org120a319}
 
@@
 and Makarov  et al.
-2013\autocite{karachentsevUPDATEDNEARBYGALAXY2013}) and its updated version from the ``Catalog \& Atlas of the LV galaxies'' database\autocite{CatalogLVGalaxies}  are used to extract the B-band, FUV $\backslash$& K-band luminosities\footnote{We use the FUV and B measurments to calculate the B-FUV color index.} , the types of the galaxie\footnote{TType=Morphology type code according to the classification by de Vaucouleurs/ Tdw1=Dwarf galaxy morphology/ Tdw2=Dwarf galaxy surface brightness morphology}s, the mass within the Holmberg radius (M26), the Hydrogen masses of the galaxies (\(M_{HI}\)) and the SFRs based on integrated  H and far-ultraviolet (FUV) measurments for galaxies within a distance of
-\(\approx 11\) Mpc. Some of those values contain limit flags, which we exclude from our present analysis. This gives a sample of 793 galaxies from 1248. From the remaing galaxies we have
-
-\begin{table}[hc]
-\centering
-\begin{tabular}{lr}
-\toprule
-{} &    0 \\
-\midrule
-Name    &  793 \\
-FUVmag  &  687 \\
-TType   &  793 \\
-Tdw1    &  580 \\
-Tdw2    &  568 \\
-Bmag    &  790 \\
-SFR\_Ha  &  566 \\
-SFR\_FUV &  688 \\
-K       &  789 \\
-MHI     &  643 \\
-color   &  686 \\
-\bottomrule
-\end{tabular}
-\end{table}
+2013\autocite{karachentsevUPDATEDNEARBYGALAXY2013}) and its updated version from the ``Catalog \& Atlas of the LV galaxies'' database\autocite{CatalogLVGalaxies}  are used to extract the B-band, FUV $\backslash$& K-band luminosities\footnote{We use the FUV and B measurments to calculate the B-FUV color index.} , the types of the galaxie\footnote{TType=Morphology type code according to the classification by de Vaucouleurs/ Tdw1=Dwarf galaxy morphology/ Tdw2=Dwarf galaxy surface brightness morphology}s, the mass within the Holmberg radius (M26), the Hydrogen masses of the galaxies (\(M_{HI}\)) and the SFRs based on integrated  H and far-ultraviolet (FUV) measurments for galaxies within a distance of \(\approx 11\) Mpc.
+Some of those values contain limit flags, which we exclude from our present analysis.
+This gives a sample of 793 galaxies from 1248.
+From the remaing galaxies we have
 
 \begin{center}
-\begin{tabular}{|l|l|}
+\begin{tabular}{lr}
+Measurment & Number of Galaxies\\[0pt]
 \hline
-Measurment & Number of Galaxies \\
-\hline
+Name & 793\\[0pt]
+FUVmag & 687\\[0pt]
+TType & 793\\[0pt]
+Tdw1 & 580\\[0pt]
+Tdw2 & 568\\[0pt]
+Bmag & 790\\[0pt]
+SFR\textsubscript{Ha} & 566\\[0pt]
+SFR\textsubscript{FUV} & 688\\[0pt]
+K & 789\\[0pt]
+MHI & 643\\[0pt]
+color & 686\\[0pt]
 \end{tabular}
@@
 $$
-
+\noindent
 if both \(SFR_{H\alpha},SFR_{FUV}\) measurments are available. If only one only one of them is given, then the SFR is equal to the given SFR value
@@
 \section{Types of galaxies}
-\label{sec:org9a48829}
+\label{sec:orgd4afc9c}
 
@@
 
-Most of the galaxies in the LCV are Higly Irregular galaxies followed by lenticular galaxies
+Most of the galaxies in the LCV are Irregular galaxies followed by lenticular galaxies
 
 Out of the 1248 galaxies the 1022 are dwarf galaxies
+RODO
+
+\subsection{{\bfseries\sffamily TODO} write a table with the types}
+\label{sec:org6c7eaf8}
 
@@
 \section{Delayed-\(\tau\) model}
-\label{sec:org5bed0e8}
+\label{sec:orgee2851e}
 
-According to P. Kroupa et al. 2020\autocite{kroupaConstraintsStarFormation2020} current star formation rates of galaxies can be described by the 'delayed-\(\tau\)' mode as
+According to P. Kroupa et al. 2020\autocite{kroupaConstraintsStarFormation2020} current star formation rates of galaxies can be described by the 'delayed-\(\tau\)' model as
 
@@
 
+\noindent
 where \(\tau\) is the star formation time-scale,  \(t_{sf}\) is the real time of star formation in a given galaxy and \(A_{del}\) a normalization constant.
@@
 \subsection{Constant \(t_{sf}\)}
-\label{sec:org0892bf5}
+\label{sec:orgd5bd959}
 The observed ages of galactic discs are \(t_{sf}\approx 12\) Gyr\autocite{knoxSurveyCoolWhite1999}, so assuming an approximation of \(t_{sf}=12.5\) Gyr, the \(\overline{SFR_{del}}\) can be calcuated, from the equation (\ref{eq:av_SFR M*}).
@@
 
-\begin{center}
-\includegraphics[width=.9\linewidth]{figs/T-A_tsf.png}
-\end{center}
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/T-A_tsf.png}
+\caption{\label{fig:$A_{del} = f(\tau)$ for constant t_{sf}}\(A_{del} = f(\tau)\) for constant t\textsubscript{sf}}
+\end{figure}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/logMt-log_A_tsf-color_x_tsf.png}
+\caption{\label{fig:A_tsf_Mt}Total Mass \(M_t\) - \(A_{del}|_{t_{sf}}\)}
+\end{figure}
+\begin{equation}\label{eq:logMt-log_A_tsf-color_x_tsf}
+\begin{align}
+& $log(A_{del}|_t_{sf}) = (9.6(4) \times 10^{-1})\cdot $log(M_t)$ + (8(4) \times 10^{-1}) \\ 
+& \textrm{with correlation } R^2=48\%
+\end{align}
+\end{equation}
+\noindent
 
 \subsection{Constant \(\tau\)}
-\label{sec:org3a3fe8a}
+\label{sec:org46757ea}
 
@@
 
-using this equation \(x\) and \(A_{del}\) can be calcuated numerically.
+using this equation \(x\) and \(A_{del}\) can be calculated numerically.
 
@@
 
-\begin{center}
-\includegraphics[width=.9\linewidth]{figs/T-A_tau.png}
-\end{center}
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/T-A_tau.png}
+\caption{\label{fig:$A_{del} = f(t_{sf})$ for constant $\tau$}\(A_{del} = f(t_{sf})\) for constant \(\tau\)}
+\end{figure}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/logStellarMass-log_A_tau-color_x_tau.png}
+\caption{\label{fig:A_tau_Mt}Total Mass \(M_t\) - \(A_{del}|_{\tau}\)}
+\end{figure}
+\begin{equation}\label{eq:logStellarMass-log_A_tau-color_x_tau}
+\begin{align}
+& $log(A_{del}|_\tau) = (8.74(12) \times 10^{-1})\cdot $log(M_t)$ + (1.31(10) \times 10^{0}) \\ 
+& \textrm{with correlation } R^2=90\%
+\end{align}
+\end{equation}
+\noindent
 
 \subsection{Comparing the two results}
-\label{sec:org26db3cc}
+\label{sec:org62d708b}
 
 \subsubsection{Comparing the \(x\)'s}
-\label{sec:orga60f19a}
+\label{sec:org7a303ba}
 
@@
 \end{equation}
+\noindent
 
@@
 \subsubsection{Comparing the normalization constants}
-\label{sec:org4dd08f6}
+\label{sec:org4a59895}
 
@@
 
+\subsubsection{Trying to make the A\textsubscript{del} cloud more compact}
+\label{sec:org4bf81bb}
+
+Having found \(x|_{t_sf}\) and \(x|_{\tau}\) we can find a relation between these two values
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/A_tau-A_tsf_Mt.png}
+\caption{\label{fig:Comparison of the 2 A_{del}s according to their total masses}Comparison of the 2 A\textsubscript{del}s according to their total masses}
+\end{figure}
+
+\subsection{Int SFR to find the A\textsubscript{del}}
+\label{sec:org6350c57}
+
+If we integrate equation (\ref{eq:SFR}) we get:
+
+\begin{equation}\label{eq:int SFR}
+\begin{align}
+\int^{t_{sf}}_0 SFR_{del} dt_{sf}&=\int^{t_{sf}}_0 \frac{A_{del}t_{sf}e^{-t_{sf}/\tau}}{\tau^2} dt_{sf}\\
+M_*&=-A_{del} \frac{{\left(t_{\mathit{sf}} \tau + \tau^{2}\right)} e^{\left(-\frac{t_{\mathit{sf}}}{\tau}\right)}}{\tau^{2}}+A_{del}\\
+M_*&=-A_{del}\frac{\tau^2(x+1)e^{-x}}{\tau^2}+A_{del}\\
+M_*& = A_{del}(1-(x+1)e^{-x})\\
+A_{del}&=M_*\frac{e^x}{e^x-x-1}
+\end{align}
+\end{equation}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/A_theor_tau-M*.png}
+\caption{\label{fig:Comparison of the 2 A_{del}s according to their total masses}Comparison of the 2 A\textsubscript{del}s according to their total masses}
+\end{figure}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/log_A_theor_tau-logStellarMass-color_x_tsf.png}
+\caption{\label{fig:Comparison of the A_del according to their Stellar Mass}Comparison of the A\textsubscript{del} according to their Stellar Mass}
+\end{figure}
+
 \section{The gas depletion timescale \(\tau_g\) \label{SEC:tau_g}}
-\label{sec:orgc1cc7d3}
+\label{sec:org325e6be}
 
@@
 
-Despite a weak logarithmic correlation (as indicated by \(R^2 = 32\%\)), there is a noticeable trend of decreasing \(\tau_g\) with increasing SFR and \(M_g\).
+Despite a weak logarithmic correlation (as indicated by \(R^2 = 32\%\) \noindent), there is a noticeable trend of decreasing \(\tau_g\) with increasing SFR and \(M_g\).
 
@@
 
-The logarithmic correlation between \(\tau_g-M_*\) is low (\(R^2 = 21\%\)), there seems to be a pattern wherein the decrease of \(\tau_g\) corresponds to an increase in the values of the Stellar Mass, but there does not seem to be one for \(\tau_g-\tau\)
+The logarithmic correlation between \(\tau_g-M_*\) is low (\(R^2 = 21\%\) \noindent), there seems to be a pattern wherein the decrease of \(\tau_g\) corresponds to an increase in the values of the Stellar Mass, but there does not seem to be one for \(\tau_g-\tau\)
 
@@
 
-Again it can be observed that as the \(\tau_g\) decreases, the corresponding values of \(M_t\) increase, but the logarithmic correlation is again low (\(R^2 = 11\%\)), and there is no clear correlation between \(\tau_g-t_{sf}\)
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/log_tsf-log_tau_g-color_log_tau.png}
+\caption{\label{fig:Correlation of the $\tau_g$ with the color index}Correlation of the \(\tau_g\) with the color index}
+\end{figure}
+
+Again it can be observed that as the \(\tau_g\) decreases, the corresponding values of \(M_t\) increase, but the logarithmic correlation is again low (\(R^2 = 11\%\) \noindent), and there is no clear correlation between \(\tau_g-t_{sf}\)
 
@@
 \section{Mass relations}
-\label{sec:org4c8a4bc}
+\label{sec:org2e3fc57}
 
@@
 \includegraphics[width=.9\linewidth]{./figs/logMg-logStellarMass-color_color.png}
-\caption{\label{fig:mg_SMass}mg\textsubscript{SMass}}
+\caption{\label{fig:mg_SMass}Gas Mass-Stellar Mass plot}
 \end{figure}
@@
 \includegraphics[width=.9\linewidth]{./figs/logStellarMass-logM26-color_log_tau_g.png}
-\caption{\label{fig:SMass_m26}SMass\textsubscript{m26}}
+\caption{\label{fig:SMass_m26}Mass inside the Holmberg radius-Stellar Mass plot}
 \end{figure}
@@
 \includegraphics[width=.9\linewidth]{./figs/logMg-logM26.png}
-\caption{\label{fig:mg_m26}mg\textsubscript{m26}}
+\caption{\label{fig:mg_m26}Mass inside the Holmberg radius-Gas Mass plot}
 \end{figure}
@@
 \includegraphics[width=.9\linewidth]{./figs/logStellarMass-logMt-color_log_SFR_0.png}
-\caption{\label{fig:SMass_mt}SMass\textsubscript{mt}}
+\caption{\label{fig:SMass_mt}Stellar Mass-Total Mass plot}
 \end{figure}
@@
 \includegraphics[width=.9\linewidth]{./figs/logMg-logMt-color_log_SFR_0.png}
-\caption{\label{fig:mg_mt}mg\textsubscript{mt}}
+\caption{\label{fig:mg_mt}Total Mass - Gas Mass plot}
 \end{figure}
@@
 \includegraphics[width=.9\linewidth]{./figs/logM26-logMt.png}
-\caption{\label{fig:m26_mt}m26\textsubscript{mt}}
+\caption{\label{fig:m26_mt}Mass inside the Holmberg radius-Total Mass plot}
 \end{figure}
@@
 
-The \(M_t-M_*\) (\ref{fig:SMass_mt}) plot is particularly noteworthy, displaying a correlation  of \(R^2 = 94\%\).
+The \(M_t-M_*\) (\ref{fig:SMass_mt}) plot is particularly noteworthy, displaying a correlation  of \(R^2 = 94\%\) \noindent.
 This plot also indicates that galaxies with greater total and stellar masses tend to have higher SFR, consistent with the findings in section \ref{SEC:tau_g} where \(\tau_g\) decreases with increasing masses.
@@
 \includegraphics[width=.9\linewidth]{./figs/log_tsf-log_Mass_ratio-color_color.png}
-\caption{\label{fig:tsf_mr}tsf\textsubscript{mr}}
+\caption{\label{fig:tsf_mr}\$\t\textsubscript{sf}\$-Mass ratio \(\left(\frac{M_*}{M_g}\right)\) plot}
 \end{figure}
@@
 \includegraphics[width=.9\linewidth]{./figs/color-log_Mass_ratio-color_logMt.png}
-\caption{\label{fig:col_Mr}col\textsubscript{Mr}}
+\caption{\label{fig:col_Mr}Mass ratio \$\frac{M_*}{M_g}\$-Color index plot}
 \end{figure}
@@
 \section{Variations in Star Formation Rate Across the Different Masses}
-\label{sec:orga487cc5}
+\label{sec:orgb7febe7}
 
@@
 \centering
-\includegraphics[width=.9\linewidth]{./figs/log_SFR_0-logMt-color_log_tau_g.png}
+\includegraphics[width=.9\linewidth]{./figs/logMt-log_SFR_0-color_log_tau_g.png}
 \caption{\label{fig:None}None}
 \end{figure}
+(<statsmodels.regression.linear\textsubscript{model.RegressionResultsWrapper} object at 0x7f3d4e77b190>, '\#+name: fig:None \n\#+caption:None\n\#+ATTR\textsubscript{\LaTeX{}}: :placement [!htpb] \n\begin{center}
+\includegraphics[width=.9\linewidth]{./figs/logMt-log_tau-color_log_tau_g.png}
+\end{center}', 'logMt-log\textsubscript{tau}-color\textsubscript{log}\textsubscript{tau}\textsubscript{g}')
+
+\subsection{{\bfseries\sffamily TODO} put that tau and tsf dont have a correlation with Mt}
+\label{sec:org5dfe35c}
 

### 2023-05-24 presentation.tex
presentation
-presentation
-made the fsolve give only positive values
-found A_del->weird SFR

--- 2023-05-07 paper2.tex
@@
-% Created 2023-04-30 Sun 20:08
+% Created 2023-05-11 Thu 16:48
 % Intended LaTeX compiler: pdflatex
-\documentclass[a4paper,twocolumn]{article}
+\documentclass[presentation]{beamer}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{hyperref}
-\usepackage{breakcites}
-\usepackage{paralist}
-\usepackage{amsmath}
-\usepackage{biblatex}
-\addbibresource{/home/dp/Documents/Research_paper_SFR/bibl/bibliography/bibliography.bib}
-\usepackage{hyperref}
-\usepackage{graphicx}
-\usepackage{caption}
-\usepackage{booktabs}
-\usepackage[T1]{fontenc}
-\usepackage{tgbonum}
-\let\itemize\compactitem
-\let\description\compactdesc
-\let\enumerate\compactenum
+\usetheme{default}
+\usecolortheme{}
+\usefonttheme{}
+\useinnertheme{}
+\useoutertheme{}
 \author{Dimitrios Papachistopoulos}
@@
 \title{Investigations of the galaxies of the LCV}
+
 \hypersetup{
@@
  pdflang={English}}
+\usepackage{biblatex}
+\addbibresource{/home/dp/Documents/Research_paper_SFR/bibl/bibliography/bibliography.bib}
 \begin{document}
@@
 
-\subsection{{\bfseries\sffamily TODO} no indent}
-\label{sec:org8d9b93a}
-\subsection{{\bfseries\sffamily TODO} fullstops}
-\label{sec:orgde0c807}
-\subsection{{\bfseries\sffamily TODO} Units in the plots}
-\label{sec:org1a3080c}
+\begin{frame}[label={sec:org9d0b2d9}]{Abstract}
+\begin{block}{LCV}
+The paper investigates the properties of galaxies in the Local Cosmological Volume (LCV), using the Catalogue of Neighboring Galaxies\autocite{karachentsevUPDATEDNEARBYGALAXY2013} and its updated version from the ``Catalog \& Atlas of the LV galaxies'' database\autocite{CatalogLVGalaxies}.
+\end{block}
+\begin{block}{The studied properties}
+\begin{enumerate}
+\item Galaxy types,
+\item Their various masses,
+\item The star formation rates (SFRs)
+\item Timescales
+\begin{enumerate}
+\item Star formation timescale \(\tau\),
+\item Gas depletion timescale \(\tau_g\)
+\item The star formation time \(t_{sf}\).
+\end{enumerate}
+\end{enumerate}
+\end{block}
+\begin{block}{Goal}
+The paper aims to understand the distribution and correlation of these properties in the sample of galaxies in the LCV, and how they relate to current astrophysical theories.
+\end{block}
+\end{frame}
 
-\begin{abstract}
-The paper investigates the properties of galaxies in the Local Cosmological Volume (LCV), using the Catalogue of Neighboring Galaxies\autocite{karachentsevUPDATEDNEARBYGALAXY2013} and its updated version from the ``Catalog \& Atlas of the LV galaxies'' database\autocite{CatalogLVGalaxies}.
-The properties studied include the galaxy types, their various masses, the star formation rates (SFRs) and the star formation timescale \(\tau\), gas depletion timescale \(\tau_g\) and the star formation time \(t_{sf}\).
-The paper aims to understand the distribution and correlation of these properties in the sample of galaxies in the LCV, and how they relate to current astrophysical theories.
-\end{abstract}
-
-\section{The Galaxies in the Local Cosmological Volume (LCV)}
-\label{sec:org120a319}
-
+\begin{frame}[label={sec:org75f05ef}]{The Galaxies in the Local Cosmological Volume (LCV)}
 The Catalogue of Neigbouring Galaxies (Karachentsev, Igor D.
 and Makarov  et al.
-2013\autocite{karachentsevUPDATEDNEARBYGALAXY2013}) and its updated version from the ``Catalog \& Atlas of the LV galaxies'' database\autocite{CatalogLVGalaxies}  are used to extract the B-band, FUV $\backslash$& K-band luminosities\footnote{We use the FUV and B measurments to calculate the B-FUV color index.} , the types of the galaxie\footnote{TType=Morphology type code according to the classification by de Vaucouleurs/ Tdw1=Dwarf galaxy morphology/ Tdw2=Dwarf galaxy surface brightness morphology}s, the mass within the Holmberg radius (M26), the Hydrogen masses of the galaxies (\(M_{HI}\)) and the SFRs based on integrated  H and far-ultraviolet (FUV) measurments for galaxies within a distance of \(\approx 11\) Mpc.
-Some of those values contain limit flags, which we exclude from our present analysis.
-This gives a sample of 793 galaxies from 1248.
-From the remaing galaxies we have
+2013\autocite{karachentsevUPDATEDNEARBYGALAXY2013}) and its updated version from the ``Catalog \& Atlas of the LV galaxies'' database\autocite{CatalogLVGalaxies}  are used
+
+\begin{block}{Data}
+\begin{enumerate}
+\item The B-band, FUV \& K-band luminosities\footnote{We use the FUV and B measurments to calculate the B-FUV color index.} ,
+\item The types of the galaxie\footnote{TType=Morphology type code according to the classification by de Vaucouleurs/ Tdw1=Dwarf galaxy morphology/ Tdw2=Dwarf galaxy surface brightness morphology}s,
+\item Masses:
+\begin{enumerate}
+\item The mass within the Holmberg radius (M26)\footnote{\uline{Definition} \alert{Holmberg radius}: \texttt{A convenient measure of the optical extent of a galaxy is the /Holmberg radius/ (Holmberg 1958), which is the major-axis radius at a surface brightness of 26.5 photographic mag arcsec-2}\autocite{MassesMasstoLightRatios}},
+\end{enumerate}
+\begin{enumerate}
+\item The Hydrogen masses of the galaxies (\(M_{HI}\))
+\end{enumerate}
+\item Their SFRs based on integrated  H and far-ultraviolet (FUV) measurments
+\end{enumerate}
+
+\begin{enumerate}
+\item The galaxies are within a distance of \(\approx 11\) Mpc.
+\item Some of those values contain limit flags, which we exclude from our present analysis. This gives a sample of 793 galaxies from 1248
+\end{enumerate}
 
 \begin{center}
-\begin{tabular}{lr}
-Measurment & Number of Galaxies\\[0pt]
+\begin{tabular}{|l|l|}
 \hline
-Name & 793\\[0pt]
-FUVmag & 687\\[0pt]
-TType & 793\\[0pt]
-Tdw1 & 580\\[0pt]
-Tdw2 & 568\\[0pt]
-Bmag & 790\\[0pt]
-SFR\textsubscript{Ha} & 566\\[0pt]
-SFR\textsubscript{FUV} & 688\\[0pt]
-K & 789\\[0pt]
-MHI & 643\\[0pt]
-color & 686\\[0pt]
+Measurment & Number of Galaxies \\
+\hline
+Name & 793 \\
+FUVmag & 687 \\
+TType & 793 \\
+Tdw1 & 580 \\
+Tdw2 & 568 \\
+Bmag & 790 \\
+SFR$\backslash$\_Ha & 566 \\
+SFR$\backslash$\_FUV & 688 \\
+K & 789 \\
+MHI & 643 \\
+color & 686 \\
+\hline
 \end{tabular}
@@
 
-The K-band values are converted to the total Stellar Masses of each galaxy according to the mass-to-light ratio of 0.6 (\cite{lelliSPARCMASSMODELS2016}), and the \(M_{HI}\) can be converted to the total mass of the gas of the galaxy using the equation \(M_g=1.33\,M_{HI}\)
-
-The total SFR of each galaxy can be calcuated by
+\begin{enumerate}
+\item The K-band values are converted to the total Stellar Masses of each galaxy according to the mass-to-light ratio\autocite{lelliSPARCMASSMODELS2016}
+$$\frac{M_*}{K}=0.6$$
+\item The \(M_{HI}\) can be converted to the total mass of the gas of the galaxy using the equation $$M_g=1.33\cdot M_{HI}$$
+\end{enumerate}
+\begin{enumerate}
+\item The total SFR of each galaxy can be calcuated by
+\end{enumerate}
 
@@
 $$
-\noindent
-if both \(SFR_{H\alpha},SFR_{FUV}\) measurments are available. If only one only one of them is given, then the SFR is equal to the given SFR value
 
@@
 $$
+\begin{enumerate}
+\item We use the FUV and B measurments to calculate the B-FUV color index.
+\end{enumerate}
 
-The condition \(SFR_o\geq 10^{-3}M_\odot yr^{-1}\) leaves 579
-galaxies. This condition is applied due to the reasons given in the P. Kroupa,M. Haslbauer, I. Banik, S. T. Nagesh and J. Pflamm-Altenburg et al. 2020 \cite{kroupaConstraintsStarFormation2020}
+The condition \(SFR_o\geq 10^{-3}M_\odot yr^{-1}\) leaves 579 galaxies.
+This condition is applied due to the reasons given in the P.
+Kroupa,M.
+Haslbauer, I.
+Banik, S.
+T.
+Nagesh and J.
+Pflamm-Altenburg et al.
+2020 \cite{kroupaConstraintsStarFormation2020}
+\end{block}
+\end{frame}
 
-\section{Types of galaxies}
-\label{sec:orgd4afc9c}
-
+\begin{frame}[label={sec:org236576b}]{Types of galaxies}
 Using the dataset of 1248 galaxies, do before using the condition and removing the galaxies with the flags, the below histograms can be plotted.
 
-Most of the galaxies in the LCV are Irregular galaxies followed by lenticular galaxies
+\begin{itemize}
+\item Most of the galaxies in the LCV are Irregular galaxies followed by lenticular galaxies
 
-Out of the 1248 galaxies the 1022 are dwarf galaxies
-RODO
+\item Out of the 1248 galaxies the 1022 are dwarf galaxies
 
-\subsection{{\bfseries\sffamily TODO} write a table with the types}
-\label{sec:org6c7eaf8}
-
-Most dwarf galaxies have low brightness and are irregulars followed by Dwarf spheroidal.
+\item Most dwarf galaxies have low brightness and are irregulars followed by Dwarf spheroidal.
+\end{itemize}
 
@@
 \end{figure}
+\end{frame}
 
-\section{Delayed-\(\tau\) model}
-\label{sec:orgee2851e}
-
+\begin{frame}[label={sec:org05089e9}]{Delayed-\(\tau\) model}
 According to P. Kroupa et al. 2020\autocite{kroupaConstraintsStarFormation2020} current star formation rates of galaxies can be described by the 'delayed-\(\tau\)' model as
@@
 
-\noindent
 where \(\tau\) is the star formation time-scale,  \(t_{sf}\) is the real time of star formation in a given galaxy and \(A_{del}\) a normalization constant.
@@
 \begin{equation}\label{eq:av_SFR M*}
-    \overline{SFR}=\frac{\zeta M_*}{t_{sf}}
+    \overline{SFR}=\frac{\zeta M_*}{t_{sf}}, \zeta = \approx 1.3
 \end{equation}
-where \(\zeta\) accommodates for mass-loss through stella evolution and \(\zeta\approx 1.3\)
+
+where \(\zeta\) accommodates for mass-loss through stellar evolution
 
@@
 
-\subsection{Constant \(t_{sf}\)}
-\label{sec:orgd5bd959}
+\begin{enumerate}
+\item Constant \(t_{sf}\)
+\item Constant \(\tau\)
+\item Integrate the SFR to find the A\textsubscript{del}
+\end{enumerate}
+
+\begin{block}{Constant \(t_{sf}\)}
 The observed ages of galactic discs are \(t_{sf}\approx 12\) Gyr\autocite{knoxSurveyCoolWhite1999}, so assuming an approximation of \(t_{sf}=12.5\) Gyr, the \(\overline{SFR_{del}}\) can be calcuated, from the equation (\ref{eq:av_SFR M*}).
@@
 
-can be solved numerically for \(x\) and using the equations (\Ref{eq:SFR}) and (\Ref{eq:av_SFR-x}) the \(A_{del}\) and \(\tau\) of each galaxy are found.
+can be solved numerically for \(x\) and using the equations (\ref{eq:SFR}) and (\ref{eq:av_SFR-x}) the \(A_{del}\) and \(\tau\) of each galaxy are found.
 
-\begin{table}[hc]
-\centering
+\begin{center}
 \begin{tabular}{lrrr}
-\toprule
-{} &    A\_tsf &      tau &    x\_tsf \\
-\midrule
-count & 5.78E+02 & 5.79E+02 & 5.79E+02 \\
-mean  & 2.25E+12 & 1.09E+11 & 1.85E+00 \\
-std   & 3.94E+13 & 1.04E+12 & 1.48E+00 \\
-min   & 2.48E+07 & 1.93E+09 & 5.59E-04 \\
-25\%   & 1.41E+08 & 4.18E+09 & 5.65E-01 \\
-50\%   & 6.84E+08 & 7.79E+09 & 1.60E+00 \\
-75\%   & 5.70E+09 & 2.21E+10 & 2.99E+00 \\
-max   & 9.10E+14 & 2.24E+13 & 6.47E+00 \\
-\bottomrule
+ & A\textsubscript{tsf} & tau & x\textsubscript{tsf}\\[0pt]
+\hline
+count & 578 & 579 & 579\\[0pt]
+mean & 2.24715e+12 & 1.08958e+11 & 1.85344\\[0pt]
+std & 3.93675e+13 & 1.04132e+12 & 1.4763\\[0pt]
+min & 2.47798e+07 & 1.93205e+09 & 0.000558601\\[0pt]
+25\% & 1.40573e+08 & 4.18098e+09 & 0.564779\\[0pt]
+50\% & 6.83764e+08 & 7.79265e+09 & 1.60408\\[0pt]
+75\% & 5.70379e+09 & 2.21327e+10 & 2.98973\\[0pt]
+max & 9.10088e+14 & 2.23774e+13 & 6.46982\\[0pt]
 \end{tabular}
-\end{table}
+\end{center}
 
@@
 \end{figure}
+
 \begin{equation}\label{eq:logMt-log_A_tsf-color_x_tsf}
@@
 \noindent
+\end{block}
 
-\subsection{Constant \(\tau\)}
-\label{sec:org46757ea}
-
+\begin{block}{Constant \(\tau\)}
 Assuming for an constant \(\tau=3.5\) Gyr, we cannot use the same \(\overline{SFR}\) since it depends on \(t_{sf}\). Using the equations\textasciitilde{}(\Ref{eq:av_SFR M*}) and (\Ref{eq:ratio})
@@
 \end{figure}
+
 \begin{equation}\label{eq:logStellarMass-log_A_tau-color_x_tau}
@@
 \noindent
+\end{block}
 
-\subsection{Comparing the two results}
-\label{sec:org62d708b}
-
-\subsubsection{Comparing the \(x\)'s}
-\label{sec:org7a303ba}
-
+\begin{block}{Comparing the two results}
+\begin{block}{Comparing the \(x\)'s}
 Comparing the two different results for x, we see that the \(x|_\tau\) has a lower \(\sigma\)
@@
 \end{figure}
+
 \begin{figure}[!htpb]
@@
 The two results are interrelated through the equation:
+
 \begin{equation}\label{eq:x_tsf-x_tau}
@@
 \end{enumerate}
+\end{block}
 
-\subsubsection{Comparing the normalization constants}
-\label{sec:org4a59895}
-
+\begin{block}{Comparing the normalization constants}
 \begin{figure}[!htpb]
@@
 \end{enumerate}
+\end{block}
 
-\subsubsection{Trying to make the A\textsubscript{del} cloud more compact}
-\label{sec:org4bf81bb}
-
+\begin{block}{Trying to make the A\textsubscript{del} cloud more compact}
 Having found \(x|_{t_sf}\) and \(x|_{\tau}\) we can find a relation between these two values
@@
 \end{figure}
+\end{block}
+\end{block}
 
-\subsection{Int SFR to find the A\textsubscript{del}}
-\label{sec:org6350c57}
-
+\begin{block}{Int SFR to find the A\textsubscript{del}}
 If we integrate equation (\ref{eq:SFR}) we get:
@@
 \end{figure}
+\end{block}
+\end{frame}
 
-\section{The gas depletion timescale \(\tau_g\) \label{SEC:tau_g}}
-\label{sec:org325e6be}
-
+\begin{frame}[label={sec:org40e1c03}]{The gas depletion timescale \(\tau_g\) \label{SEC:tau_g}}
 The gas depletion timescale \(\tau_g\) measures the time taken by a galaxy to exhaust its gas content Mg given the current SFR\autocites{nageshSimulationsStarformingMainsequence2023}[][]{pflamm-altenburgFundamentalGasDepletion2009}.
@@
 
-Despite a weak logarithmic correlation (as indicated by \(R^2 = 32\%\) \noindent), there is a noticeable trend of decreasing \(\tau_g\) with increasing SFR and \(M_g\).
+Despite a weak logarithmic correlation (as indicated by ==), there is a noticeable trend of decreasing \(\tau_g\) with increasing SFR and \(M_g\).
 
@@
 
-The logarithmic correlation between \(\tau_g-M_*\) is low (\(R^2 = 21\%\) \noindent), there seems to be a pattern wherein the decrease of \(\tau_g\) corresponds to an increase in the values of the Stellar Mass, but there does not seem to be one for \(\tau_g-\tau\)
+The logarithmic correlation between \(\tau_g-M_*\) is low (==), there seems to be a pattern wherein the decrease of \(\tau_g\) corresponds to an increase in the values of the Stellar Mass, but there does not seem to be one for \(\tau_g-\tau\)
 
@@
 
-Again it can be observed that as the \(\tau_g\) decreases, the corresponding values of \(M_t\) increase, but the logarithmic correlation is again low (\(R^2 = 11\%\) \noindent), and there is no clear correlation between \(\tau_g-t_{sf}\)
+Again it can be observed that as the \(\tau_g\) decreases, the corresponding values of \(M_t\) increase, but the logarithmic correlation is again low (==), and there is no clear correlation between \(\tau_g-t_{sf}\)
 
 There is a notable trend, wherein for high masses we have a shorter timescale.
+\end{frame}
 
-\section{Mass relations}
-\label{sec:org2e3fc57}
-
+\begin{frame}[label={sec:orgfa6d8ce}]{Mass relations}
 Many of the galaxies masses have a high correlation with each other, and also help us understand the previous calculations.
@@
 For the plot \ref{fig:mg_SMass}:
+
 \begin{equation}\label{eq:logMg-logStellarMass}
@@
 For the plot \ref{fig:SMass_mt}:
+
 \begin{equation}\label{eq:logStellarMass-logMt}
@@
 For the plot \ref{fig:mg_mt}:
+
 \begin{equation}\label{eq:logMg-logMt-color_log_SFR_0}
@@
 
-The \(M_t-M_*\) (\ref{fig:SMass_mt}) plot is particularly noteworthy, displaying a correlation  of \(R^2 = 94\%\) \noindent.
+The \(M_t-M_*\) (\ref{fig:SMass_mt}) plot is particularly noteworthy, displaying a correlation  of ==.
 This plot also indicates that galaxies with greater total and stellar masses tend to have higher SFR, consistent with the findings in section \ref{SEC:tau_g} where \(\tau_g\) decreases with increasing masses.
@@
 From the \ref{fig:col_Mr}, we conclude that when the color index is higher the Mass ratio decreases, which is to be expected, since the higher the B-FUV the more active the star formation of the galaxy.
+\end{frame}
 
-\section{Variations in Star Formation Rate Across the Different Masses}
-\label{sec:orgb7febe7}
-
+\begin{frame}[label={sec:orgbd7dd9c}]{Variations in Star Formation Rate Across the Different Masses}
 \begin{figure}[!htpb]
@@
 \end{figure}
-(<statsmodels.regression.linear\textsubscript{model.RegressionResultsWrapper} object at 0x7f3d4e77b190>, '\#+name: fig:None \n\#+caption:None\n\#+ATTR\textsubscript{\LaTeX{}}: :placement [!htpb] \n\begin{center}
+
+\begin{figure}[!htpb]
+\centering
 \includegraphics[width=.9\linewidth]{./figs/logMt-log_tau-color_log_tau_g.png}
-\end{center}', 'logMt-log\textsubscript{tau}-color\textsubscript{log}\textsubscript{tau}\textsubscript{g}')
+\caption{\label{fig:None}None}
+\end{figure}'
 
-\subsection{{\bfseries\sffamily TODO} put that tau and tsf dont have a correlation with Mt}
-\label{sec:org5dfe35c}
-
+\begin{block}{put that tau and tsf dont have a correlation with Mt}
 \pagebreak
 \printbibliography
+\end{block}
+\end{frame}
 \end{document}

### 2023-07-03 paper2.tex
i dont remember
s

@@
-% Created 2023-04-30 Sun 20:08
+% Created 2023-06-10 Sat 19:05
 % Intended LaTeX compiler: pdflatex
@@
 \subsection{{\bfseries\sffamily TODO} no indent}
-\label{sec:org8d9b93a}
+\label{sec:org4ae1c6d}
 \subsection{{\bfseries\sffamily TODO} fullstops}
-\label{sec:orgde0c807}
+\label{sec:orge244364}
 \subsection{{\bfseries\sffamily TODO} Units in the plots}
-\label{sec:org1a3080c}
+\label{sec:orgaf69437}
 
@@
 \section{The Galaxies in the Local Cosmological Volume (LCV)}
-\label{sec:org120a319}
+\label{sec:org94f634b}
 
@@
 and Makarov  et al.
-2013\autocite{karachentsevUPDATEDNEARBYGALAXY2013}) and its updated version from the ``Catalog \& Atlas of the LV galaxies'' database\autocite{CatalogLVGalaxies}  are used to extract the B-band, FUV $\backslash$& K-band luminosities\footnote{We use the FUV and B measurments to calculate the B-FUV color index.} , the types of the galaxie\footnote{TType=Morphology type code according to the classification by de Vaucouleurs/ Tdw1=Dwarf galaxy morphology/ Tdw2=Dwarf galaxy surface brightness morphology}s, the mass within the Holmberg radius (M26), the Hydrogen masses of the galaxies (\(M_{HI}\)) and the SFRs based on integrated  H and far-ultraviolet (FUV) measurments for galaxies within a distance of \(\approx 11\) Mpc.
+2013\autocite{karachentsevUPDATEDNEARBYGALAXY2013}) and its updated version from the ``Catalog \& Atlas of the LV galaxies'' database\autocite{CatalogLVGalaxies}  are used to extract the B-band, FUV $\backslash$& K-band luminosities\footnote{We use the FUV and B measurments to calculate the <FUV-B> color index.} , the types of the galaxie\footnote{TType=Morphology type code according to the classification by de Vaucouleurs/ Tdw1=Dwarf galaxy morphology/ Tdw2=Dwarf galaxy surface brightness morphology}s, the mass within the Holmberg radius (M26), the Hydrogen masses of the galaxies (\(M_{HI}\)) and the SFRs based on integrated  H and far-ultraviolet (FUV) measurments for galaxies within a distance of \(\approx 11\) Mpc.
 Some of those values contain limit flags, which we exclude from our present analysis.
@@
 \section{Types of galaxies}
-\label{sec:orgd4afc9c}
+\label{sec:org1701b4d}
 
@@
 Out of the 1248 galaxies the 1022 are dwarf galaxies
-RODO
 
 \subsection{{\bfseries\sffamily TODO} write a table with the types}
-\label{sec:org6c7eaf8}
+\label{sec:org421f46e}
 
@@
 \section{Delayed-\(\tau\) model}
-\label{sec:orgee2851e}
+\label{sec:org57c1611}
 
@@
 \subsection{Constant \(t_{sf}\)}
-\label{sec:orgd5bd959}
+\label{sec:org4a83115}
 The observed ages of galactic discs are \(t_{sf}\approx 12\) Gyr\autocite{knoxSurveyCoolWhite1999}, so assuming an approximation of \(t_{sf}=12.5\) Gyr, the \(\overline{SFR_{del}}\) can be calcuated, from the equation (\ref{eq:av_SFR M*}).
@@
 
-\begin{table}[hc]
-\centering
+\begin{center}
 \begin{tabular}{lrrr}
-\toprule
-{} &    A\_tsf &      tau &    x\_tsf \\
-\midrule
-count & 5.78E+02 & 5.79E+02 & 5.79E+02 \\
-mean  & 2.25E+12 & 1.09E+11 & 1.85E+00 \\
-std   & 3.94E+13 & 1.04E+12 & 1.48E+00 \\
-min   & 2.48E+07 & 1.93E+09 & 5.59E-04 \\
-25\%   & 1.41E+08 & 4.18E+09 & 5.65E-01 \\
-50\%   & 6.84E+08 & 7.79E+09 & 1.60E+00 \\
-75\%   & 5.70E+09 & 2.21E+10 & 2.99E+00 \\
-max   & 9.10E+14 & 2.24E+13 & 6.47E+00 \\
-\bottomrule
+ & A\textsubscript{tsf} & tau & x\textsubscript{tsf}\\[0pt]
+\hline
+count & 578 & 579 & 579\\[0pt]
+mean & 2.24715e+12 & 1.08958e+11 & 1.853\\[0pt]
+std & 3.93675e+13 & 1.04132e+12 & 1.476\\[0pt]
+min & 2.47798e+07 & 1.93205e+09 & 0.001\\[0pt]
+25\% & 1.40573e+08 & 4.18098e+09 & 0.565\\[0pt]
+50\% & 6.83764e+08 & 7.79265e+09 & 1.604\\[0pt]
+75\% & 5.70379e+09 & 2.21327e+10 & 2.99\\[0pt]
+max & 9.10088e+14 & 2.23774e+13 & 6.47\\[0pt]
 \end{tabular}
-\end{table}
+\end{center}
 
@@
 \subsection{Constant \(\tau\)}
-\label{sec:org46757ea}
+\label{sec:org7264b82}
 
@@
 
-\begin{table}[hc]
-\centering
+\begin{center}
 \begin{tabular}{lrrr}
-\toprule
-{} &    A\_tau &    x\_tau &      tsf \\
-\midrule
-count & 5.79E+02 & 5.79E+02 & 5.79E+02 \\
-mean  & 4.59E+09 & 2.54E+00 & 8.89E+09 \\
-std   & 1.50E+10 & 9.57E-01 & 3.35E+09 \\
-min   & 9.87E+06 & 4.07E-01 & 1.42E+09 \\
-25\%   & 6.50E+07 & 1.87E+00 & 6.55E+09 \\
-50\%   & 2.37E+08 & 2.44E+00 & 8.54E+09 \\
-75\%   & 1.12E+09 & 3.08E+00 & 1.08E+10 \\
-max   & 1.06E+11 & 5.77E+00 & 2.02E+10 \\
-\bottomrule
+ & A\textsubscript{tau} & x\textsubscript{tau} & tsf\\[0pt]
+\hline
+count & 579 & 579 & 579\\[0pt]
+mean & 4.58667e+09 & 2.54057 & 8.89201e+09\\[0pt]
+std & 1.49896e+10 & 0.956554 & 3.34794e+09\\[0pt]
+min & 9.87003e+06 & 0.406787 & 1.42376e+09\\[0pt]
+25\% & 6.50497e+07 & 1.87165 & 6.55079e+09\\[0pt]
+50\% & 2.36667e+08 & 2.43871 & 8.5355e+09\\[0pt]
+75\% & 1.11526e+09 & 3.07972 & 1.0779e+10\\[0pt]
+max & 1.0577e+11 & 5.77102 & 2.01986e+10\\[0pt]
 \end{tabular}
-\end{table}
+\end{center}
 
@@
 \subsection{Comparing the two results}
-\label{sec:org62d708b}
+\label{sec:orgd5edef3}
 
 \subsubsection{Comparing the \(x\)'s}
-\label{sec:org7a303ba}
+\label{sec:orgd408258}
 
@@
 \subsubsection{Comparing the normalization constants}
-\label{sec:org4a59895}
+\label{sec:org976880e}
 
@@
 \subsubsection{Trying to make the A\textsubscript{del} cloud more compact}
-\label{sec:org4bf81bb}
+\label{sec:orge02c923}
 
@@
 \subsection{Int SFR to find the A\textsubscript{del}}
-\label{sec:org6350c57}
+\label{sec:org2f66940}
 
@@
 \int^{t_{sf}}_0 SFR_{del} dt_{sf}&=\int^{t_{sf}}_0 \frac{A_{del}t_{sf}e^{-t_{sf}/\tau}}{\tau^2} dt_{sf}\\
-M_*&=-A_{del} \frac{{\left(t_{\mathit{sf}} \tau + \tau^{2}\right)} e^{\left(-\frac{t_{\mathit{sf}}}{\tau}\right)}}{\tau^{2}}+A_{del}\\
-M_*&=-A_{del}\frac{\tau^2(x+1)e^{-x}}{\tau^2}+A_{del}\\
-M_*& = A_{del}(1-(x+1)e^{-x})\\
-A_{del}&=M_*\frac{e^x}{e^x-x-1}
+\zeta\cdot M_*&=-A_{del} \frac{{\left(t_{\mathit{sf}} \tau + \tau^{2}\right)} e^{\left(-\frac{t_{\mathit{sf}}}{\tau}\right)}}{\tau^{2}}+A_{del}\\
+\zeta\cdot M_*&=-A_{del}\frac{\tau^2(x+1)e^{-x}}{\tau^2}+A_{del}\\
+\zeta\cdot M_*& = A_{del}(1-(x+1)e^{-x})\\
+A_{del}&=\zeta\cdot M_*\frac{e^x}{e^x-x-1}
 \end{align}
 \end{equation}
+
+The integral \(\int SFR dt=\) The total mass that is turned into stars.
+But during the evolution of the stars, the stars spew mass to Interstellar space, so the galaxies lose mass during this process.
+So the observed Stellar Mass M\textsubscript{*} is smaller than the total mass turned into Stellar Mass.
+
+The constant \(\zeta\) accommodates for this mass-loss and, as discussed earlier, we can assume a conservative value of 1.3 for the galaxies in the LCV.
 
@@
 
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/log_A_theor_tau-log_A_tau-color_x_tsf.png}
+\caption{\label{fig:A_theor_A_exp_tau}Comparison of the 2 \$A\textsubscript{del}|\textsubscript{\(\tau\)=const.}\$s (theoretical and experimental)}
+\end{figure}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/log_A_theor_tsf-log_A_tsf-color_x_tsf.png}
+\caption{\label{fig:A_theor_A_exp_tsf}Comparison of the 2 \$A\textsubscript{del}|\textsubscript{tsf=const.}\$s (theoretical and experimental)}
+\end{figure}
+
+From the plots \cite{fig:A_theor_A_exp_tau} and \cite{fig:A_theor_A_exp_tsf} we get correlations of \(R^2 = 91\%\) \noindent and \(A_{tsf} = (8.97(12) \times 10^{-1})\cdot A_{tsf,theor} + (1.02(10) \times 10^{0})\)  so the theoretical values fit the experimental.
+
+From the equations (\ref{eq:SFR}), (\ref{eq:av_SFR-x}) and (\ref{eq:int SFR}), the \(SFR_{0,del}\) and the \(\overline{SFR_{del}}\) are given by the equations:
+
+\begin{equation} \label{eq:SFR final}
+\begin{align}
+SFR_{0,del}&=\zeta M_*\frac{e^x}{e^x-x-1}\frac{xe^{-x}}{\tau}\\
+          &=\zeta M_*\frac{x}{\tau(e^x-x-1)}
+\end{align}
+\end{equation}
+
+\begin{equation}\label{eq:av_SFR-x final}
+\begin{align}
+\overline{SFR_{del}}&=\zeta M_*\frac{e^x}{e^x-x-1}\frac{1}{t_{sf}}[1-(1+x)e^{-x}]\\
+                   &=\zeta M_*\frac{e^x}{e^x-x-1}\frac{1}{t_{sf}}\frac{e^x-x-1}{e^x}\\
+                   &=\zeta \frac{M_*}{t_{sf}}
+\end{align}
+\end{equation}
+
+The new \(\overline{SFR_{del}}\) is the same with the \(\overline{SFR}\) of the equation (\ref{eq:av_SFR M*}).
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/SFR_avSFR.png}
+\caption{\label{fig:The $SFR_{0,del}$ and $\overline{SFR_{del}}$ for constant $\tau=1$ and $\zeta M_*=1$}The \(SFR_{0,del}\) and \(\overline{SFR_{del}}\) for constant \(\tau=1\) and \(\zeta M_*=1\)}
+\end{figure}
+
+\subsection{Calculating the \(t_{sf}\) and \(\tau\) for each galaxy}
+\label{sec:org38a8c66}
+
+Having found an expression for the \(A_{del}\), we have eliminated on out of the 3 variables and now the \(t_{sf}\) and \(\tau\) of each galaxy can be calcuated.
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/tsf-hist.png}
+\caption{\label{fig:Histogram of t_{sf} from 0 to 20 Gyr}Histogram of t\textsubscript{sf} from 0 to 20 Gyr}
+\end{figure}
+
+\begin{center}
+\begin{tabular}{lrrr}
+ & tsfG & tauG & x\\[0pt]
+\hline
+count & 579 & 579 & 579\\[0pt]
+mean & 9.047 & 3.429 & 2.548\\[0pt]
+std & 4.637 & 1.197 & 0.849\\[0pt]
+min & 1.307 & 1.262 & 0.642\\[0pt]
+25\% & 6.066 & 2.954 & 1.99\\[0pt]
+50\% & 8.238 & 3.297 & 2.467\\[0pt]
+75\% & 11.007 & 3.691 & 2.962\\[0pt]
+max & 62.635 & 27.605 & 9.487\\[0pt]
+\end{tabular}
+\end{center}
+
+\begin{center}
+\begin{tabular}{lrrr}
+ & tsfG2 & tauG2 & x2\\[0pt]
+\hline
+count & 579 & 579 & 579\\[0pt]
+mean & 27.005 & 9.848 & 2.743\\[0pt]
+std & 112.566 & 41.066 & 0\\[0pt]
+min & 0.523 & 0.191 & 2.738\\[0pt]
+25\% & 4.329 & 1.578 & 2.743\\[0pt]
+50\% & 7.345 & 2.678 & 2.743\\[0pt]
+75\% & 14.071 & 5.13 & 2.743\\[0pt]
+max & 1439.37 & 525.624 & 2.743\\[0pt]
+\end{tabular}
+\end{center}
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/tsf2-hist.png}
+\caption{\label{fig:Histogram of t_{sf} from 0 to 20 Gyr}Histogram of t\textsubscript{sf} from 0 to 20 Gyr}
+\end{figure}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/tsf_tsf2.png}
+\caption{\label{fig:Comparing the two $t_{sf}$}Comparing the two \(t_{sf}\)}
+\end{figure}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/tsf_tsf2.png}
+\caption{\label{fig:Comparing the two $t_{sf}$}Comparing the two \(t_{sf}\)}
+\end{figure}
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/logMt-color-color_tsf.png}
+\caption{\label{fig:A_theor_A_exp_tsf}Comparison of the 2 \$A\textsubscript{del}|\textsubscript{tsf=const.}\$s (theoretical and experimental)}
+\end{figure}
+
+\subsubsection{[?]}
+\label{sec:org2822411}
+\begin{itemize}
+\item Can we calculate/observe \(\zeta\)?
+\begin{itemize}
+\item If not: for galaxies with extreme star-bursting and low-metallicity galaxies \(\zeta=2-3\). Can we find those galaxies and approximate the \(\zeta\)?
+\end{itemize}
+\item Why couldn't we use (\ref{eq:av_SFR M*}) to calculate \(A_{del}\)
+\item While in the second method we see a better correlation between the age of the galaxy and the color index, we must have an older universe
+\end{itemize}
+
 \section{The gas depletion timescale \(\tau_g\) \label{SEC:tau_g}}
-\label{sec:org325e6be}
+\label{sec:org873dcd6}
 
@@
 \section{Mass relations}
-\label{sec:org2e3fc57}
+\label{sec:org1e2130d}
 
@@
 \section{Variations in Star Formation Rate Across the Different Masses}
-\label{sec:orgb7febe7}
+\label{sec:org64de891}
 
@@
 \end{figure}
-(<statsmodels.regression.linear\textsubscript{model.RegressionResultsWrapper} object at 0x7f3d4e77b190>, '\#+name: fig:None \n\#+caption:None\n\#+ATTR\textsubscript{\LaTeX{}}: :placement [!htpb] \n\begin{center}
+(<statsmodels.regression.linear\textsubscript{model.RegressionResultsWrapper} object at 0x7fbf61cc5a10>, '\#+name: fig:None \n\#+caption:None\n\#+ATTR\textsubscript{\LaTeX{}}: :placement [!htpb] \n\begin{center}
 \includegraphics[width=.9\linewidth]{./figs/logMt-log_tau-color_log_tau_g.png}
@@
 
+(<statsmodels.regression.linear\textsubscript{model.RegressionResultsWrapper} object at 0x7fbf61ee6b10>, '\#+name: fig:None \n\#+caption:None\n\#+ATTR\textsubscript{\LaTeX{}}: :placement [!htpb] \n\begin{center}
+\includegraphics[width=.9\linewidth]{./figs/logMt-log_tsf-color_log_tau_g.png}
+\end{center}', 'logMt-log\textsubscript{tsf}-color\textsubscript{log}\textsubscript{tau}\textsubscript{g}')
+
 \subsection{{\bfseries\sffamily TODO} put that tau and tsf dont have a correlation with Mt}
-\label{sec:org5dfe35c}
+\label{sec:org9a06924}
 

### 2023-07-23 paper2.tex
I recompiled (i think thats all)

@@
-% Created 2023-06-10 Sat 19:05
+% Created 2023-07-07 Fri 02:20
 % Intended LaTeX compiler: pdflatex
@@
 \subsection{{\bfseries\sffamily TODO} no indent}
-\label{sec:org4ae1c6d}
+\label{sec:org2c76487}
 \subsection{{\bfseries\sffamily TODO} fullstops}
-\label{sec:orge244364}
+\label{sec:org2eb98c4}
 \subsection{{\bfseries\sffamily TODO} Units in the plots}
-\label{sec:orgaf69437}
+\label{sec:orge067e52}
 
@@
 \section{The Galaxies in the Local Cosmological Volume (LCV)}
-\label{sec:org94f634b}
+\label{sec:orgdd9bb01}
 
@@
 \section{Types of galaxies}
-\label{sec:org1701b4d}
+\label{sec:org27414b8}
 
@@
 \subsection{{\bfseries\sffamily TODO} write a table with the types}
-\label{sec:org421f46e}
+\label{sec:org8b9d595}
 
@@
 \section{Delayed-\(\tau\) model}
-\label{sec:org57c1611}
+\label{sec:org7dfc126}
 
@@
 \subsection{Constant \(t_{sf}\)}
-\label{sec:org4a83115}
+\label{sec:orgdbc251f}
 The observed ages of galactic discs are \(t_{sf}\approx 12\) Gyr\autocite{knoxSurveyCoolWhite1999}, so assuming an approximation of \(t_{sf}=12.5\) Gyr, the \(\overline{SFR_{del}}\) can be calcuated, from the equation (\ref{eq:av_SFR M*}).
@@
 \subsection{Constant \(\tau\)}
-\label{sec:org7264b82}
+\label{sec:org2ca7572}
 
@@
 \subsection{Comparing the two results}
-\label{sec:orgd5edef3}
+\label{sec:org88a6937}
 
 \subsubsection{Comparing the \(x\)'s}
-\label{sec:orgd408258}
+\label{sec:org148b753}
 
@@
 \subsubsection{Comparing the normalization constants}
-\label{sec:org976880e}
+\label{sec:org43d0c9b}
 
@@
 \subsubsection{Trying to make the A\textsubscript{del} cloud more compact}
-\label{sec:orge02c923}
+\label{sec:orgc5da7e1}
 
@@
 \subsection{Int SFR to find the A\textsubscript{del}}
-\label{sec:org2f66940}
+\label{sec:org6191eb1}
 
@@
 \subsection{Calculating the \(t_{sf}\) and \(\tau\) for each galaxy}
-\label{sec:org38a8c66}
+\label{sec:org10a2834}
 
@@
 \subsubsection{[?]}
-\label{sec:org2822411}
+\label{sec:org88e1de2}
 \begin{itemize}
@@
 \section{The gas depletion timescale \(\tau_g\) \label{SEC:tau_g}}
-\label{sec:org873dcd6}
+\label{sec:org4223423}
 
@@
 \section{Mass relations}
-\label{sec:org1e2130d}
+\label{sec:orgb9a30c1}
 
@@
 \section{Variations in Star Formation Rate Across the Different Masses}
-\label{sec:org64de891}
+\label{sec:orge561d63}
 
@@
 \end{figure}
-(<statsmodels.regression.linear\textsubscript{model.RegressionResultsWrapper} object at 0x7fbf61cc5a10>, '\#+name: fig:None \n\#+caption:None\n\#+ATTR\textsubscript{\LaTeX{}}: :placement [!htpb] \n\begin{center}
+(<statsmodels.regression.linear\textsubscript{model.RegressionResultsWrapper} object at 0x7f234887cd50>, '\#+name: fig:None \n\#+caption:None\n\#+ATTR\textsubscript{\LaTeX{}}: :placement [!htpb] \n\begin{center}
 \includegraphics[width=.9\linewidth]{./figs/logMt-log_tau-color_log_tau_g.png}
@@
 
-(<statsmodels.regression.linear\textsubscript{model.RegressionResultsWrapper} object at 0x7fbf61ee6b10>, '\#+name: fig:None \n\#+caption:None\n\#+ATTR\textsubscript{\LaTeX{}}: :placement [!htpb] \n\begin{center}
+(<statsmodels.regression.linear\textsubscript{model.RegressionResultsWrapper} object at 0x7f23664ba6d0>, '\#+name: fig:None \n\#+caption:None\n\#+ATTR\textsubscript{\LaTeX{}}: :placement [!htpb] \n\begin{center}
 \includegraphics[width=.9\linewidth]{./figs/logMt-log_tsf-color_log_tau_g.png}
@@
 \subsection{{\bfseries\sffamily TODO} put that tau and tsf dont have a correlation with Mt}
-\label{sec:org9a06924}
+\label{sec:org8125488}
 

### 2023-07-23 final.py

@@ -7,6 +7,7 @@ import statsmodels.api as sm
 import statsmodels.formula.api as smf
 from tabulate import tabulate
 import uncertainties as unc
+from astropy import units as u
 
 
 
@@ -19,9 +20,9 @@ def caption(fname,caption,name = None):
 
 def simple_regplot(data ,
     X, Y, cap = None, name = None, n_std=2, n_pts=100, ax=None, scatter_kws=None, line_kws=None, ci_kws=None):
-    df=data
-    x=df[X]
-    y=df[Y]
+    df_data=data
+    x=df_data[X]
+    y=df_data[Y]
     """ Draw a regression line with error interval. """
     ax = plt.gca() if ax is None else ax
 
@@ -55,6 +56,12 @@ def simple_regplot(data ,
     ax.grid()
     ax.set_xlabel(X)
     ax.set_ylabel(Y)
+    ############################
+    # if log == 1:             #
+    #     ax.set_yscale("log") #
+    #     ax.set_xscale("log") #
+    ############################
+
     ax.legend(loc = "best")
     if scatter_kws == {}:
         lab = X+"-"+Y
@@ -73,13 +80,13 @@ def simple_regplot(data ,
     if name == None:
         name = cap
 
-    Cap = "#+name: fig:{} \n#+label: fig:{} \n#+caption:{}\n#+ATTR_LaTeX: :placement [!htpb] \n[[./{}.png]]".format(cap,name,name,fname)
+    Cap = "#+name: fig:{} \n#+caption:{}\n#+ATTR_LaTeX: :placement [!htpb] \n[[./{}.png]]".format(name,cap,fname)
     return fit_results, Cap , lab
 
 # Calculate the bin width using the Freedman-Diaconis rule
 def fd_bins(x):
-    iqr = df[x].quantile(0.75) - df[x].quantile(0.25)
-    bin_width = 2 * iqr / df[x].count()**(1/3)
+    iqr = x.quantile(0.75) - x.quantile(0.25)
+    bin_width = 2 * iqr / x.count()**(1/3)
 
[…]

### 2023-07-23 Finding_Adel.tex

@@
-% Created 2023-04-06 Thu 00:06
+% Created 2023-05-24 Wed 20:58
 % Intended LaTeX compiler: pdflatex
@@
 \maketitle
+
+\section{Delayed-\(\tau\) model}
+\label{sec:orgfa1060d}
+
 According to P. Kroupa et al. 2020\autocite{kroupaConstraintsStarFormation2020} current star formation rates of galaxies can be described by the 'delayed-\(\tau\)' model as
@@
 
-For a galaxy that forms stars from the time t\textsubscript{1} to t\textsubscript{2}=the pressent day (if the galaxy is still forming stars) the SFH can be written as \(SFR(t) = \overline{SFR}+\Delta SFR(t)\), such that the average SFR of the galaxy can be witten as
-
-\begin{equation}\label{eq:int of av_SFR}
-\overline{SFR} = \frac{1}{t_{sf}} \left(\int^{t_2}_{t_1}\overline{SFR}dt+ \int^{t_2}_{t_1}\Delta SFR(t)\right)
-\end{equation}
-with temporal deviations from \(\overline{SFR}\) satisfying:
-
-$$\int^{t_2}_{t_1} \Delta SFR dt = 0M_\odot$$
-
-So from the equations (\ref{eq:SFR}) and (\ref{eq:int of av_SFR}) we get the averge SFR:
+The average SFR is
 
@@
 \end{equation}
-\noindent where \(\zeta\) accommodates for mass-loss through stellar evolution and \(\zeta\approx 1.3\).
+where \(\zeta\) accommodates for mass-loss through stella evolution and \(\zeta\approx 1.3\)
 
-From the equations (\Ref{eq:int of av_SFR}) and (\ref{eq:av_SFR-x}) we can derive that the \(A_{del}\) must be independent from the time/ constant throughout the life of the galaxy.
+This is a system of 2 equations and 3 variables, since A\textsubscript{del} has never been calculated
 
-Also from the equation (\ref{eq:SFR}) we can find the units of the \(A_{del}\)
-\begin{equation} \label{eq:units}
-\begin{align}
-\left[SFR_{0,del}\right]&=\frac{\left[A_{del}\right]\left[x\right]\left[e^{-x}\right]}{\left[\tau\right]}\\
-\frac{[M_*]}{[time]}& = \frac{[A_{del}]\cdot 1\cdot 1}{[time]}\\
-[M_*]& = [A_{del}]
-\end{align}
+\subsection{Constant \(t_{sf}\)}
+\label{sec:org8a4d333}
+The observed ages of galactic discs are \(t_{sf}\approx 12\) Gyr\autocite{knoxSurveyCoolWhite1999}, so assuming an approximation of \(t_{sf}=12.5\) Gyr, the \(\overline{SFR_{del}}\) can be calcuated, from the equation (\ref{eq:av_SFR M*}).
+
+After that the equation of ratio
+
+\begin{equation} \label{eq:ratio}
+    \frac{\overline{SFR_{del}}}{SFR_{0,del}}=\frac{e^x-x-1}{x^2}
 \end{equation}
 
-So we can expect that the \(A_{del}\) can be expressed as
-\begin{equation}\label{eq:A=f(M)}
-A_{del}=c\cdot M \Leftrightarrow \log(A_{del})= log(M)+log(c)
-\end{equation}
-\noindent where c is a constant and M the stellar mass (\(M_*\)), the gas mass (\(M_g\)) or the total mass of galaxy(\(M_t = M_* + M_g\)).
+can be solved numerically for \(x\) and using the equations (\Ref{eq:SFR}) and (\Ref{eq:av_SFR-x}) the \(A_{del}\) and \(\tau\) of each galaxy are found.
 
-The equations (\ref{eq:SFR}) and (\ref{eq:av_SFR-x}) create a system of 2 equations and 3 variables (the SFR and the stellar masses are given), since A\textsubscript{del} has never been calculated
-
-\section{Constant \(t_{sf}\)}
-\label{sec:orge82f914}
-
-The observed ages of galactic discs are \(t_{sf}\approx 12\) Gyr\autocite{knoxSurveyCoolWhite1999}, so we assume an approximation of \(t_{sf}=12.5\) Gyr.
-Having one out of the three variables as a constant we can calculate the \(A_{del}|_{t_{sf}}\) and \(\tau|_{t_{sf}}\) and plot them (figures \ref{fig:A-x_tsf} and \ref{fig:A-tau_tsf}).
+\begin{center}
+\begin{tabular}{lrrr}
+ & \(A_{tsf}\) & \(\tau\) & \(x_{tsf}\)\\[0pt]
+\hline
+count & 578 & 579 & 579\\[0pt]
+mean & 2.24715e+12 & 1.08958e+11 & 1.853\\[0pt]
+std & 3.93675e+13 & 1.04132e+12 & 1.476\\[0pt]
+min & 2.47798e+07 & 1.93205e+09 & 0.001\\[0pt]
+25\% & 1.40573e+08 & 4.18098e+09 & 0.565\\[0pt]
+50\% & 6.83764e+08 & 7.79265e+09 & 1.604\\[0pt]
+75\% & 5.70379e+09 & 2.21327e+10 & 2.99\\[0pt]
+max & 9.10088e+14 & 2.23774e+13 & 6.47\\[0pt]
+\end{tabular}
+\end{center}
 
@@
 \includegraphics[width=.9\linewidth]{./figs/x-A_tsf.png}
-\caption{\label{fig:A-x_tsf}\(A_{del} = f(x)\) for constant t\textsubscript{sf}}
+\caption{\label{fig:$A_{del} = f(x)$ for constant t_{sf}}\(A_{del} = f(x)\) for constant t\textsubscript{sf}}
 \end{figure}
@@
 \includegraphics[width=.9\linewidth]{./figs/T-A_tsf.png}
-\caption{\label{fig:A-tau_tsf}\(A_{del} = f(\tau)\) for constant t\textsubscript{sf}}
+\caption{\label{fig:$A_{del} = f(\tau)$ for constant t_{sf}}\(A_{del} = f(\tau)\) for constant t\textsubscript{sf}}
 \end{figure}
-
-\section{Constant \(\tau\)}
-\label{sec:org8d5bda4}
-
-Now assuming for a constant \(\tau = 3.5\) Gyr the system can again be solved numerically for each galaxy and the values of \(A_{del}|_{\tau}\) and \(t_{sf}|_{\tau}\) can be found and plotted (figures \ref{fig:A-x_tau} and \ref{fig:A-tsf_tau}).
-
-\begin{figure}[!htpb]
-\centering
-\includegraphics[width=.9\linewidth]{./figs/x-A_tau.png}
-\caption{\label{fig:A-x_tau}\(A_{del} = f(x)\) for constant \(\tau\)}
-\end{figure}
-
-\begin{figure}[!htpb]
-\centering
-\includegraphics[width=.9\linewidth]{./figs/T-A_tau.png}
-\caption{\label{fig:A-tsf_tau}\(A_{del} = f(t_{sf})\) for constant \(\tau\)}
-\end{figure}
-
-\section{Finding the \(A_{del} = f(\text{Mass})\) relation}
-\label{sec:orgb5ebed2}
-
-If we plot the \(A_{del}\) with the 3 given masses of each galaxy, both for a constant \(\tau\) and a constant \(t_{sf}\), we observe that indeed there is a correlation in the form of:
-$$
-\log(A_{del}) = c_1\log(\text{Mass})+c_2
-$$
-
-\begin{enumerate}
-\item For a constant \(t_{sf}\) the correlations are:
-\begin{enumerate}
-\item Total mass: \(R^2=48\%\) (Fig. \ref{fig:A_tsf_Mt})
-\item Mass of the Gasses: \(R^2=43\%\) (Fig. \ref{fig:A_tsf_Mg})
-\item Stellar Mass: \(R^2=44\%\) (Fig. \ref{fig:A_tsf_StellarMass})
-\end{enumerate}
-
-\item For a constant \(\tau\) the correlations are:
-\begin{enumerate}
-\item Total mass: \(R^2=91\%\) (Fig. \ref{fig:A_tau_Mt})
-\item Mass of the Gasses: \(R^2=70\%\) (Fig. \ref{fig:A_tau_Mg})
-\item Stellar Mass: \(R^2=90\%\) (Fig. \ref{fig:A_tau_StellarMass})
-\end{enumerate}
-\end{enumerate}
-
-In both cases the best correlation is  \(A_{del} = f(M_t)\) and for \(\tau =\) const. the correlation is excelent.
-\begin{equation}\label{eq:logMt-log_A_tsf-color_x_tsf}
-\log(A_{del}|_t_{sf}) = (9.6(4) \times 10^{-1})\cdot \log(M_t) + (8(4) \times 10^{-1})
-\end{equation}
-\begin{equation}\label{eq:logMt-log_A_tau-color_x_tau}
-\log(A_{del}|_\tau) = (1.025(14) \times 10^{0})\cdot \log(M_t) + (-3.0(1.2) \times 10^{-1})
-\end{equation}
-
-For both equations (\ref{eq:logMt-log_A_tsf-color_x_tsf}) and (\ref{eq:logMt-log_A_tau-color_x_tau}) \(c_1\approx 1\) so they fit the equation (\ref{eq:A=f(M)}).
 
@@
 
+\begin{equation}\label{eq:logMt-log_A_tsf-color_x_tsf}
+\begin{align}
+& $log(A_{del}|_t_{sf}) = (9.6(4) \times 10^{-1})\cdot $log(M_t)$ + (8(4) \times 10^{-1}) \\
+& \textrm{with correlation } R^2=48\%
+\end{align}
+\end{equation}
+\noindent
+
+\pagebreak
+\subsection{Constant \(\tau\)}
+\label{sec:org59966a2}
+
+Assuming for an constant \(\tau=3.5\) Gyr, we cannot use the same \(\overline{SFR}\) since it depends on \(t_{sf}\). Using the equations\textasciitilde{}(\Ref{eq:av_SFR M*}) and (\Ref{eq:ratio})
+
+$$
+    \frac{\overline{SFR_{del}}}{SFR_{0,del}}=\frac{e^x-x-1}{x^2}\Leftrightarrow \frac{e^x-x-1}{x}=\frac{\zeta M_*}{SFR\cdot\tau}
+$$
+
+using this equation \(x\) and \(A_{del}\) can be calculated numerically.
+
+\begin{center}
+\begin{tabular}{lrrr}
+ & \(A_\tau\) & \(x_\tau\) & \(t_{sf}\)\\[0pt]
+\hline
+count & 579 & 579 & 579\\[0pt]
+mean & 4.58667e+09 & 2.54057 & 8.89201e+09\\[0pt]
+std & 1.49896e+10 & 0.956554 & 3.34794e+09\\[0pt]
+min & 9.87003e+06 & 0.406787 & 1.42376e+09\\[0pt]
+25\% & 6.50497e+07 & 1.87165 & 6.55079e+09\\[0pt]
+50\% & 2.36667e+08 & 2.43871 & 8.5355e+09\\[0pt]
+75\% & 1.11526e+09 & 3.07972 & 1.0779e+10\\[0pt]
+max & 1.0577e+11 & 5.77102 & 2.01986e+10\\[0pt]
+\end{tabular}
+\end{center}
+
 \begin{figure}[!htpb]
 \centering
-\includegraphics[width=.9\linewidth]{./figs/logMg-log_A_tsf-color_x_tsf.png}
-\caption{\label{fig:A_tsf_Mg}Mass of the gasses \(M_g\) - \(A_{del}|_{t_{sf}}\)}
+\includegraphics[width=.9\linewidth]{./figs/x-A_tau.png}
+\caption{\label{fig:$A_{del} = f(x)$ for constant $\tau$}\(A_{del} = f(x)\) for constant \(\tau\)}
 \end{figure}
@@
 \centering
-\includegraphics[width=.9\linewidth]{./figs/logStellarMass-log_A_tsf-color_x_tsf.png}
-\caption{\label{fig:A_tsf_StellarMass}Stellar Mass \(M_*\) - \(A_{del}|_{t_{sf}}\)}
-\end{figure}
-
-\begin{figure}[!htpb]
-\centering
-\includegraphics[width=.9\linewidth]{./figs/logMt-log_A_tau-color_x_tau.png}
-\caption{\label{fig:A_tau_Mt}Total Mass \(M_t\) - \(A_{del}|_{\tau}}\)}
-\end{figure}
-
-\begin{figure}[!htpb]
-\centering
-\includegraphics[width=.9\linewidth]{./figs/logMg-log_A_tau-color_x_tau.png}
-\caption{\label{fig:A_tau_Mg}Mass of the gasses \(M_g\) - \(A_{del}|_{\tau}\)}
+\includegraphics[width=.9\linewidth]{./figs/T-A_tau.png}
+\caption{\label{fig:$A_{del} = f(t_{sf})$ for constant $\tau$}\(A_{del} = f(t_{sf})\) for constant \(\tau\)}
 \end{figure}
@@
 \includegraphics[width=.9\linewidth]{./figs/logStellarMass-log_A_tau-color_x_tau.png}
-\caption{\label{fig:A_tau_StellarMass}Stellar Mass \(M_*\) - \(A_{del}|_{\tau}}\)}
+\caption{\label{fig:A_tau_Mt}Total Mass \(M_t\) - \(A_{del}|_{\tau}\)}
 \end{figure}
+
+\begin{equation}\label{eq:logStellarMass-log_A_tau-color_x_tau}
+\begin{align}
+& $log(A_{del}|_\tau) = (8.74(12) \times 10^{-1})\cdot $log(M_t)$ + (1.31(10) \times 10^{0}) \\
+& \textrm{with correlation } R^2=90\%
+\end{align}
+\end{equation}
+\noindent
+
+\pagebreak
+\subsection{Comparing the two results}
+\label{sec:org531854c}
+
+\subsubsection{Comparing the \(x\)'s}
+\label{sec:org8a255b5}
+
+Comparing the two different results for x, we see that the \(x|_\tau\) has a lower \(\sigma\)
+
+\begin{table}[hc]
+\centering
+\begin{tabular}{lrr}
+\toprule
+{} &    $x|_\tau$ & $x|_{tsf}$ \\
+\midrule
+count & 5.79E+02 & 5.79E+02 \\
+mean  & 2.54E+00 & 1.85E+00 \\
+std   & 9.57E-01 & 1.48E+00 \\
+min   & 4.07E-01 & 5.59E-04 \\
+25\%   & 1.87E+00 & 5.65E-01 \\
+50\%   & 2.44E+00 & 1.60E+00 \\
+75\%   & 3.08E+00 & 2.99E+00 \\
+max   & 5.77E+00 & 6.47E+00 \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/Comparing_the_x_Mt.png}
+\caption{\label{fig:Comparing the two x's, According to their total masses}Comparing the two x's, According to their total masses}
+\end{figure}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/x_tau-Mt-color.png}
+\caption{\label{fig:$x|_\tau=f(M_t)$, with their color index}\(x|_\tau=f(M_t)\), with their color index}
+\end{figure}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/x_tsf-x_tau-color_logMt.png}
+\caption{\label{fig:Comparing the two x, according to their total mass}Comparing the two x, according to their total mass}
+\end{figure}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/x_tsf-x_tau-color_TType.png}
+\caption{\label{fig:Comparing the two x, according to their type}Comparing the two x, according to their type}
+\end{figure}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/x_tsf-x_tau-color_color.png}
+\caption{\label{fig:Comparing the two x, according to their color index}Comparing the two x, according to their color index}
+\end{figure}
+
+The two results are interrelated through the equation:
+
+\begin{equation}\label{eq:x_tsf-x_tau}
+\begin{align}
+& x|_\tau = (6.30(6) \times 10^{-1})\cdot x|_{tsf} + (1.374(15) \times 10^{0}) \\
+& \textrm{with correlation } R^2=94\%
+\end{align}
+\end{equation}
+\noindent
+
+and from the plots the following conclusions can be drawn:
+
+\begin{enumerate}
+\item The galaxies with a higher total mass deviate less from the linear fit and are older.
+\item The younger galaxies are mainly later types of galaxies
+\item For lower x's, the galaxies have a lower color index which indicates that they are younger. So the values are inline with the experimental values.
+\end{enumerate}
+
+\subsubsection{Comparing the normalization constants}
+\label{sec:org5474350}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/Comparing_the_A_x.png}
+\caption{\label{fig:Comparing the two A_{del}}Comparing the two A\textsubscript{del}}
+\end{figure}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/A_tau-A_tsf_colo_X.png}
+\caption{\label{fig:Comparison of the 2 A_{del}s according to their $x$}Comparison of the 2 A\textsubscript{del}s according to their \(x\)}
+\end{figure}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/A_tau-A_tsf_Mt.png}
+\caption{\label{fig:Comparison of the 2 A_{del}s according to their total masses}Comparison of the 2 A\textsubscript{del}s according to their total masses}
+\end{figure}
+
+For high \(x\) and high masses the two A\textsubscript{del}s have a high correlation. Specifically:
+\begin{enumerate}
+\item For high \(x\) the \(A_{del}|_{\tau}-A_{del}|_{t_{sf}}\) plot follows a \(y=x\) trend, which means that for older stars and stars with a low star formation timescale \(\tau\), the normalization constant is the same despite the method used to calculate it.
+\item The same is true for more massive galaxies, since they deviate less from the \(y=x\) line
+\end{enumerate}
+
+\subsection{Int SFR to find the A\textsubscript{del}}
+\label{sec:org13c70a8}
+
+If we integrate equation (\ref{eq:SFR}) we get:
+
+\begin{equation}\label{eq:int SFR}
+\begin{align}
+\int^{t_{sf}}_0 SFR_{del} dt_{sf}&=\int^{t_{sf}}_0 \frac{A_{del}t_{sf}e^{-t_{sf}/\tau}}{\tau^2} dt_{sf}\\
+\zeta\cdot M_*&=-A_{del} \frac{{\left(t_{\mathit{sf}} \tau + \tau^{2}\right)} e^{\left(-\frac{t_{\mathit{sf}}}{\tau}\right)}}{\tau^{2}}+A_{del}\\
+\zeta\cdot M_*&=-A_{del}\frac{\tau^2(x+1)e^{-x}}{\tau^2}+A_{del}\\
+\zeta\cdot M_*& = A_{del}(1-(x+1)e^{-x})\\
+A_{del}&=\zeta\cdot M_*\frac{e^x}{e^x-x-1}
+\end{align}
+\end{equation}
+
+The integral \(\int SFR dt=\) The total mass that is turned into stars.
+But during the evolution of the stars, the stars spew mass to Interstellar space, so the galaxies lose mass during this process.
+So the observed Stellar Mass M\textsubscript{*} is smaller than the total mass turned into Stellar Mass.
+
+The constant \(\zeta\) accommodates for this mass-loss and, as discussed earlier, we can assume a conservative value of 1.3 for the galaxies in the LCV.
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/A_theor_tau-M*.png}
+\caption{\label{fig:Comparison of the 2 A_{del}s according to their total masses}Comparison of the 2 A\textsubscript{del}s according to their total masses}
+\end{figure}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/log_A_theor_tau-logStellarMass-color_x_tsf.png}
+\caption{\label{fig:Comparison of the A_del according to their Stellar Mass}Comparison of the A\textsubscript{del} according to their Stellar Mass}
+\end{figure}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/log_A_theor_tau-log_A_tau-color_x_tsf.png}
+\caption{\label{fig:A_theor_A_exp_tau}Comparison of the 2 \$A\textsubscript{del}|\textsubscript{\(\tau\)=const.}\$s (theoretical and experimental)}
+\end{figure}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/log_A_theor_tsf-log_A_tsf-color_x_tsf.png}
+\caption{\label{fig:A_theor_A_exp_tsf}Comparison of the 2 \$A\textsubscript{del}|\textsubscript{tsf=const.}\$s (theoretical and experimental)}
+\end{figure}
+
+From the plots we get correlations of \(R^2 = 91\%\)  and \(A_{tsf} = (8.97(12) \times 10^{-1})\cdot A_{tsf\,theor} + (1.02(10) \times 10^{0})\)  so the theoretical values fit the experimental.
+
+From the equations (\ref{eq:SFR}), (\ref{eq:av_SFR-x}) and (\ref{eq:int SFR}), the \(SFR_{0,del}\) and the \(\overline{SFR_{del}}\) are given by the equations:
+
+\begin{equation} \label{eq:SFR final}
+\begin{align}
+SFR_{0,del}&=\zeta M_*\frac{e^x}{e^x-x-1}\frac{xe^{-x}}{\tau}\\
+          &=\zeta M_*\frac{x}{\tau(e^x-x-1)}
+\end{align}
+\end{equation}
+
+\begin{equation}\label{eq:av_SFR-x final}
+\begin{align}
+\overline{SFR_{del}}&=\zeta M_*\frac{e^x}{e^x-x-1}\frac{1}{t_{sf}}[1-(1+x)e^{-x}]\\
+                   &=\zeta M_*\frac{e^x}{e^x-x-1}\frac{1}{t_{sf}}\frac{e^x-x-1}{e^x}\\
+                   &=\zeta \frac{M_*}{t_{sf}}
+\end{align}
+\end{equation}
+
+The new \(\overline{SFR_{del}}\) is the same with the \(\overline{SFR}\) of the equation (\ref{eq:av_SFR M*}).
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/SFR_avSFR.png}
+\caption{\label{fig:The $SFR_{0,del}$ and $\overline{SFR_{del}}$ for constant $\tau=1$ and $\zeta M_*=1$}The \(SFR_{0,del}\) and \(\overline{SFR_{del}}\) for constant \(\tau=1\) and \(\zeta M_*=1\)}
+\end{figure}
+
+\pagebreak
+
+\subsection{Calculating the \(t_{sf}\) and \(\tau\) for each galaxy}
+\label{sec:org1230772}
+
+Having found an expression for the \(A_{del}\), we have eliminated on out of the 3 variables and now the \(t_{sf}\) and \(\tau\) of each galaxy can be calcuated.
+
+\subsubsection{Method 1}
+\label{sec:org9e16912}
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/tsf-hist.png}
+\caption{\label{fig:Histogram of t_{sf} from 0 to 20 Gyr}Histogram of t\textsubscript{sf} from 0 to 20 Gyr}
+\end{figure}
+
+\begin{center}
+\begin{tabular}{lrrr}
+ & \(t_{sf}\) Gyr & \(\tau\) Gyr & x\\[0pt]
+\hline
+count & 579 & 579 & 579\\[0pt]
+mean & 9.047 & 3.429 & 2.548\\[0pt]
+std & 4.637 & 1.197 & 0.849\\[0pt]
+min & 1.307 & 1.262 & 0.642\\[0pt]
+25\% & 6.066 & 2.954 & 1.99\\[0pt]
+50\% & 8.238 & 3.297 & 2.467\\[0pt]
+75\% & 11.007 & 3.691 & 2.962\\[0pt]
+max & 62.635 & 27.605 & 9.487\\[0pt]
+\end{tabular}
+\end{center}
+
+\subsubsection{Method 2}
+\label{sec:org21a3006}
+\begin{center}
+\begin{tabular}{lrrr}
+ & \(t_{sf,2}\) Gyr & \(\tau_2\) Gyr & x\\[0pt]
+\hline
+count & 579 & 579 & 579\\[0pt]
+mean & 27.005 & 9.848 & 2.743\\[0pt]
+std & 112.566 & 41.066 & 0\\[0pt]
+min & 0.523 & 0.191 & 2.738\\[0pt]
+25\% & 4.329 & 1.578 & 2.743\\[0pt]
+50\% & 7.345 & 2.678 & 2.743\\[0pt]
+75\% & 14.071 & 5.13 & 2.743\\[0pt]
+max & 1439.37 & 525.624 & 2.743\\[0pt]
+\end{tabular}
+\end{center}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/tsf2-hist.png}
+\caption{\label{fig:Histogram of t_{sf} from 0 to 20 Gyr}Histogram of t\textsubscript{sf} from 0 to 20 Gyr}
+\end{figure}
+
+\begin{figure}[!htpb]
+\centering
+\includegraphics[width=.9\linewidth]{./figs/tsf_tsf2.png}
+\caption{\label{fig:Comparing the two $t_{sf}$}Comparing the two \(t_{sf}\)}
+\end{figure}
+
+\subsubsection{[?]}
+\label{sec:org84e38fd}
+\begin{itemize}
+\item Can we calculate/observe \(\zeta\)?
+\begin{itemize}
+\item If not: for galaxies with extreme star-bursting and low-metallicity galaxies \(\zeta=2-3\). Can we find those galaxies and approximate the \(\zeta\)?
+\end{itemize}
+\item Why couldn't we use (\ref{eq:av_SFR M*}) to calculate \(A_{del}\)
+\item While in the second method we see a better correlation between the age of the galaxy and the color index, we must have an older universe
+\end{itemize}
 

### 2023-07-23 final.py
Lets start over
TO AFENTIKO TRELATHIKE KAI JEKINA APO TIN ARXI

@@ -1,680 +1,0 @@
-import numpy as np
-import pandas as pd
-from scipy.optimize import fsolve
-import matplotlib.pyplot as plt
-import seaborn as sns
-import statsmodels.api as sm
-import statsmodels.formula.api as smf
-from tabulate import tabulate
-import uncertainties as unc
-from astropy import units as u
-
-
-
-pd.set_option('display.float_format', lambda x: '%.2E' % x)
-######Print images with caption
-def caption(fname,caption,name = None):
-    if name == None:
-        name = caption
-    return "#+name: fig:{} \n#+label: fig:{} \n#+caption:{} \n#+ATTR_LaTeX: :placement [!htpb]\n[[./{}.png]]".format(caption,name,name,fname)
-
-def simple_regplot(data ,
-    X, Y, cap = None, name = None, n_std=2, n_pts=100, ax=None, scatter_kws=None, line_kws=None, ci_kws=None):
-    df_data=data
-    x=df_data[X]
-    y=df_data[Y]
-    """ Draw a regression line with error interval. """
-    ax = plt.gca() if ax is None else ax
-
-    # calculate best-fit line and interval
-    x_fit = sm.add_constant(x)
-    fit_results = sm.OLS(y, x_fit,missing='drop').fit()
-
-    xconst=f'{fit_results.params[1]:.3f}'
-    const=f'{fit_results.params[0]:.3f}'
-    eval_x = sm.add_constant(np.linspace(np.min(x), np.max(x), n_pts))
-    pred = fit_results.get_prediction(eval_x)
-
-    # draw the fit line and error interval
-    ci_kws = {} if ci_kws is None else ci_kws
-    ax.fill_between(
-        eval_x[:, 1],
-        pred.predicted_mean - n_std * pred.se_mean,
-        pred.predicted_mean + n_std * pred.se_mean,
-        facecolor ='red',
-        alpha=0.5,
-        **ci_kws,
-    )
-    line_kws = {} if line_kws is None else line_kws
[…]

### 2023-07-23 main.py

@@ -1,371 +1,0 @@
-import numpy as np
-import pandas as pd
-from scipy.optimize import fsolve
-import matplotlib.pyplot as plt
-import seaborn as sns
-import statsmodels.api as sm
-import statsmodels.formula.api as smf
-
-
-def simple_regplot(data ,
-    X, Y, n_std=2, n_pts=100, ax=None, scatter_kws=None, line_kws=None, ci_kws=None):
-    df=data
-    x=df[X]
-    y=df[Y]
-    """ Draw a regression line with error interval. """
-    ax = plt.gca() if ax is None else ax
-
-    # calculate best-fit line and interval
-    x_fit = sm.add_constant(x)
-    fit_results = sm.OLS(y, x_fit,missing='drop').fit()
-
-    xconst=f'{fit_results.params[1]:.3f}'
-    const=f'{fit_results.params[0]:.3f}'
-    eval_x = sm.add_constant(np.linspace(np.min(x), np.max(x), n_pts))
-    pred = fit_results.get_prediction(eval_x)
-
-    # draw the fit line and error interval
-    ci_kws = {} if ci_kws is None else ci_kws
-    ax.fill_between(
-        eval_x[:, 1],
-        pred.predicted_mean - n_std * pred.se_mean,
-        pred.predicted_mean + n_std * pred.se_mean,
-        facecolor ='red',
-        alpha=0.5,
-        **ci_kws,
-    )
-    line_kws = {} if line_kws is None else line_kws
-    h = ax.plot(eval_x[:, 1], pred.predicted_mean, **line_kws,color='red',linestyle='dashed',label= Y+"="+xconst+X+"+"+const)
-
-    # draw the scatterplot
-    scatter_kws = {} if scatter_kws is None else scatter_kws
-    ax.scatter(x, y, **scatter_kws,label="Data")
-
-    ax.set_title(Y+ "=f("+X+ ")")
-    ax.grid()
-    ax.set_xlabel(X)
-    ax.set_ylabel(Y)
-    ax.legend(loc = "best")
-    if scatter_kws == {}:
-        plt.savefig("graphs/"+X+"-"+Y)
-        plt.show()
-    else:
[…]

### 2023-10-16 notes/notes.tex
Astropy Table
I found that the astropy package supports the mrt format and can make my life easier

% Created 2023-10-11 Wed 19:37
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\date{\today}
\title{Karachentsev List notes}
\hypersetup{
 pdfauthor={},
 pdftitle={Karachentsev List notes},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.3 (Org mode 9.6.1)}, 
 pdflang={English}}
\usepackage{biblatex}
\addbibresource{/home/dp/Documents/Research_paper_SFR/My Library/My Library.bib}
\begin{document}

\maketitle
\tableofcontents

This list contains measurements from the galaxies in the Local Cosmological Volume (LCV), and the last update of data is on 2023-06-30. I downloaded the database from \autocite{karachentsevUPDATEDNEARBYGALAXY2013}

\section{Original data set}
\label{sec:orgbd60bab}

The data I will use for this project come from the Karachentsev  catalog (2022-12-02), which is an updated version of the list used in Kroupa et al. 2020
From the list I use the tables ``Catalog of Nearby Galaxies'', ``Global Parameters of the Nearby Galaxies'' and ``List of the nearby galaxies with measured SFR''

\subsubsection{{\bfseries\sffamily IDEA} I want to merge the coordinate columns into one}
\label{sec:org9296394}

\subsection{Join the tables}
\label{sec:org3cf69e8}

<Table length=1436>
  name    dtype       unit                       description                      class     n\textsubscript{bad}
-------- ------- ------------- ----------------------------------------------- ------------ -----
    Name   str18                            Galaxy name in well-known catalogs       Column     0
   RAh\textsubscript{1}   int64             h                 Hour of Right Ascension (J2000)       Column     0
   RAm\textsubscript{1}   int64           min               Minute of Right Ascension (J2000)       Column     0
   RAs\textsubscript{1} float64             s               Second of Right Ascension (J2000)       Column     0
   DE-\textsubscript{1}    str1                               Sign of the Declination (J2000)       Column     0
   DEd\textsubscript{1}   int64           deg                   Degree of Declination (J2000)       Column     0
   DEm\textsubscript{1}   int64        arcmin                Arcminute of Declination (J2000)       Column     0
   DEs\textsubscript{1}   int64        arcsec                Arcsecond of Declination (J2000)       Column     0
   a26\textsubscript{1} float64        arcmin                      Major angular diameter (1) MaskedColumn    11
     b/a float64                                      Apparent axial ratio (1) MaskedColumn    11
    AB\textsubscript{1} float64           mag               Galactic extinction in B band (2) MaskedColumn     1
l\textsubscript{FUVmag}    str1                                          Limit flag on FUVmag MaskedColumn  1104
  FUVmag float64           mag                    GALEX FUV band magnitude (3) MaskedColumn   311
    Bmag float64           mag                   Integral B band magnitude (4) MaskedColumn     8
 l\textsubscript{Hamag}    str1                                           Limit flag on Hamag MaskedColumn  1306
   Hamag float64           mag   Integral H\{alpha\} line emission magnitude (5) MaskedColumn   700
    Kmag float64           mag                   2MASS K\textsubscript{S}\_ band magnitude (6) MaskedColumn    11
  f\textsubscript{Kmag}    str1                                          [*] Flag on Kmag (7) MaskedColumn   362
 l\textsubscript{21mag}    str1                                           Limit flag on 21mag MaskedColumn  1226
   21mag float64           mag                    H I 21 cm line magnitude (8) MaskedColumn   494
     W50   int64        km / s     H I line with at 50\% level from maximum (9) MaskedColumn   623
   TType   int64                                     Morphology type code (10) MaskedColumn     4
    Tdw1    str5                                  Dwarf galaxy morphology (11) MaskedColumn   233
    Tdw2    str1               Dwarf galaxy surface brightness morphology (12) MaskedColumn   250
    RVel   int64        km / s               Heliocentric radial velocity (13) MaskedColumn   454
     Dis float64           Mpc                                        Distance       Column     0
   f\textsubscript{Dis}    str4                           Method flag used to obtain Dis (14)       Column     0
   RAh\textsubscript{2}   int64             h                 Hour of Right Ascension (J2000)       Column     0
   RAm\textsubscript{2}   int64           min               Minute of Right Ascension (J2000)       Column     0
   RAs\textsubscript{2} float64             s               Second of Right Ascension (J2000)       Column     0
   DE-\textsubscript{2}    str1                               Sign of the Declination (J2000)       Column     0
   DEd\textsubscript{2}   int64           deg                   Degree of Declination (J2000)       Column     0
   DEm\textsubscript{2}   int64        arcmin                Arcminute of Declination (J2000)       Column     0
   DEs\textsubscript{2}   int64        arcsec                Arcsecond of Declination (J2000)       Column     0
   a26\textsubscript{2} float64           kpc                       Major linear diameter (1) MaskedColumn    11
     inc   int64           deg                                     Inclination MaskedColumn    11
      Vm   int64        km / s            Amplitude of rotational velocity (2) MaskedColumn   635
    AB\textsubscript{2} float64           mag                  Internal B band extinction (3) MaskedColumn    11
    BMag float64           mag                   Absolute B band magnitude (4) MaskedColumn     8
     SBB float64 mag / arcsec2           Average B band surface brightness (5) MaskedColumn    11
 logKLum float64     dex(Lsun)                    Log K\textsubscript{S}\_ band luminosity (6) MaskedColumn    10
  logM26 float64     dex(Msun)             Log mass within Holmberg radius (7) MaskedColumn   634
l\textsubscript{logMHI}    str1                                          Limit flag on logMHI MaskedColumn  1226
  logMHI float64     dex(Msun)                           Log hydrogen mass (8) MaskedColumn   494
     VLG   int64        km / s                             Radial velocity (9) MaskedColumn   454
  Theta1 float64                                              Tidal index (10) MaskedColumn    76
      MD   str19                                      Main disturber name (11) MaskedColumn    76
  Theta5 float64                                      Another tidal index (12) MaskedColumn    76
  Thetaj float64      dex(---)              Log K band luminosity density (13) MaskedColumn   180
\end{document}

### 2024-05-16 paper.qmd
Added theory and heatmaps
- P and f param
- Gas depletion timescale
-Heatmaps of mass and mags

---
editor_options: 
  markdown: 
    wrap: 72
---

```{python}
import numpy as np
import numpy.ma as ma
import pandas as pd
from astropy.io import ascii
from astropy.table import Table, QTable, join, hstack, vstack, unique, Column, MaskedColumn, setdiff
from astropy.utils.masked import Masked
from astropy.coordinates import SkyCoord, Galactic, Angle
from astropy.time import Time
import astropy.units as u
from astropy.utils.diff import report_diff_values
from astropy.visualization import quantity_support, hist
quantity_support()
import glob as glob
import sys
import matplotlib.pyplot as plt
from plotnine import (
    ggplot,qplot, ggsave, aes,
    after_stat,
    stage,
    geom_point, geom_smooth, geom_qq, geom_bar, geom_text, geom_label,
    position_dodge2,
    facet_wrap,
    labs,
    scale_x_continuous, scale_x_log10, scale_y_log10,
    xlim, ylim,
    stat_qq
)
from scipy import optimize, stats
from sympy import symbols, exp, log, lambdify
import seaborn as sns
from custom_table import CustomQTable
```

```{python results="none"}
dt = QTable.read("./tables/final_table.ecsv")
```

set ggplot theme for matplotlib, seaborn

```{python results="none"}
sns.set_theme(style="darkgrid")

sns.set_palette("viridis")
```

::: abstract
The paper investigates the properties of galaxies in the Local
Cosmological Volume (LCV), using the Catalogue of Neighboring
[Galaxies\@karachentsevUPDATEDNEARBYGALAXY2013](mailto:Galaxies@karachentsevUPDATEDNEARBYGALAXY2013){.email}
and its updated version from the "Catalog & Atlas of the LV galaxies"
[database\@CatalogLVGalaxies](mailto:database@CatalogLVGalaxies){.email}.
The properties studied include the galaxy types, their various masses,
the star formation rates (SFRs) and the star formation timescale $\tau$,
gas depletion timescale $\tau_g$ and the star formation time $t_{sf}$.
The paper aims to understand the distribution and correlation of these
properties in the sample of galaxies in the LCV, and how they relate to
current astrophysical theories.
:::

# The Galaxies in the Local Cosmological Volume (LCV)

The Catalogue of Neigbouring Galaxies (Karachentsev, Igor D. and Makarov
et al.
[2013\@karachentsevUPDATEDNEARBYGALAXY2013](mailto:2013@karachentsevUPDATEDNEARBYGALAXY2013){.email})
and its updated version from the "Catalog & Atlas of the LV galaxies"
[databas\@CatalogLVGalaxies](mailto:databas@CatalogLVGalaxies){.email}
are used to extract the K-band luminosities, the types of the galaxies,
the mass within the Holmberg radius (M26), the Hydrogen masses of the
galaxies ($M_{HI}$) and the SFRs based on integrated H and
far-ultraviolet (FUV) measurments for galaxies within a distance of
$\approx 11$ Mpc.

## How are the galaxies chosen

According to @kraan-kortewegCatalogueGalaxiesIo1979 the Local
Cosmological Volume is defined as the galaxies inside the radius of 10
Mpc and having radial velocities with respect to centroid of the Local
Group $V_{lg} \le 500 \, km \cdot s^{-1}$. However, this assumed a
Hubble constant of $H_0 = 50\, km \cdot s^{-1}$.

1.  **Initial Selection Criteria**: Galaxies within a 10 Mpc radius were
    initially selected based on a radial velocity limit (VLG) of 500
    km/s, considering a Hubble parameter (H0) of 50 km/s/Mpc.

2.  **Updated Criteria**: To accommodate the revised H0 value of 73
    km/s/Mpc, the VLG limit needs to be raised to 730 km/s.

3.  **Local Velocity Field**: The presence of the Virgo cluster and the
    Local Void introduces additional velocity components, complicating
    distance estimation based solely on radial velocities.

4.  **Peculiar Motions**: Collective motions within large-scale
    structures can introduce peculiar velocities, complicating distance
    estimation.

5.  **Distance Measurement Methods**: Direct distance measurements using
    methods like the tip of the red giant branch (TRGB) provide accurate
    distances but are resource-intensive, requiring extensive
    observation time with instruments like the Hubble Space Telescope
    (HST).

6.  **Inclusion Criteria**: Galaxies are included based on either radial
    velocities or distance estimates, considering the limitations and
    uncertainties in both methods.

7.  **Extension to 11 Mpc**: Galaxies with distance estimates beyond 10
    Mpc may still be included due to uncertainties in distance
    measurements and the potential influence of coherent motions and
    large-scale structures.

8.  **Sample Composition**: The LV sample comprises
    src~python~$$:results value org$${len(dt)}
    {{{results(`1448`{.org})}}} galaxies, with considerations for
    galaxies near the boundaries of the selection criteria and the
    potential influence of measurement errors.

    ```{python results="file drawer value"}
    hubble = (ggplot(dt.to_pandas())
              + aes( x = "Dis", y =  "VLG")
              + labs( x = f"Distance [{dt['Dis'].unit}]" , y = "Radial velocities $V_{LG} $"+f"[{dt['VLG'].unit:latex}]" )
              + xlim(0,11) + ylim(0,1200)
              + geom_smooth(color = "red")
              + geom_point()
              )
    fname = "figure/hubble.png"
    hubble.save(fname)
    plt.show()
    plt.close()
    ```

# Mapping the galaxies

Because matplotlib needs the coordinates in radians and between $-\pi$
and $\pi$ and, not 0 and $2\pi$, we have to convert coordinates.

```{python results="value file drawer"}
filename = "figure/mapping"

# Assuming dt is your data table containing coordinates, mass, and distance
c = dt["Coordinates"]
mass = dt["M26"].data  # Assuming mass is provided in some unit
distance = dt["Dis"].data  # Assuming distance is provided in some unit

# Extract Galactic Coordinates
galactic_coords = c.galactic

# Extract Equatorial Coordinates
equatorial_coords = c.transform_to('icrs')

# Define the size and color based on mass and distance
marker_size = np.sqrt(mass) * 0.0002  # Adjust scaling factor as needed
marker_color = distance   # Use distance directly for marker color

# Plot Galactic Coordinates
plt.figure(figsize=(8, 8))
plt.subplot(211, projection="aitoff")
plt.grid(True)
plt.scatter(galactic_coords.l.wrap_at(180 * u.deg).radian, galactic_coords.b.radian, s=marker_size, c=marker_color, cmap='viridis')
plt.colorbar(label='Distance [{}]'.format(dt['Dis'].unit))  # Add colorbar for distance
plt.title("Galactic Coordinates")

# Plot Equatorial Coordinates
plt.subplot(212, projection="mollweide")
plt.grid(True)
plt.scatter(equatorial_coords.ra.wrap_at(180 * u.deg).radian, equatorial_coords.dec.radian, s=marker_size, c=marker_color, cmap='viridis')
plt.colorbar(label='Distance [{}]'.format(dt['Dis'].unit))  # Add colorbar for distance
plt.title("Equatorial Coordinates")

plt.suptitle("Galaxies of the LCV with Mass and Distance Representation")

plt.tight_layout()  # Adjust spacing between subplots
plt.savefig(filename)
plt.close()

filename+".png"
```

## Types of galaxies

Using the dataset of src~python~$$:results value org :exports
results$${len(dt)} {{{results(`1448`{.org})}}} galaxies, we can study
the morphology of the galaxies in the LCV

### Morphology

```{python results="value drawer" var="x = \"TType\" file = \"Types\" label = \"Morphology type code\""}
x="TType"
file="Types"
label="Morphology type code"
dttype = pd.DataFrame({"x": dt["{}".format(x)]}).dropna()
morphology = (
    ggplot(dttype, aes("factor(x)"))
    + geom_bar(color="black", fill="#1f77b4", show_legend=False)
    + geom_text(
        aes(label=after_stat("count")),
        stat="count",
        nudge_y=15,
        va="bottom",
        size = 9
    )
    + geom_text(
        aes(label=after_stat("prop*100"), group=1),
        stat="count",
        va="bottom",
        format_string="({:.1f}%)",
        size = 6
    )
    + labs(x = "{}".format(label))
)
fname = "figure/{}.png".format(file)
morphology.save(fname)

"[[./"+fname+"]]"
```

1.  Morphology of dwarf galaxies

2.  Dwarf galaxy surface brightness morphology

# Understanding the Data

The catalog consists of 8 tables

1.  Catalog of Nearby Galaxies
2.  Global Parameters of the Nearby Galaxies
3.  List of Apparent Magnitudes
4.  List of Heliocentric Velocities
5.  List of Inner Kinematics
6.  List of Distances
7.  List of the nearby galaxies with measured SFR
8.  List of Bibliographic References

We want several measurments from those lists so we will join them
according to the name of the galaxy.

This catalog consists of src~python~$$:results value org$${len(dt)+1}
{{{results(`1449`{.org})}}} galaxies

## Understanding the limit flags

Some of those values contain limit flags, which we will mask for our
present analysis. However, those values will be shown in the plots, and
afterwards will be compared with the theoretical values.

```{python}
for column in dt.columns:
    if column.startswith("l_") or column.startswith("f_"):
        if column.startswith("l_"):
            corresponding_column_name = column[2:]  # Remove the 'l_' prefix
        else:
            corresponding_column_name = column[2:]  # Remove the 'f_' prefix

        try:
            all_masks_in_corresponding = all(mask in dt[corresponding_column_name].mask for mask in dt[column].mask)
            if all_masks_in_corresponding:
                print(f"All masks in {column} are also masks in {corresponding_column_name}")
            else:
                print(f"Not all masks in {column} are masks in {corresponding_column_name}")
        except AttributeError:
            print(f"We have no mask for {column}")
```

# Standarized constants

We should use some standart consistent values for our analysis.

1.  According to @speagleHighlyConsistentFramework2014
    [and\@kroupaConstraintsStarFormation2020](mailto:and@kroupaConstraintsStarFormation2020){.email}
    the $t_{sf} = 12\, Gyr$ represents a strong and consistent
    constraint of galaxy evolution, across many studies. While other
    researchers adopt a t~sf~= 13.6
    [Gyr\@haslbauerCosmologicalStarFormation2023](mailto:Gyr@haslbauerCosmologicalStarFormation2023){.email},
    we use the 12 Gyr assumption following the framework of SP14
2.  $\zeta =$ accommodates mass-loss through stellar evolution.
    According to the IGIMF theory the galaxies of the the LCV are
    expected to have 1\< $\zeta$ \<1.3, so by adopting $\zeta =1.3$ we
    are working conservatively
3.  Main Sequence z = 5

```{python results="none"}
t_sf = 12 * u.Gyr
zeta = 1.3
z = 5
```

# Calculations for values that we need

## Total stellar masses, the total gas mass and total barionic of the galaxies

The $MHI$ can be converted to the total mass of the gas of the galaxy
using the equation $M_g=1.33\, MHI$

The K-band values are converted to the total Stellar Masses of each
galaxy according to the mass-to-light ratio of 0.6
($M_\odot/Lum$)@lelliSPARCMASSMODELS2016

```{python}
dt["StellarMass"] = 0.6 * dt["KLum"]* u.Msun/u.solLum
dt["StellarMass"].description = "K-band luminosity using a mass-to-light ratio of 0.6"
dt["StellarMass"].info()
```

The total barionic mass can be calcuated as the sum of the total gas
mass of the galaxy with the Stellar mass

```{python}
dt["BarMass"] = dt["M_g"] + dt["StellarMass"]

dt["BarMass"].info()
```

### Ratio of M~g~ and StellarMass

```{python}
dt["mass_ratio"] = dt["M_g"] / dt["StellarMass"]
dt["mass_ratio"].info(["attributes", "stats"])
```

Histogram of dt$$\"mass~ratio~\"$$

```{python}
#seaborn plot of mass_ratio
sns.histplot(dt["mass_ratio"].value)
plt.xscale("log")
plt.show()
```

## Color index

Here we calculate the color indexes \<FUV-B\>

```{python}
dt["color"] = dt["FUVmag"]-dt["Bmag"]
```

The lower the value, the bluer the stars, thus the younger the star
populations

```{python results="value file drawer"}
#hist
hist(dt["color"], bins = "freedman")
plt.xlabel("Color index")
plt.ylabel("Number of stars")
plt.title("Color index <FUV - B> distribution")
#save
plt.savefig("figure/color_index.png")
plt.close()
#print in org
"./figure/color_index.png"
```

## Fixing the SFRs

### SFR units

```{python results="none"}
SFR_unit = u.Msun/u.year
```

### log to linear

they are the power in logarithmic scale. SO lets fix them

```{python}
dt.rename_column("SFRFUV", "logSFRFUV")
dt["SFRFUV"] = 10**dt["logSFRFUV"].value * SFR_unit
dt["SFRFUV"].mask = dt["logSFRFUV"].mask
dt["SFRFUV"].description = dt["logSFRFUV"].description

dt["SFRFUV"].info()
```

```{python}
dt.rename_column("SFRHa", "logSFRHa")
dt["SFRHa"] = 10**dt["logSFRHa"].value * SFR_unit
dt["SFRHa"].mask = dt["logSFRHa"].mask
dt["SFRHa"].description = dt["logSFRHa"].description
```

```{python}
plt.scatter(dt["SFRHa"],dt["SFRFUV"])
plt.show()
```

```{python}
dt[["SFRFUV", 'SFRHa']].info("stats")
```

## SFR~0~

Now we have to calculate the total SFR from the equation:

$$
    SFR_o=\frac{SFR_{FUV}+SFR_{Ha}}{2}
$$

if we have both the SFR. If we only have one of them then:

$$
    SFR_{0}=SFR_{i},\ \text{if } SFR_{j}=0,\ i\neq j,\ i,j=SFR_{FUV},\, SFR_{Ha}
$$

create the average SFR~0~ from SFRHa SFRFUV with np.ma.average

```{python}
SFR_0 = np.mean([dt["SFRHa"], dt["SFRFUV"]], axis =0, where = [~dt["SFRHa"].mask, ~dt["SFRFUV"].mask])

dt["SFR_0"] = SFR_0 * SFR_unit

dt[["SFR_0","SFRFUV", 'SFRHa']].info("stats")
```

```{python}
print(dt["SFRHa"].info('stats'))
```

## Applying the cut SFR~0~ \>= 1e-3 solMass/yr

keep only the SFR~0~ data were \>1e-3

```{python}
dc = dt.copy()
dc = dc[dc["SFR_0"].value >= 1e-3]

print(dc["SFR_0"].info())
```

```{python}
dc[["SFR_0","SFRFUV", 'SFRHa']].info("stats")
```

Histogram of SFR~0~

```{python}
hist(dc["SFR_0"].value, bins = "scott")
plt.show()
```

## Theoretical Average SFR

To calculate the average Star Formation Rate $\overline{SFR}$ we can use
the equation

$$
    \overline{SFR}=\frac{\zeta M_*}{t_{sf}}
$$

where ζ is the mass-loss through stellar evolution and we assume that
$\zeta\approx 1.3$ (see explanation in the paper\`), M\* is the stellar
mass of each galaxy and we assume that is $t_{sf}=12.5\ Gyr$

```{python}
dc["av_SFR_theor"] = 1.3 * dc["StellarMass"] / t_sf.to(u.yr)
dc["av_SFR_theor"].info()
```

```{python}
plt.scatter(y = dc["av_SFR_theor"],x = dc["SFR_0"], c = dc["color"].value)
#colobar
plt.colorbar()

plt.xscale("log")
plt.yscale("log")
plt.show()
```

## Ratio av~SFR~/SFR~0~

Now we have to calculate the ratio $\frac{\overline{SFR}}{SFR_0}$

```{python}
dc["SFR_ratio"] = dc["av_SFR_theor"] / dc["SFR_0"]

#log10 of ratio
dc["logSFR_ratio"] = np.log10(dc["SFR_ratio"])

dc[["SFR_ratio", "logSFR_ratio"]].info(["attributes","stats"])
```

log10 of ratio

```{python}
plt.scatter(y = dc["SFR_ratio"],x = dc["SFR_0"], c = dc["color"].value)
#colobar
plt.colorbar()

plt.xscale("log")
plt.yscale("log")
plt.show()
```

Scatter color and ratio

```{python results="drawer file"}
plt.scatter(y = dc["SFR_ratio"],x =dc["color"] )
#title and labels with units in latex
plt.yscale("log")
plt.title("(ratio) vs color")
plt.ylabel("(ratio)")
plt.xlabel("color")
#save in dir figure
plt.savefig("figure/ratio_vs_color.png")
plt.close()
#print file
print("figure/ratio_vs_color.png")
```

# The Delayed-τ model

"The delayed-τ model describes the SFH of a galaxy assuming that the
SFRs typically rise in the early phase of galaxy evolution and gradually
decline to the present time (e.g. Reddy et al. 2012; Carnall et al.
2019). In fact, Speagle et al. (2014) showed in their figures 9 and 10
that the SFH of galaxies following the main sequence of star-forming
galaxies can be accurately parametrized by the delayed-τ model of the
form" @haslbauerCosmologicalStarFormation2023

```{=latex}
\begin{equation}
        \label{eq:SFR} SFR_{0,del}=\frac{A_{del}xe^{-x}}{\tau},\text{ where } x=\frac{tsf}{\tau}
\end{equation}
```
`\noindent`{=latex} where

is the star formation time-scale, $tsf$ is the real time of star
formation in a given galaxy and $Adel$ a normalization constant.

The average SFR is

```{=latex}
\begin{equation}
        \label{eq:av_SFR-x} \overline{SFRdel}=\frac{Adel}{tsf}[1-(1+x)e^{-x}]
\end{equation}
```
and can also be defined by the present day stellar mass

$$\label{eq:av_SFR M*}
        \overline{SFR}=\frac{\zeta M_*}{tsf}$$

where accommodates for mass-loss through stella evolution and This is a
system of 2 equations and 3 variables

## Calculating A~del~

### Constant t~sf~

The observed ages of galactic discs are $tsf≈ 12$
[Gyr\@knoxSurveyCoolWhite1999a](mailto:Gyr@knoxSurveyCoolWhite1999a){.email},
so assuming an approximation of $tsf=12$ Gyr, the $\overline{SFR_{del}}$
can be calcuated, from the equation (`\ref{eq:av_SFR M*}`{=latex}).

After that the equation of ratio

$$\label{eq:ratio}                                        \frac{\overline{SFRdel}}{SFR0,del}=\frac{e^x-x-1}{x^2}$$

can be solved numerically for x and using the equations
(`\Ref{eq:SFR}`{=latex}) and (`\Ref{eq:av_SFR-x}`{=latex}) the $Adel$
and of each galaxy are found.

```{python}
dc["SFR_0", "SFR_ratio", "StellarMass"].info()
```

```{python}
ratio_array = np.array(dc["SFR_ratio"])
sfr_array = np.array(dc["SFR_0"])
mass_array = np.array(dc["StellarMass"])
tsf = t_sf/u.yr
x2 = np.empty(len(dc))
```

### Newton

```{python}
for i in range(len(dc)-1):
    ratio = ratio_array[i]
    mass = mass_array[i]
    sfr = sfr_array[i]
    def f(x):
        return (-sfr + zeta*mass*x**2/(np.exp(x)-1-x)/tsf )  # only one real root at x = 1

    def f_prime(x):
        return -zeta*mass*(x*(np.exp(x)*(x-2)+x+2)/(np.exp(x)-x-1)**2)/tsf

    sol = optimize.root_scalar(f, bracket=[0, 4], x0 = 3.4, fprime = f_prime, method="newton")
    x2[i] = sol.root

dc["x_n"] = x2
dc["A_n"] = dc["SFR_0"]*t_sf.to(u.yr)*np.exp(dc["x_n"])/(dc["x_n"]**2)
```

```{python}
print(dc["x_n", "A_n"].info("stats"))
```

```{python results="value drawer"}
# Assuming you have already loaded your data into an Astropy table named 'dts'
# Replace 'x' with the name of the column you want to plot

# Create a histogram
hist(dc["x_n"], bins = "freedman")  # Adjust the number of bins as needed
plt.xlabel('X values')
plt.ylabel('Frequency')
plt.title('Histogram of Astropy Column "x"')
plt.show()
```

### fsolve

```{python}
from scipy.optimize import fsolve
# Example loop
x = np.ma.empty(len(dc))
A = np.ma.empty(len(dc))
for i in range(len(dc)-1):

    ratio = ratio_array[i]
    mass = mass_array[i]
    sfr = sfr_array[i]
    def sfrx(z):
        x = z[0]
        A = z[1]

        f = np.zeros(2)
        f[0] = ratio - (np.exp(x) - x - 1) / x**2
        f[1] = sfr - A * x * tsf * np.exp(-x) / x
        return f

    # Solve the equation
    z = fsolve(sfrx, [3, 10*9])
    x[i] = z[0]
    A[i] = z[1]

    ## mask if sfr ratio or mass is nan
    if np.isnan(ratio) or np.isnan(mass):
        x[i] = np.nan
        A[i] = np.nan

dc["x_f"] = MaskedColumn(x, name = "x")
dc["A_f"] = MaskedColumn(A, name = "A", unit = u.solMass)
```

```{python}
print(dc["x_f","A_f"].info(["attributes" ,"stats"]))
```

scatter of x2 and A

### Compare the methods

```{python}
plt.scatter(dc["x_f"], dc["A_f"])
#plt.scatter(dc["x_n"], dc["A_n"], alpha = 0.7)

plt.xlabel('x')
plt.yscale("log")
plt.title('scatter of x and A')
plt.show()
```

```{python results="value file drawer"}
hist(dc["x_f"], bins = "knuth")
hist(dc["x_n"], bins = "knuth", alpha = 0.6)
plt.xlabel('x')
plt.ylabel("Number of galaxies")
plt.title('Hist of x solved with fsolve and Newton')
#show the labels
plt.legend(["fsolve", "Newton"])

plt.savefig("figure/x-hist.png")
plt.close()

"figure/x-hist.png"
```

```{python}
print(dc["x","x2"].info(["attributes" ,"stats"]))
```

```{python results="value file drawer"}
plt.scatter(dc["x_f"], dc["x_n"])
plt.xlabel('$x_{fsolve}$')
plt.ylabel(r'$x_{Newton}$')
plt.title('scatter of $x_{Newton}$ and $x_{fsolve}$')
#savefig and print the file
plt.savefig("figure/x-scatter.png")
plt.close()

"figure/x-scatter.png"
```

Since they are both prety much the same, we can assume that the more
compact is better, ie fsolve.

### Hist of A

```{python results="value file"}
hist(dc["A_f"], bins = "blocks")
hist(dc["A_n"], bins = "blocks")
plt.xscale("log")
plt.xlabel('$A_{del}$'+f'[{dc["A_n"].unit:latex}]')

plt.legend(["fsolve", "Newton"])

plt.ylabel("Number of galaxies")
plt.title('Histogram of $A_{del}$')
#save
plt.savefig("figure/A-hist.png")
plt.close()

"figure/A-hist.png"
```

## Calculating the t~sf~ and τ of the galaxies

```{python}
dc['tau'] = t_sf/dc["x_f"]

print(dc["tau"].info(["attributes", "stats"]))
```

```{python}
hist(dc["tau"].data, bins = "freedman")
plt.show()
```

```{python}
plt.scatter(dc["x_f"], dc["A_f"], c=np.log10(dc["SFR_0"]/dc["SFR_0"].unit), cmap = "viridis")
plt.title('Scatter plot of A vs x')
plt.xlabel(r'$\tau$ '+ f'[{dc["tau"].unit:latex}]')
plt.ylabel(r'$A$ '+ f'[{dc["A_f"].unit:latex}]')
plt.yscale("log")

plt.colorbar()
plt.show()
```

```{python}
print(dc["A_n", "x_n"].info())
```

```{python results="value file drawer"}
plt.scatter(dc["A_n"], dc["x_n"], c=np.log10(dc["StellarMass"]/dc["StellarMass"].unit), cmap = "viridis")
plt.title('Scatter plot of A vs x')
plt.xlabel(r'$\tau$ '+ f'[{dc["tau"].unit:latex}]')
plt.ylabel(r'$A$ '+ f'[{dc["A_f"].unit:latex}]')
plt.yscale("log")

plt.colorbar()
plt.show()
```

### IDEA Check to see if the almost inf points make any sense

## [TODO]{.todo .TODO} The gas depletion timescale τ~g~ {#the-gas-depletion-timescale-τg}

What is the gas depletion timescale?

## [TODO]{.todo .TODO} The theoretical SFR vs the observed {#the-theoretical-sfr-vs-the-observed}

# PROJ The relations of the Masses

Since the aim of the paper is to find the SFR lets first understand and
calculate the masses of the galaxies and see if we can find any relation
with the SFR.

```{python}
df = dc.to_pandas()
# Assuming df is your DataFrame
# Step 1: Identify non-numeric columns
non_numeric_columns = df.select_dtypes(exclude=['float', 'int']).columns

# Step 2: Drop non-numeric columns or handle them appropriately
df_numeric = df.drop(columns=non_numeric_columns)
# Step 3: Replace NaN values with zeros or other appropriate values

df_numeric = df_numeric.loc[:, ~df_numeric.columns.str.startswith('e_')]

df_numeric = df_numeric.loc[:, ~df_numeric.columns.str.startswith('Name')]
df_numeric = df_numeric.loc[:, ~df_numeric.columns.str.startswith('Coord')]
df_numeric = df_numeric.loc[:, ~df_numeric.columns.str.startswith('log')]
# Step 4: Calculate the correlation matrix
correlation_matrix = df_numeric.corr()

plt.close("all")
```

```{python}
# Plot heatmap using seaborn
sns.heatmap(correlation_matrix, annot=False, cmap='coolwarm', fmt=".2f", linewidths=0.5)
# Set x-axis tick labels
plt.xticks(ticks=np.arange(0.5, len(correlation_matrix.columns)), labels=correlation_matrix.columns, rotation=90)

# Set y-axis tick labels
plt.yticks(ticks=np.arange(0.5, len(correlation_matrix.index)), labels=correlation_matrix.index, rotation=0)
plt.title('Correlation Heatmap')
plt.savefig("figure/heatmap")
plt.show()
plt.close("all")
```

```{python}
clustermap = sns.clustermap(correlation_matrix, cmap='coolwarm', fmt=".2f", linewidths=0.5,
                             row_cluster=False, col_cluster=False)

ax = clustermap.ax_heatmap

# Set x-axis tick labels
ax.set_xticks(np.arange(0.5, len(correlation_matrix.columns)))
ax.set_xticklabels(correlation_matrix.columns, rotation=90)

# Set y-axis tick labels
ax.set_yticks(np.arange(0.5, len(correlation_matrix.index)))
ax.set_yticklabels(correlation_matrix.index, rotation=0)

plt.savefig("figure/clustermap")
plt.show()
plt.close("all")
```

Pairplot with StellarMass, MHI, SFR~0~ and av~SFR~, M26

```{python}
#PairGrid with StellarMass, MHI, SFR_0 and av_SFR_theor, M26
#log scale axes

sns.pairplot(df, vars=["StellarMass", "MHI", "SFR_0", "av_SFR_theor", "M26"], kind="reg", diag_kind="kde")
plt.savefig("figure/pairplot")
plt.show()
plt.close("all")
print(df[["StellarMass", "MHI", "SFR_0", "av_SFR_theor", "M26", "M_g", "tau", "A"]].corr())
```

# [TODO]{.todo .TODO} The relations of the Data {#the-relations-of-the-data}

## [TODO]{.todo .TODO} Luminosity and Masses {#luminosity-and-masses}

## [TODO]{.todo .TODO} Variations in Star Formation Rates across the different masses {#variations-in-star-formation-rates-across-the-different-masses}

# [TODO]{.todo .TODO} Filling the Catalogue {#filling-the-catalogue}

### 2024-05-16 paper.tex
Added theory and heatmaps
- P and f param
- Gas depletion timescale
-Heatmaps of mass and mags

--- 2023-03-15 paper.tex
@@
-% Created 2023-03-15 Wed 11:50
+% Created 2024-05-15 Wed 03:05
 % Intended LaTeX compiler: pdflatex
@@
 \usepackage{breakcites}
-\usepackage{apacite}
 \usepackage{paralist}
+\usepackage{amsmath}
 \usepackage{biblatex}
-\addbibresource{/home/dp/Documents/Research_paper_SFR/bibl/bibliography/bibliography.bib}
 \usepackage{hyperref}
+\usepackage{graphicx}
+\usepackage{caption}
+\usepackage{booktabs}
+\usepackage[T1]{fontenc}
+\usepackage{tgbonum}
 \let\itemize\compactitem
@@
 \let\enumerate\compactenum
-\addbibresource{/bibl/bibliography/bibliography.bib}
 \author{Dimitrios Papachistopoulos}
 \date{\today}
-\title{Finding the normalization constant of \(SFR_{del}\) and the relations between the various masses of the Galaxies}
+\title{Investigations of the galaxies of the LCV\\\medskip
+\large Finding the normalization constant of SFR_{del} and the relations between the various masses of the Galaxies}
 \hypersetup{
  pdfauthor={Dimitrios Papachistopoulos},
- pdftitle={Finding the normalization constant of \(SFR_{del}\) and the relations between the various masses of the Galaxies},
+ pdftitle={Investigations of the galaxies of the LCV},
  pdfkeywords={},
  pdfsubject={},
- pdfcreator={Emacs 28.2 (Org mode 9.6.1)}, 
+ pdfcreator={Emacs 29.3 (Org mode 9.6.24)}, 
  pdflang={English}}
@@
 \maketitle
-\tableofcontents
 
-\#\#+\LaTeX{}\textsubscript{HEADER}: \affiliation{Dr. Pavel Kroupa}
-\begin{ABSTRACT}
-
-\textbf{Abstract}
-
-\noindent\rule{\textwidth}{0.5pt}
-\end{ABSTRACT}
-\tableofcontents
+\begin{abstract}
+The paper investigates the properties of galaxies in the Local Cosmological Volume (LCV), using the Catalogue of Neighboring Galaxies(Karachentsev, Igor D.
+and Makarov, Dmitry I.
+and Kaisina, Elena I., 2013) and its updated version from the ``Catalog \& Atlas of the LV galaxies'' database(, ).
+The properties studied include the galaxy types, their various masses, the star formation rates (SFRs) and the star formation timescale \(\tau\), gas depletion timescale \(\tau_g\) and the star formation time \(t_{sf}\).
+The paper aims to understand the distribution and correlation of these properties in the sample of galaxies in the LCV, and how they relate to current astrophysical theories.
+\end{abstract}
 
 \section{The Galaxies in the Local Cosmological Volume (LCV)}
-\label{sec:org776cf02}
+\label{sec:orga2f0b32}
 
@@
 and Makarov  et al.
-2013\autocite{karachentsevUPDATEDNEARBYGALAXY2013}) and its updated version from the ``Catalog \& Atlas of the LV galaxies'' database \cite{CatalogLVGalaxies} are used to extract the K-band luminosities, the types of the galaxies, the mass within the Holmberg radius (M26), the Hydrogen masses of the galaxies (\(M_{HI}\)) and the SFRs based on integrated  H and far-ultraviolet (FUV) measurments for galaxies within a distance of
-\(\approx 11\) Mpc. The SFR values contain limit flags, which we exclude from our present analysis. This gives a sample of 793 galaxies from 1248. From the remaing galaxies we have
+2013(Karachentsev, Igor D.
+and Makarov, Dmitry I.
+and Kaisina, Elena I., 2013)) and its updated version from the ``Catalog \& Atlas of the LV galaxies'' databas(, )  are used to extract the K-band luminosities, the types of the galaxies, the mass within the Holmberg radius (M26), the Hydrogen masses of the galaxies (\(M_{HI}\)) and the SFRs based on integrated  H and far-ultraviolet (FUV) measurments for galaxies within a distance of \(\approx 11\) Mpc.
+
+\subsection{How are the galaxies chosen}
+\label{sec:orgde10150}
+
+According to (Kraan-Korteweg, R.
+C.
+and Tammann, G.
+A., 1979) the Local Cosmological Volume is defined as the galaxies inside the radius of 10 Mpc and having radial velocities with respect to centroid of the Local Group \(V_{lg} \le 500 \, km \cdot s^{-1}\).
+However, this assumed a Hubble constant of \(H_0 = 50\, km \cdot s^{-1}\).
+
+\begin{enumerate}
+\item \textbf{Initial Selection Criteria}: Galaxies within a 10 Mpc radius were initially selected based on a radial velocity limit (VLG) of 500 km/s, considering a Hubble parameter (H0) of 50 km/s/Mpc.
+
+\item \textbf{Updated Criteria}: To accommodate the revised H0 value of 73 km/s/Mpc, the VLG limit needs to be raised to 730 km/s.
+
+\item \textbf{Local Velocity Field}: The presence of the Virgo cluster and the Local Void introduces additional velocity components, complicating distance estimation based solely on radial velocities.
+
+\item \textbf{Peculiar Motions}: Collective motions within large-scale structures can introduce peculiar velocities, complicating distance estimation.
+
+\item \textbf{Distance Measurement Methods}: Direct distance measurements using methods like the tip of the red giant branch (TRGB) provide accurate distances but are resource-intensive, requiring extensive observation time with instruments like the Hubble Space Telescope (HST).
+
+\item \textbf{Inclusion Criteria}: Galaxies are included based on either radial velocities or distance estimates, considering the limitations and uncertainties in both methods.
+
+\item \textbf{Extension to 11 Mpc}: Galaxies with distance estimates beyond 10 Mpc may still be included due to uncertainties in distance measurements and the potential influence of coherent motions and large-scale structures.
+
+\item \textbf{Sample Composition}: The LV sample comprises \texttt{1448} galaxies, with considerations for galaxies near the boundaries of the selection criteria and the potential influence of measurement errors.
 
 \begin{center}
-\begin{tabular}{|l|l|}
-\hline
-Measurment & Number of Galaxies \\
-\hline
-Hydrogen-Mass & 643 \\
-M26 & 643 \\
-K-band lum. & 789 \\
-Type & 793 \\
-H \$$\backslash$alpha\$ -S & 566 \\
-FUV-SFR & 688 \\
-\hline
-\end{tabular}
+\includegraphics[width=.9\linewidth]{figure/hubble.png}
+\end{center}
+\end{enumerate}
+
+\subsection{Mapping the galaxies}
+\label{sec:orgedc2b80}
+
+Because matplotlib needs the coordinates in radians and between \(-\pi\) and \(\pi\)
+and, not 0 and \(2\pi\), we have to convert coordinates.
+
+\begin{center}
+\includegraphics[width=.9\linewidth]{figure/mapping.png}
 \end{center}
 
-The K-band values are converted to the total Stellar Masses of each galaxy according to the mass-to-light ratio of 0.6 (\cite{lelliSPARCMASSMODELS2016}), and the \(M_{HI}\) can be converted to the total mass of the gas of the galaxy using the equation \(M_g=1.33\,M_{HI}\)
+\subsection{Types of galaxies}
+\label{sec:org026d262}
 
-The total SFR of each galaxy can be calcuated by
+Using the dataset of \texttt{1448}
+galaxies, we can study the morphology of the galaxies in the LCV
+
+\subsubsection{Morphology}
+\label{sec:org66e126b}
+\begin{center}
+\includegraphics[width=.9\linewidth]{./figure/Types.png}
+\end{center}
+
+\begin{enumerate}
+\item Morphology of dwarf galaxies
+\label{sec:org9759d71}
+
+\begin{center}
+\includegraphics[width=.9\linewidth]{./figure/Types.png}
+\end{center}
+
+\item Dwarf galaxy surface brightness morphology
+\label{sec:org80a0b66}
+
+\begin{center}
+\includegraphics[width=.9\linewidth]{./figure/Types.png}
+\end{center}
+\end{enumerate}
+
+\section{Understanding the Data}
+\label{sec:org7cd3cde}
+
+The catalog consists of 8 tables
+
+\begin{enumerate}
+\item Catalog of Nearby Galaxies
+\item Global Parameters of the Nearby Galaxies
+\item List of Apparent Magnitudes
+\item List of Heliocentric Velocities
+\item List of Inner Kinematics
+\item List of Distances
+\item List of the nearby galaxies with measured SFR
+\item List of Bibliographic References
+\end{enumerate}
+
+We want several measurments from those lists so we will join them according to the name of the galaxy.
+
+This catalog consists of \texttt{1449} galaxies
+
+\subsection{Understanding the limit flags}
+\label{sec:org3ad49c4}
+
+Some of those values contain limit flags, which we will mask for our present analysis. However, those values will be shown in the plots, and afterwards will be compared with the theoretical values.
+
+\begin{verbatim}
+All masks in l_FUVmag are also masks in FUVmag
+All masks in l_Hamag are also masks in Hamag
+All masks in f_Kmag are also masks in Kmag
+All masks in l_21mag are also masks in 21mag
+We have no mask for f_Dis
+All masks in l_logMHI are also masks in logMHI
+All masks in l_mag_B are also masks in mag_B
+All masks in l_mag_FUV are also masks in mag_FUV
+All masks in l_mag_HI are also masks in mag_HI
+All masks in l_mag_Ha are also masks in mag_Ha
+All masks in l_mag_Ks are also masks in mag_Ks
+All masks in l_SFRHa are also masks in SFRHa
+All masks in l_PHa are also masks in PHa
+All masks in l_FHa are also masks in FHa
+All masks in l_SFRFUV are also masks in SFRFUV
+All masks in l_PFUV are also masks in PFUV
+All masks in l_FFUV are also masks in FFUV
+\end{verbatim}
+
+\section{Standarized constants}
+\label{sec:org7f042ce}
+
+We should use some standart consistent values for our analysis.
+
+\begin{enumerate}
+\item According to (Speagle, Joshua S.
+and Steinhardt, Charles L.
+and Capak, Peter L.
+and Silverman, John D., 2014) and(Kroupa, P and Haslbauer, M and Banik, I and Nagesh, S T and Pflamm-Altenburg, J, 2020) the \(t_{sf} = 12\, Gyr\) represents a strong and consistent constraint of galaxy evolution, across many studies.
+While other researchers adopt a t\textsubscript{sf}= 13.6 Gyr(Haslbauer, Moritz and Kroupa, Pavel and Jerabkova, Tereza, 2023), we use the 12 Gyr assumption following the framework of SP14
+\item \(\zeta =\) accommodates mass-loss through stellar evolution.
+According to the IGIMF theory the galaxies of the the LCV are expected to have 1< \(\zeta\) <1.3, so by adopting \(\zeta =1.3\) we are working conservatively
+\item Main Sequence z = 5
+\end{enumerate}
+
+\section{Calculations for values that we need}
+\label{sec:orgea354e0}
+
+\subsection{Total stellar masses, the total gas mass and total barionic of the galaxies}
+\label{sec:orgf921de0}
+
+The \(MHI\) can be converted to the total mass of the gas of the galaxy using the equation \(M_g=1.33\, MHI\)
+
+The K-band values are converted to the total Stellar Masses of each galaxy according to the mass-to-light ratio of 0.6 (\(M_\odot/Lum\))(Lelli, Federico and McGaugh, Stacy S.
+and Schombert, James M., 2016)
+
+\begin{verbatim}
+name = StellarMass
+dtype = float64
+unit = solMass
+description = Linear K_S_ band luminosity
+class = MaskedQuantity
+n_bad = 12
+length = 1448
+\end{verbatim}
+
+The total barionic mass can be calcuated as the sum of the total gas mass of the galaxy with the Stellar mass
+
+\begin{verbatim}
+name = BarMass
+dtype = float64
+unit = solMass
+description = Linear hydrogen mass
+class = MaskedQuantity
+n_bad = 513
+length = 1448
+\end{verbatim}
+
+\subsubsection{Ratio of M\textsubscript{g} and StellarMass}
+\label{sec:org6ebf887}
+
+\begin{verbatim}
+/home/dp/.local/lib/python3.10/site-packages/astropy/utils/masked/core.py:879: RuntimeWarning: divide by zero encountered in divide
+name = mass_ratio
+dtype = float64
+description = Linear hydrogen mass
+class = MaskedQuantity
+mean = 2.13272
+std = 3.81136
+min = 7.51105e-05
+max = 58.3043
+n_bad = 513
+length = 1448
+\end{verbatim}
+
+Histogram of dt[``mass\textsubscript{ratio}'']
+
+\subsection{Color index}
+\label{sec:orgdc5850f}
+
+Here we calculate the color indexes <FUV-B>
+
+The lower the value, the bluer the stars, thus the younger the star populations
+
+\begin{center}
+\includegraphics[width=.9\linewidth]{./figure/color_index.png}
+\end{center}
+
+\subsection{Fixing the SFRs}
+\label{sec:orgbc555ea}
+
+\subsubsection{SFR units}
+\label{sec:orgbb95c1a}
+
+\begin{verbatim}
+None
+\end{verbatim}
+\subsubsection{log to linear}
+\label{sec:org61b8988}
+
+they are the power in logarithmic scale. SO lets fix them
+
+\begin{verbatim}
+name = SFRFUV
+dtype = float64
+unit = solMass / yr
+class = Quantity
+n_bad = 321
+length = 1448
+\end{verbatim}
+
+\begin{verbatim}
+<QTable length=1448>
+ name          mean                 std                    min                  max      
+------ -------------------- -------------------- ------------------------ ---------------
+SFRFUV 2.27435 solMass / yr 4.13466 solMass / yr 2.13796e-10 solMass / yr 10 solMass / yr
+ SFRHa 4.97642 solMass / yr 4.94957 solMass / yr 1.38038e-10 solMass / yr 10 solMass / yr
+\end{verbatim}
+
+\subsection{SFR\textsubscript{0}}
+\label{sec:org10b773e}
+
+Now we have to calculate the total SFR from the equation:
 
@@
 
-if both \(SFR_{H\alpha},SFR_{FUV}\) measurments are available. If only one only one of them is given, then the SFR is equal to the given SFR value
+if we have both the SFR. If we only have one of them then:
 
 $$
-    SFR_o=SFR_i,\ \text{if } SFR_j=0,\ i\neq j,\ i,j=SFR_{FUV},\, SFR_{Ha}
+    SFR_{0}=SFR_{i},\ \text{if } SFR_{j}=0,\ i\neq j,\ i,j=SFR_{FUV},\, SFR_{Ha}
 $$
 
-The condition \(SFR_o\geq 10^{-3}M_\odot yr^{-1}\) leaves 579 galaxies.
-This condition is applied due to the reasons given in the P.
-Kroupa,M.
-Haslbauer, I.
-Banik, S.
-T.
-Nagesh and J.
-Pflamm-Altenburg et al.
-2020 \cite{kroupaConstraintsStarFormation2020}
+create the average SFR\textsubscript{0} from SFRHa SFRFUV with np.ma.average
 
-\section{Types of galaxies}
-\label{sec:org3f06310}
+\begin{verbatim}
+/home/dp/.local/lib/python3.10/site-packages/numpy/core/fromnumeric.py:3504: RuntimeWarning: Mean of empty slice.
+/home/dp/.local/lib/python3.10/site-packages/numpy/core/_methods.py:121: RuntimeWarning: invalid value encountered in divide
+<QTable length=1448>
+ name           mean                   std                    min                    max          n_bad
+------ ---------------------- --------------------- ------------------------ -------------------- -----
+ SFR_0 0.0722542 solMass / yr 0.316258 solMass / yr 1.75917e-10 solMass / yr 4.38718 solMass / yr   190
+SFRFUV   2.27435 solMass / yr  4.13466 solMass / yr 2.13796e-10 solMass / yr      10 solMass / yr     0
+ SFRHa   4.97642 solMass / yr  4.94957 solMass / yr 1.38038e-10 solMass / yr      10 solMass / yr     0
+\end{verbatim}
 
-Using the dataset of 1248 galaxies, do before using the condition and removing the galaxies with the flags, the below histograms can be plotted.
+\begin{verbatim}
+name = SFRHa
+mean = 4.97642 solMass / yr
+std = 4.94957 solMass / yr
+min = 1.38038e-10 solMass / yr
+max = 10 solMass / yr
+n_bad = 712
+length = 1448
+None
+\end{verbatim}
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=.9\linewidth]{./graphs/hist-Type.png}
-\caption{\label{Types of galaxies}The classification by de Vaucouleurs et al. (1991) is used for the morphology of the galaxies}
-\end{figure}
+\subsection{Applying the cut SFR\textsubscript{0} >= 1e-3 solMass/yr}
+\label{sec:org8549e88}
 
-Most of the galaxies in the LCV are Higly Irregular galaxies followed by lenticular galaxies
+keep only the SFR\textsubscript{0} data were >1e-3
 
-Out of the 1248 galaxies the 1022 are dwarf galaxies
+\begin{verbatim}
+[0;33mWARNING[0m: column logKLum has a unit but is kept as a MaskedColumn as an attempt to convert it to Quantity failed with:
+UnitTypeError("MaskedQuantity instances require normal units, not <class 'astropy.units.function.logarithmic.DexUnit'> instances.") [astropy.table.table]
+[0;33mWARNING[0m: column logM26 has a unit but is kept as a MaskedColumn as an attempt to convert it to Quantity failed with:
+UnitTypeError("MaskedQuantity instances require normal units, not <class 'astropy.units.function.logarithmic.DexUnit'> instances.") [astropy.table.table]
+[0;33mWARNING[0m: column logMHI has a unit but is kept as a MaskedColumn as an attempt to convert it to Quantity failed with:
+UnitTypeError("MaskedQuantity instances require normal units, not <class 'astropy.units.function.logarithmic.DexUnit'> instances.") [astropy.table.table]
+name = SFR_0
+dtype = float64
+unit = solMass / yr
+class = Quantity
+n_bad = 0
+length = 607
+None
+\end{verbatim}
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=.9\linewidth]{./graphs/hist-Tdw1.png}
-\caption{\label{Types of dwarf galaxies}Dwarf galaxy morphology}
-\end{figure}
+\begin{verbatim}
+<QTable length=607>
+ name           mean                  std                    min                    max         
+------ --------------------- --------------------- ------------------------ --------------------
+ SFR_0 0.149597 solMass / yr 0.442412 solMass / yr  0.00102329 solMass / yr 4.38718 solMass / yr
+SFRFUV  1.66911 solMass / yr   3.5739 solMass / yr 6.60693e-05 solMass / yr      10 solMass / yr
+ SFRHa  1.95358 solMass / yr  3.81106 solMass / yr 2.04174e-05 solMass / yr      10 solMass / yr
+\end{verbatim}
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=.9\linewidth]{./graphs/hist-Tdw2.png}
-\caption{\label{Types of dwarf galaxies brightness}Dwarf galaxy surface brightness morphology, where: H = high; N = normal; L = low; X = extremely low.}
-\end{figure}
+Histogram of SFR\textsubscript{0}
 
-Most dwarf galaxies have low brightness and are irregulars followed by Dwarf spheroidal.
+\subsection{Theoretical Average SFR}
+\label{sec:org283c16a}
 
-\section{Calculation of the normalization constant}
-\label{sec:orgbfb382e}
+To calculate the average Star Formation Rate \(\overline{SFR}\) we can use the equation
 
-According to P. Kroupa et al. 2020 current star formation rates of galaxies can be described by the 'delayed-\(\tau\)' mode as
+$$
+    \overline{SFR}=\frac{\zeta M_*}{t_{sf}}
+$$
 
-\begin{equation} \label{eq:SFR}
-SFR_{0,del}=\frac{A_{del}xe^{-x}}{\tau},\text{ where } x=\frac{t_{sf}}{\tau}
+where ζ is the mass-loss through stellar evolution and we assume that \(\zeta\approx 1.3\) (see explanation in the paper`), M* is the stellar mass of each galaxy and we assume that is   \(t_{sf}=12.5\ Gyr\)
+
+\begin{verbatim}
+name = av_SFR_theor
+dtype = float64
+unit = solMass / yr
+description = Linear K_S_ band luminosity
+class = MaskedQuantity
+n_bad = 1
+length = 607
+\end{verbatim}
+
+\subsection{Ratio av\textsubscript{SFR}/SFR\textsubscript{0}}
+\label{sec:org01c7dc6}
+
+Now we have to calculate the ratio \(\frac{\overline{SFR}}{SFR_0}\)
+
+\begin{verbatim}
+/home/dp/.local/lib/python3.10/site-packages/astropy/utils/masked/core.py:879: RuntimeWarning: divide by zero encountered in log10
+<QTable length=607>
+    name      dtype          description             class         mean     std       min      max   n_bad
+------------ ------- --------------------------- -------------- --------- -------- --------- ------- -----
+   SFR_ratio float64 Linear K_S_ band luminosity MaskedQuantity   5.77922  45.5965 0.0325391 1054.18     1
+logSFR_ratio float64 Linear K_S_ band luminosity MaskedQuantity 0.0646566 0.515905  -1.48759 3.02291     1
+\end{verbatim}
+
+log10 of ratio
+
+Scatter color and ratio
+
+\begin{center}
+\includegraphics[width=.9\linewidth]{figure/ratio_vs_color.png}
+\end{center}
+
+\section{The Delayed-\(\tau\) model}
+\label{sec:org0d51031}
+
+``The delayed-τ model describes the SFH of a galaxy assuming that the SFRs typically rise in the early phase of galaxy evolution and gradually decline to the present time (e.g.
+Reddy et al.
+2012; Carnall et al.
+2019).
+In fact, Speagle et al.
+(2014) showed in their figures 9 and 10 that the SFH of galaxies following the main sequence of star-forming galaxies can be accurately parametrized by the delayed-τ model of the form'' (Haslbauer, Moritz and Kroupa, Pavel and Jerabkova, Tereza, 2023)
+
+\begin{equation}
+        \label{eq:SFR} SFR_{0,del}=\frac{A_{del}xe^{-x}}{\tau},\text{ where } x=\frac{tsf}{\tau}
 \end{equation}
 
-\(\tau\) is the star formation time-scale and \(t_{sf}\) is the real time of star formation in a given galaxy
+\noindent where
+
+is the star formation time-scale, \(tsf\) is the real time of star formation in a given galaxy and \(Adel\) a normalization constant.
 
@@
 
-\begin{equation}\label{eq:av_SFR-x}
-\overline{SFR_{del}}=\frac{A_{del}}{t_{sf}}[1-(1+x)e^{-x}]
+\begin{equation}
+        \label{eq:av_SFR-x} \overline{SFRdel}=\frac{Adel}{tsf}[1-(1+x)e^{-x}]
 \end{equation}
@@
 \begin{equation}\label{eq:av_SFR M*}
-    \overline{SFR}=\frac{\zeta M_*}{t_{sf}}
+        \overline{SFR}=\frac{\zeta M_*}{tsf}
 \end{equation}
-where \(\zeta\) accommodates for mass-loss through stella evolution and \(\zeta\approx 1.3\)
 
-\subsection{Constant \(t_{sf}\)}
-\label{sec:org4bfffb4}
-The observed ages of galactic discs are \(t_{sf}\approx 12\) Gyr (e.g.
-Knox, Hawkins \& Hambly 1999), so assuming an approximation of \(t_{sf}=12.5\) Gyr, the \(\overline{SFR_{del}}\) can be calcuated, from the equation (\ref{eq:av_SFR M*}).
+where
+accommodates for mass-loss through stella evolution and This is a system of 2 equations and 3 variables
+
+\subsection{Calculating A\textsubscript{del}}
+\label{sec:orgb51a76e}
+
+\subsubsection{Constant t\textsubscript{sf}}
+\label{sec:org1f90dc5}
+The observed ages of galactic discs are \(tsf≈ 12\) Gyr(Knox, R.
+A.
+and Hawkins, M.
+R.
+S.
+and Hambly, N.
+C., 1999), so assuming an approximation of \(tsf=12\) Gyr, the \(\overline{SFR_{del}}\) can be calcuated, from the equation (\ref{eq:av_SFR M*}).
+
 After that the equation of ratio
 
-\begin{equation} \label{eq:ratio}
-    \frac{\overline{SFR_{del}}}{SFR_{0,del}}=\frac{e^x-x-1}{x^2}
+\begin{equation} \label{eq:ratio}                                        \frac{\overline{SFRdel}}{SFR0,del}=\frac{e^x-x-1}{x^2}
 \end{equation}
 
-can be solved numerically for \(x\) and using the equations (\Ref{eq:SFR}) and (\Ref{eq:av_SFR-x}) the \(A_{del}\) and \(\tau\) of each galaxy are found
+can be solved numerically for x and using the equations (\Ref{eq:SFR}) and (\Ref{eq:av_SFR-x}) the \(Adel\) and of each galaxy are found.
 
 \begin{verbatim}
-                x           tau         A_del
-count  550.000000  5.500000e+02  5.500000e+02
-mean     1.762321  1.126908e+11  2.600301e+12
-std      1.388768  1.067717e+12  4.456457e+13
-min      0.000559  2.198306e+09  2.477977e+07
-50%      1.513139  8.260984e+09  6.446495e+08
-max      5.686198  2.237735e+13  1.005083e+15
+<QTable length=607>
+    name     dtype      unit             description             class      n_bad
+----------- ------- ------------ --------------------------- -------------- -----
+      SFR_0 float64 solMass / yr                                   Quantity     0
+  SFR_ratio float64              Linear K_S_ band luminosity MaskedQuantity     1
+StellarMass float64      solMass Linear K_S_ band luminosity MaskedQuantity     1
+\end{verbatim}
+
+\subsubsection{Newton}
+\label{sec:org30977fb}
+
+\begin{verbatim}
+/home/dp/.local/lib/python3.10/site-packages/scipy/optimize/_root_scalar.py:315: RuntimeWarning: Derivative was zero.
+\end{verbatim}
+
+\begin{verbatim}
+<QTable length=607>
+name         mean                std                 min                 max         n_bad
+---- ------------------- ------------------- ------------------- ------------------- -----
+ x_n             1.66518             2.91771            -29.6974             11.9164     1
+ A_n 5.27714e+10 solMass 5.20772e+11 solMass 1.60997e-08 solMass 8.60539e+12 solMass     1
+None
+\end{verbatim}
+
+None
+
+\subsubsection{fsolve}
+\label{sec:org9cc68bf}
+
+\begin{verbatim}
+/tmp/babel-kO0xZX/python-PUK4ui:20: RuntimeWarning: The iteration is not making good progress, as measured by the 
+  improvement from the last five Jacobian evaluations.
+/tmp/babel-kO0xZX/python-PUK4ui:20: RuntimeWarning: The iteration is not making good progress, as measured by the 
+  improvement from the last ten iterations.
+\end{verbatim}
+
+\begin{verbatim}
+<QTable length=607>
+name  dtype    unit      class              mean                std                 min                  max        
+---- ------- ------- -------------- ------------------- ------------------- -------------------- -------------------
+ x_f float64           MaskedColumn             1.56101             2.88426             -29.6974             11.9164
+ A_f float64 solMass MaskedQuantity 1.30513e-09 solMass 8.34887e-09 solMass -1.41404e-07 solMass 6.43452e-08 solMass
+None
+\end{verbatim}
+
+scatter of x2 and A
+
+\subsubsection{Compare the methods}
+\label{sec:org31f509c}
+
+\begin{center}
+\includegraphics[width=.9\linewidth]{figure/x-hist.png}
+\end{center}
+
+\begin{verbatim}
+<QTable length=607>
+name  dtype     class       mean    std     min      max   n_bad
+---- ------- ------------ ------- ------- -------- ------- -----
+ x_f float64 MaskedColumn 1.56101 2.88426 -29.6974 11.9164     0
+ x_n float64       Column 1.66518 2.91771 -29.6974 11.9164     1
+None
 \end{verbatim}
@@
 \begin{center}
-\includegraphics[width=.9\linewidth]{./graphs/x-A_3.png}
+\includegraphics[width=.9\linewidth]{figure/x-scatter.png}
 \end{center}
 
-\subsection{Constant \(\tau\)}
-\label{sec:org3e5bf87}
-Assuming for an constant \(\tau=3.5\) Gyr, we cannot use the same \(\overline{SFR}\) and ratio. Using the equations\textasciitilde{}(\Ref{eq:av_SFR M*}) and (\Ref{eq:ratio})
+Since they are both pretty much the same, we can assume that the more compact is better, ie fsolve.
 
-$$
-    \frac{\overline{SFR_{del}}}{SFR_{0,del}}=\frac{e^x-x-1}{x^2}\Leftrightarrow \frac{e^x-x-1}{x}=\frac{\zeta M_*}{SFR\cdot\tau}
-$$
+\subsubsection{Hist of A}
+\label{sec:orgb536f22}
 
-and \(x\) and \(A_{del}\) can be calcuated numerically.
+\begin{center}
+\includegraphics[width=.9\linewidth]{figure/A-hist.png}
+\end{center}
+
+\subsection{Calculating the t\textsubscript{sf} and \(\tau\) of the galaxies}
+\label{sec:org06b21d0}
 
 \begin{verbatim}
-                  A           tsf         x_i
-count  5.500000e+02  5.500000e+02  550.000000
-mean   4.192335e+09  8.727310e+09    2.493517
-std    1.432226e+10  3.097809e+09    0.885088
-min    9.870027e+06  2.323533e+09    0.663867
-25%    6.466448e+07  6.441713e+09    1.840489
-50%    2.234694e+08  8.383763e+09    2.395361
-75%    1.034826e+09  1.077179e+10    3.077654
-max    1.057699e+11  1.796414e+10    5.132611
+/home/dp/.local/lib/python3.10/site-packages/astropy/units/quantity.py:671: RuntimeWarning: overflow encountered in divide
+name = tau
+dtype = float64
+unit = Gyr
+class = Quantity
+mean = 6.30189 Gyr
+std = 77.365 Gyr
+min = -1036.91 Gyr
+max = 988.964 Gyr
+n_bad = 0
+length = 607
+None
 \end{verbatim}
 
-\begin{center}
-\includegraphics[width=.9\linewidth]{./graphs/x-A_tau.png}
-\end{center}
-
-Comparing the two different results for x, we see that the \(x_i\) from the second solution has a lower \(\sigma\)
 \begin{verbatim}
-                x         x_i
-count  550.000000  550.000000
-mean     1.762321    2.493517
-std      1.388768    0.885088
-min      0.000559    0.663867
-25%      0.558532    1.840489
-50%      1.513139    2.395361
-75%      2.789068    3.077654
-max      5.686198    5.132611
+<QTable length=607>
+name  dtype    unit   class   n_bad
+---- ------- ------- -------- -----
+ A_n float64 solMass Quantity     1
+ x_n float64           Column     1
+None
 \end{verbatim}
 
-The \(x_i\) results are more inline with the expected values from Kroupa et al. 2020 \(2.7<x<3.4\)
-\begin{center}
-\includegraphics[width=.9\linewidth]{./graphs/x-x_i.png}
-\end{center}
+\url{None}
 
-\begin{center}
-\includegraphics[width=.9\linewidth]{./graphs/A-A_del.png}
-\end{center}
+\subsubsection{{\bfseries\sffamily IDEA} Check to see if the almost inf points make any sense}
+\label{sec:orgbb07f9e}
 
-The correlation between the 2 different \(x\) is good with an R-squared of 94\%
+\subsection{{\bfseries\sffamily TODO} The gas depletion timescale \(\tau\)\textsubscript{g}}
+\label{sec:orgae7d362}
+What is the gas depletion timescale?
 
-\subsubsection{{\bfseries\sffamily TODO} DO sigma clipping for x to see if the x's are in agreement with the theoritical values}
-\label{sec:org33fabf5}
+\subsection{{\bfseries\sffamily TODO} The theoretical SFR vs the observed}
+\label{sec:org0f23e0c}
 
-\section{Mass relations}
-\label{sec:orgcb5272f}
+\section{{\bfseries\sffamily PROJ} The relations of the Masses}
+\label{sec:org39c52db}
+Since the aim of the paper is to find the SFR lets first understand and calculate the masses of the galaxies and see if we can find any relation with the SFR.
 
-The below graphs show the correlation that the masses of the galaxies have. To consider a correlation good we need a \(R^2>70\%\)
+Pairplot with StellarMass, MHI, SFR\textsubscript{0} and av\textsubscript{SFR}, M26
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=.9\linewidth]{./graphs/logStellarMass-logM26.png}
-\caption{\label{Stellar Mass - Mass within Holmberg radius}Stellar Mass - Mass within Holmberg radius: \(R^2=0.8\)}
-\end{figure}
+\section{{\bfseries\sffamily TODO} The relations of the Data}
+\label{sec:org0f3fcd7}
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=.9\linewidth]{./graphs/logMg-logM26.png}
-\caption{\label{Gas Mass - Mass within Holmberg radius}Gas Mass - Mass within Holmberg radius: \(R^2=0.77\)}
-\end{figure}
+\subsection{{\bfseries\sffamily TODO} Luminosity and Masses}
+\label{sec:org752f14a}
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=.9\linewidth]{./graphs/logMg-logM26.png}
-\caption{\label{Gas Mass - Mass within Holmberg radius}Gas Mass/Hydrogen Mass - Mass within Holmberg radius: \(R^2=0.77\)}
-\end{figure}, \begin{figure}[htbp]
-\centering
-\includegraphics[width=.9\linewidth]{./graphs/logMHI-logM26.png}
-\caption{\label{Gas Mass - Mass within Holmberg radius}Gas Mass/Hydrogen Mass - Mass within Holmberg radius: \(R^2=0.77\)}
-\end{figure}
+\subsection{{\bfseries\sffamily TODO} Variations in Star Formation Rates across the different masses}
+\label{sec:org862160e}
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=.9\linewidth]{./graphs/logStellarMass-logMt.png}
-\caption{\label{Total Mass - Stellar Mass}Total Mass - Stellar Mass: \(R^2=0.93\)}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=.9\linewidth]{./graphs/logMg-logMt.png}
-\caption{\label{Total Mass - Gas Mass}Total Mass - Gas Mass/Hydrogen Mass: \(R^2=0.87\)}
-\end{figure},\begin{figure}[htbp]
-\centering
-\includegraphics[width=.9\linewidth]{./graphs/logMHI-logMt.png}
-\caption{\label{Total Mass - Gas Mass}Total Mass - Gas Mass/Hydrogen Mass: \(R^2=0.87\)}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=.9\linewidth]{./graphs/logM26-logMt.png}
-\caption{\label{Total Mass - Mass within Holmberg radius}Total Mass - Mass within Holmberg radius: \(R^2=0.85\)}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=.9\linewidth]{./graphs/M-MHI-M26.png}
-\caption{\label{Stellar Mass - Mass within Holmberg radius - Hydrogen Mass - Total Mass}Stellar Mass - Mass within Holmberg radius - Hydrogen Mass - Total Mass}
-\end{figure}
-
-\section{Calculate the gas depletion timescale \(\tau_g\)}
-\label{sec:orgf5cea8c}
-
-The gas depletion timescale τg measures the time taken by a galaxy to exhaust its gas content Mg given the current SFR (Pflamm-Altenburg \& Kroupa 2009).
-$$
-\tau_g=\frac{M_g}{\dot{M_*}}=\frac{M_g}{SFR}
-$$
+\section{{\bfseries\sffamily TODO} Filling the Catalogue}
+\label{sec:orgd74b51d}
 \end{document}

### 2024-07-14 notes/list.py
Deleted multi mags and fixed units

@@ -9,7 +9,9 @@ from astropy.visualization import quantity_support
 import glob
 import os
 
-# Function to clean the data before reading into a Table
+# Set non-interactive backend for matplotlib
+plt.switch_backend('Agg')
+
 def clean_file(file_path):
     with open(file_path, 'r') as file:
         lines = file.readlines()
@@ -63,7 +65,7 @@ def scatter_and_r2(table1, table2, col1_name, col2_name, title):
     plt.savefig(title)
     plt.close()
 
-# Modify magnitudes table
+### Modify magnitudes table
 magn.remove_column("r_mag")
 magn["Filter"][magn["Filter"] == "FU"] = "FUV"
 
@@ -94,6 +96,7 @@ for dcolor_item in dcolor[1:]:
 param.rename_column("a26", "A26")
 param.rename_column("AB", "AB_int")
 
+### Comparisons
 # Compare and remove columns in cat and kin tables
 scatter_and_r2(cat, kin, "W50", "W50", "cat vs kin W50")
 if len(cat["W50"]) > len(kin["W50"]):
@@ -164,6 +167,66 @@ for col in ['RAh', 'RAm', 'RAs', 'DE-', 'DEd', 'DEm', 'DEs']:
 # Reorder columns
 column_order = ["Name", "Coordinates"] + [col for col in dt.colnames if col not in ["Name", "Coordinates"]]
 dt = dt[column_order]
+
+# create a list of pairs of colums to be plotted
+pairs = [('FUVmag','mag_FUV'),
+         ('Bmag','mag_B'),
+         ('Hamag', 'mag_Ha'),
+         ('Kmag','mag_Ks'),
+         ('Bmag', 'BMag'),
+         ("21mag", "mag_HI"),
+         ('AB','AB_int')
+         ]
+
+# Create plots for each pair of columns
+for pair in pairs:
+    col1, col2 = pair
+    plt.figure(figsize=(8, 6))
+    plt.scatter(dt[col1], dt[col2])
+    plt.xlabel(col1)
+    plt.ylabel(col2)
+    plt.title(f'{col1} vs {col2}')
+    plt.grid(True)
+    plt.savefig(f'{col1} vs {col2}')
+    plt.close()
+
+pairs.remove(('Bmag', 'BMag'))
+pairs.remove(('AB', 'AB_int'))
+
+
+for pair in pairs:
+    col1, col2 = pair
+    mask1 = dt[col1].mask.sum()
[…]

### 2024-07-14 notes/list.py
check_flags+final messages

@@ -193,6 +193,7 @@ for pair in pairs:
 pairs.remove(('Bmag', 'BMag'))
 pairs.remove(('AB', 'AB_int'))
 
+all_removed = []
 
 for pair in pairs:
     col1, col2 = pair
@@ -214,6 +215,8 @@ for pair in pairs:
         dt.remove_column(f"e_{removed}")
     if f"f_{removed}" in dt.colnames:
         dt.remove_column(f"f_{removed}")
+    #List of all removed columns
+    all_removed.append(removed)
         
    
 # fix the units
@@ -226,7 +229,60 @@ dt["Thetaj"].unit = ""
 dt["SFRFUV"].unit = u.Msun / u.yr
 dt["SFRHa"].unit = u.Msun / u.yr
 
-print(dt.info())
+# Function to check flag consistency
+def check_flags(table):
+    """
+    Check for consistency between masked values and flag columns in an Astropy Table.
 
+    This function iterates over the columns of the provided table and checks if the 
+    masked values in the main columns are consistent with the corresponding flag columns 
+    (columns starting with 'l_' or 'f_'). If inconsistencies are found, it records the 
+    positions of these inconsistencies.
+
+    Parameters
+    ----------
+    table : astropy.table.Table
+        The table to be checked for flag consistency. The table should contain columns 
+        with names starting with 'l_' or 'f_' which are used as flag indicators for the 
+        main columns.
+
+    Returns
+    -------
+    flag_errors : dict
+        A dictionary where the keys are the names of the flag columns with inconsistencies, 
+        and the values are arrays of positions (indices) where the inconsistencies occur.
+        If no inconsistencies are found, the dictionary will be empty.
+    """
+    flag_errors = {}
+    for colname in table.colnames:
+        if colname.startswith('l_') or colname.startswith('f_'):
+            main_col = colname[2:]  # Remove 'l_' or 'f_' prefix to get the main column name
+            if main_col in table.colnames:
+                mask = table[main_col].mask
+                flags = table[colname]
+                
+                # Check if the flag column has non-empty entries
+                flag_positions = flags != ''  # or you can check for np.nan, or other specific flag indicators
+
+                if not np.all(mask == flag_positions):
+                    flag_errors[colname] = np.where(mask != flag_positions)[0]
+
+    return flag_errors
+# Check the flags
+flag_errors = check_flags(table)
+
+# Report the results
+if flag_errors:
+    for col, error_positions in flag_errors.items():
[…]

### 2024-07-14 notes/list.py
function compare_and_remove for readability

@@ -193,15 +193,34 @@ for pair in pairs:
 pairs.remove(('Bmag', 'BMag'))
 pairs.remove(('AB', 'AB_int'))
 
-all_removed = []
 
-for pair in pairs:
-    col1, col2 = pair
+def compare_and_remove(dt, col1, col2):
+    """
+    Compare two columns in an Astropy Table and remove the one with more masked (NaN) values.
+
+    This function compares the number of masked (NaN) values in two specified columns of an Astropy Table.
+    It removes the column with the greater number of masked values. Additionally, it removes any associated
+    flag columns (columns starting with 'l_', 'e_', or 'f_') corresponding to the removed column.
+
+    Parameters
+    ----------
+    dt : astropy.table.Table
+        The table containing the columns to be compared and potentially removed.
+    col1 : str
+        The name of the first column to be compared.
+    col2 : str
+        The name of the second column to be compared.
+
+    Returns
+    -------
+    removed : str
+        The name of the column that was removed from the table.
+    """
     mask1 = dt[col1].mask.sum()
     mask2 = dt[col2].mask.sum()
     print(f'{col1}: {mask1} NaN', f'{col2}: {mask2} NaN')
-    if mask1>=mask2:
-        dt.remove_column(col1)        
+    if mask1 >= mask2:
+        dt.remove_column(col1)
         print(f'Removed {col1}')
         removed = col1
     else:
@@ -215,8 +234,15 @@ for pair in pairs:
         dt.remove_column(f"e_{removed}")
     if f"f_{removed}" in dt.colnames:
         dt.remove_column(f"f_{removed}")
+    return removed
+
+
+all_removed = []
+for pair in pairs:
+    col1, col2 = pair
+    compiled_removed = compare_and_remove(dt, col1, col2)
     #List of all removed columns
-    all_removed.append(removed)
+    all_removed.append(compiled_removed)
         
    
 # fix the units

### 2024-07-14 notes/list.py
summary for LCV list cleaning

@@ -154,6 +154,8 @@ dt["MHI"] = (10**dt["logMHI"])
 dt["MHI"].unit = u.Msun
 dt["MHI"].description = "Linear hydrogen mass"
 
+log_columns_to_linear = ["KLum", "M26", "MHI"]
+
 # Create SkyCoord objects for coordinates
 ra_str = [f"{hour}:{minute}:{second:.1f}" for hour, minute, second in zip(dt['RAh'], dt['RAm'], dt['RAs'])]
 dec_str = [f"{sign}{degree}:{minute}:{second:.1f}" for sign, degree, minute, second in zip(dt['DE-'], dt['DEd'], dt['DEm'], dt['DEs'])]
@@ -255,6 +257,8 @@ dt["Thetaj"].unit = ""
 dt["SFRFUV"].unit = u.Msun / u.yr
 dt["SFRHa"].unit = u.Msun / u.yr
 
+fixed_units = ["logKLum", "logM26", "logMHI", "Thetaj", "SFRFUV", "SFRHa"]
+
 # Function to check flag consistency
 def check_flags(table):
     """
@@ -304,10 +308,16 @@ if flag_errors:
 else:
     print("All flags are consistent with masked values.")
     
-print("\nThe masks are not the same as the flag columns in the input data.")
-
 print(dt.info())
-print("\nWe have removed:", all_removed)
+
+print("WHAT WE HAVE DONE:")
+print("\nFixed the coordinates to sky coordinates.")
+print("\nChanged the way table 3 was displayed, so we can compare it to the other tables.")
+print(f"\nWe converted the logarithmic values to linear scale:{log_columns_to_linear} ")
+print("\nWe have removed:", all_removed, "after comparison with other columns.")
+print(f"\nThe columns {fixed_units} are now in the correct units.")
+print("\nThe masks are not the same as the flag columns in the input data.")
+print("\nMerged all tables into one.")
 print("\nThe total number of columns in the final table is:", len(dt.colnames),"with number of rows:", len(dt))
 print("\nThe final table has been saved to '../tables/final_table.fits'.")
 # Save the final table to a FITS file

### 2024-07-14 tables/inner_join.sh
inner_join with stilts

@@ -1,0 +1,5 @@
+#!/bin/bash
+
+stilts tmatch2 in1=final_table.fits in2=HECATE_LCV.fits out=inner_join.fits\
+    join=1and2 matcher=sky3d\
+    values1="Coordinates.ra Coordinates.dec Dis" values2="RA DEC D" params=0.5 

### 2024-07-14 tables/hecate_lcv_join.sh
stilts D<11+joins

@@ -1,0 +1,13 @@
+#!/bin/bash
+
+#Keep only the LCV from Hecate
+stilts tpipe in=HECATE_v1.1.fits  cmd="select D<11" out=HECATE_LCV.fits
+
+#Outter join for each row of hecate
+stilts tmatch2 in1=final_table.fits in2=HECATE_LCV.fits out=inner_join.fits\
+    join=all2 matcher=sky3d\
+    values1="Coordinates.ra Coordinates.dec Dis" values2="RA DEC D" params=0.5 
+#Inner join
+stilts tmatch2 in1=final_table.fits in2=HECATE_LCV.fits out=inner_join.fits\
+    join=1and2 matcher=sky3d\
+    values1="Coordinates.ra Coordinates.dec Dis" values2="RA DEC D" params=0.5 

### 2024-07-14 tables/inner_join.sh

@@ -1,5 +1,0 @@
-#!/bin/bash
-
-stilts tmatch2 in1=final_table.fits in2=HECATE_LCV.fits out=inner_join.fits\
-    join=1and2 matcher=sky3d\
-    values1="Coordinates.ra Coordinates.dec Dis" values2="RA DEC D" params=0.5 

### 2024-07-14 pipeline.sh
pipeline script

@@ -1,0 +1,7 @@
+#!/bin/bash
+cd tables
+./delete_lines.sh
+cd ../notes
+/bin/python3 list.py
+cd ../tables
+./hecate_lcv_join.sh

### 2024-07-15 tables/hecate_lcv_join.sh
we are back

@@ -1,6 +1,7 @@
 #!/bin/bash
 
 #Keep only the LCV from Hecate
+
 stilts tpipe in=HECATE_v1.1.fits  cmd="select D<11" out=HECATE_LCV.fits
 
 #Outter join for each row of hecate

### 2024-07-15 downloads.sh
added downlods script

@@ -1,0 +1,4 @@
+#!/bin/bash
+
+cd ~/Documents/Research_paper_SFR/
+wget --no-check-certificate -r -nH --cut-dirs=2 --accept="*.dat" --reject="*8.dat" -e robots=off -U mozilla https://www.sao.ru/lv/lvgdb/tables/

### 2024-07-15 pipeline.sh

@@ -1,4 +1,6 @@
 #!/bin/bash
+
+./downloads.sh
 cd tables
 ./delete_lines.sh
 cd ../notes

### 2024-07-15 pipeline.sh
pipelines

@@ -2,7 +2,7 @@
 
 ./downloads.sh
 cd tables
-./delete_lines.sh
+./delete_lines.sh lvg_*
 cd ../notes
 /bin/python3 list.py
 cd ../tables

### 2024-07-16 compare/compare.qmd
first compare draft

---
title: "Untitled"
format: html
bibliography: ../My_Library.bib
execute: 
  echo: true
  eval: true
---

# The data

In this script we will compare out 2 catalogs @kovlakasHeraklionExtragalacticCatalogue2021 and [@karachentsevUPDATEDNEARBYGALAXY2013, @karachentsevSTARFORMATIONPROPERTIES2013a]

-   The data have been joined based on their position in the sky (Ra, Dec, Distance).
-   We use TOPCAT to create two joins, an inner and an outer join
-   We will use the inner join for 1-1 comparisons
-   If we see that the data are similar we can use the outer join

```{python}
import numpy as np
import matplotlib.pyplot as plt
from sklearn.metrics import r2_score
from astropy.io import fits
from astropy.coordinates import SkyCoord
from astropy.table import Table, join, QTable
import astropy.units as u
from astropy.visualization import quantity_support
import glob
import os

hdul = fits.open("../tables/inner_join.fits")
print(hdul[1])
```

```{python}
print("jell
```

### 2024-07-16 notes/list.py
Split the Coords+ecsv for TOPCAT descriptions

@@ -2,7 +2,7 @@
 import numpy as np
 import matplotlib.pyplot as plt
 from sklearn.metrics import r2_score
-from astropy.io import ascii
+from astropy.io import ascii, fits
 from astropy.coordinates import SkyCoord
 from astropy.table import Table, join, QTable
 import astropy.units as u
@@ -162,14 +162,19 @@ log_columns_to_linear = ["KLum", "M26", "MHI"]
 ra_str = [f"{hour}:{minute}:{second:.1f}" for hour, minute, second in zip(dt['RAh'], dt['RAm'], dt['RAs'])]
 dec_str = [f"{sign}{degree}:{minute}:{second:.1f}" for sign, degree, minute, second in zip(dt['DE-'], dt['DEd'], dt['DEm'], dt['DEs'])]
 
-dt['Coordinates'] = SkyCoord(ra_str, dec_str, obstime="J2000", unit=(u.hourangle, u.deg))
+dt['Coordinates'] = SkyCoord(ra_str, dec_str, obstime="J2000", unit=(u.hourangle, u.deg))# make it 2 columns RA and DEC
+dt["Ra"] = dt["Coordinates"].ra
+dt["Ra"].description = "Right Ascension"
+dt["Dec"] = dt["Coordinates"].dec
+dt["Dec"].description = "Declination"
+dt.remove_column("Coordinates")
 
 # Remove original coordinate columns
 for col in ['RAh', 'RAm', 'RAs', 'DE-', 'DEd', 'DEm', 'DEs']:
     dt.remove_column(col)
 
 # Reorder columns
-column_order = ["Name", "Coordinates"] + [col for col in dt.colnames if col not in ["Name", "Coordinates"]]
+column_order = ["Name", "Ra", "Dec"] + [col for col in dt.colnames if col not in ["Name", "Ra", "Dec"]]
 dt = dt[column_order]
 
 # create a list of pairs of colums to be plotted
@@ -322,6 +327,6 @@ print(f"\nThe columns {fixed_units} are now in the correct units.")
 print("\nThe masks are not the same as the flag columns in the input data.")
 print("\nMerged all tables into one.")
 print("\nThe total number of columns in the final table is:", len(dt.colnames),"with number of rows:", len(dt))
-print("\nThe final table has been saved to '../tables/final_table.fits'.")
+print("\nThe final table has been saved to '../tables/final_table.ecsv'.")
 # Save the final table to a FITS file
[…]

### 2024-07-16 tables/hecate_lcv_join.sh

@@ -5,10 +5,10 @@
 stilts tpipe in=HECATE_v1.1.fits  cmd="select D<11" out=HECATE_LCV.fits
 
 #Outter join for each row of hecate
-stilts tmatch2 in1=final_table.fits in2=HECATE_LCV.fits out=inner_join.fits\
+stilts tmatch2 in1=final_table.ecsv in2=HECATE_LCV.fits out=inner_join.fits\
     join=all2 matcher=sky3d\
-    values1="Coordinates.ra Coordinates.dec Dis" values2="RA DEC D" params=0.5 
+    values1="Ra Dec Dis" values2="RA DEC D" params=0.5 
 #Inner join
-stilts tmatch2 in1=final_table.fits in2=HECATE_LCV.fits out=inner_join.fits\
+stilts tmatch2 in1=final_table.ecsv in2=HECATE_LCV.fits out=inner_join.fits\
     join=1and2 matcher=sky3d\
-    values1="Coordinates.ra Coordinates.dec Dis" values2="RA DEC D" params=0.5 
+    values1="Ra Dec Dis" values2="RA DEC D" params=0.5 

### 2024-07-16 notes/list.py
added file_path to save file

@@ -317,6 +317,7 @@ else:
     
 print("\nThe masks are not the same as the flag columns in the input data.")
 
+file_path = "../tables/final_table.ecsv"
 print(dt.info())
 print("WHAT WE HAVE DONE:")
 print("\nFixed the coordinates to sky coordinates.")
@@ -327,6 +328,6 @@ print(f"\nThe columns {fixed_units} are now in the correct units.")
 print("\nThe masks are not the same as the flag columns in the input data.")
 print("\nMerged all tables into one.")
 print("\nThe total number of columns in the final table is:", len(dt.colnames),"with number of rows:", len(dt))
-print("\nThe final table has been saved to '../tables/final_table.ecsv'.")
+print(f"\nThe final table has been saved to {file_path}.")
 # Save the final table to a FITS file
-ascii.write(dt, "../tables/final_table.ecsv", format = "ecsv", overwrite=True)
+ascii.write(dt, file_path, format = "ecsv", overwrite=True)

### 2024-07-17 tables/hecate_lcv_join.sh
changed distance error to 0.2 Mpc

@@ -7,8 +7,8 @@ stilts tpipe in=HECATE_v1.1.fits  cmd="select D<11" out=HECATE_LCV.fits
 #Outter join for each row of hecate
 stilts tmatch2 in1=final_table.ecsv in2=HECATE_LCV.fits out=inner_join.fits\
     join=all2 matcher=sky3d\
-    values1="Ra Dec Dis" values2="RA DEC D" params=0.5 
+    values1="Ra Dec Dis" values2="RA DEC D" params=0.2 
 #Inner join
 stilts tmatch2 in1=final_table.ecsv in2=HECATE_LCV.fits out=inner_join.fits\
     join=1and2 matcher=sky3d\
-    values1="Ra Dec Dis" values2="RA DEC D" params=0.5 
+    values1="Ra Dec Dis" values2="RA DEC D" params=0.2 

### 2024-07-17 compare/compare.qmd
fits->ecsv for simplicity

@@
 from sklearn.metrics import r2_score
-from astropy.io import fits
+from astropy.io import ascii
 from astropy.coordinates import SkyCoord
@@
 
-hdul = fits.open("../tables/inner_join.fits")
-print(hdul[1])
+dt = QTable(ascii.read("../tables/inner_join.ecsv"), masked=True)
+dt.info()
 ```
@@
 ```{python}
-print("jell
 ```

### 2024-07-17 tables/hecate_lcv_join.sh

@@ -5,10 +5,10 @@
 stilts tpipe in=HECATE_v1.1.fits  cmd="select D<11" out=HECATE_LCV.fits
 
 #Outter join for each row of hecate
-stilts tmatch2 in1=final_table.ecsv in2=HECATE_LCV.fits out=inner_join.fits\
+stilts tmatch2 in1=final_table.ecsv in2=HECATE_LCV.fits out=outer_join.ecsv\
     join=all2 matcher=sky3d\
     values1="Ra Dec Dis" values2="RA DEC D" params=0.2 
 #Inner join
-stilts tmatch2 in1=final_table.ecsv in2=HECATE_LCV.fits out=inner_join.fits\
+stilts tmatch2 in1=final_table.ecsv in2=HECATE_LCV.fits out=inner_join.ecsv\
     join=1and2 matcher=sky3d\
     values1="Ra Dec Dis" values2="RA DEC D" params=0.2 

### 2024-07-17 compare/compare.qmd
added data tabs

@@
 ---
-title: "Untitled"
+title: "Comparison of Catalogs"
 format: html
@@
 
-```{python}
-```
+The data we can compare are:
+
+::: panel-tabset
+## Coordinates
+
+| LCV   | HECATE | Description     |
+|-------|--------|-----------------|
+| Ra_1  | RA_2   | Right Ascension |
+| Dec_1 | DEC_2  | Declination     |
+| Dis   | D      | Distance        |
+
+: Coord
+
+## Velocities
+
+| LCV               | HECATE                | Description                             |
+|-------------------|--------------------|---------------------------------|
+| W50 (with errors) |                       | H I line with at 50% level from maximum |
+| RVel              |                       | Heliocentric radial velocity            |
+| Vm                |                       | Amplitude of rotational velocity        |
+| VLG               | V/V_VIR (with errors) | Radial velocity                         |
+| cz (with errors)  | V (with errors)       | Heliocentric velocity                   |
+
+: Vel
+
+## Luminosities
+
+| LCV     | HECATE | Description |
+|---------|--------|-------------|
+| logKLum | logL_K |             |
+|         |        |             |
+|         |        |             |
+
+: Lum
+
+## Magnitudes
+
+| LCV                 | HECATE | Description |
+|---------------------|--------|-------------|
+| mag_B (with errors) |        |             |
+| mag_FUV             |        |             |
+|                     |        |             |
+
+: Mag
+
+## SFR
+
+| LCV    | HECATE     | Description                                                      |
+|---------------|---------------|-------------------------------------------|
+|        | logSFR_TIR | Decimal logarithm of the total-infrared SFR estimate \[Msol/yr\] |
+|        | logSFR_FIR | Decimal logarithm of the far-infrared SFR estimate \[Msol/yr\]   |
+|        | logSFR_60u | Decimal logarithm of the 60um SFR estimate \[Msol/yr\]           |
+|        | logSFR_12u | Decimal logarithm of the 12um SFR estimate \[Msol/yr\]           |
+|        | logSFR_22u | Decimal logarithm of the 22um SFR estimate \[Msol/yr\]           |
+|        | logSFR_HEC | Decimal logarithm of the homogenised SFR estimate \[Msol/yr\]    |
+|        | logSFR_GSW | Decimal logarithm of the SFR in GSWLC-2 \[Msol/yr\]              |
+| SFRFUV |            | FUV derived integral star formation rate                         |
+| SFRHa  |            | H{alpha} derived integral star formation rate                    |
+
+## Masses
+
+| LCV            | HECATE   | Description                                               |
+|----------------|----------------|----------------------------------------|
+| logM26         |          | Log mass within Holmberg radius                           |
+| logMHI         |          | Log mass within Holmberg radius                           |
+|                | logM_HEC | Decimal logarithm of the stellar mass \[Msol\]            |
+|                | logM_GSW | Decimal logarithm of the stellar mass in GSWLC-2 \[Msol\] |
+| logStellarMass |          | Stellar Mass from M\*/L=0.6                               |
+:::

### 2024-07-17 compare/compare.qmd
Morph+Geom, Abs tabs

--- 2024-07-17 compare/compare.qmd
@@
 ---
-title: "Untitled"
+title: "Comparison of Catalogs"
 format: html
+toc: true
+toc-depth: 2
+theme: minti
 bibliography: ../My_Library.bib
@@
 dt = QTable(ascii.read("../tables/inner_join.ecsv"), masked=True)
-dt.info()
 ```
 
-```{python}
-```
+The dataset we are going to use consists of `{python} len(dt)` galaxies and `{python} len(dt.colnames)`
+
+## Comparable data
+
+::: panel-tabset
+## Coordinates
+
+| LCV   | HECATE | Description     |
+|-------|--------|-----------------|
+| Ra_1  | RA_2   | Right Ascension |
+| Dec_1 | DEC_2  | Declination     |
+| Dis   | D      | Distance        |
+
+## Velocities
+
+| LCV               | HECATE                | Description                             |
+|-------------------|--------------------|---------------------------------|
+| W50 (with errors) |                       | H I line with at 50% level from maximum |
+| RVel              | V (with errors)       | Heliocentric radial velocity            |
+| Vm                |                       | Amplitude of rotational velocity        |
+| VLG               | V/V_VIR (with errors) | Radial velocity                         |
+| cz (with errors)  |                       | Heliocentric velocity                   |
+
+## Morphology and Geometry
+
+| LCV           | HECATE               | Description                                               |
+|-----------------------|------------------------|-------------------------|
+| TType         | T (with errors)      | Numerical Hubble type following the de Vaucouleurs system |
+| inc           | I                    | Inclination (deg)                                         |
+| a26_1 (Major) | R1 (Semi-major axis) | angular diameter (arcmin)                                 |
+
+## Luminosities
+
+| LCV     | HECATE | Description |
+|---------|--------|-------------|
+| logKLum | logL_K |             |
+|         |        |             |
+|         |        |             |
+
+## Magnitudes
+
+| LCV                 | HECATE | Description |
+|---------------------|--------|-------------|
+| mag_B (with errors) |        |             |
+| mag_FUV             |        |             |
+|                     |        |             |
+
+## Absorbsion
+
+| LCV    | HECATE | Description                          |
+|--------|--------|--------------------------------------|
+| AB     |        | Galactic extinction in B band        |
+| AB_int |        | Internal B band extinction           |
+| AG     |        | Galactic absorption on B-band (mag)  |
+| AI     |        | Intrinsic absorption on B-band (mag) |
+
+## SFR
+
+| LCV    | HECATE     | Description                                                      |
+|--------------------|--------------------|--------------------------------|
+|        | logSFR_TIR | Decimal logarithm of the total-infrared SFR estimate \[Msol/yr\] |
+|        | logSFR_FIR | Decimal logarithm of the far-infrared SFR estimate \[Msol/yr\]   |
+|        | logSFR_60u | Decimal logarithm of the 60um SFR estimate \[Msol/yr\]           |
+|        | logSFR_12u | Decimal logarithm of the 12um SFR estimate \[Msol/yr\]           |
+|        | logSFR_22u | Decimal logarithm of the 22um SFR estimate \[Msol/yr\]           |
+|        | logSFR_HEC | Decimal logarithm of the homogenised SFR estimate \[Msol/yr\]    |
+|        | logSFR_GSW | Decimal logarithm of the SFR in GSWLC-2 \[Msol/yr\]              |
+| SFRFUV |            | FUV derived integral star formation rate                         |
+| SFRHa  |            | H{alpha} derived integral star formation rate                    |
+
+## Masses
+
+| LCV            | HECATE   | Description                                               |
+|--------------------|--------------------|--------------------------------|
+| logM26         |          | Log mass within Holmberg radius                           |
+| logMHI         |          | Log mass within Holmberg radius                           |
+|                | logM_HEC | Decimal logarithm of the stellar mass \[Msol\]            |
+|                | logM_GSW | Decimal logarithm of the stellar mass in GSWLC-2 \[Msol\] |
+| logStellarMass |          | Stellar Mass from M\*/L=0.6                               |
+:::

### 2024-07-18 compare/compare.qmd
func compare+scatter

--- 2024-07-17 compare/compare.qmd
@@
 from astropy.visualization import quantity_support
+#quantity_support()
+from astropy.modeling import models, fitting
+from scipy.stats import pearsonr
 import glob
 import os
+plt.style.use('ggplot')
 
 dt = QTable(ascii.read("../tables/inner_join.ecsv"), masked=True)
-dt.info()
 ```
 
+The dataset we are going to use consists of `{python} len(dt)` galaxies and `{python} len(dt.colnames)`
+
+# How are we going to compare the data?
+
+## Scatter plots and $R^2$ calculation
+
+1.  [$R^2$]{.underline}: Measures the proportion of variance explained by the linear model.
+2.  [Slope of the Fitted Line]{.underline}: Should be close to 1 for a 1-1 correlation.
+
 ```{python}
+def compare_data(x, y):
+    """
+    Performs a linear comparison between two datasets.
+
+    This function fits a linear model to the data, calculates the slope and intercept of the fitted line,
+    and computes the R-squared value and Pearson correlation coefficient to assess the fit quality.
+
+    Parameters:
+    - x (array-like): The independent variable data.
+    - y (array-like): The dependent variable data.
+
+    Returns:
+    tuple: A tuple containing the following elements:
+        - slope (float): The slope of the fitted linear model.
+        - intercept (float): The intercept of the fitted linear model.
+        - r2 (float): The R-squared value, indicating the proportion of variance explained by the linear model.
+        - corr (float): The Pearson correlation coefficient, measuring the linear correlation between x and y.
+    """
+    x_data = np.ma.array(x.value, mask=np.isnan(x.value))
+    y_data =  np.ma.array(y.value, mask=np.isnan(y.value))
+    # initialize a linear fitter
+    fit = fitting.LinearLSQFitter()
+
+    # initialize a linear model
+    line_init = models.Linear1D()
+
+    # fit the data with the fitter
+    fitted_line = fit(line_init, x_data, y_data)
+    slope = fitted_line.slope.value
+    intercept = fitted_line.intercept.value
+
+    # Predict values using the fitted model
+    y_pred = fitted_line(x_data)
+
+    # Calculate R-squared
+    r2 = r2_score(y_data, y_pred)
+
+    # Calculate Pearson correlation coefficient
+    corr, _ = pearsonr(x_data, y_data)
+
+    return slope, intercept, r2, corr
+
+def scatter_plot(x, y, xerr =0, yerr = 0):
+    """
+    Generates a scatter plot of two datasets with optional error bars, fits a linear model to the data, 
+    and displays the fitted line on the plot.
+
+    Parameters:
+    - x (array-like with units): Independent variable data.
+    - y (array-like with units): Dependent variable data.
+    xerr (array-like, optional): Error in the independent variable data. Default is 0.
+    yerr (array-like, optional): Error in the dependent variable data. Default is 0.
+
+    Returns:
+    None. The function displays a scatter plot with a fitted linear model.
+    """
+    # Convert data to masked arrays, masking NaN values
+    x_data = np.ma.array(x.value, mask=np.isnan(x.value))
+    y_data =  np.ma.array(y.value, mask=np.isnan(y.value))
+
+    # Perform linear comparison between the datasets
+    c, m, r2, corr = compare_data(x, y)
+
+    # Plot the data with error bars
+    # errorbar -> needs np.ma -> no units
+    plt.errorbar(x_data, y_data, xerr, yerr, alpha = 0.3, c = "blue", label = "Data", fmt=".k")
+
+    # Plot the fitted line with unit support
+    plt.plot(x, c*x + m*x.unit, c = "red", label = "Fit")
+
+    # Set plot labels
+    plt.xlabel(f"LCV, {x.info.name} [{x.unit}]")
+    plt.ylabel(f"HECATE, {y.info.name} [{y.unit}]")
+
+    # Display legend
+    plt.legend()
+
+    # Show the plot
+    plt.show()
 ```
+
+-   Histograms
+
+-   Deviation
+
+# Comparable data
+
+::: panel-tabset
+## Coordinates
+
+|  LCV  | HECATE |   Description   | Linear Correlation |
+|:-----:|:------:|:---------------:|:------------------:|
+| Ra_1  |  RA_2  | Right Ascension |                    |
+| Dec_1 | DEC_2  |   Declination   |                    |
+|  Dis  |   D    |    Distance     |                    |
+
+## Velocities
+
+|        LCV        |        HECATE         |               Description               | Linear Correlation |
+|:----------------:|:----------------:|:-----------------:|:----------------:|
+| W50 (with errors) |                       | H I line with at 50% level from maximum |                    |
+|       RVel        |    V (with errors)    |      Heliocentric radial velocity       |                    |
+|        Vm         |                       |    Amplitude of rotational velocity     |                    |
+|        VLG        | V/V_VIR (with errors) |             Radial velocity             |                    |
+| cz (with errors)  |                       |          Heliocentric velocity          |                    |
+
+## Morphology and Geometry
+
+|      LCV      |        HECATE        |                        Description                        | Linear Correlation |
+|:----------------:|:----------------:|:-----------------:|:----------------:|
+|     TType     |   T (with errors)    | Numerical Hubble type following the de Vaucouleurs system |                    |
+|      inc      |          I           |                     Inclination (deg)                     |                    |
+| a26_1 (Major) | R1 (Semi-major axis) |                 angular diameter (arcmin)                 |                    |
+
+## Luminosities
+
+|   LCV   | HECATE | Description |
+|:-------:|:------:|:-----------:|
+| logKLum | logL_K |             |
+|         |        |             |
+|         |        |             |
+
+## Magnitudes
+
+|         LCV         | HECATE | Description |
+|:-------------------:|:------:|:-----------:|
+| mag_B (with errors) |        |             |
+|       mag_FUV       |        |             |
+|                     |        |             |
+
+## Absorbsion
+
+|  LCV   | HECATE |                  Description                   |
+|:------:|:------:|:----------------------------------------------:|
+|   AB   |   AG   |    Galactic extinction/absorption in B band    |
+| AB_int |   AI   | Internal/Intrisic B band extinction/absorption |
+
+## SFR
+
+|  LCV   |   HECATE   |                           Description                            |
+|:------------------:|:------------------:|:------------------------------:|
+|        | logSFR_TIR | Decimal logarithm of the total-infrared SFR estimate \[Msol/yr\] |
+|        | logSFR_FIR |  Decimal logarithm of the far-infrared SFR estimate \[Msol/yr\]  |
+|        | logSFR_60u |      Decimal logarithm of the 60um SFR estimate \[Msol/yr\]      |
+|        | logSFR_12u |      Decimal logarithm of the 12um SFR estimate \[Msol/yr\]      |
+|        | logSFR_22u |      Decimal logarithm of the 22um SFR estimate \[Msol/yr\]      |
+|        | logSFR_HEC |  Decimal logarithm of the homogenised SFR estimate \[Msol/yr\]   |
+|        | logSFR_GSW |       Decimal logarithm of the SFR in GSWLC-2 \[Msol/yr\]        |
+| SFRFUV |            |             FUV derived integral star formation rate             |
+| SFRHa  |            |          H{alpha} derived integral star formation rate           |
+
+## Masses
+
+|      LCV       |  HECATE  |                        Description                        |
+|:------------------:|:------------------:|:------------------------------:|
+|     logM26     |          |              Log mass within Holmberg radius              |
+|     logMHI     |          |              Log mass within Holmberg radius              |
+|                | logM_HEC |      Decimal logarithm of the stellar mass \[Msol\]       |
+|                | logM_GSW | Decimal logarithm of the stellar mass in GSWLC-2 \[Msol\] |
+| logStellarMass |          |                Stellar Mass from M\*/L=0.6                |
+:::

### 2024-07-19 compare/compare.qmd
Fixed errordars in scatter

@@
 ```{python}
+#| echo: false
 import numpy as np
@@
 2.  [Slope of the Fitted Line]{.underline}: Should be close to 1 for a 1-1 correlation.
+3.  [Pearson Correlation $\rho$]{.underline}: Measures the strength and direction of the linear relationship between two variables, ranging from -1 to 1.
+
+In simple linear regression, $R^2$ is the square of the Pearson correlation coefficient $r$.
 
@@
 
+    # Remove NaN values
+    mask = ~np.isnan(y_data) & ~np.isnan(y_pred)
+    y_data_clean = y_data[mask]
+    y_pred_clean = y_pred[mask]
+    mask = ~np.isnan(x_data) 
+    x_data_clean = x_data[mask]
+
     # Calculate R-squared
-    r2 = r2_score(y_data, y_pred)
+    r2 = r2_score(y_data_clean, y_pred_clean)
 
     # Calculate Pearson correlation coefficient
-    corr, _ = pearsonr(x_data, y_data)
+    corr = np.sqrt(np.abs(r2))
 
     return slope, intercept, r2, corr
+```
 
-def scatter_plot(x, y, xerr =0, yerr = 0):
+4.
+[Scatter plots]{.underline}: Scatter plots are essential for visually assessing the relationship between two datasets, identifying correlations, trends, and outliers, and evaluating the fit of linear models.
+
+```{python}
+def scatter_plot(x, y, xerr = None, yerr = None):
     """
@@
 
+    # Handle default values for xerr and yerr
+    if xerr is None:
+        xerr_d = np.ma.zeros(len(x_data))
+    else:
+        xerr_d = np.ma.array(xerr.value, mask=np.isnan(xerr))
+    if yerr is None:
+        yerr_d = np.ma.zeros(len(y_data))
+    else:
+        yerr_d = np.ma.array(yerr.value, mask=np.isnan(yerr))
+
     # Perform linear comparison between the datasets
@@
     # errorbar -> needs np.ma -> no units
-    plt.errorbar(x_data, y_data, xerr, yerr, alpha = 0.3, c = "blue", label = "Data", fmt=".k")
+    plt.errorbar(x_data, y_data, xerr = xerr_d, yerr = yerr_d, alpha = 0.3, c = "blue", label = "Data", fmt=".")
 
     # Plot the fitted line with unit support
-    plt.plot(x, c*x + m*x.unit, c = "red", label = "Fit")
+    plt.plot(x, c*x + m*x.unit, c = "red", label = f"Fit: {y.info.name}$_H $= {c:.2f}$\cdot${x.info.name}$_L${m:+.2f}\n $R^2=$ {r2:.2f}")
 
@@
 
-|  LCV  | HECATE |   Description   | Linear Correlation |
-|:-----:|:------:|:---------------:|:------------------:|
-| Ra_1  |  RA_2  | Right Ascension |                    |
-| Dec_1 | DEC_2  |   Declination   |                    |
-|  Dis  |   D    |    Distance     |                    |
+```{python}
+#| echo: false
+ra_corr = round(compare_data(dt["Ra_1"],dt["RA_2"])[3],3)
+dec_corr = round(compare_data(dt["Dec_1"],dt["DEC_2"])[3],3)
+d_corr = round(compare_data(dt["Dis"],dt["D"])[3],3)
+```
+
+|  LCV  | HECATE |   Description   | Pearson Correlation \[-1,1\] |
+|:-----:|:------:|:---------------:|:----------------------------:|
+| Ra_1  |  RA_2  | Right Ascension |      `{python} ra_corr`      |
+| Dec_1 | DEC_2  |   Declination   |     `{python} dec_corr`      |
+|  Dis  |   D    |    Distance     |      `{python} d_corr`       |
+
+```{python}
+
+scatter_plot(dt["Ra_1"], dt["RA_2"]), scatter_plot(dt["Dec_1"], dt["DEC_2"]), scatter_plot(dt["Dis"], dt["D"])
+```
 
@@
 
+```{python}
+rvel_corr = round(compare_data(dt["RVel"],dt["V"])[3],3)
+rvel_corr_v = round(compare_data(dt["RVel"],dt["V_VIR"])[3],3)
+vlg_corr = round(compare_data(dt["VLG"],dt["V"])[3],3)
+vlg_corr_v = round(compare_data(dt["VLG"],dt["V_VIR"])[3],3)
+cz_corr = round(compare_data(dt["cz"],dt["V"])[3],3)
+cz_corr_v = round(compare_data(dt["cz"],dt["V_VIR"])[3],3)
+```
+
 |       LCV        |        HECATE         |         Description          |        Linear Correlation         |
-|:----------------:|:----------------:|:-----------------:|:----------------:|
-| W50 (with errors) |                       | H I line with at 50% level from maximum |                    |
-|       RVel        |    V (with errors)    |      Heliocentric radial velocity       |                    |
-|        Vm         |                       |    Amplitude of rotational velocity     |                    |
-|        VLG        | V/V_VIR (with errors) |             Radial velocity             |                    |
-| cz (with errors)  |                       |          Heliocentric velocity          |                    |
+|:----------------:|:------------------:|:----------------:|:----------------:|
+|       RVel       | V/V_VIR (with errors) | Heliocentric radial velocity | `{python} rvel_corr, rvel_corr_v` |
+|       VLG        | V/V_VIR (with errors) |       Radial velocity        |  `{python} vlg_corr, vlg_corr_v`  |
+| cz (with errors) | V/V_VIR (with errors) |    Heliocentric velocity     |   `{python} cz_corr, cz_corr_v`   |
+
+```{python}
+scatter_plot(dt["RVel"], dt["V"], yerr = dt["E_V"])
+```
 
@@
 
-|      LCV      |        HECATE        |                        Description                        | Linear Correlation |
-|:----------------:|:----------------:|:-----------------:|:----------------:|
-|     TType     |   T (with errors)    | Numerical Hubble type following the de Vaucouleurs system |                    |
-|      inc      |          I           |                     Inclination (deg)                     |                    |
-| a26_1 (Major) | R1 (Semi-major axis) |                 angular diameter (arcmin)                 |                    |
+```{python}
+#| echo: false
+
+ttype_corr = round(compare_data(dt["TType"], dt["T"])[3], 4)
+inc_corr = round(compare_data(dt["inc"], dt["I"])[3], 3)
+#a26_corr = round(compare_data(dt["a26_1"], dt["R1"])[3], 3)
+#it doesnt even compute
+```
+
+|      LCV      |        HECATE        |                        Description                        | Pearson Correlation \[-1,1\] |
+|:---------------:|:---------------:|:---------------------:|:---------------:|
+|     TType     |   T (with errors)    | Numerical Hubble type following the de Vaucouleurs system |    `{python} ttype_corr`     |
+|      inc      |          I           |                     Inclination (deg)                     |     `{python} inc_corr`      |
+| a26_1 (Major) | R1 (Semi-major axis) |                 angular diameter (arcmin)                 |              0               |
+
+As we can see we don't have any significant correlation between the data
+
+```{python}
+
+dt["TType"].info, dt["T"].info
+```
 

### 2024-07-19 compare/compare.qmd
added weights

@@
 1.  [$R^2$]{.underline}: Measures the proportion of variance explained by the linear model.
-2.  [Slope of the Fitted Line]{.underline}: Should be close to 1 for a 1-1 correlation.
-3.  [Pearson Correlation $\rho$]{.underline}: Measures the strength and direction of the linear relationship between two variables, ranging from -1 to 1.
+2.  [Slope of the Fitted Line]{.underline}: Should be close to 1 for a 1-1 correlation.[^1]
+3.  [Pearson Correlation $\rho$]{.underline}: Measures the strength and direction of the linear relationship between two variables, ranging from -1 to 1. [^2]
 
-In simple linear regression, $R^2$ is the square of the Pearson correlation coefficient $r$.
+[^1]: Fitting can be done using the uncertainties as weights. To get the standard weighting of 1/unc^2, assuming Gaussian errors, the weights to pass to the fitting are 1/unc.
+[^2]: In simple linear regression, $R^2$ is the square of the Pearson correlation coefficient $\rho$.
 
 ```{python}
-def compare_data(x, y):
+def compare_data(x, y, unc = None):
     """
@@
     - y (array-like): The dependent variable data.
+    - unc (array-like with units, optional): The uncertainties associated with the independent variable data. Default is None.
 
@@
     y_data =  np.ma.array(y.value, mask=np.isnan(y.value))
+    if unc is None:
+        w = None
+    else:
+        unc = np.ma.array(unc.value, mask=np.isnan(x.value))
+        w = 1/unc 
     # initialize a linear fitter
@@
     # fit the data with the fitter
-    fitted_line = fit(line_init, x_data, y_data)
+    fitted_line = fit(line_init, x_data, y_data, weights = w)
     slope = fitted_line.slope.value
@@
     - y (array-like with units): Dependent variable data.
-    xerr (array-like, optional): Error in the independent variable data. Default is 0.
-    yerr (array-like, optional): Error in the dependent variable data. Default is 0.
+    - xerr (array-like, optional): Error in the independent variable data. Default is 0.
+    - yerr (array-like, optional): Error in the dependent variable data. Default is 0.
 
@@
     if xerr is None:
-        xerr_d = np.ma.zeros(len(x_data))
+        xerr_d = 0
     else:
@@
     if yerr is None:
-        yerr_d = np.ma.zeros(len(y_data))
+        yerr_d = 0
     else:
@@
     # Perform linear comparison between the datasets
-    c, m, r2, corr = compare_data(x, y)
+    if yerr is not None:
+        unc = yerr
+    elif yerr is None and xerr is not None:
+        unc = xerr
+    else:
+        unc = None
+    c, m, r2, corr = compare_data(x, y, unc)
 
@@
 |       LCV        |        HECATE         |         Description          |        Linear Correlation         |
-|:----------------:|:------------------:|:----------------:|:----------------:|
+|:----------------:|:-----------------:|:----------------:|:----------------:|
 |       RVel       | V/V_VIR (with errors) | Heliocentric radial velocity | `{python} rvel_corr, rvel_corr_v` |
@@
 |      LCV      |        HECATE        |                        Description                        | Pearson Correlation \[-1,1\] |
-|:---------------:|:---------------:|:---------------------:|:---------------:|
+|:---------------:|:---------------:|:-------------------:|:---------------:|
 |     TType     |   T (with errors)    | Numerical Hubble type following the de Vaucouleurs system |    `{python} ttype_corr`     |

### 2024-07-19 compare/compare.qmd
if c=0 no plot + abs+lum

@@
 ```{python}
-def compare_data(x, y, unc = None):
+def compare_data(x, y, unc=None):
     """
@@
     """
+    try:
         x_data = np.ma.array(x.value, mask=np.isnan(x.value))
@@
             unc = np.ma.array(unc.value, mask=np.isnan(x.value))
-        w = 1/unc 
+            w = 1 / unc
         # initialize a linear fitter
@@
         # fit the data with the fitter
-    fitted_line = fit(line_init, x_data, y_data, weights = w)
+        fitted_line = fit(line_init, x_data, y_data, weights=w)
         slope = fitted_line.slope.value
@@
         return slope, intercept, r2, corr
+    except Exception:
+        return 0, 0, 0, 0
 ```
@@
     # Plot the fitted line with unit support
-    plt.plot(x, c*x + m*x.unit, c = "red", label = f"Fit: {y.info.name}$_H $= {c:.2f}$\cdot${x.info.name}$_L${m:+.2f}\n $R^2=$ {r2:.2f}")
+    if c!=0:
+        plt.plot(x, c*x.value+ m, c = "red", label = f"Fit: {y.info.name}$_H $= {c:.2f}$\cdot${x.info.name}$_L${m:+.2f}\n $R^2=$ {r2:.2f}")
 
@@
 ttype_corr = round(compare_data(dt["TType"], dt["T"])[3], 4)
-inc_corr = round(compare_data(dt["inc"], dt["I"])[3], 3)
-#a26_corr = round(compare_data(dt["a26_1"], dt["R1"])[3], 3)
-#it doesnt even compute
+inc_corr = round(compare_data(dt["inc"], dt["INCL"])[3], 3)
+a26_corr = round(compare_data(dt["a26_1"], dt["A26_1a"])[3], 3)
 ```
@@
 |     TType     |   T (with errors)    | Numerical Hubble type following the de Vaucouleurs system |    `{python} ttype_corr`     |
-|      inc      |          I           |                     Inclination (deg)                     |     `{python} inc_corr`      |
-| a26_1 (Major) | R1 (Semi-major axis) |                 angular diameter (arcmin)                 |              0               |
+|      inc      |          INCL           |                     Inclination (deg)                     |     `{python} inc_corr`      |
+| a26_1 (Major) | A26_1a (Semi-major axis) |                 angular diameter (arcmin)                 |              `{python} a26_corr`               |
 
-As we can see we don't have any significant correlation between the data
+As we can see we don't have any significant correlation between the Types of galaxies
 
@@
 
-dt["TType"].info, dt["T"].info
+scatter_plot(dt["TType"], dt["T"], yerr = dt["E_T"])
+scatter_plot(dt["inc"], dt["INCL"], yerr = dt["E_V"])
+scatter_plot(dt["a26_1"], dt["A26_1a"], yerr = dt["E_V"])
+
 ```
+
+**For the A26: In the LCV Catalog it is measured in deg, and in Hecate it is mesaured in kpc**
 
@@
 
-|   LCV   | HECATE | Description |
-|:-------:|:------:|:-----------:|
-| logKLum | logL_K |             |
-|         |        |             |
-|         |        |             |
+```{python}
+#| echo: false
+logKLum_corr = round(compare_data(dt["logKLum"], dt["logL_K"])[3], 3)
+```
+|   LCV   | HECATE | Description | Pearson Correlation \[-1,1\] |
+|:-------:|:------:|:-----------:|:----------------------------:|
+| logKLum | logL_K |             |      `{python} logKLum_corr` |
+
+```{python}
+scatter_plot(dt["logKLum"], dt["logL_K"])
+```
 
@@
 |:-------------------:|:------:|:-----------:|
-| mag_B (with errors) |        |             |
-|       mag_FUV       |        |             |
+| mag_B (with errors) |  BT (with errors)      |             |
+|       Kmag   |     K   | 2MASS band magnitude  (both)          |
 |                     |        |             |
-
 ## Absorbsion
 
-|  LCV   | HECATE |                  Description                   |
-|:------:|:------:|:----------------------------------------------:|
-|   AB   |   AG   |    Galactic extinction/absorption in B band    |
-| AB_int |   AI   | Internal/Intrisic B band extinction/absorption |
-
+```{python}
+#| echo: false
+ab_corr = round(compare_data(dt["AB"], dt["AG"])[3], 3)
+#ab_int_corr = round(compare_data(dt["AB_int"], dt["AI"])[3], 3)
+```
+|  LCV   | HECATE |                  Description                   | Pearson Correlation \[-1,1\] |
+|:------:|:------:|:----------------------------------------------:|:----------------------------:|
+|   AB   |   AG   |    Galactic extinction/absorption in B band    |      `{python} ab_corr`      |
+| AB_int |   AI   | Internal/Intrisic B band extinction/absorption |   0   |
+```{python}
+scatter_plot(dt["AB"], dt["AG"])#, scatter_plot(dt["AB_int"], dt["AI"])
+```
 ## SFR

### 2024-07-19 compare/compare.qmd
+magn

@@
 
-|         LCV         | HECATE | Description |
-|:-------------------:|:------:|:-----------:|
-| mag_B (with errors) |  BT (with errors)      |             |
-|       Kmag   |     K   | 2MASS band magnitude  (both)          |
-|                     |        |             |
+```{python}
+#| echo: false
+mag_B_corr = round(compare_data(dt["mag_B"], dt["BT"],unc = dt["E_BT"])[3], 3)
+Kmag_corr = round(compare_data(dt["Kmag"], dt["K"], unc = dt["E_K"])[3], 3)
+```
+|         LCV         | HECATE | Description | Pearson Correlation \[-1,1\] |
+|:-------------------:|:------:|:-----------:|:----------------------------:|
+| mag_B (with errors) |  BT (with errors) |             | `{python} mag_B_corr` |
+|       Kmag          |     K              | 2MASS band magnitude (both) | `{python} Kmag_corr` |
+
+```{python}
+scatter_plot(dt["mag_B"], dt["BT"], yerr = dt["E_BT"])
+scatter_plot(dt["Kmag"], dt["K"], yerr = dt["E_K"])
+```
 ## Absorbsion

### 2024-07-21 compare/compare.qmd
try sigma

--- 2024-07-19 compare/compare.qmd
@@
 
-[^1]: Fitting can be done using the uncertainties as weights. To get the standard weighting of 1/unc^2, assuming Gaussian errors, the weights to pass to the fitting are 1/unc.
+[^1]: Fitting can be done using the uncertainties as weights. To get the standard weighting of 1/unc\^2, assuming Gaussian errors, the weights to pass to the fitting are 1/unc.
+
 [^2]: In simple linear regression, $R^2$ is the square of the Pearson correlation coefficient $\rho$.
@@
 ```{python}
-def compare_data(x, y, unc=None):
+def compare_data(x, y, unc=None, sigma = False):
     """
@@
         # fit the data with the fitter
+        # check if sigma
+        if sigma is False:
             fitted_line = fit(line_init, x_data, y_data, weights=w)
+            outliers = None
+        else:
+            or_fit = fitting.FittingWithOutlierRemoval(fit, sigma_clip, niter=3, sigma=3)
+            fitted_line, outliers = or_fit(line_init, x, y, weights=w)
         slope = fitted_line.slope.value
@@
 
-        return slope, intercept, r2, corr
+        return slope, intercept, r2, corr, outliers
     except Exception:
-        return 0, 0, 0, 0
+        return 0, 0, 0, 0, None
 ```
@@
 ```{python}
-def scatter_plot(x, y, xerr = None, yerr = None):
+def scatter_plot(x, y, xerr = None, yerr = None, sigma = False):
     """
@@
         unc = None
-    c, m, r2, corr = compare_data(x, y, unc)
+    c, m, r2, corr, outliers = compare_data(x, y, unc, sigma)
 
@@
     # errorbar -> needs np.ma -> no units
-    plt.errorbar(x_data, y_data, xerr = xerr_d, yerr = yerr_d, alpha = 0.3, c = "blue", label = "Data", fmt=".")
+    if outliers is not None:
+        filtered_data = np.ma.masked_array(y_data, mask = outlier)
+        plt.scatter(x, filtered_data,  label="Fitted Data", c = "blue", fillstyle = "filled")
+        plt.errorbar(x, y, yerr=yunc, fillstyle="filled", c = "black", label="Clipped Data", fmt = "o")
+    else:
+        plt.errorbar(x_data, y_data, xerr = xerr_d, yerr = yerr_d, alpha = 0.3, c = "blue", label = "Data", fmt = ".")
 
-    # Plot the fitted line with unit support
+    # Plot the fitted line 
     if c!=0:
@@
 ttype_corr = round(compare_data(dt["TType"], dt["T"])[3], 4)
-inc_corr = round(compare_data(dt["inc"], dt["INCL"])[3], 3)
-a26_corr = round(compare_data(dt["a26_1"], dt["A26_1a"])[3], 3)
+inc_corr = round(compare_data(dt["inc"], dt["INCL"], sigma = True)[3], 3)
+a26_corr = round(compare_data(dt["a26_1"], dt["A26_1a"], sigma =True)[3], 3)
 ```
@@
 |      LCV      |          HECATE          |                        Description                        | Pearson Correlation \[-1,1\] |
-|:---------------:|:---------------:|:-------------------:|:---------------:|
+|:---------------:|:---------------:|:------------------:|:---------------:|
 |     TType     |     T (with errors)      | Numerical Hubble type following the de Vaucouleurs system |    `{python} ttype_corr`     |
@@
 scatter_plot(dt["TType"], dt["T"], yerr = dt["E_T"])
-scatter_plot(dt["inc"], dt["INCL"], yerr = dt["E_V"])
+scatter_plot(dt["inc"], dt["INCL"], yerr = dt["E_V"], sigma =True)
 scatter_plot(dt["a26_1"], dt["A26_1a"], yerr = dt["E_V"])
@@
 ```
+
 |   LCV   | HECATE | Description | Pearson Correlation \[-1,1\] |
@@
 
-|         LCV         | HECATE | Description |
-|:-------------------:|:------:|:-----------:|
-| mag_B (with errors) |  BT (with errors)      |             |
-|       Kmag   |     K   | 2MASS band magnitude  (both)          |
-|                     |        |             |
+```{python}
+#| echo: false
+mag_B_corr = round(compare_data(dt["mag_B"], dt["BT"],unc = dt["E_BT"], sigma = True)[3], 3)
+Kmag_corr = round(compare_data(dt["Kmag"], dt["K"], unc = dt["E_K"])[3], 3)
+```
+
+|         LCV         |      HECATE      |         Description         | Pearson Correlation \[-1,1\] |
+|:---------------:|:-------------:|:-------------:|:------------------------:|
+| mag_B (with errors) | BT (with errors) |                             |    `{python} mag_B_corr`     |
+|        Kmag         |        K         | 2MASS band magnitude (both) |     `{python} Kmag_corr`     |
+
+```{python}
+scatter_plot(dt["mag_B"], dt["BT"], yerr = dt["E_BT"], sigma = True)
+scatter_plot(dt["Kmag"], dt["K"], yerr = dt["E_K"])
+```
+
 ## Absorbsion
@@
 ```
+
 |  LCV   | HECATE |                  Description                   | Pearson Correlation \[-1,1\] |
-|:------:|:------:|:----------------------------------------------:|:----------------------------:|
+|:-----------:|:-----------:|:----------------------------:|:---------------:|
 |   AB   |   AG   |    Galactic extinction/absorption in B band    |      `{python} ab_corr`      |
 | AB_int |   AI   | Internal/Intrisic B band extinction/absorption |              0               |
+
 ```{python}
@@
 ```
+
 ## SFR

### 2024-07-24 notes/list.py
logSFR

@@ -156,6 +156,16 @@ dt["MHI"] = (10**dt["logMHI"])
 dt["MHI"].unit = u.Msun
 dt["MHI"].description = "Linear hydrogen mass"
 
+dt.rename_column("SFRHa", "logSFRHa")
+dt.rename_column("SFRFUV", "logSFRFUV")
+
+dt["SFRHa"] = 10**dt["logSFRHa"]
+dt["SFRFUV"] = 10**dt["logSFRFUV"]
+dt["SFRFUV"].unit = u.Msun / u.yr
+dt["SFRHa"].unit = u.Msun / u.yr
+dt["SFRHa"].description = "Linear Star Formation Rate (Hα)"
+dt["SFRFUV"].description = "Linear Star Formation Rate (FUV)"
+
 log_columns_to_linear = ["KLum", "M26", "MHI"]
 
 # Create SkyCoord objects for coordinates
@@ -260,9 +270,6 @@ dt["logM26"].unit = ""
 dt["logMHI"].unit = ""
 dt["Thetaj"].unit = ""
 
-## SFR units
-dt["SFRFUV"].unit = u.Msun / u.yr
-dt["SFRHa"].unit = u.Msun / u.yr
 
 fixed_units = ["logKLum", "logM26", "logMHI", "Thetaj", "SFRFUV", "SFRHa"]
 

### 2024-07-24 tables/hecate_lcv_join.sh

@@ -7,8 +7,8 @@ stilts tpipe in=HECATE_v1.1.fits  cmd="select D<11" out=HECATE_LCV.fits
 #Outter join for each row of hecate
 stilts tmatch2 in1=final_table.ecsv in2=HECATE_LCV.fits out=outer_join.ecsv\
     join=all2 matcher=sky3d\
-    values1="Ra Dec Dis" values2="RA DEC D" params=0.2 
+    values1="Ra Dec Dis" values2="RA DEC D" params=0.1 
 #Inner join
 stilts tmatch2 in1=final_table.ecsv in2=HECATE_LCV.fits out=inner_join.ecsv\
     join=1and2 matcher=sky3d\
-    values1="Ra Dec Dis" values2="RA DEC D" params=0.2 
+    values1="Ra Dec Dis" values2="RA DEC D" params=0.1 

### 2024-07-24 notes/list.py
added stellar mass to lcv

@@ -168,6 +168,15 @@ dt["SFRFUV"].description = "Linear Star Formation Rate (FUV)"
 
 log_columns_to_linear = ["KLum", "M26", "MHI"]
 
+# Add Stellar Mass from Mass/Light ratio M*/KLum = 0.6
+dt["StellarMass"] = (0.6 * dt["KLum"])
+dt["StellarMass"].unit = u.Msun
+dt["StellarMass"].description = "Stellar Mass (M*/K luminosity)"
+
+# Add column of logStellarMass 
+dt["logStellarMass"] = np.log10(dt["StellarMass"])
+dt["logStellarMass"].description = "Log Stellar Mass (M*/K luminosity)"
+
 # Create SkyCoord objects for coordinates
 ra_str = [f"{hour}:{minute}:{second:.1f}" for hour, minute, second in zip(dt['RAh'], dt['RAm'], dt['RAs'])]
 dec_str = [f"{sign}{degree}:{minute}:{second:.1f}" for sign, degree, minute, second in zip(dt['DE-'], dt['DEd'], dt['DEm'], dt['DEs'])]

### 2024-07-24 compare/compare.qmd
SFR+Masses

@@
 from scipy.stats import pearsonr
+import seaborn as sns
+import pandas as pd
 import glob
@@
 
-The dataset we are going to use consists of `{python} len(dt)` galaxies and `{python} len(dt.colnames)`
+The dataset we are going to use consists of `{python} len(dt)` galaxies and `{python} len(dt.colnames)` columns.
 
@@
 |      LCV      |          HECATE          |                        Description                        | Pearson Correlation \[-1,1\] |
-|:---------------:|:---------------:|:------------------:|:---------------:|
+|:----------------:|:----------------:|:------------------:|:----------------:|
 |     TType     |     T (with errors)      | Numerical Hubble type following the de Vaucouleurs system |    `{python} ttype_corr`     |
@@
 #| echo: false
-logKLum_corr = round(compare_data(dt["logKLum"], dt["logL_K"])[3], 3)
+logKLum_corr = round(compare_data(dt["logKLum"], dt["logL_K"], sigma = True)[3], 3)
 ```
@@
 #| echo: false
-mag_B_corr = round(compare_data(dt["mag_B"], dt["BT"],unc = dt["E_BT"], sigma = True)[3], 3)
+mag_B_corr = round(compare_data(dt["mag_B"], dt["BT"],unc = dt["E_BT"], sigma = False)[3], 3)
 Kmag_corr = round(compare_data(dt["Kmag"], dt["K"], unc = dt["E_K"])[3], 3)
@@
 |         LCV         |      HECATE      |         Description         | Pearson Correlation \[-1,1\] |
-|:---------------:|:-------------:|:-------------:|:------------------------:|
+|:--------------:|:--------------:|:--------------:|:----------------------:|
 | mag_B (with errors) | BT (with errors) |                             |    `{python} mag_B_corr`     |
@@
 |  LCV   | HECATE |                  Description                   | Pearson Correlation \[-1,1\] |
-|:-----------:|:-----------:|:----------------------------:|:---------------:|
+|:--------------:|:--------------:|:------------------------:|:--------------:|
 |   AB   |   AG   |    Galactic extinction/absorption in B band    |      `{python} ab_corr`      |
@@
 
-|  LCV   |   HECATE   |                           Description                            |
-|:------------------:|:------------------:|:------------------------------:|
-|        | logSFR_TIR | Decimal logarithm of the total-infrared SFR estimate \[Msol/yr\] |
-|        | logSFR_FIR |  Decimal logarithm of the far-infrared SFR estimate \[Msol/yr\]  |
-|        | logSFR_60u |      Decimal logarithm of the 60um SFR estimate \[Msol/yr\]      |
-|        | logSFR_12u |      Decimal logarithm of the 12um SFR estimate \[Msol/yr\]      |
-|        | logSFR_22u |      Decimal logarithm of the 22um SFR estimate \[Msol/yr\]      |
-|        | logSFR_HEC |  Decimal logarithm of the homogenised SFR estimate \[Msol/yr\]   |
-|        | logSFR_GSW |       Decimal logarithm of the SFR in GSWLC-2 \[Msol/yr\]        |
-| SFRFUV |            |             FUV derived integral star formation rate             |
-| SFRHa  |            |          H{alpha} derived integral star formation rate           |
+```{python}
+#| echo: false
+# Extract the relevant SFR columns
+sfr_columns = ["logSFR_TIR", "logSFR_FIR", "logSFR_60u", "logSFR_12u", "logSFR_22u", "logSFR_HEC", "logSFR_GSW", "logSFRFUV", "logSFRHa"]
+sfr_data = dt[sfr_columns].to_pandas()
+
+# Count the number of non-NaN cells for each column
+non_nan_counts = sfr_data.notna().sum()
+```
+
+|  LCV   |   HECATE   |                           Description                            |                  Count                  |
+|:--------------:|:--------------:|:------------------------:|:--------------:|
+|        | logSFR_TIR | Decimal logarithm of the total-infrared SFR estimate \[Msol/yr\] | `{python} non_nan_counts["logSFR_TIR"]` |
+|        | logSFR_FIR |  Decimal logarithm of the far-infrared SFR estimate \[Msol/yr\]  | `{python} non_nan_counts["logSFR_FIR"]` |
+|        | logSFR_60u |      Decimal logarithm of the 60um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_60u"]` |
+|        | logSFR_12u |      Decimal logarithm of the 12um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_12u"]` |
+|        | logSFR_22u |      Decimal logarithm of the 22um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_22u"]` |
+|        | logSFR_HEC |  Decimal logarithm of the homogenised SFR estimate \[Msol/yr\]   | `{python} non_nan_counts["logSFR_HEC"]` |
+|        | logSFR_GSW |       Decimal logarithm of the SFR in GSWLC-2 \[Msol/yr\]        | `{python} non_nan_counts["logSFR_GSW"]` |
+| SFRFUV |            |             FUV derived integral star formation rate             | `{python} non_nan_counts["logSFRFUV"]`  |
+| SFRHa  |            |          H{alpha} derived integral star formation rate           |  `{python} non_nan_counts["logSFRHa"]`  |
+
+```{python}
+#| echo: false
+sfr_data.drop("logSFR_GSW", axis=1, inplace=True)
+# Compute the correlation matrix
+corr_matrix = sfr_data.corr()
+
+# Create a heatmap
+plt.figure(figsize=(10, 8))
+sns.heatmap(corr_matrix, annot=True, cmap="coolwarm", vmin=-1, vmax=1)
+plt.title("Correlation Heatmap of SFR Values")
+plt.show()
+
+# Create a pair grid
+sns.pairplot(sfr_data)
+plt.show()
+
+```
+
+It is possible we dont see a correlation because we dont have a big enough common sample
 
@@
 
-|      LCV       |  HECATE  |                        Description                        |
-|:------------------:|:------------------:|:------------------------------:|
-|     logM26     |          |              Log mass within Holmberg radius              |
-|     logMHI     |          |              Log mass within Holmberg radius              |
-|                | logM_HEC |      Decimal logarithm of the stellar mass \[Msol\]       |
-|                | logM_GSW | Decimal logarithm of the stellar mass in GSWLC-2 \[Msol\] |
-| logStellarMass |          |                Stellar Mass from M\*/L=0.6                |
+```{python}
+#| echo: false
+# Extract the relevant mass columns
+mass_columns = ["logM26", "logMHI", "logM_HEC", "logM_GSW", "logStellarMass"]
+mass_data = dt[mass_columns].to_pandas()
+
+# Count the number of non-NaN cells for each column
+non_nan_counts = mass_data.notna().sum()
+```
+
+|      LCV       |  HECATE  |                        Description                        |                  Count                  |
+|:------------------:|:------------------:|:------------------------------:|:------------------------------:|
+|     logM26     |          |              Log mass within Holmberg radius              | `{python} non_nan_counts["logM26"]`     |
+|     logMHI     |          |              Log mass within Holmberg radius              | `{python} non_nan_counts["logMHI"]`     |
+|                | logM_HEC |      Decimal logarithm of the stellar mass \[Msol\]       | `{python} non_nan_counts["logM_HEC"]`   |
+|                | logM_GSW | Decimal logarithm of the stellar mass in GSWLC-2 \[Msol\] | `{python} non_nan_counts["logM_GSW"]`   |
+| logStellarMass |          |                Stellar Mass from M_*/L=0.6                | `{python} non_nan_counts["logStellarMass"]` |
+
+```{python}
+#| echo: false
+mass_data.drop("logM_GSW", axis=1, inplace=True)
+# Compute the correlation matrix
+mass_corr_matrix = mass_data.corr()
+
+# Create a heatmap
+plt.figure(figsize=(10, 8))
+sns.heatmap(mass_corr_matrix, annot=True, cmap="coolwarm", vmin=-1, vmax=1)
+plt.title("Correlation Heatmap of Mass Values")
+plt.show()
+
+# Create a pair grid
+sns.pairplot(mass_data)
+plt.show()
+```
+
 :::

### 2024-07-24 compare/compare.qmd
fixed a26

@@
 inc_corr = round(compare_data(dt["inc"], dt["INCL"], sigma = True)[3], 3)
-a26_corr = round(compare_data(dt["a26_1"], dt["A26_1a"], sigma =True)[3], 3)
+a26_corr = round(compare_data(dt["a26_1"], dt["R1"], sigma =False)[3], 3)
 ```
@@
 |      LCV      |          HECATE          |                        Description                        | Pearson Correlation \[-1,1\] |
-|:----------------:|:----------------:|:------------------:|:----------------:|
+|:----------------:|:----------------:|:-----------------:|:----------------:|
 |     TType     |     T (with errors)      | Numerical Hubble type following the de Vaucouleurs system |    `{python} ttype_corr`     |
 |      inc      |           INCL           |                     Inclination (deg)                     |     `{python} inc_corr`      |
-| a26_1 (Major) | A26_1a (Semi-major axis) |                 angular diameter (arcmin)                 |     `{python} a26_corr`      |
+| a26_1 (Major) | R1 (Semi-major axis) |                 angular diameter (arcmin)                 |     `{python} a26_corr`      |
 
-As we can see we don't have any significant correlation between the Types of galaxies
+As we can see we don't have any significant correlation between the Types of galaxies and thus the correlation of the inclanations are 0
 
@@
 scatter_plot(dt["TType"], dt["T"], yerr = dt["E_T"])
-scatter_plot(dt["inc"], dt["INCL"], yerr = dt["E_V"], sigma =True)
-scatter_plot(dt["a26_1"], dt["A26_1a"], yerr = dt["E_V"])
+scatter_plot(dt["inc"], dt["INCL"], sigma =True)
+scatter_plot(dt["a26_1"], dt["R1"])
 
 ```
-
-**For the A26: In the LCV Catalog it is measured in deg, and in Hecate it is mesaured in kpc**
-
 ## Luminosities
@@
 |         LCV         |      HECATE      |         Description         | Pearson Correlation \[-1,1\] |
-|:--------------:|:--------------:|:--------------:|:----------------------:|
+|:----------------:|:----------------:|:----------------:|:-----------------:|
 | mag_B (with errors) | BT (with errors) |                             |    `{python} mag_B_corr`     |
@@
 |  LCV   | HECATE |                  Description                   | Pearson Correlation \[-1,1\] |
-|:--------------:|:--------------:|:------------------------:|:--------------:|
+|:----------------:|:----------------:|:------------------:|:----------------:|
 |   AB   |   AG   |    Galactic extinction/absorption in B band    |      `{python} ab_corr`      |
@@
 |  LCV   |   HECATE   |                           Description                            |                  Count                  |
-|:--------------:|:--------------:|:------------------------:|:--------------:|
+|:----------------:|:----------------:|:------------------:|:----------------:|
 |        | logSFR_TIR | Decimal logarithm of the total-infrared SFR estimate \[Msol/yr\] | `{python} non_nan_counts["logSFR_TIR"]` |
@@
 |      LCV       |  HECATE  |                        Description                        |                    Count                    |
-|:------------------:|:------------------:|:------------------------------:|:------------------------------:|
+|:----------------:|:----------------:|:----------------:|:----------------:|
 |     logM26     |          |              Log mass within Holmberg radius              |     `{python} non_nan_counts["logM26"]`     |
@@
 |                | logM_GSW | Decimal logarithm of the stellar mass in GSWLC-2 \[Msol\] |    `{python} non_nan_counts["logM_GSW"]`    |
-| logStellarMass |          |                Stellar Mass from M_*/L=0.6                | `{python} non_nan_counts["logStellarMass"]` |
+| logStellarMass |          |               Stellar Mass from M\_\*/L=0.6               | `{python} non_nan_counts["logStellarMass"]` |
 
@@
 ```
+:::
 
-:::
+# Morphology

### 2024-07-25 compare/compare.qmd
fixed sigma_clip

@@
 #quantity_support()
+from astropy.stats import sigma_clip
 from astropy.modeling import models, fitting
@@
 ```{python}
-def compare_data(x, y, unc=None, sigma = False):
+def compare_data(x, y, sigma = False):
     """
@@
     - y (array-like): The dependent variable data.
-    - unc (array-like with units, optional): The uncertainties associated with the independent variable data. Default is None.
+    - unc (array-like with units, optional): The uncertainties associated with the a variable data. Default is None.
 
@@
         y_data = np.ma.array(y.value, mask=np.isnan(y.value))
-        if unc is None:
-            w = None
-        else:
-            unc = np.ma.array(unc.value, mask=np.isnan(x.value))
-            w = 1 / unc
         # initialize a linear fitter
@@
         if sigma is False:
-            fitted_line = fit(line_init, x_data, y_data, weights=w)
+            fitted_line = fit(line_init, x_data, y_data)
             outliers = None
         else:
-            or_fit = fitting.FittingWithOutlierRemoval(fit, sigma_clip, niter=3, sigma=3)
-            fitted_line, outliers = or_fit(line_init, x, y, weights=w)
+            or_fit = fitting.FittingWithOutlierRemoval(fit, sigma_clip, niter=3, sigma=2)
+            fitted_line, outliers = or_fit(line_init, x_data, y_data)
         slope = fitted_line.slope.value
@@
         # Remove NaN values
-        mask = ~np.isnan(y_data) & ~np.isnan(y_pred)
+        mask = ~np.isnan(y_data)
+        if outliers is not None:
+            mask = ~np.isnan(y_data) & ~outliers
         y_data_clean = y_data[mask]
         y_pred_clean = y_pred[mask]
-        mask = ~np.isnan(x_data)
-        x_data_clean = x_data[mask]
 
@@
     except Exception:
-        return 0, 0, 0, 0, None
+        return 0,0,0,0,None
 ```
@@
     # Perform linear comparison between the datasets
-    if yerr is not None:
-        unc = yerr
-    elif yerr is None and xerr is not None:
-        unc = xerr
-    else:
-        unc = None
-    c, m, r2, corr, outliers = compare_data(x, y, unc, sigma)
+    c, m, r2, corr, outliers = compare_data(x, y, sigma)
 
@@
     if outliers is not None:
-        filtered_data = np.ma.masked_array(y_data, mask = outlier)
-        plt.scatter(x, filtered_data,  label="Fitted Data", c = "blue", fillstyle = "filled")
-        plt.errorbar(x, y, yerr=yunc, fillstyle="filled", c = "black", label="Clipped Data", fmt = "o")
+        filtered_data = np.ma.masked_array(y_data, mask = outliers)
+        plt.errorbar(x_data, y_data, yerr=yerr_d, c = "black", label="Clipped Data", fmt = "o", fillstyle = "none")
+        plt.scatter(x_data, filtered_data,  label="Fitted Data", c = "blue")
     else:
@@
 ```
+
 ## Luminosities
@@
 logKLum_corr = round(compare_data(dt["logKLum"], dt["logL_K"], sigma = True)[3], 3)
+
 ```
@@
 ```{python}
-scatter_plot(dt["logKLum"], dt["logL_K"])
+#| echo: false
+scatter_plot(dt["logKLum"], dt["logL_K"], sigma = True)
 ```
@@
 #| echo: false
-mag_B_corr = round(compare_data(dt["mag_B"], dt["BT"],unc = dt["E_BT"], sigma = False)[3], 3)
-Kmag_corr = round(compare_data(dt["Kmag"], dt["K"], unc = dt["E_K"])[3], 3)
+mag_B_corr = round(compare_data(dt["mag_B"], dt["BT"], sigma = True)[3], 3)
+Kmag_corr = round(compare_data(dt["Kmag"], dt["K"], sigma = True)[3], 3)
 ```
@@
 scatter_plot(dt["mag_B"], dt["BT"], yerr = dt["E_BT"], sigma = True)
-scatter_plot(dt["Kmag"], dt["K"], yerr = dt["E_K"])
+scatter_plot(dt["Kmag"], dt["K"], yerr = dt["E_K"], sigma = True)
 ```
@@
 :::
-
-# Morphology

### 2024-07-25 compare/compare.qmd
removed compare tabset

@@
 
-::: panel-tabset
 ## Coordinates
@@
 |  LCV   | HECATE |                  Description                   | Pearson Correlation \[-1,1\] |
-|:----------------:|:----------------:|:------------------:|:----------------:|
+|:----------------:|:----------------:|:-----------------:|:----------------:|
 |   AB   |   AG   |    Galactic extinction/absorption in B band    |      `{python} ab_corr`      |
@@
 |  LCV   |   HECATE   |                           Description                            |                  Count                  |
-|:----------------:|:----------------:|:------------------:|:----------------:|
+|:----------------:|:----------------:|:-----------------:|:----------------:|
 |        | logSFR_TIR | Decimal logarithm of the total-infrared SFR estimate \[Msol/yr\] | `{python} non_nan_counts["logSFR_TIR"]` |
@@
 
+::: panel-tabset
+## Heatmap
 ```{python}
-#| echo: false
 mass_data.drop("logM_GSW", axis=1, inplace=True)
@@
 # Create a heatmap
-plt.figure(figsize=(10, 8))
 sns.heatmap(mass_corr_matrix, annot=True, cmap="coolwarm", vmin=-1, vmax=1)
@@
 plt.show()
-
+```
+## Plot Grid
+```{python}
 # Create a pair grid

### 2024-07-25 compare/compare.qmd
added % of clipped data

@@
         else:
-            or_fit = fitting.FittingWithOutlierRemoval(fit, sigma_clip, niter=3, sigma=2)
+            or_fit = fitting.FittingWithOutlierRemoval(fit, sigma_clip, niter =3, sigma=3)
             fitted_line, outliers = or_fit(line_init, x_data, y_data)
@@
     if outliers is not None:
-        filtered_data = np.ma.masked_array(y_data, mask = outliers)
-        plt.errorbar(x_data, y_data, yerr=yerr_d, c = "black", label="Clipped Data", fmt = "o", fillstyle = "none")
-        plt.scatter(x_data, filtered_data,  label="Fitted Data", c = "blue")
+        filtered_data = np.ma.masked_array(y.value , mask = outliers)
+        outlier_percentage = (np.sum(outliers) / len(outliers)) * 100
+
+        plt.errorbar(x.value, y.value, yerr=yerr_d, c = "black", label="Clipped Data, {} ({}%)".format(np.sum(outliers), round(outlier_percentage,1)), fmt = "o", fillstyle = "none")
+        plt.scatter(x[~outliers], y[~outliers],  label=f"Fitted Data, {np.sum(~filtered_data.mask)}", c = "blue")
+
     else:
@@
 |  Dis  |   D    |    Distance     |      `{python} d_corr`       |
-
+::: panel-tabset
+## Right Ascnsion
 ```{python}
 
-scatter_plot(dt["Ra_1"], dt["RA_2"]), scatter_plot(dt["Dec_1"], dt["DEC_2"]), scatter_plot(dt["Dis"], dt["D"])
+scatter_plot(dt["Ra_1"], dt["RA_2"])
 ```
-
+## Declination
+```{python}
+scatter_plot(dt["Dec_1"], dt["DEC_2"]), 
+```
+## Distance
+```{python}
+scatter_plot(dt["Dis"], dt["D"])
+```
+:::
 ## Velocities

### 2024-07-25 compare/compare.qmd
Heatmaps and pairgrids

@@
 execute: 
-  echo: true
+  echo: false
   eval: true
@@
 
+Some data seem to have a very good linear correlation but they have many outliers. This is why we will clip the outliers whith $sigma > 3$
+
 -   Histograms
@@
 |  Dis  |   D    |    Distance     |      `{python} d_corr`       |
+
 ::: panel-tabset
 ## Right Ascnsion
+
 ```{python}
@@
 ```
+
 ## Declination
+
 ```{python}
@@
 ```
+
 ## Distance
+
 ```{python}
@@
 :::
+
 ## Velocities
@@
 |:----------------:|:-----------------:|:----------------:|:----------------:|
-|       RVel       | V/V_VIR (with errors) | Heliocentric radial velocity | `{python} rvel_corr, rvel_corr_v` |
-|       VLG        | V/V_VIR (with errors) |       Radial velocity        |  `{python} vlg_corr, vlg_corr_v`  |
-| cz (with errors) | V/V_VIR (with errors) |    Heliocentric velocity     |   `{python} cz_corr, cz_corr_v`   |
+| RVel (km/s) |   V (km/s)   |      Heliocentric radial velocity      | `{python} rvel_corr` |
+| VLG (km/s)  |              |            Radial velocity             |                      |
+|  cz (km/s)  |              |         Heliocentric velocity          |                      |
+|             | V_VIR (km/s) | Virgo-infall corrected radial velocity |                      |
+
+::: panel-tabset
+## Heliocentric radial Velocity
 
@@
 ```
+
+## Scatter Grid
+```{python}
+vel_data = dt[["RVel", "V", "VLG", "cz", "V_VIR"]].to_pandas()
+
+# Create a pair grid
+sns.pairplot(vel_data, corner=True)
+plt.show()
+```
+
+## Heatmap
+```{python}
+# Compute the correlation matrix
+corr_matrix = vel_data.corr()
+
+# Create a heatmap
+plt.figure(figsize=(10, 8))
+sns.heatmap(corr_matrix, annot=True, cmap="coolwarm", vmin=-1, vmax=1)
+plt.title("Correlation Heatmap of Velocity Values")
+plt.show()
+```
+
+:::
 
@@
 
-As we can see we don't have any significant correlation between the Types of galaxies and thus the correlation of the inclanations are 0
+::: panel-tabset
+## Galaxy Types
 
@@
 scatter_plot(dt["TType"], dt["T"], yerr = dt["E_T"])
-scatter_plot(dt["inc"], dt["INCL"], sigma =True)
-scatter_plot(dt["a26_1"], dt["R1"])
 
 ```
+As we can see we don't have any significant correlation between the Types of galaxies and thus the correlation of the inclanations are 0
+
+## Inclanation
+```{python}
+scatter_plot(dt["inc"], dt["INCL"], sigma =True)
+```
+## Major Axis
+
+```{python}
+scatter_plot(dt["a26_1"], dt["R1"])
+```
+
+:::
 
@@
 
+::: panel-tabset
+# B mag
 ```{python}
 scatter_plot(dt["mag_B"], dt["BT"], yerr = dt["E_BT"], sigma = True)
+```
+
+## K mag
+
+```{python}
+
 scatter_plot(dt["Kmag"], dt["K"], yerr = dt["E_K"], sigma = True)
 ```
-
+:::
 ## Absorbsion
@@
 
+::: panel-tabset
+## Heatmap
 ```{python}
@@
 plt.show()
-
+```
+## Scatter Grid
+```{python}
 # Create a pair grid 
-sns.pairplot(sfr_data)
+sns.pairplot(sfr_data, corner=True)
 plt.show()
@@
 ```
-
-It is possible we dont see a correlation because we dont have a big enough common sample
+:::
+It is possible we dont see a good correlation because we dont have a big enough common sample
 
@@
 ## Heatmap
+
 ```{python}
@@
 ```
+
 ## Plot Grid
+
 ```{python}
 # Create a pair grid
-sns.pairplot(mass_data)
+sns.pairplot(mass_data, corner=True)
 plt.show()

### 2024-07-25 compare/compare.qmd
b/k tab
pdf+rm warnings

@@
   eval: true
+  warning: false
 ---
@@
 
-1.  [$R^2$]{.underline}: Measures the proportion of variance explained by the linear model.
-2.  [Slope of the Fitted Line]{.underline}: Should be close to 1 for a 1-1 correlation.[^1]
-3.  [Pearson Correlation $\rho$]{.underline}: Measures the strength and direction of the linear relationship between two variables, ranging from -1 to 1. [^2]
+1.  $R^2$: Measures the proportion of variance explained by the linear model.
+2.  Slope of the Fitted Line: Should be close to 1 for a 1-1 correlation.[^1]
+3.  Pearson Correlation $\rho$: Measures the strength and direction of the linear relationship between two variables, ranging from -1 to 1. [^2]
 
@@
 ::: panel-tabset
-# B mag
+## B mag
 ```{python}

### 2024-07-25 compare/compare.qmd
expl:heatmap, sim vel,

@@
 
-4.
-[Scatter plots]{.underline}: Scatter plots are essential for visually assessing the relationship between two datasets, identifying correlations, trends, and outliers, and evaluating the fit of linear models.
+4.  [Plots]{.underline}: Plots are essential for visually assessing the relationship between two datasets, identifying correlations, trends, and outliers, and evaluating the fit of linear models.
 
 ```{python}
-def scatter_plot(x, y, xerr = None, yerr = None, sigma = False):
+def scatter_plot(x, y, xerr = None, yerr = None, sigma = False, logscale = False):
     """
@@
 
-Some data seem to have a very good linear correlation but they have many outliers. This is why we will clip the outliers whith $sigma > 3$
+Some data seem to have a very good linear correlation but they have many outliers. This is why we will clip the outliers with $sigma > 3$
 
--   Histograms
+- Correlation Heatmaps: A correlation heatmap is a graphical tool that displays the correlation between multiple variables as a color-coded matrix.
+It’s like a color chart that shows us how closely related different variables are.
 
--   Deviation
+In a correlation heatmap, each variable is represented by a row and a column, and the cells show the correlation between them.
+The color of each cell represents the strength and direction of the correlation, with darker colors indicating stronger correlations.
+
+- Histograms: Because not all of our data have the same number of counts, the comparison with histograms between data that are not the same, doesn't help us right now.[^3] This is why we will only use histograms for comparing the distribution of same-data columns normalized by their maximum value
+
+[^3]: When we will use the outer join table we could use histograms due to the large number of counts.
 
@@
 ::: panel-tabset
-## Right Ascnsion
+## Right Ascension
 
@@
 ```
-
+[?] The close correlation between all of the velocities, could be due to the fact that all of them measure the velocity of each galaxy, but from a different frame of reference.
 ## Heatmap
@@
 ```{python}
-scatter_plot(dt["a26_1"], dt["R1"])
+scatter_plot(dt["a26_1"], dt["R1"], logscale = True)
 ```
@@
 :::
-## Absorbsion
+## Absorpsion
 
@@
 |   AB   |   AG   |    Galactic extinction/absorption in B band    |      `{python} ab_corr`      |
-| AB_int |   AI   | Internal/Intrisic B band extinction/absorption |              0               |
+| AB_int |   AI   | Internal/Intrinsic B band extinction/absorption |              0               |
 
 ```{python}
-scatter_plot(dt["AB"], dt["AG"])#, scatter_plot(dt["AB_int"], dt["AI"])
+scatter_plot(dt["AB"], dt["AG"], logscale = True)#, scatter_plot(dt["AB_int"], dt["AI"])
 ```

### 2024-07-25 compare/compare.qmd
rel diff + log a26

@@
 import astropy.units as u
-from astropy.visualization import quantity_support
+from astropy.visualization import quantity_support, hist
 #quantity_support()
@@
     try:
-        x_data = np.ma.array(x.value, mask=np.isnan(x.value))
+        x_data = np.ma.array(x.value, mask=np.isnan(x.value)&x.mask)
         y_data = np.ma.array(y.value, mask=np.isnan(y.value))
@@
 
+- Percentage change: We can calculate the percentage change of the data for each galaxy and then we can see if the data are similar, based on minimum, the maximum and the mean value of the difference.
+
+$$\text{Percentage change} = \frac{V_{Hecate} - V_{LCV}}{V_{Hecate}}\cdot 100 \%$$
+
+```{python}
+def relative_diff(hec, lcv):
+    diff = 100*(hec - lcv) / hec
+    diff[np.isinf(diff)] = np.nan
+    return diff
+```
+
 # Comparable data
@@
 ```
+**Percentage change:**
+```{python}
+dt["diff_T"] = relative_diff(dt["T"], dt["TType"])
+dt["diff_T"].info("stats")
+```
+```{python}
+sns.distplot(dt["diff_T"])
+plt.xlabel("Percentage change of Types of Galaxies")
+plt.show()
+```
 As we can see we don't have any significant correlation between the Types of galaxies and thus the correlation of the inclanations are 0
@@
 ```
+
+```{python}
+dt["diff_inc"] = relative_diff(dt["INCL"], dt["inc"])
+dt["diff_inc"].info("stats")
+```
+```{python}
+sns.distplot(dt["diff_inc"])
+plt.xlabel("Percentage change of the inclination of the galaxies [%]")
+plt.show()
+```
+
 ## Major Axis
@@
 ```{python}
-scatter_plot(dt["a26_1"], dt["R1"], logscale = True)
+scatter_plot(dt["a26_1"], dt["R1"])
+```
+it is not very clear if we truly have a correlation or not. We need to see the linear correlation of the decimal logarithms.
+
+```{python}
+dt["log_a26"] = np.log(dt["a26_1"].data)
+dt["log_a26"].unit = u.arcmin
+dt["log_R1"] = np.log(dt["R1"].data)
+dt["log_R1"].unit = u.arcmin
+dt["log_R1"].info
+```
+```{python}
+scatter_plot(dt["log_a26"], dt["log_R1"], sigma = True)
 ```

### 2024-07-28 compare/compare.qmd
galaxy table + percent hist

@@
 
+<!-- -->
+
 -   Percentage change: We can calculate the percentage change of the data for each galaxy and then we can see if the data are similar, based on minimum, the maximum and the mean value of the difference.
@@
 def relative_diff(hec, lcv):
-    diff = 100*(hec - lcv) / hec
+    diff = (hec - lcv) *100/ hec
     diff[np.isinf(diff)] = np.nan
@@
 ## Scatter Grid
+
 ```{python}
@@
 ```
-[?] The close correlation between all of the velocities, could be due to the fact that all of them measure the velocity of each galaxy, but from a different frame of reference.
-## Heatmap
+
+\[?\] The close correlation between all of the velocities, could be due to the fact that all of them measure the velocity of each galaxy, but from a different frame of reference. \## Heatmap
+
 ```{python}
@@
 ```
-
 :::
@@
 
+```{=html}
+<table style="border-collapse:collapse;border-spacing:0" class="tg"><thead>
+<tr><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Hubble stage T </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">−6 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">−5 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">−4 </th>
+<th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">−3 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">−2 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">−1 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">0 </th>
+<th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">1 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">2 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">3 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">4 </th>
+<th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">5 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">6 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">7 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">8 </th>
+<th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">9 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">10 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">11 </th></tr>
+</thead>
+<tbody>
+<tr><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">de Vaucouleurs class </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">cE </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">E </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">E+ </td>
+<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">S0− </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">S00 </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">S0+ </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">S0/a </td>
+<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sa </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sab </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sb </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sbc </td>
+<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sc </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Scd </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sd </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sdm </td>
+<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sm </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Im </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal"> </td></tr>
+<tr><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Approximate Hubble class </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal" colspan="3">E </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal" colspan="3">S0 </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">S0/a </td>
+<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sa </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sa-b </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sb </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sb-c </td>
+<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal" colspan="3">Sc </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sc-Irr </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Irr I </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal"></td>
+<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal"></td></tr>
+</tbody></table>
+```
+
 ```{python}
@@
 ```
+
 **Percentage change:**
+
 ```{python}
@@
 ```
+
 ```{python}
-sns.distplot(dt["diff_T"])
-plt.xlabel("Percentage change of Types of Galaxies")
+sigma_T = sigma_clip(dt["diff_T"])
+sigma_T.info("stats"), dt["diff_T"].info("stats")
+```
+
+```{python}
+sns.histplot(dt["diff_T"], kde = True, label="Unclipped data")
+sns.histplot(sigma_T, kde = True, label = "Sigma=3")
+plt.title("Percentage change Distribution [%]")
+plt.xlim([-200, 200])
+plt.xlabel("Types of Galaxies")
+plt.legend()
 plt.show()
 ```
+
 As we can see we don't have any significant correlation between the Types of galaxies and thus the correlation of the inclanations are 0
@@
 ## Inclanation
+
 ```{python}
@@
 ```
+
 ```{python}
-sns.distplot(dt["diff_inc"])
-plt.xlabel("Percentage change of the inclination of the galaxies [%]")
+sns.histplot(dt["diff_inc"], kde = True)
+plt.title("Percentage change Distribution [%]")
+plt.xlabel(f"Inclination of the galaxies [{dt['inc'].unit}]")
 plt.show()
@@
 ```
+
 it is not very clear if we truly have a correlation or not. We need to see the linear correlation of the decimal logarithms.
@@
 ```{python}
-dt["log_a26"] = np.log(dt["a26_1"].data)
+dt["log_a26"] = np.log10(dt["a26_1"].data)
 dt["log_a26"].unit = u.arcmin
-dt["log_R1"] = np.log(dt["R1"].data)
+dt["log_R1"] = np.log10(dt["R1"].data)
 dt["log_R1"].unit = u.arcmin
@@
 ```
+
 ```{python}
@@
 :::
-
 ## Luminosities
@@
 ## B mag
+
 ```{python}
@@
 ```
+
+```{python}
+dt["diff_K_mag"] = relative_diff(dt["Kmag"], dt["K"])
+dt["diff_K_mag"].info("stats")
+```
+
+```{python}
+sns.histplot(dt["diff_K_mag"], kde = True)
+plt.title("Percentage change Distribution [%]")
+plt.xlabel(f"K band magnitude [{dt['K'].unit}]")
+plt.show()
+```
 :::
+
 ## Absorpsion
@@
 
+::: panel-tabset
+## Galactic
+
 ```{python}
@@
 ```
+
+## Internal
+
+```{python}
+plt.scatter(dt["AB_int"],dt["AI"],)
+plt.xlabel(f"LCV, AB_int [{dt['AB_int'].unit}]")
+plt.ylabel(f"HECATE, AI [{dt['AI'].unit}]")
+plt.yscale("log")
+plt.show()
+```
+
+If we use the decimal logarithm of the data we can clearly see the linear correlation.
+
+```{python}
+sns.jointplot(x=dt["AB_int"], y=dt["AI"], kind="reg",)
+```
+:::
 
@@
 ```
+
 ## Scatter Grid
+
 ```{python}
@@
 :::
+
 It is possible we dont see a good correlation because we dont have a big enough common sample

### 2024-07-28 compare/compare.qmd
percent_desc_histogram

@@
 plt.style.use('ggplot')
+pd.set_option('display.float_format', lambda x: '%.f' % x)
 
@@
 def relative_diff(hec, lcv):
-    diff = (hec - lcv) *100/ hec
+    """
+    Calculate the relative difference between two sets of values.
+
+    Parameters:
+    hec (numpy.ndarray): An array of values representing the HEC dataset.
+    lcv (numpy.ndarray): An array of values representing the LCV dataset.
+
+    Returns:
+    numpy.ndarray: An array of relative differences between the HEC and LCV datasets.
+    The relative difference is calculated as ((HEC - LCV) * 100) / |HEC|.
+    Any infinite values in the result are replaced with NaN.
+    """
+    diff = (hec - lcv) * 100 / np.abs(hec)
     diff[np.isinf(diff)] = np.nan
     return diff
+
+def percent_desc_histogram(x, sigmaclip = True, zoom = None):
+    """
+    This function creates a histogram of the given data and optionally applies a 3-sigma clip.
+
+    Parameters:
+    - x (array-like): The input data to create the histogram.
+    - sigmaclip (bool, optional): Whether to apply a 3-sigma clip to the data. Default is True.
+    - zoom (tuple, optional): The range of values to display on the x-axis of the histogram. Default is None.
+
+    Returns:
+    - t_pd (DataFrame): A pandas DataFrame containing statistical information about the input data.
+
+    The function uses the seaborn library to create the histogram and applies a 3-sigma clip if `sigmaclip` is True.
+    The histogram is displayed with appropriate labels and titles.
+    The statistical information about the input data is returned as a pandas DataFrame.
+    """
+    plt.close()
+    temp_table = QTable()
+    temp_table["Percentage change"]= x.copy()
+
+    if sigmaclip is True:
+        temp_table["Percentage change, after 3 sigma clip"] = sigma_clip(temp_table["Percentage change"],3)
+
+    t_pd = temp_table.to_pandas()
+
+    sns.histplot(temp_table["Percentage change"], kde = True, label = "Percentage change")
+
+    if sigmaclip is True:
+        sns.histplot(temp_table["Percentage change, after 3 sigma clip"], kde = True, label = "Percentage change, after 3 sigma clip")
+
+    plt.xlim(zoom)
+    plt.xlabel("Percentage change Distribution [%]")
+    plt.title("Types of Galaxies")
+    plt.legend()
+    plt.show()
+
+    return t_pd.describe(percentiles=[]).map('{:,.0f}'.format).style.set_properties(**{'text-align': 'center'})
 ```
@@
 ```{python}
+dt["INCL"].mask = np.isnan(dt["INCL"])
+```
+```{python}
 #| echo: false
@@
 ```{python}
-dt["diff_T"] = relative_diff(dt["T"], dt["TType"])
-dt["diff_T"].info("stats")
+
+dt["diff_T"] = relative_diff(hec = dt["T"], lcv = dt["TType"])
+percent_desc_histogram(dt["diff_T"], zoom = [-200,200])
 ```
-
-```{python}
-sigma_T = sigma_clip(dt["diff_T"])
-sigma_T.info("stats"), dt["diff_T"].info("stats")
-```
-
-```{python}
-sns.histplot(dt["diff_T"], kde = True, label="Unclipped data")
-sns.histplot(sigma_T, kde = True, label = "Sigma=3")
-plt.title("Percentage change Distribution [%]")
-plt.xlim([-200, 200])
-plt.xlabel("Types of Galaxies")
-plt.legend()
-plt.show()
-```
-
-As we can see we don't have any significant correlation between the Types of galaxies and thus the correlation of the inclanations are 0
 
@@
 ```{python}
-dt["diff_inc"] = relative_diff(dt["INCL"], dt["inc"])
-dt["diff_inc"].info("stats") 
+dt["INCL"].mask
+```
+```{python}
+dt["diff_inc"] = relative_diff(hec = dt["INCL"],lcv = dt["inc"])
+percent_desc_histogram(dt["diff_inc"])
 ```
@@
 ```{python}
-sns.histplot(dt["diff_inc"], kde = True)
-plt.title("Percentage change Distribution [%]")
-plt.xlabel(f"Inclination of the galaxies [{dt['inc'].unit}]")
-plt.show()
+#k = sigma_clip(dt["diff_inc"])
+dt["diff_T"].info
 ```

### 2024-07-29 compare/compare.qmd
Inclination

@@
 
-## Inclanation
+## Inclination
 
 ```{python}
-scatter_plot(dt["inc"], dt["INCL"], sigma =True)
+temp = dt[["inc", "INCL"]].to_pandas()
+
+sns.histplot(temp[["inc", "INCL"]], kde = True)
+plt.xlabel("Inclination of galaxies [deg]")
+plt.show()
+
+temp["Percentage Change [%]"] = (-temp["inc"] + temp["INCL"])/temp["INCL"]
+temp.loc[np.isinf(temp["Percentage Change [%]"]), "Percentage Change [%]"] = np.nan
+sns.histplot(temp["Percentage Change [%]"], kde = True)
+plt.show()
+temp.describe()
 ```
 
-```{python}
-dt["INCL"].mask
-```
-```{python}
-dt["diff_inc"] = relative_diff(hec = dt["INCL"],lcv = dt["inc"])
-percent_desc_histogram(dt["diff_inc"])
-```
-
-```{python}
-#k = sigma_clip(dt["diff_inc"])
-dt["diff_T"].info
-```
+We can see that for values in the range $[\sim 30^\circ,\sim 80^\circ]$, the values of the LCV inclination are higher.
+However, since their means, median, min and maxes are similar and the percentage change is practically 0% (mean, median, $\sigma$ = 0 with a range $[-3\%,1\%]$), we can ignore the differences and assume they are the same values.
 

### 2024-07-30 compare/compare.qmd
K Lum and Mag

@@
 #quantity_support()
-from astropy.stats import sigma_clip
+from astropy.stats import sigma_clip, SigmaClip
 from astropy.modeling import models, fitting
@@
     try:
-        x_data = np.ma.array(x.value, mask=np.isnan(x.value)&x.mask)
+        x_data = np.ma.array(x.value, mask=np.isnan(x.value))
         y_data = np.ma.array(y.value, mask=np.isnan(y.value))
@@
 
-\[?\] The close correlation between all of the velocities, could be due to the fact that all of them measure the velocity of each galaxy, but from a different frame of reference. \## Heatmap
+\[?\] The close correlation between all of the velocities, could be due to the fact that all of them measure the velocity of each galaxy, but from a different frame of reference.
+
+## Heatmap
 
@@
 ```
+:::
 
-:::
 ## Luminosities
@@
 #| echo: false
-scatter_plot(dt["logKLum"], dt["logL_K"], sigma = True)
+dt["diff_L_K"] = relative_diff(hec = dt["logL_K"].value, lcv = dt["logKLum"])
+temp = dt[["logKLum", "logL_K", "diff_L_K"]].to_pandas()
+sns.histplot(temp["diff_L_K"], kde = True)
+plt.xlabel("Percentage change [%]")
+plt.title("K-band Luminosities")
+plt.show()
+```
+
+```{python}
+temp.rename(columns = {"logKLum":"log(L_K)_{LCV}$", "logL_K":"log(L_K)_{HEC}", "diff_L_K":"Percentage Change [%]"}, inplace=True)
+```
+
+```{python}
+temp.describe()
 ```
@@
 ```{python}
-scatter_plot(dt["mag_B"], dt["BT"], yerr = dt["E_BT"], sigma = True)
+scatter_plot(dt["mag_B"], dt["BT"], yerr = dt["E_BT"], sigma=True)
 ```
@@
 dt["diff_K_mag"] = relative_diff(dt["Kmag"], dt["K"])
-dt["diff_K_mag"].info("stats")
+
+temp = dt[["diff_K_mag"]].to_pandas()
+c = temp["diff_K_mag"]
+up_clip = c.mean() + 3*c.std()
+low_clip = c.mean() - 3*c.std()
+temp["Percentage Change, after 3 sigma clip [%]"] = temp["diff_K_mag"].clip(low_clip, up_clip)
+temp.rename(columns={"diff_K_mag":"Percentage Change [%]"}, inplace=True)
+temp.describe()
 ```
@@
 ```{python}
-sns.histplot(dt["diff_K_mag"], kde = True)
+sns.histplot(temp, kde = True)
 plt.title("Percentage change Distribution [%]")

### 2024-07-30 compare/compare.qmd
SFR KDE

@@
 
-If we use the decimal logarithm of the data we can clearly see the linear correlation.
-
 ```{python}
@@
 plt.show()
+```
 
+## Density Grids
+
+```{python}
+# Create a pair grid 
+sns.pairplot(sfr_data, corner=True, kind="kde", diag_kind="hist")
+plt.show()
 ```
+
 :::

### 2024-07-31 compare/compare.qmd
Stellar Masses

@@
 ::: panel-tabset
+## Stellar Masses Comparison
+
+```{python}
+
+dt["diff_M"] =  relative_diff(hec = dt["logM_HEC"].data, lcv = dt["logStellarMass"])
+temp = dt[["diff_M"]].to_pandas()
+sns.histplot(temp, kde = True)
+plt.title("Percentage change Distribution [%]")
+plt.xlabel(r"$\log_{10}M_*$ "+f"[{dt['logM_HEC'].unit}]")
+plt.show()
+
+```
+
+```{python}
+temp.rename(columns={"diff_M":"Percantage Change [%]"}, inplace = True)
+```
+```{python}
+temp.describe()
+```
 ## Heatmap
@@
 ```
+
+## Density Grid
+
+```{python}
+# Create a pair grid
+sns.pairplot(mass_data, corner=True, kind="kde", diag_kind="hist")
+plt.show()
+```
 :::

### 2024-07-31 compare/compare.qmd
Minor fixes

@@
 2.  Slope of the Fitted Line: Should be close to 1 for a 1-1 correlation.[^1]
+
+[^1]: Some data seem to have a very good linear correlation but they have many outliers. This is why we will clip the outliers with $\sigma > 3$
+
 3.  Pearson Correlation $\rho$: Measures the strength and direction of the linear relationship between two variables, ranging from -1 to 1. [^2]
-
-[^1]: Fitting can be done using the uncertainties as weights. To get the standard weighting of 1/unc\^2, assuming Gaussian errors, the weights to pass to the fitting are 1/unc.
 
@@
 
-Some data seem to have a very good linear correlation but they have many outliers. This is why we will clip the outliers with $sigma > 3$
+-   Histograms: Because not all of our data have the same number of counts, the comparison with histograms between data that are not the same, doesn't help us right now.[^3] This is why we will only use histograms for comparing the distribution of same-data columns normalized by their maximum value
+
+[^3]: When we will use the outer join table we could use histograms due to the large number of counts.
 
@@
 
--   Histograms: Because not all of our data have the same number of counts, the comparison with histograms between data that are not the same, doesn't help us right now.[^3] This is why we will only use histograms for comparing the distribution of same-data columns normalized by their maximum value
+-   Kernel Density Estimate (KDE) plot: The KDE plot visually represents the distribution of data, providing insights into its shape, central tendency, and spread.
 
-[^3]: When we will use the outer join table we could use histograms due to the large number of counts.
-
-<!-- -->
-
--   Percentage change: We can calculate the percentage change of the data for each galaxy and then we can see if the data are similar, based on minimum, the maximum and the mean value of the difference.
+5.
+Percentage change: We can calculate the percentage change of the data for each galaxy and then we can see if the data are similar, based on minimum, the maximum and the mean value of the difference.
 
@@
 dt["log_R1"].unit = u.arcmin
-dt["log_R1"].info
 ```
@@
 ```{python}
-temp.describe()
+temp.describe(percentiles=[])
 ```
@@
 temp.rename(columns={"diff_K_mag":"Percentage Change [%]"}, inplace=True)
-temp.describe()
+temp.describe(percentiles=[])
 ```
@@
 
-## Absorpsion
+## Absorption
 
@@
 ## Internal
-
 ```{python}
-plt.scatter(dt["AB_int"],dt["AI"],)
+sns.jointplot(x=dt["AB_int"], y=dt["AI"], kind="reg",)
 plt.xlabel(f"LCV, AB_int [{dt['AB_int'].unit}]")
 plt.ylabel(f"HECATE, AI [{dt['AI'].unit}]")
-plt.yscale("log")
 plt.show()
 ```
-
-```{python}
-sns.jointplot(x=dt["AB_int"], y=dt["AI"], kind="reg",)
-```
+Here we can see an attempt to correlate the internal absorption of the two catalogs, however as it is very clear, there is no correlation, since even their distributions are not similar.
 :::
@@
 # Create a pair grid 
+plt.figure(figsize=(10, 8))
 sns.pairplot(sfr_data, corner=True)

### 2024-07-31 compare/compare.qmd
minor fixes x2

@@
 
-In this script we will compare out 2 catalogs @kovlakasHeraklionExtragalacticCatalogue2021 and [@karachentsevUPDATEDNEARBYGALAXY2013, @karachentsevSTARFORMATIONPROPERTIES2013a]
+In this script we will compare 2 catalogs @kovlakasHeraklionExtragalacticCatalogue2021 and [@karachentsevUPDATEDNEARBYGALAXY2013, @karachentsevSTARFORMATIONPROPERTIES2013a]
 
@@
 -   If we see that the data are similar we can use the outer join
+-   For the comparison we keep the parameters names exactly they are given in the catalogs
 
@@
 It’s like a color chart that shows us how closely related different variables are.
-
 In a correlation heatmap, each variable is represented by a row and a column, and the cells show the correlation between them.
@@
     temp_table = QTable()
-    temp_table["Percentage change"]= x.copy()
+    temp_table["Percentage change [%]"]= x.copy()
 
     if sigmaclip is True:
-        temp_table["Percentage change, after 3 sigma clip"] = sigma_clip(temp_table["Percentage change"],3)
+        temp_table["Percentage change [%], after 3 sigma clip"] = sigma_clip(temp_table["Percentage change [%]"],3)
 
@@
 
-    sns.histplot(temp_table["Percentage change"], kde = True, label = "Percentage change")
+    sns.histplot(temp_table["Percentage change [%]"], kde = True, label = "Percentage change [%]")
 
     if sigmaclip is True:
-        sns.histplot(temp_table["Percentage change, after 3 sigma clip"], kde = True, label = "Percentage change, after 3 sigma clip")
+        sns.histplot(temp_table["Percentage change [%], after 3 sigma clip"], kde = True, label = "Percentage change [%], after 3 sigma clip")
 
@@
 
-\[?\] The close correlation between all of the velocities, could be due to the fact that all of them measure the velocity of each galaxy, but from a different frame of reference.
-
 ## Heatmap
@@
 :::
+
+\[?\] The close correlation between all of the velocities, could be due to the fact that all of them measure the velocity of each galaxy, but from a different frame of reference.
 
@@
 ```
+
+[?] After the sigma clip we only lose 39 galaxies ($14\%$) and we can see that both the median and the mean of the percentage change are close to $0\%$.This is why we can assume that the Types of the galaxies are the same for the two catalogs
 
@@
 ```
+
+[?]
 :::
@@
 Here we can see an attempt to correlate the internal absorption of the two catalogs, however as it is very clear, there is no correlation, since even their distributions are not similar.
+[?]
 :::
@@
 
-It is possible we dont see a good correlation because we dont have a big enough common sample
+[?] It is possible we dont see a good correlation because we dont have a big enough common sample
 
@@
 |                | logM_GSW | Decimal logarithm of the stellar mass in GSWLC-2 \[Msol\] |    `{python} non_nan_counts["logM_GSW"]`    |
-| logStellarMass |          |               Stellar Mass from M\_\*/L=0.6               | `{python} non_nan_counts["logStellarMass"]` |
+| logStellarMass |          |               Stellar Mass from $M_*/L=0.6$               | `{python} non_nan_counts["logStellarMass"]` |
 

### 2024-09-22 compare/.ipynb_checkpoints/compare-checkpoint.tex
arxiv style

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
]{article}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
  \setmainfont[]{Latin Modern Roman}
  \setmathfont[]{Latin Modern Math}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{luacolor}
  \usepackage[soul]{lua-ul}
\else
  \usepackage{soul}

\fi
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Comparison of Catalogs},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\newcommand{\runninghead}{A Preprint }
\title{Comparison of Catalogs}
\def\asep{\\\\\\ } % default: all authors on same column
\author{}
\date{}
\begin{document}
\maketitle

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{3}
\tableofcontents
}
\section{The data}\label{the-data}

In this script we will compare 2 catalogs Kovlakas et al. (2021) and
Karachentsev and Kaisina (2013)

\begin{itemize}
\tightlist
\item
  The data have been joined based on their position in the sky (Ra,
  Dec).

  \begin{itemize}
  \tightlist
  \item
    We assume that every galaxy within 2 arc seconds of the initial
    coordinates is the same galaxy.
  \end{itemize}
\item
  We use TOPCAT to create two joins, an inner and an outer join
\item
  We will use the inner join for 1-1 comparisons
\item
  If we see that the data are similar we can use the outer join
\item
  For the comparison we keep the parameters names exactly they are given
  in the catalogs
\end{itemize}

The dataset we are going to use for the comparison (inner join) consists
of 288 galaxies and 168 columns.

\section{Catalog Completeness}\label{catalog-completeness}

Checking for completeness in galaxy catalogs is essential to ensure that
the data accurately represents the true population of galaxies.
Incomplete catalogs can lead to biased results in statistical studies,
such as the distribution of galaxy luminosity, mass, or star formation
rates. Additionally, missing galaxies, especially those at faint
magnitudes or large distances, can distort cosmological measurements and
hinder our understanding of galaxy formation and evolution.

Completeness checks are crucial for addressing selection biases,
ensuring accurate redshift distributions, and validating galaxy
simulations. They help identify gaps in the data and guide follow-up
observations, ensuring that the catalog provides a reliable sample for
scientific analysis. Without these checks, conclusions drawn from the
data may be inaccurate or incomplete.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

Checking for completeness in galaxy catalogs is essential to ensure that
the data accurately represents the true population of galaxies.
Incomplete catalogs can lead to biased results in statistical studies,
such as the distribution of galaxy luminosity, mass, or star formation
rates. Additionally, missing galaxies, especially those at faint
magnitudes or large distances, can distort cosmological measurements and
hinder our understanding of galaxy formation and evolution. Completeness
checks are crucial for addressing selection biases, ensuring accurate
redshift distributions, and validating galaxy simulations.

Distance-based corrections are applied to mitigate these biases by
adjusting for the underrepresentation of galaxies at greater distances.
As galaxies move farther away, they become fainter and harder to detect,
leading to a drop in the number of detected galaxies. Methods like
\textbf{volume corrections} (e.g., V/Vmax) and \textbf{luminosity
function-based corrections} help account for these effects by estimating
the true galaxy population based on the observed sample. These
corrections ensure that statistical analyses, even in incomplete
catalogs, more accurately reflect the full galaxy population.

\begin{longtable}[]{@{}lr@{}}
\toprule\noalign{}
Table & Number of galaxies \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Inner join & 288 \\
Outer join & 2901 \\
LCV & 1316 \\
HECATE & 2901 \\
Unique galaxies in LCV & 1028 \\
Unique Galaxies in Hecate & 2613 \\
\end{longtable}

\subsection{Completeness of the Inner
join}\label{completeness-of-the-inner-join}

\[
\text{Completeness (X)}=\frac{\text{(Galaxies in Inner Join)}}{\text{(Galaxies in X)}}×100\%
\]

Completeness (HECATE)= 10 \%

Completeness (LCV)= 22 \%

\subsection{Completeness in Outer
join}\label{completeness-in-outer-join}

\[
\text{Completeness (X)}=\frac{\text{(Galaxies in Outer Join form X)}}{\text{(Galaxies in X)}}×100\%
\]

Completeness (HECATE)= 90 \%

Completeness (LCV)= 78 \%

Combined Completeness
=\(\frac{\text{Total galaxies in Outer}}{\text{Unique galaxies in HECATE + LCV}}\)=
80 \%

\subsection{Completeness of the Catalogs, based on the Distance and the
Morphological
Type}\label{completeness-of-the-catalogs-based-on-the-distance-and-the-morphological-type}

\begin{figure}

\begin{minipage}{0.50\linewidth}

\centering{

\includegraphics{compare_files/figure-pdf/fig-dis-comp-output-1.pdf}

}

\subcaption{\label{fig-dis-comp-1}HECATE}

\end{minipage}%
%
\begin{minipage}{0.50\linewidth}

\centering{

\includegraphics{compare_files/figure-pdf/fig-dis-comp-output-2.pdf}

}

\subcaption{\label{fig-dis-comp-2}LCV}

\end{minipage}%

\caption{\label{fig-dis-comp}Histograms showing the Completeness of the
Catalogs}

\end{figure}%

\begin{figure}

\begin{minipage}{0.50\linewidth}

\centering{

\includegraphics{compare_files/figure-pdf/fig-type-comp-output-1.pdf}

}

\subcaption{\label{fig-type-comp-1}HECATE}

\end{minipage}%
%
\begin{minipage}{0.50\linewidth}

\centering{

\includegraphics{compare_files/figure-pdf/fig-type-comp-output-2.pdf}

}

\subcaption{\label{fig-type-comp-2}LCV}

\end{minipage}%

\caption{\label{fig-type-comp}Histograms showing the Completeness of the
Catalogs}

\end{figure}%

\begin{figure}

\begin{minipage}{0.50\linewidth}

\begin{longtable}[]{@{}rr@{}}
\toprule\noalign{}
Value & Count \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
-3 & 138 \\
-2 & 224 \\
-1 & 119 \\
0 & 4 \\
1 & 7 \\
2 & 2 \\
3 & 8 \\
4 & 9 \\
5 & 7 \\
6 & 24 \\
7 & 31 \\
8 & 86 \\
9 & 166 \\
10 & 484 \\
11 & 4 \\
\end{longtable}

\end{minipage}%
%
\begin{minipage}{0.50\linewidth}

\begin{longtable}[]{@{}rr@{}}
\toprule\noalign{}
Value & Count \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
-5 & 52 \\
-4.9 & 7 \\
-4.8 & 13 \\
-4.7 & 2 \\
-4.3 & 2 \\
-4 & 3 \\
-3.9 & 1 \\
-3.7 & 1 \\
-3.5 & 3 \\
-3.3 & 1 \\
-3.1 & 1 \\
-3 & 11 \\
-2.9 & 3 \\
-2.8 & 3 \\
-2.7 & 3 \\
-2.6 & 5 \\
-2.5 & 1 \\
-2.1 & 2 \\
-2 & 3 \\
-1.9 & 1 \\
-1.8 & 3 \\
-1.7 & 1 \\
-1.6 & 1 \\
-1.3 & 2 \\
-1 & 8 \\
-0.8 & 1 \\
-0.4 & 2 \\
-0.1 & 1 \\
0 & 3 \\
0.1 & 1 \\
0.4 & 1 \\
0.5 & 1 \\
0.6 & 1 \\
1 & 5 \\
1.1 & 2 \\
1.2 & 1 \\
1.3 & 1 \\
1.5 & 2 \\
1.6 & 2 \\
1.8 & 1 \\
1.9 & 2 \\
2.1 & 1 \\
2.2 & 2 \\
2.3 & 1 \\
2.4 & 3 \\
2.5 & 1 \\
2.6 & 1 \\
2.7 & 1 \\
2.9 & 1 \\
3 & 3 \\
3.1 & 4 \\
3.2 & 1 \\
3.3 & 6 \\
3.4 & 3 \\
3.5 & 2 \\
3.6 & 2 \\
3.8 & 2 \\
3.9 & 2 \\
4 & 13 \\
4.1 & 1 \\
4.2 & 2 \\
4.4 & 2 \\
4.5 & 1 \\
4.7 & 1 \\
4.8 & 1 \\
5 & 21 \\
5.1 & 5 \\
5.2 & 5 \\
5.3 & 1 \\
5.4 & 3 \\
5.5 & 1 \\
5.7 & 1 \\
5.8 & 2 \\
5.9 & 9 \\
6 & 13 \\
6.1 & 7 \\
6.4 & 1 \\
6.5 & 2 \\
6.7 & 3 \\
6.8 & 2 \\
6.9 & 5 \\
7 & 11 \\
7.1 & 1 \\
7.2 & 2 \\
7.3 & 1 \\
7.4 & 2 \\
7.5 & 4 \\
7.6 & 1 \\
7.7 & 3 \\
7.8 & 6 \\
7.9 & 9 \\
8 & 19 \\
8.1 & 4 \\
8.2 & 3 \\
8.3 & 5 \\
8.4 & 2 \\
8.5 & 4 \\
8.6 & 5 \\
8.7 & 6 \\
8.8 & 9 \\
8.9 & 15 \\
9 & 29 \\
9.1 & 4 \\
9.2 & 4 \\
9.3 & 2 \\
9.4 & 4 \\
9.5 & 13 \\
9.6 & 4 \\
9.7 & 17 \\
9.8 & 48 \\
9.9 & 90 \\
10 & 203 \\
\end{longtable}

\end{minipage}%

\end{figure}%

As we can see from the histograms Figure~\ref{fig-dis-comp} and
Figure~\ref{fig-type-comp} the sample of nique galaxies of each catalog,
gets smaller by an almost constant proportion (Inner join).

This means there is no bias in the selection of the galaxies.

\section{How are we going to compare the
data?}\label{how-are-we-going-to-compare-the-data}

\subsection{\texorpdfstring{Scatter plots and \(R^2\)
calculation}{Scatter plots and R\^{}2 calculation}}\label{scatter-plots-and-r2-calculation}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \(R^2\): Measures the proportion of variance explained by the linear
  model.
\item
  Slope of the Fitted Line: Should be close to 1 for a 1-1
  correlation.\footnote{Some data seem to have a very good linear
    correlation but they have many outliers. This is why we will clip
    the outliers with \(\sigma > 3\)}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  Pearson Correlation \(\rho\): Measures the strength and direction of
  the linear relationship between two variables, ranging from -1 to 1.
  \footnote{In simple linear regression, \(R^2\) is the square of the
    Pearson correlation coefficient \(\rho\).}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  \ul{Plots}: Plots are essential for visually assessing the
  relationship between two datasets, identifying correlations, trends,
  and outliers, and evaluating the fit of linear models.
\end{enumerate}

\begin{itemize}
\tightlist
\item
  Histograms: Because not all of our data have the same number of
  counts, the comparison with histograms between data that are not the
  same, doesn't help us right now.\footnote{When we will use the outer
    join table we could use histograms due to the large number of
    counts.} This is why we will only use histograms for comparing the
  distribution of same-data columns normalized by their maximum value
\end{itemize}

\begin{itemize}
\item
  Correlation Heatmaps: A correlation heatmap is a graphical tool that
  displays the correlation between multiple variables as a color-coded
  matrix. It's like a color chart that shows us how closely related
  different variables are. In a correlation heatmap, each variable is
  represented by a row and a column, and the cells show the correlation
  between them. The color of each cell represents the strength and
  direction of the correlation, with darker colors indicating stronger
  correlations.
\item
  Kernel Density Estimate (KDE) plot: The KDE plot visually represents
  the distribution of data, providing insights into its shape, central
  tendency, and spread.
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{4}
\tightlist
\item
  Percentage change: We can calculate the percentage change of the data
  for each galaxy and then we can see if the data are similar, based on
  minimum, the maximum and the mean value of the difference.
\end{enumerate}

\[\text{Percentage change} = \frac{V_{Hecate} - V_{LCV}}{V_{Hecate}}\cdot 100 \%\]

\section{Comparable data}\label{comparable-data}

\subsection{Coordinates}\label{coordinates}

\begin{longtable}[]{@{}cccc@{}}
\toprule\noalign{}
LCV & HECATE & Description & Pearson Correlation {[}-1,1{]} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Ra\_1 & RA\_2 & Right Ascension & 1.0 \\
Dec\_1 & DEC\_2 & Declination & 1.0 \\
Dis & D & Distance & 0.881 \\
\end{longtable}

\subsubsection{Right Ascension}

\includegraphics{compare_files/figure-pdf/cell-12-output-1.pdf}

\subsubsection{Declination}

\includegraphics{compare_files/figure-pdf/cell-13-output-1.pdf}

\subsubsection{Distance}

\includegraphics{compare_files/figure-pdf/cell-14-output-1.pdf}

\subsection{Velocities}\label{velocities}

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2603}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
LCV
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
HECATE
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Description
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Linear Correlation
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
RVel (km/s) & V (km/s) & Heliocentric radial velocity & 0.994 \\
VLG (km/s) & & Radial velocity & \\
cz (km/s) & & Heliocentric velocity & \\
& V\_VIR (km/s) & Virgo-infall corrected radial velocity & \\
\end{longtable}

\includegraphics{compare_files/figure-pdf/cell-16-output-1.pdf}

\includegraphics{compare_files/figure-pdf/cell-18-output-1.pdf}

{[}?{]} The close correlation between all of the velocities, could be
due to the fact that all of them measure the velocity of each galaxy,
but from a different frame of reference.

\subsection{Morphology and Geometry}\label{morphology-and-geometry}

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2603}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
LCV
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
HECATE
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Description
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Pearson Correlation {[}-1,1{]}
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
TType & T (with errors) & Numerical Hubble type following the de
Vaucouleurs system & 0.7107 \\
inc & INCL & Inclination (deg) & 0 \\
a26\_1 (Major) & R1 (Semi-major axis) & angular diameter (arcmin) & 0 \\
\end{longtable}

\subsubsection{Galaxy Types}

\includegraphics{compare_files/figure-pdf/cell-21-output-1.pdf}

\textbf{Percentage change:}

\includegraphics{compare_files/figure-pdf/cell-22-output-1.pdf}

\begin{longtable}[]{@{}lll@{}}
\toprule\noalign{}
& diff\_T & diff\_T\_clip \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
count & 229 & 191 \\
mean & -30 & -1 \\
std & 119 & 10 \\
min & -1000 & -39 \\
25\% & -11 & -2 \\
50\% & 0 & 0 \\
75\% & 0 & 2 \\
max & 131 & 30 \\
\end{longtable}

{[}?{]} After the sigma clip we only lose 39 galaxies (\(14\%\)) and we
can see that both the median and the mean of the percentage change are
close to \(0\%\).This is why we can assume that the Types of the
galaxies are the same for the two catalogs

\paragraph{Normalize the scale of galaxy
types}\label{normalize-the-scale-of-galaxy-types}

It is very possible that the two catalogs use different scaling methods,
as indicated by the use of decimal numbers in HECATE.

\begin{longtable}[]{@{}lllll@{}}
\toprule\noalign{}
& T & TType & T\_norm & TType\_norm \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
count & 229 & 287 & 229 & 287 \\
mean & 7 & 7 & 1 & 1 \\
std & 5 & 5 & 0 & 0 \\
min & -5 & -3 & 0 & 0 \\
25\% & 7 & 6 & 1 & 1 \\
50\% & 10 & 9 & 1 & 1 \\
75\% & 10 & 10 & 1 & 1 \\
max & 10 & 10 & 1 & 1 \\
\end{longtable}

Also, as we can see the minimum values are lower by 2 in HECATE, which
complies with the linear fit.

\includegraphics{compare_files/figure-pdf/cell-25-output-1.pdf}

\includegraphics{compare_files/figure-pdf/cell-26-output-1.pdf}

\includegraphics{compare_files/figure-pdf/cell-27-output-1.pdf}

\subsubsection{Inclination}

\includegraphics{compare_files/figure-pdf/cell-28-output-1.pdf}

\includegraphics{compare_files/figure-pdf/cell-28-output-2.pdf}

\begin{longtable}[]{@{}llll@{}}
\toprule\noalign{}
& inc & INCL & Percentage Change {[}\%{]} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
count & 287 & 209 & 202 \\
mean & 60 & 59 & -0 \\
std & 19 & 23 & 0 \\
min & 9 & 0 & -3 \\
25\% & 47 & 47 & -0 \\
50\% & 60 & 59 & 0 \\
75\% & 72 & 78 & 0 \\
max & 90 & 90 & 1 \\
\end{longtable}

We can see that for values in the range
\([\sim 30^\circ,\sim 80^\circ]\), the values of the LCV inclination are
higher. However, since their means, median, min and maxes are similar
and the percentage change is practically 0\% (mean, median, \(\sigma\) =
0 with a range \([-3\%,1\%]\)), we can ignore the differences and assume
they are the same values.

\subsubsection{Major Axis}

\includegraphics{compare_files/figure-pdf/cell-29-output-1.pdf}

it is not very clear if we truly have a correlation or not. We need to
see the linear correlation of the decimal logarithms.

\begin{verbatim}
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  5 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  5 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  5 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  5 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  5 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  5 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  5 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  5 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  5 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  5 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
\end{verbatim}

\includegraphics{compare_files/figure-pdf/cell-31-output-2.pdf}

\subsection{Luminosities}\label{luminosities}

\begin{longtable}[]{@{}cccc@{}}
\toprule\noalign{}
LCV & HECATE & Description & Pearson Correlation {[}-1,1{]} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
logKLum & logL\_K & & 0 \\
\end{longtable}

\includegraphics{compare_files/figure-pdf/cell-33-output-1.pdf}

\begin{longtable}[]{@{}llll@{}}
\toprule\noalign{}
& log(L\_K)\_\{LCV\}\$ & log(L\_K)\_\{HEC\} & Percentage Change
{[}\%{]} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
count & 287 & 70 & 70 \\
mean & 8 & 9 & -4 \\
std & 1 & 1 & 8 \\
min & 3 & 5 & -48 \\
50\% & 8 & 9 & -0 \\
max & 11 & 11 & 7 \\
\end{longtable}

\subsection{Magnitudes}\label{magnitudes}

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2603}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
LCV
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
HECATE
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Description
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Pearson Correlation {[}-1,1{]}
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
mag\_B (with errors) & BT (with errors) & & 0 \\
Kmag & K & 2MASS band magnitude (both) & 0 \\
\end{longtable}

\subsubsection{B mag}

\includegraphics{compare_files/figure-pdf/cell-37-output-1.pdf}

\subsubsection{K mag}

\includegraphics{compare_files/figure-pdf/cell-38-output-1.pdf}

\begin{longtable}[]{@{}lll@{}}
\toprule\noalign{}
& Percentage Change {[}\%{]} & Percentage Change, after 3 sigma clip
{[}\%{]} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
count & 70 & 70 \\
mean & -5 & -5 \\
std & 12 & 10 \\
min & -70 & -42 \\
50\% & -0 & -0 \\
max & 16 & 16 \\
\end{longtable}

\includegraphics{compare_files/figure-pdf/cell-40-output-1.pdf}

{[}?{]}

\subsection{SFR}\label{sfr}

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2603}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
LCV
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
HECATE
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Description
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Count
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
& logSFR\_TIR & Decimal logarithm of the total-infrared SFR estimate
{[}Msol/yr{]} & 21 \\
& logSFR\_FIR & Decimal logarithm of the far-infrared SFR estimate
{[}Msol/yr{]} & 22 \\
& logSFR\_60u & Decimal logarithm of the 60um SFR estimate {[}Msol/yr{]}
& 48 \\
& logSFR\_12u & Decimal logarithm of the 12um SFR estimate {[}Msol/yr{]}
& 26 \\
& logSFR\_22u & Decimal logarithm of the 22um SFR estimate {[}Msol/yr{]}
& 23 \\
& logSFR\_HEC & Decimal logarithm of the homogenised SFR estimate
{[}Msol/yr{]} & 73 \\
& logSFR\_GSW & Decimal logarithm of the SFR in GSWLC-2 {[}Msol/yr{]} &
0 \\
SFRFUV & & FUV derived integral star formation rate & 220 \\
SFRHa & & H\{alpha\} derived integral star formation rate & 223 \\
\end{longtable}

\includegraphics{compare_files/figure-pdf/cell-42-output-1.pdf}

\subsection{Masses}\label{masses}

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
LCV
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
HECATE
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Description
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Count
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
logM26 & & Log mass within Holmberg radius & 233 \\
logMHI & & Log mass within Holmberg radius & 233 \\
& logM\_HEC & Decimal logarithm of the stellar mass {[}Msol{]} & 64 \\
& logM\_GSW & Decimal logarithm of the stellar mass in GSWLC-2
{[}Msol{]} & 0 \\
logStellarMass & & Stellar Mass from \(M_*/L=0.6\) & 287 \\
\end{longtable}

\subsubsection{Stellar Masses Comparison}

\includegraphics{compare_files/figure-pdf/cell-44-output-1.pdf}

\begin{longtable}[]{@{}ll@{}}
\toprule\noalign{}
& Percantage Change {[}\%{]} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
count & 64 \\
mean & -1 \\
std & 5 \\
min & -19 \\
50\% & 1 \\
max & 9 \\
\end{longtable}

\subsubsection{Heatmap}

\includegraphics{compare_files/figure-pdf/cell-47-output-1.pdf}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-karachentsevSTARFORMATIONPROPERTIES2013a}
Karachentsev, Igor D., and Elena I. Kaisina. 2013. {``{STAR FORMATION
PROPERTIES IN THE LOCAL VOLUME GALAXIES VIA Hα AND FAR-ULTRAVIOLET
FLUXES}.''} \emph{AJ} 146 (3): 46.
\url{https://doi.org/10.1088/0004-6256/146/3/46}.

\bibitem[\citeproctext]{ref-karachentsevUPDATEDNEARBYGALAXY2013}
Karachentsev, Igor D., Dmitry I. Makarov, and Elena I. Kaisina. 2013.
{``{UPDATED NEARBY GALAXY CATALOG}.''} \emph{AJ} 145 (4): 101.
\url{https://doi.org/10.1088/0004-6256/145/4/101}.

\bibitem[\citeproctext]{ref-kovlakasHeraklionExtragalacticCatalogue2021}
Kovlakas, K., A. Zezas, J. J. Andrews, A. Basu-Zych, T. Fragos, A.
Hornschemeier, K. Kouroumpatzakis, B. Lehmer, and A. Ptak. 2021. {``The
{Heraklion Extragalactic Catalogue} ({HECATE}): A Value-Added Galaxy
Catalogue for Multimessenger Astrophysics.''} \emph{Monthly Notices of
the Royal Astronomical Society} 506 (September): 1896--1915.
\url{https://doi.org/10.1093/mnras/stab1799}.

\end{CSLReferences}

\end{document}

### 2024-09-22 pca.py
quick pca analysis

@@ -1,0 +1,199 @@
+#!/usr/bin/env python3
+
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+# Astropy for ecsv data
+from astropy.io import ascii
+from astropy.table import Table, QTable
+from sklearn.decomposition import PCA
+from sklearn.preprocessing import StandardScaler
+
+# Reading the ECSV file
+data = ascii.read("tables/final_table.ecsv")
+
+data = data.to_pandas()
+print(data.shape)
+# keep only columns with numeric data types
+numeric_data = data.select_dtypes(include=[np.number])
+
+# drop columns with e_ in the name
+numeric_data = numeric_data.drop(
+    columns=[col for col in numeric_data.columns if "e_" in col]
+)
+print(numeric_data.describe())
+
+# normalize the data with standard scaler
+scaler = StandardScaler()
+scaled_data = scaler.fit_transform(numeric_data)
+normalized_data = pd.DataFrame(scaled_data, columns=numeric_data.columns)
+print(normalized_data.describe())
+
+# fill the scaled_data arrays with 0 where there were nans
+normalized_data = normalized_data.fillna(0)
+
+
+# PCA analysis
+pca = PCA()
+pca_data = pca.fit_transform(normalized_data)
+
+# print the explained variance ratio
+expl_var = pca.explained_variance_ratio_
+df_expl_var = (
+    pd.DataFrame(
+        data=zip(range(1, len(expl_var) + 1), expl_var, expl_var.cumsum()),
+        columns=["PCA", "Explained Variance (%)", "Total Explained Variance (%)"],
+    )
+    .set_index("PCA")
+    .mul(100)
+    .round(1)
+)
+print(df_expl_var)
+# Plotting our explained variance
+import matplotlib.pyplot as plt
+
+fig, ax = plt.subplots(figsize=(8, 8))
+ax.bar(
+    x=df_expl_var.index,
+    height=df_expl_var["Explained Variance (%)"],
+    label="Explained Variance",
+    width=0.9,
+    color="#AAD8D3",
+)
+ax.plot(
+    df_expl_var["Total Explained Variance (%)"],
+    label="Total Explained Variance",
+    marker="o",
[…]

### 2024-09-22 tables/pca.R

@@ -1,0 +1,32 @@
+library(tidyverse)
+library(ggfortify)
+
+# open outer_join.ecsv
+dat <- read.table("outer_join.fits", header = TRUE, sep = "\t")
+str(dat)
+summary(dat)
+
+# pca analysis
+
+## 1. Data preparation: select numeric columns
+
+num_cols <- select_if(dat, is.numeric)
+char_cols <- select_if(dat, is.character)
+
+num_cols %>% nrow 
+
+## 2. Center and scale
+num_cols <- scale(num_cols, center = TRUE, scale = TRUE)
+## 3. remove columns with E_ in the column name
+num_cols <- as_tibble(num_cols) %>% select(-matches("^E_"))
+
+## 3. NA and NaN = 0
+num_cols[is.na(num_cols)] <- 0
+
+#pca
+pca_result <- prcomp(num_cols, center = TRUE, scale. = TRUE)
+
+# biplot with autoplot
+autoplot(pca_result, data = dat,color = "logM_HEC" )#,loadings = TRUE, loadings.label = TRUE, loadings.label.size = 3)
+
+

### 2024-09-22 notes/list.py
debugging in list.py

@@ -283,7 +283,7 @@ dt["Thetaj"].unit = ""
 fixed_units = ["logKLum", "logM26", "logMHI", "Thetaj", "SFRFUV", "SFRHa"]
 
 # Function to check flag consistency
-def check_flags(table):
+def check_flags(table, log_file="flag_errors_table.txt"):
     """
     Check for consistency between masked values and flag columns in an Astropy Table.
 
@@ -306,32 +306,54 @@ def check_flags(table):
         and the values are arrays of positions (indices) where the inconsistencies occur.
         If no inconsistencies are found, the dictionary will be empty.
     """
-    flag_errors = {}
+    flag_errors = []
+
+    # Iterate over columns with 'l_' or 'f_' prefix to identify limit flags or other flag indicators
     for colname in table.colnames:
         if colname.startswith('l_') or colname.startswith('f_'):
             main_col = colname[2:]  # Remove 'l_' or 'f_' prefix to get the main column name
             if main_col in table.colnames:
                 mask = table[main_col].mask
                 flags = table[colname]
-                
-                # Check if the flag column has non-empty entries
-                flag_positions = flags != ''  # or you can check for np.nan, or other specific flag indicators
 
-                if not np.all(mask == flag_positions):
-                    flag_errors[colname] = np.where(mask != flag_positions)[0]
+                # Check where the flag indicates a limit but the main column isn't masked
+                flag_positions = flags != ''  # Adjust for specific flag indicators if needed
+                inconsistent_mask = (~mask) & flag_positions  # Only add masks, don't remove existing ones
+
+                # If inconsistencies exist, log them by adding masks
+                if np.any(inconsistent_mask):
+                    # Apply mask where the flag indicates a limit but the column is not masked
+                    for i in np.where(inconsistent_mask)[0]:
+                        if flags[i] != '' and not mask[i]:  # Flag indicates a limit, but the main column is not masked
+                            table[main_col].mask[i] = True  # Apply mask
+                            # Log the error
+                            flag_errors.append([colname, i, f"Mask applied to {main_col} at index {i}"])
+
+    # Print names of affected columns
+    affected_columns = set([error[0] for error in flag_errors])
+    if affected_columns:
+        print("Inconsistencies found in the following columns:")
+        for col in affected_columns:
+            print(col)
+    else:
+        print("All flags are consistent with masked values.")
+
[…]

### 2024-09-22 tables/hecate_lcv_join.sh
new joins for unique galaxies

@@ -2,13 +2,23 @@
 
 #Keep only the LCV from Hecate
 
-stilts tpipe in=HECATE_v1.1.fits  cmd="select D<11" out=HECATE_LCV.fits
+#stilts tpipe in=HECATE_v1.1.fits  cmd="select D<11" out=HECATE_LCV.fits
 
 #Outter join for each row of hecate
 stilts tmatch2 in1=final_table.ecsv in2=HECATE_LCV.fits out=outer_join.ecsv\
-    join=all2 matcher=sky3d\
-    values1="Ra Dec Dis" values2="RA DEC D" params=0.1 
+    join=all2 matcher=sky\
+    values1="Ra Dec" values2="RA DEC" params=2 
 #Inner join
 stilts tmatch2 in1=final_table.ecsv in2=HECATE_LCV.fits out=inner_join.ecsv\
-    join=1and2 matcher=sky3d\
-    values1="Ra Dec Dis" values2="RA DEC D" params=0.1 
+    join=1and2 matcher=sky\
+    values1="Ra Dec" values2="RA DEC " params=2 
+
+#Hecate not LCV
+stilts tmatch2 in1=final_table.ecsv in2=HECATE_LCV.fits out=HEC_not_LCV_join.ecsv\
+    join=2not1 matcher=sky\
+    values1="Ra Dec" values2="RA DEC" params=2
+    
+#LCV not Hecate  
+stilts tmatch2 in2=final_table.ecsv in1=HECATE_LCV.fits out=LCV_not_HEC_join.ecsv\
+    join=2not1 matcher=sky\
+    values1="Ra Dec" values2="RA DEC" params=2

### 2024-09-22 compare/.ipynb_checkpoints/compare-checkpoint.qmd
- catalog completeness (dis and T) - pairplot with correlation - styling

--- 2024-07-31 compare/compare.qmd
@@
 title: "Comparison of Catalogs"
-format: html
+format: 
+  html: 
+    code-fold: true
+    html-math-method: katex
+  pdf: default
+  arxiv-pdf:
+    keep-tex: true    
 toc: true
-toc-depth: 2
+toc-depth: 3
 theme: minti
@@
 
--   The data have been joined based on their position in the sky (Ra, Dec, Distance).
+-   The data have been joined based on their position in the sky (Ra, Dec).
+    -   We assume that every galaxy within 2 arc seconds of the initial coordinates is the same galaxy.
 -   We use TOPCAT to create two joins, an inner and an outer join
@@
 from sklearn.metrics import r2_score
+import astropy
 from astropy.io import ascii
@@
 import os
+from tabulate import tabulate
+
 plt.style.use('ggplot')
@@
 dt = QTable(ascii.read("../tables/inner_join.ecsv"), masked=True)
+
+inner = dt
+outer = QTable(ascii.read("../tables/outer_join.ecsv"), masked=True)
+hec_not_lcv = QTable(ascii.read("../tables/HEC_not_LCV_join.ecsv"), masked=True)
+lcv_not_hec = QTable(ascii.read("../tables/LCV_not_HEC_join.ecsv"), masked=True)
+
+lcv = QTable(ascii.read("../tables/final_table.ecsv"), masked=True)
+hec = QTable(ascii.read("../tables/HECATE_LCV.ecsv"), masked=True)
 ```
 
-The dataset we are going to use consists of `{python} len(dt)` galaxies and `{python} len(dt.colnames)` columns.
+The dataset we are going to use for the comparison (inner join) consists of `{python} len(dt)` galaxies and `{python} len(dt.colnames)` columns.
+
+# Catalog Completeness
+
+Checking for completeness in galaxy catalogs is essential to ensure that the data accurately represents the true population of galaxies.
+Incomplete catalogs can lead to biased results in statistical studies, such as the distribution of galaxy luminosity, mass, or star formation rates.
+Additionally, missing galaxies, especially those at faint magnitudes or large distances, can distort cosmological measurements and hinder our understanding of galaxy formation and evolution.
+
+Completeness checks are crucial for addressing selection biases, ensuring accurate redshift distributions, and validating galaxy simulations.
+They help identify gaps in the data and guide follow-up observations, ensuring that the catalog provides a reliable sample for scientific analysis.
+Without these checks, conclusions drawn from the data may be inaccurate or incomplete.
+
+------------------------------------------------------------------------
+
+Checking for completeness in galaxy catalogs is essential to ensure that the data accurately represents the true population of galaxies.
+Incomplete catalogs can lead to biased results in statistical studies, such as the distribution of galaxy luminosity, mass, or star formation rates.
+Additionally, missing galaxies, especially those at faint magnitudes or large distances, can distort cosmological measurements and hinder our understanding of galaxy formation and evolution.
+Completeness checks are crucial for addressing selection biases, ensuring accurate redshift distributions, and validating galaxy simulations.
+
+Distance-based corrections are applied to mitigate these biases by adjusting for the underrepresentation of galaxies at greater distances.
+As galaxies move farther away, they become fainter and harder to detect, leading to a drop in the number of detected galaxies.
+Methods like **volume corrections** (e.g., V/Vmax) and **luminosity function-based corrections** help account for these effects by estimating the true galaxy population based on the observed sample.
+These corrections ensure that statistical analyses, even in incomplete catalogs, more accurately reflect the full galaxy population.
+
+```{python}
+#| output: asis
+# Creating a dataframe with the lengths of each table
+data = {
+    "Table": ["Inner join", "Outer join", "LCV", "HECATE", "Unique galaxies in LCV", "Unique Galaxies in Hecate"],
+    "Number of galaxies": [len(dt), len(outer), len(lcv), len(hec), len(lcv_not_hec), len(hec_not_lcv)]
+}
+
+df_lengths = pd.DataFrame(data)
+
+# Pretty print the dataframe in markdown format
+df_lengths_md = df_lengths.to_markdown(index=False)
+print(df_lengths_md)
+
+```
+
+## Completeness of the Inner join
+
+$$
+\text{Completeness (X)}=\frac{\text{(Galaxies in Inner Join)}}{\text{(Galaxies in X)}}×100\%
+$$
+
+Completeness (HECATE)= `{python} round(len(dt)/len(hec) *100)` %
+
+Completeness (LCV)= `{python} round(len(dt)/len(lcv) *100)` %
+
+## Completeness in Outer join
+
+$$
+\text{Completeness (X)}=\frac{\text{(Galaxies in Outer Join form X)}}{\text{(Galaxies in X)}}×100\%
+$$
+
+Completeness (HECATE)= `{python} round(len(hec_not_lcv)/len(hec)*100)` %
+
+Completeness (LCV)= `{python} round(len(lcv_not_hec)/len(lcv)*100)` %
+
+Combined Completeness =$\frac{\text{Total galaxies in Outer}}{\text{Unique galaxies in HECATE + LCV}}$= `{python} round(len(outer)/(len(lcv_not_hec)+(len(hec_not_lcv))) * 100)` %
+
+## Completeness of the Catalogs, based on the Distance and the Morphological Type
+
+```{python}
+#| fig-cap: "Histograms showing the Completeness of the Catalogs"
+#| layout-ncol: 2
+#| fig-subcap: 
+#| - "HECATE"
+#| - "LCV"
+#| label: fig-dis-comp
+
+plt.close()
+# Using numpy's histogram function to get the bin edges automatically for the first dataset
+_, bin_edges = np.histogram(hec["D"].data, bins='auto')  # 'auto' decides the best number of bins for the data
+
+# Step 2: Use the same bin edges for all datasets
+sns.histplot(hec["D"].value, bins=bin_edges, kde=True, label="HECATE")
+sns.histplot(hec_not_lcv["D"].value, bins=bin_edges, kde=True, label="Unique for Hecate")
+sns.histplot(inner["D"].value, bins=bin_edges, kde=True, label="Inner join")
+
+plt.title("Completeness of Distance for HECATE")
+plt.xlabel("Distance [Mpc]")
+plt.ylabel("Number of galaxies")
+plt.legend()
+plt.show()
+plt.close()
+
+# Using numpy's histogram function to get the bin edges automatically for the first dataset
+_, bin_edges = np.histogram(lcv["Dis"].data, bins='auto')  # 'auto' decides the best number of bins for the data
+sns.histplot(lcv["Dis"].value, bins=bin_edges, kde = True, label = "LCV")
+sns.histplot(lcv_not_hec["Dis"].value, bins=bin_edges, kde = True, label = "Unique for LCV")
+sns.histplot(inner["Dis"].value, bins=bin_edges, kde = True, label = "Inner join")
+plt.title("Completeness of Distance for LCV")
+plt.xlabel("Distance [Mpc]")
+plt.ylabel("Number of galaxies")
+plt.legend()
+plt.show()
+plt.close()
+
+```
+
+```{python}
+#| layout-ncol: 2
+#| fig-cap: "Histograms showing the Completeness of the Catalogs"
+#| fig-subcap: 
+#| - "HECATE"
+#| - "LCV"
+#| label: fig-type-comp
+# Using numpy's histogram function to get the bin edges automatically for the first dataset
+bin_edges = 16
+
+sns.histplot(hec["T"], bins=bin_edges, kde = True, label = "HECATE")
+sns.histplot(hec_not_lcv["T"], bins=bin_edges, kde = True, label = "Unique for Hecate")
+sns.histplot(inner["T"].value, bins=bin_edges, kde = True, label = "Inner join")
+plt.title("Completeness of Types of galaxies for HECATE")
+plt.xlabel("Type")
+plt.ylabel("Number of galaxies")
+plt.legend()
+plt.show()
+plt.close()
+
+bin_edges = 14
+
+sns.histplot(lcv["TType"], bins=bin_edges, kde = True, label = "LCV")
+sns.histplot(lcv_not_hec["TType"], bins=bin_edges, kde = True, label = "Unique for LCV")
+sns.histplot(inner["TType"].value, bins=bin_edges, kde = True, label = "Inner join")
+plt.title("Completeness of Types of galaxies for LCV")
+plt.xlabel("Type")
+plt.ylabel("Number of galaxies")
+plt.legend()
+plt.show()
+plt.close()
+
+```
+
+As we can see from the histograms @fig-dis-comp and @fig-type-comp the sample of nique galaxies of each catalog, gets smaller by an almost constant proportion (Inner join).
+
+This means there is no bias in the selection of the galaxies.
 
@@
 [^1]: Some data seem to have a very good linear correlation but they have many outliers. This is why we will clip the outliers with $\sigma > 3$
+
+<!-- -->
 
@@
 
+<!-- -->
+
 -   Correlation Heatmaps: A correlation heatmap is a graphical tool that displays the correlation between multiple variables as a color-coded matrix.
-It’s like a color chart that shows us how closely related different variables are.
+It's like a color chart that shows us how closely related different variables are.
 In a correlation heatmap, each variable is represented by a row and a column, and the cells show the correlation between them.
 The color of each cell represents the strength and direction of the correlation, with darker colors indicating stronger correlations.
+
+```{python}
+
+# Define a function that creates a pairplot with correlation coefficients
+def pairplot_with_correlation(df, cmap="coolwarm", font_size=12, font_style='italic', font_weight='bold', box_color='white'):
+    """
+    Creates a Seaborn pairplot with correlation coefficients displayed on the upper triangle.
+
+    Parameters:
+    df : pandas.DataFrame
+        The dataframe containing the data for the pairplot.
+    cmap : str, optional
+        The colormap to use for coloring the correlation coefficients (default is 'coolwarm_r').
+    font_size : int, optional
+        The font size for the correlation coefficient annotations (default is 12).
+    font_style : str, optional
+        The font style for the correlation coefficient annotations (default is 'italic').
+    font_weight : str, optional
+        The font weight for the correlation coefficient annotations (default is 'bold').
+    box_color : str, optional
+        The background color of the box around the correlation coefficients (default is 'white').
+
+    Returns:
+    A Seaborn pairplot with correlation coefficients displayed in a heatmap style.
+    """
+    plt.close()
+    # Create Pairplot
+    pairplot = sns.pairplot(df, plot_kws={"color": "green"}, diag_kws = {"color" : "green"})
+
+    # Calculate Correlations
+    corr_matrix = df.corr()
+
+    # Define a colormap
+    colormap = plt.get_cmap(cmap)
+
+    # Overlay Correlation Coefficients with customized annotations
+    for i, j in zip(*np.triu_indices_from(corr_matrix, 1)):
+        # Get the correlation value
+        corr_value = corr_matrix.iloc[i, j]
+
+        # Get a color from the colormap based on the correlation value
+        color = colormap((corr_value + 1) / 2)  # Normalize between 0 and 1
+
+        # Annotate the plot with the correlation value, using a box, bold, and italic
+        pairplot.axes[i, j].annotate(f"{corr_value:.2f}", 
+                                     xy=(0.5, 0.5), 
+                                     xycoords='axes fraction',
+                                     ha='center', 
+                                     va='center', 
+                                     fontsize=font_size,  # Font size
+                                     fontstyle=font_style,  # Font style
+                                     fontweight=font_weight,  # Font weight
+                                     bbox=dict(facecolor=box_color, edgecolor=color, boxstyle='round,pad=0.5'),  # Box around the text
+                                     color=color)  # Use heatmap color for text
+
+    # Show the plot
+    plt.show()
+
+```
 
@@
 ::: panel-tabset
-## Right Ascension
+### Right Ascension
 
@@
 
-## Declination
+### Declination
 
@@
 
-## Distance
+### Distance
 
@@
 
-::: panel-tabset
-## Heliocentric radial Velocity
-
 ```{python}
@@
 
-## Scatter Grid
+```{python}
+vel_data = dt[["RVel", "V", "VLG", "cz", "V_VIR"]].to_pandas()
+```
 
 ```{python}
-vel_data = dt[["RVel", "V", "VLG", "cz", "V_VIR"]].to_pandas()
-
-# Create a pair grid
-sns.pairplot(vel_data, corner=True)
-plt.show()
+pairplot_with_correlation(vel_data)
 ```
-
-## Heatmap
-
-```{python}
-# Compute the correlation matrix
-corr_matrix = vel_data.corr()
-
-# Create a heatmap
-plt.figure(figsize=(10, 8))
-sns.heatmap(corr_matrix, annot=True, cmap="coolwarm", vmin=-1, vmax=1)
-plt.title("Correlation Heatmap of Velocity Values")
-plt.show()
-```
-:::
 
@@
 ::: panel-tabset
-## Galaxy Types
-
-```{=html}
-<table style="border-collapse:collapse;border-spacing:0" class="tg"><thead>
-<tr><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Hubble stage T </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">−6 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">−5 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">−4 </th>
-<th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">−3 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">−2 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">−1 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">0 </th>
-<th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">1 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">2 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">3 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">4 </th>
-<th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">5 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">6 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">7 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">8 </th>
-<th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">9 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">10 </th><th style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">11 </th></tr>
-</thead>
-<tbody>
-<tr><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">de Vaucouleurs class </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">cE </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">E </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">E+ </td>
-<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">S0− </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">S00 </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">S0+ </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">S0/a </td>
-<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sa </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sab </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sb </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sbc </td>
-<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sc </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Scd </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sd </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sdm </td>
-<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sm </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Im </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal"> </td></tr>
-<tr><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Approximate Hubble class </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal" colspan="3">E </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal" colspan="3">S0 </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">S0/a </td>
-<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sa </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sa-b </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sb </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sb-c </td>
-<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal" colspan="3">Sc </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Sc-Irr </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal">Irr I </td><td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal"></td>
-<td style="border-color:inherit;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;padding:10px 5px;text-align:center;vertical-align:top;word-break:normal"></td></tr>
-</tbody></table>
-```
+### Galaxy Types
 
@@
 scatter_plot(dt["TType"], dt["T"], yerr = dt["E_T"])
-
 ```
@@
 percent_desc_histogram(dt["diff_T"], zoom = [-200,200])
+dt["diff_T_clip"] = sigma_clip(dt["diff_T"], sigma=3)
+dt[["diff_T", "diff_T_clip"]].to_pandas().describe()
+
 ```
 
-[?] After the sigma clip we only lose 39 galaxies ($14\%$) and we can see that both the median and the mean of the percentage change are close to $0\%$.This is why we can assume that the Types of the galaxies are the same for the two catalogs
+\[?\] After the sigma clip we only lose 39 galaxies ($14\%$) and we can see that both the median and the mean of the percentage change are close to $0\%$.This is why we can assume that the Types of the galaxies are the same for the two catalogs
 
-## Inclination
+#### Normalize the scale of galaxy types
+
+It is very possible that the two catalogs use different scaling methods, as indicated by the use of decimal numbers in HECATE.
 
 ```{python}
+types = dt[["T", "TType"]].to_pandas()
+```
+
+```{python}
+def min_max_normalize(series):
+    return (series - series.min()) / (series.max() - series.min())
+
+types["T_norm"] = min_max_normalize(types["T"])
+types["T_norm"].mask = types["T"].mask
+types["TType_norm"] = min_max_normalize(types["TType"])
+types.describe()
+```
+
+Also, as we can see the minimum values are lower by 2 in HECATE, which complies with the linear fit.
+
+```{python}
+sns.histplot(types[["TType_norm", "T_norm"]], kde = True)
+plt.xlabel("Types of galaxies")
+plt.show()
+```
+
+```{python}
+types["norm_diff"] = (-types["TType_norm"] + types["T_norm"])
+sns.histplot(types["norm_diff"], kde = True)
+
+plt.xlabel(r"$T_{HECATE}-T_{LCV}$")
+plt.show()
+```
+
+```{python}
+types["norm_rel_diff"] = (-types["TType_norm"] + types["T_norm"])/types["T"]
+sns.histplot(types["norm_rel_diff"], kde = True)
+plt.xlim(-0.2,0.2)
+plt.xlabel(r"$(T_{HECATE}-T_{LCV})/T_{HECATE}$")
+plt.show()
+```
+
+### Inclination
+
+```{python}
+
 temp = dt[["inc", "INCL"]].to_pandas()
@@
 
-## Major Axis
+### Major Axis
 
@@
 #| echo: false
+#| warning: false
 logKLum_corr = round(compare_data(dt["logKLum"], dt["logL_K"], sigma = True)[3], 3)
@@
 #| echo: false
+#| warning: false
 mag_B_corr = round(compare_data(dt["mag_B"], dt["BT"], sigma = True)[3], 3)
@@
 ::: panel-tabset
-## B mag
+### B mag
 
@@
 
-## K mag
+### K mag
 
 ```{python}
-
 scatter_plot(dt["Kmag"], dt["K"], yerr = dt["E_K"], sigma = True)
@@
 
-[?]
-:::
-
-## Absorption
-
-```{python}
-#| echo: false
-ab_corr = round(compare_data(dt["AB"], dt["AG"])[3], 3)
-#ab_int_corr = round(compare_data(dt["AB_int"], dt["AI"])[3], 3)
-```
-
-|  LCV   | HECATE |                   Description                   | Pearson Correlation \[-1,1\] |
-|:----------------:|:----------------:|:-----------------:|:----------------:|
-|   AB   |   AG   |    Galactic extinction/absorption in B band     |      `{python} ab_corr`      |
-| AB_int |   AI   | Internal/Intrinsic B band extinction/absorption |              0               |
-
-::: panel-tabset
-## Galactic
-
-```{python}
-scatter_plot(dt["AB"], dt["AG"], logscale = True)#, scatter_plot(dt["AB_int"], dt["AI"])
-```
-
-## Internal
-```{python}
-sns.jointplot(x=dt["AB_int"], y=dt["AI"], kind="reg",)
-plt.xlabel(f"LCV, AB_int [{dt['AB_int'].unit}]")
-plt.ylabel(f"HECATE, AI [{dt['AI'].unit}]")
-plt.show()
-```
-Here we can see an attempt to correlate the internal absorption of the two catalogs, however as it is very clear, there is no correlation, since even their distributions are not similar.
-[?]
+\[?\]
 :::
@@
 
-::: panel-tabset
-## Heatmap
-
 ```{python}
@@
 sfr_data.drop("logSFR_GSW", axis=1, inplace=True)
-# Compute the correlation matrix
-corr_matrix = sfr_data.corr()
 
-# Create a heatmap
-plt.figure(figsize=(10, 8))
-sns.heatmap(corr_matrix, annot=True, cmap="coolwarm", vmin=-1, vmax=1)
-plt.title("Correlation Heatmap of SFR Values")
-plt.show()
+# Example usage of the function
+pairplot_with_correlation(sfr_data)
+
 ```
-
-## Scatter Grid
-
-```{python}
-# Create a pair grid 
-plt.figure(figsize=(10, 8))
-sns.pairplot(sfr_data, corner=True)
-plt.show()
-```
-
-## Density Grids
-
-```{python}
-# Create a pair grid 
-sns.pairplot(sfr_data, corner=True, kind="kde", diag_kind="hist")
-plt.show()
-```
-
-:::
-
-[?] It is possible we dont see a good correlation because we dont have a big enough common sample
 
@@
 ::: panel-tabset
-## Stellar Masses Comparison
+### Stellar Masses Comparison
 
@@
 plt.show()
+plt.close()
 
@@
 ```
-## Heatmap
+
+### Heatmap
 
@@
 # Compute the correlation matrix
-mass_corr_matrix = mass_data.corr()
 
-# Create a heatmap
-sns.heatmap(mass_corr_matrix, annot=True, cmap="coolwarm", vmin=-1, vmax=1)
-plt.title("Correlation Heatmap of Mass Values")
-plt.show()
-```
-
-## Plot Grid
-
-```{python}
-# Create a pair grid
-sns.pairplot(mass_data, corner=True)
-plt.show()
-```
-
-## Density Grid
-
-```{python}
-# Create a pair grid
-sns.pairplot(mass_data, corner=True, kind="kde", diag_kind="hist")
-plt.show()
+pairplot_with_correlation(mass_data)
 ```

### 2024-09-27 compare/compare.qmd
created functions for completeness (plot and table of bins)

@@
 import os
+from tabulate import tabulate
+from IPython.display import Markdown, display
+
 plt.style.use('ggplot')
@@
 dt = QTable(ascii.read("../tables/inner_join.ecsv"), masked=True)
+
+inner = dt
+outer = QTable(ascii.read("../tables/outer_join.ecsv"), masked=True)
+hec_not_lcv = QTable(ascii.read("../tables/HEC_not_LCV_join.ecsv"), masked=True)
+lcv_not_hec = QTable(ascii.read("../tables/LCV_not_HEC_join.ecsv"), masked=True)
+
+lcv = QTable(ascii.read("../tables/final_table.ecsv"), masked=True)
+hec = QTable(ascii.read("../tables/HECATE_LCV.ecsv"), masked=True)
 ```
 
-The dataset we are going to use consists of `{python} len(dt)` galaxies and `{python} len(dt.colnames)` columns.
+The dataset we are going to use for the comparison (inner join) consists of `{python} len(dt)` galaxies and `{python} len(dt.colnames)` columns.
+
+# Catalog Completeness
+
+Checking for completeness in galaxy catalogs is essential to ensure that the data accurately represents the true population of galaxies.
+Incomplete catalogs can lead to biased results in statistical studies, such as the distribution of galaxy luminosity, mass, or star formation rates.
+Additionally, missing galaxies, especially those at faint magnitudes or large distances, can distort cosmological measurements and hinder our understanding of galaxy formation and evolution.
+
+Completeness checks are crucial for addressing selection biases, ensuring accurate redshift distributions, and validating galaxy simulations.
+They help identify gaps in the data and guide follow-up observations, ensuring that the catalog provides a reliable sample for scientific analysis.
+Without these checks, conclusions drawn from the data may be inaccurate or incomplete.
+
+------------------------------------------------------------------------
+
+Checking for completeness in galaxy catalogs is essential to ensure that the data accurately represents the true population of galaxies.
+Incomplete catalogs can lead to biased results in statistical studies, such as the distribution of galaxy luminosity, mass, or star formation rates.
+Additionally, missing galaxies, especially those at faint magnitudes or large distances, can distort cosmological measurements and hinder our understanding of galaxy formation and evolution.
+Completeness checks are crucial for addressing selection biases, ensuring accurate redshift distributions, and validating galaxy simulations.
+
+Distance-based corrections are applied to mitigate these biases by adjusting for the underrepresentation of galaxies at greater distances.
+As galaxies move farther away, they become fainter and harder to detect, leading to a drop in the number of detected galaxies.
+Methods like **volume corrections** (e.g., V/Vmax) and **luminosity function-based corrections** help account for these effects by estimating the true galaxy population based on the observed sample.
+These corrections ensure that statistical analyses, even in incomplete catalogs, more accurately reflect the full galaxy population.
+
+```{python}
+#| output: asis
+# Creating a dataframe with the lengths of each table
+data = {
+    "Table": ["Inner join", "Outer join", "LCV", "HECATE", "Unique galaxies in LCV", "Unique Galaxies in Hecate"],
+    "Number of galaxies": [len(dt), len(outer), len(lcv), len(hec), len(lcv_not_hec), len(hec_not_lcv)]
+}
+
+df_lengths = pd.DataFrame(data)
+
+# Pretty print the dataframe in markdown format
+df_lengths_md = df_lengths.to_markdown(index=False)
+print(df_lengths_md)
+
+```
+
+## Completeness of the Inner join
+
+$$
+\text{Completeness (X)}=\frac{\text{(Galaxies in Inner Join)}}{\text{(Galaxies in X)}}×100\%
+$$
+
+Completeness (HECATE)= `{python} round(len(dt)/len(hec) *100)` %
+
+Completeness (LCV)= `{python} round(len(dt)/len(lcv) *100)` %
+
+## Completeness in Outer join
+
+$$
+\text{Completeness (X)}=\frac{\text{(Galaxies in Outer Join form X)}}{\text{(Galaxies in X)}}×100\%
+$$
+
+Completeness (HECATE)= `{python} round(len(hec_not_lcv)/len(hec)*100)` %
+
+Completeness (LCV)= `{python} round(len(lcv_not_hec)/len(lcv)*100)` %
+
+Combined Completeness =$\frac{\text{Total galaxies in Outer}}{\text{Unique galaxies in HECATE + LCV}}$= `{python} round(len(outer)/(len(lcv_not_hec)+(len(hec_not_lcv))) * 100)` %
+
+## Completeness of the Data
+
+```{python}
+def plot_completeness(dataset_choice="lcv", column_name="Dis", description="Distance", units=True, logx=False, logy=False, bins=0, keep_nan=False):
+    """
+    Plots histograms with KDE and displays a table of counts and percentages for each bin, 
+    based on the choice of dataset (LCV or HEC).
+
+    Parameters:
+    - dataset_choice: A string indicating which dataset to use ("lcv" or "hec")
+    - column_name: The column name in the Qtable to plot and analyze (default is "Dis")
+    - description: What to show in the title and the axis (default "Distance")
+    - units: Show units or not (default is True)
+    - logx: logarithmic x-axis (default is False)
+    - logy: logarithmic y-axis (default is False)
+    - bins: Number of bins or custom bin edges (default is 'auto')
+    - keep_nan: keep (True) or remove NaN's (default is True)
+    """
+
+    if dataset_choice == "lcv":
+        main_df, unique_df, label = lcv, lcv_not_hec, "LCV"
+    elif dataset_choice == "hec" and hec is not None and hec_not_lcv is not None:
+        main_df, unique_df, label = hec, hec_not_lcv, "HECATE"
+    else:
+        raise ValueError("Invalid dataset choice. Please choose 'lcv' or 'hec' with valid datasets.")
+
+# Remove NaN values and strip units before plotting
+    if not keep_nan:
+        main_data_clean = main_df[column_name].value.filled(np.nan)
+        main_data_clean = main_data_clean[~np.isnan(main_data_clean)]
+
+        unique_data_clean = unique_df[column_name].value.filled(np.nan)
+        unique_data_clean = unique_data_clean[~np.isnan(unique_data_clean)]
+    else:
+        main_data_clean = main_df[column_name].value.filled(np.nan)
+        unique_data_clean = unique_df[column_name].value.filled(np.nan)
+
+    # Check if bins is an integer or array of bin edges
+    if bins == 0:
+        counts, bin_edges = np.histogram(main_data_clean, bins='auto')
+    elif isinstance(bins, int):
+        counts, bin_edges = np.histogram(main_data_clean, bins=bins)
+    else:
+        bin_edges = bins  # If bins is an array of bin edges
+
+    # Plot the histograms
+    sns.histplot(main_data_clean.data, bins=bin_edges, kde=True, label=label)
+    sns.histplot(unique_data_clean.data, bins=bin_edges, kde=True, label=f"Unique for {label}")
+
+    # Set logarithmic axes if requested
+    if logx:
+        plt.xscale('log')
+    if logy:
+        plt.yscale('log')
+
+    # Set the title and labels
+    plt.title(f"Completeness of {description} for {label}")
+    if units and main_df[column_name].unit is not None:
+        plt.xlabel(f"{description} [{main_df[column_name].unit}]")
+    else:
+        plt.xlabel(f"{description}")
+    plt.ylabel("Number of galaxies")
+    plt.legend()
+
+    # Calculate histogram counts for each dataset
+    main_counts, _ = np.histogram(main_data_clean, bins=bin_edges)
+    unique_counts, _ = np.histogram(unique_data_clean, bins=bin_edges)
+
+    # Calculate bin centers for annotation
+    bin_centers = 0.5 * (bin_edges[1:] + bin_edges[:-1])
+
+    # Annotate percentages on the bars
+    for i, center in enumerate(bin_centers):
+        if main_counts[i] > 0:
+            unique_pct = (unique_counts[i] / main_counts[i]) * 100
+            plt.text(center, unique_counts[i], f'{unique_pct:.1f}%', color="green", ha='center', va='bottom')
+
+    # Show the plot
+    plt.show()
+    plt.close()
+
+```
+
+```{python}
+def table_completeness(dataset_choice, column_name="Dis", description = "Distance", keep_nan = False):
+    """
+    Creates a table of counts and percentages for each bin based on the chosen dataset (LCV or HEC).
+
+    Parameters:
+    - dataset_choice: A string indicating which dataset to use ("lcv" or "hec")
+    - column_name: The column name in the datasets to analyze (default is "Dis")
+    - description: what to show in the title and the axis (default "Distance")
+    """
+
+    if dataset_choice == "lcv":
+        main_df, unique_df, label = lcv, lcv_not_hec, "LCV"
+    elif dataset_choice == "hec" and hec is not None and hec_not_lcv is not None:
+        main_df, unique_df, label = hec, hec_not_lcv, "HEC"
+    else:
+        raise ValueError("Invalid dataset choice. Please choose 'lcv' or 'hec' with valid datasets.")
+
+    # Remove NaN values before plotting
+    if keep_nan == False:
+        main_df = main_df[~np.isnan(main_df[column_name].data)]
+        unique_df = unique_df[~np.isnan(unique_df[column_name].data)]
+    else:
+        main_df = main_df[column_name].data
+        unique_dF = unique_df[column_name].data
+    counts, bin_edges = np.histogram(main_df[column_name].data, bins='auto')
+
+    main_counts, _ = np.histogram(main_df[column_name].data, bins=bin_edges)
+    unique_counts, _ = np.histogram(unique_df[column_name].data, bins=bin_edges)
+    inner_counts, _ = np.histogram(inner[column_name].data, bins=bin_edges)
+
+    bin_centers = 0.5 * (bin_edges[1:] + bin_edges[:-1])
+    table_data = []
+
+    for i in range(len(bin_centers)):
+        if main_counts[i] > 0:
+            unique_pct = (unique_counts[i] / main_counts[i]) * 100
+            inner_pct = (inner_counts[i] / main_counts[i]) * 100
+            table_data.append({
+                "Bin Start": round(bin_edges[i]),
+                "Bin End": round(bin_edges[i+1]),
+                f"Unique %": f'{unique_pct:.0f}%',
+                "Inner %": f'{inner_pct:.0f}%'
+            })
+    table_df = pd.DataFrame(table_data)
+    return table_df
+```
+
+### Distance
+
+```{python}
+#| fig-cap: "Histograms showing the Distance Completeness of the Catalogs"
+#| layout-ncol: 2
+#| fig-subcap: 
+#| - "HECATE"
+#| - "LCV"
+#| label: fig-dis-comp
+
+plot_completeness("hec", column_name = "D", description = "Distance", keep_nan = True)
+plot_completeness("lcv",keep_nan = True)
+```
+```{python}
+#| label: tbl-dis-comp
+#| tbl-cap: "Table showing the Completeness of the Catalogs, per bin"
+#| layout-ncol: 2
+#| tbl-subcap: 
+#| - "HECATE"
+#| - "LCV"
+table_completeness("hec", column_name = "D", description = "Distance")
+
+table_completeness("lcv")
+```
+
+### Type
+
+```{python}
+#| layout-ncol: 2
+#| fig-cap: "Histograms showing the Type Completeness of the Catalogs"
+#| fig-subcap: 
+#| - "HECATE"
+#| - "LCV"
+#| label: fig-type-comp
+plt.close()
+plot_completeness("hec", column_name = "T", description = "Type", units = False)
+plot_completeness("lcv", column_name = "TType", description = "Type", units = False, bins = 12)
+```
+
+As we can see from the histograms @fig-dis-comp and @fig-type-comp the sample of unique galaxies of each catalog, gets smaller by an almost constant proportion (Inner join).
+
+This means there is no bias in the selection of the galaxies.
+
+### Helocentric Radial Velocities
+
+```{python}
+#| layout-ncol: 2
+#| fig-cap: "Histograms showing the Velocity Completeness of the Catalogs"
+#| fig-subcap: 
+#| - "HECATE"
+#| - "LCV"
+#| label: fig-type-comp
+plt.close()
+plot_completeness("hec", column_name = "V", description = "Velocities", keep_nan = True, logx = True)
+plot_completeness("lcv", column_name = "RVel", description = "Velocities",keep_nan = True)
+```
+
+```{python}
+
+```
+
+### Luminosities
+
+```{python}
+#| layout-ncol: 2
+#| fig-cap: "Histograms showing the $L_K$ Completeness of the Catalogs"
+#| fig-subcap: 
+#| - "HECATE"
+#| - "LCV"
+#| label: fig-type-comp
+plt.close()
+plot_completeness("hec", column_name = "logL_K", description = "$log_{10}(L_K)$", units = False,keep_nan = False, bins = 0)
+plot_completeness("lcv", column_name = "logKLum", description = "$log_{10}(L_K)$",units=False,keep_nan = False)
+```
+
+```{python}
+# Plot the histograms
+plt.close()
+sns.histplot(hec_not_lcv["logL_K"], kde=True, label = "afd")
+sns.histplot(hec["logL_K"], kde=True, label=f"Unique for")
+plt.legend()
+plt.show()
+plt.close()
+```
+
+```{python}
+sns.scatterplot(table_completeness("hec", "logL_K"),x = "Bin End", y = "Unique %")
+plt.show()
+```
+
+### Magnitudes
+
+### SFR
+
+### Masses
 
@@
     """
+    plt.close()
     # Convert data to masked arrays, masking NaN values
@@
     plt.show()
+    plt.close()
 ```

### 2024-09-27 compare/compare.tex
created functions for completeness (plot and table of bins)

--- 2024-09-22 compare/.ipynb_checkpoints/compare-checkpoint.tex
@@
 
-\caption{\label{fig-dis-comp}Histograms showing the Completeness of the
-Catalogs}
+\caption{\label{fig-dis-comp}Histograms showing the Distance
+Completeness of the Catalogs}
 
 \end{figure}%
+
+\begin{table}
+
+\caption{\label{tbl-dis-comp}Table showing the Completeness of the
+Catalogs, per bin}
+
+\begin{minipage}{0.50\linewidth}
+
+\subcaption{\label{tbl-dis-comp-1}HECATE}
+
+\centering{
+
+\begin{tabular}{rrll}
+\toprule
+Bin Start & Bin End & Unique \% & Inner \%\\
+\midrule
+0 & 0 & 43\% & 57\%\\
+0 & 1 & 93\% & 7\%\\
+1 & 1 & 95\% & 5\%\\
+1 & 2 & 98\% & 2\%\\
+2 & 2 & 98\% & 2\%\\
+2 & 2 & 95\% & 5\%\\
+2 & 3 & 98\% & 2\%\\
+3 & 3 & 96\% & 4\%\\
+3 & 4 & 96\% & 4\%\\
+4 & 4 & 95\% & 5\%\\
+4 & 4 & 96\% & 4\%\\
+4 & 5 & 90\% & 10\%\\
+5 & 5 & 81\% & 19\%\\
+5 & 6 & 86\% & 14\%\\
+6 & 6 & 62\% & 38\%\\
+6 & 6 & 58\% & 42\%\\
+6 & 7 & 74\% & 26\%\\
+7 & 7 & 71\% & 29\%\\
+7 & 7 & 62\% & 38\%\\
+7 & 8 & 64\% & 36\%\\
+8 & 8 & 52\% & 48\%\\
+8 & 9 & 71\% & 29\%\\
+9 & 9 & 69\% & 31\%\\
+9 & 9 & 77\% & 23\%\\
+9 & 10 & 75\% & 25\%\\
+10 & 10 & 73\% & 27\%\\
+10 & 11 & 73\% & 27\%\\
+11 & 11 & 83\% & 17\%\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{minipage}%
+%
+\begin{minipage}{0.50\linewidth}
+
+\subcaption{\label{tbl-dis-comp-2}LCV}
+
+\centering{
+
+\begin{tabular}{rrll}
+\toprule
+Bin Start & Bin End & Unique \% & Inner \%\\
+\midrule
+0 & 1 & 68\% & 32\%\\
+1 & 2 & 50\% & 50\%\\
+2 & 3 & 67\% & 33\%\\
+3 & 4 & 80\% & 20\%\\
+4 & 5 & 85\% & 15\%\\
+5 & 6 & 79\% & 21\%\\
+6 & 6 & 73\% & 27\%\\
+6 & 7 & 83\% & 17\%\\
+7 & 8 & 74\% & 26\%\\
+8 & 9 & 72\% & 28\%\\
+9 & 10 & 85\% & 15\%\\
+10 & 11 & 78\% & 22\%\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{minipage}%
+
+\end{table}%
 
@@
 
-\caption{\label{fig-type-comp}Histograms showing the Completeness of the
-Catalogs}
-
-\end{figure}%
-
-\begin{figure}
-
-\begin{minipage}{0.50\linewidth}
-
-\begin{longtable}[]{@{}rr@{}}
-\toprule\noalign{}
-Value & Count \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
--3 & 138 \\
--2 & 224 \\
--1 & 119 \\
-0 & 4 \\
-1 & 7 \\
-2 & 2 \\
-3 & 8 \\
-4 & 9 \\
-5 & 7 \\
-6 & 24 \\
-7 & 31 \\
-8 & 86 \\
-9 & 166 \\
-10 & 484 \\
-11 & 4 \\
-\end{longtable}
-
-\end{minipage}%
-%
-\begin{minipage}{0.50\linewidth}
-
-\begin{longtable}[]{@{}rr@{}}
-\toprule\noalign{}
-Value & Count \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
--5 & 52 \\
--4.9 & 7 \\
--4.8 & 13 \\
--4.7 & 2 \\
--4.3 & 2 \\
--4 & 3 \\
--3.9 & 1 \\
--3.7 & 1 \\
--3.5 & 3 \\
--3.3 & 1 \\
--3.1 & 1 \\
--3 & 11 \\
--2.9 & 3 \\
--2.8 & 3 \\
--2.7 & 3 \\
--2.6 & 5 \\
--2.5 & 1 \\
--2.1 & 2 \\
--2 & 3 \\
--1.9 & 1 \\
--1.8 & 3 \\
--1.7 & 1 \\
--1.6 & 1 \\
--1.3 & 2 \\
--1 & 8 \\
--0.8 & 1 \\
--0.4 & 2 \\
--0.1 & 1 \\
-0 & 3 \\
-0.1 & 1 \\
-0.4 & 1 \\
-0.5 & 1 \\
-0.6 & 1 \\
-1 & 5 \\
-1.1 & 2 \\
-1.2 & 1 \\
-1.3 & 1 \\
-1.5 & 2 \\
-1.6 & 2 \\
-1.8 & 1 \\
-1.9 & 2 \\
-2.1 & 1 \\
-2.2 & 2 \\
-2.3 & 1 \\
-2.4 & 3 \\
-2.5 & 1 \\
-2.6 & 1 \\
-2.7 & 1 \\
-2.9 & 1 \\
-3 & 3 \\
-3.1 & 4 \\
-3.2 & 1 \\
-3.3 & 6 \\
-3.4 & 3 \\
-3.5 & 2 \\
-3.6 & 2 \\
-3.8 & 2 \\
-3.9 & 2 \\
-4 & 13 \\
-4.1 & 1 \\
-4.2 & 2 \\
-4.4 & 2 \\
-4.5 & 1 \\
-4.7 & 1 \\
-4.8 & 1 \\
-5 & 21 \\
-5.1 & 5 \\
-5.2 & 5 \\
-5.3 & 1 \\
-5.4 & 3 \\
-5.5 & 1 \\
-5.7 & 1 \\
-5.8 & 2 \\
-5.9 & 9 \\
-6 & 13 \\
-6.1 & 7 \\
-6.4 & 1 \\
-6.5 & 2 \\
-6.7 & 3 \\
-6.8 & 2 \\
-6.9 & 5 \\
-7 & 11 \\
-7.1 & 1 \\
-7.2 & 2 \\
-7.3 & 1 \\
-7.4 & 2 \\
-7.5 & 4 \\
-7.6 & 1 \\
-7.7 & 3 \\
-7.8 & 6 \\
-7.9 & 9 \\
-8 & 19 \\
-8.1 & 4 \\
-8.2 & 3 \\
-8.3 & 5 \\
-8.4 & 2 \\
-8.5 & 4 \\
-8.6 & 5 \\
-8.7 & 6 \\
-8.8 & 9 \\
-8.9 & 15 \\
-9 & 29 \\
-9.1 & 4 \\
-9.2 & 4 \\
-9.3 & 2 \\
-9.4 & 4 \\
-9.5 & 13 \\
-9.6 & 4 \\
-9.7 & 17 \\
-9.8 & 48 \\
-9.9 & 90 \\
-10 & 203 \\
-\end{longtable}
-
-\end{minipage}%
+\caption{\label{fig-type-comp}Histograms showing the Type Completeness
+of the Catalogs}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-12-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-14-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-13-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-15-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-14-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-16-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-16-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-18-output-1.pdf}
 
-\includegraphics{compare_files/figure-pdf/cell-18-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-20-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-21-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-23-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-22-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-24-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-25-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-27-output-1.pdf}
 
-\includegraphics{compare_files/figure-pdf/cell-26-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-28-output-1.pdf}
 
-\includegraphics{compare_files/figure-pdf/cell-27-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-29-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-28-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-30-output-1.pdf}
 
-\includegraphics{compare_files/figure-pdf/cell-28-output-2.pdf}
+\includegraphics{compare_files/figure-pdf/cell-30-output-2.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-29-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-31-output-1.pdf}
 
@@
 
-\begin{verbatim}
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  5 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  5 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  5 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  5 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  5 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  5 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  5 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  5 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  5 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  5 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
- ** On entry to DLASCL parameter number  4 had an illegal value
-\end{verbatim}
-
-\includegraphics{compare_files/figure-pdf/cell-31-output-2.pdf}
+\includegraphics{compare_files/figure-pdf/cell-33-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-33-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-35-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-37-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-39-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-38-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-40-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-40-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-42-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-42-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-44-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-44-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-46-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-47-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-49-output-1.pdf}
 

### 2024-09-30 compare/compare.qmd
completeness notes+rm percent_hist

@@
 from astropy.visualization import quantity_support, hist
+import scipy
 #quantity_support()
@@
 
-Completeness checks are crucial for addressing selection biases, ensuring accurate redshift distributions, and validating galaxy simulations.
-They help identify gaps in the data and guide follow-up observations, ensuring that the catalog provides a reliable sample for scientific analysis.
+Completeness checks are crucial for addressing selection biases, identify gaps in the data and guide follow-up observations, ensuring that the catalog provides a reliable sample for scientific analysis.
 Without these checks, conclusions drawn from the data may be inaccurate or incomplete.
 
-------------------------------------------------------------------------
-
-Checking for completeness in galaxy catalogs is essential to ensure that the data accurately represents the true population of galaxies.
-Incomplete catalogs can lead to biased results in statistical studies, such as the distribution of galaxy luminosity, mass, or star formation rates.
-Additionally, missing galaxies, especially those at faint magnitudes or large distances, can distort cosmological measurements and hinder our understanding of galaxy formation and evolution.
-Completeness checks are crucial for addressing selection biases, ensuring accurate redshift distributions, and validating galaxy simulations.
-
-Distance-based corrections are applied to mitigate these biases by adjusting for the underrepresentation of galaxies at greater distances.
-As galaxies move farther away, they become fainter and harder to detect, leading to a drop in the number of detected galaxies.
-Methods like **volume corrections** (e.g., V/Vmax) and **luminosity function-based corrections** help account for these effects by estimating the true galaxy population based on the observed sample.
-These corrections ensure that statistical analyses, even in incomplete catalogs, more accurately reflect the full galaxy population.
+## Completeness of the LCV Catalog
+
+The local volume selection has been made by taking into account galaxies with: 1. Radial velocities of $$
+    V_{LG}<600 \text{ km}\cdot\text{m}^{-1}
+    $$ {#eq-lcv-vel} 2. Distances of D\<11 Mpc
+
+A simultaneous fulfillment of both conditions (1) and (2) is not required.
+
+-   Completeness within a 10 Mpc radius is difficult to assess due to:
+    -   Variability in galaxy properties (luminosity, size, surface brightness, gas content)
+    -   Errors in distance measurements (Tully–Fisher method errors of \~20–25%), especially at the 10 Mpc boundary.
+        -   Accurate distances are mainly known within \~5 Mpc.
+    -   Non-Hubble motions (\~300 km/s) may make up half of the adopted velocity constraint @eq-lcv-vel
+        -   Solution for our usage: only keep the galaxies inside a radius of $D=11 Mpc$
+        -   HI sources in surveys with low angular resolution: "The presence around our Galaxy of hundreds of high-velocity clouds with low line-of-sight velocities and small W50 widths also provokes the inclusion of false “nearby” dwarf galaxies in the LV"@karachentsevUPDATEDNEARBYGALAXY2013
+        -   photographic emulsion defect -\> exotic cases of galaxies -\> radial velocity of $+614 km s^{−1}$
+-   Astro-Spam and Survey Errors:
+    -   Automatic surveys produce false detections (e.g., stars misclassified as galaxies, high-velocity clouds mistaken for dwarfs).
+-   Conditional Completeness Estimate:
+    -   Galaxies brighter than $M_B^c = -11^m$ or with linear diameters larger than $A_{26} = 1.0$ kpc show (40–60)% completeness.
+    -   "among the members of the Local Group (D \< 1 Mpc), only half of the galaxies have absolute magnitudes brighter than −11m.
+Consequently, more than half of the ultra-faint dwarf companions around normal galaxies, like the Sombrero galaxy (D = 9.3 Mpc), still remain outside our field of view."
+-   Undetected Ultra-Faint Dwarfs:
+    -   Many faint dwarf galaxies remain undetected beyond the Local Group. Estimated population of undetected dwarfs could be as large as $10^3–10^4$ within the LV.
+-   Surface Brightness Distribution:
+    -   Surface brightness remains consistent across distances, except for ultra-faint dwarfs ($SB <31 \text{mag}\cdot\text{arcsec}^{-2}$).
+    -   Faintest dwarf galaxies are detectable only nearby due to their resolution into individual stars.
+-   Luminosity-Size Relationship:
+    -   Observations align with cosmological models predicting $L\sim A^3$ @navarroStructureColdDark1996, though deviations occur for extremely low surface brightness galaxies.
+    -   "The deviation from it at the extremely low surface brightness end is due to a systematic overestimation of dwarf galaxy sizes, the brightness profiles of which lie entirely below the Holmberg isophote."
+
+## Completeness of HECATE
+
+The completeness of HECATE is difficult to assess due to: - Unknown selection function of HyperLEDA and selection effects from other cross-correlated catalogs.
+- Estimation based on comparing B-band luminosity distribution with the galaxy luminosity function (LF).
+
+-   HECATE is:
+
+    -   Complete down to $L_B\sim 10^{9.5} L_{B,\odot}$ for distances less than 33 Mpc.
+
+    -   Complete down to $L_B\sim 10^{10} L_{B,\odot}$ for distances between 67 Mpc and 100 Mpc.
+
+    -   Incomplete at distances greater than 167 Mpc, even for the brightest galaxies.
+
+-   Completeness estimates based on B-band luminosity density:
+
+    -   \>75% complete for distances less than 100 Mpc. $\sim 50\%$ complete at distances of $\sim170$ Mpc.
+
+    -   Completeness exceeds 100% within 30 Mpc due to the overdensity of galaxies around the Milky Way.
+
+-   Completeness in terms of stellar mass (M\*):
+
+    -   Similar to B-band completeness when measured with $K_s$-band luminosity as a tracer for stellar mass.
+
+    -   Overdensity at small distances and cut-off at large distances are observed.
+
+-   Completeness in terms of star formation rate (SFR):
+
+    -   \~50% complete between 30 and 150 Mpc.
+
+    -   Lower SFR completeness due to limitations in WISE-based SFR estimates, which lack full sky coverage.
+
+    -   Despite IRAS’s limited depth, it provides \>50% coverage for star-forming galaxies in the local neighborhood.
+
+    -   HECATE's nonuniform SFR and stellar mass coverage, affecting the reliability of stellar population parameters.
+
+In this section we will check the completeness
 
@@
 
-# Remove NaN values and strip units before plotting
+    # Remove NaN values before plotting
     if not keep_nan:
-        main_data_clean = main_df[column_name].value.filled(np.nan)
-        main_data_clean = main_data_clean[~np.isnan(main_data_clean)]
-
-        unique_data_clean = unique_df[column_name].value.filled(np.nan)
-        unique_data_clean = unique_data_clean[~np.isnan(unique_data_clean)]
+        main_data_clean = main_df[~np.isnan(main_df[column_name].data)].data
+        unique_ddata_clean = unique_df[~np.isnan(unique_df[column_name].data)]
     else:
-        main_data_clean = main_df[column_name].value.filled(np.nan)
-        unique_data_clean = unique_df[column_name].value.filled(np.nan)
+        main_data_clean = main_df[column_name].data
+        unique_data_clean = unique_df[column_name].data
 
@@
     # Plot the histograms
-    sns.histplot(main_data_clean.data, bins=bin_edges, kde=True, label=label)
-    sns.histplot(unique_data_clean.data, bins=bin_edges, kde=True, label=f"Unique for {label}")
+    sns.histplot(main_data_clean, bins=bin_edges, kde=True, label=label)
+    sns.histplot(unique_data_clean, bins=bin_edges, kde=True, label=f"Unique for {label}")
 
@@
         main_df = main_df[column_name].data
-        unique_dF = unique_df[column_name].data
+        unique_df = unique_df[column_name].data
     counts, bin_edges = np.histogram(main_df[column_name].data, bins='auto')
@@
 
-plot_completeness("hec", column_name = "D", description = "Distance", keep_nan = True)
-plot_completeness("lcv",keep_nan = True)
-```
-```{python}
-#| label: tbl-dis-comp
-#| tbl-cap: "Table showing the Completeness of the Catalogs, per bin"
+#HECATE
+
+main = hec["D"].data
+unique = hec_not_lcv["D"].data
+counts, bin_edges = np.histogram(main)
+
+main_counts, _ = np.histogram(main, bins=bin_edges)
+unique_counts, _ = np.histogram(unique, bins=bin_edges)
+
+plt.subplot(2,1,1)
+sns.histplot(main, bins = bin_edges, kde = True, label = "HECATE")
+sns.histplot(unique, bins = bin_edges, kde = True, label = "Unique for HECATE")
+plt.legend()
+plt.title("Completenes of Distance for HECATE")
+unique_pct = (unique_counts/main_counts)*100 
+###
+plt.subplot(2,1,2)
+ax = sns.lineplot(x = bin_edges[1:], y = unique_pct)
+ax.set(xlabel='xlabel', ylabel='ylabel', title='title')
+
+#changing ylables ticks
+plt.yticks(np.arange(min(unique_pct), max(unique_pct)+1, 5.0))
+y_value=['{:,.0f}'.format(x) + '%' for x in ax.get_yticks()]
+ax.set_yticklabels(y_value)
+plt.ylabel("Completeness %")
+plt.xlabel("Distance [{}]".format(hec["D"].unit))
+plt.title("")
+plt.show()
+
+#LCV
+main = lcv["Dis"].data
+unique = lcv_not_hec["Dis"].data
+counts, bin_edges = np.histogram(main)
+
+main_counts, _ = np.histogram(main, bins=bin_edges)
+unique_counts, _ = np.histogram(unique, bins=bin_edges)
+
+plt.subplot(2,1,1)
+sns.histplot(main, bins = bin_edges, kde = True, label = "LCV")
+sns.histplot(unique, bins = bin_edges, kde = True, label = "Unique for LCV")
+plt.legend()
+plt.title("Completenes of Distance for LCV")
+unique_pct = (unique_counts/main_counts)*100 
+###
+plt.subplot(2,1,2)
+ax = sns.lineplot(x = bin_edges[1:], y = unique_pct)
+ax.set(xlabel='xlabel', ylabel='ylabel', title='title')
+
+#changing ylables ticks
+plt.yticks(np.arange(min(unique_pct), max(unique_pct)+1, 5.0))
+y_value=['{:,.0f}'.format(x) + '%' for x in ax.get_yticks()]
+ax.set_yticklabels(y_value)
+
+plt.ylabel("Completeness %")
+plt.xlabel("Distance [{}]".format(lcv["Dis"].unit))
+plt.title("")
+plt.show()
+
+plt.close()
+```
+
+```{python}
+#| fig-cap: "Histograms showing the Type Completeness of the Catalogs"
 #| layout-ncol: 2
-#| tbl-subcap: 
-#| - "HECATE"
-#| - "LCV"
-table_completeness("hec", column_name = "D", description = "Distance")
-
-table_completeness("lcv")
-```
-
-### Type
-
-```{python}
-#| layout-ncol: 2
-#| fig-cap: "Histograms showing the Type Completeness of the Catalogs"
 #| fig-subcap: 
@@
 #| label: fig-type-comp
-plt.close()
-plot_completeness("hec", column_name = "T", description = "Type", units = False)
-plot_completeness("lcv", column_name = "TType", description = "Type", units = False, bins = 12)
+main = hec["T"].data
+main = main[~np.isnan(main)]
+unique = hec_not_lcv["T"].data
+unique = unique[~np.isnan(unique)]
+counts, bin_edges = np.histogram(main, bins = 12)
+
+main_counts, _ = np.histogram(main, bins=bin_edges)
+unique_counts, _ = np.histogram(unique, bins=bin_edges)
+
+plt.subplot(2,1,1)
+sns.histplot(main, bins = bin_edges, kde = True, label = "HECATE")
+sns.histplot(unique, bins = bin_edges, kde = True, label = "Unique for HECATE")
+plt.legend()
+plt.title("Completenes of Types for HECATE")
+unique_pct = (unique_counts/main_counts)*100 
+###
+plt.subplot(2,1,2)
+ax = sns.lineplot(x = bin_edges[1:], y = unique_pct)
+ax.set(xlabel='xlabel', ylabel='ylabel', title='title')
+
+#changing ylables ticks
+plt.yticks(np.arange(min(unique_pct), max(unique_pct)+1, 5.0))
+y_value=['{:,.0f}'.format(x) + '%' for x in ax.get_yticks()]
+ax.set_yticklabels(y_value)
+plt.ylabel("Completeness %")
+plt.xlabel("Types of galaxies")
+plt.title("")
+plt.show()
+
+#LCV
+main = lcv["TType"].data
+main = main[~np.isnan(main)]
+unique = lcv_not_hec["TType"].data
+unique = unique[~np.isnan(unique)]
+counts, bin_edges = np.histogram(main)
+
+main_counts, _ = np.histogram(main, bins=bin_edges)
+unique_counts, _ = np.histogram(unique, bins=bin_edges)
+
+plt.subplot(2,1,1)
+sns.histplot(main, bins = bin_edges, kde = True, label = "LCV")
+sns.histplot(unique, bins = bin_edges, kde = True, label = "Unique for LCV")
+plt.legend()
+plt.title("Completenes of Distance for LCV")
+unique_pct = (unique_counts/main_counts)*100
+
+plt.subplot(2,1,2)
+ax = sns.lineplot(x = bin_edges[1:] ,y = unique_pct)
+ax.set(xlabel='xlabel', ylabel='ylabel', title='title')
+
+#changing ylables ticks
+plt.yticks(np.arange(min(unique_pct), max(unique_pct)+1, 10.0))
+y_value=['{:,.0f}'.format(x) + '%' for x in ax.get_yticks()]
+ax.set_yticklabels(y_value)
+
+plt.ylabel("Completeness %")
+plt.xlabel("Types of galaxies")
+plt.title("")
+plt.show()
 ```
@@
 This means there is no bias in the selection of the galaxies.
-
-### Helocentric Radial Velocities
-
-```{python}
-#| layout-ncol: 2
-#| fig-cap: "Histograms showing the Velocity Completeness of the Catalogs"
-#| fig-subcap: 
-#| - "HECATE"
-#| - "LCV"
-#| label: fig-type-comp
-plt.close()
-plot_completeness("hec", column_name = "V", description = "Velocities", keep_nan = True, logx = True)
-plot_completeness("lcv", column_name = "RVel", description = "Velocities",keep_nan = True)
-```
-
-```{python}
-
-```
-
-### Luminosities
-
-```{python}
-#| layout-ncol: 2
-#| fig-cap: "Histograms showing the $L_K$ Completeness of the Catalogs"
-#| fig-subcap: 
-#| - "HECATE"
-#| - "LCV"
-#| label: fig-type-comp
-plt.close()
-plot_completeness("hec", column_name = "logL_K", description = "$log_{10}(L_K)$", units = False,keep_nan = False, bins = 0)
-plot_completeness("lcv", column_name = "logKLum", description = "$log_{10}(L_K)$",units=False,keep_nan = False)
-```
-
-```{python}
-# Plot the histograms
-plt.close()
-sns.histplot(hec_not_lcv["logL_K"], kde=True, label = "afd")
-sns.histplot(hec["logL_K"], kde=True, label=f"Unique for")
-plt.legend()
-plt.show()
-plt.close()
-```
-
-```{python}
-sns.scatterplot(table_completeness("hec", "logL_K"),x = "Bin End", y = "Unique %")
-plt.show()
-```
-
-### Magnitudes
-
-### SFR
-
-### Masses
 
@@
     return diff
-
-def percent_desc_histogram(x, sigmaclip = True, zoom = None):
-    """
-    This function creates a histogram of the given data and optionally applies a 3-sigma clip.
-
-    Parameters:
-    - x (array-like): The input data to create the histogram.
-    - sigmaclip (bool, optional): Whether to apply a 3-sigma clip to the data. Default is True.
-    - zoom (tuple, optional): The range of values to display on the x-axis of the histogram. Default is None.
-
-    Returns:
-    - t_pd (DataFrame): A pandas DataFrame containing statistical information about the input data.
-
-    The function uses the seaborn library to create the histogram and applies a 3-sigma clip if `sigmaclip` is True.
-    The histogram is displayed with appropriate labels and titles.
-    The statistical information about the input data is returned as a pandas DataFrame.
-    """
-    plt.close()
-    temp_table = QTable()
-    temp_table["Percentage change [%]"]= x.copy()
-
-    if sigmaclip is True:
-        temp_table["Percentage change [%], after 3 sigma clip"] = sigma_clip(temp_table["Percentage change [%]"],3)
-
-    t_pd = temp_table.to_pandas()
-
-    sns.histplot(temp_table["Percentage change [%]"], kde = True, label = "Percentage change [%]")
-
-    if sigmaclip is True:
-        sns.histplot(temp_table["Percentage change [%], after 3 sigma clip"], kde = True, label = "Percentage change [%], after 3 sigma clip")
-
-    plt.xlim(zoom)
-    plt.xlabel("Percentage change Distribution [%]")
-    plt.title("Types of Galaxies")
-    plt.legend()
-    plt.show()
-
-    return t_pd.describe(percentiles=[]).map('{:,.0f}'.format).style.set_properties(**{'text-align': 'center'})
 ```
@@
 
-**Percentage change:**
-
-```{python}
-
-dt["diff_T"] = relative_diff(hec = dt["T"], lcv = dt["TType"])
-percent_desc_histogram(dt["diff_T"], zoom = [-200,200])
-dt["diff_T_clip"] = sigma_clip(dt["diff_T"], sigma=3)
-dt[["diff_T", "diff_T_clip"]].to_pandas().describe()
-
-```
-
-\[?\] After the sigma clip we only lose 39 galaxies ($14\%$) and we can see that both the median and the mean of the percentage change are close to $0\%$.This is why we can assume that the Types of the galaxies are the same for the two catalogs
-
-#### Normalize the scale of galaxy types
+"Morphological type of galaxy in the numerical code according to the classification by de Vaucouleurs et al.
+(1991).
+It should be noted that about three quarters of objects in the LV are dwarf galaxies, which require a more detailed morphological classification.
+For example, dwarf spheroidal galaxies and normal ellipticals are usually denoted by the same numerical code T \< 0, although their physical properties drastically differ.
+The classification problem arises as well for the “transient” type dwarf galaxies, T r, which combine the features of spheroidal (Sph) and irregular (Ir)systems.
+Due to small classification errors, such objects may “jump” from one end of the T scale to the other." @karachentsevUPDATEDNEARBYGALAXY2013
+
+-   we can assume that the galaxies from the upper left and lower right regions of the plot are classified differently because of this
+-   this might explain the large errors E_T of HECATE
+-   why we see a difference in the distribution of @fig-type-comp
+
+We can remove the "problematic" galaxies by only keeping the ones with: $$
+|{T_{HECATE}-T_{LCV}}|<7
+$$
+
+```{python}
+types = dt[["T", "TType","E_T"]]
+types["diff"] = dt["T"]-dt["TType"]
+types = types[np.abs(types["diff"])<7]
+scatter_plot(types["TType"], types["T"])
+```
+
+````{=html}
+<!-- #### Normalize the scale of galaxy types
 
@@
 types["TType_norm"] = min_max_normalize(types["TType"])
-types.describe()
+#types.describe()
 ```
@@
 ```
+-->
+````
 
@@
 ```{python}
-
+#| layout: [[50,50],[1]]
+plt.close()
 temp = dt[["inc", "INCL"]].to_pandas()
 
-sns.histplot(temp[["inc", "INCL"]], kde = True)
+sns.histplot(temp["INCL"], kde = True, label = "HECATE")
+sns.histplot(temp["inc"], kde = True, label = "LCV")
+plt.legend()
 plt.xlabel("Inclination of galaxies [deg]")
@@
 ```{python}
-#| echo: false
+#| output: false 
 #| warning: false

### 2024-09-30 compare/compare.tex
completeness notes+rm percent_hist

@@
 Completeness checks are crucial for addressing selection biases,
-ensuring accurate redshift distributions, and validating galaxy
-simulations. They help identify gaps in the data and guide follow-up
-observations, ensuring that the catalog provides a reliable sample for
-scientific analysis. Without these checks, conclusions drawn from the
-data may be inaccurate or incomplete.
+identify gaps in the data and guide follow-up observations, ensuring
+that the catalog provides a reliable sample for scientific analysis.
+Without these checks, conclusions drawn from the data may be inaccurate
+or incomplete.
 
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+\subsection{Completeness of the LCV
+Catalog}\label{completeness-of-the-lcv-catalog}
 
-Checking for completeness in galaxy catalogs is essential to ensure that
-the data accurately represents the true population of galaxies.
-Incomplete catalogs can lead to biased results in statistical studies,
-such as the distribution of galaxy luminosity, mass, or star formation
-rates. Additionally, missing galaxies, especially those at faint
-magnitudes or large distances, can distort cosmological measurements and
-hinder our understanding of galaxy formation and evolution. Completeness
-checks are crucial for addressing selection biases, ensuring accurate
-redshift distributions, and validating galaxy simulations.
+The local volume selection has been made by taking into account galaxies
+with: 1. Radial velocities of
+\begin{equation}\phantomsection\label{eq-lcv-vel}{
+    V_{LG}<600 \text{ km}\cdot\text{m}^{-1}
+    }\end{equation} 2. Distances of D\textless11 Mpc
 
-Distance-based corrections are applied to mitigate these biases by
-adjusting for the underrepresentation of galaxies at greater distances.
-As galaxies move farther away, they become fainter and harder to detect,
-leading to a drop in the number of detected galaxies. Methods like
-\textbf{volume corrections} (e.g., V/Vmax) and \textbf{luminosity
-function-based corrections} help account for these effects by estimating
-the true galaxy population based on the observed sample. These
-corrections ensure that statistical analyses, even in incomplete
-catalogs, more accurately reflect the full galaxy population.
+A simultaneous fulfillment of both conditions (1) and (2) is not
+required.
+
+\begin{itemize}
+\tightlist
+\item
+  Completeness within a 10 Mpc radius is difficult to assess due to:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Variability in galaxy properties (luminosity, size, surface
+    brightness, gas content)
+  \item
+    Errors in distance measurements (Tully--Fisher method errors of
+    \textasciitilde20--25\%), especially at the 10 Mpc boundary.
+
+    \begin{itemize}
+    \tightlist
+    \item
+      Accurate distances are mainly known within \textasciitilde5 Mpc.
+    \end{itemize}
+  \item
+    Non-Hubble motions (\textasciitilde300 km/s) may make up half of the
+    adopted velocity constraint Equation~\ref{eq-lcv-vel}
+
+    \begin{itemize}
+    \tightlist
+    \item
+      Solution for our usage: only keep the galaxies inside a radius of
+      \(D=11 Mpc\)
+    \item
+      HI sources in surveys with low angular resolution: ``The presence
+      around our Galaxy of hundreds of high-velocity clouds with low
+      line-of-sight velocities and small W50 widths also provokes the
+      inclusion of false ``nearby'' dwarf galaxies in the
+      LV''Karachentsev, Makarov, and Kaisina (2013)
+    \item
+      photographic emulsion defect -\textgreater{} exotic cases of
+      galaxies -\textgreater{} radial velocity of \(+614 km s^{−1}\)
+    \end{itemize}
+  \end{itemize}
+\item
+  Astro-Spam and Survey Errors:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Automatic surveys produce false detections (e.g., stars
+    misclassified as galaxies, high-velocity clouds mistaken for
+    dwarfs).
+  \end{itemize}
+\item
+  Conditional Completeness Estimate:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Galaxies brighter than \(M_B^c = -11^m\) or with linear diameters
+    larger than \(A_{26} = 1.0\) kpc show (40--60)\% completeness.
+  \item
+    ``among the members of the Local Group (D \textless{} 1 Mpc), only
+    half of the galaxies have absolute magnitudes brighter than −11m.
+    Consequently, more than half of the ultra-faint dwarf companions
+    around normal galaxies, like the Sombrero galaxy (D = 9.3 Mpc),
+    still remain outside our field of view.''
+  \end{itemize}
+\item
+  Undetected Ultra-Faint Dwarfs:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Many faint dwarf galaxies remain undetected beyond the Local Group.
+    Estimated population of undetected dwarfs could be as large as
+    \(10^3–10^4\) within the LV.
+  \end{itemize}
+\item
+  Surface Brightness Distribution:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Surface brightness remains consistent across distances, except for
+    ultra-faint dwarfs (\(SB <31 \text{mag}\cdot\text{arcsec}^{-2}\)).
+  \item
+    Faintest dwarf galaxies are detectable only nearby due to their
+    resolution into individual stars.
+  \end{itemize}
+\item
+  Luminosity-Size Relationship:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Observations align with cosmological models predicting \(L\sim A^3\)
+    Navarro, Frenk, and White (1996), though deviations occur for
+    extremely low surface brightness galaxies.
+  \item
+    ``The deviation from it at the extremely low surface brightness end
+    is due to a systematic overestimation of dwarf galaxy sizes, the
+    brightness profiles of which lie entirely below the Holmberg
+    isophote.''
+  \end{itemize}
+\end{itemize}
+
+\subsection{Completeness of HECATE}\label{completeness-of-hecate}
+
+The completeness of HECATE is difficult to assess due to: - Unknown
+selection function of HyperLEDA and selection effects from other
+cross-correlated catalogs. - Estimation based on comparing B-band
+luminosity distribution with the galaxy luminosity function (LF).
+
+\begin{itemize}
+\item
+  HECATE is:
+
+  \begin{itemize}
+  \item
+    Complete down to \(L_B\sim 10^{9.5} L_{B,\odot}\) for distances less
+    than 33 Mpc.
+  \item
+    Complete down to \(L_B\sim 10^{10} L_{B,\odot}\) for distances
+    between 67 Mpc and 100 Mpc.
+  \item
+    Incomplete at distances greater than 167 Mpc, even for the brightest
+    galaxies.
+  \end{itemize}
+\item
+  Completeness estimates based on B-band luminosity density:
+
+  \begin{itemize}
+  \item
+    \textgreater75\% complete for distances less than 100 Mpc.
+    \(\sim 50\%\) complete at distances of \(\sim170\) Mpc.
+  \item
+    Completeness exceeds 100\% within 30 Mpc due to the overdensity of
+    galaxies around the Milky Way.
+  \end{itemize}
+\item
+  Completeness in terms of stellar mass (M*):
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Similar to B-band completeness when measured with K\_s-band
+    luminosity as a tracer for stellar mass. Overdensity at small
+    distances and cut-off at large distances are observed.
+  \end{itemize}
+\item
+  Completeness in terms of star formation rate (SFR):
+
+  \begin{itemize}
+  \item
+    \textasciitilde50\% complete between 30 and 150 Mpc.
+  \item
+    Lower SFR completeness due to limitations in WISE-based SFR
+    estimates, which lack full sky coverage.
+  \item
+    Despite IRAS's limited depth, it provides \textgreater50\% coverage
+    for star-forming galaxies in the local neighborhood.
+  \end{itemize}
+\end{itemize}
+
+In this section we will check the completeness
 
@@
 
-\subsection{Completeness of the Catalogs, based on the Distance and the
-Morphological
-Type}\label{completeness-of-the-catalogs-based-on-the-distance-and-the-morphological-type}
+\subsection{Completeness of the Data}\label{completeness-of-the-data}
+
+\subsubsection{Distance}\label{distance}
 
@@
 \end{figure}%
-
-\begin{table}
-
-\caption{\label{tbl-dis-comp}Table showing the Completeness of the
-Catalogs, per bin}
-
-\begin{minipage}{0.50\linewidth}
-
-\subcaption{\label{tbl-dis-comp-1}HECATE}
-
-\centering{
-
-\begin{tabular}{rrll}
-\toprule
-Bin Start & Bin End & Unique \% & Inner \%\\
-\midrule
-0 & 0 & 43\% & 57\%\\
-0 & 1 & 93\% & 7\%\\
-1 & 1 & 95\% & 5\%\\
-1 & 2 & 98\% & 2\%\\
-2 & 2 & 98\% & 2\%\\
-2 & 2 & 95\% & 5\%\\
-2 & 3 & 98\% & 2\%\\
-3 & 3 & 96\% & 4\%\\
-3 & 4 & 96\% & 4\%\\
-4 & 4 & 95\% & 5\%\\
-4 & 4 & 96\% & 4\%\\
-4 & 5 & 90\% & 10\%\\
-5 & 5 & 81\% & 19\%\\
-5 & 6 & 86\% & 14\%\\
-6 & 6 & 62\% & 38\%\\
-6 & 6 & 58\% & 42\%\\
-6 & 7 & 74\% & 26\%\\
-7 & 7 & 71\% & 29\%\\
-7 & 7 & 62\% & 38\%\\
-7 & 8 & 64\% & 36\%\\
-8 & 8 & 52\% & 48\%\\
-8 & 9 & 71\% & 29\%\\
-9 & 9 & 69\% & 31\%\\
-9 & 9 & 77\% & 23\%\\
-9 & 10 & 75\% & 25\%\\
-10 & 10 & 73\% & 27\%\\
-10 & 11 & 73\% & 27\%\\
-11 & 11 & 83\% & 17\%\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{minipage}%
-%
-\begin{minipage}{0.50\linewidth}
-
-\subcaption{\label{tbl-dis-comp-2}LCV}
-
-\centering{
-
-\begin{tabular}{rrll}
-\toprule
-Bin Start & Bin End & Unique \% & Inner \%\\
-\midrule
-0 & 1 & 68\% & 32\%\\
-1 & 2 & 50\% & 50\%\\
-2 & 3 & 67\% & 33\%\\
-3 & 4 & 80\% & 20\%\\
-4 & 5 & 85\% & 15\%\\
-5 & 6 & 79\% & 21\%\\
-6 & 6 & 73\% & 27\%\\
-6 & 7 & 83\% & 17\%\\
-7 & 8 & 74\% & 26\%\\
-8 & 9 & 72\% & 28\%\\
-9 & 10 & 85\% & 15\%\\
-10 & 11 & 78\% & 22\%\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{minipage}%
-
-\end{table}%
 
@@
 As we can see from the histograms Figure~\ref{fig-dis-comp} and
-Figure~\ref{fig-type-comp} the sample of nique galaxies of each catalog,
-gets smaller by an almost constant proportion (Inner join).
+Figure~\ref{fig-type-comp} the sample of unique galaxies of each
+catalog, gets smaller by an almost constant proportion (Inner join).
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-14-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-13-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-15-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-14-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-16-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-15-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-18-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-17-output-1.pdf}
 
-\includegraphics{compare_files/figure-pdf/cell-20-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-19-output-1.pdf}
 
@@
 
+\includegraphics{compare_files/figure-pdf/cell-22-output-1.pdf}
+
+``Morphological type of galaxy in the numerical code according to the
+classification by de Vaucouleurs et al.~(1991). It should be noted that
+about three quarters of objects in the LV are dwarf galaxies, which
+require a more detailed morphological classification. For example, dwarf
+spheroidal galaxies and normal ellipticals are usually denoted by the
+same numerical code T \textless{} 0, although their physical properties
+drastically differ. The classification problem arises as well for the
+``transient'' type dwarf galaxies, T r, which combine the features of
+spheroidal (Sph) and irregular (Ir)systems. Due to small classification
+errors, such objects may ``jump'' from one end of the T scale to the
+other.'' Karachentsev, Makarov, and Kaisina (2013)
+
+\begin{itemize}
+\tightlist
+\item
+  we can assume that the galaxies from the upper left and lower right
+  regions of the plot are classified differently because of this
+\item
+  this might explain the large errors E\_T of HECATE
+\item
+  why we see a difference in the distribution of
+  Figure~\ref{fig-type-comp}
+\end{itemize}
+
+We can remove the ``problematic'' galaxies by only keeping the ones
+with: \[
+|{T_{HECATE}-T_{LCV}}|<7
+\]
+
 \includegraphics{compare_files/figure-pdf/cell-23-output-1.pdf}
-
-\textbf{Percentage change:}
-
-\includegraphics{compare_files/figure-pdf/cell-24-output-1.pdf}
-
-\begin{longtable}[]{@{}lll@{}}
-\toprule\noalign{}
-& diff\_T & diff\_T\_clip \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-count & 229 & 191 \\
-mean & -30 & -1 \\
-std & 119 & 10 \\
-min & -1000 & -39 \\
-25\% & -11 & -2 \\
-50\% & 0 & 0 \\
-75\% & 0 & 2 \\
-max & 131 & 30 \\
-\end{longtable}
-
-{[}?{]} After the sigma clip we only lose 39 galaxies (\(14\%\)) and we
-can see that both the median and the mean of the percentage change are
-close to \(0\%\).This is why we can assume that the Types of the
-galaxies are the same for the two catalogs
-
-\paragraph{Normalize the scale of galaxy
-types}\label{normalize-the-scale-of-galaxy-types}
-
-It is very possible that the two catalogs use different scaling methods,
-as indicated by the use of decimal numbers in HECATE.
-
-\begin{longtable}[]{@{}lllll@{}}
-\toprule\noalign{}
-& T & TType & T\_norm & TType\_norm \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-count & 229 & 287 & 229 & 287 \\
-mean & 7 & 7 & 1 & 1 \\
-std & 5 & 5 & 0 & 0 \\
-min & -5 & -3 & 0 & 0 \\
-25\% & 7 & 6 & 1 & 1 \\
-50\% & 10 & 9 & 1 & 1 \\
-75\% & 10 & 10 & 1 & 1 \\
-max & 10 & 10 & 1 & 1 \\
-\end{longtable}
-
-Also, as we can see the minimum values are lower by 2 in HECATE, which
-complies with the linear fit.
-
-\includegraphics{compare_files/figure-pdf/cell-27-output-1.pdf}
-
-\includegraphics{compare_files/figure-pdf/cell-28-output-1.pdf}
-
-\includegraphics{compare_files/figure-pdf/cell-29-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-30-output-1.pdf}
+\begin{figure}
 
-\includegraphics{compare_files/figure-pdf/cell-30-output-2.pdf}
+\begin{minipage}{0.50\linewidth}
+\includegraphics{compare_files/figure-pdf/cell-29-output-1.pdf}\end{minipage}%
+%
+\begin{minipage}{0.50\linewidth}
+\includegraphics{compare_files/figure-pdf/cell-29-output-2.pdf}\end{minipage}%
+\newline
+\begin{minipage}{\linewidth}
 
@@
 
+\end{minipage}%
+
+\end{figure}%
+
 We can see that for values in the range
@@
 
-\includegraphics{compare_files/figure-pdf/cell-31-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-30-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-33-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-32-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-35-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-34-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-39-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-38-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-40-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-39-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-42-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-41-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-44-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-43-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-46-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-45-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-49-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-48-output-1.pdf}
 
@@
 PROPERTIES IN THE LOCAL VOLUME GALAXIES VIA Hα AND FAR-ULTRAVIOLET
-FLUXES}.''} \emph{AJ} 146 (3): 46.
+FLUXES}.''} \emph{The Astronomical Journal} 146 (3): 46.
 \url{https://doi.org/10.1088/0004-6256/146/3/46}.
@@
 Karachentsev, Igor D., Dmitry I. Makarov, and Elena I. Kaisina. 2013.
-{``{UPDATED NEARBY GALAXY CATALOG}.''} \emph{AJ} 145 (4): 101.
-\url{https://doi.org/10.1088/0004-6256/145/4/101}.
+{``{UPDATED NEARBY GALAXY CATALOG}.''} \emph{The Astronomical Journal}
+145 (4): 101. \url{https://doi.org/10.1088/0004-6256/145/4/101}.
 
@@
 
+\bibitem[\citeproctext]{ref-navarroStructureColdDark1996}
+Navarro, Julio F., Carlos S. Frenk, and Simon D. M. White. 1996. {``The
+{Structure} of {Cold Dark Matter Halos}.''} \emph{The Astrophysical
+Journal} 462 (May): 563. \url{https://doi.org/10.1086/177173}.
+
 \end{CSLReferences}

### 2024-10-02 compare/compare.qmd
replaced scatter plot

@@
 
-The local volume selection has been made by taking into account galaxies with: 1. Radial velocities of $$
+The local volume selection has been made by taking into account galaxies with:
+
+1. Radial velocities of
+$$
     V_{LG}<600 \text{ km}\cdot\text{m}^{-1}
-    $$ {#eq-lcv-vel} 2. Distances of D\<11 Mpc
+$$ {#eq-lcv-vel}
+
+2. Distances of D\<11 Mpc
 
@@
 
-```{python}
-def scatter_plot(x, y, xerr = None, yerr = None, sigma = False, logscale = False):
-    """
-    Generates a scatter plot of two datasets with optional error bars, fits a linear model to the data, 
-    and displays the fitted line on the plot.
-
-    Parameters:
-    - x (array-like with units): Independent variable data.
-    - y (array-like with units): Dependent variable data.
-    - xerr (array-like, optional): Error in the independent variable data. Default is 0.
-    - yerr (array-like, optional): Error in the dependent variable data. Default is 0.
-
-    Returns:
-    None. The function displays a scatter plot with a fitted linear model.
-    """
-    plt.close()
-    # Convert data to masked arrays, masking NaN values
-    x_data = np.ma.array(x.value, mask=np.isnan(x.value))
-    y_data =  np.ma.array(y.value, mask=np.isnan(y.value))
-
-    # Handle default values for xerr and yerr
-    if xerr is None:
-        xerr_d = 0
-    else:
-        xerr_d = np.ma.array(xerr.value, mask=np.isnan(xerr))
-    if yerr is None:
-        yerr_d = 0
-    else:
-        yerr_d = np.ma.array(yerr.value, mask=np.isnan(yerr))
-
-    # Perform linear comparison between the datasets
-    c, m, r2, corr, outliers = compare_data(x, y, sigma)
-
-    # Plot the data with error bars
-    # errorbar -> needs np.ma -> no units
-    if outliers is not None:
-        filtered_data = np.ma.masked_array(y.value , mask = outliers)
-        outlier_percentage = (np.sum(outliers) / len(outliers)) * 100
-
-        plt.errorbar(x.value, y.value, yerr=yerr_d, c = "black", label="Clipped Data, {} ({}%)".format(np.sum(outliers), round(outlier_percentage,1)), fmt = "o", fillstyle = "none")
-        plt.scatter(x[~outliers], y[~outliers],  label=f"Fitted Data, {np.sum(~filtered_data.mask)}", c = "blue")
-
-    else:
-        plt.errorbar(x_data, y_data, xerr = xerr_d, yerr = yerr_d, alpha = 0.3, c = "blue", label = "Data", fmt = ".")
-
-    # Plot the fitted line 
-    if c!=0:
-        plt.plot(x, c*x.value+ m, c = "red", label = f"Fit: {y.info.name}$_H $= {c:.2f}$\cdot${x.info.name}$_L${m:+.2f}\n $R^2=$ {r2:.2f}")
-
-    # Set plot labels
-    plt.xlabel(f"LCV, {x.info.name} [{x.unit}]")
-    plt.ylabel(f"HECATE, {y.info.name} [{y.unit}]")
-
-    # Display legend
-    plt.legend()
-
-    # Show the plot
-    plt.show()
-    plt.close()
-```
-
 -   Histograms: Because not all of our data have the same number of counts, the comparison with histograms between data that are not the same, doesn't help us right now.[^3] This is why we will only use histograms for comparing the distribution of same-data columns normalized by their maximum value
@@
 
-```{python}
-#| echo: false
-ra_corr = round(compare_data(dt["Ra_1"],dt["RA_2"])[3],3)
-dec_corr = round(compare_data(dt["Dec_1"],dt["DEC_2"])[3],3)
-d_corr = round(compare_data(dt["Dis"],dt["D"])[3],3)
-```
-
 |  LCV  | HECATE |   Description   | Pearson Correlation \[-1,1\] |
 |:-----:|:------:|:---------------:|:----------------------------:|
-| Ra_1  |  RA_2  | Right Ascension |      `{python} ra_corr`      |
-| Dec_1 | DEC_2  |   Declination   |     `{python} dec_corr`      |
-|  Dis  |   D    |    Distance     |      `{python} d_corr`       |
-
-::: panel-tabset
-### Right Ascension
-
-```{python}
-
-scatter_plot(dt["Ra_1"], dt["RA_2"])
-```
-
-### Declination
-
-```{python}
-scatter_plot(dt["Dec_1"], dt["DEC_2"]), 
-```
-
-### Distance
-
-```{python}
-scatter_plot(dt["Dis"], dt["D"])
-```
-:::
+|  Dis  |   D    |    Distance     |      `{python} round(compare_data(dt["Dis"],dt["D"])[3],3)`       |
+
+```{python}
+#| label: fig-coord-compare 
+#| layout-align: center
+#| fig-cap: "Comparison of the Distances"
+
+plt.close()
+fig, ax = plt.subplots()
+sns.regplot(x = dt["Dis"].data, y = dt["D"].data,
+                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
+                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
+ax.errorbar(dt["Dis"].data, dt["D"].data, yerr = dt["E_D"].data, fmt='none', capsize=2, zorder=1, color = "blue", alpha = 0.3)
+results = scipy.stats.linregress(x = dt["Dis"], y=dt["D"])
+plt.xlabel("$D_{LCV}$"+" [{}]".format(dt["Dis"].unit))
+plt.ylabel("$D_{HEC}$"+" [{}]".format(dt["D"].unit))
+plt.legend(["Data",
+            "$D_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot D_{LCV}+$"+
+                f"$({results.intercept:+.2f})$"+
+            f"\n $R^2 = {results.rvalue**2*100:.0f}\%$"])
+plt.tight_layout()
+plt.show()
+```
+
+- The average error of the distance in the HECATE catalog is $\overline{E_D} = \pm 1.6$ Mpc, so the intercept is included in the error.
+- So we can assume that the Distances are the same
 
@@
 rvel_corr = round(compare_data(dt["RVel"],dt["V"])[3],3)
-rvel_corr_v = round(compare_data(dt["RVel"],dt["V_VIR"])[3],3)
-vlg_corr = round(compare_data(dt["VLG"],dt["V"])[3],3)
-vlg_corr_v = round(compare_data(dt["VLG"],dt["V_VIR"])[3],3)
-cz_corr = round(compare_data(dt["cz"],dt["V"])[3],3)
-cz_corr_v = round(compare_data(dt["cz"],dt["V_VIR"])[3],3)
 ```
@@
 ```{python}
-scatter_plot(dt["RVel"], dt["V"], yerr = dt["E_V"])
-```
+#| label: fig-vel-compare
+#| layout-align: center
+#| fig-cap: "Comparison of the Radial Velocities"
+plt.close()
+fig, ax = plt.subplots()
+sns.regplot(x = dt["RVel"].data, y = dt["V"].data,
+                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
+                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
+
+ax.errorbar(dt["RVel"].data, dt["V"].data, yerr = dt["E_V"].data, fmt='none', capsize=2, zorder=1, color = "blue")
+results = scipy.stats.linregress(x = dt["RVel"], y=dt["V"])
+plt.xlabel("$V_{LCV}$"+" [{}]".format(dt["RVel"].unit))
+plt.ylabel("$V_{HEC}$"+" [{}]".format(dt["V"].unit))
+plt.legend(["Data",
+            "$V_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot V_{LCV}+$"+
+            f"$({results.intercept:+.2f})$"+
+            f"\n $R^2 = {results.rvalue**2*100:.0f}\%$"])
+plt.show()
+```
+
+- The average error of the radial velocity in the HECATE catalog is $\overline{E_V} = \pm 12\text{km}\cdot s^{-1}$ , so the intercept is included in the error.
+- So we can assume that the radial velocities are the same
 
@@
 ```{python}
-
-scatter_plot(dt["TType"], dt["T"], yerr = dt["E_T"])
+#| label: fig-types-compare
+#| layout-ncol: 2
+#| layout-align: center
+#| fig-cap: "Comparison of the Types of galaxies"
+#| fig-subcap: 
+#| - "All the galaxies, without the correction" 
+#| - "Comparison with the correction $|{T_{HECATE}-T_{LCV}}|<7$"
+
+plt.close()
+fig, ax = plt.subplots()
+sns.regplot(x = dt["TType"].data, y = dt["T"].data,
+                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
+                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
+
+ax.errorbar(dt["TType"].data, dt["T"].data, yerr = dt["E_T"].data, fmt='none', capsize=2, zorder=1, color = "blue")
+temp = dt[["TType", "T"]].to_pandas().dropna()
+results = scipy.stats.linregress(x = temp["TType"],
+                                y = temp["T"])
+plt.xlabel("$Type_{LCV}$")
+plt.ylabel("$Type_{HEC}$")
+plt.legend(["Data",
+            "$T_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot T_{LCV}+$"+
+            f"$({results.intercept:+.2f})$"+
+            f"\n $R^2 = {results.rvalue**2*100:.0f}\%$"])
+plt.show()
+
+types = dt[["T", "TType","E_T"]]
+types["diff"] = dt["T"]-dt["TType"]
+types = types[np.abs(types["diff"])<7]
+
+plt.close()
+fig, ax = plt.subplots()
+sns.regplot(x = types["TType"].data, y = types["T"].data,
+                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
+                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
+
+ax.errorbar(types["TType"].data, types["T"].data, yerr = types["E_T"].data, fmt='none', capsize=2, zorder=1, color = "blue")
+results = scipy.stats.linregress(x= types["TType"].data,
+                                y = types["T"].data)
+plt.xlabel("$Type_{LCV}$")
+plt.ylabel("$Type_{HEC}$")
+plt.legend(["Data",
+            "$T_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot T_{LCV}+$"+
+            f"$({results.intercept:+.2f})$"+
+            f"\n $R^2 = {results.rvalue**2*100:.0f}\%$"])
+plt.show()
 ```
@@
 
-We can remove the "problematic" galaxies by only keeping the ones with: $$
+We can remove the "problematic" galaxies by only keeping the ones with: 
+$$
 |{T_{HECATE}-T_{LCV}}|<7
@@
 
-```{python}
-types = dt[["T", "TType","E_T"]]
-types["diff"] = dt["T"]-dt["TType"]
-types = types[np.abs(types["diff"])<7]
-scatter_plot(types["TType"], types["T"])
-```
-
-````{=html}
+- The average uncertainty of the morphological type in the HECATE catalog is $\overline{E_T} = \pm 1.4$, so the intercept is included in the error.
+- So we can assume that the Distances are the same
+
 <!-- #### Normalize the scale of galaxy types
@@
 ```
+TType
 
@@
 -->
-````
 
@@
 ```{python}
-#| layout: [[50,50],[1]]
+#| layout: [[50,50]]
 plt.close()
@@
 plt.show()
+```
+```{python}
 temp.describe()
@@
 ```{python}
-scatter_plot(dt["a26_1"], dt["R1"])
+#| label: fig-axis-compare
+#| layout-ncol: 2
+#| layout-align: center
+#| fig-cap: "Comparison of the Major Axises of the galaxies"
+#| fig-subcap: 
+#| - "Linear scale" 
+#| - "$log_{10}$ scale"
+plt.close()
+fig, ax = plt.subplots()
+sns.regplot(x = dt["a26_1"].data, y = dt["R1"].data,
+                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
+                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
+temp = dt[["a26_1","R1"]].to_pandas().dropna()
+results = scipy.stats.linregress(x = temp["a26_1"], y = temp["R1"])
+
+plt.xlabel("(Major angular diameter$)_{LCV}$")
+plt.ylabel("(Semi major axis$)_{HEC}$")
+plt.legend(["Data",
+            "$R1_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot a_{26,LCV}$"+
+            f"${results.intercept:+.2f}$"+
+            f"\n $R^2 = {results.rvalue**2*100:.2f}\%$"])
+plt.show()
+dt["log_a26"] = np.log10(dt["a26_1"].data)
+dt["log_R1"] = np.log10(dt["R1"].data)
+plt.close()
+fig, ax = plt.subplots()
+p = sns.regplot(x = dt["log_a26"].data, y = dt["log_R1"].data,
+                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
+                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
+
+temp = dt[["log_a26","log_R1"]].to_pandas().dropna()
+results = scipy.stats.linregress(x = temp["log_a26"], y = temp["log_R1"])
+plt.xlabel("(Major angular diameter$)_{LCV}$"+" [{}]".format(dt["a26_1"].unit))
+plt.ylabel("(Semi major axis$)_{HEC}$"+" [{}]".format(dt["R1"].unit))
+plt.legend(["Data",
+            "$log_{10}(R1_{HEC})=$" +f"{results.slope:.2f}"+"$\cdot log_{10}(a_{26,LCV})$"+
+            f"${results.intercept:+.2f}$"+
+            f"\n $R^2 = {results.rvalue**2*100:.0f}\%$"])
+plt.show()
 ```
@@
 
-```{python}
-dt["log_a26"] = np.log10(dt["a26_1"].data)
-dt["log_a26"].unit = u.arcmin
-dt["log_R1"] = np.log10(dt["R1"].data)
-dt["log_R1"].unit = u.arcmin
-```
-
-```{python}
-scatter_plot(dt["log_a26"], dt["log_R1"], sigma = True)
-```
+$\overline{R_1} = 3.9$ [arcmin],  $\overline{a_{26}} = 9.3$ [arcmin], so the intercept is negligable.
+$$
+R_1 = 0.48\cdot a_{26}-0.34 \sim \frac{1}{2}a_{26}
+$$
+
+$$
+\log(R1) = 0.89\log(a_{26})-10^{0.38} = \log(10^{-0.38}a_{26}^{0.89}) = \log(0.41\cdot a_{26}^{0.89})\Rightarrow R1\simeq \frac{a_{26}}{2}
+$$
+
 :::
@@
 | logKLum | logL_K |             |   `{python} logKLum_corr`    |
+
+```{python}
+#| label: fig-KLum-compare
+#| fig-cap: "Comparison of the $L_K$ of the galaxies"
+plt.close()
+fig, ax = plt.subplots()
+sns.regplot(x = dt["logKLum"], y = dt["logL_K"],
+                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
+                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
+temp = dt[["logKLum","logL_K"]].to_pandas().dropna()
+results = scipy.stats.linregress(x = temp["logKLum"], y = temp["logL_K"])
+plt.xlabel("log($L_{K, LCV} $"+"/{})".format(dt["KLum"].unit.to_string("latex")))
+plt.ylabel("log($L_{K, HECATE} $"+"/{})".format(dt["KLum"].unit.to_string("latex")))
+plt.legend(["Data",
+            "$log(L_{K,HEC})=$" +f"{results.slope:.2f}"+"$\cdot log(L_{K,LCV})$"+
+            f"${results.intercept:+.2f}$"+
+            f"\n $R^2 = {results.rvalue**2*100:.2f}\%$"])
+plt.show()
+```
+
+$$
+\log(L_{K,HEC})=1.16\log(L_{K,LCV})-1.78=\log\left(\frac{{L_{K,LCV}}^{1.16}}{10^{1.78}}\right) \Leftrightarrow L_{K,HEC}=0.02\cdot{L_{K,LCV}}^{1.16}
+$$
+
+So as we can see the usage of a linear fitting is not correct here.
+But we can clearly see a linear correlation.
+
+We will use the relative difference of the two luminosities, to see if statistically they are the same:
 
@@
 
-::: panel-tabset
-### B mag
-
-```{python}
-scatter_plot(dt["mag_B"], dt["BT"], yerr = dt["E_BT"], sigma=True)
-```
-
-### K mag
-
-```{python}
-scatter_plot(dt["Kmag"], dt["K"], yerr = dt["E_K"], sigma = True)
-```
+```{python}
+#| label: fig-Mag-compare
+#| layout-ncol: 2
+#| layout-align: center
+#| fig-cap: "Comparison of the Magnitudes of the galaxies"
+#| fig-subcap: 
+#| - "$M_B$" 
+#| - "$M_K$"
+#| 
+plt.close()
+fig, ax = plt.subplots()
+sns.regplot(x = dt["mag_B"].data, y = dt["BT"].data,
+                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
+                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
+ax.errorbar(dt["mag_B"].data, dt["BT"].data, xerr = dt["e_mag_B"].data, yerr = dt["E_BT"].data, fmt='none', capsize=2, zorder=1, color = "blue")
+temp = dt[["mag_B","BT"]].to_pandas().dropna()
+results = scipy.stats.linregress(x = temp["mag_B"], y = temp["BT"])
+plt.xlabel("$M_{B,LCV}$"+" [{}]".format(dt["mag_B"].unit.to_string("latex")))
+plt.ylabel("$M_{B,HECATE} $"+" [{}]".format(dt["BT"].unit.to_string("latex")))
+plt.legend(["Data",
+            "$M_{B,HEC}=$" +f"{results.slope:.2f}"+"$\cdot M_{B,LCV}$"+
+            f"${results.intercept:+.2f}$"+
+            f"\n $R^2 = {results.rvalue**2*100:.2f}\%$"])
+plt.show()
+
+#M_K
+plt.close()
+fig, ax = plt.subplots()
+sns.regplot(x = dt["Kmag"].data, y = dt["K"].data,
+                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
+                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
+ax.errorbar(dt["Kmag"].data, dt["K"].data, yerr = dt["E_K"].data, fmt='none', capsize=2, zorder=1, color = "blue")
+temp = dt[["Kmag","K"]].to_pandas().dropna()
+results = scipy.stats.linregress(x = temp["Kmag"], y = temp["K"])
+plt.xlabel("$M_{K,LCV}$"+" [{}]".format(dt["Kmag"].unit.to_string("latex")))
+plt.ylabel("$M_{K,HECATE} $"+" [{}]".format(dt["K"].unit.to_string("latex")))
+plt.legend(["Data",
+            "$M_{K,HEC}=$" +f"{results.slope:.2f}"+"$\cdot M_{K,LCV}$"+
+            f"${results.intercept:+.2f}$"+
+            f"\n $R^2 = {results.rvalue**2*100:.2f}\%$"])
+plt.show()
+```
+
+- $M_B$: it is a 1-1 correlation, since the average error $M_{B,HECATE} = 0.4\ mag$, so the itercept is smaller than the error
+- $M_K$: we need to examine it more, since the intercept is bigger than the error $M_{K,HECATE} = 0.09\ mag$
 
@@
 temp.rename(columns={"diff_K_mag":"Percentage Change [%]"}, inplace=True)
-temp.describe(percentiles=[])
 ```
@@
 plt.show()
-```
-
-\[?\]
-:::
+
+sns.histplot(dt["Kmag"].data, label = "LCV")
+sns.histplot(dt["K"].data, label = "HECATE")
+plt.legend()
+plt.xlabel(f"K band magnitude [{dt['K'].unit}]")
+plt.show()
+```
+```{python}
+temp.describe(percentiles=[])
+```
+
+\[?\] this 5\% average in the difference probably exists because of the low number of galaxies we compare, so we can ignore it.
 
@@
 
+```{python}
+#| label: fig-sfr-lcv
+#| layout-ncol: 2
+#| layout-align: center
+#| fig-cap: "Comparison of the $SFR_{FUV}-SFR_{Ha} of the galaxies"
+#| fig-subcap: 
+#| - "Linear scale" 
+#| - "Decimal logarithmic scale"
+
+##linear
+plt.close()
+fig, ax = plt.subplots()
+temp = lcv[["SFRHa","SFRFUV"]].to_pandas().dropna()
+x = temp["SFRHa"]
+y = temp["SFRFUV"]
+sns.regplot(x = x, y = y,
+                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
+                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
+results = scipy.stats.linregress(x = x, y = y)
+plt.axvline(x=1e-3, color='green', linestyle='--', linewidth=2)
+plt.xlabel("$SFR_{Ha}$"+" [{}]".format(dt["SFRHa"].unit.to_string("latex")))
+plt.ylabel("$SFR_{FUV} $"+" [{}]".format(dt["SFRFUV"].unit.to_string("latex")))
+plt.legend(["Data",
+            "$SFR_{FUV}=$" +f"{results.slope:.2f}"+"$\cdot SFR_{Ha}$"+
+            f"${results.intercept:+.2f}$"+
+            f"\n $R^2 = {results.rvalue**2*100:.2f}\%$"])
+plt.show()
+
+##log
+
+plt.close()
+
+x = np.log10(temp["SFRHa"])
+y = np.log10(temp["SFRFUV"])
+fig, ax = plt.subplots()
+sns.regplot(x = x, y = y,
+                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
+                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
+results = scipy.stats.linregress(x = x, y = y)
+plt.axvline(x=-3, color='green', linestyle='--', linewidth=2)
+
+plt.xlabel("$log(SFR_{Ha})$"+" [{}]".format(dt["logSFR_HEC"].unit.to_string("latex")))
+plt.ylabel("$log(SFR_{FUV})$"+" [{}]".format(dt["logSFR_HEC"].unit.to_string("latex")))
+plt.legend(["Data",
+            "$log(SFR_{FUV})=$" +f"{results.slope:.2f}"+"$\cdot log(SFR_{Ha})$"+
+            f"${results.intercept:+.2f}$"+
+            f"\n $R^2 = {results.rvalue**2*100:.2f}\%$"])
+plt.show()
+```
+
+The SFR according to @kroupaConstraintsStarFormation2020, can be calculated from the mean of SFR from the Ha and FUV, for $SFR>10^{-3}\ M_\odot\, yr^{-1}$.
+As we can see from the plots @fig-sfr-lcv it is a good aproximation for all SFR's
+
+$$
+SFR = \frac{SFR_{FUV}+SFR_{H\alpha}}{2}, \text{if both exist, else: } SFR = SFR_i,\ i= FUV,\, H\alpha
+$$
+
+```{python}
+sfr_fuv = dt['SFRFUV']
+sfr_ha = dt['SFRHa']
+
+dt["SFR_t"] =np.log10(np.nanmean([sfr_fuv, sfr_ha], axis=0))
+dt["SFR_t"].unit = dt["SFRFUV"].unit
+```
+
+```{python}
+#| label: fig-SFR-compare
+#| layout-ncol: 2
+#| layout-align: center
+#| fig-cap: "Comparison of the SFR's of the galaxies"
+#| fig-subcap: 
+#| - "Linear scale" 
+#| - "Decimal logarithmic scale"
+
+##linear
+plt.close()
+fig, ax = plt.subplots()
+temp = dt[["SFR_t","logSFR_HEC"]].to_pandas().dropna()
+temp = temp[temp["SFR_t"]>-3]
+sns.regplot(x = 10**temp["SFR_t"], y = 10**temp["logSFR_HEC"],
+                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
+                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
+results = scipy.stats.linregress(x = 10**temp["SFR_t"], y = 10**temp["logSFR_HEC"])
+plt.xlabel("$SFR_{LCV}$"+" [{}]".format(dt["SFR_t"].unit.to_string("latex")))
+plt.ylabel("$SFR_{HECATE} $"+" [{}]".format(dt["SFR_t"].unit.to_string("latex")))
+plt.legend(["Data",
+            "$SFR_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot SFR_{LCV}$"+
+            f"${results.intercept:+.2f}$"+
+            f"\n $R^2 = {results.rvalue**2*100:.2f}\%$"])
+plt.show()
+
+##log
+
+plt.close()
+fig, ax = plt.subplots()
+temp = dt[["SFR_t","logSFR_HEC"]].to_pandas().dropna()
+temp = temp[temp["SFR_t"]>-3]
+sns.regplot(x = temp["SFR_t"], y = temp["logSFR_HEC"],
+                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
+                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
+results = scipy.stats.linregress(x = temp["SFR_t"], y = temp["logSFR_HEC"])
+plt.xlabel("$log(SFR_{LCV})$"+" [{}]".format(dt["logSFR_HEC"].unit.to_string("latex")))
+plt.ylabel("$log(SFR_{HECATE})$"+" [{}]".format(dt["logSFR_HEC"].unit.to_string("latex")))
+plt.legend(["Data",
+            "$log(SFR_{HEC})=$" +f"{results.slope:.2f}"+"$\cdot log(SFR_{LCV})$"+
+            f"${results.intercept:+.2f}$"+
+            f"\n $R^2 = {results.rvalue**2*100:.2f}\%$"])
+plt.show()
+```
+
+?EXPLANATION? this low correlation maybe comes from the inaccuracy/approximation of @kroupaConstraintsStarFormation2020
+
 ## Masses
@@
 ::: panel-tabset
+
 ### Stellar Masses Comparison
 
+```{python}
+#| label: fig-Mass-compare
+#| fig-cap: "Comparison of the Stellar Masses of the galaxies"
+
+plt.close()
+fig, ax = plt.subplots()
+temp = dt[["logStellarMass","logM_HEC"]].to_pandas().dropna()
+x = temp["logStellarMass"]
+y = temp["logM_HEC"]
+sns.regplot(x = x, y = y, 
+                scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'), 
+                line_kws=dict(alpha=0.7, color='red', linewidth=3))
+results = scipy.stats.linregress(x = x, y = y)
+plt.xlabel("$log(M_{*,LCV})$"+" [{}]".format(dt["logM_HEC"].unit.to_string("latex")))
+plt.ylabel("$log(M_{*,HECATE} )$"+" [{}]".format(dt["logM_HEC"].unit.to_string("latex")))
+plt.legend(["Data",
+            "$log(M_{*,HEC})=$" +f"{results.slope:.2f}"+"$\cdot log(M_{*,LCV})$"+
+            f"${results.intercept:+.2f}$"+
+            f"\n $R^2 = {results.rvalue**2*100:.2f}\%$"])
+plt.show()
+
+```
 ```{python}
@@
 
-```{python}
-temp.rename(columns={"diff_M":"Percantage Change [%]"}, inplace = True)
-```
-
-```{python}
-temp.describe(percentiles=[])
-```
+$$
+\log{M_{*,HECATE}}=1.07\cdot\log{M_{*,LCV}}-0.69, \text{ but } \log{M_*}>6\Rightarrow M_{*,HEC}\sim M_{*,LCV}
+$$
+
+As we can see the aproximation of Mass/Light=const.=0.6 is a pretty good approximation, for the calculation of $\log(M_*/M_\odot)$, especially for high-mass galaxies
 

### 2024-10-02 compare/compare.tex
replaced scatter plot

@@
   \begin{itemize}
-  \tightlist
-  \item
-    Similar to B-band completeness when measured with K\_s-band
-    luminosity as a tracer for stellar mass. Overdensity at small
-    distances and cut-off at large distances are observed.
+  \item
+    Similar to B-band completeness when measured with \(K_s\)-band
+    luminosity as a tracer for stellar mass.
+  \item
+    Overdensity at small distances and cut-off at large distances are
+    observed.
   \end{itemize}
@@
     for star-forming galaxies in the local neighborhood.
+  \item
+    HECATE's nonuniform SFR and stellar mass coverage, affecting the
+    reliability of stellar population parameters.
   \end{itemize}
@@
 \endlastfoot
-Ra\_1 & RA\_2 & Right Ascension & 1.0 \\
-Dec\_1 & DEC\_2 & Declination & 1.0 \\
 Dis & D & Distance & 0.881 \\
@@
 
-\subsubsection{Right Ascension}
-
-\includegraphics{compare_files/figure-pdf/cell-13-output-1.pdf}
-
-\subsubsection{Declination}
-
-\includegraphics{compare_files/figure-pdf/cell-14-output-1.pdf}
-
-\subsubsection{Distance}
-
-\includegraphics{compare_files/figure-pdf/cell-15-output-1.pdf}
+\begin{figure}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-coord-compare-output-1.pdf}
+
+}
+
+\caption{\label{fig-coord-compare}Comparison of the Distances}
+
+\end{figure}%
+
+\begin{itemize}
+\tightlist
+\item
+  The average error of the distance in the HECATE catalog is
+  \(\overline{E_D} = \pm 1.6\) Mpc, so the intercept is included in the
+  error.
+\item
+  So we can assume that the Distances are the same
+\end{itemize}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-17-output-1.pdf}
-
-\includegraphics{compare_files/figure-pdf/cell-19-output-1.pdf}
+\begin{figure}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-vel-compare-output-1.pdf}
+
+}
+
+\caption{\label{fig-vel-compare}Comparison of the Radial Velocities}
+
+\end{figure}%
+
+\begin{itemize}
+\tightlist
+\item
+  The average error of the radial velocity in the HECATE catalog is
+  \(\overline{E_V} = \pm 12\text{km}\cdot s^{-1}\) , so the intercept is
+  included in the error.
+\item
+  So we can assume that the radial velocities are the same
+\end{itemize}
+
+\includegraphics{compare_files/figure-pdf/cell-15-output-1.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-22-output-1.pdf}
+\begin{figure}
+
+\begin{minipage}{0.50\linewidth}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-types-compare-output-1.pdf}
+
+}
+
+\subcaption{\label{fig-types-compare-1}All the galaxies, without the
+correction}
+
+\end{minipage}%
+%
+\begin{minipage}{0.50\linewidth}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-types-compare-output-2.pdf}
+
+}
+
+\subcaption{\label{fig-types-compare-2}Comparison with the correction
+\(|{T_{HECATE}-T_{LCV}}|<7\)}
+
+\end{minipage}%
+
+\caption{\label{fig-types-compare}Comparison of the Types of galaxies}
+
+\end{figure}%
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-23-output-1.pdf}
+\begin{itemize}
+\tightlist
+\item
+  The average uncertainty of the morphological type in the HECATE
+  catalog is \(\overline{E_T} = \pm 1.4\), so the intercept is included
+  in the error.
+\item
+  So we can assume that the Distances are the same
+\end{itemize}
 
@@
 \begin{minipage}{0.50\linewidth}
-\includegraphics{compare_files/figure-pdf/cell-29-output-1.pdf}\end{minipage}%
+\includegraphics{compare_files/figure-pdf/cell-24-output-1.pdf}\end{minipage}%
 %
 \begin{minipage}{0.50\linewidth}
-\includegraphics{compare_files/figure-pdf/cell-29-output-2.pdf}\end{minipage}%
-\newline
-\begin{minipage}{\linewidth}
+\includegraphics{compare_files/figure-pdf/cell-24-output-2.pdf}\end{minipage}%
+
+\end{figure}%
 
@@
 
-\end{minipage}%
-
-\end{figure}%
-
 We can see that for values in the range
@@
 
-\includegraphics{compare_files/figure-pdf/cell-30-output-1.pdf}
+\begin{figure}
+
+\begin{minipage}{0.50\linewidth}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-axis-compare-output-1.pdf}
+
+}
+
+\subcaption{\label{fig-axis-compare-1}Linear scale}
+
+\end{minipage}%
+%
+\begin{minipage}{0.50\linewidth}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-axis-compare-output-2.pdf}
+
+}
+
+\subcaption{\label{fig-axis-compare-2}\(log_{10}\) scale}
+
+\end{minipage}%
+
+\caption{\label{fig-axis-compare}Comparison of the Major Axises of the
+galaxies}
+
+\end{figure}%
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-32-output-1.pdf}
+\(\overline{R_1} = 3.9\) {[}arcmin{]}, \(\overline{a_{26}} = 9.3\)
+{[}arcmin{]}, so the intercept is negligable. \[
+R_1 = 0.48\cdot a_{26}-0.34 \sim \frac{1}{2}a_{26}
+\]
+
+\[
+\log(R1) = 0.89\log(a_{26})-10^{0.38} = \log(10^{-0.38}a_{26}^{0.89}) = \log(0.41\cdot a_{26}^{0.89})\Rightarrow R1\simeq \frac{a_{26}}{2}
+\]
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-34-output-1.pdf}
+\begin{figure}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-klum-compare-output-1.pdf}
+
+}
+
+\caption{\label{fig-klum-compare}Comparison of the \(L_K\) of the
+galaxies}
+
+\end{figure}%
+
+\[
+\log(L_{K,HEC})=1.16\log(L_{K,LCV})-1.78=\log\left(\frac{{L_{K,LCV}}^{1.16}}{10^{1.78}}\right) \Leftrightarrow L_{K,HEC}=0.02\cdot{L_{K,LCV}}^{1.16}
+\]
+
+So as we can see the usage of a linear fitting is not correct here. But
+we can clearly see a linear correlation.
+
+We will use the relative difference of the two luminosities, to see if
+statistically they are the same:
+
+\includegraphics{compare_files/figure-pdf/cell-29-output-1.pdf}
 
@@
 
-\subsubsection{B mag}
-
-\includegraphics{compare_files/figure-pdf/cell-38-output-1.pdf}
-
-\subsubsection{K mag}
-
-\includegraphics{compare_files/figure-pdf/cell-39-output-1.pdf}
+\begin{figure}
+
+\begin{minipage}{0.50\linewidth}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-mag-compare-output-1.pdf}
+
+}
+
+\subcaption{\label{fig-mag-compare-1}\(M_B\)}
+
+\end{minipage}%
+%
+\begin{minipage}{0.50\linewidth}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-mag-compare-output-2.pdf}
+
+}
+
+\subcaption{\label{fig-mag-compare-2}\(M_K\)}
+
+\end{minipage}%
+
+\caption{\label{fig-mag-compare}Comparison of the Magnitudes of the
+galaxies}
+
+\end{figure}%
+
+\begin{itemize}
+\tightlist
+\item
+  \(M_B\): it is a 1-1 correlation, since the average error
+  \(M_{B,HECATE} = 0.4\ mag\), so the itercept is smaller than the error
+\item
+  \(M_K\): we need to examine it more, since the intercept is bigger
+  than the error \(M_{K,HECATE} = 0.09\ mag\)
+\end{itemize}
+
+\includegraphics{compare_files/figure-pdf/cell-35-output-1.pdf}
+
+\includegraphics{compare_files/figure-pdf/cell-35-output-2.pdf}
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-41-output-1.pdf}
-
-{[}?{]}
+{[}?{]} this 5\% average in the difference probably exists because of
+the low number of galaxies we compare, so we can ignore it.
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-43-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-38-output-1.pdf}
+
+\begin{figure}
+
+\begin{minipage}{0.50\linewidth}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-sfr-lcv-output-1.pdf}
+
+}
+
+\subcaption{\label{fig-sfr-lcv-1}Linear scale}
+
+\end{minipage}%
+%
+\begin{minipage}{0.50\linewidth}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-sfr-lcv-output-2.pdf}
+
+}
+
+\subcaption{\label{fig-sfr-lcv-2}Decimal logarithmic scale}
+
+\end{minipage}%
+
+\caption{\label{fig-sfr-lcv}Comparison of the \$SFR\_\{FUV\}-SFR\_\{Ha\}
+of the galaxies}
+
+\end{figure}%
+
+The SFR according to Kroupa et al. (2020), can be calculated from the
+mean of SFR from the Ha and FUV, for \(SFR>10^{-3}\ M_\odot\, yr^{-1}\).
+As we can see from the plots Figure~\ref{fig-sfr-lcv} it is a good
+aproximation for all SFR's
+
+\[
+SFR = \frac{SFR_{FUV}+SFR_{H\alpha}}{2}, \text{if both exist, else: } SFR = SFR_i,\ i= FUV,\, H\alpha
+\]
+
+\begin{figure}
+
+\begin{minipage}{0.50\linewidth}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-sfr-compare-output-1.pdf}
+
+}
+
+\subcaption{\label{fig-sfr-compare-1}Linear scale}
+
+\end{minipage}%
+%
+\begin{minipage}{0.50\linewidth}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-sfr-compare-output-2.pdf}
+
+}
+
+\subcaption{\label{fig-sfr-compare-2}Decimal logarithmic scale}
+
+\end{minipage}%
+
+\caption{\label{fig-sfr-compare}Comparison of the SFR's of the galaxies}
+
+\end{figure}%
+
+?EXPLANATION? this low correlation maybe comes from the
+inaccuracy/approximation of Kroupa et al. (2020)
 
@@
 
+\begin{figure}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-mass-compare-output-1.pdf}
+
+}
+
+\caption{\label{fig-mass-compare}Comparison of the Stellar Masses of the
+galaxies}
+
+\end{figure}%
+
+\includegraphics{compare_files/figure-pdf/cell-44-output-1.pdf}
+
+\[
+\log{M_{*,HECATE}}=1.07\cdot\log{M_{*,LCV}}-0.69, \text{ but } \log{M_*}>6\Rightarrow M_{*,HEC}\sim M_{*,LCV}
+\]
+
+As we can see the aproximation of Mass/Light=const.=0.6 is a pretty good
+approximation, for the calculation of \(\log(M_*/M_\odot)\), especially
+for high-mass galaxies
+
+\subsubsection{Heatmap}
+
 \includegraphics{compare_files/figure-pdf/cell-45-output-1.pdf}
-
-\begin{longtable}[]{@{}ll@{}}
-\toprule\noalign{}
-& Percantage Change {[}\%{]} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-count & 64 \\
-mean & -1 \\
-std & 5 \\
-min & -19 \\
-50\% & 1 \\
-max & 9 \\
-\end{longtable}
-
-\subsubsection{Heatmap}
-
-\includegraphics{compare_files/figure-pdf/cell-48-output-1.pdf}
 
@@
 
+\bibitem[\citeproctext]{ref-kroupaConstraintsStarFormation2020}
+Kroupa, P, M Haslbauer, I Banik, S T Nagesh, and J Pflamm-Altenburg.
+2020. {``Constraints on the Star Formation Histories of Galaxies in the
+{Local Cosmological Volume}.''} \emph{Monthly Notices of the Royal
+Astronomical Society} 497 (1): 37--43.
+\url{https://doi.org/10.1093/mnras/staa1851}.
+
 \bibitem[\citeproctext]{ref-navarroStructureColdDark1996}

### 2024-10-05 compare/compare.qmd
def and expl

@@
 
-In this script we will compare 2 catalogs @kovlakasHeraklionExtragalacticCatalogue2021 and [@karachentsevUPDATEDNEARBYGALAXY2013, @karachentsevSTARFORMATIONPROPERTIES2013a]
+In this script we will compare 2 catalogs, HECATE (@kovlakasHeraklionExtragalacticCatalogue2021) and LCV ([@karachentsevUPDATEDNEARBYGALAXY2013, @karachentsevSTARFORMATIONPROPERTIES2013a])
 
@@
 import scipy
+from scipy.optimize import curve_fit
 #quantity_support()
@@
 
-Checking for completeness in galaxy catalogs is essential to ensure that the data accurately represents the true population of galaxies.
+Checking for completeness in galaxy catalogs is essential to ensure that the data accurately represents the true population of galaxies, for $z \approx 0$.
 Incomplete catalogs can lead to biased results in statistical studies, such as the distribution of galaxy luminosity, mass, or star formation rates.
@@
 
-1. Radial velocities of
-$$
+1.  Radial velocities of $$
      V_{LG}<600 \text{ km}\cdot\text{m}^{-1}
@@
 
-2. Distances of D\<11 Mpc
+2.  Distances of $$
+       D<11\ \text{Mpc}
+       $$ {#eq-lcv-dis}
 
@@
 
--   Completeness within a 10 Mpc radius is difficult to assess due to:
-    -   Variability in galaxy properties (luminosity, size, surface brightness, gas content)
-    -   Errors in distance measurements (Tully–Fisher method errors of \~20–25%), especially at the 10 Mpc boundary.
+### Difficulties in calculating the Completeness
+
+As explained in (@karachentsevUPDATEDNEARBYGALAXY2013), it is difficult to calculate the completeness of the catalog.
+
+1.
+Completeness within a 10 Mpc radius is difficult to assess due to: - Variability in galaxy properties (luminosity, size, surface brightness, gas content) - Errors in distance measurements (Tully–Fisher method errors of \~20–25%), especially at the 10 Mpc boundary.
     -   Accurate distances are mainly known within \~5 Mpc.
-    -   Non-Hubble motions (\~300 km/s) may make up half of the adopted velocity constraint @eq-lcv-vel
+    -   Non-Hubble motions (\~300 km/s)[^1] may make up half of the adopted velocity constraint (@eq-lcv-vel)
     -   Solution for our usage: only keep the galaxies inside a radius of $D=11 Mpc$
-        -   HI sources in surveys with low angular resolution: "The presence around our Galaxy of hundreds of high-velocity clouds with low line-of-sight velocities and small W50 widths also provokes the inclusion of false “nearby” dwarf galaxies in the LV"@karachentsevUPDATEDNEARBYGALAXY2013
-        -   photographic emulsion defect -\> exotic cases of galaxies -\> radial velocity of $+614 km s^{−1}$
--   Astro-Spam and Survey Errors:
-    -   Automatic surveys produce false detections (e.g., stars misclassified as galaxies, high-velocity clouds mistaken for dwarfs).
--   Conditional Completeness Estimate:
-    -   Galaxies brighter than $M_B^c = -11^m$ or with linear diameters larger than $A_{26} = 1.0$ kpc show (40–60)% completeness.
+    -   HI sources in surveys with low angular resolution: "The presence around our Galaxy of hundreds of high-velocity clouds with low line-of-sight velocities and small W50 widths also provokes the inclusion of false “nearby” dwarf galaxies in the LV"(@karachentsevUPDATEDNEARBYGALAXY2013)
+2.  Astro-Spam and Survey Errors: - Automatic surveys produce false detections (e.g., stars misclassified as galaxies, high-velocity clouds mistaken for dwarfs).
+3.
+Conditional Completeness Estimate: - Galaxies brighter than $M_B^c = -11^m$ or with linear diameters larger than $A_{26} = 1.0$ kpc show (40–60)% completeness.
 - "among the members of the Local Group (D \< 1 Mpc), only half of the galaxies have absolute magnitudes brighter than −11m.
 Consequently, more than half of the ultra-faint dwarf companions around normal galaxies, like the Sombrero galaxy (D = 9.3 Mpc), still remain outside our field of view."
--   Undetected Ultra-Faint Dwarfs:
-    -   Many faint dwarf galaxies remain undetected beyond the Local Group. Estimated population of undetected dwarfs could be as large as $10^3–10^4$ within the LV.
--   Surface Brightness Distribution:
-    -   Surface brightness remains consistent across distances, except for ultra-faint dwarfs ($SB <31 \text{mag}\cdot\text{arcsec}^{-2}$).
+4.  Undetected Ultra-Faint Dwarfs: - Many faint dwarf galaxies remain undetected beyond the Local Group. Estimated population of undetected dwarfs could be as large as $10^3–10^4$ within the LV.
+5.
+Surface Brightness Distribution: - Surface brightness remains consistent across distances, except for ultra-faint dwarfs ($SB <31 \text{mag}\cdot\text{arcsec}^{-2}$).
 - Faintest dwarf galaxies are detectable only nearby due to their resolution into individual stars.
--   Luminosity-Size Relationship:
-    -   Observations align with cosmological models predicting $L\sim A^3$ @navarroStructureColdDark1996, though deviations occur for extremely low surface brightness galaxies.
+6.
+Luminosity-Size Relationship: - Observations align with cosmological models predicting $L\sim A^3$ (@navarroStructureColdDark1996), though deviations occur for extremely low surface brightness galaxies.
 - "The deviation from it at the extremely low surface brightness end is due to a systematic overestimation of dwarf galaxy sizes, the brightness profiles of which lie entirely below the Holmberg isophote."
+
+[^1]: *Non-Hubble motion refers to the component of a galaxy's velocity that deviates from the uniform expansion of the universe, described by the equation* $V= H_0 d + v_p$,where $V$ is the total velocity, $H_0 d$ represents the Hubble flow, and $v_p$​ is the peculiar velocity.
+@Essay
 
@@
 ## Completeness of the Data
-
-```{python}
-def plot_completeness(dataset_choice="lcv", column_name="Dis", description="Distance", units=True, logx=False, logy=False, bins=0, keep_nan=False):
-    """
-    Plots histograms with KDE and displays a table of counts and percentages for each bin, 
-    based on the choice of dataset (LCV or HEC).
-
-    Parameters:
-    - dataset_choice: A string indicating which dataset to use ("lcv" or "hec")
-    - column_name: The column name in the Qtable to plot and analyze (default is "Dis")
-    - description: What to show in the title and the axis (default "Distance")
-    - units: Show units or not (default is True)
-    - logx: logarithmic x-axis (default is False)
-    - logy: logarithmic y-axis (default is False)
-    - bins: Number of bins or custom bin edges (default is 'auto')
-    - keep_nan: keep (True) or remove NaN's (default is True)
-    """
-
-    if dataset_choice == "lcv":
-        main_df, unique_df, label = lcv, lcv_not_hec, "LCV"
-    elif dataset_choice == "hec" and hec is not None and hec_not_lcv is not None:
-        main_df, unique_df, label = hec, hec_not_lcv, "HECATE"
-    else:
-        raise ValueError("Invalid dataset choice. Please choose 'lcv' or 'hec' with valid datasets.")
-
-    # Remove NaN values before plotting
-    if not keep_nan:
-        main_data_clean = main_df[~np.isnan(main_df[column_name].data)].data
-        unique_ddata_clean = unique_df[~np.isnan(unique_df[column_name].data)]
-    else:
-        main_data_clean = main_df[column_name].data
-        unique_data_clean = unique_df[column_name].data
-
-    # Check if bins is an integer or array of bin edges
-    if bins == 0:
-        counts, bin_edges = np.histogram(main_data_clean, bins='auto')
-    elif isinstance(bins, int):
-        counts, bin_edges = np.histogram(main_data_clean, bins=bins)
-    else:
-        bin_edges = bins  # If bins is an array of bin edges
-
-    # Plot the histograms
-    sns.histplot(main_data_clean, bins=bin_edges, kde=True, label=label)
-    sns.histplot(unique_data_clean, bins=bin_edges, kde=True, label=f"Unique for {label}")
-
-    # Set logarithmic axes if requested
-    if logx:
-        plt.xscale('log')
-    if logy:
-        plt.yscale('log')
-
-    # Set the title and labels
-    plt.title(f"Completeness of {description} for {label}")
-    if units and main_df[column_name].unit is not None:
-        plt.xlabel(f"{description} [{main_df[column_name].unit}]")
-    else:
-        plt.xlabel(f"{description}")
-    plt.ylabel("Number of galaxies")
-    plt.legend()
-
-    # Calculate histogram counts for each dataset
-    main_counts, _ = np.histogram(main_data_clean, bins=bin_edges)
-    unique_counts, _ = np.histogram(unique_data_clean, bins=bin_edges)
-
-    # Calculate bin centers for annotation
-    bin_centers = 0.5 * (bin_edges[1:] + bin_edges[:-1])
-
-    # Annotate percentages on the bars
-    for i, center in enumerate(bin_centers):
-        if main_counts[i] > 0:
-            unique_pct = (unique_counts[i] / main_counts[i]) * 100
-            plt.text(center, unique_counts[i], f'{unique_pct:.1f}%', color="green", ha='center', va='bottom')
-
-    # Show the plot
-    plt.show()
-    plt.close()
-
-```
 
@@
 
-### Distance
-
 ```{python}
@@
 
-plt.subplot(2,1,1)
-sns.histplot(main, bins = bin_edges, kde = True, label = "HECATE")
-sns.histplot(unique, bins = bin_edges, kde = True, label = "Unique for HECATE")
-plt.legend()
-plt.title("Completenes of Distance for HECATE")
+fig, (ax1, ax2) = plt.subplots(2, 1, sharex=True)
+sns.histplot(main, bins = bin_edges, kde = True, label = "HECATE", ax = ax1)
+sns.histplot(unique, bins = bin_edges, kde = True, label = "Unique for HECATE", ax = ax1)
+ax1.set_title("Completenes of Distance for HECATE")
+ax1.tick_params(labelbottom=True)
 unique_pct = (unique_counts/main_counts)*100 
@@
 plt.subplot(2,1,2)
-ax = sns.lineplot(x = bin_edges[1:], y = unique_pct)
-ax.set(xlabel='xlabel', ylabel='ylabel', title='title')
-
+sns.lineplot(x = bin_edges[1:], y = unique_pct, marker = "o", ax = ax2)
 #changing ylables ticks
-plt.yticks(np.arange(min(unique_pct), max(unique_pct)+1, 5.0))
-y_value=['{:,.0f}'.format(x) + '%' for x in ax.get_yticks()]
-ax.set_yticklabels(y_value)
-plt.ylabel("Completeness %")
-plt.xlabel("Distance [{}]".format(hec["D"].unit))
-plt.title("")
+# Set y-axis ticks for ax2 (completeness percentage)
+ax2.set_yticks(np.arange(min(unique_pct), max(unique_pct) + 1, 5.0))
+
+# Format the y-tick labels to display as percentages
+y_value = ['{:,.0f}%'.format(x) for x in ax2.get_yticks()]
+ax2.set_yticklabels(y_value)
+ax2.set(xlabel = "Distance [{}]".format(lcv["Dis"].unit), ylabel="Completeness %")
 plt.show()
@@
 
-plt.subplot(2,1,1)
-sns.histplot(main, bins = bin_edges, kde = True, label = "LCV")
-sns.histplot(unique, bins = bin_edges, kde = True, label = "Unique for LCV")
-plt.legend()
-plt.title("Completenes of Distance for LCV")
+fig, (ax1, ax2) = plt.subplots(2, 1, sharex=True)
+sns.histplot(main, bins = bin_edges, kde = True, label = "LCV", ax = ax1)
+sns.histplot(unique, bins = bin_edges, kde = True, label = "Unique for LCV", ax = ax1)
+ax1.legend()
+ax1.set_title("Completenes of Distance for LCV")
+ax1.tick_params(labelbottom=True)
 unique_pct = (unique_counts/main_counts)*100 
 ###
-plt.subplot(2,1,2)
-ax = sns.lineplot(x = bin_edges[1:], y = unique_pct)
-ax.set(xlabel='xlabel', ylabel='ylabel', title='title')
+sns.lineplot(x = bin_edges[1:], y = unique_pct, marker = "o", ax = ax2)
 
 #changing ylables ticks
-plt.yticks(np.arange(min(unique_pct), max(unique_pct)+1, 5.0))
-y_value=['{:,.0f}'.format(x) + '%' for x in ax.get_yticks()]
-ax.set_yticklabels(y_value)
-
-plt.ylabel("Completeness %")
-plt.xlabel("Distance [{}]".format(lcv["Dis"].unit))
-plt.title("")
+# Set y-axis ticks for ax2 (completeness percentage)
+ax2.set_yticks(np.arange(min(unique_pct), max(unique_pct) + 1, 5.0))
+
+# Format the y-tick labels to display as percentages
+y_value = ['{:,.0f}%'.format(x) for x in ax2.get_yticks()]
+ax2.set_yticklabels(y_value)
+ax2.set(xlabel = "Distance [{}]".format(lcv["Dis"].unit), ylabel="Completeness %")
 plt.show()
@@
 
-plt.subplot(2,1,1)
-sns.histplot(main, bins = bin_edges, kde = True, label = "HECATE")
-sns.histplot(unique, bins = bin_edges, kde = True, label = "Unique for HECATE")
-plt.legend()
-plt.title("Completenes of Types for HECATE")
+fig, (ax1, ax2) = plt.subplots(2, 1, sharex=True)
+sns.histplot(main, bins = bin_edges, kde = True, label = "HECATE",ax = ax1)
+sns.histplot(unique, bins = bin_edges, kde = True, label = "Unique for HECATE",ax = ax1)
+ax1.legend()
+ax1.set_title("Completenes of Types for HECATE")
+ax1.tick_params(labelbottom=True)
 unique_pct = (unique_counts/main_counts)*100 
 ###
-plt.subplot(2,1,2)
-ax = sns.lineplot(x = bin_edges[1:], y = unique_pct)
-ax.set(xlabel='xlabel', ylabel='ylabel', title='title')
+
+sns.lineplot(x = bin_edges[1:], y = unique_pct, marker = "o",ax = ax2)
 
 #changing ylables ticks
-plt.yticks(np.arange(min(unique_pct), max(unique_pct)+1, 5.0))
-y_value=['{:,.0f}'.format(x) + '%' for x in ax.get_yticks()]
-ax.set_yticklabels(y_value)
-plt.ylabel("Completeness %")
-plt.xlabel("Types of galaxies")
-plt.title("")
-plt.show()
-
+# Set y-axis ticks for ax2 (completeness percentage)
+ax2.set_yticks(np.arange(min(unique_pct), max(unique_pct) + 1, 5.0))
+
+# Format the y-tick labels to display as percentages
+y_value = ['{:,.0f}%'.format(x) for x in ax2.get_yticks()]
+ax2.set_yticklabels(y_value)
+
+ax2.set(xlabel = "Types of galaxies", ylabel="Completeness %")
+plt.show()
+######
 #LCV
@@
 
-plt.subplot(2,1,1)
-sns.histplot(main, bins = bin_edges, kde = True, label = "LCV")
-sns.histplot(unique, bins = bin_edges, kde = True, label = "Unique for LCV")
-plt.legend()
-plt.title("Completenes of Distance for LCV")
+fig, (ax1, ax2) = plt.subplots(2, 1, sharex=True)
+sns.histplot(main, bins = bin_edges, kde = True, label = "LCV", ax = ax1)
+sns.histplot(unique, bins = bin_edges, kde = True, label = "Unique for LCV", ax = ax1)
+ax1.legend()
+ax1.set_title("Completenes of Types for LCV")
+ax1.tick_params(labelbottom=True)
 unique_pct = (unique_counts/main_counts)*100
 
-plt.subplot(2,1,2)
-ax = sns.lineplot(x = bin_edges[1:] ,y = unique_pct)
-ax.set(xlabel='xlabel', ylabel='ylabel', title='title')
+sns.lineplot(x = bin_edges[1:] ,y = unique_pct, marker = "o", ax = ax2)
 
 #changing ylables ticks
-plt.yticks(np.arange(min(unique_pct), max(unique_pct)+1, 10.0))
-y_value=['{:,.0f}'.format(x) + '%' for x in ax.get_yticks()]
-ax.set_yticklabels(y_value)
-
-plt.ylabel("Completeness %")
-plt.xlabel("Types of galaxies")
-plt.title("")
-plt.show()
-```
-
-As we can see from the histograms @fig-dis-comp and @fig-type-comp the sample of unique galaxies of each catalog, gets smaller by an almost constant proportion (Inner join).
+# Set y-axis ticks for ax2 (completeness percentage)
+ax2.set_yticks(np.arange(min(unique_pct), max(unique_pct) + 1, 10.0))
+
+# Format the y-tick labels to display as percentages
+y_value = ['{:,.0f}%'.format(x) for x in ax2.get_yticks()]
+ax2.set_yticklabels(y_value)
+
+ax2.set(xlabel = "Types of galaxies", ylabel="Completeness %")
+plt.show()
+```
+
+As we can see from the histograms (@fig-dis-comp) and (@fig-type-comp) the sample of unique galaxies of each catalog, gets smaller by an almost constant proportion (Inner join).
 
@@
 
-## Scatter plots and $R^2$ calculation
+For the comparison of our data we will mainly use two methods: linear regression and comparison of the distributions.
+
+For the linear regression out main tools are scatter plots and $R^2$
 
 1.  $R^2$: Measures the proportion of variance explained by the linear model.
-2.  Slope of the Fitted Line: Should be close to 1 for a 1-1 correlation.[^1]
-
-[^1]: Some data seem to have a very good linear correlation but they have many outliers. This is why we will clip the outliers with $\sigma > 3$
-
-<!-- -->
+
+2.  Slope of the Fitted Line: Should be close to 1 for a 1-1 correlation.
 
@@
 
-4.  [Plots]{.underline}: Plots are essential for visually assessing the relationship between two datasets, identifying correlations, trends, and outliers, and evaluating the fit of linear models.
-
--   Histograms: Because not all of our data have the same number of counts, the comparison with histograms between data that are not the same, doesn't help us right now.[^3] This is why we will only use histograms for comparing the distribution of same-data columns normalized by their maximum value
-
-[^3]: When we will use the outer join table we could use histograms due to the large number of counts.
-
-<!-- -->
-
--   Correlation Heatmaps: A correlation heatmap is a graphical tool that displays the correlation between multiple variables as a color-coded matrix.
+4.
+Plots: Plots are essential for visually assessing the relationship between two datasets, identifying correlations, trends, and outliers, and evaluating the fit of linear models.
+Beside scatter plots and histograms, another useful plot is the Correlation Heatmap.
+
+    > Correlation Heatmaps: A correlation heatmap is a graphical tool that displays the correlation between multiple variables as a color-coded matrix.
 It's like a color chart that shows us how closely related different variables are.
@@
 
--   Kernel Density Estimate (KDE) plot: The KDE plot visually represents the distribution of data, providing insights into its shape, central tendency, and spread.
-
-5.
-Percentage change: We can calculate the percentage change of the data for each galaxy and then we can see if the data are similar, based on minimum, the maximum and the mean value of the difference.
+For the distrabution comparisons we will use histograms and Kernel Density Estimate (KDE) plots.
+The KDE plots visually represent the distribution of data, providing insights into its shape, central tendency, and spread.
+
+Finally, we will examine the percentage change for each galaxy.
+
+-   Percentage change: We can calculate the percentage change of the data for each galaxy and then we can see if the data are similar, based on minimum, the maximum and the mean value of the difference.
 
@@
 | LCV | HECATE | Description |              Pearson Correlation \[-1,1\]              |
-|:-----:|:------:|:---------------:|:----------------------------:|
+|:---------------:|:---------------:|:---------------:|:--------------------:|
 | Dis |   D    |  Distance   | `{python} round(compare_data(dt["Dis"],dt["D"])[3],3)` |
@@
 
-- The average error of the distance in the HECATE catalog is $\overline{E_D} = \pm 1.6$ Mpc, so the intercept is included in the error.
+-   The average error of the distance in the HECATE catalog is $\overline{\delta D} = \pm 1.6$ Mpc, so the intercept is included in the error.
 -   So we can assume that the Distances are the same
@@
 
-- The average error of the radial velocity in the HECATE catalog is $\overline{E_V} = \pm 12\text{km}\cdot s^{-1}$ , so the intercept is included in the error.
+-   The average error of the radial velocity in the HECATE catalog is $\overline{\delta V} = \pm 12\text{km}\cdot s^{-1}$ , so the intercept is included in the error.
 -   So we can assume that the radial velocities are the same
@@
 ```{python}
+#| label: fig-vel-pairplot
+#| fig-cap: "The correlation Matrix of the Velocities.
+The lower left triangle is is composed of the scatter plots of the various velocities, the diagonal shows their distrubution and the upper right triangle shows the correlations of the Velocities"
 pairplot_with_correlation(vel_data)
@@
 \[?\] The close correlation between all of the velocities, could be due to the fact that all of them measure the velocity of each galaxy, but from a different frame of reference.
+
+The strong correlation between the velocities reported by the HECATE and LCV catalogs can be attributed to the fact that both measure the same intrinsic galaxy velocities but reference them to different frames.
+For instance, velocities can be corrected for the movement of the Earth (heliocentric frame) or the for the Virgo-infall.
+These corrections shift the measured velocity slightly, but the fundamental measurement remains consistent.
+This explains why the velocities are highly correlated, as they represent the same physical phenomenon but adjusted for different reference points.
+
+{{<pagebreak>}}
 
@@
 ### Galaxy Types
+
+"Morphological type of galaxy in the numerical code according to the classification by de Vaucouleurs et al.
+(1991).
+It should be noted that about three quarters of objects in the LV are dwarf galaxies, which require a more detailed morphological classification.
+For example, dwarf spheroidal galaxies and normal ellipticals are usually denoted by the same numerical code T \< 0, although their physical properties drastically differ.
+The classification problem arises as well for the “transient” type dwarf galaxies, T r, which combine the features of spheroidal (Sph) and irregular (Ir)systems.
+Due to small classification errors, such objects may “jump” from one end of the T scale to the other." (@karachentsevUPDATEDNEARBYGALAXY2013)
 
@@
 types["diff"] = dt["T"]-dt["TType"]
-types = types[np.abs(types["diff"])<7]
+types = types[np.abs(types["diff"])<dt["TType"].std()]
 
@@
 
-"Morphological type of galaxy in the numerical code according to the classification by de Vaucouleurs et al.
-(1991).
-It should be noted that about three quarters of objects in the LV are dwarf galaxies, which require a more detailed morphological classification.
-For example, dwarf spheroidal galaxies and normal ellipticals are usually denoted by the same numerical code T \< 0, although their physical properties drastically differ.
-The classification problem arises as well for the “transient” type dwarf galaxies, T r, which combine the features of spheroidal (Sph) and irregular (Ir)systems.
-Due to small classification errors, such objects may “jump” from one end of the T scale to the other." @karachentsevUPDATEDNEARBYGALAXY2013
-
 -   we can assume that the galaxies from the upper left and lower right regions of the plot are classified differently because of this
 -   this might explain the large errors E_T of HECATE
--   why we see a difference in the distribution of @fig-type-comp
+-   why we see a difference in the distribution of (@fig-type-comp)
 
@@
 $$
-|{T_{HECATE}-T_{LCV}}|<7
-$$
-
-- The average uncertainty of the morphological type in the HECATE catalog is $\overline{E_T} = \pm 1.4$, so the intercept is included in the error.
+|{T_{HECATE}-T_{LCV}}|<\sigma_{T_{LCV}} = 4.8
+$$
+
+-   The average uncertainty of the morphological type in the HECATE catalog is $\overline{\delta T} = \pm 1.4$, so the intercept is included in the error.
 -   So we can assume that the Distances are the same
 
-<!-- #### Normalize the scale of galaxy types
-
-It is very possible that the two catalogs use different scaling methods, as indicated by the use of decimal numbers in HECATE.
-
-```{python}
-types = dt[["T", "TType"]].to_pandas()
-```
-
-```{python}
-def min_max_normalize(series):
-    return (series - series.min()) / (series.max() - series.min())
-
-types["T_norm"] = min_max_normalize(types["T"])
-types["T_norm"].mask = types["T"].mask
-types["TType_norm"] = min_max_normalize(types["TType"])
-#types.describe()
-```
-TType
-
-Also, as we can see the minimum values are lower by 2 in HECATE, which complies with the linear fit.
-
-```{python}
-sns.histplot(types[["TType_norm", "T_norm"]], kde = True)
-plt.xlabel("Types of galaxies")
-plt.show()
-```
-
-```{python}
-types["norm_diff"] = (-types["TType_norm"] + types["T_norm"])
-sns.histplot(types["norm_diff"], kde = True)
-
-plt.xlabel(r"$T_{HECATE}-T_{LCV}$")
-plt.show()
-```
-
-```{python}
-types["norm_rel_diff"] = (-types["TType_norm"] + types["T_norm"])/types["T"]
-sns.histplot(types["norm_rel_diff"], kde = True)
-plt.xlim(-0.2,0.2)
-plt.xlabel(r"$(T_{HECATE}-T_{LCV})/T_{HECATE}$")
-plt.show()
-```
--->
-
 ### Inclination
@@
 ```{python}
-#| layout: [[50,50]]
+#| label: fig-incl-compare
+#| layout-ncol: 2
+#| layout-align: center
+#| fig-cap: "Comparison of the Inclination of the galaxies"
+#| fig-subcap: 
+#| - "Distribution of the Inclination of the galaxies" 
+#| - "Distribution of the Percentage Change" 
 plt.close()
@@
 
-We can see that for values in the range $[\sim 30^\circ,\sim 80^\circ]$, the values of the LCV inclination are higher.
+We can see that for values in the range $[\sim 30^\circ,\sim 80^\circ]$, the values of the LCV inclination are higher (@fig-incl-compare).
 However, since their means, median, min and maxes are similar and the percentage change is practically 0% (mean, median, $\sigma$ = 0 with a range $[-3\%,1\%]$), we can ignore the differences and assume they are the same values.
@@
 
-it is not very clear if we truly have a correlation or not. We need to see the linear correlation of the decimal logarithms.
-
-$\overline{R_1} = 3.9$ [arcmin],  $\overline{a_{26}} = 9.3$ [arcmin], so the intercept is negligable.
+it is not very clear if we truly have a correlation or not (@fig-axis-compare-1). We need to see the linear correlation of the decimal logarithms (@fig-axis-compare-2).
+
+$\overline{R_1} = 3.9$ \[arcmin\], $\overline{a_{26}} = 9.3$ \[arcmin\], so the intercept is negligable.
+
 $$
@@
 $$
-
 :::
@@
 #| echo: false
+#| output: asis 
 #| warning: false
@@
 ```{python}
-#| label: fig-KLum-compare
-#| fig-cap: "Comparison of the $L_K$ of the galaxies"
+#| label: fig-klum-compare
+#| layout-ncol: 2 
+#| fig-cap: "Comparison of the $L_K$ of the galaxies."
+#| fig-subcap: 
+#| - "Linear Regression with free paramaters, $y=ax+b$ "
+#| - "Linear Regrassion $y=x$ "
+
 plt.close()
@@
 plt.show()
+
+data = dt[["logKLum", "logL_K"]]
+data = dt[~np.isnan(data["logL_K"])]
+logL_K_LCV = data['logKLum']  # Replace with actual column names
+logL_K_HECATE = data['logL_K']  # Replace with actual column names
+
+# Plot the data and both fits
+plt.figure(figsize=(8, 6))
+plt.scatter(logL_K_LCV, logL_K_HECATE, color='blue', label='Data', alpha =0.5, edgecolors="white")
+
+# Plot free fit (with intercept)
+plt.plot(logL_K_LCV, results.slope * logL_K_LCV + results.intercept, color='green', label='Free Fit: $log(L_{K,HEC})=$'+ f'{results.slope:.2f}'+ "$\cdot log(L_{K,LCV})$"+ f'{results.intercept:.2f}'+f"\n $R^2 = {results.rvalue**2*100:.2f}\%$")
+
+slope_forced = 1
+# Plot forced fit (through the origin)
+results_f = scipy.stats.linregress(x = logL_K_HECATE, y = slope_forced*logL_K_LCV)
+plt.plot(logL_K_LCV, slope_forced * logL_K_LCV, color='red', label='Forced Fit: $log(L_{K,HEC})=$' +f' = {slope_forced:.2f}'"$\cdot log(L_{K,LCV})$"+f"\n $R^2 = {results_f.rvalue**2*100:.2f}\%$")
+
+plt.xlabel("log($L_{K, LCV} $"+"/{})".format(dt["KLum"].unit.to_string("latex")))
+plt.ylabel("log($L_{K, HECATE} $"+"/{})".format(dt["KLum"].unit.to_string("latex")))
+plt.legend()
+plt.grid(True)
+plt.show()
 ```
@@
 
-So as we can see the usage of a linear fitting is not correct here.
-But we can clearly see a linear correlation.
-
-We will use the relative difference of the two luminosities, to see if statistically they are the same:
-
-```{python}
-#| echo: false
-dt["diff_L_K"] = relative_diff(hec = dt["logL_K"].value, lcv = dt["logKLum"])
-temp = dt[["logKLum", "logL_K", "diff_L_K"]].to_pandas()
-sns.histplot(temp["diff_L_K"], kde = True)
-plt.xlabel("Percentage change [%]")
-plt.title("K-band Luminosities")
-plt.show()
-```
-
-```{python}
-temp.rename(columns = {"logKLum":"log(L_K)_{LCV}$", "logL_K":"log(L_K)_{HEC}", "diff_L_K":"Percentage Change [%]"}, inplace=True)
-```
-
-```{python}
-temp.describe(percentiles=[])
-```
+To assess whether the two galaxy catalogs have a 1-1 correlation, I applied two types of linear fits to the data: a free fit and a forced fit.
+The free fit allows both the slope and intercept to vary freely, meaning the line can take on any slope and can cross the y-axis at any point.
+In contrast, for the forced fit, I set the slope to exactly 1 and fixed the line to pass through the origin, meaning the equation becomes y=xy=x.
+This forced fit represents a perfect 1-1 relationship, where the values from one catalog should match the other exactly, without any shift or scaling.
+
+After fitting the data using both methods, I calculated the $R^2$ value for each fit.
+In this case, both the free fit and the forced fit produced very similar $R^2$ values, around 87.13%[^3], indicating that both fits explain about 87% of the variance in the data (@fig-klum-compare).
+
+[^3]: The difference of the linear regression with the free parameters and the forced regression is $\Delta R^2 = 1.14\cdot 10^{-13}\%$
+
+The fact that both the free and forced fits have nearly identical $R^2$ values suggests that the data closely follows a 1-1 relationship.
+In the free fit, the best-fitting line had a very small intercept, which shows that allowing the line to shift vertically did not significantly improve how well the line fits the data.
+This strongly indicates that the data from the two catalogs are well-aligned and follow the relationship y=x quite closely, which is what we expect if the catalogs are in good agreement.
+
+While these results are promising, it's important to note that achieving an $R^2$ of 87%—while high—doesn't necessarily prove a perfect 1-1 correlation.
+There may still be small discrepancies or uncertainties in the data that prevent a perfect match.
+Nonetheless, the fact that fixing the slope to 1 and forcing the line through the origin gave such a good result suggests that the two catalogs are very consistent with each other.
 
@@
 ```{python}
-#| label: fig-Mag-compare
+#| label: fig-mag-compare
 #| layout-ncol: 2
@@
 
-- $M_B$: it is a 1-1 correlation, since the average error $M_{B,HECATE} = 0.4\ mag$, so the itercept is smaller than the error
-- $M_K$: we need to examine it more, since the intercept is bigger than the error $M_{K,HECATE} = 0.09\ mag$
+-   $M_B$: it is a 1-1 correlation, since the average error $M_{B,HECATE} = 0.4\ mag$, so the itercept is smaller than the error (@fig-mag-compare)
+-   $M_K$: we need to examine it more, since the intercept is bigger than the error $M_{K,HECATE} = 0.09\ mag$ (@fig-mag-compare)
 
@@
 
-\[?\] this 5\% average in the difference probably exists because of the low number of galaxies we compare, so we can ignore it.
+\[?\] this 5% mean in the difference probably exists because of the low number of galaxies we compare, so we can ignore it.
 
@@
 #| layout-align: center
-#| fig-cap: "Comparison of the $SFR_{FUV}-SFR_{Ha} of the galaxies"
+#| fig-cap: "Comparison of the $SFR_{FUV}-SFR_{Ha}$ of the galaxies"
 #| fig-subcap: 
@@
 
-The SFR according to @kroupaConstraintsStarFormation2020, can be calculated from the mean of SFR from the Ha and FUV, for $SFR>10^{-3}\ M_\odot\, yr^{-1}$.
-As we can see from the plots @fig-sfr-lcv it is a good aproximation for all SFR's
+The SFR according to (@kroupaConstraintsStarFormation2020), can be calculated from the mean of SFR from the Ha and FUV, for $SFR>10^{-3}\ M_\odot\, yr^{-1}$.
+As we can see from the plots (@fig-sfr-lcv) it is a good aproximation for all SFR's
 
@@
 
-?EXPLANATION? this low correlation maybe comes from the inaccuracy/approximation of @kroupaConstraintsStarFormation2020
+\[?\]EXPLANATION this low correlation maybe comes from the inaccuracy/approximation of (@kroupaConstraintsStarFormation2020)
+
+The reason is that this aproximation is accurate if we consider a stable SFR over time.
+However, we tend to observe higher Ha for more recent SF activity.
+(we discussed it in our last meeting, I need a refrence).
 
@@
 ::: panel-tabset
-
 ### Stellar Masses Comparison
@@
 ```
-```{python}
-
-dt["diff_M"] =  relative_diff(hec = dt["logM_HEC"].data, lcv = dt["logStellarMass"])
-temp = dt[["diff_M"]].to_pandas()
-sns.histplot(temp, kde = True)
-plt.title("Percentage change Distribution [%]")
-plt.xlabel(r"$\log_{10}M_*$ "+f"[{dt['logM_HEC'].unit}]")
-plt.show()
-plt.close()
-
-```
 
@@
 ```
+
+The heatmap is used to visually assess the correlations between different mass estimates of the galaxies, including the mass within the Holmberg radius ($M_{26}$), the HI gas mass ($M_{HI}$​), the stellar mass from the HECATE catalog ($M_{HEC}$​), and the stellar mass derived assuming a mass-to-light ratio of 0.6 (StellarMass).
+The purpose of this visualization is to quickly identify whether these different mass measurements show consistent correlations, which would suggest that they capture similar aspects of the galaxies' mass distributions.
+
+This quick check using the heatmap helps confirm that, while different catalogs and methods might have their own specific ways of calculating galaxy masses, the overall mass estimates align well, offering a solid basis for further analysis of galaxy properties.
 :::
+
+------------------------------------------------------------------------

### 2024-10-05 compare/compare.tex
def and expl

@@
 \usepackage{xcolor}
-\ifLuaTeX
-  \usepackage{luacolor}
-  \usepackage[soul]{lua-ul}
-\else
-  \usepackage{soul}
-
-\fi
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
 
-In this script we will compare 2 catalogs Kovlakas et al. (2021) and
-Karachentsev and Kaisina (2013)
+In this script we will compare 2 catalogs, HECATE (Kovlakas et al.
+(2021)) and LCV (Karachentsev and Kaisina (2013))
 
@@
 Checking for completeness in galaxy catalogs is essential to ensure that
-the data accurately represents the true population of galaxies.
-Incomplete catalogs can lead to biased results in statistical studies,
-such as the distribution of galaxy luminosity, mass, or star formation
-rates. Additionally, missing galaxies, especially those at faint
-magnitudes or large distances, can distort cosmological measurements and
-hinder our understanding of galaxy formation and evolution.
+the data accurately represents the true population of galaxies, for
+\(z \approx 0\). Incomplete catalogs can lead to biased results in
+statistical studies, such as the distribution of galaxy luminosity,
+mass, or star formation rates. Additionally, missing galaxies,
+especially those at faint magnitudes or large distances, can distort
+cosmological measurements and hinder our understanding of galaxy
+formation and evolution.
 
@@
 The local volume selection has been made by taking into account galaxies
-with: 1. Radial velocities of
+with:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  Radial velocities of
   \begin{equation}\phantomsection\label{eq-lcv-vel}{
    V_{LG}<600 \text{ km}\cdot\text{m}^{-1}
-    }\end{equation} 2. Distances of D\textless11 Mpc
+  }\end{equation}
+\item
+  Distances of \begin{equation}\phantomsection\label{eq-lcv-dis}{
+     D<11\ \text{Mpc}
+     }\end{equation}
+\end{enumerate}
 
@@
 
+\subsubsection{Difficulties in calculating the
+Completeness}\label{difficulties-in-calculating-the-completeness}
+
+As explained in (Karachentsev, Makarov, and Kaisina (2013)), it is
+difficult to calculate the completeness of the catalog.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Completeness within a 10 Mpc radius is difficult to assess due to: -
+  Variability in galaxy properties (luminosity, size, surface
+  brightness, gas content) - Errors in distance measurements
+  (Tully--Fisher method errors of \textasciitilde20--25\%), especially
+  at the 10 Mpc boundary.
+
   \begin{itemize}
@@
   \item
-  Completeness within a 10 Mpc radius is difficult to assess due to:
-
-  \begin{itemize}
-  \tightlist
-  \item
-    Variability in galaxy properties (luminosity, size, surface
-    brightness, gas content)
-  \item
-    Errors in distance measurements (Tully--Fisher method errors of
-    \textasciitilde20--25\%), especially at the 10 Mpc boundary.
-
-    \begin{itemize}
-    \tightlist
-    \item
     Accurate distances are mainly known within \textasciitilde5 Mpc.
-    \end{itemize}
-  \item
-    Non-Hubble motions (\textasciitilde300 km/s) may make up half of the
-    adopted velocity constraint Equation~\ref{eq-lcv-vel}
-
-    \begin{itemize}
-    \tightlist
+  \item
+    Non-Hubble motions (\textasciitilde300 km/s)\footnote{\emph{Non-Hubble
+      motion refers to the component of a galaxy's velocity that
+      deviates from the uniform expansion of the universe, described by
+      the equation} \(V= H_0 d + v_p\),where \(V\) is the total
+      velocity, \(H_0 d\) represents the Hubble flow, and
+      \(v_p\)\hspace{0pt} is the peculiar velocity. {``Essay''} (n.d.)}
+    may make up half of the adopted velocity constraint
+    (Equation~\ref{eq-lcv-vel})
   \item
@@
     inclusion of false ``nearby'' dwarf galaxies in the
-      LV''Karachentsev, Makarov, and Kaisina (2013)
-    \item
-      photographic emulsion defect -\textgreater{} exotic cases of
-      galaxies -\textgreater{} radial velocity of \(+614 km s^{−1}\)
+    LV''(Karachentsev, Makarov, and Kaisina (2013))
   \end{itemize}
-  \end{itemize}
-\item
-  Astro-Spam and Survey Errors:
-
-  \begin{itemize}
-  \tightlist
-  \item
-    Automatic surveys produce false detections (e.g., stars
-    misclassified as galaxies, high-velocity clouds mistaken for
-    dwarfs).
-  \end{itemize}
-\item
-  Conditional Completeness Estimate:
-
-  \begin{itemize}
-  \tightlist
-  \item
-    Galaxies brighter than \(M_B^c = -11^m\) or with linear diameters
-    larger than \(A_{26} = 1.0\) kpc show (40--60)\% completeness.
-  \item
-    ``among the members of the Local Group (D \textless{} 1 Mpc), only
-    half of the galaxies have absolute magnitudes brighter than −11m.
-    Consequently, more than half of the ultra-faint dwarf companions
-    around normal galaxies, like the Sombrero galaxy (D = 9.3 Mpc),
-    still remain outside our field of view.''
-  \end{itemize}
-\item
-  Undetected Ultra-Faint Dwarfs:
-
-  \begin{itemize}
-  \tightlist
-  \item
-    Many faint dwarf galaxies remain undetected beyond the Local Group.
-    Estimated population of undetected dwarfs could be as large as
-    \(10^3–10^4\) within the LV.
-  \end{itemize}
-\item
-  Surface Brightness Distribution:
-
-  \begin{itemize}
-  \tightlist
-  \item
-    Surface brightness remains consistent across distances, except for
-    ultra-faint dwarfs (\(SB <31 \text{mag}\cdot\text{arcsec}^{-2}\)).
-  \item
-    Faintest dwarf galaxies are detectable only nearby due to their
-    resolution into individual stars.
-  \end{itemize}
-\item
-  Luminosity-Size Relationship:
-
-  \begin{itemize}
-  \tightlist
-  \item
-    Observations align with cosmological models predicting \(L\sim A^3\)
-    Navarro, Frenk, and White (1996), though deviations occur for
-    extremely low surface brightness galaxies.
-  \item
-    ``The deviation from it at the extremely low surface brightness end
+\item
+  Astro-Spam and Survey Errors: - Automatic surveys produce false
+  detections (e.g., stars misclassified as galaxies, high-velocity
+  clouds mistaken for dwarfs).
+\item
+  Conditional Completeness Estimate: - Galaxies brighter than
+  \(M_B^c = -11^m\) or with linear diameters larger than
+  \(A_{26} = 1.0\) kpc show (40--60)\% completeness. - ``among the
+  members of the Local Group (D \textless{} 1 Mpc), only half of the
+  galaxies have absolute magnitudes brighter than −11m. Consequently,
+  more than half of the ultra-faint dwarf companions around normal
+  galaxies, like the Sombrero galaxy (D = 9.3 Mpc), still remain outside
+  our field of view.''
+\item
+  Undetected Ultra-Faint Dwarfs: - Many faint dwarf galaxies remain
+  undetected beyond the Local Group. Estimated population of undetected
+  dwarfs could be as large as \(10^3–10^4\) within the LV.
+\item
+  Surface Brightness Distribution: - Surface brightness remains
+  consistent across distances, except for ultra-faint dwarfs
+  (\(SB <31 \text{mag}\cdot\text{arcsec}^{-2}\)). - Faintest dwarf
+  galaxies are detectable only nearby due to their resolution into
+  individual stars.
+\item
+  Luminosity-Size Relationship: - Observations align with cosmological
+  models predicting \(L\sim A^3\) (Navarro, Frenk, and White (1996)),
+  though deviations occur for extremely low surface brightness galaxies.
+  - ``The deviation from it at the extremely low surface brightness end
   is due to a systematic overestimation of dwarf galaxy sizes, the
@@
   isophote.''
-  \end{itemize}
-\end{itemize}
+\end{enumerate}
 
@@
 
-\subsubsection{Distance}\label{distance}
-
 \begin{figure}
@@
 
-As we can see from the histograms Figure~\ref{fig-dis-comp} and
-Figure~\ref{fig-type-comp} the sample of unique galaxies of each
+As we can see from the histograms (Figure~\ref{fig-dis-comp}) and
+(Figure~\ref{fig-type-comp}) the sample of unique galaxies of each
 catalog, gets smaller by an almost constant proportion (Inner join).
@@
 
-\subsection{\texorpdfstring{Scatter plots and \(R^2\)
-calculation}{Scatter plots and R\^{}2 calculation}}\label{scatter-plots-and-r2-calculation}
+For the comparison of our data we will mainly use two methods: linear
+regression and comparison of the distributions.
+
+For the linear regression out main tools are scatter plots and \(R^2\)
 
@@
 \def\labelenumi{\arabic{enumi}.}
-\tightlist
 \item
@@
 \item
-  Slope of the Fitted Line: Should be close to 1 for a 1-1
-  correlation.\footnote{Some data seem to have a very good linear
-    correlation but they have many outliers. This is why we will clip
-    the outliers with \(\sigma > 3\)}
-\end{enumerate}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{2}
-\tightlist
+  Slope of the Fitted Line: Should be close to 1 for a 1-1 correlation.
 \item
@@
 \setcounter{enumi}{3}
-\tightlist
-\item
-  \ul{Plots}: Plots are essential for visually assessing the
-  relationship between two datasets, identifying correlations, trends,
-  and outliers, and evaluating the fit of linear models.
-\end{enumerate}
-
-\begin{itemize}
-\tightlist
-\item
-  Histograms: Because not all of our data have the same number of
-  counts, the comparison with histograms between data that are not the
-  same, doesn't help us right now.\footnote{When we will use the outer
-    join table we could use histograms due to the large number of
-    counts.} This is why we will only use histograms for comparing the
-  distribution of same-data columns normalized by their maximum value
-\end{itemize}
-
-\begin{itemize}
-\item
+\item
+  Plots: Plots are essential for visually assessing the relationship
+  between two datasets, identifying correlations, trends, and outliers,
+  and evaluating the fit of linear models. Beside scatter plots and
+  histograms, another useful plot is the Correlation Heatmap.
+
+  \begin{quote}
   Correlation Heatmaps: A correlation heatmap is a graphical tool that
@@
   correlations.
-\item
-  Kernel Density Estimate (KDE) plot: The KDE plot visually represents
-  the distribution of data, providing insights into its shape, central
+  \end{quote}
+\end{enumerate}
+
+For the distrabution comparisons we will use histograms and Kernel
+Density Estimate (KDE) plots. The KDE plots visually represent the
+distribution of data, providing insights into its shape, central
 tendency, and spread.
-\end{itemize}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{4}
+
+Finally, we will examine the percentage change for each galaxy.
+
+\begin{itemize}
 \tightlist
@@
   minimum, the maximum and the mean value of the difference.
-\end{enumerate}
+\end{itemize}
 
@@
 
-\begin{longtable}[]{@{}cccc@{}}
+\begin{longtable}[]{@{}
+  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2329}}
+  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2329}}
+  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2329}}
+  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.3014}}@{}}
 \toprule\noalign{}
-LCV & HECATE & Description & Pearson Correlation {[}-1,1{]} \\
+\begin{minipage}[b]{\linewidth}\centering
+LCV
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+HECATE
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Description
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Pearson Correlation {[}-1,1{]}
+\end{minipage} \\
 \midrule\noalign{}
@@
   The average error of the distance in the HECATE catalog is
-  \(\overline{E_D} = \pm 1.6\) Mpc, so the intercept is included in the
-  error.
+  \(\overline{\delta D} = \pm 1.6\) Mpc, so the intercept is included in
+  the error.
 \item
@@
   The average error of the radial velocity in the HECATE catalog is
-  \(\overline{E_V} = \pm 12\text{km}\cdot s^{-1}\) , so the intercept is
-  included in the error.
+  \(\overline{\delta V} = \pm 12\text{km}\cdot s^{-1}\) , so the
+  intercept is included in the error.
 \item
@@
 
-\includegraphics{compare_files/figure-pdf/cell-15-output-1.pdf}
+\begin{figure}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-vel-pairplot-output-1.pdf}
+
+}
+
+\caption{\label{fig-vel-pairplot}The correlation Matrix of the
+Velocities. The lower left triangle is is composed of the scatter plots
+of the various velocities, the diagonal shows their distrubution and the
+upper right triangle shows the correlations of the Velocities}
+
+\end{figure}%
 
@@
 but from a different frame of reference.
+
+The strong correlation between the velocities reported by the HECATE and
+LCV catalogs can be attributed to the fact that both measure the same
+intrinsic galaxy velocities but reference them to different frames. For
+instance, velocities can be corrected for the movement of the Earth
+(heliocentric frame) or the for the Virgo-infall. These corrections
+shift the measured velocity slightly, but the fundamental measurement
+remains consistent. This explains why the velocities are highly
+correlated, as they represent the same physical phenomenon but adjusted
+for different reference points.
+
+\newpage{}
 
@@
 
-\begin{figure}
-
-\begin{minipage}{0.50\linewidth}
-
-\centering{
-
-\includegraphics{compare_files/figure-pdf/fig-types-compare-output-1.pdf}
-
-}
-
-\subcaption{\label{fig-types-compare-1}All the galaxies, without the
-correction}
-
-\end{minipage}%
-%
-\begin{minipage}{0.50\linewidth}
-
-\centering{
-
-\includegraphics{compare_files/figure-pdf/fig-types-compare-output-2.pdf}
-
-}
-
-\subcaption{\label{fig-types-compare-2}Comparison with the correction
-\(|{T_{HECATE}-T_{LCV}}|<7\)}
-
-\end{minipage}%
-
-\caption{\label{fig-types-compare}Comparison of the Types of galaxies}
-
-\end{figure}%
-
 ``Morphological type of galaxy in the numerical code according to the
@@
 errors, such objects may ``jump'' from one end of the T scale to the
-other.'' Karachentsev, Makarov, and Kaisina (2013)
+other.'' (Karachentsev, Makarov, and Kaisina (2013))
+
+\begin{figure}
+
+\begin{minipage}{0.50\linewidth}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-types-compare-output-1.pdf}
+
+}
+
+\subcaption{\label{fig-types-compare-1}All the galaxies, without the
+correction}
+
+\end{minipage}%
+%
+\begin{minipage}{0.50\linewidth}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-types-compare-output-2.pdf}
+
+}
+
+\subcaption{\label{fig-types-compare-2}Comparison with the correction
+\(|{T_{HECATE}-T_{LCV}}|<7\)}
+
+\end{minipage}%
+
+\caption{\label{fig-types-compare}Comparison of the Types of galaxies}
+
+\end{figure}%
 
@@
   why we see a difference in the distribution of
-  Figure~\ref{fig-type-comp}
+  (Figure~\ref{fig-type-comp})
 \end{itemize}
@@
 with: \[
-|{T_{HECATE}-T_{LCV}}|<7
+|{T_{HECATE}-T_{LCV}}|<\sigma_{T_{LCV}} = 4.8
 \]
@@
   The average uncertainty of the morphological type in the HECATE
-  catalog is \(\overline{E_T} = \pm 1.4\), so the intercept is included
-  in the error.
+  catalog is \(\overline{\delta T} = \pm 1.4\), so the intercept is
+  included in the error.
 \item
@@
 \begin{minipage}{0.50\linewidth}
-\includegraphics{compare_files/figure-pdf/cell-24-output-1.pdf}\end{minipage}%
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-incl-compare-output-1.pdf}
+
+}
+
+\subcaption{\label{fig-incl-compare-1}Distribution of the Inclination of
+the galaxies}
+
+\end{minipage}%
 %
 \begin{minipage}{0.50\linewidth}
-\includegraphics{compare_files/figure-pdf/cell-24-output-2.pdf}\end{minipage}%
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-incl-compare-output-2.pdf}
+
+}
+
+\subcaption{\label{fig-incl-compare-2}Distribution of the Percentage
+Change}
+
+\end{minipage}%
+
+\caption{\label{fig-incl-compare}Comparison of the Inclination of the
+galaxies}
 
@@
 \([\sim 30^\circ,\sim 80^\circ]\), the values of the LCV inclination are
-higher. However, since their means, median, min and maxes are similar
-and the percentage change is practically 0\% (mean, median, \(\sigma\) =
-0 with a range \([-3\%,1\%]\)), we can ignore the differences and assume
-they are the same values.
+higher (Figure~\ref{fig-incl-compare}). However, since their means,
+median, min and maxes are similar and the percentage change is
+practically 0\% (mean, median, \(\sigma\) = 0 with a range
+\([-3\%,1\%]\)), we can ignore the differences and assume they are the
+same values.
 
@@
 
-it is not very clear if we truly have a correlation or not. We need to
-see the linear correlation of the decimal logarithms.
+it is not very clear if we truly have a correlation or not
+(Figure~\ref{fig-axis-compare-1}). We need to see the linear correlation
+of the decimal logarithms (Figure~\ref{fig-axis-compare-2}).
 
 \(\overline{R_1} = 3.9\) {[}arcmin{]}, \(\overline{a_{26}} = 9.3\)
-{[}arcmin{]}, so the intercept is negligable. \[
+{[}arcmin{]}, so the intercept is negligable.
+
+\[
 R_1 = 0.48\cdot a_{26}-0.34 \sim \frac{1}{2}a_{26}
@@
 
+\begin{minipage}{0.50\linewidth}
+
 \centering{
@@
 
+\subcaption{\label{fig-klum-compare-1}Linear Regression with free
+paramaters, \(y=ax+b\)}
+
+\end{minipage}%
+%
+\begin{minipage}{0.50\linewidth}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-klum-compare-output-2.pdf}
+
+}
+
+\subcaption{\label{fig-klum-compare-2}Linear Regrassion \(y=x\)}
+
+\end{minipage}%
+
 \caption{\label{fig-klum-compare}Comparison of the \(L_K\) of the
-galaxies}
+galaxies.}
 
@@
 
-So as we can see the usage of a linear fitting is not correct here. But
-we can clearly see a linear correlation.
-
-We will use the relative difference of the two luminosities, to see if
-statistically they are the same:
-
-\includegraphics{compare_files/figure-pdf/cell-29-output-1.pdf}
-
-\begin{longtable}[]{@{}llll@{}}
-\toprule\noalign{}
-& log(L\_K)\_\{LCV\}\$ & log(L\_K)\_\{HEC\} & Percentage Change
-{[}\%{]} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-count & 287 & 70 & 70 \\
-mean & 8 & 9 & -4 \\
-std & 1 & 1 & 8 \\
-min & 3 & 5 & -48 \\
-50\% & 8 & 9 & -0 \\
-max & 11 & 11 & 7 \\
-\end{longtable}
+To assess whether the two galaxy catalogs have a 1-1 correlation, I
+applied two types of linear fits to the data: a free fit and a forced
+fit. The free fit allows both the slope and intercept to vary freely,
+meaning the line can take on any slope and can cross the y-axis at any
+point. In contrast, for the forced fit, I set the slope to exactly 1 and
+fixed the line to pass through the origin, meaning the equation becomes
+y=xy=x. This forced fit represents a perfect 1-1 relationship, where the
+values from one catalog should match the other exactly, without any
+shift or scaling.
+
+After fitting the data using both methods, I calculated the \(R^2\)
+value for each fit. In this case, both the free fit and the forced fit
+produced very similar \(R^2\) values, around 87.13\%\footnote{The
+  difference of the linear regression with the free parameters and the
+  forced regression is \(\Delta R^2 = 1.14\cdot 10^{-13}\%\)},
+indicating that both fits explain about 87\% of the variance in the data
+(Figure~\ref{fig-klum-compare}).
+
+The fact that both the free and forced fits have nearly identical
+\(R^2\) values suggests that the data closely follows a 1-1
+relationship. In the free fit, the best-fitting line had a very small
+intercept, which shows that allowing the line to shift vertically did
+not significantly improve how well the line fits the data. This strongly
+indicates that the data from the two catalogs are well-aligned and
+follow the relationship y=x quite closely, which is what we expect if
+the catalogs are in good agreement.
+
+While these results are promising, it's important to note that achieving
+an \(R^2\) of 87\%---while high---doesn't necessarily prove a perfect
+1-1 correlation. There may still be small discrepancies or uncertainties
+in the data that prevent a perfect match. Nonetheless, the fact that
+fixing the slope to 1 and forcing the line through the origin gave such
+a good result suggests that the two catalogs are very consistent with
+each other.
 
@@
   \(M_{B,HECATE} = 0.4\ mag\), so the itercept is smaller than the error
+  (Figure~\ref{fig-mag-compare})
 \item
@@
   than the error \(M_{K,HECATE} = 0.09\ mag\)
+  (Figure~\ref{fig-mag-compare})
 \end{itemize}
 
-\includegraphics{compare_files/figure-pdf/cell-35-output-1.pdf}
-
-\includegraphics{compare_files/figure-pdf/cell-35-output-2.pdf}
+\includegraphics{compare_files/figure-pdf/cell-26-output-1.pdf}
+
+\includegraphics{compare_files/figure-pdf/cell-26-output-2.pdf}
 
@@
 
-{[}?{]} this 5\% average in the difference probably exists because of
-the low number of galaxies we compare, so we can ignore it.
+{[}?{]} this 5\% mean in the difference probably exists because of the
+low number of galaxies we compare, so we can ignore it.
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-38-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-29-output-1.pdf}
 
@@
 
-\caption{\label{fig-sfr-lcv}Comparison of the \$SFR\_\{FUV\}-SFR\_\{Ha\}
-of the galaxies}
+\caption{\label{fig-sfr-lcv}Comparison of the \(SFR_{FUV}-SFR_{Ha}\) of
+the galaxies}
 
@@
 
-The SFR according to Kroupa et al. (2020), can be calculated from the
+The SFR according to (Kroupa et al. (2020)), can be calculated from the
 mean of SFR from the Ha and FUV, for \(SFR>10^{-3}\ M_\odot\, yr^{-1}\).
-As we can see from the plots Figure~\ref{fig-sfr-lcv} it is a good
+As we can see from the plots (Figure~\ref{fig-sfr-lcv}) it is a good
 aproximation for all SFR's
@@
 
-?EXPLANATION? this low correlation maybe comes from the
-inaccuracy/approximation of Kroupa et al. (2020)
+{[}?{]}EXPLANATION this low correlation maybe comes from the
+inaccuracy/approximation of (Kroupa et al. (2020))
+
+The reason is that this aproximation is accurate if we consider a stable
+SFR over time. However, we tend to observe higher Ha for more recent SF
+activity. (we discussed it in our last meeting, I need a refrence).
 
@@
 
-\includegraphics{compare_files/figure-pdf/cell-44-output-1.pdf}
-
 \[
@@
 
-\includegraphics{compare_files/figure-pdf/cell-45-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-35-output-1.pdf}
+
+The heatmap is used to visually assess the correlations between
+different mass estimates of the galaxies, including the mass within the
+Holmberg radius (\(M_{26}\)), the HI gas mass (\(M_{HI}\)\hspace{0pt}),
+the stellar mass from the HECATE catalog (\(M_{HEC}\)\hspace{0pt}), and
+the stellar mass derived assuming a mass-to-light ratio of 0.6
+(StellarMass). The purpose of this visualization is to quickly identify
+whether these different mass measurements show consistent correlations,
+which would suggest that they capture similar aspects of the galaxies'
+mass distributions.
+
+This quick check using the heatmap helps confirm that, while different
+catalogs and methods might have their own specific ways of calculating
+galaxy masses, the overall mass estimates align well, offering a solid
+basis for further analysis of galaxy properties.
+
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
 
@@
 \begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-Essay}
+{``Essay.''} n.d. Accessed October 5, 2024.
+\url{https://ned.ipac.caltech.edu/level5/Glossary/Essay_pecmotion.html}.
+
 \bibitem[\citeproctext]{ref-karachentsevSTARFORMATIONPROPERTIES2013a}

### 2024-10-19 compare/compare.qmd
minor fixes

@@
 
-In this script we will compare 2 catalogs, HECATE (@kovlakasHeraklionExtragalacticCatalogue2021) and LCV ([@karachentsevUPDATEDNEARBYGALAXY2013, @karachentsevSTARFORMATIONPROPERTIES2013a])
+In this script we will compare 2 catalogs, HECATE (@kovlakasHeraklionExtragalacticCatalogue2021) and LVG ([@karachentsevUPDATEDNEARBYGALAXY2013, @karachentsevSTARFORMATIONPROPERTIES2013a])
 
@@
 outer = QTable(ascii.read("../tables/outer_join.ecsv"), masked=True)
-hec_not_lcv = QTable(ascii.read("../tables/HEC_not_LCV_join.ecsv"), masked=True)
-lcv_not_hec = QTable(ascii.read("../tables/LCV_not_HEC_join.ecsv"), masked=True)
-
-lcv = QTable(ascii.read("../tables/final_table.ecsv"), masked=True)
+hec_not_lvg = QTable(ascii.read("../tables/HEC_not_LVG_join.ecsv"), masked=True)
+lvg_not_hec = QTable(ascii.read("../tables/LVG_not_HEC_join.ecsv"), masked=True)
+
+lvg = QTable(ascii.read("../tables/final_table.ecsv"), masked=True)
 hec = QTable(ascii.read("../tables/HECATE_LCV.ecsv"), masked=True)
@@
 
-The dataset we are going to use for the comparison (inner join) consists of `{python} len(dt)` galaxies and `{python} len(dt.colnames)` columns.
+The dataset we are going to use for the comparison (inner join) consists of `{python} len(dt)` galaxies and `{python} len(dt.colnames)` columns with their physical  characteristics.
 
@@
 
-## Completeness of the LCV Catalog
+## Completeness of the LVG Catalog
 
@@
 
-1.  Radial velocities of $$
+1.  Radial velocities of
+
+$$
      V_{LG}<600 \text{ km}\cdot\text{m}^{-1}
-    $$ {#eq-lcv-vel}
-
-2.  Distances of $$
+$$ {#eq-lvg-vel}
+
+1.  Distances of
+
+$$
        D<11\ \text{Mpc}
-       $$ {#eq-lcv-dis}
+$$ {#eq-lvg-dis}
 
@@
     -   Accurate distances are mainly known within \~5 Mpc.
-    -   Non-Hubble motions (\~300 km/s)[^1] may make up half of the adopted velocity constraint (@eq-lcv-vel)
+    -   Non-Hubble motions (\~300 km/s)[^1] may make up half of the adopted velocity constraint (@eq-lvg-vel)
         -   Solution for our usage: only keep the galaxies inside a radius of $D=11 Mpc$
     -   HI sources in surveys with low angular resolution: "The presence around our Galaxy of hundreds of high-velocity clouds with low line-of-sight velocities and small W50 widths also provokes the inclusion of false “nearby” dwarf galaxies in the LV"(@karachentsevUPDATEDNEARBYGALAXY2013)
-2.  Astro-Spam and Survey Errors: - Automatic surveys produce false detections (e.g., stars misclassified as galaxies, high-velocity clouds mistaken for dwarfs).
-3.
-Conditional Completeness Estimate: - Galaxies brighter than $M_B^c = -11^m$ or with linear diameters larger than $A_{26} = 1.0$ kpc show (40–60)% completeness.
-- "among the members of the Local Group (D \< 1 Mpc), only half of the galaxies have absolute magnitudes brighter than −11m.
-Consequently, more than half of the ultra-faint dwarf companions around normal galaxies, like the Sombrero galaxy (D = 9.3 Mpc), still remain outside our field of view."
-4.  Undetected Ultra-Faint Dwarfs: - Many faint dwarf galaxies remain undetected beyond the Local Group. Estimated population of undetected dwarfs could be as large as $10^3–10^4$ within the LV.
-5.
-Surface Brightness Distribution: - Surface brightness remains consistent across distances, except for ultra-faint dwarfs ($SB <31 \text{mag}\cdot\text{arcsec}^{-2}$).
-- Faintest dwarf galaxies are detectable only nearby due to their resolution into individual stars.
-6.
-Luminosity-Size Relationship: - Observations align with cosmological models predicting $L\sim A^3$ (@navarroStructureColdDark1996), though deviations occur for extremely low surface brightness galaxies.
-- "The deviation from it at the extremely low surface brightness end is due to a systematic overestimation of dwarf galaxy sizes, the brightness profiles of which lie entirely below the Holmberg isophote."
 
@@
 @Essay
+
+2.  Astro-Spam and Survey Errors:
+    -   Automatic surveys produce false detections (e.g., stars misclassified as galaxies, high-velocity clouds mistaken for dwarfs).
+
+3.  Conditional Completeness Estimate: - Galaxies brighter than $M_B^c = -11^m$ or with linear diameters larger than $A_{26} = 1.0$ kpc show (40–60)% completeness.
+    -   "among the members of the Local Group (D \< 1 Mpc), only half of the galaxies have absolute magnitudes brighter than $−11^m$.
+Consequently, more than half of the ultra-faint dwarf companions around normal galaxies, like the Sombrero galaxy (D = 9.3 Mpc), still remain outside our field of view."
+
+4.  Undetected Ultra-Faint Dwarfs:
+    -   Many faint dwarf galaxies remain undetected beyond the Local Group. Estimated population of undetected dwarfs could be as large as $10^3–10^4$ within the LV.
+
+5.  Surface Brightness Distribution:
+    -   Surface brightness remains consistent across distances, except for ultra-faint dwarfs ($SB <31 \text{mag}\cdot\text{arcsec}^{-2}$).
+    -   Faintest dwarf galaxies are detectable only nearby due to their resolution into individual stars.
+
+6.  Luminosity-Size Relationship:
+    -   Observations align with cosmological models predicting $L\sim A^3$ (@navarroStructureColdDark1996), though deviations occur for extremely low surface brightness galaxies.
+    -   "The deviation from it at the extremely low surface brightness end is due to a systematic overestimation of dwarf galaxy sizes, the brightness profiles of which lie entirely below the Holmberg isophote."
 
@@
 data = {
-    "Table": ["Inner join", "Outer join", "LCV", "HECATE", "Unique galaxies in LCV", "Unique Galaxies in Hecate"],
-    "Number of galaxies": [len(dt), len(outer), len(lcv), len(hec), len(lcv_not_hec), len(hec_not_lcv)]
+    "Table": ["Inner join", "Outer join", "LVG", "HECATE", "Unique galaxies in LVG", "Unique Galaxies in Hecate"],
+    "Number of galaxies": [len(dt), len(outer), len(lvg), len(hec), len(lvg_not_hec), len(hec_not_lvg)]
 }
@@
 
-Completeness (LCV)= `{python} round(len(dt)/len(lcv) *100)` %
+Completeness (LVG)= `{python} round(len(dt)/len(lvg) *100)` %
 
@@
 
-Completeness (HECATE)= `{python} round(len(hec_not_lcv)/len(hec)*100)` %
-
-Completeness (LCV)= `{python} round(len(lcv_not_hec)/len(lcv)*100)` %
-
-Combined Completeness =$\frac{\text{Total galaxies in Outer}}{\text{Unique galaxies in HECATE + LCV}}$= `{python} round(len(outer)/(len(lcv_not_hec)+(len(hec_not_lcv))) * 100)` %
+Completeness (HECATE)= `{python} round(len(hec_not_lvg)/len(hec)*100)` %
+
+Completeness (LVG)= `{python} round(len(lvg_not_hec)/len(lvg)*100)` %
+
+Combined Completeness =$\frac{\text{Total galaxies in Outer}}{\text{Unique galaxies in HECATE + LVG}}$= `{python} round(len(outer)/(len(lvg_not_hec)+(len(hec_not_lvg))) * 100)` %
 
@@
     """
-    Creates a table of counts and percentages for each bin based on the chosen dataset (LCV or HEC).
+    Creates a table of counts and percentages for each bin based on the chosen dataset (LVG or HEC).
 
     Parameters:
-    - dataset_choice: A string indicating which dataset to use ("lcv" or "hec")
+    - dataset_choice: A string indicating which dataset to use ("lvg" or "hec")
     - column_name: The column name in the datasets to analyze (default is "Dis")
@@
 
-    if dataset_choice == "lcv":
-        main_df, unique_df, label = lcv, lcv_not_hec, "LCV"
-    elif dataset_choice == "hec" and hec is not None and hec_not_lcv is not None:
-        main_df, unique_df, label = hec, hec_not_lcv, "HEC"
+    if dataset_choice == "lvg":
+        main_df, unique_df, label = lvg, lvg_not_hec, "LVG"
+    elif dataset_choice == "hec" and hec is not None and hec_not_lvg is not None:
+        main_df, unique_df, label = hec, hec_not_lvg, "HEC"
     else:
-        raise ValueError("Invalid dataset choice. Please choose 'lcv' or 'hec' with valid datasets.")
+        raise ValueError("Invalid dataset choice. Please choose 'lvg' or 'hec' with valid datasets.")
 
@@
 
-    for i in range(len(bin_centers)):
-        if main_counts[i] > 0:
-            unique_pct = (unique_counts[i] / main_counts[i]) * 100
-            inner_pct = (inner_counts[i] / main_counts[i]) * 100
-            table_data.append({
-                "Bin Start": round(bin_edges[i]),
-                "Bin End": round(bin_edges[i+1]),
-                f"Unique %": f'{unique_pct:.0f}%',
-                "Inner %": f'{inner_pct:.0f}%'
+    # Calculate percentages in a vectorized way
+    with np.errstate(divide='ignore', invalid='ignore'):  # Handle division by zero safely
+        unique_pct = np.divide(unique_counts, main_counts, out=np.zeros_like(unique_counts, dtype=float), where=main_counts!=0) * 100
+        inner_pct = np.divide(inner_counts, main_counts, out=np.zeros_like(inner_counts, dtype=float), where=main_counts!=0) * 100
+
+    # Construct the DataFrame in a vectorized manner
+    table_df = pd.DataFrame({
+        "Bin Start": np.round(bin_edges[:-1]),
+        "Bin End": np.round(bin_edges[1:]),
+        "Main Counts": main_counts,
+        "Unique Counts": unique_counts,
+        "Unique %": unique_pct,
+        "Inner Counts": inner_counts,
+        "Inner %": inner_pct
     })
-    table_df = pd.DataFrame(table_data)
     return table_df
@@
 #| - "HECATE"
-#| - "LCV"
+#| - "LVG"
 #| label: fig-dis-comp
@@
 main = hec["D"].data
-unique = hec_not_lcv["D"].data
+unique = hec_not_lvg["D"].data
 counts, bin_edges = np.histogram(main)
@@
 ax2.set_yticklabels(y_value)
-ax2.set(xlabel = "Distance [{}]".format(lcv["Dis"].unit), ylabel="Completeness %")
-plt.show()
-
-#LCV
-main = lcv["Dis"].data
-unique = lcv_not_hec["Dis"].data
+ax2.set(xlabel = "Distance [{}]".format(lvg["Dis"].unit), ylabel="Completeness %")
+plt.show()
+
+#LVG
+main = lvg["Dis"].data
+unique = lvg_not_hec["Dis"].data
 counts, bin_edges = np.histogram(main)
@@
 fig, (ax1, ax2) = plt.subplots(2, 1, sharex=True)
-sns.histplot(main, bins = bin_edges, kde = True, label = "LCV", ax = ax1)
-sns.histplot(unique, bins = bin_edges, kde = True, label = "Unique for LCV", ax = ax1)
+sns.histplot(main, bins = bin_edges, kde = True, label = "LVG", ax = ax1)
+sns.histplot(unique, bins = bin_edges, kde = True, label = "Unique for LVG", ax = ax1)
 ax1.legend()
-ax1.set_title("Completenes of Distance for LCV")
+ax1.set_title("Completenes of Distance for LVG")
 ax1.tick_params(labelbottom=True)
@@
 ax2.set_yticklabels(y_value)
-ax2.set(xlabel = "Distance [{}]".format(lcv["Dis"].unit), ylabel="Completeness %")
+ax2.set(xlabel = "Distance [{}]".format(lvg["Dis"].unit), ylabel="Completeness %")
 plt.show()
@@
 #| - "HECATE"
-#| - "LCV"
+#| - "LVG"
 #| label: fig-type-comp
@@
 main = main[~np.isnan(main)]
-unique = hec_not_lcv["T"].data
+unique = hec_not_lvg["T"].data
 unique = unique[~np.isnan(unique)]
@@
 ######
-#LCV
-main = lcv["TType"].data
+#LVG
+main = lvg["TType"].data
 main = main[~np.isnan(main)]
-unique = lcv_not_hec["TType"].data
+unique = lvg_not_hec["TType"].data
 unique = unique[~np.isnan(unique)]
@@
 fig, (ax1, ax2) = plt.subplots(2, 1, sharex=True)
-sns.histplot(main, bins = bin_edges, kde = True, label = "LCV", ax = ax1)
-sns.histplot(unique, bins = bin_edges, kde = True, label = "Unique for LCV", ax = ax1)
+sns.histplot(main, bins = bin_edges, kde = True, label = "LVG", ax = ax1)
+sns.histplot(unique, bins = bin_edges, kde = True, label = "Unique for LVG", ax = ax1)
 ax1.legend()
-ax1.set_title("Completenes of Types for LCV")
+ax1.set_title("Completenes of Types for LVG")
 ax1.tick_params(labelbottom=True)
@@
 
-As we can see from the histograms (@fig-dis-comp) and (@fig-type-comp) the sample of unique galaxies of each catalog, gets smaller by an almost constant proportion (Inner join).
-
-This means there is no bias in the selection of the galaxies.
-
+```{=html}
+<!--As we can see from the histograms (@fig-dis-comp) and (@fig-type-comp) the sample of unique galaxies of each catalog, gets smaller by an almost constant proportion (Inner join).
+
+This means there is no bias in the selection of the galaxies.-->
+```
 # How are we going to compare the data?
@@
 
-For the distrabution comparisons we will use histograms and Kernel Density Estimate (KDE) plots.
+For the distribution comparisons we will use histograms and Kernel Density Estimate (KDE) plots.
 The KDE plots visually represent the distribution of data, providing insights into its shape, central tendency, and spread.
@@
 
-$$\text{Percentage change} = \frac{V_{Hecate} - V_{LCV}}{V_{Hecate}}\cdot 100 \%$$
-
-```{python}
-def relative_diff(hec, lcv):
+$$\text{Percentage change} = \frac{V_{Hecate} - V_{LVG}}{V_{Hecate}}\cdot 100 \%$$
+
+```{python}
+def relative_diff(hec, lvg):
     """
@@
     hec (numpy.ndarray): An array of values representing the HEC dataset.
-    lcv (numpy.ndarray): An array of values representing the LCV dataset.
+    lvg (numpy.ndarray): An array of values representing the LVG dataset.
 
     Returns:
-    numpy.ndarray: An array of relative differences between the HEC and LCV datasets.
-    The relative difference is calculated as ((HEC - LCV) * 100) / |HEC|.
+    numpy.ndarray: An array of relative differences between the HEC and LVG datasets.
+    The relative difference is calculated as ((HEC - LVG) * 100) / |HEC|.
     Any infinite values in the result are replaced with NaN.
     """
-    diff = (hec - lcv) * 100 / np.abs(hec)
+    diff = (hec - lvg) * 100 / np.abs(hec)
     diff[np.isinf(diff)] = np.nan
@@
 
-| LCV | HECATE | Description |              Pearson Correlation \[-1,1\]              |
-|:---------------:|:---------------:|:---------------:|:--------------------:|
-| Dis |   D    |  Distance   | `{python} round(compare_data(dt["Dis"],dt["D"])[3],3)` |
+| LVG | HECATE | Description |
+|:---------------:|:---------------:|:---------------:|
+| Dis |   D    |  Distance   |
 
@@
 results = scipy.stats.linregress(x = dt["Dis"], y=dt["D"])
-plt.xlabel("$D_{LCV}$"+" [{}]".format(dt["Dis"].unit))
+plt.xlabel("$D_{LVG}$"+" [{}]".format(dt["Dis"].unit))
 plt.ylabel("$D_{HEC}$"+" [{}]".format(dt["D"].unit))
 plt.legend(["Data",
-            "$D_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot D_{LCV}+$"+
+            "$D_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot D_{LVG}+$"+
                 f"$({results.intercept:+.2f})$"+
@@
 
-```{python}
-rvel_corr = round(compare_data(dt["RVel"],dt["V"])[3],3)
-```
-
-|     LCV     |    HECATE    |              Description               |  Linear Correlation  |
-|:----------------:|:-----------------:|:----------------:|:----------------:|
-| RVel (km/s) |   V (km/s)   |      Heliocentric radial velocity      | `{python} rvel_corr` |
-| VLG (km/s)  |              |            Radial velocity             |                      |
-|  cz (km/s)  |              |         Heliocentric velocity          |                      |
-|             | V_VIR (km/s) | Virgo-infall corrected radial velocity |                      |
+|     LVG     |    HECATE    |              Description               |
+|:----------------:|:-----------------:|:----------------:|
+| RVel (km/s) |   V (km/s)   |      Heliocentric radial velocity      |
+| VLG (km/s)  |              |            Radial velocity             |
+|  cz (km/s)  |              |         Heliocentric velocity          |
+|             | V_VIR (km/s) | Virgo-infall corrected radial velocity |
 
@@
 results = scipy.stats.linregress(x = dt["RVel"], y=dt["V"])
-plt.xlabel("$V_{LCV}$"+" [{}]".format(dt["RVel"].unit))
+plt.xlabel("$V_{LVG}$"+" [{}]".format(dt["RVel"].unit))
 plt.ylabel("$V_{HEC}$"+" [{}]".format(dt["V"].unit))
 plt.legend(["Data",
-            "$V_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot V_{LCV}+$"+
+            "$V_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot V_{LVG}+$"+
             f"$({results.intercept:+.2f})$"+
@@
 #| fig-cap: "The correlation Matrix of the Velocities.
-The lower left triangle is is composed of the scatter plots of the various velocities, the diagonal shows their distrubution and the upper right triangle shows the correlations of the Velocities"
+The lower left triangle is composed of the scatter plots of the various velocities, the diagonal shows their distrubution and the upper right triangle shows the correlations of the Velocities"
 pairplot_with_correlation(vel_data)
@@
 
-\[?\] The close correlation between all of the velocities, could be due to the fact that all of them measure the velocity of each galaxy, but from a different frame of reference.
-
-The strong correlation between the velocities reported by the HECATE and LCV catalogs can be attributed to the fact that both measure the same intrinsic galaxy velocities but reference them to different frames.
+\[?\] The strong correlation between the velocities reported by the HECATE and LVG catalogs (@fig-vel-pairplot) can be attributed to the fact that both measure the same intrinsic galaxy velocities but reference them to different frames.
 For instance, velocities can be corrected for the movement of the Earth (heliocentric frame) or the for the Virgo-infall.
@@
 
-{{<pagebreak>}}
+{{< pagebreak >}}
 
@@
 
-```{python}
-#| echo: false
-
-ttype_corr = round(compare_data(dt["TType"], dt["T"])[3], 4)
-inc_corr = round(compare_data(dt["inc"], dt["INCL"], sigma = True)[3], 3)
-a26_corr = round(compare_data(dt["a26_1"], dt["R1"], sigma =False)[3], 3)
-```
-
-|      LCV      |        HECATE        |                        Description                        | Pearson Correlation \[-1,1\] |
-|:----------------:|:----------------:|:-----------------:|:----------------:|
-|     TType     |   T (with errors)    | Numerical Hubble type following the de Vaucouleurs system |    `{python} ttype_corr`     |
-|      inc      |         INCL         |                     Inclination (deg)                     |     `{python} inc_corr`      |
-| a26_1 (Major) | R1 (Semi-major axis) |                 angular diameter (arcmin)                 |     `{python} a26_corr`      |
+|      LVG      |        HECATE        |                        Description                        |
+|:----------------:|:----------------:|:-----------------:|
+|     TType     |   T (with errors)    | Numerical Hubble type following the de Vaucouleurs system |
+|      inc      |         INCL         |                     Inclination (deg)                     |
+| a26_1 (Major) | R1 (Semi-major axis) |                 angular diameter (arcmin)                 |
 
@@
 
+"as they correspond to types T \< 1.
+The shortcomings of such a simplified classification of dwarf systems have become apparent; hence, van den Bergh (1959) proposed a more refined scheme where dwarf galaxies were assumed to be divided by luminosity class...Such an approach allowed us to avoid unpleasant cases in which a dwarf galaxy of intermediate type jumps over due to a misclassification from one end of the de Vaucouleurs sequence (T \< 1) to the other (T = 9, 10)." (@karachentsevSTARFORMATIONPROPERTIES2013a)
+
 ```{python}
@@
 #| - "All the galaxies, without the correction" 
-#| - "Comparison with the correction $|{T_{HECATE}-T_{LCV}}|<7$"
+#| - "Comparison with the correction $|{T_{HECATE}-T_{LVG}}|<σ_{Τ_{LVG}}$"
 
@@
                                 y = temp["T"])
-plt.xlabel("$Type_{LCV}$")
+plt.xlabel("$Type_{LVG}$")
 plt.ylabel("$Type_{HEC}$")
 plt.legend(["Data",
-            "$T_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot T_{LCV}+$"+
+            "$T_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot T_{LVG}+$"+
             f"$({results.intercept:+.2f})$"+
@@
                                 y = types["T"].data)
-plt.xlabel("$Type_{LCV}$")
+plt.xlabel("$Type_{LVG}$")
 plt.ylabel("$Type_{HEC}$")
 plt.legend(["Data",
-            "$T_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot T_{LCV}+$"+
+            "$T_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot T_{LVG}+$"+
             f"$({results.intercept:+.2f})$"+
@@
 -   we can assume that the galaxies from the upper left and lower right regions of the plot are classified differently because of this
--   this might explain the large errors E_T of HECATE
+-   this might explain the large errors $\delta T$ of HECATE
 -   why we see a difference in the distribution of (@fig-type-comp)
@@
 $$
-|{T_{HECATE}-T_{LCV}}|<\sigma_{T_{LCV}} = 4.8
+|{T_{HECATE}-T_{LVG}}|<\sigma_{T_{LVG}} = 4.8
 $$
@@
 -   The average uncertainty of the morphological type in the HECATE catalog is $\overline{\delta T} = \pm 1.4$, so the intercept is included in the error.
--   So we can assume that the Distances are the same
+-   So we can assume that the Morphological Types are the same
 
@@
 sns.histplot(temp["INCL"], kde = True, label = "HECATE")
-sns.histplot(temp["inc"], kde = True, label = "LCV")
+sns.histplot(temp["inc"], kde = True, label = "LVG")
 plt.legend()
@@
 ```{python}
-temp.describe()
-```
-
-We can see that for values in the range $[\sim 30^\circ,\sim 80^\circ]$, the values of the LCV inclination are higher (@fig-incl-compare).
+# Display specific statistics, excluding the 25th and 75th percentiles
+summary_stats = temp.describe().drop(['25%', '75%'])
+summary_stats
+```
+
+We can see that for values in the range $[\sim 30^\circ,\sim 80^\circ]$, the values of the LVG inclination are higher (@fig-incl-compare).
 However, since their means, median, min and maxes are similar and the percentage change is practically 0% (mean, median, $\sigma$ = 0 with a range $[-3\%,1\%]$), we can ignore the differences and assume they are the same values.
@@
 
-plt.xlabel("(Major angular diameter$)_{LCV}$")
+plt.xlabel("(Major angular diameter$)_{LVG}$")
 plt.ylabel("(Semi major axis$)_{HEC}$")
 plt.legend(["Data",
-            "$R1_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot a_{26,LCV}$"+
+            "$R1_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot a_{26,LVG}$"+
             f"${results.intercept:+.2f}$"+
@@
 results = scipy.stats.linregress(x = temp["log_a26"], y = temp["log_R1"])
-plt.xlabel("(Major angular diameter$)_{LCV}$"+" [{}]".format(dt["a26_1"].unit))
+plt.xlabel("(Major angular diameter$)_{LVG}$"+" [{}]".format(dt["a26_1"].unit))
 plt.ylabel("(Semi major axis$)_{HEC}$"+" [{}]".format(dt["R1"].unit))
 plt.legend(["Data",
-            "$log_{10}(R1_{HEC})=$" +f"{results.slope:.2f}"+"$\cdot log_{10}(a_{26,LCV})$"+
+            "$log_{10}(R1_{HEC})=$" +f"{results.slope:.2f}"+"$\cdot log_{10}(a_{26,LVG})$"+
             f"${results.intercept:+.2f}$"+
@@
 :::
+
+{{< pagebreak >}}
 
@@
 
-|   LCV   | HECATE | Description | Pearson Correlation \[-1,1\] |
-|:-------:|:------:|:-----------:|:----------------------------:|
-| logKLum | logL_K |             |   `{python} logKLum_corr`    |
+|   LVG   | HECATE | Description |
+|:-------:|:------:|:-----------:|
+| logKLum | logL_K |             |
 
@@
 results = scipy.stats.linregress(x = temp["logKLum"], y = temp["logL_K"])
-plt.xlabel("log($L_{K, LCV} $"+"/{})".format(dt["KLum"].unit.to_string("latex")))
+plt.xlabel("log($L_{K, LVG} $"+"/{})".format(dt["KLum"].unit.to_string("latex")))
 plt.ylabel("log($L_{K, HECATE} $"+"/{})".format(dt["KLum"].unit.to_string("latex")))
 plt.legend(["Data",
-            "$log(L_{K,HEC})=$" +f"{results.slope:.2f}"+"$\cdot log(L_{K,LCV})$"+
+            "$log(L_{K,HEC})=$" +f"{results.slope:.2f}"+"$\cdot log(L_{K,LVG})$"+
             f"${results.intercept:+.2f}$"+
@@
 data = dt[~np.isnan(data["logL_K"])]
-logL_K_LCV = data['logKLum']  # Replace with actual column names
+logL_K_LVG = data['logKLum']  # Replace with actual column names
 logL_K_HECATE = data['logL_K']  # Replace with actual column names
@@
 plt.figure(figsize=(8, 6))
-plt.scatter(logL_K_LCV, logL_K_HECATE, color='blue', label='Data', alpha =0.5, edgecolors="white")
+plt.scatter(logL_K_LVG, logL_K_HECATE, color='blue', label='Data', alpha =0.5, edgecolors="white")
 
 # Plot free fit (with intercept)
-plt.plot(logL_K_LCV, results.slope * logL_K_LCV + results.intercept, color='green', label='Free Fit: $log(L_{K,HEC})=$'+ f'{results.slope:.2f}'+ "$\cdot log(L_{K,LCV})$"+ f'{results.intercept:.2f}'+f"\n $R^2 = {results.rvalue**2*100:.2f}\%$")
+plt.plot(logL_K_LVG, results.slope * logL_K_LVG + results.intercept, color='green', label='Free Fit: $log(L_{K,HEC})=$'+ f'{results.slope:.2f}'+ "$\cdot log(L_{K,LVG})$"+ f'{results.intercept:.2f}'+f"\n $R^2 = {results.rvalue**2*100:.2f}\%$")
 
@@
 # Plot forced fit (through the origin)
-results_f = scipy.stats.linregress(x = logL_K_HECATE, y = slope_forced*logL_K_LCV)
-plt.plot(logL_K_LCV, slope_forced * logL_K_LCV, color='red', label='Forced Fit: $log(L_{K,HEC})=$' +f' = {slope_forced:.2f}'"$\cdot log(L_{K,LCV})$"+f"\n $R^2 = {results_f.rvalue**2*100:.2f}\%$")
-
-plt.xlabel("log($L_{K, LCV} $"+"/{})".format(dt["KLum"].unit.to_string("latex")))
+results_f = scipy.stats.linregress(x = logL_K_HECATE, y = slope_forced*logL_K_LVG)
+plt.plot(logL_K_LVG, slope_forced * logL_K_LVG, color='red', label='Forced Fit: $log(L_{K,HEC})=$' +f' = {slope_forced:.2f}'"$\cdot log(L_{K,LVG})$"+f"\n $R^2 = {results_f.rvalue**2*100:.2f}\%$")
+
+plt.xlabel("log($L_{K, LVG} $"+"/{})".format(dt["KLum"].unit.to_string("latex")))
 plt.ylabel("log($L_{K, HECATE} $"+"/{})".format(dt["KLum"].unit.to_string("latex")))
@@
 $$
-\log(L_{K,HEC})=1.16\log(L_{K,LCV})-1.78=\log\left(\frac{{L_{K,LCV}}^{1.16}}{10^{1.78}}\right) \Leftrightarrow L_{K,HEC}=0.02\cdot{L_{K,LCV}}^{1.16}
+\log(L_{K,HEC})=1.16\log(L_{K,LVG})-1.78=\log\left(\frac{{L_{K,LVG}}^{1.16}}{10^{1.78}}\right) \Leftrightarrow L_{K,HEC}=0.02\cdot{L_{K,LVG}}^{1.16}
 $$
@@
 The free fit allows both the slope and intercept to vary freely, meaning the line can take on any slope and can cross the y-axis at any point.
-In contrast, for the forced fit, I set the slope to exactly 1 and fixed the line to pass through the origin, meaning the equation becomes y=xy=x.
+In contrast, for the forced fit, I set the slope to exactly 1 and fixed the line to pass through the origin, meaning the equation becomes $y=x$.
 This forced fit represents a perfect 1-1 relationship, where the values from one catalog should match the other exactly, without any shift or scaling.
@@
 
-|         LCV         |      HECATE      |         Description         | Pearson Correlation \[-1,1\] |
-|:----------------:|:----------------:|:----------------:|:-----------------:|
-| mag_B (with errors) | BT (with errors) |                             |    `{python} mag_B_corr`     |
-|        Kmag         |        K         | 2MASS band magnitude (both) |     `{python} Kmag_corr`     |
+|         LVG         |      HECATE      |         Description         |
+|:-------------------:|:----------------:|:---------------------------:|
+| mag_B (with errors) | BT (with errors) |                             |
+|        Kmag         |        K         | 2MASS band magnitude (both) |
 
@@
 results = scipy.stats.linregress(x = temp["mag_B"], y = temp["BT"])
-plt.xlabel("$M_{B,LCV}$"+" [{}]".format(dt["mag_B"].unit.to_string("latex")))
+plt.xlabel("$M_{B,LVG}$"+" [{}]".format(dt["mag_B"].unit.to_string("latex")))
 plt.ylabel("$M_{B,HECATE} $"+" [{}]".format(dt["BT"].unit.to_string("latex")))
 plt.legend(["Data",
-            "$M_{B,HEC}=$" +f"{results.slope:.2f}"+"$\cdot M_{B,LCV}$"+
+            "$M_{B,HEC}=$" +f"{results.slope:.2f}"+"$\cdot M_{B,LVG}$"+
             f"${results.intercept:+.2f}$"+
@@
 results = scipy.stats.linregress(x = temp["Kmag"], y = temp["K"])
-plt.xlabel("$M_{K,LCV}$"+" [{}]".format(dt["Kmag"].unit.to_string("latex")))
+plt.xlabel("$M_{K,LVG}$"+" [{}]".format(dt["Kmag"].unit.to_string("latex")))
 plt.ylabel("$M_{K,HECATE} $"+" [{}]".format(dt["K"].unit.to_string("latex")))
 plt.legend(["Data",
-            "$M_{K,HEC}=$" +f"{results.slope:.2f}"+"$\cdot M_{K,LCV}$"+
+            "$M_{K,HEC}=$" +f"{results.slope:.2f}"+"$\cdot M_{K,LVG}$"+
             f"${results.intercept:+.2f}$"+
@@
 ```{python}
-dt["diff_K_mag"] = relative_diff(dt["Kmag"], dt["K"])
-
-temp = dt[["diff_K_mag"]].to_pandas()
-c = temp["diff_K_mag"]
-up_clip = c.mean() + 3*c.std()
-low_clip = c.mean() - 3*c.std()
-temp["Percentage Change, after 3 sigma clip [%]"] = temp["diff_K_mag"].clip(low_clip, up_clip)
-temp.rename(columns={"diff_K_mag":"Percentage Change [%]"}, inplace=True)
-```
-
-```{python}
-sns.histplot(temp, kde = True)
-plt.title("Percentage change Distribution [%]")
-plt.xlabel(f"K band magnitude [{dt['K'].unit}]")
-plt.show()
-
-sns.histplot(dt["Kmag"].data, label = "LCV")
-sns.histplot(dt["K"].data, label = "HECATE")
+#| label: fig-kmag-compare
+#| layout-ncol: 2 
+#| fig-cap: "Comparison of the $L_K$ of the galaxies."
+#| fig-subcap: 
+#| - "Linear Regression with free paramaters, $y=ax+b$ "
+#| - "Linear Regrassion $y=x$ "
+
+plt.close()
+fig, ax = plt.subplots()
+temp = dt[["Kmag","K"]].to_pandas().dropna()
+K_LVG = temp['Kmag']  # Replace with actual column names
+K_HECATE = temp['K']  # Replace with actual column names
+
+sns.regplot(x = K_LVG, y = K_HECATE,
+                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
+                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
+results = scipy.stats.linregress(x = temp["Kmag"], y = temp["K"])
+r2_free = results.rvalue
+plt.xlabel("$M_{K,LVG}$"+" [{}]".format(dt["Kmag"].unit.to_string("latex")))
+plt.ylabel("$M_{K,HECATE} $"+" [{}]".format(dt["K"].unit.to_string("latex")))
+plt.legend(["Data",
+            "$M_{K,HEC}=$" +f"{results.slope:.2f}"+"$\cdot M_{K,LVG}$"+
+            f"${results.intercept:+.2f}$"+
+            f"\n $R^2 = {results.rvalue**2*100:.2f}\%$"])
+plt.show()
+
+# Plot the data and both fits
+plt.figure(figsize=(8, 6))
+plt.scatter(K_LVG, K_HECATE, color='blue', label='Data', alpha =0.5, edgecolors="white")
+
+# Plot free fit (with intercept)
+plt.plot(K_LVG, results.slope * K_LVG + results.intercept, color='green', label='Free Fit: $M_{K,HEC}=$'+ f'{results.slope:.2f}'+ "$\cdot M_{K,LVG}$"+ f'{results.intercept:.2f}'+f"\n $R^2 = {results.rvalue**2*100:.2f}\%$")
+
+slope_forced = 1
+# Plot forced fit (through the origin)
+results_f = pearsonr(x = K_HECATE, y = slope_forced*K_LVG)
+plt.plot(K_LVG, slope_forced * K_LVG, color='red', label='Forced Fit: $M_{K,HEC}=$' +f' = {slope_forced:.2f}'"$\cdot M_{K,LVG}$"+f"\n $R^2 = {results_f.statistic**2*100:.2f}\%$")
+
+plt.xlabel("$M_{K,LVG}$"+" [{}]".format(dt["Kmag"].unit.to_string("latex")))
+plt.ylabel("$M_{K,HECATE} $"+" [{}]".format(dt["K"].unit.to_string("latex")))
 plt.legend()
-plt.xlabel(f"K band magnitude [{dt['K'].unit}]")
-plt.show()
-```
-
-```{python}
-temp.describe(percentiles=[])
-```
-
-\[?\] this 5% mean in the difference probably exists because of the low number of galaxies we compare, so we can ignore it.
-
+plt.grid(True)
+plt.show()
+```
+
+Following the same logic as in @fig-klum-compare, we force the parameters of the linear regression to be $y=1\cdot x + 0$.
+
+In this case, the data is such that both the forced fit and the free fit explain the variance almost identically (@fig-kmag-compare-2).
+This can happen when the data roughly follows the pattern $y≈x$, but with a slight bias that the free fit can account for (in this case, a slope slightly greater than 1 and a negative intercept).
+
+{{< pagebreak >}}
 ## SFR
@@
 
-|  LCV   |   HECATE   |                           Description                            |                  Count                  |
-|:----------------:|:----------------:|:-----------------:|:----------------:|
-|        | logSFR_TIR | Decimal logarithm of the total-infrared SFR estimate \[Msol/yr\] | `{python} non_nan_counts["logSFR_TIR"]` |
-|        | logSFR_FIR |  Decimal logarithm of the far-infrared SFR estimate \[Msol/yr\]  | `{python} non_nan_counts["logSFR_FIR"]` |
-|        | logSFR_60u |      Decimal logarithm of the 60um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_60u"]` |
-|        | logSFR_12u |      Decimal logarithm of the 12um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_12u"]` |
-|        | logSFR_22u |      Decimal logarithm of the 22um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_22u"]` |
-|        | logSFR_HEC |  Decimal logarithm of the homogenised SFR estimate \[Msol/yr\]   | `{python} non_nan_counts["logSFR_HEC"]` |
-|        | logSFR_GSW |       Decimal logarithm of the SFR in GSWLC-2 \[Msol/yr\]        | `{python} non_nan_counts["logSFR_GSW"]` |
-| SFRFUV |            |             FUV derived integral star formation rate             | `{python} non_nan_counts["logSFRFUV"]`  |
-| SFRHa  |            |          H{alpha} derived integral star formation rate           |  `{python} non_nan_counts["logSFRHa"]`  |
-
-```{python}
+|  LVG   |   HECATE   |                           Description                            |
+|:----------------:|:----------------:|:-----------------:|
+|        | logSFR_TIR | Decimal logarithm of the total-infrared SFR estimate \[Msol/yr\] |
+|        | logSFR_FIR |  Decimal logarithm of the far-infrared SFR estimate \[Msol/yr\]  |
+|        | logSFR_60u |      Decimal logarithm of the 60um SFR estimate \[Msol/yr\]      |
+|        | logSFR_12u |      Decimal logarithm of the 12um SFR estimate \[Msol/yr\]      |
+|        | logSFR_22u |      Decimal logarithm of the 22um SFR estimate \[Msol/yr\]      |
+|        | logSFR_HEC |  Decimal logarithm of the homogenised SFR estimate \[Msol/yr\]   |
+|        | logSFR_GSW |       Decimal logarithm of the SFR in GSWLC-2 \[Msol/yr\]        |
+| SFRFUV |            |             FUV derived integral star formation rate             |
+| SFRHa  |            |          H{alpha} derived integral star formation rate           |
+
+```{python}
+#| label: fig-sfr-pairplot
+#| layout-align: center
+#| fig-cap: "Comparison of the $SFR_{i}$ of the galaxies"
 #| echo: false
@@
 
-```{python}
-#| label: fig-sfr-lcv
+The SFR according to (@kroupaConstraintsStarFormation2020), can be calculated from the mean of SFR from the Ha and FUV, for $SFR>10^{-3}\ M_\odot\, yr^{-1}$.
+As we can see from the plots (@fig-sfr-lvg) it could be a good aproximation.
+
+$$
+SFR = \frac{SFR_{FUV}+SFR_{H\alpha}}{2}, \text{if both exist, else: } SFR = SFR_i,\ i= FUV,\, H\alpha
+$$ {#eq-sfr-mean}
+
+```{python}
+#| label: fig-sfr-lvg
 #| layout-ncol: 2
@@
 fig, ax = plt.subplots()
-temp = lcv[["SFRHa","SFRFUV"]].to_pandas().dropna()
+temp = lvg[["SFRHa","SFRFUV"]].to_pandas().dropna()
 x = temp["SFRHa"]
@@
 
-The SFR according to (@kroupaConstraintsStarFormation2020), can be calculated from the mean of SFR from the Ha and FUV, for $SFR>10^{-3}\ M_\odot\, yr^{-1}$.
-As we can see from the plots (@fig-sfr-lcv) it is a good aproximation for all SFR's
-
-$$
-SFR = \frac{SFR_{FUV}+SFR_{H\alpha}}{2}, \text{if both exist, else: } SFR = SFR_i,\ i= FUV,\, H\alpha
-$$
-
 ```{python}
@@
 ```{python}
-#| label: fig-SFR-compare
+#| label: fig-sfr-compare
 #| layout-ncol: 2
@@
 results = scipy.stats.linregress(x = 10**temp["SFR_t"], y = 10**temp["logSFR_HEC"])
-plt.xlabel("$SFR_{LCV}$"+" [{}]".format(dt["SFR_t"].unit.to_string("latex")))
+plt.xlabel("$SFR_{LVG}$"+" [{}]".format(dt["SFR_t"].unit.to_string("latex")))
 plt.ylabel("$SFR_{HECATE} $"+" [{}]".format(dt["SFR_t"].unit.to_string("latex")))
 plt.legend(["Data",
-            "$SFR_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot SFR_{LCV}$"+
+            "$SFR_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot SFR_{LVG}$"+
             f"${results.intercept:+.2f}$"+
@@
 results = scipy.stats.linregress(x = temp["SFR_t"], y = temp["logSFR_HEC"])
-plt.xlabel("$log(SFR_{LCV})$"+" [{}]".format(dt["logSFR_HEC"].unit.to_string("latex")))
+plt.xlabel("$log(SFR_{LVG})$"+" [{}]".format(dt["logSFR_HEC"].unit.to_string("latex")))
 plt.ylabel("$log(SFR_{HECATE})$"+" [{}]".format(dt["logSFR_HEC"].unit.to_string("latex")))
 plt.legend(["Data",
-            "$log(SFR_{HEC})=$" +f"{results.slope:.2f}"+"$\cdot log(SFR_{LCV})$"+
+            "$log(SFR_{HEC})=$" +f"{results.slope:.2f}"+"$\cdot log(SFR_{LVG})$"+
             f"${results.intercept:+.2f}$"+
@@
 
-\[?\]EXPLANATION this low correlation maybe comes from the inaccuracy/approximation of (@kroupaConstraintsStarFormation2020)
-
-The reason is that this aproximation is accurate if we consider a stable SFR over time.
-However, we tend to observe higher Ha for more recent SF activity.
-(we discussed it in our last meeting, I need a refrence).
+The low correlation in @fig-sfr-compare-1 and the interval in @fig-sfr-compare-2 show that the approximation (@eq-sfr-mean) is not great. According to @karachentsevSTARFORMATIONPROPERTIES2013a:
+
+-   **Hα and FUV timescales**: $H_\alpha$ traces short-term star formation (\~10 Myr) via massive O-type stars, while FUV traces longer-term star formation (\~100 Myr) from B-type stars.
+
+-   **Discrepancies due to star formation bursts**: In galaxies with bursty or episodic star formation, Hα can significantly overestimate SFR compared to FUV, which lags in reflecting recent star formation events.
+
+-   **Low-mass galaxy variability**: The scatter between $SFR_{\text{H}\alpha}$ and $SFR_{\text{FUV}}$ is particularly high in low-mass, dwarf galaxies, where stochastic star formation history causes wide variability between the two indicators.
+
+-   **Measurement uncertainties**: Internal extinction, errors in distance estimates, and IMF stochasticity introduce biases in both Hα and FUV fluxes, making simple averaging inappropriate.
+
+-   **Conclusion**: The $SFR_{\text{total}} = \text{mean}(SFR_{\text{H}\alpha}, SFR_{\text{FUV}})$ method oversimplifies the complexity of star formation processes and is not reliable for galaxies with variable star formation or significant measurement uncertainties
+
+{{< pagebreak >}}
 
@@
 
-|      LCV       |  HECATE  |                        Description                        |                    Count                    |
-|:----------------:|:----------------:|:----------------:|:----------------:|
-|     logM26     |          |              Log mass within Holmberg radius              |     `{python} non_nan_counts["logM26"]`     |
-|     logMHI     |          |              Log mass within Holmberg radius              |     `{python} non_nan_counts["logMHI"]`     |
-|                | logM_HEC |      Decimal logarithm of the stellar mass \[Msol\]       |    `{python} non_nan_counts["logM_HEC"]`    |
-|                | logM_GSW | Decimal logarithm of the stellar mass in GSWLC-2 \[Msol\] |    `{python} non_nan_counts["logM_GSW"]`    |
-| logStellarMass |          |               Stellar Mass from $M_*/L=0.6$               | `{python} non_nan_counts["logStellarMass"]` |
+|      LVG       |  HECATE  |                        Description                        |
+|:----------------:|:----------------:|:----------------:|
+|     logM26     |          |              Log mass within Holmberg radius              |
+|     logMHI     |          |              Log mass within Holmberg radius              |
+|                | logM_HEC |      Decimal logarithm of the stellar mass \[Msol\]       |
+|                | logM_GSW | Decimal logarithm of the stellar mass in GSWLC-2 \[Msol\] |
+| logStellarMass |          |               Stellar Mass from $M_*/L=0.6$               |
 
 ::: panel-tabset
+{{< pagebreak >}}
+
 ### Stellar Masses Comparison
+
+{{< pagebreak >}}
 
@@
 results = scipy.stats.linregress(x = x, y = y)
-plt.xlabel("$log(M_{*,LCV})$"+" [{}]".format(dt["logM_HEC"].unit.to_string("latex")))
+plt.xlabel("$log(M_{*,LVG})$"+" [{}]".format(dt["logM_HEC"].unit.to_string("latex")))
 plt.ylabel("$log(M_{*,HECATE} )$"+" [{}]".format(dt["logM_HEC"].unit.to_string("latex")))
 plt.legend(["Data",
-            "$log(M_{*,HEC})=$" +f"{results.slope:.2f}"+"$\cdot log(M_{*,LCV})$"+
+            "$log(M_{*,HEC})=$" +f"{results.slope:.2f}"+"$\cdot log(M_{*,LVG})$"+
             f"${results.intercept:+.2f}$"+
@@
 $$
-\log{M_{*,HECATE}}=1.07\cdot\log{M_{*,LCV}}-0.69, \text{ but } \log{M_*}>6\Rightarrow M_{*,HEC}\sim M_{*,LCV}
+\log{M_{*,HECATE}}=1.07\cdot\log{M_{*,LVG}}-0.69, \text{ but } \log{M_*}>6\Rightarrow M_{*,HEC}\sim M_{*,LVG}
 $$
@@
 
+{{< pagebreak >}}
 ### Heatmap

### 2024-10-19 compare/compare.tex
minor fixes

@@
 In this script we will compare 2 catalogs, HECATE (Kovlakas et al.
-(2021)) and LCV (Karachentsev and Kaisina (2013))
+(2021)) and LVG (Karachentsev and Kaisina (2013))
 
@@
 The dataset we are going to use for the comparison (inner join) consists
-of 288 galaxies and 168 columns.
+of 288 galaxies and 168 columns with their physical characteristics.
 
@@
 
-\subsection{Completeness of the LCV
-Catalog}\label{completeness-of-the-lcv-catalog}
+\subsection{Completeness of the LVG
+Catalog}\label{completeness-of-the-lvg-catalog}
 
@@
 \def\labelenumi{\arabic{enumi}.}
+\tightlist
 \item
   Radial velocities of
-  \begin{equation}\phantomsection\label{eq-lcv-vel}{
+\end{enumerate}
+
+\begin{equation}\phantomsection\label{eq-lvg-vel}{
      V_{LG}<600 \text{ km}\cdot\text{m}^{-1}
 }\end{equation}
-\item
-  Distances of \begin{equation}\phantomsection\label{eq-lcv-dis}{
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Distances of
+\end{enumerate}
+
+\begin{equation}\phantomsection\label{eq-lvg-dis}{
        D<11\ \text{Mpc}
 }\end{equation}
-\end{enumerate}
 
@@
     may make up half of the adopted velocity constraint
-    (Equation~\ref{eq-lcv-vel})
+    (Equation~\ref{eq-lvg-vel})
+
+    \begin{itemize}
+    \tightlist
     \item
@@
       \(D=11 Mpc\)
+    \end{itemize}
   \item
@@
   \end{itemize}
-\item
-  Astro-Spam and Survey Errors: - Automatic surveys produce false
-  detections (e.g., stars misclassified as galaxies, high-velocity
-  clouds mistaken for dwarfs).
+\end{enumerate}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  Astro-Spam and Survey Errors:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Automatic surveys produce false detections (e.g., stars
+    misclassified as galaxies, high-velocity clouds mistaken for
+    dwarfs).
+  \end{itemize}
 \item
@@
   \(M_B^c = -11^m\) or with linear diameters larger than
-  \(A_{26} = 1.0\) kpc show (40--60)\% completeness. - ``among the
-  members of the Local Group (D \textless{} 1 Mpc), only half of the
-  galaxies have absolute magnitudes brighter than −11m. Consequently,
-  more than half of the ultra-faint dwarf companions around normal
-  galaxies, like the Sombrero galaxy (D = 9.3 Mpc), still remain outside
-  our field of view.''
-\item
-  Undetected Ultra-Faint Dwarfs: - Many faint dwarf galaxies remain
-  undetected beyond the Local Group. Estimated population of undetected
-  dwarfs could be as large as \(10^3–10^4\) within the LV.
-\item
-  Surface Brightness Distribution: - Surface brightness remains
-  consistent across distances, except for ultra-faint dwarfs
-  (\(SB <31 \text{mag}\cdot\text{arcsec}^{-2}\)). - Faintest dwarf
-  galaxies are detectable only nearby due to their resolution into
-  individual stars.
-\item
-  Luminosity-Size Relationship: - Observations align with cosmological
-  models predicting \(L\sim A^3\) (Navarro, Frenk, and White (1996)),
-  though deviations occur for extremely low surface brightness galaxies.
-  - ``The deviation from it at the extremely low surface brightness end
+  \(A_{26} = 1.0\) kpc show (40--60)\% completeness.
+
+  \begin{itemize}
+  \tightlist
+  \item
+    ``among the members of the Local Group (D \textless{} 1 Mpc), only
+    half of the galaxies have absolute magnitudes brighter than
+    \(−11^m\). Consequently, more than half of the ultra-faint dwarf
+    companions around normal galaxies, like the Sombrero galaxy (D = 9.3
+    Mpc), still remain outside our field of view.''
+  \end{itemize}
+\item
+  Undetected Ultra-Faint Dwarfs:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Many faint dwarf galaxies remain undetected beyond the Local Group.
+    Estimated population of undetected dwarfs could be as large as
+    \(10^3–10^4\) within the LV.
+  \end{itemize}
+\item
+  Surface Brightness Distribution:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Surface brightness remains consistent across distances, except for
+    ultra-faint dwarfs (\(SB <31 \text{mag}\cdot\text{arcsec}^{-2}\)).
+  \item
+    Faintest dwarf galaxies are detectable only nearby due to their
+    resolution into individual stars.
+  \end{itemize}
+\item
+  Luminosity-Size Relationship:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Observations align with cosmological models predicting \(L\sim A^3\)
+    (Navarro, Frenk, and White (1996)), though deviations occur for
+    extremely low surface brightness galaxies.
+  \item
+    ``The deviation from it at the extremely low surface brightness end
     is due to a systematic overestimation of dwarf galaxy sizes, the
@@
     isophote.''
+  \end{itemize}
 \end{enumerate}
@@
 Outer join & 2901 \\
-LCV & 1316 \\
+LVG & 1316 \\
 HECATE & 2901 \\
-Unique galaxies in LCV & 1028 \\
+Unique galaxies in LVG & 1028 \\
 Unique Galaxies in Hecate & 2613 \\
@@
 
-Completeness (LCV)= 22 \%
+Completeness (LVG)= 22 \%
 
@@
 
-Completeness (LCV)= 78 \%
+Completeness (LVG)= 78 \%
 
 Combined Completeness
-=\(\frac{\text{Total galaxies in Outer}}{\text{Unique galaxies in HECATE + LCV}}\)=
+=\(\frac{\text{Total galaxies in Outer}}{\text{Unique galaxies in HECATE + LVG}}\)=
 80 \%
@@
 
-\subcaption{\label{fig-dis-comp-2}LCV}
+\subcaption{\label{fig-dis-comp-2}LVG}
 
@@
 
-\subcaption{\label{fig-type-comp-2}LCV}
+\subcaption{\label{fig-type-comp-2}LVG}
 
@@
 \end{figure}%
-
-As we can see from the histograms (Figure~\ref{fig-dis-comp}) and
-(Figure~\ref{fig-type-comp}) the sample of unique galaxies of each
-catalog, gets smaller by an almost constant proportion (Inner join).
-
-This means there is no bias in the selection of the galaxies.
 
@@
 
-For the distrabution comparisons we will use histograms and Kernel
+For the distribution comparisons we will use histograms and Kernel
 Density Estimate (KDE) plots. The KDE plots visually represent the
@@
 
-\[\text{Percentage change} = \frac{V_{Hecate} - V_{LCV}}{V_{Hecate}}\cdot 100 \%\]
+\[\text{Percentage change} = \frac{V_{Hecate} - V_{LVG}}{V_{Hecate}}\cdot 100 \%\]
 
@@
 
+\begin{longtable}[]{@{}ccc@{}}
+\toprule\noalign{}
+LVG & HECATE & Description \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Dis & D & Distance \\
+\end{longtable}
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-coord-compare-output-1.pdf}
+
+}
+
+\caption{\label{fig-coord-compare}Comparison of the Distances}
+
+\end{figure}%
+
+\begin{itemize}
+\tightlist
+\item
+  The average error of the distance in the HECATE catalog is
+  \(\overline{\delta D} = \pm 1.6\) Mpc, so the intercept is included in
+  the error.
+\item
+  So we can assume that the Distances are the same
+\end{itemize}
+
+\subsection{Velocities}\label{velocities}
+
+\begin{longtable}[]{@{}ccc@{}}
+\toprule\noalign{}
+LVG & HECATE & Description \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+RVel (km/s) & V (km/s) & Heliocentric radial velocity \\
+VLG (km/s) & & Radial velocity \\
+cz (km/s) & & Heliocentric velocity \\
+& V\_VIR (km/s) & Virgo-infall corrected radial velocity \\
+\end{longtable}
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-vel-compare-output-1.pdf}
+
+}
+
+\caption{\label{fig-vel-compare}Comparison of the Radial Velocities}
+
+\end{figure}%
+
+\begin{itemize}
+\tightlist
+\item
+  The average error of the radial velocity in the HECATE catalog is
+  \(\overline{\delta V} = \pm 12\text{km}\cdot s^{-1}\) , so the
+  intercept is included in the error.
+\item
+  So we can assume that the radial velocities are the same
+\end{itemize}
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-vel-pairplot-output-1.pdf}
+
+}
+
+\caption{\label{fig-vel-pairplot}The correlation Matrix of the
+Velocities. The lower left triangle is composed of the scatter plots of
+the various velocities, the diagonal shows their distrubution and the
+upper right triangle shows the correlations of the Velocities}
+
+\end{figure}%
+
+{[}?{]} The strong correlation between the velocities reported by the
+HECATE and LVG catalogs (Figure~\ref{fig-vel-pairplot}) can be
+attributed to the fact that both measure the same intrinsic galaxy
+velocities but reference them to different frames. For instance,
+velocities can be corrected for the movement of the Earth (heliocentric
+frame) or the for the Virgo-infall. These corrections shift the measured
+velocity slightly, but the fundamental measurement remains consistent.
+This explains why the velocities are highly correlated, as they
+represent the same physical phenomenon but adjusted for different
+reference points.
+
+\newpage{}
+
+\subsection{Morphology and Geometry}\label{morphology-and-geometry}
+
 \begin{longtable}[]{@{}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2329}}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2329}}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2329}}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.3014}}@{}}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3273}}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3273}}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3455}}@{}}
 \toprule\noalign{}
 \begin{minipage}[b]{\linewidth}\centering
-LCV
+LVG
 \end{minipage} & \begin{minipage}[b]{\linewidth}\centering
@@
 Description
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Pearson Correlation {[}-1,1{]}
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-Dis & D & Distance & 0.881 \\
-\end{longtable}
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{compare_files/figure-pdf/fig-coord-compare-output-1.pdf}
-
-}
-
-\caption{\label{fig-coord-compare}Comparison of the Distances}
-
-\end{figure}%
-
-\begin{itemize}
-\tightlist
-\item
-  The average error of the distance in the HECATE catalog is
-  \(\overline{\delta D} = \pm 1.6\) Mpc, so the intercept is included in
-  the error.
-\item
-  So we can assume that the Distances are the same
-\end{itemize}
-
-\subsection{Velocities}\label{velocities}
-
-\begin{longtable}[]{@{}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2603}}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}@{}}
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\centering
-LCV
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-HECATE
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Description
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Linear Correlation
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-RVel (km/s) & V (km/s) & Heliocentric radial velocity & 0.994 \\
-VLG (km/s) & & Radial velocity & \\
-cz (km/s) & & Heliocentric velocity & \\
-& V\_VIR (km/s) & Virgo-infall corrected radial velocity & \\
-\end{longtable}
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{compare_files/figure-pdf/fig-vel-compare-output-1.pdf}
-
-}
-
-\caption{\label{fig-vel-compare}Comparison of the Radial Velocities}
-
-\end{figure}%
-
-\begin{itemize}
-\tightlist
-\item
-  The average error of the radial velocity in the HECATE catalog is
-  \(\overline{\delta V} = \pm 12\text{km}\cdot s^{-1}\) , so the
-  intercept is included in the error.
-\item
-  So we can assume that the radial velocities are the same
-\end{itemize}
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{compare_files/figure-pdf/fig-vel-pairplot-output-1.pdf}
-
-}
-
-\caption{\label{fig-vel-pairplot}The correlation Matrix of the
-Velocities. The lower left triangle is is composed of the scatter plots
-of the various velocities, the diagonal shows their distrubution and the
-upper right triangle shows the correlations of the Velocities}
-
-\end{figure}%
-
-{[}?{]} The close correlation between all of the velocities, could be
-due to the fact that all of them measure the velocity of each galaxy,
-but from a different frame of reference.
-
-The strong correlation between the velocities reported by the HECATE and
-LCV catalogs can be attributed to the fact that both measure the same
-intrinsic galaxy velocities but reference them to different frames. For
-instance, velocities can be corrected for the movement of the Earth
-(heliocentric frame) or the for the Virgo-infall. These corrections
-shift the measured velocity slightly, but the fundamental measurement
-remains consistent. This explains why the velocities are highly
-correlated, as they represent the same physical phenomenon but adjusted
-for different reference points.
-
-\newpage{}
-
-\subsection{Morphology and Geometry}\label{morphology-and-geometry}
-
-\begin{longtable}[]{@{}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2603}}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}@{}}
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\centering
-LCV
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-HECATE
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Description
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Pearson Correlation {[}-1,1{]}
 \end{minipage} \\
@@
 TType & T (with errors) & Numerical Hubble type following the de
-Vaucouleurs system & 0.7107 \\
-inc & INCL & Inclination (deg) & 0 \\
-a26\_1 (Major) & R1 (Semi-major axis) & angular diameter (arcmin) & 0 \\
+Vaucouleurs system \\
+inc & INCL & Inclination (deg) \\
+a26\_1 (Major) & R1 (Semi-major axis) & angular diameter (arcmin) \\
 \end{longtable}
@@
 
+``as they correspond to types T \textless{} 1. The shortcomings of such
+a simplified classification of dwarf systems have become apparent;
+hence, van den Bergh (1959) proposed a more refined scheme where dwarf
+galaxies were assumed to be divided by luminosity class\ldots Such an
+approach allowed us to avoid unpleasant cases in which a dwarf galaxy of
+intermediate type jumps over due to a misclassification from one end of
+the de Vaucouleurs sequence (T \textless{} 1) to the other (T = 9,
+10).'' (Karachentsev and Kaisina (2013))
+
 \begin{figure}
@@
 \subcaption{\label{fig-types-compare-2}Comparison with the correction
-\(|{T_{HECATE}-T_{LCV}}|<7\)}
+\(|{T_{HECATE}-T_{LVG}}|<σ_{Τ_{LVG}}\)}
 
@@
 \item
-  this might explain the large errors E\_T of HECATE
+  this might explain the large errors \(\delta T\) of HECATE
 \item
@@
 with: \[
-|{T_{HECATE}-T_{LCV}}|<\sigma_{T_{LCV}} = 4.8
+|{T_{HECATE}-T_{LVG}}|<\sigma_{T_{LVG}} = 4.8
 \]
@@
 \item
-  So we can assume that the Distances are the same
+  So we can assume that the Morphological Types are the same
 \end{itemize}
@@
 min & 9 & 0 & -3 \\
-25\% & 47 & 47 & -0 \\
 50\% & 60 & 59 & 0 \\
-75\% & 72 & 78 & 0 \\
 max & 90 & 90 & 1 \\
@@
 We can see that for values in the range
-\([\sim 30^\circ,\sim 80^\circ]\), the values of the LCV inclination are
+\([\sim 30^\circ,\sim 80^\circ]\), the values of the LVG inclination are
 higher (Figure~\ref{fig-incl-compare}). However, since their means,
@@
 
+\newpage{}
+
 \subsection{Luminosities}\label{luminosities}
 
-\begin{longtable}[]{@{}cccc@{}}
+\begin{longtable}[]{@{}ccc@{}}
 \toprule\noalign{}
-LCV & HECATE & Description & Pearson Correlation {[}-1,1{]} \\
+LVG & HECATE & Description \\
 \midrule\noalign{}
@@
 \endlastfoot
-logKLum & logL\_K & & 0 \\
+logKLum & logL\_K & \\
 \end{longtable}
@@
 \[
-\log(L_{K,HEC})=1.16\log(L_{K,LCV})-1.78=\log\left(\frac{{L_{K,LCV}}^{1.16}}{10^{1.78}}\right) \Leftrightarrow L_{K,HEC}=0.02\cdot{L_{K,LCV}}^{1.16}
+\log(L_{K,HEC})=1.16\log(L_{K,LVG})-1.78=\log\left(\frac{{L_{K,LVG}}^{1.16}}{10^{1.78}}\right) \Leftrightarrow L_{K,HEC}=0.02\cdot{L_{K,LVG}}^{1.16}
 \]
@@
 fixed the line to pass through the origin, meaning the equation becomes
-y=xy=x. This forced fit represents a perfect 1-1 relationship, where the
-values from one catalog should match the other exactly, without any
+\(y=x\). This forced fit represents a perfect 1-1 relationship, where
+the values from one catalog should match the other exactly, without any
 shift or scaling.
@@
 
+\begin{longtable}[]{@{}ccc@{}}
+\toprule\noalign{}
+LVG & HECATE & Description \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+mag\_B (with errors) & BT (with errors) & \\
+Kmag & K & 2MASS band magnitude (both) \\
+\end{longtable}
+
+\begin{figure}
+
+\begin{minipage}{0.50\linewidth}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-mag-compare-output-1.pdf}
+
+}
+
+\subcaption{\label{fig-mag-compare-1}\(M_B\)}
+
+\end{minipage}%
+%
+\begin{minipage}{0.50\linewidth}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-mag-compare-output-2.pdf}
+
+}
+
+\subcaption{\label{fig-mag-compare-2}\(M_K\)}
+
+\end{minipage}%
+
+\caption{\label{fig-mag-compare}Comparison of the Magnitudes of the
+galaxies}
+
+\end{figure}%
+
+\begin{itemize}
+\tightlist
+\item
+  \(M_B\): it is a 1-1 correlation, since the average error
+  \(M_{B,HECATE} = 0.4\ mag\), so the itercept is smaller than the error
+  (Figure~\ref{fig-mag-compare})
+\item
+  \(M_K\): we need to examine it more, since the intercept is bigger
+  than the error \(M_{K,HECATE} = 0.09\ mag\)
+  (Figure~\ref{fig-mag-compare})
+\end{itemize}
+
+\begin{figure}
+
+\begin{minipage}{0.50\linewidth}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-kmag-compare-output-1.pdf}
+
+}
+
+\subcaption{\label{fig-kmag-compare-1}Linear Regression with free
+paramaters, \(y=ax+b\)}
+
+\end{minipage}%
+%
+\begin{minipage}{0.50\linewidth}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-kmag-compare-output-2.pdf}
+
+}
+
+\subcaption{\label{fig-kmag-compare-2}Linear Regrassion \(y=x\)}
+
+\end{minipage}%
+
+\caption{\label{fig-kmag-compare}Comparison of the \(L_K\) of the
+galaxies.}
+
+\end{figure}%
+
+Following the same logic as in Figure~\ref{fig-klum-compare}, we force
+the parameters of the linear regression to be \(y=1\cdot x + 0\).
+
+In this case, the data is such that both the forced fit and the free fit
+explain the variance almost identically
+(Figure~\ref{fig-kmag-compare-2}). This can happen when the data roughly
+follows the pattern \(y≈x\), but with a slight bias that the free fit
+can account for (in this case, a slope slightly greater than 1 and a
+negative intercept).
+
+\newpage{}
+
+\subsection{SFR}\label{sfr}
+
 \begin{longtable}[]{@{}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2603}}@{}}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3273}}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3273}}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3455}}@{}}
 \toprule\noalign{}
 \begin{minipage}[b]{\linewidth}\centering
-LCV
+LVG
 \end{minipage} & \begin{minipage}[b]{\linewidth}\centering
@@
 Description
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Pearson Correlation {[}-1,1{]}
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-mag\_B (with errors) & BT (with errors) & & 0 \\
-Kmag & K & 2MASS band magnitude (both) & 0 \\
-\end{longtable}
-
-\begin{figure}
-
-\begin{minipage}{0.50\linewidth}
-
-\centering{
-
-\includegraphics{compare_files/figure-pdf/fig-mag-compare-output-1.pdf}
-
-}
-
-\subcaption{\label{fig-mag-compare-1}\(M_B\)}
-
-\end{minipage}%
-%
-\begin{minipage}{0.50\linewidth}
-
-\centering{
-
-\includegraphics{compare_files/figure-pdf/fig-mag-compare-output-2.pdf}
-
-}
-
-\subcaption{\label{fig-mag-compare-2}\(M_K\)}
-
-\end{minipage}%
-
-\caption{\label{fig-mag-compare}Comparison of the Magnitudes of the
-galaxies}
-
-\end{figure}%
-
-\begin{itemize}
-\tightlist
-\item
-  \(M_B\): it is a 1-1 correlation, since the average error
-  \(M_{B,HECATE} = 0.4\ mag\), so the itercept is smaller than the error
-  (Figure~\ref{fig-mag-compare})
-\item
-  \(M_K\): we need to examine it more, since the intercept is bigger
-  than the error \(M_{K,HECATE} = 0.09\ mag\)
-  (Figure~\ref{fig-mag-compare})
-\end{itemize}
-
-\includegraphics{compare_files/figure-pdf/cell-26-output-1.pdf}
-
-\includegraphics{compare_files/figure-pdf/cell-26-output-2.pdf}
-
-\begin{longtable}[]{@{}lll@{}}
-\toprule\noalign{}
-& Percentage Change {[}\%{]} & Percentage Change, after 3 sigma clip
-{[}\%{]} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-count & 70 & 70 \\
-mean & -5 & -5 \\
-std & 12 & 10 \\
-min & -70 & -42 \\
-50\% & -0 & -0 \\
-max & 16 & 16 \\
-\end{longtable}
-
-{[}?{]} this 5\% mean in the difference probably exists because of the
-low number of galaxies we compare, so we can ignore it.
-
-\subsection{SFR}\label{sfr}
-
-\begin{longtable}[]{@{}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2603}}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}@{}}
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\centering
-LCV
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-HECATE
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Description
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Count
 \end{minipage} \\
@@
 & logSFR\_TIR & Decimal logarithm of the total-infrared SFR estimate
-{[}Msol/yr{]} & 21 \\
+{[}Msol/yr{]} \\
 & logSFR\_FIR & Decimal logarithm of the far-infrared SFR estimate
-{[}Msol/yr{]} & 22 \\
-& logSFR\_60u & Decimal logarithm of the 60um SFR estimate {[}Msol/yr{]}
-& 48 \\
-& logSFR\_12u & Decimal logarithm of the 12um SFR estimate {[}Msol/yr{]}
-& 26 \\
-& logSFR\_22u & Decimal logarithm of the 22um SFR estimate {[}Msol/yr{]}
-& 23 \\
+{[}Msol/yr{]} \\
+& logSFR\_60u & Decimal logarithm of the 60um SFR estimate
+{[}Msol/yr{]} \\
+& logSFR\_12u & Decimal logarithm of the 12um SFR estimate
+{[}Msol/yr{]} \\
+& logSFR\_22u & Decimal logarithm of the 22um SFR estimate
+{[}Msol/yr{]} \\
 & logSFR\_HEC & Decimal logarithm of the homogenised SFR estimate
-{[}Msol/yr{]} & 73 \\
-& logSFR\_GSW & Decimal logarithm of the SFR in GSWLC-2 {[}Msol/yr{]} &
-0 \\
-SFRFUV & & FUV derived integral star formation rate & 220 \\
-SFRHa & & H\{alpha\} derived integral star formation rate & 223 \\
+{[}Msol/yr{]} \\
+& logSFR\_GSW & Decimal logarithm of the SFR in GSWLC-2 {[}Msol/yr{]} \\
+SFRFUV & & FUV derived integral star formation rate \\
+SFRHa & & H\{alpha\} derived integral star formation rate \\
 \end{longtable}
 
-\includegraphics{compare_files/figure-pdf/cell-29-output-1.pdf}
-
-\begin{figure}
-
-\begin{minipage}{0.50\linewidth}
-
-\centering{
-
-\includegraphics{compare_files/figure-pdf/fig-sfr-lcv-output-1.pdf}
-
-}
-
-\subcaption{\label{fig-sfr-lcv-1}Linear scale}
-
-\end{minipage}%
-%
-\begin{minipage}{0.50\linewidth}
-
-\centering{
-
-\includegraphics{compare_files/figure-pdf/fig-sfr-lcv-output-2.pdf}
-
-}
-
-\subcaption{\label{fig-sfr-lcv-2}Decimal logarithmic scale}
-
-\end{minipage}%
-
-\caption{\label{fig-sfr-lcv}Comparison of the \(SFR_{FUV}-SFR_{Ha}\) of
-the galaxies}
+\begin{figure}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-sfr-pairplot-output-1.pdf}
+
+}
+
+\caption{\label{fig-sfr-pairplot}Comparison of the \(SFR_{i}\) of the
+galaxies}
 
@@
 mean of SFR from the Ha and FUV, for \(SFR>10^{-3}\ M_\odot\, yr^{-1}\).
-As we can see from the plots (Figure~\ref{fig-sfr-lcv}) it is a good
-aproximation for all SFR's
-
-\[
+As we can see from the plots (Figure~\ref{fig-sfr-lvg}) it could be a
+good aproximation.
+
+\begin{equation}\phantomsection\label{eq-sfr-mean}{
 SFR = \frac{SFR_{FUV}+SFR_{H\alpha}}{2}, \text{if both exist, else: } SFR = SFR_i,\ i= FUV,\, H\alpha
-\]
+}\end{equation}
+
+\begin{figure}
+
+\begin{minipage}{0.50\linewidth}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-sfr-lvg-output-1.pdf}
+
+}
+
+\subcaption{\label{fig-sfr-lvg-1}Linear scale}
+
+\end{minipage}%
+%
+\begin{minipage}{0.50\linewidth}
+
+\centering{
+
+\includegraphics{compare_files/figure-pdf/fig-sfr-lvg-output-2.pdf}
+
+}
+
+\subcaption{\label{fig-sfr-lvg-2}Decimal logarithmic scale}
+
+\end{minipage}%
+
+\caption{\label{fig-sfr-lvg}Comparison of the \(SFR_{FUV}-SFR_{Ha}\) of
+the galaxies}
+
+\end{figure}%
 
@@
 
-{[}?{]}EXPLANATION this low correlation maybe comes from the
-inaccuracy/approximation of (Kroupa et al. (2020))
-
-The reason is that this aproximation is accurate if we consider a stable
-SFR over time. However, we tend to observe higher Ha for more recent SF
-activity. (we discussed it in our last meeting, I need a refrence).
+The low correlation in Figure~\ref{fig-sfr-compare-1} and the interval
+in Figure~\ref{fig-sfr-compare-2} show that the approximation
+(Equation~\ref{eq-sfr-mean}) is not great. According to Karachentsev and
+Kaisina (2013):
+
+\begin{itemize}
+\item
+  \textbf{Hα and FUV timescales}: \(H_\alpha\) traces short-term star
+  formation (\textasciitilde10 Myr) via massive O-type stars, while FUV
+  traces longer-term star formation (\textasciitilde100 Myr) from B-type
+  stars.
+\item
+  \textbf{Discrepancies due to star formation bursts}: In galaxies with
+  bursty or episodic star formation, Hα can significantly overestimate
+  SFR compared to FUV, which lags in reflecting recent star formation
+  events.
+\item
+  \textbf{Low-mass galaxy variability}: The scatter between
+  \(SFR_{\text{H}\alpha}\) and \(SFR_{\text{FUV}}\) is particularly high
+  in low-mass, dwarf galaxies, where stochastic star formation history
+  causes wide variability between the two indicators.
+\item
+  \textbf{Measurement uncertainties}: Internal extinction, errors in
+  distance estimates, and IMF stochasticity introduce biases in both Hα
+  and FUV fluxes, making simple averaging inappropriate.
+\item
+  \textbf{Conclusion}: The
+  \(SFR_{\text{total}} = \text{mean}(SFR_{\text{H}\alpha}, SFR_{\text{FUV}})\)
+  method oversimplifies the complexity of star formation processes and
+  is not reliable for galaxies with variable star formation or
+  significant measurement uncertainties
+\end{itemize}
+
+\newpage{}
 
@@
 \begin{longtable}[]{@{}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
-  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}@{}}
 \toprule\noalign{}
 \begin{minipage}[b]{\linewidth}\centering
-LCV
+LVG
 \end{minipage} & \begin{minipage}[b]{\linewidth}\centering
@@
 Description
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Count
 \end{minipage} \\
@@
 \endlastfoot
-logM26 & & Log mass within Holmberg radius & 233 \\
-logMHI & & Log mass within Holmberg radius & 233 \\
-& logM\_HEC & Decimal logarithm of the stellar mass {[}Msol{]} & 64 \\
+logM26 & & Log mass within Holmberg radius \\
+logMHI & & Log mass within Holmberg radius \\
+& logM\_HEC & Decimal logarithm of the stellar mass {[}Msol{]} \\
 & logM\_GSW & Decimal logarithm of the stellar mass in GSWLC-2
-{[}Msol{]} & 0 \\
-logStellarMass & & Stellar Mass from \(M_*/L=0.6\) & 287 \\
+{[}Msol{]} \\
+logStellarMass & & Stellar Mass from \(M_*/L=0.6\) \\
 \end{longtable}
@@
 \subsubsection{Stellar Masses Comparison}
+
+\newpage{}
 
@@
 \[
-\log{M_{*,HECATE}}=1.07\cdot\log{M_{*,LCV}}-0.69, \text{ but } \log{M_*}>6\Rightarrow M_{*,HEC}\sim M_{*,LCV}
+\log{M_{*,HECATE}}=1.07\cdot\log{M_{*,LVG}}-0.69, \text{ but } \log{M_*}>6\Rightarrow M_{*,HEC}\sim M_{*,LVG}
 \]
@@
 
+\newpage{}
+
 \subsubsection{Heatmap}
 
-\includegraphics{compare_files/figure-pdf/cell-35-output-1.pdf}
+\includegraphics{compare_files/figure-pdf/cell-31-output-1.pdf}
 

### 2024-10-19 tables/hecate_lvg_join.sh

@@ -14,11 +14,11 @@ stilts tmatch2 in1=final_table.ecsv in2=HECATE_LCV.fits out=inner_join.ecsv\
     values1="Ra Dec" values2="RA DEC " params=2 
 
 #Hecate not LCV
-stilts tmatch2 in1=final_table.ecsv in2=HECATE_LCV.fits out=HEC_not_LCV_join.ecsv\
+stilts tmatch2 in1=final_table.ecsv in2=HECATE_LCV.fits out=HEC_not_LVG_join.ecsv\
     join=2not1 matcher=sky\
     values1="Ra Dec" values2="RA DEC" params=2
     
 #LCV not Hecate  
-stilts tmatch2 in2=final_table.ecsv in1=HECATE_LCV.fits out=LCV_not_HEC_join.ecsv\
+stilts tmatch2 in2=final_table.ecsv in1=HECATE_LCV.fits out=LVG_not_HEC_join.ecsv\
     join=2not1 matcher=sky\
     values1="Ra Dec" values2="RA DEC" params=2

### 2024-10-19 mcmc/A_free_20%.py
mcmc

@@ -1,0 +1,93 @@
+import pymc as pm
+import numpy as np
+import pandas as pd
+from astropy.io import ascii
+from astropy.table import QTable
+import astropy.units as u
+import arviz as az
+from tqdm import tqdm
+import gc
+
+
+# Function to prepare the dataset
+def prepare_data(file_path):
+    # Load your dataset
+    dt = QTable(ascii.read(file_path), masked=True)
+    
+    # Transform to physical units
+    dt["SFR_HEC"] = (10**dt["logSFR_HEC"].value * u.solMass/u.yr).to(u.solMass/u.Gyr)  # SFR in Gyr units
+    dt["logSFR_HEC_Gyr"] = np.log10(dt["logSFR_HEC"].value) # logSFR in Gyr units
+    
+    # Convert to DataFrame and drop missing values
+    data = dt[["logSFR_HEC_Gyr", "logM_HEC"]].to_pandas().dropna()
+    print(data)
+    del dt
+    gc.collect()
+    return data
+
+# Function to run MCMC for a given galaxy
+def run_mcmc_for_galaxy(row):
+    with pm.Model() as model:
+        # Priors for t_today, logtau, and logA in log space
+        t_today = pm.Uniform('t_today', lower=10, upper=15)
+        logtau = pm.Uniform('logtau', lower=-3, upper=3)  # tau in log 
+        logA = pm.Uniform('logA', lower=-3, upper=12)  # log scale for A
+        # Convert tau and  to linear scale
+
+        tau = 10**logtau  # tau in linear scale
+        # Assume Mtot and logSFR_today_observed come from the sample
+        Mtot = row['logM_HEC']  # M_HEC is already in solMass
+        logSFR_today_observed = row['logSFR_HEC_Gyr']  # logSFR in Gyr units
+
+        # Use the corrected logarithmic form of SFR
+        logSFR_today = logA + np.log10(t_today) - 2 * np.log10(tau) - (t_today / tau) * np.log10(np.e)
+
+        # Likelihood (assuming Gaussian errors on log(SFR))
+        sigma = 0.1  # Example uncertainty in log(SFR)
+        SFR_likelihood = pm.Normal('SFR_likelihood', mu=logSFR_today, sigma=sigma, observed=logSFR_today_observed)
+
+        # Sampling using NUTS
+        try:
+            trace = pm.sample(2000, tune=2000, target_accept=0.95, init='jitter+adapt_diag',
+                              chains = 4, cores= 6,
[…]

### 2024-11-04 compare/quick_comp.py
weighted comparison

@@ -1,0 +1,113 @@
+#!/usr/bin/env python3
+
+import numpy as np
+import pandas as pd
+import statsmodels.api as sm
+import matplotlib.pyplot as plt
+
+# plt.style.use("seaborn-v0_8-whitegrid")
+# plt.style.use("ggplot")
+
+# Load the data
+data = pd.read_csv("../tables/inner_join.csv")
+cols = pd.read_csv("Reordered_Final_Comparison_Table.csv")
+
+data["SFR_total"] = data[["SFRFUV", "SFRHa"]].mean(axis=1)
+
+
+def perform_linear_regression_analysis_fixed(
+    x, y, desc=None, error=None, log_transform_x=False, log_transform_y=False
+):
+    # Check if the error column is None or NaN
+    if error is None or error == "None":
+        print(f"Warning: Error column for {x} vs {y} is not specified or is None.")
+
+    # Extract and align data, dropping NaNs
+    if error and error in data.columns:
+        aligned_data = data[[x, y, error]].dropna()
+    else:
+        aligned_data = data[[x, y]].dropna()
+
+    # Proceed only if there's sufficient data
+    if len(aligned_data) < 2:
+        print(f"Insufficient data for the pair ({x}, {y})")
+        return
+
+    x_data = aligned_data[x]
+    y_data = aligned_data[y]
+
+    # Apply log transformation if specified
+    if log_transform_x:
+        x_data = np.log10(x_data)
+    if log_transform_y:
+        y_data = np.log10(y_data)
+
+    # Weight calculation based on the error column if available
+    if error and error in aligned_data.columns:
+        y_err_data = aligned_data[error]
+        weights = 1 / y_err_data**2
+        model = sm.WLS(y_data, sm.add_constant(x_data), weights=weights)
+    else:
+        model = sm.OLS(y_data, sm.add_constant(x_data))
+
+    results = model.fit()
+
+    # Fit parameters
+    slope = results.params[1]
+    intercept = results.params[0]
+    slope_err = results.bse[1]
+    intercept_err = results.bse[0]
+    r_squared = results.rsquared
+
+    # Calculate residuals
+    residuals = y_data - (intercept + slope * x_data)
+
+    # Plot
+    fig, axs = plt.subplots(2, 1, figsize=(10, 10))
+
+    # Scatter plot with fit
+    if error and error in data.columns:
+        axs[0].errorbar(
[…]

### 2024-11-04 r_mcmc/R/functions.R
R_mcmc_stan

@@ -1,0 +1,75 @@
+# functions.R
+
+# Function to load and prepare the data
+prepare_data <- function(data_csv) {
+  dt <- data_csv %>%
+    mutate(
+      SFR_HEC = 10^logSFR_HEC_Gyr
+    ) %>%
+    drop_na(logSFR_HEC_Gyr, logM_HEC)
+  return(dt)
+}
+
+# Function to define initial values for the Stan model
+iiinit_function <- function() {
+  list( 
+   list(
+      t_today = 13.6,            # Initial guess for t_today
+      logtau = log10(6.3),       # Initial guess for log(tau)
+      logA = log10(5.268e+10)    # Initial guess for log(A)
+    )
+  )
+}
+init_function <-function(chains, N) {
+  lapply(1:chains, function(i) list(
+    t_today = rep(13.6, N),
+    logtau = rep(log10(6.3), N),
+    logA = rep(log10(5.268e+10), N)
+  ))
+}
+
+
+# Function to extract posterior predictions and compute residuals
+extract_posterior_predictions <- function(stan_fit, sfr_data) {
+  # Access the fit object (assuming the first fit object)
+  fit <- stan_fit
+  
+  # Extract draws for logSFR_today_pred
+  draws <- fit$draws(variables = "logSFR_today_pred")
+  
+  # Convert to data frame
+  draws_df <- as_draws_df(draws)
+  
+  # Gather data into long format
+  pred_summaries <- draws_df %>%
+    pivot_longer(
+      cols = starts_with("logSFR_today_pred"),
+      names_to = "variable",
+      values_to = "value"
+    ) %>%
+    group_by(variable) %>%
+    summarise(
+      mean = mean(value),
+      sd = sd(value)
+    )
+  
+  # Extract the index from variable names
+  pred_summaries <- pred_summaries %>%
+    mutate(
+      index = as.integer(str_extract(variable, "\\d+"))
+    )
+  
+  # Prepare observed data with index
+  observed_data <- sfr_data %>%
+    mutate(index = row_number())
+  
+  # Join predictions with observed data
+  pred_summaries <- pred_summaries %>%
+    inner_join(observed_data, by = "index") %>%
+    mutate(
+      residual = logSFR_HEC_Gyr - mean,
+      standardized_residual = residual / sd
+    )
+  
+  return(pred_summaries)
+}

### 2024-11-04 r_mcmc/_targets.R

@@ -1,0 +1,106 @@
+# Created by use_targets().
+# Follow the comments below to fill in this target script.
+# Then follow the manual to check and run the pipeline:
+#   https://books.ropensci.org/targets/walkthrough.html#inspect-the-pipeline
+
+# Load packages required to define the pipeline:
+library(targets)
+library(tarchetypes) # Load other packages as needed.
+library(stantargets)
+
+# Set target options:
+tar_option_set(
+  packages = c("readr", "dplyr", "tidyr", "stringr", "posterior"),
+  # format = "qs", # Optionally set the default storage format. qs is fast.
+  #
+  # Pipelines that take a long time to run may benefit from
+  # optional distributed computing. To use this capability
+  # in tar_make(), supply a {crew} controller
+  # as discussed at https://books.ropensci.org/targets/crew.html.
+  # Choose a controller that suits your needs. For example, the following
+  # sets a controller that scales up to a maximum of two workers
+  # which run as local R processes. Each worker launches when there is work
+  # to do and exits if 60 seconds pass with no tasks to run.
+  #
+  #   controller = crew::crew_controller_local(workers = 2, seconds_idle = 60)
+  #
+  # Alternatively, if you want workers to run on a high-performance computing
+  # cluster, select a controller from the {crew.cluster} package.
+  # For the cloud, see plugin packages like {crew.aws.batch}.
+  # The following example is a controller for Sun Grid Engine (SGE).
+  # 
+  #   controller = crew.cluster::crew_controller_sge(
+  #     # Number of workers that the pipeline can scale up to:
+  #     workers = 10,
+  #     # It is recommended to set an idle time so workers can shut themselves
+  #     # down if they are not running tasks.
+  #     seconds_idle = 120,
+  #     # Many clusters install R as an environment module, and you can load it
+  #     # with the script_lines argument. To select a specific verison of R,
+  #     # you may need to include a version string, e.g. "module load R/4.3.2".
+  #     # Check with your system administrator if you are unsure.
+  #     script_lines = "module load R"
+  #   )
+  #
+  # Set other options as needed.
+)
+
+# Run the R scripts in the R/ folder with your custom functions:
+tar_source()
[…]

### 2024-11-04 mcmc/A_free_20%.py
test_galaxies

@@ -21,6 +21,7 @@ def prepare_data(file_path):
     # Convert to DataFrame and drop missing values
     data = dt[["logSFR_HEC_Gyr", "logM_HEC"]].to_pandas().dropna()
     print(data)
+    data.to_csv("test_galaxies.csv")
     del dt
     gc.collect()
     return data
@@ -88,6 +89,6 @@ def run_mcmc_for_sample(data, sample_fraction=0.2, save_file="mcmc_results.csv")
 
 # Run the MCMC process
 if __name__ == "__main__":
-    data = prepare_data("./tables/outer_join.ecsv")
+    data = prepare_data("../tables/outer_join.ecsv")
     results_df = run_mcmc_for_sample(data, sample_fraction=0.2)
     print(results_df)

### 2024-11-04 compare/compare.qmd
fixed outer join
- all2 -> 1or2
- updated the catalog

@@
 temp = dt[["TType", "T"]].to_pandas().dropna()
+temp["TType"] = temp["TType"].astype("float64")
+temp["T"] = temp["T"].astype("float64")
+
 results = scipy.stats.linregress(x = temp["TType"],

### 2024-11-04 pipeline.sh

@@ -7,3 +7,5 @@ cd ../notes
 /bin/python3 list.py
 cd ../tables
 ./hecate_lcv_join.sh
+cd ../compare
+quarto render compare.qmd

### 2024-11-04 tables/hecate_lvg_join.sh

@@ -6,19 +6,23 @@
 
 #Outter join for each row of hecate
 stilts tmatch2 in1=final_table.ecsv in2=HECATE_LCV.fits out=outer_join.ecsv\
-    join=all2 matcher=sky\
+    join=1or2 matcher=sky\
     values1="Ra Dec" values2="RA DEC" params=2 
+    
+echo "Done Outter"    
 #Inner join
 stilts tmatch2 in1=final_table.ecsv in2=HECATE_LCV.fits out=inner_join.ecsv\
     join=1and2 matcher=sky\
     values1="Ra Dec" values2="RA DEC " params=2 
-
+    
+echo "Done Inner"    
 #Hecate not LCV
 stilts tmatch2 in1=final_table.ecsv in2=HECATE_LCV.fits out=HEC_not_LVG_join.ecsv\
     join=2not1 matcher=sky\
     values1="Ra Dec" values2="RA DEC" params=2
-    
+echo "Done Hecate not LCV"    
 #LCV not Hecate  
 stilts tmatch2 in2=final_table.ecsv in1=HECATE_LCV.fits out=LVG_not_HEC_join.ecsv\
     join=2not1 matcher=sky\
     values1="Ra Dec" values2="RA DEC" params=2
+echo "Done LCV not Hecate"    

### 2024-11-05 compare/quick_comp.py
dwarf classification

@@ -14,6 +14,36 @@ cols = pd.read_csv("Reordered_Final_Comparison_Table.csv")
 
 data["SFR_total"] = data[["SFRFUV", "SFRHa"]].mean(axis=1)
 
+# Define the mass and luminosity thresholds
+mass_threshold = 9  # Log(Mass) threshold for dwarf vs massive
+
+
+# Classify galaxies based on logM_HEC, logKLum, Tdw1, and Tdw2 with method flags
+def classify_galaxy(row):
+    # Initialize the classification and method flag
+    classification = "undefined"
+    method = ""
+
+    # Check Tdw1 and Tdw2 columns for morphological classification
+    if not pd.isna(row["Tdw1"]) or not pd.isna(row["Tdw2"]):
+        classification = "Dwarf"
+        method = "Tdw"  # Classification based on morphology (Tdw1 or Tdw2)
+    # Check mass classification
+    elif row["logM_HEC"] < mass_threshold:
+        classification = "Dwarf"
+        method = "Mass"  # Classification based on mass
+    elif row["logM_HEC"] >= mass_threshold:
+        classification = "Massive"
+        method = "Mass"
+
+    return classification, method
+
+
+# Apply the classification function and split into two new columns
+data[["mass_type", "classification_method"]] = data.apply(
+    lambda row: pd.Series(classify_galaxy(row)), axis=1
+)
+
 
 def perform_linear_regression_analysis_fixed(
     x, y, desc=None, error=None, log_transform_x=False, log_transform_y=False
@@ -24,9 +54,9 @@ def perform_linear_regression_analysis_fixed(
 
     # Extract and align data, dropping NaNs
     if error and error in data.columns:
-        aligned_data = data[[x, y, error]].dropna()
+        aligned_data = data[[x, y, error, "mass_type"]].dropna()
     else:
-        aligned_data = data[[x, y]].dropna()
+        aligned_data = data[[x, y, "mass_type"]].dropna()
 
     # Proceed only if there's sufficient data
     if len(aligned_data) < 2:
@@ -35,6 +65,7 @@ def perform_linear_regression_analysis_fixed(
 
     x_data = aligned_data[x]
     y_data = aligned_data[y]
+    groups = aligned_data.groupby("mass_type")
 
     # Apply log transformation if specified
     if log_transform_x:
@@ -62,20 +93,27 @@ def perform_linear_regression_analysis_fixed(
     # Calculate residuals
     residuals = y_data - (intercept + slope * x_data)
 
+    # Define markers for each mass type
[…]

### 2024-12-16 r_mcmc/R/functions.R
new stan try
y -> old x.stan

@@ -24,8 +24,8 @@ prepare_data <- function(data_csv) {
 init_function <-function(chains, N) {
   lapply(1:chains, function(i) list(
     t_sf = rep(13.6, N),
-    #logtau = rep(log10(4), N), # MS galaxies 3.5<tau<4.5
-    #logA = rep(10, N),
+    logtau = rep(log10(4), N), # MS galaxies 3.5<tau<4.5
+    logA = rep(5.5, N),
     tau = rep(4,N),
     zeta = rep(1.3,N)
   ))

### 2024-12-16 r_mcmc/_targets.R

@@ -71,165 +71,178 @@ list(
   tar_stan_mcmc(
     stan_fit,
     stan_files = "x.stan",
+    #stdout = "out.txt",
+    #stderr = "error.txt",
     data = list(
       N = nrow(sfr_data),
-      #logSFR_UNGC_Gyr = sfr_data$logSFR_UNGC_Gyr,
+      logSFR_UNGC_Gyr = sfr_data$logSFR_UNGC_Gyr,
       id_numbers = sfr_data$id_number,
-      #mass = sfr_data$logM_HEC
-      mass = sfr_data$StellarMass,
-      SFR_obs = sfr_data$SFR_UNGC_Gyr
+      M_star = sfr_data$logM_HEC
     ),
     chains = 3,
     parallel_chains = 6,
-    iter_sampling = 3500,
-    iter_warmup = 2500,
-    init = init_function(3,1132)
+    iter_sampling = 2000,
+    iter_warmup = 1500,
+    init = init_function(3,1132),
+    
   ),
-  # 
-  # tar_stan_summary(
-  #   id_summary,
-  #   fit = stan_fit_mcmc_x,
-  #   data = list(
-  #     N = nrow(sfr_data),
-  #     logSFR_UNGC_Gyr = sfr_data$logSFR_UNGC_Gyr,
-  #     id_numbers = sfr_data$id_number
-  #   ),
-  #   variables = "id"
-  # ),
-  # 
-  # tar_stan_summary(
-  #   sfr_summary,
-  #   fit = stan_fit_mcmc_x,
-  #   data = list(
-  #     N = nrow(sfr_data),
-  #     logSFR_UNGC_Gyr = sfr_data$logSFR_UNGC_Gyr,
-  #     id_numbers = sfr_data$id_number
-  #   ),
-  #   variables = "logSFR_today"
-  # ),
-  # 
-  # tar_stan_summary(
-  #   t_sf_summary,
-  #   fit = stan_fit_mcmc_x,
-  #   data = list(
-  #     N = nrow(sfr_data),
-  #     logSFR_UNGC_Gyr = sfr_data$logSFR_UNGC_Gyr,
-  #     id_numbers = sfr_data$id_number
-  #   ),
-  #   variables = "t_sf"),
-  #   
-  # tar_stan_summary(
-  #   tau_summary,
-  #   fit = stan_fit_mcmc_x,
-  #   data = list(
[…]

### 2024-12-16 compare/compare.qmd
presentations
one for Chatzidimitriou, one for akras team

@@
 ---
+```{python}
+
+```
 

### 2024-12-16 compare/compare.tex
presentations
one for Chatzidimitriou, one for akras team

@@
 The dataset we are going to use for the comparison (inner join) consists
-of 288 galaxies and 168 columns with their physical characteristics.
+of 3934 galaxies and 172 columns with their physical characteristics.
 
@@
 \endlastfoot
-Inner join & 288 \\
-Outer join & 2901 \\
-LVG & 1316 \\
+Inner join & 3934 \\
+Outer join & 3934 \\
+LVG & 1321 \\
 HECATE & 2901 \\
-Unique galaxies in LVG & 1028 \\
+Unique galaxies in LVG & 1033 \\
 Unique Galaxies in Hecate & 2613 \\
@@
 
-Completeness (HECATE)= 10 \%
-
-Completeness (LVG)= 22 \%
+Completeness (HECATE)= 136 \%
+
+Completeness (LVG)= 298 \%
 
@@
 =\(\frac{\text{Total galaxies in Outer}}{\text{Unique galaxies in HECATE + LVG}}\)=
-80 \%
+108 \%
 
@@
 \endlastfoot
-count & 287 & 209 & 202 \\
-mean & 60 & 59 & -0 \\
-std & 19 & 23 & 0 \\
-min & 9 & 0 & -3 \\
-50\% & 60 & 59 & 0 \\
+count & 1308 & 1994 & 202 \\
+mean & 55 & 51 & -0 \\
+std & 20 & 20 & 0 \\
+min & 0 & 0 & -3 \\
+50\% & 54 & 50 & 0 \\
 max & 90 & 90 & 1 \\

### 2024-12-16 presentation.qmd
presentations
one for Chatzidimitriou, one for akras team

---
title: "Παρουσιαση πτυχιακης"
subtitle: ""
author: "Δημήτρης Παπαχριστόπουλος"
format:
  revealjs:
    theme: moon
    center: true
    smaller: true
    #embed-resources: true
    chalkboard: true 
    controls: true
    slide-number: true 
    revealjs-plugin: 
      - PdfExport
    bibliography: My_Library.bib
editor: 
  markdown: 
    wrap: sentence
---

# Γαλαξιες

::::: columns
::: {.column width="50%"}
-   Οι γαλαξίες είναι τεράστιες δομές που περιέχουν:
    -   Αστέρια
    -   Αέρια και σκόνη που συμβάλλουν στη δημιουργία νέων άστρων.
    -   Αστρικά και πλανητικά συστήματα
    -   Απομεινάρια άστρων (λευκοί νάνοι, αστέρες νετρονίων και μαύρες τρύπες)
:::

::: {.column width="50%"}
![NGC 4414](figure/1308px-NGC_4414_(NASA-med).jpg){fig-align="center"}
:::

**Κρατιούνται ενωμένα από τη δύναμη της βαρύτητας.**
:::::

------------------------------------------------------------------------

## Μορφολογια

::::: columns
::: column
-   **Σπειροειδείς**
-   **Ελλειπτικοί**
-   **Ακανόνιστοι**
:::

::: column
-   **Νάνοι γαλαξίες:** $M_*\lessapprox 10^7\ M_\odot$
:::

![By Antonio Ciccolella / M. De Leo](figure/1280px-Hubble_-_de_Vaucouleurs_Galaxy_Morphology_Diagram.png){fig-align="center" width="600"}
:::::

# Αστρογενεση

::::: columns
::: {.column width="50%"}
**Η αστρογένεση** είναι η διαδικασία κατά την οποία πυκνές περιοχές εντός μοριακών νεφών καταρρέουν

![](figure/evolution.png){fig-align="center"}
:::

::: {.column width="50%"}
**Ο ρυθμός αστρογένεσης** (SFR = Star Formation Rate) ορίζεται ως το σύνολο της αέριας μάζας ενός γαλαξία που μετατρέπεται σε άστρα σε ένα συγκεκριμένο χρονικό διάστημα.

Συνήθως εκφράζεται σε ηλιακές μάζες ανά έτος ($M_\odot\cdot yr^{-1}$)
:::
:::::

# Εμμεσος υπολογισμος SFR

::: incremental
-   **Ροή στο Hα**

-   **Ροή στο μακρινό υπεριώδες (FUV)**

-   **Ροή στο υπέρυθρο (IR)**

-   Ραδιοφωνική συνεχής εκπομπή

-   Εκπομπή ακτίνων Χ
:::

::: notes
Εκτιμάται με διάφορες φωτομετρικές ή φασματικές μεθόδους, βάση της λαμπρότητας τουλάχιστον ενός φάσματος φωτός ή την ένταση μιας φασματικής γραμμής.
Οι διαφορετικές λαμπρότητες/εντάσεις έχουν διαφορετικές πηγές οι οποίες μπορούν να μας προσφέρουν διαφορετικές πληροφορίες για τους μηχανισμούς εκπομπής, αλλά και για τις πηγές ακτινοβολίας του εκάστοτε γαλαξία.

-   *Εκπομπή Hα* : Παρέχει πληροφορίες για τον αριθμό των ιονίζοντων φωτονίων, με την υπόθεση ότι όλα τα ιοντίζοντα φωτόνια χρησιμοποιούνται πλήρως και επανεκπέμπονται.
    Αυτά τα φωτόνια προέρχονται κυρίως από θερμά άστρα μεγάλης μάζας, στα αρχικά στάδια ζωής τους (νέα άστρα τύπου Ο, ηλικίας \~10 Myr).
    Η παρουσία σκόνης μπορεί να επηρεάσει σημαντικά τις παρατηρήσεις.
    Ανήκει στο οπτικό φάσμα (wavelength: ~6563 Å).

-   *Ροή στο μακρινό υπεριώδες (FUV)*: Εκπέμπεται κυρίως από νεαρά (θερμά) άστρα, τα οποία είναι παλαιότερα ή λιγότερο μαζικά άστρα (άστρα τύπου Β, ηλικίας \~100 Myr), σε σχέση με αυτά που είναι υπεύθυνα για την εκπομπή Hα.
    Επίσης η παρουσία σκόνης μπορεί να επηρεάσει σημαντικά τις παρατηρήσεις.
    υπεριώδες φάσμα (wavelength: ~1300–2000 Å).

-   *Ροή στο υπέρυθρο (IR)*: Υποθέτει ότι ένα σταθερό ποσοστό της εκπεμπόμενης αστρικής ακτινοβολίας απορροφάται από τη σκόνη, η οποία στη συνέχεια την επανεκπέμπεται σε υπέρυθρα μήκη κύματος, ενισχύοντας τη συνολική υπέρυθρη ακτινοβολία.
Ανήκει στο υπέρυθρο φάσμα (wavelength: ~8–1000 μm).

-   *Ραδιοφωνική συνεχής εκπομπή*: Παρουσιάζει υψηλή συσχέτιση με την υπέρυθρη ακτινοβολία (IR).
    Η προέλευση αυτής της εκπομπής είναι πολύπλοκη, καθώς οφείλεται στη σύγχροτρον ακτινοβολία από σχετικιστικά ηλεκτρόνια και τη θερμική ακτινοβολία Bremsstrahlung από θερμό αέριο.
Ανήκει στο ραδιοφωνικό φάσμα (wavelength: ~cm to m range).

-   *Εκπομπή ακτίνων Χ*: Σε γαλαξίες με έντονη αστρογένεση, οι ακτίνες Χ προέρχονται κυρίως από διπλά συστήματα υψηλής μάζας (Αστέρας νετρονίων ή Μελανή Οπή με μαζικό συνοδό αστέρα) και θερμό αέριο από εκρήξεις υπερκαινοφανών, με τη φωτεινότητα τους να συσχετίζεται στατιστικά με τον ρυθμό αστρογένεσης (SFR) έως το redshift $z~4$.
    Ένα σημαντικό πλεονέκτημα των ακτίνων Χ είναι ότι δεν επηρεάζονται από τη σκόνη, επιτρέποντας ακριβείς παρατηρήσεις σε υψηλά redshifts.
Ανήκει στο ακτίνων Χ φάσμα (wavelength: ~0.01–10 nm, ή ενέργεια: ~0.1–10 keV).

:::

# Νομος του Hubble

-   **Νόμος του Hubble**:
    -   Οι γαλαξίες **απομακρύνονται** μεταξύ τους καθώς το Σύμπαν διαστέλλεται.
    -   $V = H_0\times d$, όπου $H_0 \approx 69.8 \text{ km/s/Mpc}$ είναι η σταθερά του Hubble.
-   **Ερυθρομετατόπιση (Redshift)**:
    -   Το φως από απομακρυνόμενους γαλαξίες:
        -   εμφανίζεται μετατοπισμένο προς το κόκκινο μέρος του φάσματος.
        -   χρειάζεται περισσότερο χρόνο για να φτάσει σε εμάς (βλέπουμε στο παρελθόν).

------------------------------------------------------------------------

![](figure/Age_by_redshift.png){fig-align="center"}

# Lilly-Madau Plot

![@madau2014](./figure/lily-madau.png){fig-align="center"}

# Delayed-$τ$ model

$$
SFR_{del}=A_{del}\frac{t_{sf}}{\tau^2}e^{-\frac{t_{sf}}{\tau}}\ \left[\frac{M_\odot}{yr} \right],\ t_{sf} = T_{\text{universe}} - t_{\text{start}}
$$

![](figure/Screenshot%20from%202024-12-08%2000-12-51.png){fig-align="center" width="600"}

::: {.fragment .fade-in}
$$\int_0^{t_{sf}}\text{SFR(t)} \text{dt} = Μ_*$$
:::

::: notes
-   **Το delayed-**$\tau$ model περιγράφει την ιστορία σχηματισμού αστέρων (SFH) ενός γαλαξία, υποθέτοντας ότι οι ρυθμοί σχηματισμού αστέρων (SFRs) συνήθως αυξάνονται στην αρχική φάση εξέλιξης του γαλαξία και βαθμιαία μειώνονται.

- Κρουπα χρησιμοποίησε δεδομένα για στο sfr kai M_*  και υπολόγισε τις παραμέτρους του μοντέλου, για να δείξει την ασυμφωνία του με το lilly madau

-   **Speagle et al. (2014):**[@speagle2014] Το SFH γαλαξιών της κύρια ακολουθίας, μπορεί να παραμετροποιηθεί με ακρίβεια βάση αυτού του μοντέλου
:::

# Δεδομενα

:::::: columns
::: {.column width="50%"}
Γαλαξίες του Local Cosmological Volume

-   $D \leq 10$ Mpc
-   Redshift: $z = 0 \rightarrow t_{sf} = 13.8-t_{\text{start}}$
:::

:::: {.column width="50%"}
::: {.fragment .fade-in}
-   Για αυτούς τους γαλαξίες έχουμε:
    -   SFR από Hα, FUV και IR
    -   Αστρικές μάζες
:::
::::

| Table                    | Number of galaxies |
|:-------------------------|-------------------:|
| UNGC [@karachentsev2013] |               1321 |
| HECATE [@kovlakas2021]   |               2901 |
| Join                     |           **3934** |
::::::

# Πρωτη προσεγγιση

-   Σύστημα 2 εξισώσεων και 2 μεταβλητών ($A_{del},\ \tau$), κρατώντας το $t_{sf} = 13.6$ Gyr σταθερό.
-   Λύση με υπολογιστικές μεθόδους
    -   Python fsolve
-   Θα γίνει για *όλους* τους γαλαξίες του τελικού καταλόγου.

::: notes
Η συνάρτηση fsolve της βιβλιοθήκης SciPy χρησιμοποιεί τη μέθοδο του Powell, η οποία συνδυάζει τις μεθόδους Newton-Raphson και κλίσης, για την εύρεση των ριζών ενός συστήματος μη γραμμικών εξισώσεων
:::

## Υπολογισμος $\tau$

:::::: columns
::: {.column width="50%"}
![](figure/tau-hist.png)
:::

:::: {.column width="50%"}
::: incremental
-   **Προβλήματα Μεθόδου:**
    -   Επιτρέπει την ύπαρξη αρνητικών $\tau$
    -   $t_{sf} = 13.6\, \text{Gyr}$, αποκλείει την περίπτωση κάποιοι γαλαξίες να έχουν διαφορετικό $t_{sf}$
:::
::::
::::::

# Markov Chain Monte Carlo

-   Υπολογίζει και τις 3 μεταβλητές ταυτόχρονα
-   Σύστημα 2 εξισώσεων και 3 μεταβλητών ($A_{del},\ \tau, t_{sf}$), δεν κρατάμε το $t_{sf} = 13.6$ Gyr σταθερό.
-   Mας δίνει σφάλματα για τα αποτελέσματα
-   Μπορούμε να περιορίσουμε το διάστημα των τιμών

::: notes
Αλυσίδες Markov: Σειρές καταστάσεων όπου η επόμενη κατάσταση εξαρτάται μόνο από την τρέχουσα.

Δειγματοληψία Monte Carlo: Χρήση τυχαίων δειγμάτων για την εκτίμηση στατιστικών μεγεθών.

Συνδυασμός MCMC: Δημιουργία αλυσίδων Markov που παράγουν δείγματα από την επιθυμητή κατανομή.
:::

------------------------------------------------------------------------

:::: {.columns}

::: {.column width="70%"}
![](r_mcmc/plots/Hists/logA.png)
:::

::: {.column width="30%"}

Εύρος $A_{del}$ από προηγούμενη μέθοδο:

$log(A_{del}) = [-1,13]$
:::

::::

------------------------------------------------------------------------

:::: {.columns}

::: {.column width="70%"}
![](r_mcmc/plots/Hists/logtau.png)
:::

::: {.column width="30%"}

Δεν υπάρχουν αρνητικές τιμές για το $\tau$
:::

::::

------------------------------------------------------------------------

:::: {.columns}

::: {.column width="70%"}
![](r_mcmc/plots/Hists/t_sf.png)
:::

::: {.column width="30%"}
Έχουμε γαλαξίες με $t_{sf}\neq 13.6$ Gyr
:::

::::

# Μελλοντικα σχεδια

-   Να τρέξω τον κώδικα με όλα τα δεδομένα
-   Να κάνω την τελική σύγκριση των δύο μεθόδων (1-1 γαλαξία)
-   Να δω πως το $t_{sf}$ επηρεάζεται από την μάζα των γαλαξιών και από τον τύπο του γαλαξία

------------------------------------------------------------------------

### 2024-12-16 pca.py

@@ -1,199 +1,0 @@
-#!/usr/bin/env python3
-
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-import seaborn as sns
-
-# Astropy for ecsv data
-from astropy.io import ascii
-from astropy.table import Table, QTable
-from sklearn.decomposition import PCA
-from sklearn.preprocessing import StandardScaler
-
-# Reading the ECSV file
-data = ascii.read("tables/final_table.ecsv")
-
-data = data.to_pandas()
-print(data.shape)
-# keep only columns with numeric data types
-numeric_data = data.select_dtypes(include=[np.number])
-
-# drop columns with e_ in the name
-numeric_data = numeric_data.drop(
-    columns=[col for col in numeric_data.columns if "e_" in col]
-)
-print(numeric_data.describe())
-
-# normalize the data with standard scaler
-scaler = StandardScaler()
-scaled_data = scaler.fit_transform(numeric_data)
-normalized_data = pd.DataFrame(scaled_data, columns=numeric_data.columns)
-print(normalized_data.describe())
-
-# fill the scaled_data arrays with 0 where there were nans
-normalized_data = normalized_data.fillna(0)
-
-
-# PCA analysis
-pca = PCA()
-pca_data = pca.fit_transform(normalized_data)
-
-# print the explained variance ratio
-expl_var = pca.explained_variance_ratio_
-df_expl_var = (
-    pd.DataFrame(
-        data=zip(range(1, len(expl_var) + 1), expl_var, expl_var.cumsum()),
-        columns=["PCA", "Explained Variance (%)", "Total Explained Variance (%)"],
-    )
-    .set_index("PCA")
-    .mul(100)
-    .round(1)
-)
-print(df_expl_var)
-# Plotting our explained variance
-import matplotlib.pyplot as plt
-
-fig, ax = plt.subplots(figsize=(8, 8))
-ax.bar(
-    x=df_expl_var.index,
-    height=df_expl_var["Explained Variance (%)"],
-    label="Explained Variance",
-    width=0.9,
-    color="#AAD8D3",
-)
-ax.plot(
-    df_expl_var["Total Explained Variance (%)"],
-    label="Total Explained Variance",
-    marker="o",
[…]

### 2024-12-16 thesis.qmd
begin of thesis
- Abstract
- Skeleton
- SFR and traces

---
title: "thesis"
author: "Dimitris Papachristopoulos"
format: 
  pdf: default
  #logo: ./figure/
  arxiv-pdf:
    keep-tex: true    
toc: true
toc-depth: 3
theme: minti
bibliography: ./My_Library.bib
execute: 
  echo: false
  eval: true
  warning: false
editor: visual
---

{{<pagebreak>}}

# Abstract

The Star Formation History (SFH) of a galaxy can offer many insights not only for the evolution and the future of the galaxy, but also for the evolution of the Universe. This is why there are various theoretical models trying to describe the SFH of galaxies. One of those models is the Delayed-Tau model, which approximates the Star Formation Rates (SFR) of galaxies as a function with a rising SFR at the beginning, until it reaches a peak at a time $\tau$, unique for each galaxy, and then it drops at an exponential rate.

@haslbauer2023 argues that the Delayed-$\tau$ model is opposed to the Lilly-Madau plot ([@madau2014]), which plots the observed SFR's of galaxies with the corresponding redshifts ($z$) and calculates a cosmic SFR peak at $z\approx 2$. The way they calculated this inconsistency is by using observatory data for SFR and Stellar Masses [^1] from the UNGC catalog (@karachentsev2013, @karachentsevSTARFORMATIONPROPERTIES2013) for calculating the parameters (the timescale $\tau$ and the normalization constant $A_{del}$) of the model. This calculation for the galaxies of the Local Cosmological Volume (LCV), allows the investigation of the SFR throughout the life each galaxy and so we can find the expected time of peak of the SFR.

[^1]: They calculated the Stellar Masses by using a Mass to Light ratio of 0.6

In this thesis project, we will try to calculate the same parameters, by using a bigger sample size and the method Markov Chain Monte Carlo, to examine if the inconsistencies of the model derive from the results of the previous analysis, or if it is an intrinsic problem of the model

**Keywords:** Galaxies, Galaxy Evolution, Star Formation History (SFH), Star Formation Rate (SFR), Delayed-$\tau$, Local Cosmological Volume, Lilly-Madau Plot, Redshift, Markov Chain Monte Carlo (MCMC).

{{<pagebreak>}}

# Galaxy Morphology and Star-Forming Regions

## Galaxy Ingridients

## Galaxy Classification

### Hubble-de Vacouler Classification

### Dwarf Galaxies

## Star-Formnig Regions

# Star Formation History (SFH)

The SFH of a galaxy describes the evolution of its star formation rate over time. By selecting an appropriate model for SFH, we can analyze stellar production, predict periods of active or quiescent star formation, and determine when SFR stabilizes.

Understanding SFH models is crucial for interpreting internal and external processes affecting galaxies and identifying conditions for intense star formation in their early stages.Star Formation Rate

## Star Formation Rate

The star formation rate (SFR) is defined as the total gas mass of a galaxy converted into stars over a specific time interval. It is typically expressed in solar masses per year ($M_\odot \cdot \text{yr}^{-1}$).

The SFR varies significantly over time, and its integration over time provides the total stellar mass formed during the galaxy’s history of star formation. Specifically:

where $\zeta$ accounts for mass loss, approximately $\zeta \approx 1.3$ (@kroupaConstraintsStarFormation2020).

### Estimating SFR from Spectra

SFR can be estimated using various photometric or spectroscopic methods based on the luminosity of at least one spectral band or the intensity of a spectral line. Different luminosities and intensities trace distinct emission mechanisms, offering insights into a galaxy’s radiation sources. Below are common methods:

- **H\boldmath${\alpha}$ Emission**: Traces the number of ionizing photons, assuming full usage and re-emission. These photons mainly originate from hot, massive stars (O-type stars, \~10 Myr). Dust can significantly affect observations.

- **Infrared (IR) Flux**: Assumes a fixed fraction of stellar radiation is absorbed by dust, re-emitted at infrared wavelengths, and enhances total IR radiation.

- **Radio Continuum Emission**: Strongly correlated with IR. Its origin is complex, involving synchrotron radiation from relativistic electrons and thermal Bremsstrahlung from hot gas.

- **Far-Ultraviolet (FUV) Flux**: Mainly emitted by young, hot stars (e.g., B-type stars, \~100 Myr). Dust presence can also significantly affect observations.

- **X-Ray Emission**: In star-forming galaxies, X-rays arise from high-mass binary systems (neutron star or black hole with massive stellar companion) and hot gas from supernovae, correlating with SFR up to redshift $z \sim 4$. X-rays are dust-insensitive, enabling accurate high-redshift observations.

SFR for different luminosities $L_i$ can be calculated as:

$$
\text{SFR} = \mathcal{K}_i\times L_i
$$ {#eq-sfr-spectra}

where $\mathcal{K}_i$ is a constant specific to each $L_i$ ($i =$ H$α$, IR, radio, FUV, X). In our analysis, we lack radio and X-ray data.

For FUV and H$α$ observations, which are affected by dust, corrections or models accounting for dust absorption are applied. Generally:

Following @madauCosmicStarFormation2014, this method may underestimate true SFRs, as different galaxy populations exhibit varying absorption mechanisms.

A more robust estimate of total SFR is:

where $L_{\text{FUV}}$ is uncorrected for absorption.

## Main Sequence Galaxies

The SFR and stellar mass of a galaxy are tightly correlated by the relationship:

$$
\log(\text{SFR}) = \alpha \log(M_*)+\beta
$$

where $\alpha(t)$ and $\beta(t)$ depend on time and redshift $z$ (@speagleHighlyConsistentFramework2014):

### Star Formation History Models

Parameterized SFH models are commonly used, offering simplicity through a few parameters (@carnallHowMeasureGalaxy2019a):

1. **Exponential Decline (τ Model)**:

   where $\tau$ is the timescale and $t_{\text{sf}} = t - T_0$ is the star formation time.

2. **Delayed Exponential (τ Model)**:

   accounting for an initial rise in SFR before declining. Here, $\tau$ is the time to reach maximum SFR.

3. **Log-Normal Model**:

   with $\tau$ and $T_0$ as free parameters.

4. **Double Power Law**:

   where $\tau$ is the timescale, and $\alpha$, $\beta$ govern the SFR rise and fall.

Non-parametric models are also available, providing flexibility for galaxies with complex SFH patterns.

## Delayed-$τ$ Model

The delayed $τ$ model is widely used for describing an initial starburst followed by a gradual decline in SFR. This places galaxies on the main sequence. It is particularly effective for massive galaxies (@haslbauerCosmologicalStarFormation2023). However, it assumes smooth SFR evolution and may overestimate peak SFR in high-redshift galaxies.

Using the delayed τ model, we compute $\tau$, $t_{\text{sf}}$, and normalization constant $A_{\text{del}}$ with:

$$
\text{SFR}_0 = \text{SFR}(t_{sf}) = A_{del}\frac{t_{sf}}{\tau^2}e^{-t_{sf}/\tau}
$$ {#eq-delayed-current}

where $\text{SFR}_0$ is given in the catalogs.

# Hubble Law

## Redshift 
## Lookback time

# Lilly-Madau Plot

# Delayed-$\tau$ model

# Computational Methods

## Newton-Raphson
## Markov Chain Monte Carlo

# Prepering the Catalogs

UNGC HECATE join etc...

## Catalog Completeness
## Comparing the Catalogs
## The "special" case of the Star Formation Rates

# Calculating the parameters

## According to pre-existing bibliography
### Problems with the method

## MCMC

### 2024-12-25 r_mcmc/R/functions.R
tsf->x

@@ -24,6 +24,7 @@ prepare_data <- function(data_csv) {
 init_function <-function(chains, N) {
   lapply(1:chains, function(i) list(
     t_sf = rep(13.6, N),
+    #x = rep(3, N),
     logtau = rep(log10(4), N), # MS galaxies 3.5<tau<4.5
     logA = rep(5.5, N),
     tau = rep(4,N),

### 2024-12-25 r_mcmc/_targets.R

@@ -79,11 +79,11 @@ list(
       id_numbers = sfr_data$id_number,
       M_star = sfr_data$logM_HEC
     ),
-    chains = 3,
-    parallel_chains = 6,
-    iter_sampling = 2000,
-    iter_warmup = 1500,
-    init = init_function(3,1132),
+    chains = 10,
+    parallel_chains = 8,
+    iter_sampling = 5000,
+    iter_warmup = 3500,
+    init = init_function(10,1132),
     
   ),
 
@@ -160,7 +160,17 @@ list(
     ),
     variables = "logA"
   ),
-
+  
+  tar_stan_summary(
+    x_summary,
+    fit = stan_fit_mcmc_x,
+    data = list(
+      N = nrow(sfr_data),
+      logSFR_UNGC_Gyr = sfr_data$logSFR_UNGC_Gyr,
+      id_numbers = sfr_data$id_number
+    ),
+    variables = "x"
+  ),
   tar_target(
     divergences,
     stan_fit_diagnostics_x$divergent__
@@ -183,7 +193,6 @@ list(
                              "t_sf" = t_sf_summary,
                              "log_tsf" = log_tsf_summary,
                              "logSFR_today" = sfr_summary,
-                             "id" = id_summary,
                              "logtau" = logtau_summary)
 
       # Generate the plot
@@ -210,7 +219,6 @@ list(
                              "t_sf" = t_sf_summary,
                              "log_tsf" = log_tsf_summary,
                              "logSFR_today" = sfr_summary,
-                             "id" = id_summary,
                              "logtau" = logtau_summary)
       max_count <- max(ggplot_build(
         ggplot(summary_data, aes(x = mean)) +

### 2024-12-26 thesis.qmd
SFR translation and hubble

@@
 
-## Galaxy Ingridients
-
 ## Galaxy Classification
 
-### Hubble-de Vacouler Classification
+### Hubble-de Vaucouleurs Classification
 
@@
 
-## Star-Formnig Regions
+## Star-Forming Regions
 
@@
 
-Understanding SFH models is crucial for interpreting internal and external processes affecting galaxies and identifying conditions for intense star formation in their early stages.Star Formation Rate
+Understanding SFH models is crucial for interpreting internal and external processes affecting galaxies and identifying conditions for intense star formation in their early stages.
 
@@
 
-where $\zeta$ accounts for mass loss, approximately $\zeta \approx 1.3$ (@kroupaConstraintsStarFormation2020).
+$$
+\int_0^{t_{sf}} \text{SFR}(t)dt = \zeta M_*(t_{sf}),\ t_{sf}=\text{Time of Star Formation,} 
+$$ {#eq-sfr_int}
+
+where $\zeta$ accounts for mass loss during the Star Formation and is approximately $\zeta \approx 1.3$ (@kroupaConstraintsStarFormation2020).
 
@@
 
-- **H\boldmath${\alpha}$ Emission**: Traces the number of ionizing photons, assuming full usage and re-emission.
-These photons mainly originate from hot, massive stars (O-type stars, \~10 Myr).
+[^2]
+
+[^2]:
+    -   [@calzettiStarFormationRate2012], [@ASTR620GalaxiesFall]
+
+-   **Hα** \boldmath$\alpha$ **Emission**: Young, hot, massive stars (O-type stars, \~10 Myr, \~20 $M_\odot$) produce a number of ionizing photons, which they ionize the surrounding hydrogen rich gas.
+The hydorgen undergoes recombination cascades which produce Balmer emission lines of $H\alpha$ (0.6563 $\mu m$) and $H\beta$ (0.4861 $\mu m$).
 Dust can significantly affect observations.
 
-- **Infrared (IR) Flux**: Assumes a fixed fraction of stellar radiation is absorbed by dust, re-emitted at infrared wavelengths, and enhances total IR radiation.
+-   **Far-Ultraviolet (FUV) Flux**: Mainly emitted by young, hot stars ( B-type stars, \~100 Myr). Dust presence can also significantly affect observations.
+
+-   **Infrared (IR) Flux**: The stars in a galaxy can heat up the dust in different ways, which then emits radiation in different parts of the IR spectrum.
+For example, young and massive, short-lived stars, emit UV radiation which then the heated dust emits in a wavelength of $\approx 60 \mu m$, whereas dust heated by UV-faint old or low-mass stars will emit at $\approx 100-150\mu m$.
+As a result, the total IR emission is age-agnostic and provides a more accurate approximation of the SFR because it accounts for contributions from both young and old stellar populations.
 
 -   **Radio Continuum Emission**: Strongly correlated with IR. Its origin is complex, involving synchrotron radiation from relativistic electrons and thermal Bremsstrahlung from hot gas.
-
-- **Far-Ultraviolet (FUV) Flux**: Mainly emitted by young, hot stars (e.g., B-type stars, \~100 Myr). Dust presence can also significantly affect observations.
 
@@
 $$
-\text{SFR} = \mathcal{K}_i\times L_i
+\text{SFR}_i = \mathcal{K}_i\times L_i
 $$ {#eq-sfr-spectra}
 
-where $\mathcal{K}_i$ is a constant specific to each $L_i$ ($i =$ H$α$, IR, radio, FUV, X). In our analysis, we lack radio and X-ray data.
+where $\mathcal{K}_i$ is a constant specific to each $L_i$ ($i =$ H$\alpha$, IR, radio, FUV, X). In our analysis, we lack radio and X-ray data.
 
-For FUV and H$α$ observations, which are affected by dust, corrections or models accounting for dust absorption are applied. Generally:
+Since the luminosities $L_{\text{FUV}}$ and $L_{\text{H}\alpha}$ originate from young stars and are highly sensitive to dust, we either directly observe stars unaffected by dust or use correction models to account for dust absorption.
+It is crucial to ensure that these models neither underestimate nor overestimate the luminosities by overlooking or double-counting the same sources.
 
-Following @madauCosmicStarFormation2014, this method may underestimate true SFRs, as different galaxy populations exhibit varying absorption mechanisms.
+Additionally, because these luminosities are emitted by similar stellar populations, we can reasonably expect the $SFR_{\text{FUV}}$ and $SFR_{\text{H}\alpha}$ to be approximately equal.
+As shown in the data from [@karachentsevSTARFORMATIONPROPERTIES2013] and supported by [@kroupaConstraintsStarFormation2020], a suitable approach for estimating the total SFR from FUV and H$\alpha$ observations is to calculate their average:
 
-A more robust estimate of total SFR is:
+$$
+SFR_{\text{FUV},H\alpha} = \text{mean}(SFR_{\text{FUV}}, SFR_{\text{H}\alpha}) 
+$$ {#eq-SFR_comb}
 
-where $L_{\text{FUV}}$ is uncorrected for absorption.
+where $L_{\text{FUV}}$ and $L_{\text{H}\alpha}$ are corrected for dust attenuation.
+
+![Plot showing the linear relation $\log_{10}\text{SFR}_{FUV} = \log_{10}\text{SFR}_{H\alpha}$, as well as their distrubutions](figure/log_SFR_FUV_Ha.png){fig-align="center" width="500"}
+
+According to [@madau2014], this method often underestimates the SFR, since different galaxy populations may systematically follow distinct absorption mechanisms depending on their characteristics.
+
+Since $SFR_{\text{FUV}}$, based on the uncorrected $L_{FUV}$, represents the emission from unobstructed stellar populations, and $SFR_{TIR}$ isaccounts for dust-reprocessed light, a more accurate way to calculate the total SFR of a galaxy is:
+
+$$
+SFR_{\text{total}} = \mathcal{K}_{\text{FUV}} \cdot L_{\text{FUV}} + \mathcal{K}_{\text{IR}} \cdot L_{\text{IR}}
+$$ {#eq-SFR_tot_madau}
+
+Following the same reasoning as the previous formula, the total SFR can be expressed as:
+
+$$
+SFR_{\text{total}} = \text{mean}\left(\mathcal{K}_{\text{FUV}} \cdot L_{\text{FUV}}, \mathcal{K}_{\text{H}\alpha} \cdot L_{\text{H}\alpha}\right) + \mathcal{K}_{\text{IR}} \cdot L_{\text{IR}} \\
+= SFR_{\text{FUV},H\alpha}+ SFR_{\text{IR}}
+$$
+
+where $L_{\text{FUV}}$ and $L_{\text{H}\alpha}$ are not corrected for dust absorption.
+However, since we do not have enough galaxies with both traces, we will use a different method of calculating the total SFR, which we will discuss later.
 
@@
 
-1. **Exponential Decline (τ Model)**:
+-   **Exponential Decline (Tau Model):** The star formation rate (SFR) decreases exponentially over time, following the equation:
 
-   where $\tau$ is the timescale and $t_{\text{sf}} = t - T_0$ is the star formation time.
+$$
+  \text{SFR}(t) \propto e^{-t_{\text{sf}}/\tau}
+$$
 
-2. **Delayed Exponential (τ Model)**:
+where $\tau$ is the timescale, $t_{\text{sf}} = t - T_0$ is the star formation time, $t$ is the age of the Universe, and $T_0$ is the time when star formation began.
 
-   accounting for an initial rise in SFR before declining. Here, $\tau$ is the time to reach maximum SFR.
+-   **Delayed Exponential (Delayed Tau Model):** This model provides a more complex representation where the SFR initially increases, reaches a peak, and then declines exponentially over time.
+The equation for this model is:
 
-3. **Log-Normal Model**:
+$$
+  \text{SFR}(t) \propto t_{\text{sf}} e^{-t_{\text{sf}}/\tau}
+$$
 
-   with $\tau$ and $T_0$ as free parameters.
+This accounts for an initial growth phase followed by a decline. In this case, $\tau$ represents the time it takes for the galaxy to reach $\text{SFR}_{\text{max}}$.
 
-4. **Double Power Law**:
+-   **Log-Normal Distribution Model:** The SFR follows a normalized log-normal distribution, which can accurately model the star formation rate density ($\text{SFRD} = \text{SFR}/M_*$) in individual galaxies.
+The general form of the equation is:
 
-   where $\tau$ is the timescale, and $\alpha$, $\beta$ govern the SFR rise and fall.
+$$
+  \text{SFR}(t) \propto \frac{1}{\tau} \exp\left(-\frac{(\ln(t) - T_0)^2}{2\tau^2}\right)
+$$
 
-Non-parametric models are also available, providing flexibility for galaxies with complex SFH patterns.
+where $\tau$ and $T_0$ are free parameters of the distribution that lack physical significance, as the SFR does not necessarily peak at $t = e^{T_0}$.
+
+-   **Double Power Law:** This model describes a scenario where the SFR rises and then falls sharply, useful for modeling galaxies experiencing rapid changes in star formation. The equation is:
+
+$$
+  \text{SFR}(t) \propto \left[\left(\frac{t}{\tau}\right)^\alpha + \left(\frac{t}{\tau}\right)^\beta\right]^{-1}
+$$
+
+where $\tau$ is the timescale and $\alpha$, $\beta$ are exponents that govern the rise and fall of the SFR.
+
+```{bash}
+gnuplot -e "
+set terminal svg;
+set output 'figure/combined_models.svg';
+set xlabel 'Time (t)';
+set ylabel 'SFR(t)';
+set title 'Star Formation Rate Models';
+set grid;
+plot exp(-x/8) title 'Exponential Decline (tau=2)' with lines lw 2, \
+     x*exp(-x/2) title 'Delayed Exponential (tau=2)' with lines lw 2, \
+     (1/1)*exp(-((log(x)-2)**2)/(2*1**2)) title 'Log-Normal (tau=1, T0=2)' with lines lw 2, \
+     1 / ((x/2)**2 + (x/2)**3) title 'Double Power Law (alpha=2, beta=3)' with lines lw 2;
+"
+```
+
+```{r}
+#| fig.cap="Star Formation Rate over the time of star formation, for different parametric models"
+library(ggplot2)
+library(dplyr)
+
+# Define time values (positive times)
+t <- seq(0.1, 30, length.out = 300)
+
+# Define SFR models
+exponential_decline <- function(t, tau) exp(-t / tau)
+delayed_exponential <- function(t, tau) t * exp(-t / tau)
+log_normal <- function(t, tau, T0) (1 / tau) * exp(-((log(t) - log(T0))^2) / (2 * tau^2))
+double_power_law <- function(t, tau, alpha, beta) 1 / ((t / tau)^alpha + (t / tau)^(-beta))
+
+# Generate data for each model
+data <- data.frame(
+  t = rep(t, 4),
+  SFR = c(
+    exponential_decline(t, tau = 2),
+    delayed_exponential(t, tau = 2),
+    log_normal(t, tau = 2, T0 = 12),
+    double_power_law(t, tau = 2, alpha = 2, beta = 8)
+  ),
+  Model = rep(c("Exponential Decline", "Delayed Exponential", "Log-Normal", "Double Power Law"), each = length(t))
+)
+
+# Plot all models
+ggplot(data, aes(x = t, y = SFR, color = Model)) +
+  geom_line(size = 1) +
+  labs(
+    title = "Star Formation Rate Models",
+    x = expression("Star Formation time (" * t[sf] * ") [Gyr]"),
+    y = expression("SFR(" * t[sf] * ") ["* M['☉']/yr *"]" ),
+    color = "Model"
+  ) +
+  scale_x_continuous(limits = c(0, 30)) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5))
+
+```
+
+Additionally, there are non-parametric models, which do not follow a specific functional form to describe the star formation of a galaxy.
+These models are more flexible in adapting to galaxies with more complex star formation patterns.
 
@@
 
-# Hubble Law
+# Lilly-Madau Plot
 
-## Redshift 
-## Lookback time
+The Lilly-Madau plot is one of the most important plots in the field of galaxy evolution. It describes how the SFRD of the universe evolved over time, with observational data. to figure out
+
+## Redshift and lookback time
+
+According to Hubble–Lemaître law, all the galaxies are moving away from each other, at a speed proportional to their distance, due to the expansion of the universe.
+
+$V = H_0\times d$, where $H_0 \approx 69.8 \text{ km/s/Mpc}$ is the Hubble constant and $d$ is the distance between the two galaxies.[^3]
+
+[^3]: We also have non-Hubble motions $V = H_0\times d + V_0$, where $V_0$ is the peculiar velocity and it could, for example, be due to galaxy cluster dynamics.
+For the current explanation we are going to ignore it.
+This way the radial velocity $v$ is equal to $V$
+
+Since we have galaxies with relative motions emitting light waves, we can observe the Doppler effect.
+Specifically, since the galaxies are moving away from each other, and thus from us also, we observe radiation with longer wavelenghts.
+
+*Redshift* ($z$) is the doppler shift resulting from radial motion:
+
+$$
+z = \frac{\lambda_{observed}}{\lambda_{emitted}}-1
+$$
+
+In special relativity, $z$ is related to radial velocity $v$ by [@hoggDistanceMeasuresCosmology2000]
+
+$$
+1+z = \sqrt{\frac{1+v/c}{1-v/c}}
+$$ {#eq-z-rel} For small $v/c$ we can rewrite @eq-z-rel, as:
+
+$$
+z \approx \frac{V}{c} = \frac{H_0\times d}{c}
+$$
+
+But, because light takes time to cover the distance $d$ between two galaxies, when the light finally reaches as, we will see the observed galaxy, as it was when the light was emitted, and not how it is at this moment.
+If we substitute time that it took the light to reach us over the distance, then we arrive at the relation [@longairGalaxyFormation1998]:
+
+$$
+t_\text{emitted} \propto z^{-3/2}
+$$
+
+*The lookback time* is the difference between the current age of the Universe and the age of the Universe when the light was emitted
+
+$$
+t_L = T_0-t_\text{emitted}
+$$
 
@@
 ## Newton-Raphson
+
 ## Markov Chain Monte Carlo
@@
 ## Catalog Completeness
+
 ## Comparing the Catalogs
+
 ## The "special" case of the Star Formation Rates
@@
 ## According to pre-existing bibliography
+
 ### Problems with the method

### 2024-12-26 thesis.tex
SFR translation and hubble

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
]{article}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
    \setmainfont[]{Latin Modern Roman}
  \setmathfont[]{Latin Modern Math}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={thesis},
  pdfauthor={Dimitris Papachristopoulos},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\newcommand{\runninghead}{A Preprint }
\title{thesis}
\def\asep{\\\\\\ } % default: all authors on same column
\author{\textbf{Dimitris Papachristopoulos}\\}
\date{}
\begin{document}
\maketitle

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{3}
\tableofcontents
}

\newpage{}

\section{Abstract}\label{abstract}

The Star Formation History (SFH) of a galaxy can offer many insights not
only for the evolution and the future of the galaxy, but also for the
evolution of the Universe. This is why there are various theoretical
models trying to describe the SFH of galaxies. One of those models is
the Delayed-Tau model, which approximates the Star Formation Rates (SFR)
of galaxies as a function with a rising SFR at the beginning, until it
reaches a peak at a time \(\tau\), unique for each galaxy, and then it
drops at an exponential rate.

Haslbauer, Kroupa, and Jerabkova (2023a) argues that the
Delayed-\(\tau\) model is opposed to the Lilly-Madau plot ((Madau and
Dickinson 2014)), which plots the observed SFR's of galaxies with the
corresponding redshifts (\(z\)) and calculates a cosmic SFR peak at
\(z\approx 2\). The way they calculated this inconsistency is by using
observatory data for SFR and Stellar Masses \footnote{They calculated
  the Stellar Masses by using a Mass to Light ratio of 0.6} from the
UNGC catalog (Karachentsev, Makarov, and Kaisina (2013), Karachentsev
and Kaisina (2013)) for calculating the parameters (the timescale
\(\tau\) and the normalization constant \(A_{del}\)) of the model. This
calculation for the galaxies of the Local Cosmological Volume (LCV),
allows the investigation of the SFR throughout the life each galaxy and
so we can find the expected time of peak of the SFR.

In this thesis project, we will try to calculate the same parameters, by
using a bigger sample size and the method Markov Chain Monte Carlo, to
examine if the inconsistencies of the model derive from the results of
the previous analysis, or if it is an intrinsic problem of the model

\textbf{Keywords:} Galaxies, Galaxy Evolution, Star Formation History
(SFH), Star Formation Rate (SFR), Delayed-\(\tau\), Local Cosmological
Volume, Lilly-Madau Plot, Redshift, Markov Chain Monte Carlo (MCMC).

\newpage{}

\section{Galaxy Morphology and Star-Forming
Regions}\label{galaxy-morphology-and-star-forming-regions}

\subsection{Galaxy Classification}\label{galaxy-classification}

\subsubsection{Hubble-de Vaucouleurs
Classification}\label{hubble-de-vaucouleurs-classification}

\subsubsection{Dwarf Galaxies}\label{dwarf-galaxies}

\subsection{Star-Forming Regions}\label{star-forming-regions}

\section{Star Formation History (SFH)}\label{star-formation-history-sfh}

The SFH of a galaxy describes the evolution of its star formation rate
over time. By selecting an appropriate model for SFH, we can analyze
stellar production, predict periods of active or quiescent star
formation, and determine when SFR stabilizes.

Understanding SFH models is crucial for interpreting internal and
external processes affecting galaxies and identifying conditions for
intense star formation in their early stages.

\subsection{Star Formation Rate}\label{star-formation-rate}

The star formation rate (SFR) is defined as the total gas mass of a
galaxy converted into stars over a specific time interval. It is
typically expressed in solar masses per year
(\(M_\odot \cdot \text{yr}^{-1}\)).

The SFR varies significantly over time, and its integration over time
provides the total stellar mass formed during the galaxy's history of
star formation. Specifically:

\begin{equation}\phantomsection\label{eq-sfr_int}{
\int_0^{t_{sf}} \text{SFR}(t)dt = \zeta M_*(t_{sf}),\ t_{sf}=\text{Time of Star Formation,} 
}\end{equation}

where \(\zeta\) accounts for mass loss during the Star Formation and is
approximately \(\zeta \approx 1.3\) (Kroupa et al. (2020)).

\subsubsection{Estimating SFR from
Spectra}\label{estimating-sfr-from-spectra}

SFR can be estimated using various photometric or spectroscopic methods
based on the luminosity of at least one spectral band or the intensity
of a spectral line. Different luminosities and intensities trace
distinct emission mechanisms, offering insights into a galaxy's
radiation sources. Below are common methods:

\footnote{\begin{itemize}
  \tightlist
  \item
    (Calzetti 2012), ({``{ASTR620 Galaxies} - {Fall} 2017''} n.d.)
  \end{itemize}}

\begin{itemize}
\item
  \textbf{Hα} \boldmath\(\alpha\) \textbf{Emission}: Young, hot, massive
  stars (O-type stars, \textasciitilde10 Myr, \textasciitilde20
  \(M_\odot\)) produce a number of ionizing photons, which they ionize
  the surrounding hydrogen rich gas. The hydorgen undergoes
  recombination cascades which produce Balmer emission lines of
  \(H\alpha\) (0.6563 \(\mu m\)) and \(H\beta\) (0.4861 \(\mu m\)). Dust
  can significantly affect observations.
\item
  \textbf{Far-Ultraviolet (FUV) Flux}: Mainly emitted by young, hot
  stars ( B-type stars, \textasciitilde100 Myr). Dust presence can also
  significantly affect observations.
\item
  \textbf{Infrared (IR) Flux}: The stars in a galaxy can heat up the
  dust in different ways, which then emits radiation in different parts
  of the IR spectrum. For example, young and massive, short-lived stars,
  emit UV radiation which then the heated dust emits in a wavelength of
  \(\approx 60 \mu m\), whereas dust heated by UV-faint old or low-mass
  stars will emit at \(\approx 100-150\mu m\). As a result, the total IR
  emission is age-agnostic and provides a more accurate approximation of
  the SFR because it accounts for contributions from both young and old
  stellar populations.
\item
  \textbf{Radio Continuum Emission}: Strongly correlated with IR. Its
  origin is complex, involving synchrotron radiation from relativistic
  electrons and thermal Bremsstrahlung from hot gas.
\item
  \textbf{X-Ray Emission}: In star-forming galaxies, X-rays arise from
  high-mass binary systems (neutron star or black hole with massive
  stellar companion) and hot gas from supernovae, correlating with SFR
  up to redshift \(z \sim 4\). X-rays are dust-insensitive, enabling
  accurate high-redshift observations.
\end{itemize}

SFR for different luminosities \(L_i\) can be calculated as:

\begin{equation}\phantomsection\label{eq-sfr-spectra}{
\text{SFR}_i = \mathcal{K}_i\times L_i
}\end{equation}

where \(\mathcal{K}_i\) is a constant specific to each \(L_i\) (\(i =\)
H\(\alpha\), IR, radio, FUV, X). In our analysis, we lack radio and
X-ray data.

Since the luminosities \(L_{\text{FUV}}\) and \(L_{\text{H}\alpha}\)
originate from young stars and are highly sensitive to dust, we either
directly observe stars unaffected by dust or use correction models to
account for dust absorption. It is crucial to ensure that these models
neither underestimate nor overestimate the luminosities by overlooking
or double-counting the same sources.

Additionally, because these luminosities are emitted by similar stellar
populations, we can reasonably expect the \(SFR_{\text{FUV}}\) and
\(SFR_{\text{H}\alpha}\) to be approximately equal. As shown in the data
from (Karachentsev and Kaisina 2013) and supported by (Kroupa et al.
2020), a suitable approach for estimating the total SFR from FUV and
H\(\alpha\) observations is to calculate their average:

\begin{equation}\phantomsection\label{eq-SFR_comb}{
SFR_{\text{FUV},H\alpha} = \text{mean}(SFR_{\text{FUV}}, SFR_{\text{H}\alpha}) 
}\end{equation}

where \(L_{\text{FUV}}\) and \(L_{\text{H}\alpha}\) are corrected for
dust attenuation.

\begin{figure}[H]

{\centering \includegraphics[width=5.20833in,height=\textheight]{figure/log_SFR_FUV_Ha.png}

}

\caption{Plot showing the linear relation
\(\log_{10}\text{SFR}_{FUV} = \log_{10}\text{SFR}_{H\alpha}\), as well
as their distrubutions}

\end{figure}%

According to (Madau and Dickinson 2014), this method often
underestimates the SFR, since different galaxy populations may
systematically follow distinct absorption mechanisms depending on their
characteristics.

Since \(SFR_{\text{FUV}}\), based on the uncorrected \(L_{FUV}\),
represents the emission from unobstructed stellar populations, and
\(SFR_{TIR}\) isaccounts for dust-reprocessed light, a more accurate way
to calculate the total SFR of a galaxy is:

\begin{equation}\phantomsection\label{eq-SFR_tot_madau}{
SFR_{\text{total}} = \mathcal{K}_{\text{FUV}} \cdot L_{\text{FUV}} + \mathcal{K}_{\text{IR}} \cdot L_{\text{IR}}
}\end{equation}

Following the same reasoning as the previous formula, the total SFR can
be expressed as:

\[
SFR_{\text{total}} = \text{mean}\left(\mathcal{K}_{\text{FUV}} \cdot L_{\text{FUV}}, \mathcal{K}_{\text{H}\alpha} \cdot L_{\text{H}\alpha}\right) + \mathcal{K}_{\text{IR}} \cdot L_{\text{IR}} \\
= SFR_{\text{FUV},H\alpha}+ SFR_{\text{IR}}
\]

where \(L_{\text{FUV}}\) and \(L_{\text{H}\alpha}\) are not corrected
for dust absorption. However, since we do not have enough galaxies with
both traces, we will use a different method of calculating the total
SFR, which we will discuss later.

\subsection{Main Sequence Galaxies}\label{main-sequence-galaxies}

The SFR and stellar mass of a galaxy are tightly correlated by the
relationship:

\[
\log(\text{SFR}) = \alpha \log(M_*)+\beta
\]

where \(\alpha(t)\) and \(\beta(t)\) depend on time and redshift \(z\)
(Speagle et al. (2014)):

\subsubsection{Star Formation History
Models}\label{star-formation-history-models}

Parameterized SFH models are commonly used, offering simplicity through
a few parameters (Carnall et al. (2019)):

\begin{itemize}
\tightlist
\item
  \textbf{Exponential Decline (Tau Model):} The star formation rate
  (SFR) decreases exponentially over time, following the equation:
\end{itemize}

\[
  \text{SFR}(t) \propto e^{-t_{\text{sf}}/\tau}
\]

where \(\tau\) is the timescale, \(t_{\text{sf}} = t - T_0\) is the star
formation time, \(t\) is the age of the Universe, and \(T_0\) is the
time when star formation began.

\begin{itemize}
\tightlist
\item
  \textbf{Delayed Exponential (Delayed Tau Model):} This model provides
  a more complex representation where the SFR initially increases,
  reaches a peak, and then declines exponentially over time. The
  equation for this model is:
\end{itemize}

\[
  \text{SFR}(t) \propto t_{\text{sf}} e^{-t_{\text{sf}}/\tau}
\]

This accounts for an initial growth phase followed by a decline. In this
case, \(\tau\) represents the time it takes for the galaxy to reach
\(\text{SFR}_{\text{max}}\).

\begin{itemize}
\tightlist
\item
  \textbf{Log-Normal Distribution Model:} The SFR follows a normalized
  log-normal distribution, which can accurately model the star formation
  rate density (\(\text{SFRD} = \text{SFR}/M_*\)) in individual
  galaxies. The general form of the equation is:
\end{itemize}

\[
  \text{SFR}(t) \propto \frac{1}{\tau} \exp\left(-\frac{(\ln(t) - T_0)^2}{2\tau^2}\right)
\]

where \(\tau\) and \(T_0\) are free parameters of the distribution that
lack physical significance, as the SFR does not necessarily peak at
\(t = e^{T_0}\).

\begin{itemize}
\tightlist
\item
  \textbf{Double Power Law:} This model describes a scenario where the
  SFR rises and then falls sharply, useful for modeling galaxies
  experiencing rapid changes in star formation. The equation is:
\end{itemize}

\[
  \text{SFR}(t) \propto \left[\left(\frac{t}{\tau}\right)^\alpha + \left(\frac{t}{\tau}\right)^\beta\right]^{-1}
\]

where \(\tau\) is the timescale and \(\alpha\), \(\beta\) are exponents
that govern the rise and fall of the SFR.

\begin{figure}[H]

{\centering \includegraphics{thesis_files/figure-pdf/unnamed-chunk-2-1.pdf}

}

\caption{Star Formation Rate over the time of star formation, for
different parametric models}

\end{figure}%

Additionally, there are non-parametric models, which do not follow a
specific functional form to describe the star formation of a galaxy.
These models are more flexible in adapting to galaxies with more complex
star formation patterns.

\subsection{\texorpdfstring{Delayed-\(τ\)
Model}{Delayed-τ Model}}\label{delayed-ux3c4-model}

The delayed \(τ\) model is widely used for describing an initial
starburst followed by a gradual decline in SFR. This places galaxies on
the main sequence. It is particularly effective for massive galaxies
(Haslbauer, Kroupa, and Jerabkova (2023b)). However, it assumes smooth
SFR evolution and may overestimate peak SFR in high-redshift galaxies.

Using the delayed τ model, we compute \(\tau\), \(t_{\text{sf}}\), and
normalization constant \(A_{\text{del}}\) with:

\begin{equation}\phantomsection\label{eq-delayed-current}{
\text{SFR}_0 = \text{SFR}(t_{sf}) = A_{del}\frac{t_{sf}}{\tau^2}e^{-t_{sf}/\tau}
}\end{equation}

where \(\text{SFR}_0\) is given in the catalogs.

\section{Lilly-Madau Plot}\label{lilly-madau-plot}

The Lilly-Madau plot is one of the most important plots in the field of
galaxy evolution. It describes how the SFRD of the universe evolved over
time, with observational data. to figure out

\subsection{Redshift and lookback
time}\label{redshift-and-lookback-time}

According to Hubble--Lemaître law, all the galaxies are moving away from
each other, at a speed proportional to their distance, due to the
expansion of the universe.

\(V = H_0\times d\), where \(H_0 \approx 69.8 \text{ km/s/Mpc}\) is the
Hubble constant and \(d\) is the distance between the two
galaxies.\footnote{We also have non-Hubble motions
  \(V = H_0\times d + V_0\), where \(V_0\) is the peculiar velocity and
  it could, for example, be due to galaxy cluster dynamics. For the
  current explanation we are going to ignore it. This way the radial
  velocity \(v\) is equal to \(V\)}

Since we have galaxies with relative motions emitting light waves, we
can observe the Doppler effect. Specifically, since the galaxies are
moving away from each other, and thus from us also, we observe radiation
with longer wavelenghts.

\emph{Redshift} (\(z\)) is the doppler shift resulting from radial
motion:

\[
z = \frac{\lambda_{observed}}{\lambda_{emitted}}-1
\]

In special relativity, \(z\) is related to radial velocity \(v\) by
(Hogg, n.d.)

\begin{equation}\phantomsection\label{eq-z-rel}{
1+z = \sqrt{\frac{1+v/c}{1-v/c}}
}\end{equation} For small \(v/c\) we can rewrite
Equation~\ref{eq-z-rel}, as:

\[
z \approx \frac{V}{c} = \frac{H_0\times d}{c}
\]

But, because light takes time to cover the distance \(d\) between two
galaxies, when the light finally reaches as, we will see the observed
galaxy, as it was when the light was emitted, and not how it is at this
moment. If we substitute time that it took the light to reach us over
the distance, then we arrive at the relation (Longair 1998):

\[
t_\text{emitted} \propto z^{-3/2}
\]

\emph{The lookback time} is the difference between the current age of
the Universe and the age of the Universe when the light was emitted

\[
t_L = T_0-t_\text{emitted}
\]

\section{Lilly-Madau Plot}\label{lilly-madau-plot-1}

\section{\texorpdfstring{Delayed-\(\tau\)
model}{Delayed-\textbackslash tau model}}\label{delayed-tau-model}

\section{Computational Methods}\label{computational-methods}

\subsection{Newton-Raphson}\label{newton-raphson}

\subsection{Markov Chain Monte Carlo}\label{markov-chain-monte-carlo}

\section{Prepering the Catalogs}\label{prepering-the-catalogs}

UNGC HECATE join etc\ldots{}

\subsection{Catalog Completeness}\label{catalog-completeness}

\subsection{Comparing the Catalogs}\label{comparing-the-catalogs}

\subsection{The ``special'' case of the Star Formation
Rates}\label{the-special-case-of-the-star-formation-rates}

\section{Calculating the parameters}\label{calculating-the-parameters}

\subsection{According to pre-existing
bibliography}\label{according-to-pre-existing-bibliography}

\subsubsection{Problems with the method}\label{problems-with-the-method}

\subsection*{MCMC}\label{mcmc}
\addcontentsline{toc}{subsection}{MCMC}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-ASTR620GalaxiesFall}
{``{ASTR620 Galaxies} - {Fall} 2017.''} n.d. Accessed October 27, 2024.
\url{https://www.astro.umd.edu/~richard/ASTRO620/index_fall2017.html}.

\bibitem[\citeproctext]{ref-calzettiStarFormationRate2012}
Calzetti, Daniela. 2012. {``Star {Formation Rate Indicators}.''} August
15, 2012. \url{http://arxiv.org/abs/1208.2997}.

\bibitem[\citeproctext]{ref-carnallHowMeasureGalaxy2019a}
Carnall, Adam C., Joel Leja, Benjamin D. Johnson, Ross J. McLure, James
S. Dunlop, and Charlie Conroy. 2019. {``How to {Measure Galaxy Star
Formation Histories}. {I}. {Parametric Models}.''} \emph{The
Astrophysical Journal} 873 (1): 44.
\url{https://doi.org/10.3847/1538-4357/ab04a2}.

\bibitem[\citeproctext]{ref-haslbauerCosmologicalStarFormation2023}
Haslbauer, Moritz, Pavel Kroupa, and Tereza Jerabkova. 2023b. {``The
Cosmological Star Formation History from the {Local Cosmological Volume}
of Galaxies and Constraints on the Matter Homogeneity.''} \emph{Monthly
Notices of the Royal Astronomical Society} 524 (3): 3252--62.
\url{https://doi.org/10.1093/mnras/stad1986}.

\bibitem[\citeproctext]{ref-haslbauer2023}
---------. 2023a. {``The Cosmological Star Formation History from the
Local Cosmological Volume of Galaxies and Constraints on the Matter
Homogeneity.''} \emph{Monthly Notices of the Royal Astronomical Society}
524 (3): 3252--62. \url{https://doi.org/10.1093/mnras/stad1986}.

\bibitem[\citeproctext]{ref-hoggDistanceMeasuresCosmology2000}
Hogg, David W. n.d. {``Distance Measures in Cosmology.''}
\url{https://doi.org/10.48550/arXiv.astro-ph/9905116}.

\bibitem[\citeproctext]{ref-karachentsevSTARFORMATIONPROPERTIES2013}
Karachentsev, Igor D., and Elena I. Kaisina. 2013. {``{STAR FORMATION
PROPERTIES IN THE LOCAL VOLUME GALAXIES VIA Hα AND FAR-ULTRAVIOLET
FLUXES}.''} \emph{The Astronomical Journal} 146 (3): 46.
\url{https://doi.org/10.1088/0004-6256/146/3/46}.

\bibitem[\citeproctext]{ref-karachentsev2013}
Karachentsev, Igor D., Dmitry I. Makarov, and Elena I. Kaisina. 2013.
{``UPDATED NEARBY GALAXY CATALOG.''} \emph{The Astronomical Journal} 145
(4): 101. \url{https://doi.org/10.1088/0004-6256/145/4/101}.

\bibitem[\citeproctext]{ref-kroupaConstraintsStarFormation2020}
Kroupa, P, M Haslbauer, I Banik, S T Nagesh, and J Pflamm-Altenburg.
2020. {``Constraints on the Star Formation Histories of Galaxies in the
{Local Cosmological Volume}.''} \emph{Monthly Notices of the Royal
Astronomical Society} 497 (1): 37--43.
\url{https://doi.org/10.1093/mnras/staa1851}.

\bibitem[\citeproctext]{ref-longairGalaxyFormation1998}
Longair, Malcolm S. 1998. \emph{Galaxy Formation}. Springer Science \&
Business Media.

\bibitem[\citeproctext]{ref-madau2014}
Madau, Piero, and Mark Dickinson. 2014. {``Cosmic Star Formation
History.''} \emph{Annual Review of Astronomy and Astrophysics} 52 (1):
415--86. \url{https://doi.org/10.1146/annurev-astro-081811-125615}.

\bibitem[\citeproctext]{ref-speagleHighlyConsistentFramework2014}
Speagle, Joshua S., Charles L. Steinhardt, Peter L. Capak, and John D.
Silverman. 2014. {``A {Highly Consistent Framework} for the {Evolution}
of the {Star-Forming} "{Main Sequence}" from z\textasciitilde0-6.''}
\emph{The Astrophysical Journal Supplement Series} 214 (2): 15.
\url{https://doi.org/10.1088/0067-0049/214/2/15}.

\end{CSLReferences}

\end{document}

### 2025-01-02 thesis.qmd
morphology thesis

@@
     keep-tex: true    
+    link-citations: true
+    link-bibliography: true
 toc: true
@@
 
-@haslbauer2023 argues that the Delayed-$\tau$ model is opposed to the Lilly-Madau plot ([@madau2014]), which plots the observed SFR's of galaxies with the corresponding redshifts ($z$) and calculates a cosmic SFR peak at $z\approx 2$.
-The way they calculated this inconsistency is by using observatory data for SFR and Stellar Masses [^1] from the UNGC catalog (@karachentsev2013, @karachentsevSTARFORMATIONPROPERTIES2013) for calculating the parameters (the timescale $\tau$ and the normalization constant $A_{del}$) of the model.
+@haslbauerCosmologicalStarFormation2023 argue that the Delayed-$\tau$ model is opposed to the Lilly-Madau plot ([@madauCosmicStarFormation2014]), which plots the observed SFR's of galaxies with the corresponding redshifts ($z$) and calculates a cosmic SFR peak at $z\approx 2$.
+The way they calculated this inconsistency is by using observatory data for SFR and Stellar Masses [^1] from the UNGC catalog (@karachentsevUPDATEDNEARBYGALAXY2013, @karachentsevSTARFORMATIONPROPERTIES2013) for calculating the parameters (the timescale $\tau$ and the normalization constant $A_{del}$) of the model.
 This calculation for the galaxies of the Local Cosmological Volume (LCV), allows the investigation of the SFR throughout the life each galaxy and so we can find the expected time of peak of the SFR.
@@
 
+This thesis will focus on how a specific parametric model tries to explain the Star-Formation Histories of galaxies, but to do that, we first need to understand what a galaxy is, what it is made of, the mechanisms of its evolution, and how we can distinguish them.
+
+The study of galaxies is a very active field of astronomy since it is a relatively young discipline.
+Until 1920, astronomers who observed spiral nebulae were not certain what they were.
+In 1921, two papers were published: one argued that the Milky Way constituted the whole Universe and that the spiral nebulae were part of it, while the second argued that each spiral nebula was, in fact, a distinct "island universe" [@shapleyScaleUniverse1921].
+This debate became known as the Great Debate[^2].
+
+[^2]: @hoskinGreatDebateWhat1976
+
+In 1925, Edwin Hubble put an end to the debate by showing that the distances to the spiral nebulae were far too great compared to other objects within the Milky Way.
+The method he used involved observing Cepheid variable stars in these nebulae.
+By applying the period-luminosity relationship, which had been discovered by Henrietta Swan Leavitt [@leavitt1777VariablesMagellanic1907], Hubble was able to determine their distances.
+This groundbreaking discovery confirmed that spiral nebulae were indeed separate galaxies, marking the beginning of extragalactic astronomy and revolutionizing our understanding of the Universe.
+
+Today we know that galaxies are large-scale structures containing, Stars, gas and dust, Stellar and planetary systems and Stellar remnants (white dwarves, neutron stars and black holes).
+Those structures are held together by their gravity, having Stellar Masses more than $\sim 10^5\ M_\odot$, and an average diameter of $\sim 4\ \text{kpc}$.
+They are extremely diverse systems, and each galaxy differs in mass, size, brightness, stellar populations and morphology.
+This is exactly why we have created systems to classify them.
+
 ## Galaxy Classification
 
-### Hubble-de Vaucouleurs Classification
+The most common method of classification is the *Hubble-de Vacouleur* classification, which categorizes galaxies based on their morphology.
+
+-   **Elliptical Galaxies (E):** Ellipsoidal shapes with smooth brightness profiles, containing older stars and minimal interstellar matter.
+Their eccentricity takes values from 0 to 0.7, so we can categorize them even further, form E0 to E7
+
+-   **Lenticular Galaxies (S0):** Intermediate between elliptical and spiral galaxies,
+
+-   **Spiral Galaxies:** Characterized by a central bulge and spiral arms.
+Depending on the arm tightness we can categorize them as *a,b,c,d* from tight to looser, and depending if they have a bar or not they are subdivided into:
+
+    -   **Unbarred Spirals (S):** No central bar; classified as Sa, Sb, Sc, etc., based on arm tightness and bulge size.
+
+    -   **Barred Spirals (SB):** Feature a central bar; denoted as SBa, SBb, SBc, etc.
+
+-   **Irregular Galaxies (Irr):** Lack regular structure, often rich in gas and dust with high star formation rates.
+
+Intermediate galaxies between ellipticals and spirals are called **Lenticular galaxies (S0-SB0)**, featuring a central bulge and disk but lacking significant spiral structure.
+
+[![Tuning-fork-style diagram of the Hubble sequenceBy Cosmogoblin - Own work, CC0, https://commons.wikimedia.org/w/index.php?curid=121743256](figure/1311px-Hubble_Tuning_Fork_diagram.svg.png){fig-align="center" width="400"}](https://commons.wikimedia.org/w/index.php?curid=121743256)
+
+| **Hubble** | E | E-S0 | S0 | S0/a | Sa | Sa-b | Sb | Sb-c | Sc | Sc-Irr | Irr |
+|:----:|:----:|:----:|:----:|:----:|:----:|:----:|:----:|:----:|:----:|:----:|:----:|
+| **T** | -5 | \[-4,-3\] | \[-2,-1\] | 0 | 1 | 2 | 3 | 4 | \[5,6,7\] | 8 | \[9,10,11\] |
+
+: This table was based on the \LaTeX files of [@RC3ThirdReference]
 
@@
 Different luminosities and intensities trace distinct emission mechanisms, offering insights into a galaxy’s radiation sources.
-Below are common methods:
+Below are common methods:[^3]
 
-[^2]
-
-[^2]:
-    -   [@calzettiStarFormationRate2012], [@ASTR620GalaxiesFall]
+[^3]: @calzettiStarFormationRate2012, @mushotzkyASTR620GalaxiesFall2017
 
@@
 
-According to [@madau2014], this method often underestimates the SFR, since different galaxy populations may systematically follow distinct absorption mechanisms depending on their characteristics.
+According to [@madauCosmicStarFormation2014], this method often underestimates the SFR, since different galaxy populations may systematically follow distinct absorption mechanisms depending on their characteristics.
 
@@
 
-Parameterized SFH models are commonly used, offering simplicity through a few parameters (@carnallHowMeasureGalaxy2019a):
+```{r}
+#| fig.cap="Star Formation Rate over the time of star formation, for different parametric models"
+library(ggplot2)
+library(dplyr)
+library(latex2exp)
+
+# Define time values (positive times)
+t <- seq(0.01, 12, length.out = 200)
+
+# Define SFR models
+exponential_decline <- function(t, tau) exp(-t / tau)
+delayed_exponential <- function(t, tau) t * exp(-t / tau)
+log_normal <- function(t, tau, T0) (1 / tau) * exp(-((log(t) - log(T0))^2) / (2 * tau^2))
+double_power_law <- function(t, tau, alpha, beta) 1 / ((t / tau)^alpha + (t / tau)^(-beta))
+
+# Generate data for each model
+data <- data.frame(
+  t = rep(t, 4),
+  SFR = c(
+    exponential_decline(t, tau = 2),
+    delayed_exponential(t, tau = 2),
+    log_normal(t, tau = 2, T0 = 10),
+    double_power_law(t, tau = 2, alpha = 2, beta = 5)
+  ),
+  Model = rep(c("\nExponential Decline\n(τ=2 Gyr)", "\nDelayed Exponential\n(τ=2 Gyr)", "\nLog-Normal\n(τ = 2 Gyr, To = 10 Gyr)", "\nDouble Power Law\n(τ = 2 Gyr, α = 2, β = 5)"), each = length(t))
+)
+
+# Plot all models
+ggplot(data, aes(x = t, y = SFR, color = Model)) +
+  geom_line(size = 1) +
+  labs(
+    title = "Star Formation Rate Models",
+    x = TeX("Star Formation time ( $t_{sf}$ ) [Gyr]"),
+    y = TeX("SFR($t_{sf}$) [ M$_*$/yr ]" ),
+    color = "Model"
+  ) +
+  scale_x_continuous(limits = c(0, 12)) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5))
+
+```
+
+Parameterized SFH models are commonly used, offering simplicity through a few parameters [@carnallHowMeasureGalaxy2019a]:
 
@@
 
-```{bash}
-gnuplot -e "
-set terminal svg;
-set output 'figure/combined_models.svg';
-set xlabel 'Time (t)';
-set ylabel 'SFR(t)';
-set title 'Star Formation Rate Models';
-set grid;
-plot exp(-x/8) title 'Exponential Decline (tau=2)' with lines lw 2, \
-     x*exp(-x/2) title 'Delayed Exponential (tau=2)' with lines lw 2, \
-     (1/1)*exp(-((log(x)-2)**2)/(2*1**2)) title 'Log-Normal (tau=1, T0=2)' with lines lw 2, \
-     1 / ((x/2)**2 + (x/2)**3) title 'Double Power Law (alpha=2, beta=3)' with lines lw 2;
-"
-```
-
-```{r}
-#| fig.cap="Star Formation Rate over the time of star formation, for different parametric models"
-library(ggplot2)
-library(dplyr)
-
-# Define time values (positive times)
-t <- seq(0.1, 30, length.out = 300)
-
-# Define SFR models
-exponential_decline <- function(t, tau) exp(-t / tau)
-delayed_exponential <- function(t, tau) t * exp(-t / tau)
-log_normal <- function(t, tau, T0) (1 / tau) * exp(-((log(t) - log(T0))^2) / (2 * tau^2))
-double_power_law <- function(t, tau, alpha, beta) 1 / ((t / tau)^alpha + (t / tau)^(-beta))
-
-# Generate data for each model
-data <- data.frame(
-  t = rep(t, 4),
-  SFR = c(
-    exponential_decline(t, tau = 2),
-    delayed_exponential(t, tau = 2),
-    log_normal(t, tau = 2, T0 = 12),
-    double_power_law(t, tau = 2, alpha = 2, beta = 8)
-  ),
-  Model = rep(c("Exponential Decline", "Delayed Exponential", "Log-Normal", "Double Power Law"), each = length(t))
-)
-
-# Plot all models
-ggplot(data, aes(x = t, y = SFR, color = Model)) +
-  geom_line(size = 1) +
-  labs(
-    title = "Star Formation Rate Models",
-    x = expression("Star Formation time (" * t[sf] * ") [Gyr]"),
-    y = expression("SFR(" * t[sf] * ") ["* M['☉']/yr *"]" ),
-    color = "Model"
-  ) +
-  scale_x_continuous(limits = c(0, 30)) +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-
 Additionally, there are non-parametric models, which do not follow a specific functional form to describe the star formation of a galaxy.
@@
 
-The Lilly-Madau plot is one of the most important plots in the field of galaxy evolution. It describes how the SFRD of the universe evolved over time, with observational data. to figure out
+The Lilly-Madau plot is one of the most important plots in the field of galaxy evolution.
+It describes how the SFRD of the universe evolved over time, with observational data.
+But to understand it, we first need to understand how the observed age of the Universe and the redshifts of galaxies are related.
 
@@
 
-$V = H_0\times d$, where $H_0 \approx 69.8 \text{ km/s/Mpc}$ is the Hubble constant and $d$ is the distance between the two galaxies.[^3]
+$V = H_0\times d$, where $H_0 \approx 69.8 \text{ km/s/Mpc}$ is the Hubble constant and $d$ is the distance between the two galaxies.[^4]
 
-[^3]: We also have non-Hubble motions $V = H_0\times d + V_0$, where $V_0$ is the peculiar velocity and it could, for example, be due to galaxy cluster dynamics.
+[^4]: We also have non-Hubble motions $V = H_0\times d + V_0$, where $V_0$ is the peculiar velocity and it could, for example, be due to galaxy cluster dynamics.
 For the current explanation we are going to ignore it.
@@
 
-# Lilly-Madau Plot
+## Lilly-Madau Plot
 

### 2025-01-11 .ipynb_checkpoints/thesis-checkpoint.qmd
1st chapter 1st edition

--- 2025-01-02 thesis.qmd
@@
 | **Hubble** | E | E-S0 | S0 | S0/a | Sa | Sa-b | Sb | Sb-c | Sc | Sc-Irr | Irr |
-|:----:|:----:|:----:|:----:|:----:|:----:|:----:|:----:|:----:|:----:|:----:|:----:|
+|:--:|:--:|:--:|:--:|:--:|:--:|:--:|:--:|:--:|:--:|:--:|:--:|
 | **T** | -5 | \[-4,-3\] | \[-2,-1\] | 0 | 1 | 2 | 3 | 4 | \[5,6,7\] | 8 | \[9,10,11\] |

### 2025-01-11 r_mcmc/_targets.R

@@ -79,11 +79,11 @@ list(
       id_numbers = sfr_data$id_number,
       M_star = sfr_data$logM_HEC
     ),
-    chains = 10,
+    chains = 4,
     parallel_chains = 8,
     iter_sampling = 5000,
     iter_warmup = 3500,
-    init = init_function(10,1132),
+    init = init_function(4,1132),
     
   ),
 

### 2025-01-15 thesis.qmd
Add thesis title

@@
 ---
-title: "thesis"
-author: "Dimitris Papachristopoulos"
+title: "Analysis of observational data, to calculate the Delayed-Tau model parameters"
+author: "Dimitrios Papachristopoulos"
 format: 
   pdf: default  
-  #logo: ./figure/
-  arxiv-pdf:
-    keep-tex: true    
-    link-citations: true
-    link-bibliography: true
+  # arxiv-pdf:
+  #    keep-tex: true    
+  #    link-citations: true
+  #    link-bibliography: true
+  #    runninghead: ""
 toc: true
 toc-depth: 3
-theme: minti
 bibliography: ./My_Library.bib
@@
 @haslbauerCosmologicalStarFormation2023 argue that the Delayed-$\tau$ model is opposed to the Lilly-Madau plot ([@madauCosmicStarFormation2014]), which plots the observed SFR's of galaxies with the corresponding redshifts ($z$) and calculates a cosmic SFR peak at $z\approx 2$.
-The way they calculated this inconsistency is by using observatory data for SFR and Stellar Masses [^1] from the UNGC catalog (@karachentsevUPDATEDNEARBYGALAXY2013, @karachentsevSTARFORMATIONPROPERTIES2013) for calculating the parameters (the timescale $\tau$ and the normalization constant $A_{del}$) of the model.
+The way they calculated this inconsistency is by using observatory data for SFR and Stellar Masses from the UNGC catalog (@karachentsevUPDATEDNEARBYGALAXY2013, @karachentsevSTARFORMATIONPROPERTIES2013) for calculating the parameters (the timescale $\tau$ and the normalization constant $A_{del}$) of the model.
 This calculation for the galaxies of the Local Cosmological Volume (LCV), allows the investigation of the SFR throughout the life each galaxy and so we can find the expected time of peak of the SFR.
-
-[^1]: They calculated the Stellar Masses by using a Mass to Light ratio of 0.6
 
@@
 In 1921, two papers were published: one argued that the Milky Way constituted the whole Universe and that the spiral nebulae were part of it, while the second argued that each spiral nebula was, in fact, a distinct "island universe" [@shapleyScaleUniverse1921].
-This debate became known as the Great Debate[^2].
+This debate became known as the Great Debate[^1].
 
-[^2]: @hoskinGreatDebateWhat1976
+[^1]: @hoskinGreatDebateWhat1976
 
@@
 
-The most common method of classification is the *Hubble-de Vacouleur* classification, which categorizes galaxies based on their morphology.
+One of the most common methods of classification is the *Hubble classification [@hubbleCepheidsSpiralNebulae1925]* , which categorizes galaxies based on their morphology.
 
@@
 
--   **Lenticular Galaxies (S0):** Intermediate between elliptical and spiral galaxies,
+-   **Lenticular Galaxies (S0):** Intermediate between elliptical and spiral galaxies, featuring a central bulge and disk but lacking significant spiral structure.
 
@@
 
-Intermediate galaxies between ellipticals and spirals are called **Lenticular galaxies (S0-SB0)**, featuring a central bulge and disk but lacking significant spiral structure.
+::: {#fig-morphology layout-ncol="2"}
+![Tuning-fork-style diagram of the Hubble sequence By Cosmogoblin - Own work, CC0, <https://commons.wikimedia.org/w/index.php?curid=121743256>](figure/1311px-Hubble_Tuning_Fork_diagram.svg.png){#fig-hubble}
 
-[![Tuning-fork-style diagram of the Hubble sequenceBy Cosmogoblin - Own work, CC0, https://commons.wikimedia.org/w/index.php?curid=121743256](figure/1311px-Hubble_Tuning_Fork_diagram.svg.png){fig-align="center" width="400"}](https://commons.wikimedia.org/w/index.php?curid=121743256)
+![Hubble-de Vaucouleurs classification system By @devaucouleursClassificationMorphologyExternal1959](figure/de-vacouler-system.png){#fig-deVac}
+
+Diagrams visualizing the Hubble and Hubble-de Vaucouleurs morphological classification systems
+:::
+
+Although Hubble’s original scheme was revolutionary, **de Vaucouleurs** recognized that not all galaxies fit neatly into its categories.
+In response, he introduced a more nuanced classification system [@devaucouleursClassificationMorphologyExternal1959] that:
+
+-   **Accounts for Rings**: Some galaxies feature ring-like structures around their bulge or bar. To denote this, de Vaucouleurs added **(R)** to the classification (for example, (R)SBa).
+
+-   **Differentiates Bar Strength**: Since bars can vary from subtle to dominant, he proposed **SA** (unbarred), **SAB** (weakly barred), and **SB** (strongly barred).
+
+-   **Incorporates Numerical Types (T-Types)**: To capture subtle transitions along the morphological sequence, de Vaucouleurs assigned a numerical index (TTT) ranging from -6 (pure compact ellipticals) to +10 (extreme irregulars).
+Intermediate values (e.g., -1 for S0, 2 for Sab, 5 for Sc, etc.) let astronomers pinpoint galaxies that don’t fit cleanly into the original categories.
+
+This expanded framework also embraces **early-type** and **late-type** galaxies as part of a continuous evolutionary sequence:
+
+-   **Early-type galaxies** (E and S0):
+
+    -   Smooth appearance.
+
+    -   Predominantly older stellar populations.
+
+    -   Minimal amounts of gas and dust.
+
+    -   Assigned negative T-values ($-6 \le T < 0$).
+
+-   **Late-type galaxies** (Spirals and Irregulars):
+
+    -   Rich in gas and dust.
+
+    -   Significant ongoing star formation.
+
+    -   Smaller bulges and more open arms from Sa/SBa to Sc/SBc.
+
+    -   Assigned positive T-values , extending to +11 for extreme irregulars.
+
+By offering extra designations for bar strength, ring features, and transitional morphologies, de Vaucouleurs’ system paints a more complete picture of galaxies and how they evolve.
+It allows researchers to quantify where a galaxy lies along the continuum, rather than forcing it into a single rigid label.
 
@@
 
+Despite the usefulness of de Vaucouleurs’ numerical T-type system , we run into practical issues when classifying dwarf galaxies.
+These galaxies need a more detailed classification system, since the T-Type system can denote galaxies, whose physical properties drastically differ, with by the same number.
+For instance, dwarf spheroidals and normal ellipticals both end up with a T-value below zero (T \< 0), even though their properties are vastly different.
+Then there are “transient” dwarf galaxies (Tr), whose features bridge spheroidal (Sph)(Sph) and irregular (Ir)(Ir) types.
+Inaccuracies in classification can cause these hybrids to “jump” from one extreme of the T-scale to the other with only a small error in morphology.
+
+To address this, van den Bergh suggested dividing dwarf galaxies by luminosity class, which prevents them from leaping between extreme categories.
+This refined approach better reflects the intrinsic diversity of dwarf systems, ensuring that subtle morphological differences are more accurately captured and reducing the risk of placing galaxies at the wrong end of the classification scale [@karachentsevUPDATEDNEARBYGALAXY2013]
+
 ## Star-Forming Regions
+
+One of the main ingredients of the galaxies are large scale molecular clouds, rich in hydrogen, with masses of order $10^5\ M_\odot$, typical dimensions of $\sim 10$ parsec, temperatures of 10-100 K and densities of 10-300 molecules/cm$^3$ [@polsStellarStructureEvolution2009].
+Stars are created inside these clouds when a perturbation disturbs them, and thus their pressure equilibrium, and they start to collapse into smaller clouds under their self-gravity.
+
+The collapse leads to the formation of protostars, which eventually become main-sequence stars.
+The presence of dust within these clouds is crucial, as it shields the interior regions from ultraviolet radiation, allowing the gas to cool to temperatures below 100 K, facilitating star formation .
+
+The location of the star forming regions within a galaxy depend on the morphology.
+In spiral galaxies, star formation mainly occurs along the disk, where the molecular clouds are dense due to the compression caused by spiral density waves.
+The compression not only initiates the collapse of the clouds and thus the star formation, but also feeds the arms with gas, which sustains the star formation.
+
+In elliptical galaxies, on the other hand, star formation is minimal because they lack the cold gas reservoirs needed for new stars to form.
+Irregular galaxies, with their chaotic structures, often have patchy but vigorous star-forming regions, as they retain significant amounts of gas.
+
+A special case are the starburst galaxies, who have a extremely active star forming regions, and seem to convert the gas into stars extremely fast (even 100 times faster than the Milky Way).
+These starbursts often concentrate their intense star-formation activity in compact regions about 1 kpc in size (typically in galaxy nuclei).
+Due to their high star-formation rates, starbursts host large numbers of young stars.
 
@@
 Different luminosities and intensities trace distinct emission mechanisms, offering insights into a galaxy’s radiation sources.
-Below are common methods:[^3]
+Below are common methods:[^2]
 
-[^3]: @calzettiStarFormationRate2012, @mushotzkyASTR620GalaxiesFall2017
+[^2]: @calzettiStarFormationRate2012, @mushotzkyASTR620GalaxiesFall2017
 
@@
 
-```{r}
-#| fig.cap="Star Formation Rate over the time of star formation, for different parametric models"
-library(ggplot2)
-library(dplyr)
-library(latex2exp)
-
-# Define time values (positive times)
-t <- seq(0.01, 12, length.out = 200)
-
-# Define SFR models
-exponential_decline <- function(t, tau) exp(-t / tau)
-delayed_exponential <- function(t, tau) t * exp(-t / tau)
-log_normal <- function(t, tau, T0) (1 / tau) * exp(-((log(t) - log(T0))^2) / (2 * tau^2))
-double_power_law <- function(t, tau, alpha, beta) 1 / ((t / tau)^alpha + (t / tau)^(-beta))
-
-# Generate data for each model
-data <- data.frame(
-  t = rep(t, 4),
-  SFR = c(
-    exponential_decline(t, tau = 2),
-    delayed_exponential(t, tau = 2),
-    log_normal(t, tau = 2, T0 = 10),
-    double_power_law(t, tau = 2, alpha = 2, beta = 5)
-  ),
-  Model = rep(c("\nExponential Decline\n(τ=2 Gyr)", "\nDelayed Exponential\n(τ=2 Gyr)", "\nLog-Normal\n(τ = 2 Gyr, To = 10 Gyr)", "\nDouble Power Law\n(τ = 2 Gyr, α = 2, β = 5)"), each = length(t))
-)
-
-# Plot all models
-ggplot(data, aes(x = t, y = SFR, color = Model)) +
-  geom_line(size = 1) +
-  labs(
-    title = "Star Formation Rate Models",
-    x = TeX("Star Formation time ( $t_{sf}$ ) [Gyr]"),
-    y = TeX("SFR($t_{sf}$) [ M$_*$/yr ]" ),
-    color = "Model"
-  ) +
-  scale_x_continuous(limits = c(0, 12)) +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
+![Star Formation Rate over the time of star formation, for different parametric models](figure/sfr-models.png){fig-align="center" width="350"}
 
@@
 
-$V = H_0\times d$, where $H_0 \approx 69.8 \text{ km/s/Mpc}$ is the Hubble constant and $d$ is the distance between the two galaxies.[^4]
+$V = H_0\times d$, where $H_0 \approx 69.8 \text{ km/s/Mpc}$ is the Hubble constant and $d$ is the distance between the two galaxies.[^3]
 
-[^4]: We also have non-Hubble motions $V = H_0\times d + V_0$, where $V_0$ is the peculiar velocity and it could, for example, be due to galaxy cluster dynamics.
+[^3]: We also have non-Hubble motions $V = H_0\times d + V_0$, where $V_0$ is the peculiar velocity and it could, for example, be due to galaxy cluster dynamics.
 For the current explanation we are going to ignore it.
@@
 
+![](figure/lily-madau.png){fig-align="center" width="450"}
+
 # Delayed-$\tau$ model
+
+More details about the model and how it clashes with the Lilly-Madau plot
 

### 2025-01-24 thesis.qmd
lilly madau explanation

@@
 
+It is also important to define the Star Formation Density (SFRD):
+
+$$
+\text{SFRD} = \frac{1}{V}\sum^N_{i=1}\text{SFR}_{o,i},
+$$ where $V$ is the comoving volume [^2] of a region of the universe, $N$ is the number of galaxies of the regions and SFR$_{0,i}$ is the current SFR of each galaxy $i$.
+
+[^2]: Comoving volume factors out the expansion of the universe, it remains a constant measure of “space” over time, making it possible to compare star formation at different epochs
+
+For the Local Cosmological Volume, which we will focus on, the volume is the sphere with its center at the Milky Way and a radius of 11 Mpc $V = \frac{4}{3}\pi(11\, \text{Mpc})^3\approx 5575.3\, \text{Mpc}^3$.
+
 ### Estimating SFR from Spectra
@@
 Different luminosities and intensities trace distinct emission mechanisms, offering insights into a galaxy’s radiation sources.
-Below are common methods:[^2]
+Below are common methods:[^3]
 
-[^2]: @calzettiStarFormationRate2012, @mushotzkyASTR620GalaxiesFall2017
+[^3]: @calzettiStarFormationRate2012, @mushotzkyASTR620GalaxiesFall2017
 
@@
 
-## Delayed-$τ$ Model
-
-The delayed $τ$ model is widely used for describing an initial starburst followed by a gradual decline in SFR.
-This places galaxies on the main sequence.
-It is particularly effective for massive galaxies (@haslbauerCosmologicalStarFormation2023).
-However, it assumes smooth SFR evolution and may overestimate peak SFR in high-redshift galaxies.
-
-Using the delayed τ model, we compute $\tau$, $t_{\text{sf}}$, and normalization constant $A_{\text{del}}$ with:
-
-$$
-\text{SFR}_0 = \text{SFR}(t_{sf}) = A_{del}\frac{t_{sf}}{\tau^2}e^{-t_{sf}/\tau}
-$$ {#eq-delayed-current}
-
-where $\text{SFR}_0$ is given in the catalogs.
-
-# Lilly-Madau Plot
+# Lilly-Madau Plot and Delayed-$\tau$ model conflicts
 
@@
 
-![](figure/lily-madau.png){fig-align="center" width="450"}
+![The history of cosmic star formation as shown in @madauCosmicStarFormation2014](figure/lily-madau.png){fig-align="center" width="450"}
 
-# Delayed-$\tau$ model
+Using observational data from UV and IR traces for the SFR for galaxies of different redshifts ($z$) @madauCosmicStarFormation2014 where able to calculate the cosmic SFRD, at different ages of the universe, and reveals three periods of the universe.
 
-More details about the model and how it clashes with the Lilly-Madau plot
+-   **Rising Era** (SFRD$\propto(1+z)^{-2.9},\ 3\lesssim z \lesssim 8$): The SFRD is relatively low at very high redshifts (e.g., $z>6$) and then rises as we move closer to $z \sim 2$.
+This indicates that early galaxies were ramping up their star-forming activity.
+
+-   **Peak Star Formation** ($z \sim 2$): Often dubbed “cosmic noon,” this epoch exhibits the highest SFRD in cosmic history when the Universe was $\sim 3.5$ Gyr old.
+Galaxies are vigorously converting gas into stars, and many of the most massive galaxy systems today formed much of their stellar content during this phase.
+
+-   **Decline to Present Day **(SFRD$\propto (1+z)^{2.7},z\lesssim 2$): After $z \sim 2$, the global SFRD drops by about an order of magnitude towards the present day ($z=0$).
+
+The best-fit function of the comoving SFRD($z$):
+
+$$
+SFRD(z) = 0.015 \, \frac{(1+z)^{2.7}}{1 + \left(\frac{1+z}{2.9}\right)^{5.6}}
+\quad \left[M_\odot \,\mathrm{yr}^{-1}\,\mathrm{Mpc}^{-3}\right],
+$$
+
+## Delayed-$\tau$ model
+
+The delayed $τ$ model is widely used for describing an initial starburst followed by a gradual decline in SFR.
+This places galaxies on the main sequence.
+It is particularly effective for massive galaxies (@haslbauerCosmologicalStarFormation2023).
+However, it assumes smooth SFR evolution and may overestimate peak SFR in high-redshift galaxies.
+
+Using the delayed τ model, we compute $\tau$, $t_{\text{sf}}$, and normalization constant $A_{\text{del}}$ with:
+
+$$
+\text{SFR}_0 = \text{SFR}(t_{sf}) = A_{del}\frac{t_{sf}}{\tau^2}e^{-t_{sf}/\tau}
+$$ {#eq-delayed-current}
+
+where $\text{SFR}_0$ is given in the catalogs.
 

### 2025-01-24 final.py

@@ -1,11 +1,11 @@
-# #+title:Investigations of the galaxies of the LCV
-# #+subtitle: Finding the normalization constant of $SFR_{del}$ and the relations between the various masses of the Galaxies
+# #+title:Investigations of the galaxies in the LCV
+# #+subtitle: Finding the normalization constant of $SFR_{del}$ and the relations between the parameters of the Galaxies
 # #+author: Dimitrios Papachistopoulos
-# #+PROPERTY: header-args :lang python :eval python :exports results :tangle final.py :comments both :results output :session main
+# #+PROPERTY: header-args :lang python :eval python :exports results :tangle final.py :comments both :results output :session main_paper
 
 # :latex_prop:
 # #+OPTIONS: toc:nil
-# #+LaTeX_CLASS_OPTIONS: [a4paper,twocolumn]
+# #+LaTeX_CLASS_OPTIONS: [a4paper]
 # #+LaTeX_HEADER: \usepackage{breakcites}
 # #+LaTeX_HEADER: \usepackage{paralist}
 # #+LaTeX_HEADER: \usepackage{amsmath}
@@ -26,6 +26,7 @@
 
 # [[file:paper.org::+begin_src python :results none][No heading:1]]
 import numpy as np
+import numpy.ma as ma
 import pandas as pd
 from astropy.io import ascii
 from astropy.table import Table, QTable, join, hstack, vstack, unique, Column, MaskedColumn, setdiff
@@ -34,7 +35,8 @@ from astropy.coordinates import SkyCoord, Galactic, Angle
 from astropy.time import Time
 import astropy.units as u
 from astropy.utils.diff import report_diff_values
-from astropy.visualization import quantity_support
+from astropy.visualization import quantity_support, hist
+quantity_support()
 import glob as glob
 import sys
 import matplotlib.pyplot as plt
@@ -50,13 +52,19 @@ from plotnine import (
     xlim, ylim,
     stat_qq
 )
-from scipy.optimize import fsolve
+from scipy import optimize, stats
 from sympy import symbols, exp, log, lambdify
-
-
-dt = QTable.read("./tables/final_table.ecsv")
-dt.info()
+import seaborn as sns
+import plotly.express as px
 # No heading:1 ends here
+
+# [[file:paper.org::+begin_src python :results none][No heading:2]]
+dt = QTable.read("./tables/outer_join.ecsv")
[…]

### 2025-01-27 pipeline.sh
cowsay

@@ -1,16 +1,26 @@
 #!/bin/bash
 
+cowsay "Download UNGC"
 ./downloads.sh
 cd tables
+cowsay "Delete Problem Galaxies"
 ./delete_lines.sh lvg_*
 cd ../notes
-/bin/python3 list.py
+cowsay "compare UNCG"
+./list.py
 cd ../tables
+cowsay "Join UNGC-HEC based on distance"
 ./hecate_lcv_join.sh
 cd ../compare
+cowsay "Compare lists"
 quarto render compare.qmd
 cd ../tables
+cowsay "Mass Flags"
 ./mass_type.sh
 cd ../compare.sh
+cowsay "quick comparison"
 ./quick_diff.py
 ./quick_comp.py
+cd ../tables
+cowsay "Join the common columns"
+./column_join.sh

### 2025-01-27 thesis.qmd
catalog+ yaml abstract

@@
 author: "Dimitrios Papachristopoulos"
+fontfamily: fontenc
 format: 
@@
 toc: true
+toc-expand: true
 toc-depth: 3
+number-sections: true
+appendix-style: plain
 bibliography: ./My_Library.bib
+
 execute: 
@@
 editor: visual
----
 
-{{<pagebreak>}}
-
-# Abstract
-
+abstract: |
   The Star Formation History (SFH) of a galaxy can offer many insights not only for the evolution and the future of the galaxy, but also for the evolution of the Universe.
@@
 The way they calculated this inconsistency is by using observatory data for SFR and Stellar Masses from the UNGC catalog (@karachentsevUPDATEDNEARBYGALAXY2013, @karachentsevSTARFORMATIONPROPERTIES2013) for calculating the parameters (the timescale $\tau$ and the normalization constant $A_{del}$) of the model.
-This calculation for the galaxies of the Local Cosmological Volume (LCV), allows the investigation of the SFR throughout the life each galaxy and so we can find the expected time of peak of the SFR.
+This calculation for the galaxies of the Local Cosmological Volume (LV), allows the investigation of the SFR throughout the life each galaxy and so we can find the expected time of peak of the SFR.
 
@@
   **Keywords:** Galaxies, Galaxy Evolution, Star Formation History (SFH), Star Formation Rate (SFR), Delayed-$\tau$, Local Cosmological Volume, Lilly-Madau Plot, Redshift, Markov Chain Monte Carlo (MCMC).
-
-{{<pagebreak>}}
+---
 
@@
 
--   **Decline to Present Day **(SFRD$\propto (1+z)^{2.7},z\lesssim 2$): After $z \sim 2$, the global SFRD drops by about an order of magnitude towards the present day ($z=0$).
+-   **Decline to Present Day** (SFRD$\propto (1+z)^{2.7},z\lesssim 2$): After $z \sim 2$, the global SFRD drops by about an order of magnitude towards the present day ($z=0$).
 
@@
 
-# Prepering the Catalogs
+# Data of the Local Cosmological Volume
 
-UNGC HECATE join etc...
+In our current analysis, we will use two different catalogs of galaxies, containing galaxies within the Local Cosmological Volume (LV), which is defined as a sphere with a radius of 11 Mpc centred around the Milky Way, to remain consistent with with the analysis of @kroupaConstraintsStarFormation2020 and @haslbauerCosmologicalStarFormation2023.
+The reason we focus on the LV and thus only at small distances is because we want to understand the SFR of the galaxies as they are today and since the redshift depends on distance, we can assume that the redshift of our galaxy sample is $z = 0 \Rightarrow t_\text{emitted}=T_0 = 13.8$ Gyr.
+
+The observational data of galaxies located inside the LV are extracted from the catalogs:
+
+-   **HECATE** [@kovlakasHeraklionExtragalacticCatalogue2021]**:** The Heraklion Extragalactic Catalogue (HECATE) is an all-sky value-added galaxy catalog containing 204,733 galaxies with redshifts up to 0.047 (D ≤ 200 Mpc), from which 2901 are in the LV.
+It incorporates data from multiple surveys and databases, providing information on positions, sizes, distances, morphological classifications, star formation rates, stellar masses, metallicities, and nuclear activity classifications.
+HECATE is well-suited for multi-wavelength and multi-messenger astrophysics, including demographic studies and transient event follow-up.
+
+-   **UNGC Catalog** [@karachentsevUPDATEDNEARBYGALAXY2013; @karachentsevSTARFORMATIONPROPERTIES2013]**:** The Updated Nearby Galaxy Catalog (UNGC)[^5] provides a distance-limited within 11 Mpc or radial velocities of $V < 600\ km \cdot s^{−1}$.
+Selecting galaxies whith $D\leq 11$ Mpc, we get a sample of 1321 galaxies.
+It offers detailed star formation rate estimates derived from H$\alpha$ and far-ultraviolet (FUV) fluxes, making it particularly valuable for studying nearby galaxies and local star formation processes.
+The UNGC catalog focuses on galaxies with well-determined distances and includes detailed environmental and morphological data.
+
+[^5]: The UNGC tables can be downloaded using the following link: <https://www.sao.ru/lv/lvgdb/introduction.php>. Here, we use the latest update from 17.01.2025.
 
@@
 ## MCMC
+
+{{<pagebreak>}}
+
+# Linear Comparison of the catalogs {.appendix}
+
+{{<pagebreak>}}
+
+# References {.unnumbered}
+
+::: {#refs}
+:::

### 2025-01-27 r_mcmc/R/functions.R
new SFR run

@@ -7,12 +7,12 @@ prepare_data <- function(data_csv) {
            logM_HEC = ifelse(is.na(logM_HEC), 0.822 * K, logM_HEC), # Replace missing logM_HEC with 0.8 * K
            logM_HEC = ifelse(is.na(logM_HEC), 0.822 * KLum, logM_HEC) # Replace missing logM_HEC with 0.8 * KLum
            ) %>%
-    select(logSFR_UNGC_Gyr, id_number, logM_HEC) %>%
+    select(logSFR_total, id_number, logM_HEC) %>%
     filter(
-      logSFR_UNGC_Gyr >=-3,
-      !is.na(logSFR_UNGC_Gyr),
-      !is.nan(logSFR_UNGC_Gyr),
-      is.finite(logSFR_UNGC_Gyr),
+      #iogSFR_total >=-3,
+      !is.na(logSFR_total),
+      !is.nan(logSFR_total),
+      is.finite(logSFR_total),
       !is.na(logM_HEC),
       !is.nan(logM_HEC),
       is.finite(logM_HEC)

### 2025-01-27 r_mcmc/_targets.R

@@ -7,6 +7,8 @@
 library(targets)
 library(tarchetypes) # Load other packages as needed.
 library(stantargets)
+library(crew)
+library(future)
 
 # Set target options:
 tar_option_set(
@@ -51,11 +53,12 @@ tar_source()
 
 # Replace the target list below with your own:
 # Define the pipeline
-list(
+#list(
+tar_plan(
   # Step 1: Load and prepare data
   tar_target(
     csv_file_path,
-    "outer_join.csv",
+    "filled.csv",
     format = "file"
   ),
   tar_target(
@@ -75,15 +78,15 @@ list(
     #stderr = "error.txt",
     data = list(
       N = nrow(sfr_data),
-      logSFR_UNGC_Gyr = sfr_data$logSFR_UNGC_Gyr,
+      logSFR_total = sfr_data$logSFR_total,
       id_numbers = sfr_data$id_number,
       M_star = sfr_data$logM_HEC
     ),
-    chains = 4,
+    chains = 7,
     parallel_chains = 8,
-    iter_sampling = 5000,
-    iter_warmup = 3500,
-    init = init_function(4,1132),
+    iter_sampling = 4500,
+    iter_warmup = 3000,
+    init = init_function(7,1761),
     
   ),
 
@@ -92,7 +95,7 @@ list(
     fit = stan_fit_mcmc_x,
     data = list(
       N = nrow(sfr_data),
-      logSFR_UNGC_Gyr = sfr_data$logSFR_UNGC_Gyr,
+      logSFR_total = sfr_data$logSFR_total,
       id_numbers = sfr_data$id_number
     ),
     variables = "id"
@@ -103,7 +106,7 @@ list(
     fit = stan_fit_mcmc_x,
     data = list(
       N = nrow(sfr_data),
-      logSFR_UNGC_Gyr = sfr_data$logSFR_UNGC_Gyr,
+      logSFR_total = sfr_data$logSFR_total,
       id_numbers = sfr_data$id_number
     ),
     variables = "logSFR_today"
@@ -114,7 +117,7 @@ list(
     fit = stan_fit_mcmc_x,
     data = list(
       N = nrow(sfr_data),
-      logSFR_UNGC_Gyr = sfr_data$logSFR_UNGC_Gyr,
+      logSFR_total = sfr_data$logSFR_total,
       id_numbers = sfr_data$id_number
     ),
[…]

### 2025-01-27 tables/column_join.sh

@@ -1,0 +1,14 @@
+#!/bin/bash
+
+stilts tpipe \
+  in=outer_join.ecsv \
+  omode=out out=filled.ecsv \
+  cmd='addcol -units "Mpc" -desc "Merge Distance" merge_D "NULL_D ? Dis : D"' \
+  cmd='addcol -units "km/h" -desc "Merge radial velocity" merge_V "NULL_V ? RVel : V"' \
+  cmd='addcol -desc "Merge numerical Hubble Type" merge_T "NULL_T ? TType : T"' \
+  cmd='addcol -units "log(Lsol)" -desc "Merge logK" merge_logKLum "NULL_logL_K ? logKLum : logL_K"' \
+  cmd='addcol -units "mag" -desc "Merge K mag" merge_Kmag "NULL_K ? Kmag : K"' \
+  cmd='addcol -units "mag" -desc "Merge B mag" merge_Bmag "NULL_BT ? mag_B : BT"' \
+  cmd='addcol -units "log(Msol/yr)" -desc "Merge of log SFR" logSFR_total "NULL_logSFR_HEC ? 0.7*logSFR_UNGC : logSFR_HEC"'\
+  cmd='addcol -units "Msol/yr" -desc "Total SFR in linear scale" SFR_total "exp10(logSFR_total)"'\
+  cmd='addcol -units "log(Msol)" -desc "" logSFR_total "NULL_logSFR_HEC ? 0.7*logSFR_UNGC : logSFR_HEC"'\

### 2025-02-02 thesis.qmd
catalogs+appendix A

@@
 
-A special case are the starburst galaxies, who have a extremely active star forming regions, and seem to convert the gas into stars extremely fast (even 100 times faster than the Milky Way).
+A special case are the starburst galaxies, which have extremely active star-forming regions, and seem to convert the gas into stars extremely fast (even 100 times faster than the Milky Way).
 These starbursts often concentrate their intense star-formation activity in compact regions about 1 kpc in size (typically in galaxy nuclei).
@@
 
-![Star Formation Rate over the time of star formation, for different parametric models](figure/sfr-models.png){fig-align="center" width="350"}
+![Star Formation Rate over the time of star formation, for different parametric models](figure/sfr-models.png){fig-align="center" width="300"}
 
@@
 
--   **UNGC Catalog** [@karachentsevUPDATEDNEARBYGALAXY2013; @karachentsevSTARFORMATIONPROPERTIES2013]**:** The Updated Nearby Galaxy Catalog (UNGC)[^5] provides a distance-limited within 11 Mpc or radial velocities of $V < 600\ km \cdot s^{−1}$.
-Selecting galaxies whith $D\leq 11$ Mpc, we get a sample of 1321 galaxies.
+-   **UNGC Catalog** [@karachentsevUPDATEDNEARBYGALAXY2013; @karachentsevSTARFORMATIONPROPERTIES2013]**:** The Updated Nearby Galaxy Catalog (UNGC)[^5] provides a distance-limited sample of galaxies, within 11 Mpc or radial velocities of $V < 600\ km \cdot s^{−1}$.
+Selecting galaxies with $D\leq 11$ Mpc, we get a sample of 1321 galaxies.
 It offers detailed star formation rate estimates derived from H$\alpha$ and far-ultraviolet (FUV) fluxes, making it particularly valuable for studying nearby galaxies and local star formation processes.
@@
 
+We will join the two catalogs, based on the coordinates of the galaxies, so we could assure a bigger and more coplete sample size for our analysis.
+But first we need to undestand them and examine if there are any inconsistances between UNGC and HECATE.
+
 ## Catalog Completeness
+
+The Completeness of a catalog refers to the extent to which a catalog includes all the galaxies within a specified region of the sky, distance, or luminosity range.
+A complete catalog accurately represents the true population of galaxies, which eleminates the bias of the sample.
+No catalog could trully be $100\%$ complete, but by understanding the shortcomings of the the catalog, we can account for the possible biases that can occur in our analysis.
+
+The *HECATE* catalog is designed to be a more comprehensive resource, covering a broader range of distances and luminosities.
+
+-   **Luminosity and Distance Dependence:** The HECATE catalog is more complete for brighter galaxies (with luminosities above $10^{9.5} L_{B,\odot}$) and distances within 33 Mpc, which includes the LV.
+For galaxies with luminosities around $10^{10} L_{B,\odot}$)​, the catalog remains complete up to distances of 100 Mpc.
+-   **Luminosity Density:** The catalog's completeness is also estimated based on the luminosity density in the B-band.
+Within 30 Mpc, the catalog is over 100% complete due to the high density of galaxies around the Milky Way.
+However, at distances around 170 Mpc, the completeness drops to approximately 50%, indicating that many galaxies are missing.
+-   **Star Formation Rate and Stellar Mass:** The completeness of SFR is around 50% for distances between 30 and 150 Mpc, primarily due to limitations in the WISE survey coverage.
+Similarly, the completeness of stellar mass estimates is comparable to that of the B-band luminosity, with overdensities at short distances and a sharp cutoff at larger distances.
+
+The *UNGC* catalog focuses on galaxies within the LV, specifically those with radial velocities less than 600 km/s and distances within 11 Mpc.
+It is around $40\%-60\%$ complete for galaxies with B-band magnitude $M_B^c < -11^m$.
+In the Local Group ($D \leq 10 \, \text{Mpc}$) only half the galaxies have $M_B^c > -11^m$ and it is expected that for distances $\sim 9 \, \text{Mpc}$ more than half of the ultra-faint galaxies are missing.
+Specifically, it is estimated that around $10^3–10^4$ galaxies of the LV are not included in UNGC.
+
+The incompleteness for ultra-faint galaxies is primarily due to their low surface brightness, making them difficult to detect beyond the Local Group.
+This limitation is particularly significant for studies of dwarf galaxies and the faint end of the galaxy luminosity function
 
@@
 
-## The "special" case of the Star Formation Rates
+Before we merge the two catalogs we need to compare the corresponding quantities to ensure that there are no major incompatabilities. The quantities that are comparable are:
+
+-   Distances \[Mpc\]
+-   Radial Velocities \[km/s\]
+-   Morphology and Geometry of the galaxies
+    -   Morphological type (Numerical Hubble)
+    -   Inclination \[degrees\]
+    -   Angular Diameter of the Major and Semi-major axis \[arcmin\]
+-   K-band Luminosity \[$L_\odot$\]
+-   K and B-band Magnitudes \[mag\]
+-   Star Formation Rates \[$M_\odot/yr$\]
+
+For the comparison of our data we will use linear regression, accounting for the errors of the observed data, where $R^2$ and the slope of the fitted line should be close to 1[^6].
+We will also plot the residuals ($y_\text{Regression}-y_\text{observed}$) and if the mean value $\overline{\text{Residuals}}\approx 0$, then the linear regression is succesfull.
+
+[^6]: $R^2$ Measures the proportion of variance explained by the linear model. For a model to be acceptable the $R^2$ should be atleast $80\%$
+
+All the results are shown in @sec-regressions, except the comparisons of the Morphological Types and of the SFRs,who need more detailed analysis.
+
+To begin with the morphological types of the galaxies we first need to understand possible incompatabilities of the given types of each catalog.
+
+::: {#fig-TTypes layout-ncol=2}
+![Before the clipping of the transient types](compare/quickplots/Hubble%20Morphology.png)
+
+![After the clipping of the transient types](compare/quickplots/Type_clip.png)
+
+Scatter plots and the residuals of the Hubble Numerical morphological types
+:::
 
@@
 
-# Linear Comparison of the catalogs {.appendix}
+# Appendix A: Scatter plots of the comparisons {#sec-regressions .appendix}
+
+::: {layout-ncol="2"}
+![Linear Regression of the Distances in Mpc](compare/quickplots/Distance.png){width="300"}
+
+![Linear Regression of the Radial Velocities in km/s](compare/quickplots/Heliocentric%20radial%20velocity.png){width="300"}
+:::
+
+::: {#fig-elephants layout-ncol="2"}
+![Linear Regression of the K-band luminosity in $L_\odot$](compare/quickplots/K-Luminosity.png){width="300"}
+
+![Linear Regression of the B-Band Magnitude](compare/quickplots/Magnitude%20(B-band).png){width="300"}
+
+![Linear Regression of the K-Band Magnitude](compare/quickplots/Magnitude%20(K-band).png){width="300"}
+
+![Linear Regression of the Angular Diameter of the Major and Semi-major axis in arciminutes](compare/quickplots/Major%20Axis%20(arcmin).png){width="300"}
+:::
 

### 2025-02-04 thesis.qmd
delayed-tau vs lilly-madau

@@
 \text{SFRD} = \frac{1}{V}\sum^N_{i=1}\text{SFR}_{o,i},
-$$ where $V$ is the comoving volume [^2] of a region of the universe, $N$ is the number of galaxies of the regions and SFR$_{0,i}$ is the current SFR of each galaxy $i$.
+$$
+
+where $V$ is the comoving volume [^2] of a region of the universe, $N$ is the number of galaxies of the regions and SFR$_{0,i}$ is the current SFR of each galaxy $i$.
 
@@
 1+z = \sqrt{\frac{1+v/c}{1-v/c}}
-$$ {#eq-z-rel} For small $v/c$ we can rewrite @eq-z-rel, as:
+$$ {#eq-z-rel}
+
+For small $v/c$ we can rewrite @eq-z-rel, as:
 
@@
 
-Using the delayed τ model, we compute $\tau$, $t_{\text{sf}}$, and normalization constant $A_{\text{del}}$ with:
+Using the delayed-$\tau$ model, we compute $\tau$, $t_{\text{sf}}$, and normalization constant $A_{\text{del}}$ with:
 
@@
 where $\text{SFR}_0$ is given in the catalogs.
+According to these model the timescale, at which the SFR peaks, is around $3.5\lessapprox\tau\lessapprox 4.5$ [@speagleHighlyConsistentFramework2014].
+If we intergrate the SFR(t), we can calculate the present day averaged SFR:
+
+$$
+\overline{\text{SFR}_\text{del}} = \frac{1}{t_{sf}}\int^{t_\text{end}}_{t_\text{start}}\text{SFR}_{del}(t)dt = \frac{A_{del}}{t_{sf}}\left[1-\left(1+\frac{t_{sf}}{\tau}\right)\exp\left(-\frac{t_{sf}}{\tau}\right)\right]
+$$ {#eq-delayed-current-averaged}
+
+Where $\overline{\text{SFR}}$ can be calculated by the stellar masses of the galaxy of interest:
+
+$$
+\overline{\text{SFR}_\text{del}} = \frac{\zeta M_*}{t_sf}
+$$ {#eq-averaged-SFR-M*}
+
+and $\zeta$ accounts for the mass-loss through stellar evolution, and is $\zeta \approx 1.3$ [@kroupaConstraintsStarFormation2020].
+
+Using these two equations @haslbauerCosmologicalStarFormation2023 calculated the parameters $\tau,\ A_{del}$ of the model, for a constant $t_{sf}$ for all the galaxies, and thus they were able to approximate Cosmic SFRD of the LV.
+They found that the SFHs implied from the LV galaxies systematically underestimate the SFRDs at $z \lesssim 3$ and overestimates the SFRDs at $z\gtrsim 6$ as in comparison to those of MD14.
+In particular, the SFRD at the peak of the Lilly-Madau plot is $2.16 \pm 0.32$ lower in the case of the delayed-$\tau$.
+However, since they assume that all the galaxies begin at the same time and their sample size is not representative of the observed Universe, better calculations could potentially fix these discrepancies.
+However, these parametrization of the SFH could also be inadequate to describe galaxy evolution, especially for galaxies with $M_*<10^{10}\ M_\odot$, as discussed in @haslbauerCosmologicalStarFormation2023.
 
@@
 
-To begin with the morphological types of the galaxies we first need to understand possible incompatabilities of the given types of each catalog.
+To begin with the morphological types of the galaxies we first need to understand possible incompatibilities of the given types of each catalog.
 
-::: {#fig-TTypes layout-ncol=2}
+::: {#fig-TTypes layout-ncol="2"}
 ![Before the clipping of the transient types](compare/quickplots/Hubble%20Morphology.png)
@@
 
-Scatter plots and the residuals of the Hubble Numerical morphological types
+Scatter plots and the residuals of the Hubble Numerical morphological types show a good correlation between the two datasets, if we ignore the transient galaxies.
 :::

### 2025-02-04 thesis.qmd
common galaxy count

@@
 
-Before we merge the two catalogs we need to compare the corresponding quantities to ensure that there are no major incompatabilities. The quantities that are comparable are:
+Before we merge the two catalogs we need to compare the corresponding quantities of the 288 common galaxies to ensure that there are no major incompatabilities. The quantities that are comparable are:
 
--   Distances \[Mpc\]
--   Radial Velocities \[km/s\]
+-   Distances \[Mpc\] (288/288 galaxies)
+-   Radial Velocities \[km/s\] (286/288 galaxies)
 -   Morphology and Geometry of the galaxies
-    -   Morphological type (Numerical Hubble)
-    -   Inclination \[degrees\]
-    -   Angular Diameter of the Major and Semi-major axis \[arcmin\]
--   K-band Luminosity \[$L_\odot$\]
--   K and B-band Magnitudes \[mag\]
--   Star Formation Rates \[$M_\odot/yr$\]
+    -   Morphological type (229/288 galaxies)
+    -   Inclination \[degrees\] (209/288 galaxies)
+    -   Angular Diameter of the Major and Semi-major axis \[arcmin\] (261/288 galaxies)
+-   K-band Luminosity \[$L_\odot$\] and Magnitude (70/288 galaxies)
+-   B-band Magnitudes \[mag\] (244/288 galaxies)
+-   Star Formation Rates \[$M_\odot/yr$\] (73/288 galaxies)
 

### 2025-02-05 thesis.qmd
comp-Tr

@@
 
-### Dwarf Galaxies
+### Dwarf Galaxies {#sec-dwarves}
 
@@
 
-[^6]: $R^2$ Measures the proportion of variance explained by the linear model. For a model to be acceptable the $R^2$ should be atleast $80\%$
+[^6]: $R^2$ Measures the proportion of variance explained by the linear model.
+For a model to be acceptable the $R^2$ should be higher than $80\%$, or close to it if $\overline{\text{Residuals}}\approx 0$
 
@@
 
-To begin with the morphological types of the galaxies we first need to understand possible incompatibilities of the given types of each catalog.
+To begin with the morphological types of the galaxies, we first need to address possible potential inconsistencies in the classifications of the two catalogs.
+As we can see in @fig-TType-all, some galaxies "jump" from one side of the classification to the other side, depending on the catalog.
+These galaxies are dwarf galaxies, so we can safely assume that they are Tr type galaxies, as discussed in @sec-dwarves.
+For the rest of the analysis we will adopt the Numerical Morphological Type from the HECATE catalog, since it includes a larger number of galaxies, ensuring better
+data compatibility. Additionally, the HECATE catalog boasts an accuracy of 0.1 and provides errors in comparison with the UNGC.
 
 ::: {#fig-TTypes layout-ncol="2"}
-![Before the clipping of the transient types](compare/quickplots/Hubble%20Morphology.png)
+![Before the clipping of the transient types](compare/quickplots/Hubble%20Morphology.png){#fig-TType-all}
 
@@
 
-Scatter plots and the residuals of the Hubble Numerical morphological types show a good correlation between the two datasets, if we ignore the transient galaxies.
+Scatter plots and the residuals of the Hubble Numerical morphological types show a good correlation between the two datasets, if we ignore the Transient dwarf galaxies.
 :::

### 2025-02-05 compare/quick_comp.py
quick_comp+units+N_sample

@@ -55,6 +55,7 @@ data["logSFR_mean"] = np.log10(data["SFR_mean"])
 def perform_linear_regression_analysis_fixed(
     x,
     y,
+    unit = None,
     desc=None,
     x_error=None,
     y_error=None,
@@ -71,6 +72,8 @@ def perform_linear_regression_analysis_fixed(
         col for col in [x, y, x_error, y_error, "mass_type"] if col in data.columns
     ]
     aligned_data = data[error_cols].dropna()
+    total_sample_size = len(aligned_data)
+
 
     # Proceed only if there's sufficient data
     if len(aligned_data) < 2:
@@ -105,10 +108,10 @@ def perform_linear_regression_analysis_fixed(
     results = model.fit()
 
     # Fit parameters
-    slope = results.params[1]
-    intercept = results.params[0]
-    slope_err = results.bse[1]
-    intercept_err = results.bse[0]
+    slope = results.params.iloc[1]  # Use .iloc for positional indexing
+    intercept = results.params.iloc[0]
+    slope_err = results.bse.iloc[1]
+    intercept_err = results.bse.iloc[0]
     r_squared = results.rsquared
 
     # Calculate residuals
@@ -123,6 +126,7 @@ def perform_linear_regression_analysis_fixed(
     # Scatter plot with fit
     for name, group in groups:
         marker_shape = marker_dict[name] if marker_dict and name in marker_dict else "o"
+        sample_size = len(group)  # Count the number of points in the group
 
         x_data_g = group[x] if log_transform_x is False else np.log10(group[x])
         y_data_g = group[y] if log_transform_y is False else np.log10(group[y])
@@ -137,7 +141,7 @@ def perform_linear_regression_analysis_fixed(
             fmt=marker_shape,
             ecolor="grey",
             capsize=3,
-            label=name,
+            label=f"{name} (N = {sample_size})",
         )
     # Plot the fitted line
     x_range = axs[0].get_xlim()
@@ -149,27 +153,37 @@ def perform_linear_regression_analysis_fixed(
         color="red",
         label=f"Fit: y = ({slope:.3f} ± {slope_err:.3f})x + ({intercept:.3f} ± {intercept_err:.3f})",
     )
-    axs[0].set_xlabel(
-        f"UNGC({'log10(' if log_transform_x else ''}{x}{')' if log_transform_x else ''})"
-    )
-    axs[0].set_ylabel(
[…]

### 2025-02-06 tables/column_join.sh
fixed SFR and M total

@@ -9,6 +9,6 @@ stilts tpipe \
   cmd='addcol -units "log(Lsol)" -desc "Merge logK" merge_logKLum "NULL_logL_K ? logKLum : logL_K"' \
   cmd='addcol -units "mag" -desc "Merge K mag" merge_Kmag "NULL_K ? Kmag : K"' \
   cmd='addcol -units "mag" -desc "Merge B mag" merge_Bmag "NULL_BT ? mag_B : BT"' \
-  cmd='addcol -units "log(Msol/yr)" -desc "Merge of log SFR" logSFR_total "NULL_logSFR_HEC ? 0.7*logSFR_UNGC : logSFR_HEC"'\
+  cmd='addcol -units "log(Msol/yr)" -desc "Merge of log SFR" logSFR_total "NULL_logSFR_HEC ? 0.7*logSFR_UNGC-0.6 : logSFR_HEC"'\
   cmd='addcol -units "Msol/yr" -desc "Total SFR in linear scale" SFR_total "exp10(logSFR_total)"'\
-  cmd='addcol -units "log(Msol)" -desc "" logSFR_total "NULL_logSFR_HEC ? 0.7*logSFR_UNGC : logSFR_HEC"'\
+  cmd='addcol -units "log(Msol)" -desc "" logM_total "NULL_logM_HEC ? log10(0.82)+merge_logKLum: logM_HEC"'\

### 2025-02-06 thesis.qmd
quick_comp+units+N_sample
SFR-comparison

@@
 
-### Estimating SFR from Spectra
+### Estimating SFR from Spectra {#sec-SFR-est}
 
@@
 
--   **Hα** \boldmath$\alpha$ **Emission**: Young, hot, massive stars (O-type stars, \~10 Myr, \~20 $M_\odot$) produce a number of ionizing photons, which they ionize the surrounding hydrogen rich gas.
+-   **H**\boldmath$\alpha$ **Emission**: Young, hot, massive stars (O-type stars, \~10 Myr, \~20 $M_\odot$) produce a number of ionizing photons, which they ionize the surrounding hydrogen rich gas.
 The hydorgen undergoes recombination cascades which produce Balmer emission lines of $H\alpha$ (0.6563 $\mu m$) and $H\beta$ (0.4861 $\mu m$).
@@
 
-![Plot showing the linear relation $\log_{10}\text{SFR}_{FUV} = \log_{10}\text{SFR}_{H\alpha}$, as well as their distrubutions](figure/log_SFR_FUV_Ha.png){fig-align="center" width="500"}
+![Plot showing the linear relation $\log_{10}\text{SFR}_{FUV} = \log_{10}\text{SFR}_{H\alpha}$, as well as their distributions, based on the data from UNGC](figure/log_SFR_FUV_Ha.png){#fig-SFR-Ha-FUV fig-align="center" width="500"}
 
@@
 = SFR_{\text{FUV},H\alpha}+ SFR_{\text{IR}}
-$$
+$$ {#eq-SFR-tot-mean}
 
@@
 
--   Distances \[Mpc\] (288/288 galaxies)
--   Radial Velocities \[km/s\] (286/288 galaxies)
+-   Distances \[Mpc\] (288/288 common galaxies)
+-   Radial Velocities \[km/s\] (286/288 common galaxies)
 -   Morphology and Geometry of the galaxies
-    -   Morphological type (229/288 galaxies)
-    -   Inclination \[degrees\] (209/288 galaxies)
-    -   Angular Diameter of the Major and Semi-major axis \[arcmin\] (261/288 galaxies)
--   K-band Luminosity \[$L_\odot$\] and Magnitude (70/288 galaxies)
--   B-band Magnitudes \[mag\] (244/288 galaxies)
--   Star Formation Rates \[$M_\odot/yr$\] (73/288 galaxies)
+    -   Morphological type (229/288 common galaxies)
+    -   Inclination \[degrees\] (209/288 common galaxies)
+    -   Angular Diameter of the Major and Semi-major axis \[arcmin\] (261/288 common galaxies)
+-   K-band Luminosity \[$L_\odot$\] and Magnitude (70/288 common galaxies)
+-   B-band Magnitudes \[mag\] (244/288 common galaxies)
+-   Star Formation Rates \[$M_\odot/yr$\] (73/288 common galaxies)
 
 For the comparison of our data we will use linear regression, accounting for the errors of the observed data, where $R^2$ and the slope of the fitted line should be close to 1[^6].
-We will also plot the residuals ($y_\text{Regression}-y_\text{observed}$) and if the mean value $\overline{\text{Residuals}}\approx 0$, then the linear regression is succesfull.
+We will also plot the residuals ($y_\text{Regression}-y_\text{observed}$) and if the mean value $\overline{\text{Residuals}}\approx 0$, then the linear regression is considered succesfull.
 
-[^6]: $R^2$ Measures the proportion of variance explained by the linear model.
+[^6]: $R^2$ measures the proportion of variance explained by the linear model.
 For a model to be acceptable the $R^2$ should be higher than $80\%$, or close to it if $\overline{\text{Residuals}}\approx 0$
 
-All the results are shown in @sec-regressions, except the comparisons of the Morphological Types and of the SFRs,who need more detailed analysis.
+All the results are shown in @sec-regressions, except the comparisons of the Morphological Types and of the SFRs, that need more detailed analysis.[^7]
 
-To begin with the morphological types of the galaxies, we first need to address possible potential inconsistencies in the classifications of the two catalogs.
+[^7]: The names of the x and y axes are written as they are given in the corresponding catalog, except the ones in decimal logarithmic scale, that are notated appropriately.
+
+To begin with the morphological types of the galaxies, we first need to address potential inconsistencies in the classifications of the two catalogs.
 As we can see in @fig-TType-all, some galaxies "jump" from one side of the classification to the other side, depending on the catalog.
 These galaxies are dwarf galaxies, so we can safely assume that they are Tr type galaxies, as discussed in @sec-dwarves.
-For the rest of the analysis we will adopt the Numerical Morphological Type from the HECATE catalog, since it includes a larger number of galaxies, ensuring better
-data compatibility. Additionally, the HECATE catalog boasts an accuracy of 0.1 and provides errors in comparison with the UNGC.
+For the rest of the analysis we will adopt the Numerical Morphological Type from the HECATE catalog, since it includes a larger number of galaxies, ensuring better data compatibility.
+Additionally, the HECATE catalog boasts an accuracy of 0.1 and provides errors, while the UNGC provides a rigid categorization of the galaxies with no errors.
 
@@
 :::
+
+Next we need to analyze the SFR from the two catalogs.
+The catalogs provide different SFR estimators, H$\alpha$ and FUV from UNGC and the total IR from HECATE.
+As already discussed in @sec-SFR-est, the two estimators FUV and H$\alpha$ can be combined using their average ($\text{mean}(SFR_{FUV},SFR_{H\alpha})$), however both estimators and their average can potentially underestimate the SFR due to dust attenuation ($SFR_{TIR}$ is not affected by this), and this is exactly what is observed in @fig-SFR-comparison.
+
+![Scatter plot and the residuals of the $\text{mean}(SFR_{FUV},SFR_{H\alpha})$ from the UNGC catalog and the $SFR_{TIR}$.
+The SFR estimation from the FUV and H$\alpha$ is systematically lower than the $SFR_{TIR}$ estimator as expected.
+The $R^2$ is smaller than 80% however due to $\overline{\text{Residuals}}=0$ we can assume that the quantities are comparable.](images/paste-1.png){#fig-SFR-comparison width="60%"}
+
+In reality those estimators compliment each other and this is exactly why we they are not equal.
+The total SFR could potentially be calculated by @eq-SFR-tot-mean, however due to the lack of samples with both traces the calculation of $\text{SFR}_\text{total}$ is not possible without introducing biases to our data.
+Due to the underestimation from the estimators of UNGC, the main estimator used in our analysis will be the $TIR$ estimator and the $\text{mean}(SFR_{FUV},SFR_{H\alpha})$ will be transformed into the expected $\text{SFR}_\text{TIR}$ according to the linear regression of @fig-SFR-comparison.
 

### 2025-02-06 thesis.qmd
figure->images

@@
 
-![Star Formation Rate over the time of star formation, for different parametric models](figure/sfr-models.png){fig-align="center" width="300"}
+![Star Formation Rate over the time of star formation, for different parametric models](images/sfr-models.png){fig-align="center" width="300"}
 
@@
 
-![The history of cosmic star formation as shown in @madauCosmicStarFormation2014](figure/lily-madau.png){fig-align="center" width="450"}
+![The history of cosmic star formation as shown in @madauCosmicStarFormation2014](images/lily-madau.png){fig-align="center" width="450"}
 
@@
 The SFR estimation from the FUV and H$\alpha$ is systematically lower than the $SFR_{TIR}$ estimator as expected.
-The $R^2$ is smaller than 80% however due to $\overline{\text{Residuals}}=0$ we can assume that the quantities are comparable.](images/paste-1.png){#fig-SFR-comparison width="60%"}
+The $R^2$ is smaller than 80% however due to $\overline{\text{Residuals}}=0$ we can assume that the quantities are comparable.](compare/quickplots/SFR.png){#fig-SFR-comparison width="60%"}
 

### 2025-02-08 thesis.qmd
N-R+Markov-Chains+Monte_carlo

@@
 
+The Newton-Raphson method is one of the most common numerical methods for estimating the root of a real-valued function.
+This method is based on the concept of linear approximation, where the function is locally approximated by its tangent line.
+It starts with initial guess of the root and iteratively refines the result using a formula that involves derivative of the function.
+
+Let $x_n$ be the n-th approximation of the root and $f(x), f'(x)$ the function and the derivative, respectivelly. Then the refined approximation of the root $x_{n+1}$ is given by the formula
+
+$$
+x_{n+1} = x_n - \frac{f(x_n)}{f'(x_n)},\ n\in \mathbb{N}
+$$
+
+The iteration stops when $f(x_n)=0$, or after it reaches a certain number of iterations.
+If the initial estimation $x_0$ is close to the actual root, then the accuracy of the approximation increases rapidly with each iteration.
+If, however, the initial guess is poor, the model may fail to converge, which occurs when
+
+$$
+\left|\frac{f(x_n)f''(x_n)}{f'(x_n)^2}\right|>1.
+$$
+
+Therefore, while the Newton-Raphson method is a powerful tool in numerical analysis, due to its efficiency and ease of use, it is reliant on a good initial guess which is not always possible.
+
 ## Markov Chain Monte Carlo
+
+Markov Chain Monte Carlo (MCMC) is a computer–driven sampling method which combines two properties: *Monte–Carlo* and *Markov chain*
+
+A *Markov Chain* is a type of stochastic process that represents a sequence of events where the likelihood of each event depends solely on the state reached in the preceding event.
+In other words the future of each state depends only on the current state and not the past [@andrieuIntroductionMCMCMachine2003].
+
+$$
+\Pr(X_{n+1}=x\mid X_1=x_1, X_2=x_2, \ldots, X_n=x_n) = \Pr(X_{n+1}=x\mid X_n=x_n),
+$$
+
+if both conditional probabilities are well defined, that is, if $\Pr(X_1=x_1,\ldots,X_n=x_n)>0$.
+
+A great example of such a chain is the board game snake and ladders.
+The dice has a uniform probabiliy  distribution across 6 stages (integers 1 to 6).
+The players have a position on the board, but their next position on the board is only based on the current position and the random roll of the dice.
+The one dimension random walk algorithm is also a Markov Chain.
+
+The *Monte Carlo* method is a computational method that uses random values from a given probability distribution to approximate the features of the given distribution [@vanravenzwaaijSimpleIntroductionMarkov2018].
+For example, if we want to calculate the mean of a normal distribution we can to draw a large number of random samples from the distribution, and calculate the sample mean of those, instead of calculating it directly.
 
@@
 
+After the merging of the two catalogs we get a final sample of 3934 galaxies out of each only 288 are included in both catalogs and where used for the comparison.
+1033 are unique galaxies in the UNGC and the remaining 2613 are unique in the HECATE catalogs.
+Additionally, 1842 galaxies have SFR data (778 from HECATE and 1137 from UNGC), and 3042 galaxies have Stellar Mass data (1605 from HECATE, with the rest estimated using a mass-to-light ratio of 0.82 as provided by HECATE).
+1761 galaxies have both SFR and $M_*$ data.
+
 # Calculating the parameters

### 2025-02-09 thesis.qmd
mcmc theory

@@
 
-[^1]: @hoskinGreatDebateWhat1976
+[^1]: The chain is homogeneous if $T \forall x^{(i)}$ remains invariant (the probability of moving from $x^{(i−1)}$ to $x^{(i)}$ does not depend on the iteration number $i$.) and $\sum_{x^{(i)}} T\bigl(x^{(j)} \mid x^{(i-1)}\bigr) = 1$.
 
@@
 
+*MCMC* combines the properties of Markov chains and Monte Carlo, allowing the approximation of aspects of posterior distributions that cannot be directly calculated.
+
+Let $x^{(i)}$ be a homoguneous Markov chain[^5] inside a high-dimensional space $X$ of the set of possible configurations of a system and the space on which the posterior is defined, $x^{(i)}\in X = {x_1,x_2,...}$.
+
+[^5]: The chain is homogeneous if $T \forall x^{(i)}$ remains invariant (the probability of moving from $x^{(i−1)}$ to $x^{(i)}$ does not depend on the iteration number $i$.) and $\sum_{x^{(i)}} T\bigl(x^{(j)} \mid x^{(i-1)}\bigr) = 1$.
+
+The chain is described by the formula:
+
+$$
+p\bigl(x^{(i)} \mid x^{(i-1)},\dots,x^{(1)}\bigr) = T\bigl(x^{(i)} \mid x^{(i-1)}\bigr),
+$$
+
+where $T$ is the transition matrix and $p$ is the probability, following Bayes' rule $p(x|D) \propto p(D|x)\cdot p(x)$ ($D$ indicates the data).
+We chose $T$ in such a way that its stationary distribution is the posterior $p$:
+
+$$
+p\bigl(x^{(i)}\bigr)
+\;=\;
+\sum_{x^{(i-1)}} 
+p\bigl(x^{(i-1)}\bigr)\;T\bigl(x^{(i)} \mid x^{(i-1)}\bigr).
+$$
+
+$T$ should be *irreducible*, so any state of the chain has a positive probability of visiting all the other states, meaning that $T$ cannot be broken into smaller tables, and *aperiodic*, so the chain does not get trapped in cycles.
+
+In continuous state spaces, the transition matrix $T$ becomes an integral kernel $K$ and $p(x)$ becomes the corresponding eigenfunction
+
+$$
+ p\bigl(x^{(i)}\bigr) = \int p\bigl(x^{(i-1)}\bigr)\,K\bigl(x^{(i)} \mid x^{(i-1)}\bigr)\,dx^{(i-1)} .
+$$
+
+$K$ is the conditional density of $x^{(i)}$, and it is chosen by the corresponding MCMC algorithm, such as the Metropolis-Hastings algorithm.
+
+In practice, this means that given a prior distribution for the parameters of the examed model (in our case we assume priors for the parameters $t_{sf},\ \tau,\ A_{del}$ from the delayed-$\tau$ model) and the likelihood based on observed data (we have experimental data for the SFR and $M_*$), a MCMC algorithm can calculate the posterior probability of the model and thus approximate the distribution of the parameters.
+From these distributions, their mean values are the values of the parameters and their variance is the error.
+
+To calculate these, the algorithm firstly initializes some chains in the parameter space ($t_{sf},\ \tau,\ A_{del}$) and begins sampling the posterior distribution based on the values of the parameters.
+The first iterations are discarded, since if the sampling begins in a low probability region it can significantly affect the variance of results (burn-in period)[@andrieuIntroductionMCMCMachine2003].
+Eventually, the chains should converge.
+To examine this we use the diagnostics $\hat{R}<1.01$ and ESS\>100.
+The diagnostics indicate if different chains have converged to the same posterior region and if the sample of draws autocorrelates, respectively.[^6]
+
+[^6]: For more information about the metrics used by the Stan software you can visit <https://mc-stan.org/docs/2_36/reference-manual/analysis.html#effective-sample-size.section>
+
 # Data of the Local Cosmological Volume
@@
 
--   **UNGC Catalog** [@karachentsevUPDATEDNEARBYGALAXY2013; @karachentsevSTARFORMATIONPROPERTIES2013]**:** The Updated Nearby Galaxy Catalog (UNGC)[^5] provides a distance-limited sample of galaxies, within 11 Mpc or radial velocities of $V < 600\ km \cdot s^{−1}$.
+-   **UNGC Catalog** [@karachentsevUPDATEDNEARBYGALAXY2013; @karachentsevSTARFORMATIONPROPERTIES2013]**:** The Updated Nearby Galaxy Catalog (UNGC)[^7] provides a distance-limited sample of galaxies, within 11 Mpc or radial velocities of $V < 600\ km \cdot s^{−1}$.
 Selecting galaxies with $D\leq 11$ Mpc, we get a sample of 1321 galaxies.
@@
 
-[^5]: The UNGC tables can be downloaded using the following link: <https://www.sao.ru/lv/lvgdb/introduction.php>. Here, we use the latest update from 17.01.2025.
+[^7]: The UNGC tables can be downloaded using the following link: <https://www.sao.ru/lv/lvgdb/introduction.php>. Here, we use the latest update from 17.01.2025.
 
@@
 -   **Luminosity and Distance Dependence:** The HECATE catalog is more complete for brighter galaxies (with luminosities above $10^{9.5} L_{B,\odot}$) and distances within 33 Mpc, which includes the LV.
-For galaxies with luminosities around $10^{10} L_{B,\odot}$)​, the catalog remains complete up to distances of 100 Mpc.
+For galaxies with luminosities around $10^{10} L_{B,\odot}$, the catalog remains complete up to distances of 100 Mpc.
 -   **Luminosity Density:** The catalog's completeness is also estimated based on the luminosity density in the B-band.
@@
 The incompleteness for ultra-faint galaxies is primarily due to their low surface brightness, making them difficult to detect beyond the Local Group.
-This limitation is particularly significant for studies of dwarf galaxies and the faint end of the galaxy luminosity function
+This limitation is particularly significant for studies of dwarf galaxies and the faint end of the galaxy luminosity function.
 
@@
 
-For the comparison of our data we will use linear regression, accounting for the errors of the observed data, where $R^2$ and the slope of the fitted line should be close to 1[^6].
+For the comparison of our data we will use linear regression, accounting for the errors of the observed data, where $R^2$ and the slope of the fitted line should be close to 1[^8].
 We will also plot the residuals ($y_\text{Regression}-y_\text{observed}$) and if the mean value $\overline{\text{Residuals}}\approx 0$, then the linear regression is considered succesfull.
 
-[^6]: $R^2$ measures the proportion of variance explained by the linear model.
+[^8]: $R^2$ measures the proportion of variance explained by the linear model.
 For a model to be acceptable the $R^2$ should be higher than $80\%$, or close to it if $\overline{\text{Residuals}}\approx 0$
 
-All the results are shown in @sec-regressions, except the comparisons of the Morphological Types and of the SFRs, that need more detailed analysis.[^7]
+All the results are shown in @sec-regressions, except the comparisons of the Morphological Types and of the SFRs, that need more detailed analysis.[^9]
 
-[^7]: The names of the x and y axes are written as they are given in the corresponding catalog, except the ones in decimal logarithmic scale, that are notated appropriately.
+[^9]: The names of the x and y axes are written as they are given in the corresponding catalog, except the ones in decimal logarithmic scale, that are notated appropriately.
 

### 2025-02-09 r_mcmc/_targets.R
corrected likelihood

@@ -100,13 +100,22 @@ tar_plan(
     ),
     variables = "id"
   ),
-
+ # tar_stan_summary(
+ #    sfr_summary_t,
+ #    fit = stan_fit_mcmc_x,
+ #    data = list(
+ #      N = nrow(sfr_data),
+ #      logSFR_total = sfr_data$logSFR_total,
+ #      id_numbers = sfr_data$id_number
+ #    ),
+ #    variables = "logSFR_total"
+ #  ),
   tar_stan_summary(
     sfr_summary,
     fit = stan_fit_mcmc_x,
     data = list(
       N = nrow(sfr_data),
-      logSFR_total = sfr_data$logSFR_total,
+      logSFR_today = sfr_data$logSFR_today,
       id_numbers = sfr_data$id_number
     ),
     variables = "logSFR_today"
@@ -196,6 +205,7 @@ tar_plan(
                              "t_sf" = t_sf_summary,
                              "log_tsf" = log_tsf_summary,
                              "logSFR_today" = sfr_summary,
+                             #"logSFR_total" = sfr_summary_t,
                              "logtau" = logtau_summary)
 
       # Generate the plot

### 2025-02-11 thesis.qmd
small changes

@@
 The way they calculated this inconsistency is by using observatory data for SFR and Stellar Masses from the UNGC catalog (@karachentsevUPDATEDNEARBYGALAXY2013, @karachentsevSTARFORMATIONPROPERTIES2013) for calculating the parameters (the timescale $\tau$ and the normalization constant $A_{del}$) of the model.
-This calculation for the galaxies of the Local Cosmological Volume (LV), allows the investigation of the SFR throughout the life each galaxy and so we can find the expected time of peak of the SFR.
+This calculation for the galaxies of the Local Cosmological Volume (LV), allows the investigation of the SFR throughout the life of each galaxy and so we can find the expected time of peak of the SFR.
 
@@
 -   **Elliptical Galaxies (E):** Ellipsoidal shapes with smooth brightness profiles, containing older stars and minimal interstellar matter.
-Their eccentricity takes values from 0 to 0.7, so we can categorize them even further, form E0 to E7
+Their eccentricity takes values from 0 to 0.7, so we can categorize them even further, from E0 to E7
 
@@
 -   **H**\boldmath$\alpha$ **Emission**: Young, hot, massive stars (O-type stars, \~10 Myr, \~20 $M_\odot$) produce a number of ionizing photons, which they ionize the surrounding hydrogen rich gas.
-The hydorgen undergoes recombination cascades which produce Balmer emission lines of $H\alpha$ (0.6563 $\mu m$) and $H\beta$ (0.4861 $\mu m$).
+The hydrogen undergoes recombination cascades which produce Balmer emission lines of $H\alpha$ (0.6563 $\mu m$) and $H\beta$ (0.4861 $\mu m$).
 Dust can significantly affect observations.
@@
 
-But, because light takes time to cover the distance $d$ between two galaxies, when the light finally reaches as, we will see the observed galaxy, as it was when the light was emitted, and not how it is at this moment.
+But, because light takes time to cover the distance $d$ between two galaxies, when the light finally reaches us, we will see the observed galaxy, as it was when the light was emitted, and not how it is at this moment.
 If we substitute time that it took the light to reach us over the distance, then we arrive at the relation [@longairGalaxyFormation1998]:
@@
 This method is based on the concept of linear approximation, where the function is locally approximated by its tangent line.
-It starts with initial guess of the root and iteratively refines the result using a formula that involves derivative of the function.
+It starts with an initial guess of the root and iteratively refines the result using a formula that involves derivative of the function.
 
-Let $x_n$ be the n-th approximation of the root and $f(x), f'(x)$ the function and the derivative, respectivelly. Then the refined approximation of the root $x_{n+1}$ is given by the formula
+Let $x_n$ be the n-th approximation of the root and $f(x), f'(x)$ the function and the derivative, respectively. Then the refined approximation of the root $x_{n+1}$ is given by the formula
 
@@
 
-A great example of such a chain is the board game snake and ladders.
-The dice has a uniform probabiliy distribution across 6 stages (integers 1 to 6).
+A great example of such a chain is the board game "Snake and Ladders".
+The dice has a uniform probability distribution across 6 stages (integers 1 to 6).
 The players have a position on the board, but their next position on the board is only based on the current position and the random roll of the dice.
@@
 
-Let $x^{(i)}$ be a homoguneous Markov chain[^5] inside a high-dimensional space $X$ of the set of possible configurations of a system and the space on which the posterior is defined, $x^{(i)}\in X = {x_1,x_2,...}$.
+Let $x^{(i)}$ be a homogeneous Markov chain[^5] inside a high-dimensional space $X$ of the set of possible configurations of a system and the space on which the posterior is defined, $x^{(i)}\in X = {x_1,x_2,...}$.
 
@@
 
-In practice, this means that given a prior distribution for the parameters of the examed model (in our case we assume priors for the parameters $t_{sf},\ \tau,\ A_{del}$ from the delayed-$\tau$ model) and the likelihood based on observed data (we have experimental data for the SFR and $M_*$), a MCMC algorithm can calculate the posterior probability of the model and thus approximate the distribution of the parameters.
+In practice, this means that given a prior distribution for the parameters of the examined model (in our case we assume priors for the parameters $t_{sf},\ \tau,\ A_{del}$ from the delayed-$\tau$ model) and the likelihood based on observed data (we have experimental data for the SFR and $M_*$), a MCMC algorithm can calculate the posterior probability of the model and thus approximate the distribution of the parameters.
 From these distributions, their mean values are the values of the parameters and their variance is the error.
@@
 
-We will join the two catalogs, based on the coordinates of the galaxies, so we could assure a bigger and more coplete sample size for our analysis.
+We will join the two catalogs, based on the coordinates of the galaxies, so we could assure a bigger and more complete sample size for our analysis.
 But first we need to undestand them and examine if there are any inconsistances between UNGC and HECATE.

### 2025-02-17 r_mcmc/R/functions.R
tex and cleanup

@@ -3,32 +3,107 @@
 # Function to load and prepare the data
 prepare_data <- function(data_csv) {
   dt <- data_csv %>%
-    mutate(id_number = row_number(),
-           logM_HEC = ifelse(is.na(logM_HEC), 0.822 * K, logM_HEC), # Replace missing logM_HEC with 0.8 * K
-           logM_HEC = ifelse(is.na(logM_HEC), 0.822 * KLum, logM_HEC) # Replace missing logM_HEC with 0.8 * KLum
-           ) %>%
+    mutate(
+      logM_HEC = ifelse(is.na(logM_HEC), 0.822 * K, logM_HEC), # Replace missing logM_HEC with 0.8 * K
+      logM_HEC = ifelse(is.na(logM_HEC), 0.822 * KLum, logM_HEC) # Replace missing logM_HEC with 0.8 * KLum
+    ) %>%
     select(logSFR_total, id_number, logM_HEC) %>%
     filter(
-      #iogSFR_total >=-3,
+      # iogSFR_total >=-3,
       !is.na(logSFR_total),
       !is.nan(logSFR_total),
       is.finite(logSFR_total),
       !is.na(logM_HEC),
       !is.nan(logM_HEC),
       is.finite(logM_HEC)
-      )
+    )
   return(dt)
 }
 
 # Function to define initial values for the Stan model
-init_function <-function(chains, N) {
-  lapply(1:chains, function(i) list(
-    t_sf = rep(13.6, N),
-    #x = rep(3, N),
-    logtau = rep(log10(4), N), # MS galaxies 3.5<tau<4.5
-    logA = rep(5.5, N),
-    tau = rep(4,N),
-    zeta = rep(1.3,N)
-  ))
+init_function <- function(chains, N) {
+  lapply(1:chains, function(i) {
+    list(
+      t_sf = rep(13.6, N),
+      # x = rep(3, N),
+      logtau = rep(log10(4), N), # MS galaxies 3.5<tau<4.5
+      # logA = rep(5.5, N),
+      tau = rep(4, N),
+      zeta = rep(1.3, N)
+    )
+  })
 }
 
+mean_vs_median <- function(summary_data, summary_variables) {
+  ggplot(summary_data, aes(x = mean, y = median)) +
+    geom_point() +
+    geom_abline(intercept = 0, slope = 1, color = "red", linetype = "dashed") +
+    labs(
+      title = paste("Mean vs. Median of", summary_variables),
[…]

### 2025-02-17 r_mcmc/_targets.R

@@ -12,7 +12,7 @@ library(future)
 
 # Set target options:
 tar_option_set(
-  packages = c("readr", "tidyverse","tibble", "stringr", "posterior","bayesplot", "loo","ggplot2", "scales"),
+  packages = c("readr", "tidyverse", "tibble", "stringr", "posterior", "bayesplot", "loo", "ggplot2", "scales", "latex2exp", "ggeasy"),
   # format = "qs", # Optionally set the default storage format. qs is fast.
   #
   # Pipelines that take a long time to run may benefit from
@@ -24,13 +24,13 @@ tar_option_set(
   # which run as local R processes. Each worker launches when there is work
   # to do and exits if 60 seconds pass with no tasks to run.
   #
-  #controller = crew::crew_controller_local(workers = 2)
+  controller = crew::crew_controller_local(workers = 6)
   #
   # Alternatively, if you want workers to run on a high-performance computing
   # cluster, select a controller from the {crew.cluster} package.
   # For the cloud, see plugin packages like {crew.aws.batch}.
   # The following example is a controller for Sun Grid Engine (SGE).
-  # 
+  #
   #   controller = crew.cluster::crew_controller_sge(
   #     # Number of workers that the pipeline can scale up to:
   #     workers = 10,
@@ -53,9 +53,10 @@ tar_source()
 
 # Replace the target list below with your own:
 # Define the pipeline
-#list(
+# list(
 tar_plan(
-  # Step 1: Load and prepare data
+
+  #### Load and prepare data####
   tar_target(
     csv_file_path,
     "filled.csv",
@@ -65,17 +66,26 @@ tar_plan(
     read_data,
     read.csv(csv_file_path)
   ),
+  # add id_number to the data
+  tar_target(
+    id_data,
+    {
+      data <- read_data
+      data$id_number <- 1:nrow(data)
+      data
+    }
+  ),
   tar_target(
     sfr_data,
-    prepare_data(read_data)
+    prepare_data(id_data)
   ),
-  
-  # Step 2: Fit the Stan model
+
+  #### Fit the Stan model####
   tar_stan_mcmc(
     stan_fit,
     stan_files = "x.stan",
-    #stdout = "out.txt",
-    #stderr = "error.txt",
+    # stdout = "out.txt",
+    # stderr = "error.txt",
     data = list(
       N = nrow(sfr_data),
[…]

### 2025-02-17 r_mcmc/R/functions.R
SFR_diff_comparison

@@ -107,3 +107,39 @@ plot_metrics <- function(summary_data, summary_variables, metrics) {
 
   ggsave(sprintf("plots/metrics/%s.png", fname))
 }
+
+
+sfr_comparison_plot <- function(sfr_diff, logSFR_pred, logSFR_total) {
+  default_colors <- scales::hue_pal()(2)
+  # Create a scatter plot of logSFR_pred vs logSFR_total
+  ggplot(sfr_diff, aes(y = logSFR_pred, x = logSFR_total, color = flag)) +
+    geom_point(size = 0.9) +
+    # Error bar for x based on _sigma
+    geom_errorbar(
+      aes(
+        ymin = logSFR_pred - logSFR_pred_sigma,
+        ymax = logSFR_pred + logSFR_pred_sigma
+      ),
+      width = 0.1
+    ) +
+    # legend for keep and discard = "Kept data", "Discarded data"+ the number of points for eac
+    scale_color_manual(
+      values = c("Keep" = default_colors[2], "Discard" = default_colors[1]),
+      breaks = c("Keep", "Discard"),
+      labels = c(
+        paste("Kept data (n =", sum(sfr_diff$flag == "Keep"), ")"),
+        paste("Discarded data (n =", sum(sfr_diff$flag == "Discard"), ")")
+      )
+    ) +
+    geom_abline(intercept = 0, slope = 1, color = "red", linetype = "dashed") +
+    xlim(-8, 1) +
+    labs(
+      title = TeX("Comparison of $log_{10}SFR_{pred}$ and $log_{10}SFR_{obs}$"),
+      x = TeX("$log_{10}\\left[\\frac{SFR_{obs}}{M_o/yr} \\right]$"),
+      y = TeX("$log_{10}\\left[\\frac{SFR_{pred}}{M_o/yr} \\right]$")
+    ) +
+    ggeasy::easy_center_title() +
+    ggeasy::easy_legend_at("top")
+
+  ggsave("plots/sfr_diff_plot.png")
+}

### 2025-02-17 r_mcmc/_targets.R

@@ -308,30 +308,24 @@ tar_plan(
   ),
 
   #### Comparisons####
-  # target to compare sfr_pred and sfr_obs visually
-  tar_target(
-    sfr_comparison,
-    {
-      # Create a scatter plot of logSFR_pred vs logSFR_total
-      ggplot(joined_data, aes(y = logSFR_pred, x = logSFR_total)) +
-        geom_point(size = 0.9) +
-        # Error bar for x based on _sigma
-        geom_errorbar(
-          aes(
-            ymin = logSFR_pred - logSFR_pred_sigma,
-            ymax = logSFR_pred + logSFR_pred_sigma
-          ),
-          width = 0.1
-        ) +
-        geom_abline(intercept = 0, slope = 1, color = "red", linetype = "dashed") +
-        xlim(-8, 1) +
-        labs(
-          title = "Comparison of logSFR_pred and logSFR_total",
-          x = TeX("$log_{10}\\left[\\frac{SFR_{total}}{M_o/yr} \\right]$"),
-          y = TeX("$log_{10}\\left[\\frac{SFR_{pred}}{M_o/yr} \\right]$")
-        )
 
-      ggsave("plots/sfr_comparison.png")
+  # SFRs should be almost equal. Target to flag the rows with big differences
+  tar_target(
+    sfr_diff,
+    {
+      # Flag the rows with big differences
+      joined_data %>%
+        mutate(
+          diff = logSFR_pred - logSFR_total,
+          flag = ifelse(abs(diff) < 2, "Keep", "Discard")
+        ) %>%
+        # return joined with all the columns + the new column SFR_flag
+        select(everything())
     }
-  )
+  ),
+  # plot the all SFRs and color based on flag
+  tar_target(
+    sfr_diff_plot,
+    sfr_comparison_plot(sfr_diff, logSFR_pred, logSFR_total)
+  ),
 )

### 2025-02-17 r_mcmc/R/functions.R
TeX -> expressions+unicode 2299

@@ -135,8 +135,9 @@ sfr_comparison_plot <- function(sfr_diff, logSFR_pred, logSFR_total) {
     xlim(-8, 1) +
     labs(
       title = TeX("Comparison of $log_{10}SFR_{pred}$ and $log_{10}SFR_{obs}$"),
-      x = TeX("$log_{10}\\left[\\frac{SFR_{obs}}{M_o/yr} \\right]$"),
-      y = TeX("$log_{10}\\left[\\frac{SFR_{pred}}{M_o/yr} \\right]$")
+      # x = TeX("$log_{10}\\left[\\frac{SFR_{obs}}{M_\u2299/yr} \\right]$"),
+      x = expression(log[10] * bgroup("[", frac(SFR[obs], M["\u2299"] / yr), "]")),
+      y = expression(log[10] * bgroup("[", frac(SFR[pred], M["\u2299"] / yr), "]"))
     ) +
     ggeasy::easy_center_title() +
     ggeasy::easy_legend_at("top")

### 2025-02-17 r_mcmc/_targets.R

@@ -212,12 +212,12 @@ tar_plan(
     summary_names, # in latex2exp format
     {
       switch(summary_variables,
-        "logSFR_pred" = TeX("$\\log_{10}\\left[\\frac{SFR_{pred}}{M_o/yr}\\right]$"),
-        "log_tsf" = TeX("$log_{10}\\left[\\frac{t_{sf}}{Gyr}\\right]$"),
-        "t_sf" = TeX("$t_{sf}$ [Gyr]"),
-        "tau" = TeX("$\\tau$ [Gyr]"),
-        "logA" = TeX("$\\log\\left[\\frac{A_{del}}{M_o/yr}\\right]$"),
-        "logtau" = TeX("$log_{10}\\left[\\frac{\\tau}{Gyr}\\right]$")
+        logSFR_pred = expression(log[10] * bgroup("[", frac(SFR[obs], M["\u2299"] / yr), "]")),
+        log_tsf = expression(log[10] * bgroup("[", frac(t[sf], "Gyr"), "]")),
+        t_sf = expression(t[sf] * " [Gyr]"),
+        tau = expression(tau * " [Gyr]"),
+        logA = expression(log * bgroup("[", frac(A[del], M["\u2299"] / yr), "]")),
+        logtau = expression(log[10] * bgroup("[", frac(tau, "Gyr"), "]"))
       )
     },
     pattern = map(summary_variables) # Branch over variables
@@ -299,13 +299,7 @@ tar_plan(
       joined_data
     }
   ),
-  tar_target(
-    save_joined_data,
-    {
-      # Save the joined data
-      write.csv(joined_data, "joined_data.csv")
-    }
-  ),
+
 
   #### Comparisons####
 
@@ -328,4 +322,11 @@ tar_plan(
     sfr_diff_plot,
     sfr_comparison_plot(sfr_diff, logSFR_pred, logSFR_total)
   ),
+  tar_target(
+    save_joined_data,
+    {
+      # Save the joined data
+      write.csv(sfr_diff, "joined_data.csv")
+    }
+  )
 )

### 2025-02-18 presentations/presentation_chatzidimitriou.qmd
cleaning main dir

---
title: "Τιτλος"
subtitle: ""
author: "Δημήτρης Παπαχριστόπουλος"
format:
  revealjs:
    theme: moon
    #embed-resources: true
    controls: true
    slide-number: true 
    revealjs-plugin: 
      - PdfExport
    bibliography: My_Library.bib
editor: 
  markdown: 
    wrap: sentence
---

# Περιληψη Εργασιας

-   **Αστρογένεση & Εξέλιξη**: Προσφέρει κρίσιμα στοιχεία για την εξέλιξη γαλαξιών και Σύμπαντος.\
    Το delayed τ-model προσεγγίζει την ιστορία του ρυθμού αστρογένεσης.

-   **Παράμετροι & Ασυμφωνίες**: Υπολογισμός σταθεράς κανονικοποίησης και χρονικής κλίμακας.\
    Προβλέπει μέγιστο ρυθμό αστρογένεσης σε χαμηλότερο redshift από το παρατηρούμενο.

::: notes
Η ιστορία αστρογένεσης ενός γαλαξία παρέχει σημαντικά στοιχεία τόσο για την εξέλιξή του όσο και για την εξέλιξη ολόκληρου του Σύμπαντος.
Το παραμετροποιημένο μοντέλο “delayed τ-model” στοχεύει στην προσεγγιστική περιγραφή της ιστορίας αστρογένεσης των γαλαξιών.
Ο Pavel Kroupa (2023) [@haslbauer2023] υπολογίζει τις παραμέτρους του μοντέλου αυτού, αξιοποιώντας παρατηρησιακά δεδομένα του ρυθμού αστρογένεσης (star formation rate) και εφαρμόζοντας υπολογιστικές μεθόδους για τον προσδιορισμό της σταθεράς κανονικοποίησης και της χαρακτηριστικής χρονικής κλίμακας (time scale).

Η εξαγωγή αυτών των παραμέτρων επιτρέπει τη διερεύνηση του τρόπου με τον οποίο ο ρυθμός αστρογένεσης μεταβάλλεται με την πάροδο του χρόνου για διαφορετικούς γαλαξίες.
Ωστόσο, τα αποτελέσματα δείχνουν ότι το “delayed τ-model” παρουσιάζει ασυμφωνίες με καθιερωμένες κοσμολογικές θεωρίες και παρατηρησιακά δεδομένα, καθώς προβλέπει το μέγιστο του ρυθμού αστρογένεσης σε διαφορετικό κοσμολογικό χρόνο (δηλαδή σε χαμηλότερο redshift) από αυτόν που υποδεικνύουν οι παρατηρήσεις (z ≈ 2).
Επιπλέον, υποδηλώνει ότι το συγκεκριμένο μοντέλο είναι ικανοποιητικό μόνο για αρκετά μεγάλους γαλαξίες.
:::

------------------------------------------------------------------------

-   **Βελτιώσεις & Στόχοι**: Αξιοποίηση νέων δεδομένων και μεθόδου MCMC.\
    Σύγκριση διαφορετικών προσεγγίσεων για ακριβέστερη περιγραφή της αστρογένεσης.

::: notes
Στην παρούσα εργασία θα επιχειρήσουμε να βελτιώσουμε τις προηγούμενες αναλύσεις, χρησιμοποιώντας διαφορετικά σύνολα δεδομένων καθώς και τη μέθοδο Markov Chain Monte Carlo (MCMC).
Στόχος μας είναι να συγκρίνουμε τα αποτελέσματα από διαφορετικές μεθοδολογικές προσεγγίσεις, ώστε να διερευνήσουμε αν οι βελτιώσεις αυτές μπορούν να άρουν τις αναντιστοιχίες και να προσφέρουν μια πιο ακριβή περιγραφή της αστρογένεσης των γαλαξιών.
:::

# Τι ειναι το LCV

-   $D \leq 10 Mpc$
-   Ακτινικές ταχύτητες $V_{lg} \le 500 \, km \cdot s^{-1}$

*Δεν είναι αναγκαίο να ισχύουν και οι δύο προϋποθέσεις ταυτόχρονα.*

## Γιατι LCV?

Θέλουμε γαλαξίες, για τους οποίους έχουμε παρατηρήσεις από την ίδια ηλικία σύμπαντος.

Όσο μεγαλύτερο redshift ($z$), τόσο αλλάζει και ο ρυθμός αστρογένεσης

![](./figure/lily-madau.png){fig-align="center"}

[@madau2014]

# δεδομενα

-   UNGC: Ο καταλογος αποτελείται από **1507** γαλαξίες του LCV
-   HECATE: Ο κατάλογος αποτελείται από **204733** γαλαξίες, σε αποστάσεις 0\<D\<200 Mpc ($z = 0.047$). Εντός του LCV, έχουμε **2901** γαλαξίες

# UNGC

[@karachentsev2013]

[@karachentsevSTARFORMATIONPROPERTIES2013]

## Δεδομενα

| *Data* | *Source/Survey* |
|------------------------------------|------------------------------------|
| Angular diameters, morphological types | POSS-II/ESO/SERC photographic sky surveys |
| Apparent magnitudes in FUV, B, Ks bands | GALEX, 2MASS |
| Hα and H i fluxes | HIPASS, ALFALFA, SAO RAS 6 m telescope |
| Radial velocities | LEDA, HIPASS, ALFALFA |
| Distance estimates | TRGB method (HST), Tully-Fisher relation, Cepheid luminosity |

## Μερικη Πληροτητα

-   Για $M_B^c<-11^m$ ή $A_{26}>1.0 \text{ kpc}$: 40–60% πληρότητα.

## Μη Ανιχνευμενοι Νανοι

-   $10^3–10^4$ υπέρ-αμυδροί νάνοι παραμένουν αόρατοι.

::: notes
Πληρότητα

Η πληρότητα είναι το ποσοστό των αντικείμενων που παρατηρούμε σε σχέση με τον πραγματικό ή θεωρητικό αριθμό που θα έπρεπε να παρατηρούμε, καθώς και τα όρια των τιμών που παρατηρούμε λόγω της ακρίβειας των οργάνων.\
Είναι σημαντικό να το γνωρίζουμε ώστε να αναγνωρίσουμε τυχόν προκαταλήψεις (bias) που μπορεί να προκύψουν.

Μερική Πληρότητα

-   Για $M_B^c < -11^m$ ή $A_{26} > 1.0 \, \text{kpc}$: 40–60% πληρότητα.
-   Στην Τοπική Ομάδα ($D < 1 \, \text{Mpc}$) μόνο οι μισοί γαλαξίες με $M_B^c > -11^m$:\
    → Άρα, πέρα από $\sim 9 \, \text{Mpc}$ χάνονται περισσότεροι από τους μισούς υπέρ-αμυδρούς νάνους.

Μη Ανιχνευμένοι Νάνοι

-   $10^3–10^4$ υπέρ-αμυδροί νάνοι παραμένουν αόρατοι.

Επιφανειακή Φωτεινότητα

-   Παρόμοια κατανομή SB, εκτός από υπέρ-αμυδρούς νάνους ($SB < 31 \, \text{mag/arcsec}^2$), ανιχνεύσιμους μόνο κοντά.
-   Σφάλματα στις αποστάσεις:
    -   Μέθοδος Tully–Fisher: ($\sim 20–25\%$).
    -   Ακριβείς αποστάσεις γνωστές κυρίως εντός ($\sim 5 \, \text{Mpc}$).
-   Μη-Hubble κινήσεις ($\sim 300 \, \text{km/s}$):\
    Οι “μη-Hubble” κινήσεις (peculiar motions) είναι ταχύτητες που δεν οφείλονται στη διαστολή του σύμπαντος (Hubble flow), αλλά σε τοπικές βαρυτικές αλληλεπιδράσεις, όπως έλξεις από κοντινούς γαλαξίες ή ομάδες γαλαξιών.\
    Αυτές οι κινήσεις προσθέτουν αβεβαιότητα στους υπολογισμούς ταχυτήτων και αποστάσεων.\
    Στην προκειμένη περίπτωση, επειδή το όριο της ταχύτητας είναι 600 km/s, οι μη-Hubble κινήσεις καταλαμβάνουν περίπου το μισό από αυτό το όριο, περιορίζοντας την ακρίβεια.\
    Για να μειωθεί η επίδραση αυτών των κινήσεων, η ανάλυση περιορίζεται σε αποστάσεις μικρότερες από 11 Mpc ($D < 11 \, \text{Mpc}$), όπου οι επιδράσεις των μη-Hubble κινήσεων είναι μικρότερες σε σχέση με την κοσμική διαστολή.

Πηγές HI

-   Πηγές HI με χαμηλή γωνιακή ανάλυση:\
    Νέφη υψηλής ταχύτητας κατατάσσονται λανθασμένα ως νάνοι γαλαξίες.
-   Αυτόματες έρευνες:
    -   Αστέρες κατατάσσονται ως γαλαξίες.\
    -   Νέφη κατατάσσονται ως νάνοι.
:::

# HECATE

[@kovlakas2021]

## Δεδομενα

| **Data**                      | **Source**              |
|-------------------------------|-------------------------|
| Positions, sizes, distances   | HyperLEDA, NED          |
| Redshift and size information | HyperLEDA, NED          |
| Distance measurements         | NED-D, CosmicFlows 3.0  |
| Multiwavelength photometry    | IRAS, WISE, SDSS, 2MASS |

## Πληροτητα σε B-band

-   Έως $L_B \sim 10^{9.5} L_{B,\odot}$ για D\<33 Mpc.
-   Ομοίως και για την μάζα (χρήση $K_s$)

## Πληροτητα σε SFR

-   Επηρεάζεται από περιορισμένη κάλυψη WISE/IRAS.
-   IRAS: \>50% κάλυψη για $D\lessapprox 10$ Mpc

# Ενωση των καταλογων

![](compare/quickplots/Magnitude%20(K-band).png){fig-align="center"}

## Κοινα δεδομενα

|         |        |                              |
|---------|--------|------------------------------|
| UNGC    | HECATE | Description                  |
| Dis     | D      | Distance                     |
| RVel    | V      | Heliocentric radial velocity |
| TType   | T      | Hubble Morphology            |
| logKLum | logL_K | K-Luminosity                 |
| mag_B   | BT     | Magnitude (B-band)           |
| Kmag    | K      | Magnitude (K-band)           |
| inc     | INCL   | Inclination (deg)            |
| a26_1   | R1     | Major Axis (arcmin)          |

## Ειδικη περιπτωση τα SFR

![](compare/quickplots/SFR.png){fig-align="center"}

# Τι ειναι το SFR?

Ο ρυθμός αστρογένεσης (SFR = Star Formation Rate) ορίζεται ως το σύνολο της αέριας μάζας ενός γαλαξία που μετατρέπεται σε άστρα σε ένα συγκεκριμένο χρονικό διάστημα.
Συνήθως εκφράζεται σε ηλιακές μάζες ανά έτος ($M_\odot\cdot yr^{-1}$)

$$
\int^{t_{sf}}_0 \text{SFR(t) } dt = \zeta M_*(t_{sf}), \ \zeta \approx 1.3
$$

## Απο που τα παρατηρουμε;

-   Εκτιμάται με διάφορες φωτομετρικές ή φασματικές μεθόδους

-   Διαφορετικές πηγές $\rightarrow$ πληροφορίες για μηχανισμούς εκπομπής και πηγές ακτινοβολίας

$$ 
  SFR_i = K_i \times L_i
$$

::: notes
Εκτιμάται με διάφορες φωτομετρικές ή φασματικές μεθόδους, βάση της λαμπρότητας τουλάχιστον ενός φάσματος φωτός ή την ένταση μιας φασματικής γραμμής.
Οι διαφορετικές λαμπρότητες/εντάσεις έχουν διαφορετικές πηγές οι οποίες μπορούν να μας προσφέρουν διαφορετικές πληροφορίες για τους μηχανισμούς εκπομπής, αλλά και για τις πηγές ακτινοβολίας του εκάστοτε γαλαξία.
:::

## Εμμεσος υπολογισμός SFR

::: incremental
-   **Γραμμή εκπομπής Hα**

-   **Ροή στο μακρινό υπεριώδες (FUV)**

-   **Ροή στο υπέρυθρο (IR)**

-   Ραδιοφωνική συνεχής εκπομπή

-   Εκπομπή ακτίνων Χ
:::

## Πως ενωνουμε τα SFR διαφορετικων πηγων;

### FUV & Hα

$$
SFR_{mean}=\frac{SFR_{FUV}+SFR_{Ha}}{2}
$$

![](figure/log_SFR_FUV_Ha.png){fig-align="center" width="500"}

## Πως το ενωνουμε με το SFR\_{IR};

![](figure/Screenshot%20from%202024-12-07%2021-49-48.png){fig-align="center"}

## FUV → IR

![](compare/quickplots/SFR.png){fig-align="center"}

# Delayed-$τ$ model

$$
SFR_{0,del}=A_{del}\frac{t_{sf}}{\tau^2}e^{-\frac{t_{sf}}{\tau}}
$$

![](figure/Screenshot%20from%202024-12-08%2000-12-51.png){fig-align="center" width="500"}

::: notes
-   **Το delayed-**$\tau$ model περιγράφει την ιστορία σχηματισμού αστέρων (SFH) ενός γαλαξία, υποθέτοντας ότι οι ρυθμοί σχηματισμού αστέρων (SFRs) συνήθως αυξάνονται στην αρχική φάση εξέλιξης του γαλαξία και βαθμιαία μειώνονται.

-   **Speagle et al. (2014):**[@speagle2014] Το SFH γαλαξιών της κύρια ακολουθίας, μπορεί να παραμετροποιηθεί με ακρίβεια βάση αυτού του μοντέλου
:::

------------------------------------------------------------------------
::: note
$SFR_{0,del}=A_{del}\frac{t_{sf}}{\tau^2}e^{-\frac{t_{sf}}{\tau}}= \frac{A_{del}xe^{-x}}{\tau},\text{ where } x=\frac{t_{sf}}{\tau}$

$$
\overline{SFR_{del}}=\frac{1}{t_{sf}}\int^{t_{sf}}_0 \text{SFR(t)}d\text{t}
$$

$$
\frac{\zeta M_*}{t_{sf}} = \frac{A_{del}}{t_{sf}}[1-(1+x)e^{-x}]
$$
:::

## Σταθερα μεγεθη

H τιμή $t_{sf} = 13.6, Gyr$ αποτελεί έναν ισχυρό και συνεπή περιορισμό της εξέλιξης των γαλαξιών, σε πολλές μελέτες.

## Πρώτη προσσέγγιση

-   Σύστημα 2 εξισώσεων και 2 μεταβλητών ($A_{del},\ \tau$), κρατώντας το $t_{sf} = 13.6$ σταθερό.
-   Λύση με υπολογιστικές μεθόδους
    -   Python fsolve
- Θα γίνει για όλους τους γαλαξίες του τελικού μου καταλόγου.

::: notes
```         
Η συνάρτηση fsolve της βιβλιοθήκης SciPy χρησιμοποιεί τη μέθοδο του Powell, η οποία συνδυάζει τις μεθόδους Newton-Raphson και κλίσης, για την εύρεση των ριζών ενός συστήματος μη γραμμικών εξισώσεων
```
:::

## Υπολογισμος $\tau$

![](figure/tau-hist.png)

# Προβληματα μεθοδου

::: incremental
-   $t_{sf} = 13.6\, \text{Gyr}$, αποκλείει την περίπτωση κάποιοι γαλαξίες να έχουν διαφορετικό $t_{sf}$
-   Επιτρέπει την ύπαρξη αρνητικών $\tau$
:::

# Markov Chain Monte Carlo

-   Υπολογίζει και τις 3 μεταβολές ταυτόχρονα
-   Mας δίνει σφάλματα για τα αποτελέσματα
-   Μπορούμε να περιορίσουμε το διάστημα των τιμών
-   Σύστημα 2 εξισώσεων και 2 μεταβλητών ($A_{del},\ \tau$), κρατώντας το $t_{sf} = 13.6$ σταθερό.
::: notes
Αλυσίδες Markov: Σειρές καταστάσεων όπου η επόμενη κατάσταση εξαρτάται μόνο από την τρέχουσα.

Δειγματοληψία Monte Carlo: Χρήση τυχαίων δειγμάτων για την εκτίμηση στατιστικών μεγεθών.

Συνδυασμός MCMC: Δημιουργία αλυσίδων Markov που παράγουν δείγματα από την επιθυμητή κατανομή.
:::

------------------------------------------------------------------------

![](r_mcmc/plots/Hists/logA.png)

------------------------------------------------------------------------

![](r_mcmc/plots/Hists/logtau.png)

------------------------------------------------------------------------

![](r_mcmc/plots/Hists/t_sf.png)

# Μελλοντικα σχεδια

-   Να ολοκληρώσω την ένωση SFR
-   Να τρέξω τον κώδικα με τα καινούργια δεδομένα
-   Να κάνω την τελική σύγκριση των δύο μεθόδων *(1-1 γαλαξία)
-   Να δω πως το $t_{sf}$ επιρεάζεται από την μάζα των γαλαξιών και από τον τύπο του γαλαξία

------------------------------------------------------------------------

### 2025-02-18 mcmc/A_free_20%.py

@@ -1,94 +1,0 @@
-import pymc as pm
-import numpy as np
-import pandas as pd
-from astropy.io import ascii
-from astropy.table import QTable
-import astropy.units as u
-import arviz as az
-from tqdm import tqdm
-import gc
-
-
-# Function to prepare the dataset
-def prepare_data(file_path):
-    # Load your dataset
-    dt = QTable(ascii.read(file_path), masked=True)
-    
-    # Transform to physical units
-    dt["SFR_HEC"] = (10**dt["logSFR_HEC"].value * u.solMass/u.yr).to(u.solMass/u.Gyr)  # SFR in Gyr units
-    dt["logSFR_HEC_Gyr"] = np.log10(dt["logSFR_HEC"].value) # logSFR in Gyr units
-    
-    # Convert to DataFrame and drop missing values
-    data = dt[["logSFR_HEC_Gyr", "logM_HEC"]].to_pandas().dropna()
-    print(data)
-    data.to_csv("test_galaxies.csv")
-    del dt
-    gc.collect()
-    return data
-
-# Function to run MCMC for a given galaxy
-def run_mcmc_for_galaxy(row):
-    with pm.Model() as model:
-        # Priors for t_today, logtau, and logA in log space
-        t_today = pm.Uniform('t_today', lower=10, upper=15)
-        logtau = pm.Uniform('logtau', lower=-3, upper=3)  # tau in log 
-        logA = pm.Uniform('logA', lower=-3, upper=12)  # log scale for A
-        # Convert tau and  to linear scale
-
-        tau = 10**logtau  # tau in linear scale
-        # Assume Mtot and logSFR_today_observed come from the sample
-        Mtot = row['logM_HEC']  # M_HEC is already in solMass
-        logSFR_today_observed = row['logSFR_HEC_Gyr']  # logSFR in Gyr units
-
-        # Use the corrected logarithmic form of SFR
-        logSFR_today = logA + np.log10(t_today) - 2 * np.log10(tau) - (t_today / tau) * np.log10(np.e)
-
-        # Likelihood (assuming Gaussian errors on log(SFR))
-        sigma = 0.1  # Example uncertainty in log(SFR)
-        SFR_likelihood = pm.Normal('SFR_likelihood', mu=logSFR_today, sigma=sigma, observed=logSFR_today_observed)
-
-        # Sampling using NUTS
-        try:
-            trace = pm.sample(2000, tune=2000, target_accept=0.95, init='jitter+adapt_diag',
-                              chains = 4, cores= 6,
[…]

### 2025-02-18 notes/final.py

@@ -724,9 +724,7 @@ dc["A_n"] = np.where(np.isinf(dc["A_n"]), np.nan, dc["A_n"])
 
 
 # #+RESULTS:
-# : /home/dp/.local/lib/python3.10/site-packages/astropy/units/quantity.py:671: RuntimeWarning:
-# :
-# : divide by zero encountered in divide
+# : /home/dp/.local/lib/python3.10/site-packages/astropy/units/quantity.py:671: RuntimeWarning: divide by zero encountered in divide
 
 
 # [[file:paper.org::*Newton][Newton:2]]
@@ -775,9 +773,7 @@ dc["A_f"] = MaskedColumn(A, name = "A", unit = u.solMass)
 
 
 # #+RESULTS:
-# : /tmp/babel-U1HWkT/python-cY3cqT:23: RuntimeWarning:
-# :
-# : The iteration is not making good progress, as measured by the
+# : /tmp/babel-etXArC/python-M39CsK:23: RuntimeWarning: The iteration is not making good progress, as measured by the
 # :   improvement from the last ten iterations.
 
 
@@ -938,10 +934,7 @@ print(dc[["tau"]].info("stats"))
 
 
 # #+RESULTS:
-# : /home/dp/.local/lib/python3.10/site-packages/astropy/units/quantity.py:671: RuntimeWarning:
-# :
-# : overflow encountered in divide
-# :
+# : /home/dp/.local/lib/python3.10/site-packages/astropy/units/quantity.py:671: RuntimeWarning: overflow encountered in divide
 # : <QTable length=518>
 # : name     mean         std         min          max     n_bad
 # : ---- ------------ ----------- ------------ ----------- -----
@@ -987,8 +980,15 @@ fig.show()
 
 
 # #+RESULTS:
-# : Gtk-[1;32mMessage[0m: [34m18:40:56.073[0m: Failed to load module "canberra-gtk-module"
-# : Gtk-[1;32mMessage[0m: [34m18:40:56.077[0m: Failed to load module "canberra-gtk-module"
+# : Gtk-[1;32mMessage[0m: [34m00:08:33.411[0m: Failed to load module "canberra-gtk-module"
+# : Gtk-[1;32mMessage[0m: [34m00:08:33.414[0m: Failed to load module "canberra-gtk-module"
+# : Gtk-[1;32mMessage[0m: [34m00:08:34.657[0m: Failed to load module "canberra-gtk-module"
[…]

### 2025-02-18 NR/NR_sfr.py
NR and fsolve scripts

@@ -1,0 +1,97 @@
+import numpy as np
+from scipy import optimize
+import matplotlib.pyplot as plt
+import astropy.units as u
+from astropy.table import QTable
+from joblib import Parallel, delayed
+
+# Read the data
+dt = QTable.read("../tables/filled.ecsv")
+
+# Define constants
+zeta = 1.3  # Mass-loss through stellar evolution
+t_sf = 13.6 * u.Gyr  # Star formation timescale
+#tsf = t_sf.to(u.yr).value  # Convert t_sf to years
+tsf = t_sf.value  # Convert t_sf to years
+
+# Initialize arrays (same as original)
+x_n = np.empty(len(dt))
+A_n = np.empty(len(dt))
+
+# Extract SFR and M arrays
+SFR_arr = np.array(dt["SFR_total"])
+M_arr = np.array(dt["logM_total"])
+
+
+# Function to solve for x using the Newton-Raphson method
+def solve_x_n(i):
+    SFR, M = SFR_arr[i], M_arr[i]
+    if np.isnan(SFR) or np.isnan(M):
+        return np.nan  # Handle NaNs early
+    try:
+    # Define the function and its derivative for the Newton-Raphson method
+        def f(x):
+            return (-SFR + zeta * M * x**2 / (np.exp(x) - 1 - x) / tsf)
+
+        def f_prime(x):
+            return -zeta * M * (x * (np.exp(x) * (x - 2) + x + 2) / (np.exp(x) - x - 1)**2) / t_sf.value
+        sol = optimize.root_scalar(f, bracket=[0, 4], x0=3.4, fprime=f_prime, method="newton")
+        return sol.root if sol.converged else np.nan
+    except ValueError:
+        return np.nan
+
+# Run the solver in parallel
+num_cores = 12  # Use all CPU cores
+x_n[:] = Parallel(n_jobs=num_cores)(delayed(solve_x_n)(i) for i in range(len(dt)))
+
+# Compute A_n for all valid x_n (same as original, but vectorized)
+valid_x = ~np.isnan(x_n)
+A_n[valid_x] = SFR_arr[valid_x] * tsf * np.exp(x_n[valid_x]) / (x_n[valid_x]**2)
+A_n[~valid_x] = np.nan  # Keep NaNs consistent
+
+# Add results to the DataFrame (same as original)
+dt["x_n"] = x_n
[…]

### 2025-02-18 NR/fsolve_SFR.py

@@ -1,0 +1,128 @@
+import numpy as np
+from scipy import optimize
+import matplotlib.pyplot as plt
+import astropy.units as u
+from astropy.table import QTable, MaskedColumn
+from joblib import Parallel, delayed
+from scipy.optimize import fsolve
+
+# Read the data
+dt = QTable.read("../tables/filled.ecsv")
+
+t_sf = 13.6 * u.Gyr
+zeta = 1.3
+
+
+dt["av_SFR_theor"] = 1.3 * dt["logM_total"].value * u.M_sun / t_sf.to(u.yr)
+
+dt["SFR_ratio"] = dt["av_SFR_theor"].value / dt["SFR_total"].value
+
+#log10 of ratio
+dt["logSFR_ratio"] = np.log10(dt["SFR_ratio"].value)
+
+
+ratio_array = np.array(dt["SFR_ratio"])
+sfr_array = np.array(dt["SFR_total"])
+mass_array = np.array(dt["logM_total"])
+av_array = np.array(dt["av_SFR_theor"])
+
+#tsf = t_sf.to(u.yr).value
+tsf = t_sf.value
+
+x_f = np.ma.empty(len(dt))
+A_f = np.ma.empty(len(dt))
+
+
+# Function to solve for x using fsolve
+def solve_x_f(i):
+    SFR, M = sfr_array[i], mass_array[i]
+    
+    # Handle NaNs early
+    if np.isnan(SFR) or np.isnan(M):
+        return np.nan, np.nan  
+    
+    try:
+        ratio = ratio_array[i]
+        sfr = SFR
+
+        def sfrx(z):
+            x, A = z
+            f = np.zeros(2)
+            f[0] = ratio - (np.exp(x) - x - 1) / x**2
+            f[1] = sfr*1e9 - A * x ** 2 * np.exp(-x) / tsf
+            return f
+
+        # Solve the equation
+        z = fsolve(sfrx, [3, 1e+8])
+        return z[0], z[1]   # Scale A back to its correct unit
+
+    except (ValueError, RuntimeError):
+        return np.nan, np.nan  # Ensure robustness
+
+
+# Run the solver in parallel
+num_cores = 12  # Use all CPU cores
+results = Parallel(n_jobs=num_cores)(delayed(solve_x_f)(i) for i in range(len(dt)))
+
+# Unpack results into arrays
[…]

### 2025-02-18 NR/fsolve_no_parallell.py

@@ -1,0 +1,108 @@
+import numpy as np
+from scipy import optimize
+import matplotlib.pyplot as plt
+import astropy.units as u
+from astropy.table import qtable
+from joblib import parallel, delayed
+from scipy.optimize import fsolve
+
+# read the data
+dt = qtable.read("../tables/filled.ecsv")
+
+# define constants
+zeta = 1.3  # mass-loss through stellar evolution
+t_sf = 13.6 * u.gyr  # star formation timescale
+tsf = t_sf.to(u.yr).value  # convert t_sf to years
+
+# initialize arrays (same as original)
+x = np.empty(len(dt))
+a = np.empty(len(dt))
+
+# extract sfr and m arrays
+sfr_arr = np.array(dt["sfr_total"])
+m_arr = np.array(dt["logm_total"])
+av_sfr = zeta * m_arr / tsf
+ratio_sfr = av_sfr / sfr_arr
+
+
+# function to solve for x using fsolve
+def solve_x_f(i):
+    sfr, m = sfr_arr[i], m_arr[i]
+    
+    # handle nans early
+    if np.isnan(sfr) or np.isnan(m):
+        return np.nan, np.nan  
+    
+    try:
+        ratio = ratio_sfr[i]
+        sfr = sfr_arr[i]
+
+        def sfrx(z):
+            x, a = z
+            f = np.zeros(2)
+            f[0] = ratio - (np.exp(x) - x - 1) / x**2
+            f[1] = sfr - a * 10**(-9) * x * tsf * np.exp(-x) / x
+            return f
+
+        # solve the equation
+        z = fsolve(sfrx, [3, 1e+8])
+        return z[0], z[1] * 10**9  # scale a back to its correct unit
+
+    except (valueerror, runtimeerror):
+        return np.nan, np.nan  # ensure robustness
+
+
+# run the solver in parallel
+num_cores = 12  # use all cpu cores
+results = parallel(n_jobs=num_cores)(delayed(solve_x_f)(i) for i in range(len(dt)))
+
+# unpack results into arrays
+x_f[:], a_f[:] = np.array(results).t  # transpose to separate x_f and a_f
+
+dt["x_f"] = x_f
+dt["a_f"] = a_f
+dt["tau"] = t_sf/dt["x_f"]
+
+# print stats (same as original)
+print(dt["x_f", "a_f", "tau"].info("stats"))
+
[…]

### 2025-03-01 NR/NR_sfr.py
norm tau
turned tau from uniform to normal prior in stan

@@ -1,9 +1,9 @@
-import numpy as np
-from scipy import optimize
-import matplotlib.pyplot as plt
 import astropy.units as u
+import matplotlib.pyplot as plt
+import numpy as np
 from astropy.table import QTable
 from joblib import Parallel, delayed
+from scipy import optimize
 
 # Read the data
 dt = QTable.read("../tables/filled.ecsv")

### 2025-03-03 NR/NR_sfr copy.py
nr logM to linear

@@ -1,0 +1,108 @@
+import numpy as np
+from scipy import optimize
+import matplotlib.pyplot as plt
+import astropy.units as u
+from astropy.table import QTable
+from joblib import Parallel, delayed
+
+#set working directory
+import os.path
+os.chdir("/home/dp/Documents/Research_paper_SFR/NR/")  # Replace with your directory
+
+# Read the data
+
+dt = QTable.read("filled.ecsv")
+# Define constants
+zeta = 1.3  # Mass-loss through stellar evolution
+t_sf = 13.6 * u.Gyr  # Star formation timescale
+tsf = t_sf.to(u.yr).value  # Convert t_sf to years
+#tsf = t_sf.value  # Convert t_sf to years
+
+# Initialize arrays (same as original)
+x_n = np.empty(len(dt))
+A_n = np.empty(len(dt))
+
+# Extract SFR and M arrays
+SFR_arr = np.array(dt["SFR_total"])
+M_arr = np.array(dt["M_total"])
+
+K = SFR_arr*tsf/(zeta*M_arr)
+k_arr=1/K
+# Function to solve for x using the Newton-Raphson method
+def solve_x_n(i):
+    SFR, M, k = SFR_arr[i], M_arr[i], k_arr[i]
+    if np.isnan(SFR) or np.isnan(M) or np.isnan(k):
+        return np.nan  # Handle NaNs early
+    try:
+    # Define the function and its derivative for the Newton-Raphson method
+        def f(x):
+            return (k*x**2-np.exp(x)+x+1)
+
+        def f_prime(x):
+            return (2*k*x -np.exp(x)+1)
+        sol = optimize.root_scalar(f, x0=2, fprime=f_prime, method="newton")
+        return sol.root if sol.converged else np.nan
+    except ValueError:
+        return np.nan
+
+# Run the solver in parallel
+num_cores = 4  # Use all CPU cores
+x_n[:] = Parallel(n_jobs=num_cores)(delayed(solve_x_n)(i) for i in range(len(dt)))
+
+# Compute A_n for all valid x_n (same as original, but vectorized)
+valid_x = ~np.isnan(x_n)
+A_n[valid_x] = SFR_arr[valid_x] * tsf * np.exp(x_n[valid_x]) / (x_n[valid_x]**2)
+A_n[~valid_x] = np.nan  # Keep NaNs consistent
[…]

### 2025-03-03 NR/NR_sfr.py

@@ -5,9 +5,13 @@ from astropy.table import QTable
 from joblib import Parallel, delayed
 from scipy import optimize
 
-# Read the data
-dt = QTable.read("../tables/filled.ecsv")
+#set working directory
+import os.path
+os.chdir("/home/dp/Documents/Research_paper_SFR/NR/")  # Replace with your directory
 
+# Read the data
+
+dt = QTable.read("filled.ecsv")
 # Define constants
 zeta = 1.3  # Mass-loss through stellar evolution
 t_sf = 13.6 * u.Gyr  # Star formation timescale

### 2025-03-03 NR/fsolve_SFR.py

@@ -1,128 +1,0 @@
-import numpy as np
-from scipy import optimize
-import matplotlib.pyplot as plt
-import astropy.units as u
-from astropy.table import QTable, MaskedColumn
-from joblib import Parallel, delayed
-from scipy.optimize import fsolve
-
-# Read the data
-dt = QTable.read("../tables/filled.ecsv")
-
-t_sf = 13.6 * u.Gyr
-zeta = 1.3
-
-
-dt["av_SFR_theor"] = 1.3 * dt["logM_total"].value * u.M_sun / t_sf.to(u.yr)
-
-dt["SFR_ratio"] = dt["av_SFR_theor"].value / dt["SFR_total"].value
-
-#log10 of ratio
-dt["logSFR_ratio"] = np.log10(dt["SFR_ratio"].value)
-
-
-ratio_array = np.array(dt["SFR_ratio"])
-sfr_array = np.array(dt["SFR_total"])
-mass_array = np.array(dt["logM_total"])
-av_array = np.array(dt["av_SFR_theor"])
-
-#tsf = t_sf.to(u.yr).value
-tsf = t_sf.value
-
-x_f = np.ma.empty(len(dt))
-A_f = np.ma.empty(len(dt))
-
-
-# Function to solve for x using fsolve
-def solve_x_f(i):
-    SFR, M = sfr_array[i], mass_array[i]
-    
-    # Handle NaNs early
-    if np.isnan(SFR) or np.isnan(M):
-        return np.nan, np.nan  
-    
-    try:
-        ratio = ratio_array[i]
-        sfr = SFR
-
-        def sfrx(z):
-            x, A = z
-            f = np.zeros(2)
-            f[0] = ratio - (np.exp(x) - x - 1) / x**2
-            f[1] = sfr*1e9 - A * x ** 2 * np.exp(-x) / tsf
-            return f
-
-        # Solve the equation
-        z = fsolve(sfrx, [3, 1e+8])
-        return z[0], z[1]   # Scale A back to its correct unit
-
-    except (ValueError, RuntimeError):
-        return np.nan, np.nan  # Ensure robustness
-
-
-# Run the solver in parallel
-num_cores = 12  # Use all CPU cores
-results = Parallel(n_jobs=num_cores)(delayed(solve_x_f)(i) for i in range(len(dt)))
-
-# Unpack results into arrays
[…]

### 2025-03-03 NR/fsolve_no_parallell.py

@@ -1,108 +1,0 @@
-import numpy as np
-from scipy import optimize
-import matplotlib.pyplot as plt
-import astropy.units as u
-from astropy.table import qtable
-from joblib import parallel, delayed
-from scipy.optimize import fsolve
-
-# read the data
-dt = qtable.read("../tables/filled.ecsv")
-
-# define constants
-zeta = 1.3  # mass-loss through stellar evolution
-t_sf = 13.6 * u.gyr  # star formation timescale
-tsf = t_sf.to(u.yr).value  # convert t_sf to years
-
-# initialize arrays (same as original)
-x = np.empty(len(dt))
-a = np.empty(len(dt))
-
-# extract sfr and m arrays
-sfr_arr = np.array(dt["sfr_total"])
-m_arr = np.array(dt["logm_total"])
-av_sfr = zeta * m_arr / tsf
-ratio_sfr = av_sfr / sfr_arr
-
-
-# function to solve for x using fsolve
-def solve_x_f(i):
-    sfr, m = sfr_arr[i], m_arr[i]
-    
-    # handle nans early
-    if np.isnan(sfr) or np.isnan(m):
-        return np.nan, np.nan  
-    
-    try:
-        ratio = ratio_sfr[i]
-        sfr = sfr_arr[i]
-
-        def sfrx(z):
-            x, a = z
-            f = np.zeros(2)
-            f[0] = ratio - (np.exp(x) - x - 1) / x**2
-            f[1] = sfr - a * 10**(-9) * x * tsf * np.exp(-x) / x
-            return f
-
-        # solve the equation
-        z = fsolve(sfrx, [3, 1e+8])
-        return z[0], z[1] * 10**9  # scale a back to its correct unit
-
-    except (valueerror, runtimeerror):
-        return np.nan, np.nan  # ensure robustness
-
-
-# run the solver in parallel
-num_cores = 12  # use all cpu cores
-results = parallel(n_jobs=num_cores)(delayed(solve_x_f)(i) for i in range(len(dt)))
-
-# unpack results into arrays
-x_f[:], a_f[:] = np.array(results).t  # transpose to separate x_f and a_f
-
-dt["x_f"] = x_f
-dt["a_f"] = a_f
-dt["tau"] = t_sf/dt["x_f"]
-
-# print stats (same as original)
-print(dt["x_f", "a_f", "tau"].info("stats"))
-
[…]

### 2025-03-03 thesis.qmd
start calc chapter

@@
   warning: false
-editor: visual
+#editor: visual
 
@@
 
-![Plot showing the linear relation $\log_{10}\text{SFR}_{FUV} = \log_{10}\text{SFR}_{H\alpha}$, as well as their distributions, based on the data from UNGC](figure/log_SFR_FUV_Ha.png){#fig-SFR-Ha-FUV fig-align="center" width="500"}
+![Plot showing the linear relation $\log\text{SFR}_{FUV} = \log\text{SFR}_{H\alpha}$, as well as their distributions, based on the data from UNGC](figure/log_SFR_FUV_Ha.png){#fig-SFR-Ha-FUV fig-align="center" width="500"}
 
@@
 \overline{\text{SFR}_\text{del}} = \frac{\zeta M_*}{t_sf}
-$$ {#eq-averaged-SFR-M*}
+$$ {#eq-averaged-SFR-M}
 
@@
 
+Using the merged catalog, we can use the SFR and $M_*$ data to calculate the parameters for the delayed-$tau$ model, for each individual galaxy.
+The parameters are going to be calculated using two different computational methods.
+
+Firstly, using the Newton-Ramphson algorithm, the parameters $\tau$ and $A_{del}$ can be calculated from the equations @eq-delayed-current and @eq-delayed-current-averaged, assuming the same $t_{sf} = 13.6$ Gyr for every galaxy, meaning that all the galaxies start the star formation proccess around the same time, 13.6 Gyr ago, or 0.2 Gyr after the Big Bang.
+This is the same method used in @haslbauerCosmologicalStarFormation2023, but instead of using only the SFR from UNGC and adopting a mass-to-light ratio of 0.6 from the $L_K$, we use the merged catalog.
+
+The second method for the calclulation of the parameters is the MCMC method. Using the logarithmic form of the model
+
+$$
+\log(\text{SFR})= \log(A_{del})+\log(x)-\log(\tau)-x\cdot\log e,\text{ where } x=\frac{t_sf}{\tau},
+$${#eq-log-SFR}
+
+and by combining @eq-delayed-current-averaged and @eq-averaged-SFR-M:
+
+$$
+A_{del}=\frac{\zeta M_*}{1-(1+x)e^{-x}},
+$${#eq-A}
+
+we can create a MCMC model to calculate the parameters, with the priors:
+
+- $\tau \sim \text{normal(mean=4 Gyr, }\sigma = 1 )$, within the limits $[1,20]$ Gyr,
+- $t_{sf}\sim \text{uniform(lower bound = 1 Gyr, upper bound = 13.8 Gyr)}$,
+- $\zeta \sim \text{normal(mean=1.3, }\sigma = 0.01)$, within the limits $[1,2]$,
+
+and the likelihood:
+
+- $\log(\text{SFR}_{obs}) \sim \text{normal}\left(\log(\text{SFR}_\text{MCMC}), \sigma = 0.1\right)$
+
 ## According to pre-existing bibliography

### 2025-03-03 NR/NR_sfr copy.py
M->lin&sSFR in list

@@ -1,108 +1,0 @@
-import numpy as np
-from scipy import optimize
-import matplotlib.pyplot as plt
-import astropy.units as u
-from astropy.table import QTable
-from joblib import Parallel, delayed
-
-#set working directory
-import os.path
-os.chdir("/home/dp/Documents/Research_paper_SFR/NR/")  # Replace with your directory
-
-# Read the data
-
-dt = QTable.read("filled.ecsv")
-# Define constants
-zeta = 1.3  # Mass-loss through stellar evolution
-t_sf = 13.6 * u.Gyr  # Star formation timescale
-tsf = t_sf.to(u.yr).value  # Convert t_sf to years
-#tsf = t_sf.value  # Convert t_sf to years
-
-# Initialize arrays (same as original)
-x_n = np.empty(len(dt))
-A_n = np.empty(len(dt))
-
-# Extract SFR and M arrays
-SFR_arr = np.array(dt["SFR_total"])
-M_arr = np.array(dt["M_total"])
-
-K = SFR_arr*tsf/(zeta*M_arr)
-k_arr=1/K
-# Function to solve for x using the Newton-Raphson method
-def solve_x_n(i):
-    SFR, M, k = SFR_arr[i], M_arr[i], k_arr[i]
-    if np.isnan(SFR) or np.isnan(M) or np.isnan(k):
-        return np.nan  # Handle NaNs early
-    try:
-    # Define the function and its derivative for the Newton-Raphson method
-        def f(x):
-            return (k*x**2-np.exp(x)+x+1)
-
-        def f_prime(x):
-            return (2*k*x -np.exp(x)+1)
-        sol = optimize.root_scalar(f, x0=2, fprime=f_prime, method="newton")
-        return sol.root if sol.converged else np.nan
-    except ValueError:
-        return np.nan
-
-# Run the solver in parallel
-num_cores = 4  # Use all CPU cores
-x_n[:] = Parallel(n_jobs=num_cores)(delayed(solve_x_n)(i) for i in range(len(dt)))
-
-# Compute A_n for all valid x_n (same as original, but vectorized)
-valid_x = ~np.isnan(x_n)
-A_n[valid_x] = SFR_arr[valid_x] * tsf * np.exp(x_n[valid_x]) / (x_n[valid_x]**2)
-A_n[~valid_x] = np.nan  # Keep NaNs consistent
[…]

### 2025-03-03 NR/NR_sfr.py

@@ -1,22 +1,22 @@
-import astropy.units as u
-import matplotlib.pyplot as plt
 import numpy as np
+from scipy import optimize
+import matplotlib.pyplot as plt
+import astropy.units as u
 from astropy.table import QTable
 from joblib import Parallel, delayed
-from scipy import optimize
 
 #set working directory
-import os.path
-os.chdir("/home/dp/Documents/Research_paper_SFR/NR/")  # Replace with your directory
+# import os.path
+# os.chdir("/home/dp/Documents/Research_paper_SFR/NR/")  # Replace with your directory
 
 # Read the data
 
-dt = QTable.read("filled.ecsv")
+dt = QTable.read("./tables/filled.ecsv")
 # Define constants
 zeta = 1.3  # Mass-loss through stellar evolution
 t_sf = 13.6 * u.Gyr  # Star formation timescale
-#tsf = t_sf.to(u.yr).value  # Convert t_sf to years
-tsf = t_sf.value  # Convert t_sf to years
+tsf = t_sf.to(u.yr).value  # Convert t_sf to years
+#tsf = t_sf.value  # Convert t_sf to years
 
 # Initialize arrays (same as original)
 x_n = np.empty(len(dt))
@@ -24,28 +24,29 @@ A_n = np.empty(len(dt))
 
 # Extract SFR and M arrays
 SFR_arr = np.array(dt["SFR_total"])
-M_arr = np.array(dt["logM_total"])
+M_arr = np.array(dt["M_total"])
 
-
+K = SFR_arr*tsf/(zeta*M_arr)
+k_arr=1/K
 # Function to solve for x using the Newton-Raphson method
 def solve_x_n(i):
-    SFR, M = SFR_arr[i], M_arr[i]
-    if np.isnan(SFR) or np.isnan(M):
+    SFR, M, k = SFR_arr[i], M_arr[i], k_arr[i]
+    if np.isnan(SFR) or np.isnan(M) or np.isnan(k):
         return np.nan  # Handle NaNs early
     try:
     # Define the function and its derivative for the Newton-Raphson method
         def f(x):
-            return (-SFR + zeta * M * x**2 / (np.exp(x) - 1 - x) / tsf)
+            return (k*x**2-np.exp(x)+x+1)
 
         def f_prime(x):
[…]

### 2025-03-03 tables/column_join.sh

@@ -13,6 +13,7 @@ stilts tpipe \
   cmd='addcol -units "Msol/yr" -desc "Total SFR in linear scale" SFR_total "exp10(logSFR_total)"'\
   cmd='addcol -units "log(Msol)" -desc "" logM_total "NULL_logM_HEC ? log10(0.82)+merge_logKLum: logM_HEC"'\
   cmd='addcol -units "Msol" -desc "Total M_* in linear scale" M_total "exp10(logM_total)"'\
+  cmd='addcol -units "1/yr" -desc "Specific SFR" sSFR "SFR_total/M_total"'\
   cmd='addcol -desc "ID column" ID "Index"'\
 
 

### 2025-03-04 thesis.qmd
NR method param.

@@
 
-Using the merged catalog, we can use the SFR and $M_*$ data to calculate the parameters for the delayed-$tau$ model, for each individual galaxy.
+Using the merged catalog, we can use the SFR and $M_*$ data to calculate the parameters for the delayed-$\tau$ model, for each individual galaxy.
 The parameters are going to be calculated using two different computational methods.
 
-Firstly, using the Newton-Ramphson algorithm, the parameters $\tau$ and $A_{del}$ can be calculated from the equations @eq-delayed-current and @eq-delayed-current-averaged, assuming the same $t_{sf} = 13.6$ Gyr for every galaxy, meaning that all the galaxies start the star formation proccess around the same time, 13.6 Gyr ago, or 0.2 Gyr after the Big Bang.
-This is the same method used in @haslbauerCosmologicalStarFormation2023, but instead of using only the SFR from UNGC and adopting a mass-to-light ratio of 0.6 from the $L_K$, we use the merged catalog.
+Firstly, using the Newton-Ramphson algorithm, the parameters $\tau$ and $A_{del}$ can be calculated from the equations @eq-delayed-current and @eq-delayed-current-averaged, assuming the same $t_{sf} = 13.6$ Gyr for every galaxy, meaning that all the galaxies start the star formation process around the same time, 13.6 Gyr ago, or $t_\text{start} = 0.2$ Gyr after the Big Bang.
+Solving @eq-averaged-SFR-M and @eq-delayed-current-averaged , for $A_{del}$:
+
+$$
+A_{del}=\frac{\zeta M_*}{1-(1+x)e^{-x}}, \text{ where } x=\frac{t_sf}{\tau},
+$$ {#eq-A}
+
+and substituting in the model, the delayed-$\tau$ model takes the form:
+
+$$
+\text{SFR} = \frac{\zeta}{t_{sf}}M_*\frac{x^2}{e^x-x-1} \Leftrightarrow\text{sSFR}\frac{t_{sf}}{\zeta} = \frac{x^2}{e^x-x-1}, \text{ where sSFR}\equiv\frac{\text{SFR}}{M_*}\left[\frac{1}{yr}\right].
+$$
+
+The specific-SFR (sSFR) describes the rate of change of the stellar mass in a galaxy. Assuming a function $g(x)$ and its derivative $g'(x)$ for the Newton-Raphson algorithm:
+
+$$
+g(x) = \frac{\zeta}{t_{sf}\cdot sSFR}\cdot x^2-e^x+x+1\Leftrightarrow g'(x) = \frac{\zeta}{t_{sf}\cdot sSFR}\cdot 2x-e^x+1
+$$
+
+the root $x_0\Leftrightarrow g(x_0) = 0$, can be found, for each galaxy.
+From @eq-A we can calculate the normilization constant of the galaxies, as well as their charachteristic timescales $\tau = t_{sf}\cdot x$.
+
+![Alt text](NR/tau_A_double_plot.png){#fig-A-tau}
+
+In @fig-A-tau, two shapes are prominent.
+One in the range $\frac{A_{del}}{M_\odot}\in[10^{15},10^{29}]$ and one in the range $\frac{A_{del}}{M_\odot}\in[0,10^{15}]$.
+The second range does not have any negative $\tau$ values and $\overline{\tau} = 16.2$ Gyr, while the first range has 153 negative $\tau$ values and $\overline{\tau} = -2.7\cdot 10^9$ Gyr.
+It is obvious, from @fig-A-M, that the first range is subject to the instabilities of the method.
+
+From @eq-A, we expect a good linear correlation between $A_{del}$ and $M_*$ of a given galaxy, where the variance of the linear regression comes from $\frac{\zeta}{1-(x+1)e^{-x}}$.
+So, for the expected values of $x$, $2.7<x<3.4$ [@kroupaConstraintsStarFormation2020], and even for bigger $x$, there should not be a significant variance, since $\lim_{x\rightarrow\infty}\frac{\zeta}{1-(x+1)e^{-x}}=\zeta\approx1.3$.
+However, for $x\rightarrow 0$, the algorithm is not able to converge since $\lim_{x\rightarrow 0}\frac{\zeta}{1-(x+1)e^{-x}}=\infty$, and the linear regression of $A_{del}-M_*$ can not be successful, as it can be seen from @fig-A-M.
+
+![](/NR/A-M_*-c_x.png){#fig-A-M}
+
+Since convergence can not occur for $x\ll 1$, this method should not be used for galaxies in the begging phases of their star formation [^10].
+If the assumption, $t_{sf}=13.6$ Gyr for all the galaxies is correct, then an inconstancy in the plot $A_{del}-\text{sSFR}$ should only be observed, for higher values of the sSFR, since, according to the delayed- $\tau$ model, higher sSFR values indicate a rising SFR, while lower SFR values indicate that the bulk of $M_*$ is already produced and the galaxy is in the declining SFR phase.
+However, as seen from @fig-A-sSFR, this inconsistency occurs in galaxies for both high and low sSFR's, meaning that the the model has convergence issues both for slow rising SFR and quenching galaxies, indicating an intrinsic problem with this approach.
+
+[^10]: For $x=1$ is the peak of the SFR, $x<1$ is the the rising phase and for $x>1$ the SFR declines exponentially ( @eq-delayed-current ).
+
+![Alt text](NR/A-sSFR.png){#fig-A-sSFR}
 
@@
 $$
-\log(\text{SFR})= \log(A_{del})+\log(x)-\log(\tau)-x\cdot\log e,\text{ where } x=\frac{t_sf}{\tau},
-$${#eq-log-SFR}
-
-and by combining @eq-delayed-current-averaged and @eq-averaged-SFR-M:
-
-$$
-A_{del}=\frac{\zeta M_*}{1-(1+x)e^{-x}},
-$${#eq-A}
+\log(\text{SFR})= \log(A_{del})+\log(x)-\log(\tau)-x\cdot\log e,
+$$ {#eq-log-SFR}
 

### 2025-03-04 NR/A_sSFR.sh

@@ -1,0 +1,88 @@
+topcat -stilts plot2plane \
+   xpix=1242 ypix=525 \
+   xlog=true ylog=true xlabel='sSFR [1/yr]' ylabel='A_{del} [M_\odot]' grid=true texttype=latex \
+   xmin=4.0E-15 xmax=8.287E-8 ymin=458 ymax=4.545E33 \
+   legend=true legpos=0.9957,0.968 \
+   in=/home/dp/Documents/Research_paper_SFR/NR/filled_with_NR.csv ifmt=CSV x=sSFR y=A_n shading=auto size=2 forcebitmap = true\
+   layer_1=Mark \
+      icmd_1='select A_n>1e17' \
+      color_1=blue \
+      leglabel_1='A_{del}>10^{15}' \
+   layer_2=Mark \
+      icmd_2='select !(A_n>1e17)' \
+      leglabel_2='A_{del}<10^{15}'\
+   out=/home/dp/Documents/Research_paper_SFR/NR/A-sSFR.png 
+   
+   
+topcat -stilts plot2plane \
+   xpix=1242 ypix=525 \
+   ylog=true xlabel='\log(M_*/M_\odot)' ylabel='A_{del}\, [M_\odot]' grid=true texttype=latex \
+   xmin=2.94 xmax=11.4 ymin=458 ymax=4.545E33 \
+   legend=true legpos=0.0091,0.984 \
+   in=/home/dp/Documents/Research_paper_SFR/NR/filled_with_NR.csv ifmt=CSV x=logM_total y=A_n shading=auto size=2 antialias=true forcebitmap = true\
+   layer_1=Mark \
+      icmd_1='select A_n>1e17' \
+      color_1=blue \
+      leglabel_1='A_{del}>10^{15}\\ \log(A_{del})=0.58\cdot\log(M_*)+18.5\\Correlation = 55\% \\ \hline' \
+   layer_2=LinearFit \
+      icmd_2='select A_n>1e17' \
+      color_2=blue \
+      leglabel_2='A_{del}>10^{15}\\ \log(A_{del})=0.58\cdot\log(M_*)+18.5\\Correlation = 55\% \\ \hline' \
+   layer_3=Mark \
+      icmd_3='select !(A_n>1e17)' \
+      color_3=green \
[…]

### 2025-03-04 NR/NR_sfr.py

@@ -40,7 +40,7 @@ def solve_x_n(i):
 
         def f_prime(x):
             return (2*k*x -np.exp(x)+1)
-        sol = optimize.root_scalar(f, x0=2, fprime=f_prime, method="newton")
+        sol = optimize.root_scalar(f, x0=3, fprime=f_prime, method="newton")
         return sol.root if sol.converged else np.nan
     except ValueError:
         return np.nan
@@ -61,48 +61,48 @@ dt["tau"][valid_x] = (t_sf/dt["x_n"][valid_x])
 dt["tau"][~valid_x] = np.nan
 dt["A_n"] = A_n * u.solMass  # Add units to A_n
 
-
-
-
 # Print stats (same as original)
 print(dt["x_n", "A_n", "tau"].info("stats"))
 
-
-
-
-# Scatter plot
-plt.figure(figsize=(8, 6))
-#add color from M_total
-plt.scatter(dt["tau"], dt['A_n'], c=dt["logM_total"].value, cmap="viridis", alpha=0.6, edgecolors="k")
-plt.yscale("log")
-#plt.xlim(0, 6)
-#plt.ylim(10**9, 10**11)
-# Labels and title
-plt.xlabel("tau")
-plt.ylabel("A_n (Solar Mass)")
-plt.title("Scatter Plot of A_n vs tau")
-
-# Grid for readability
-plt.grid(True, linestyle="--", alpha=0.5)
-plt.colorbar(label="logM_total")
-
-# Show the plot
-plt.savefig("tau_A.png")
-plt.show()
-plt.close()
-
-# hist tau
-plt.figure(figsize=(8, 6))
-plt.hist(dt["tau"], bins=50, color="skyblue", edgecolor="black")
-plt.xlabel("tau")
-plt.ylabel("Frequency")
-plt.title("Histogram of tau")
-plt.grid(True, linestyle="--", alpha=0.5)
-plt.savefig("hist_tau.png")
-plt.close()
+#remove rows with NaN values in the tau and A_n columns
+dt=dt[~np.isnan(dt["tau"])]
+dt=dt[~np.isnan(dt["A_n"])]
 
 # Save the updated table with NR results
-output_filename = "filled_with_NR.csv"
+output_filename = "NR/filled_with_NR.csv"
 dt.write(output_filename, format="ascii.csv", overwrite=True)
 
[…]

### 2025-03-09 thesis.qmd
uni-norm tau
turned tau to both uniform and normal prior in stan

@@
 the root $x_0\Leftrightarrow g(x_0) = 0$, can be found, for each galaxy.
-From @eq-A we can calculate the normilization constant of the galaxies, as well as their charachteristic timescales $\tau = t_{sf}\cdot x$.
+From @eq-A we can calculate the normalization constant of the galaxies, as well as their characteristic timescales $\tau = t_{sf}\cdot x$.
 
@@
 
-The second method for the calclulation of the parameters is the MCMC method. Using the logarithmic form of the model
+The second method for the calculation of the parameters is the MCMC method. Using the logarithmic form of the model
 
@@
 
--   $\tau \sim \text{normal(mean=4 Gyr, }\sigma = 1 )$, within the limits $[1,20]$ Gyr,
+-   $\tau \sim \text{uniform(lower bound = 1 Gyr, upper bound = 13.8 Gyr)}$,
 -   $t_{sf}\sim \text{uniform(lower bound = 1 Gyr, upper bound = 13.8 Gyr)}$,
@@
 
-and the likelihood:
+and the likelihood $\log(\text{SFR}_{obs}) \sim \text{normal}\left(\log(\text{SFR}_\text{MCMC}), \sigma = 0.1\right)$, while taking the Stellar Masses of the galaxies as they are, without any variance, and $A_{del}$ is calculated by @eq-A.
+The MCMC run consists of 6 chains with 8000 iterations each (2500 iterations for the burn-in phase).
+Using this method, the galaxies can have different $t_{sf}$, while only taking positive values for their timescales.
 
--   $\log(\text{SFR}_{obs}) \sim \text{normal}\left(\log(\text{SFR}_\text{MCMC}), \sigma = 0.1\right)$
+The prior of the $\tau$ and $t_{sf}$ follow a uniform distribution, since we do not want to introduce any unwanted bias in the value selection of the MCMC sampler.
+While there is bibliography that could justify using a normal distribution for $\tau$, for example @speagleHighlyConsistentFramework2014 and @kroupaConstraintsStarFormation2020 explain that the galaxies of the Main Sequence are expected to have $3.5\lesssim\tau/\text{Gyr}\lesssim4.5$, this could significantly influence the results of galaxies with slow rising SFR's.
+In the same way a wrong prior for $t_{sf}$ could effect the results, especially of younger galaxies.
+While the choice of different priors is possible, for the aim of this thesis, the uniform distribution is the best choice.
 
-## According to pre-existing bibliography
+Using these priors, the metrics of the Stan programm give good results ($\hat{R}<1.001$ and $\text{ESS} >1000$), while the calculated values correspond to the data of the catalog.
+Specifically, we use the data to recalculate the SFR from the predicted parameters, using the delayed-$\tau$ model and compare it to the observational data (@fig-comp-sfr-obs-pred), and also compare the normalization constant to the stellar masses of the galaxies (@fig-A-M-mcmc).
 
-### Problems with the method
+![Comparison of the observed SFR with the predicted by the parameters given by the MCMC run.](r_mcmc/plots/sfr_diff_plot.png){#fig-comp-sfr-obs-pred}
 
-## MCMC
+![Linear fit for $A_{del}\sim M_*$, with a correlation of 94%.
+The black dashed line is the linear regression weighted by $x$, with a fit $\log(A_{del}) = 0.95\cdot\log(M_*)+0.60, with a corralation of 98\%$](method_comparison/A_M_MCMC.png){#fig-A-M-mcmc}
+
+In @fig-sSFR-A-both-methods, it can be seen that the MCMC run does not have the same inconsistancies with the NR method, and in @fig-tau-hist-both it seems that the MCMC method captures better both the galaxies with small timescales, and the galaxies with slow rising SFR's.
+
+![$A_{del}-\text{sSFR}$ plot, where $A_{del}$ is calculated with different methods.
+In blue is the normalization constant as it is calculated by the MCMC method, while in red are results from Newton-Raphson.](method_comparison/sSFR_A.png){#fig-sSFR-A-both-methods}
+
+![Distribution of $\tau$ values, from the two methods.
+In blue is the timescale distribution as it is calculated by the MCMC method, while in red are results from Newton-Raphson.](method_comparison/tau_hist.png){#fig-tau-hist-both}
 

### 2025-03-09 NR/NR_sfr.py

@@ -1,9 +1,9 @@
-import numpy as np
-from scipy import optimize
-import matplotlib.pyplot as plt
 import astropy.units as u
+import matplotlib.pyplot as plt
+import numpy as np
 from astropy.table import QTable
 from joblib import Parallel, delayed
+from scipy import optimize
 
 #set working directory
 # import os.path

### 2025-03-09 method_comparison/plots.sh

@@ -1,0 +1,51 @@
+topcat -stilts plot2plane \
+   xpix=1818 ypix=543 \
+   xlog=true ylog=true xlabel='sSFR\ [1/yr]' ylabel='A\ [M_\odot]' grid=true texttype=latex \
+   xmin=4.0E-15 xmax=8.287E-8 ymin=603 ymax=1.622E27 \
+   legend=true legpos=0.0112,0.939 \
+   ifmt=CSV x=sSFR size=2 \
+   layer_1=Mark \
+      in_1=/home/dp/Documents/Research_paper_SFR/r_mcmc/joined_data.csv \
+      y_1=A \
+      shading_1=auto color_1=blue \
+      leglabel_1=MCMC \
+   layer_2=Mark \
+      in_2=/home/dp/Documents/Research_paper_SFR/NR/filled_with_NR.csv \
+      y_2=A_n \
+      shading_2=translucent translevel_2=0.2 \
+      leglabel_2=N-R \
+   out=/home/dp/Documents/Research_paper_SFR/method_comparison/sSFR_A.png
+
+topcat -stilts plot2plane \
+   xpix=1242 ypix=525 \
+   xlabel='\tau\ [Gyr]' ylabel="Number of galaxies" grid=true texttype=latex \
+   xmin=0 xmax=20 ymin=-2.0E-5 ymax=216 \
+   legend=true legpos=0.9911,0.976 \
+   ifmt=CSV x=tau \
+   layer_1=Histogram \
+      in_1=/home/dp/Documents/Research_paper_SFR/r_mcmc/joined_data.csv \
+      leglabel_1=MCMC color_1=blue\
+   layer_2=Histogram \
+      in_2=/home/dp/Documents/Research_paper_SFR/NR/filled_with_NR.csv \
+      color_2=red \
+      leglabel_2=N-R \
+   out=/home/dp/Documents/Research_paper_SFR/method_comparison/tau_hist.png
+
+topcat -stilts plot2plane \
+   xpix=1242 ypix=525 \
+   ylog=true xlabel='log(M_*/M_\odot)' ylabel='A_{del}\ [M_\odot]' grid=true texttype=latex \
+   xmin=2.94 xmax=11.4 ymin=1199 ymax=9.713E11 \
+   auxmap=viridis auxfunc=histogram auxmin=0.07 auxmax=13.71 \
+   auxvisible=true auxlabel='x=t_{sf}/\tau' \
[…]

### 2025-03-09 r_mcmc/R/functions.R

@@ -1,142 +1,0 @@
-# functions.R
-
-# Function to load and prepare the data
-prepare_data <- function(data_csv) {
-  dt <- data_csv %>%
-    select(logSFR_total, ID, logM_total, M_total) %>%
-    filter(
-      # iogSFR_total >=-3,
-      !is.na(logSFR_total),
-      !is.nan(logSFR_total),
-      is.finite(logSFR_total),
-      !is.na(logM_total),
-      !is.nan(logM_total),
-      is.finite(logM_total)
-    ) %>%
-    return(dt)
-}
-
-# Function to define initial values for the Stan model
-init_function <- function(chains, N) {
-  lapply(1:chains, function(i) {
-    list(
-      t_sf = rep(13.6, N),
-      # x = rep(3, N),
-      logtau = rep(log10(4), N), # MS galaxies 3.5<tau<4.5
-      # logA = rep(5.5, N),
-      tau = rep(4, N),
-      zeta = rep(1.3, N)
-    )
-  })
-}
-
-mean_vs_median <- function(summary_data, summary_variables) {
-  ggplot(summary_data, aes(x = mean, y = median)) +
-    geom_point() +
-    geom_abline(intercept = 0, slope = 1, color = "red", linetype = "dashed") +
-    labs(
-      title = paste("Mean vs. Median of", summary_variables),
-      x = "Mean",
-      y = "Median"
-    )
-  ggsave(sprintf("plots/Mean-Median/%s.png", summary_variables))
-}
-
-# Function to create histograms of the mcmc results, with mean value highlighted
-plot_histograms <- function(summary_data, summary_variables, summary_names) {
-  max_count <- max(ggplot_build(
-    ggplot(summary_data, aes(x = mean)) +
-      geom_histogram(bins = 30)
-  )$data[[1]]$count, na.rm = TRUE)
-
-  p <- ggplot(summary_data, aes(x = mean)) +
-    geom_histogram(alpha = 0.7, bins = 40, fill = "blue", color = "black") +
-    geom_vline(aes(xintercept = mean(mean)), color = "red", linetype = "dashed", size = 1) +
-    geom_text(
-      aes(
-        x = mean(mean),
-        label = format(mean(mean), scientific = TRUE, digits = 2) # Scientific notation, 2 decimal points
-      ),
-      y = max_count + 1, # Place the text slightly above the maximum bar
[…]

### 2025-03-09 r_mcmc/_targets.R

@@ -1,297 +1,0 @@
-# Created by use_targets().
-# Follow the comments below to fill in this target script.
-# Then follow the manual to check and run the pipeline:
-#   https://books.ropensci.org/targets/walkthrough.html#inspect-the-pipeline
-
-# Load packages required to define the pipeline:
-library(targets)
-library(tarchetypes) # Load other packages as needed.
-library(stantargets)
-library(crew)
-library(future)
-
-# Set target options:
-tar_option_set(
-  packages = c("readr", "tidyverse", "tibble", "stringr", "posterior", "bayesplot", "loo", "ggplot2", "scales", "latex2exp", "ggeasy"),
-  # format = "qs", # Optionally set the default storage format. qs is fast.
-  #
-  # Pipelines that take a long time to run may benefit from
-  # optional distributed computing. To use this capability
-  # in tar_make(), supply a {crew} controller
-  # as discussed at https://books.ropensci.org/targets/crew.html.
-  # Choose a controller that suits your needs. For example, the following
-  # sets a controller that scales up to a maximum of two workers
-  # which run as local R processes. Each worker launches when there is work
-  # to do and exits if 60 seconds pass with no tasks to run.
-  #
-  # controller = crew::crew_controller_local(workers = 6)
-  #
-  # Alternatively, if you want workers to run on a high-performance computing
-  # cluster, select a controller from the {crew.cluster} package.
-  # For the cloud, see plugin packages like {crew.aws.batch}.
-  # The following example is a controller for Sun Grid Engine (SGE).
-  #
-  #   controller = crew.cluster::crew_controller_sge(
-  #     # Number of workers that the pipeline can scale up to:
-  #     workers = 10,
-  #     # It is recommended to set an idle time so workers can shut themselves
-  #     # down if they are not running tasks.
-  #     seconds_idle = 120,
-  #     # Many clusters install R as an environment module, and you can load it
-  #     # with the script_lines argument. To select a specific verison of R,
-  #     # you may need to include a version string, e.g. "module load R/4.3.2".
[…]

### 2025-03-09 r_mcmc_uni/_targets.R

@@ -1,0 +1,297 @@
+# Created by use_targets().
+# Follow the comments below to fill in this target script.
+# Then follow the manual to check and run the pipeline:
+#   https://books.ropensci.org/targets/walkthrough.html#inspect-the-pipeline
+
+# Load packages required to define the pipeline:
+library(targets)
+library(tarchetypes) # Load other packages as needed.
+library(stantargets)
+library(crew)
+library(future)
+
+# Set target options:
+tar_option_set(
+  packages = c("readr", "tidyverse", "tibble", "stringr", "posterior", "bayesplot", "loo", "ggplot2", "scales", "latex2exp", "ggeasy"),
+  # format = "qs", # Optionally set the default storage format. qs is fast.
+  #
+  # Pipelines that take a long time to run may benefit from
+  # optional distributed computing. To use this capability
+  # in tar_make(), supply a {crew} controller
+  # as discussed at https://books.ropensci.org/targets/crew.html.
+  # Choose a controller that suits your needs. For example, the following
+  # sets a controller that scales up to a maximum of two workers
+  # which run as local R processes. Each worker launches when there is work
+  # to do and exits if 60 seconds pass with no tasks to run.
+  #
+  # controller = crew::crew_controller_local(workers = 6)
+  #
+  # Alternatively, if you want workers to run on a high-performance computing
+  # cluster, select a controller from the {crew.cluster} package.
+  # For the cloud, see plugin packages like {crew.aws.batch}.
+  # The following example is a controller for Sun Grid Engine (SGE).
+  #
+  #   controller = crew.cluster::crew_controller_sge(
+  #     # Number of workers that the pipeline can scale up to:
+  #     workers = 10,
+  #     # It is recommended to set an idle time so workers can shut themselves
+  #     # down if they are not running tasks.
+  #     seconds_idle = 120,
+  #     # Many clusters install R as an environment module, and you can load it
+  #     # with the script_lines argument. To select a specific verison of R,
+  #     # you may need to include a version string, e.g. "module load R/4.3.2".
[…]

### 2025-03-09 method_comparison/plots.sh
Compare for norm-uni-NR

@@ -5,7 +5,7 @@ topcat -stilts plot2plane \
    legend=true legpos=0.0112,0.939 \
    ifmt=CSV x=sSFR size=2 \
    layer_1=Mark \
-      in_1=/home/dp/Documents/Research_paper_SFR/r_mcmc/joined_data.csv \
+      in_1=/home/dp/Documents/Research_paper_SFR/r_mcmc_uni/joined_data.csv \
       y_1=A \
       shading_1=auto color_1=blue \
       leglabel_1=MCMC \
@@ -23,12 +23,15 @@ topcat -stilts plot2plane \
    legend=true legpos=0.9911,0.976 \
    ifmt=CSV x=tau \
    layer_1=Histogram \
-      in_1=/home/dp/Documents/Research_paper_SFR/r_mcmc/joined_data.csv \
+      in_1=/home/dp/Documents/Research_paper_SFR/r_mcmc_uni/joined_data.csv \
       leglabel_1=MCMC color_1=blue\
    layer_2=Histogram \
       in_2=/home/dp/Documents/Research_paper_SFR/NR/filled_with_NR.csv \
       color_2=red \
       leglabel_2=N-R \
+   layer_3=Histogram \
+      in_3=/home/dp/Documents/Research_paper_SFR/r_mcmc_normal/joined_data.csv \
+      leglabel_3="MCMC with \tau\sim normal(4,1)" color_3=green\
    out=/home/dp/Documents/Research_paper_SFR/method_comparison/tau_hist.png
 
 topcat -stilts plot2plane \
@@ -38,7 +41,7 @@ topcat -stilts plot2plane \
    auxmap=viridis auxfunc=histogram auxmin=0.07 auxmax=13.71 \
    auxvisible=true auxlabel='x=t_{sf}/\tau' \
    legend=true legpos=0.0103,0.944 \
-   in=/home/dp/Documents/Research_paper_SFR/r_mcmc/joined_data.csv ifmt=CSV x=logM_total y=A \
+   in=/home/dp/Documents/Research_paper_SFR/r_mcmc_uni/joined_data.csv ifmt=CSV x=logM_total y=A \
     leglabel='log(A_{del}) = 0.86\cdot log(M_*) + 1.5 \\ Correlation=94\%' antialias=true \
    layer_1=Mark \
       aux_1=x \
@@ -48,4 +51,27 @@ topcat -stilts plot2plane \
       weight_3=x \
[…]

### 2025-03-09 method_comparison/sfrd.py

@@ -1,0 +1,150 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import pandas as pd
+import scipy.integrate  # Ensure scipy is imported
+from astropy.cosmology import Planck18 as cosmo  # Using Planck 2018 cosmology
+import astropy.units as u
+
+
+# Import data
+data_uni = pd.read_csv('r_mcmc_uni/joined_data.csv')
+data_norm = pd.read_csv('r_mcmc_normal/joined_data.csv')
+data_nr = pd.read_csv('NR/filled_with_NR.csv')
+
+# Define the A and tau values for each dataset
+A_values_uni = data_uni['A'].values
+tau_values_uni = (data_uni['tau']*u.Gyr.to(u.yr)).values
+sigma_A_values_uni = data_uni['A_sigma'].values
+sigma_tau_values_uni = (data_uni['tau_sigma']*u.Gyr.to(u.yr)).values
+
+A_values_norm = data_norm['A'].values
+tau_values_norm = (data_norm['tau']*u.Gyr.to(u.yr)).values
+sigma_A_values_norm = data_norm['A_sigma'].values
+sigma_tau_values_norm = (data_norm['tau_sigma']*u.Gyr.to(u.yr)).values
+
+A_values_nr = data_nr['A_n'].values
+tau_values_nr = (data_nr['tau']*u.Gyr.to(u.yr)).values
+
+# Volume factor
+V = (4/3 * np.pi * 11**3)
+
+# Define the SFR function
+
+
+def sfr_function(t, A, tau):
+    return A * (t / tau**2) * np.exp(-t / tau) / V
+
+# Define the error propagation function (only for datasets with sigmas)
+
+
+def sfr_error(t, A, tau, sigma_A, sigma_tau):
+    dSFR_dA = (t / tau**2) * np.exp(-t / tau) / V
+    dSFR_dtau = A * np.exp(-t / tau) * ((2 * t / tau**3) - (t**2 / tau**4)) / V
+    sigma_SFR = np.sqrt((dSFR_dA * sigma_A)**2 + (dSFR_dtau * sigma_tau)**2)
+    return sigma_SFR
+
+
+# Define custom time steps and corresponding redshifts
+custom_times = np.array([0, 10.5, 12.3, 12.9, 13.2, 13.3])  # Gyr
+redshifts = np.array([0, 2, 4, 6, 8, 10])  # Corresponding redshifts
+
+# Interpolate time steps for smooth plotting
[…]

### 2025-03-09 r_mcmc_normal/sfrd.py

@@ -1,53 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-
-# import data from joined_data.csv file
-import pandas as pd
-data = pd.read_csv('r_mcmc/joined_data.csv')
-
-# Define the A and tau values
-A_values = data['A'].values
-tau_values = data['tau'].values
-sigma_A_values = data['A_sigma'].values
-sigma_tau_values = data['tau_sigma'].values
-V = (4/3*np.pi*10**3)
-# Define the SFR function
-def sfr_function(t, A, tau):
-    return A * (t / tau**2) * np.exp(-t / tau)/V
-
-# Define the error propagation function
-def sfr_error(t, A, tau, sigma_A, sigma_tau):
-    dSFR_dA = (t / tau**2) * np.exp(-t / tau)/V
-    dSFR_dtau = A * np.exp(-t / tau) * ( (2*t / tau**3) - (t**2 / tau**4) )/V
-    
-    sigma_SFR = np.sqrt((dSFR_dA * sigma_A)**2 + (dSFR_dtau * sigma_tau)**2)
-    return sigma_SFR
-
-# Define time steps from 0 to 13.8 Gyr in 0.5 Gyr intervals
-time_steps = np.arange(0.3, 13.8 + 0.5, 0.5)
-
-
-
-# Compute total SFR and its uncertainty at each time step
-total_sfr = np.zeros_like(time_steps)
-total_sfr_error = np.zeros_like(time_steps)
-
-for i, t in enumerate(time_steps):
-    sfr_i = sfr_function(t, A_values, tau_values)
-    sigma_sfr_i = sfr_error(t, A_values, tau_values, sigma_A_values, sigma_tau_values)
-    
-    total_sfr[i] = np.sum(sfr_i)  
-    total_sfr_error[i] = np.sqrt(np.sum(sigma_sfr_i**2))  # Sum errors in quadrature
-
-# Plot the results with error bars
-plt.figure(figsize=(8, 5))
-plt.errorbar(13.8-time_steps, total_sfr, yerr=total_sfr_error, fmt='o-', capsize=3, label="Total SFRD")
-#log scale for x-y
-plt.yscale('log')
-plt.xlabel("Lookback Time (Gyr)")
-plt.ylabel("Total SFR/Volume")
-plt.title("Total SFRD    Over Time with Uncertainty")
-plt.legend()
-plt.grid()
-plt.savefig('r_mcmc/sfrd.png')
-plt.close()

### 2025-03-16 NR/A_sSFR.sh
Colors to the dataset

@@ -45,7 +45,7 @@ topcat -stilts plot2plane \
    auxclip=0,1 auxfunc=histolog auxmin=3 auxmax=5.123E13 \
    auxvisible=true auxlabel='\tau\, [Gyr]' \
    legend=true legpos=0.0091,0.984 \
-   in=/home/dp/Documents/Research_paper_SFR/NR/filled_with_NR.csv ifmt=CSV x=logM_total y=A_n aux=tau shading=aux size=2 auxnullcolor= antialias=true forcebitmap = true\
+   in=/home/dp/Documents/Research_paper_SFR/NR/filled_with_NR.csv ifmt=CSV x=logM_total y=A_n aux=tau_n shading=aux size=2 auxnullcolor= antialias=true forcebitmap = true\
    layer_1=Mark \
       icmd_1='select A_n>1e17' \
       leglabel_1='A_{del}>10^{15}\\ \log(A_{del})=0.58\cdot\log(M_*)+18.5\\Correlation = 55\% \\ \hline' \

### 2025-03-16 NR/NR_sfr.py

@@ -56,30 +56,23 @@ A_n[~valid_x] = np.nan  # Keep NaNs consistent
 
 # Add results to the DataFrame (same as original)
 dt["x_n"] = x_n
-dt['tau'] = np.empty(len(dt))
-dt["tau"][valid_x] = (t_sf/dt["x_n"][valid_x])
-dt["tau"][~valid_x] = np.nan
+dt['tau_n'] = np.empty(len(dt))
+dt["tau_n"][valid_x] = (t_sf/dt["x_n"][valid_x])
+dt["tau_n"][~valid_x] = np.nan
 dt["A_n"] = A_n * u.solMass  # Add units to A_n
 
 # Print stats (same as original)
-print(dt["x_n", "A_n", "tau"].info("stats"))
+print(dt["x_n", "A_n", "tau_n"].info("stats"))
 
-#remove rows with NaN values in the tau and A_n columns
-dt=dt[~np.isnan(dt["tau"])]
+#remove rows with NaN values in the tau_n and A_n columns
+dt=dt[~np.isnan(dt["tau_n"])]
 dt=dt[~np.isnan(dt["A_n"])]
-
-# Save the updated table with NR results
-output_filename = "NR/filled_with_NR.csv"
-dt.write(output_filename, format="ascii.csv", overwrite=True)
-
-print(f"Results saved to {output_filename}")
-
 
 # Create a figure with two subplots
 fig, (ax1, ax2) = plt.subplots(1, 2, figsize=(14, 6))
 
 # First subplot (without zoom)
-scatter1 = ax1.scatter(dt["tau"], dt['A_n'], c=dt["logM_total"].value, cmap="viridis", edgecolors="k")
+scatter1 = ax1.scatter(dt["tau_n"], dt['A_n'], c=dt["logM_total"].value, cmap="viridis", edgecolors="k")
 ax1.set_yscale("log")
 ax1.set_xlim(-1e10, 1e10)  # Adjust x-axis limits if needed
 ax1.set_ylim(0, 1e31)  # Adjust y-axis limits if needed
@@ -88,7 +81,7 @@ ax1.set_ylabel(r"$A_{del}\, [M_{\odot}]$")
 ax1.grid(True, linestyle="--", alpha=0.5)
 
 # Second subplot (with zoom)
-scatter2 = ax2.scatter(dt["tau"], dt['A_n'], c=dt["logM_total"].value, cmap="viridis", edgecolors="k")
[…]

### 2025-03-16 compare/quick_comp.py

@@ -14,7 +14,7 @@ import astropy.units as u
 # plt.style.use("ggplot")
 
 # Get data
-data = pd.read_csv("../tables/inner_join.csv")
+data = pd.read_csv("./tables/inner_join.csv")
 
 # Define the mass and luminosity thresholds
 mass_threshold = 9  # Log(Mass) threshold for dwarf vs massive
@@ -45,7 +45,7 @@ data[["mass_type", "classification_method"]] = data.apply(
     lambda row: pd.Series(classify_galaxy(row)), axis=1
 )
 
-cols = pd.read_csv("Reordered_Final_Comparison_Table.csv")
+cols = pd.read_csv("compare/Reordered_Final_Comparison_Table.csv")
 
 data["SFR_mean"] = data[["SFRFUV", "SFRHa"]].mean(axis=1)
 # log SFR_mean
@@ -126,10 +126,12 @@ def perform_linear_regression_analysis_fixed(
     # Scatter plot with fit
     for name, group in groups:
         marker_shape = marker_dict[name] if marker_dict and name in marker_dict else "o"
-        sample_size = len(group)  # Count the number of points in the group
-
+        sample_size = len(group.dropna(subset=[x,y]))  # Count the number of points in the group
+        
+        
         x_data_g = group[x] if log_transform_x is False else np.log10(group[x])
         y_data_g = group[y] if log_transform_y is False else np.log10(group[y])
+        
         x_err_data = group[x_error] if x_error in group.columns else None
         y_err_data = group[y_error] if y_error in group.columns else None
 
@@ -171,7 +173,7 @@ def perform_linear_regression_analysis_fixed(
     # Residuals plot
     for name, group in groups:
         marker_shape = marker_dict.get(name, "o") if marker_dict else "o"
-        sample_size = len(group)  # Count the number of points in the group
+        sample_size = len(group.dropna(subset=[x, y]))  # Count the number of points in the group
 
         x_data_g = group[x] if log_transform_x is False else np.log10(group[x])
         residuals_g = group[y] - (intercept + slope * group[x])
@@ -189,7 +191,13 @@ def perform_linear_regression_analysis_fixed(
     axs[1].legend()
     axs[1].grid(True)
 
-    # Residuals histogram plot
+    # Residuals histogram plot with on the mass category
+    for name, group in groups:
[…]

### 2025-03-16 r_mcmc_normal/_targets.R

@@ -238,14 +238,14 @@ tar_plan(
         ID = id_summary$mean, # Assuming id is the identifier
         logSFR_pred = sfr_summary$mean,
         logSFR_pred_sigma = sfr_summary$sd,
-        t_sf = t_sf_summary$mean,
-        t_sf_sigma = t_sf_summary$sd,
-        tau = tau_summary$mean,
-        tau_sigma = tau_summary$sd,
-        A = A_summary$mean,
-        A_sigma = A_summary$sd,
-        x = x_summary$mean,
-        x_sigma = x_summary$sd
+        t_sf_np = t_sf_summary$mean,
+        t_sf_sigma_np = t_sf_summary$sd,
+        tau_np = tau_summary$mean,
+        tau_sigma_np = tau_summary$sd,
+        A_np = A_summary$mean,
+        A_sigma_np = A_summary$sd,
+        x_np = x_summary$mean,
+        x_sigma_np = x_summary$sd
       )
 
 

### 2025-03-16 r_mcmc_uni/_targets.R

@@ -238,14 +238,14 @@ tar_plan(
         ID = id_summary$mean, # Assuming id is the identifier
         logSFR_pred = sfr_summary$mean,
         logSFR_pred_sigma = sfr_summary$sd,
-        t_sf = t_sf_summary$mean,
-        t_sf_sigma = t_sf_summary$sd,
-        tau = tau_summary$mean,
-        tau_sigma = tau_summary$sd,
-        A = A_summary$mean,
-        A_sigma = A_summary$sd,
-        x = x_summary$mean,
-        x_sigma = x_summary$sd
+        t_sf_up = t_sf_summary$mean,
+        t_sf_sigma_up = t_sf_summary$sd,
+        tau_up = tau_summary$mean,
+        tau_sigma_up = tau_summary$sd,
+        A_up = A_summary$mean,
+        A_sigma_up = A_summary$sd,
+        x_up = x_summary$mean,
+        x_sigma_up = x_summary$sd
       )
 
 

### 2025-03-16 tables/column_join.sh

@@ -14,7 +14,13 @@ stilts tpipe \
   cmd='addcol -units "log(Msol)" -desc "" logM_total "NULL_logM_HEC ? log10(0.82)+merge_logKLum: logM_HEC"'\
   cmd='addcol -units "Msol" -desc "Total M_* in linear scale" M_total "exp10(logM_total)"'\
   cmd='addcol -units "1/yr" -desc "Specific SFR" sSFR "SFR_total/M_total"'\
+  cmd='addcol -units "log10(1/yr)" -desc "Specific SFR in logarithmic scale" logsSFR "log10(sSFR)"'\
   cmd='addcol -desc "ID column" ID "Index"'\
+  cmd='addcol -desc "g-r color" gr "g-r"'\
+  cmd='addcol -desc "b-v color" bv "bt-vt"'\
+  cmd='addcol -desc "b-u color" bu "bt-ut"'\
+  cmd='addcol -desc "absolute mag of B-Band" MB "merge_Bmag - 5*log10(merge_D)-25"'\
+  cmd='addcol -desc "absolute mag of r-Band" MR "r - 5*log10(r)-25"'\
 
 
 stilts tpipe \

### 2025-03-16 method_comparison/sfrd.py
SFRD lilly-Madau

@@ -12,18 +12,18 @@ data_norm = pd.read_csv('r_mcmc_normal/joined_data.csv')
 data_nr = pd.read_csv('NR/filled_with_NR.csv')
 
 # Define the A and tau values for each dataset
-A_values_uni = data_uni['A'].values
-tau_values_uni = (data_uni['tau']*u.Gyr.to(u.yr)).values
-sigma_A_values_uni = data_uni['A_sigma'].values
-sigma_tau_values_uni = (data_uni['tau_sigma']*u.Gyr.to(u.yr)).values
+A_values_uni = data_uni['A_up'].values
+tau_values_uni = (data_uni['tau_up']*u.Gyr.to(u.yr)).values
+sigma_A_values_uni = data_uni['A_sigma_up'].values
+sigma_tau_values_uni = (data_uni['tau_sigma_up']*u.Gyr.to(u.yr)).values
 
-A_values_norm = data_norm['A'].values
-tau_values_norm = (data_norm['tau']*u.Gyr.to(u.yr)).values
-sigma_A_values_norm = data_norm['A_sigma'].values
-sigma_tau_values_norm = (data_norm['tau_sigma']*u.Gyr.to(u.yr)).values
+A_values_norm = data_norm['A_np'].values
+tau_values_norm = (data_norm['tau_np']*u.Gyr.to(u.yr)).values
+sigma_A_values_norm = data_norm['A_sigma_np'].values
+sigma_tau_values_norm = (data_norm['tau_sigma_np']*u.Gyr.to(u.yr)).values
 
 A_values_nr = data_nr['A_n'].values
-tau_values_nr = (data_nr['tau']*u.Gyr.to(u.yr)).values
+tau_values_nr = (data_nr['tau_n']*u.Gyr.to(u.yr)).values
 
 # Volume factor
 V = (4/3 * np.pi * 11**3)
@@ -135,7 +135,7 @@ ax3.set_xticklabels([f"{d:.1f}" for d in co_moving_distances])
 
 # Y-axis
 ax1.set_yscale('log')
-ax1.set_ylabel(r"$\log_{10}\left(\frac{\text{SFRD}}{\text{M}_\odot \text{yr}^{-1} \text{Mpc}^{-3}}\right)$")
+ax1.set_ylabel(r"$\text{SFRD}\ \left(\text{M}_\odot \text{yr}^{-1} \text{Mpc}^{-3}\right)$")
 ax1.legend()
[…]

### 2025-03-16 presentations/presentation.qmd
zezas presentation

--- 2024-12-16 presentation.qmd
@@
       - PdfExport
-    bibliography: My_Library.bib
 editor: 

### 2025-03-16 presentations/presentation_chatzidimitriou.qmd
zezas presentation

@@
 ---
-title: "Τιτλος"
-subtitle: ""
+title: "Analysis of observational data, to calculate the Delayed-Tau model parameters"
 author: "Δημήτρης Παπαχριστόπουλος"
@@
 
-# Τι ειναι το LCV
+# Τι ειναι το Local Cosmological Volume
 
@@
 
-![](figure/log_SFR_FUV_Ha.png){fig-align="center" width="500"}
+![](../figure/log_SFR_FUV_Ha.png){fig-align="center" width="500"}
 
@@
 
-![](figure/Screenshot%20from%202024-12-07%2021-49-48.png){fig-align="center"}
+![](../figure/Screenshot%20from%202024-12-07%2021-49-48.png){fig-align="center"}
 
@@
 
-![](compare/quickplots/SFR.png){fig-align="center"}
+![](../compare/quickplots/SFR.png){fig-align="center"}
 

### 2025-03-16 presentations/zezas.qmd
zezas presentation

---
title: "Analysis of observational data, to calculate the Delayed-Tau model parameters"
author: "Δημήτρης Παπαχριστόπουλος"
bibliography: ../My_Library.bib
format:
  revealjs:
    theme: moon
    embed-resources: true
    controls: true
    slide-number: true 
    scrollable: true
    revealjs-plugin: 
      - PdfExport
editor: 
  markdown: 
    wrap: sentence
---

![](../figure/hauslbauer.png)

------------------------------------------------------------------------

-   **Αστρογένεση & Εξέλιξη**: Το delayed-τ model προσεγγίζει την ιστορία του ρυθμού αστρογένεσης.

-   **Παράμετροι**: Υπολογισμός παραμέτρων του μοντέλου.

-   **Ασυμφωνίες**: Το μοντέλο παρουσιάζει ασυμφωνίες με καθιερωμένες κοσμολογικές θεωρίες και παρατηρησιακά δεδομένα

::: notes
Το παραμετροποιημένο μοντέλο “delayed τ-model” στοχεύει στην προσεγγιστική περιγραφή της ιστορίας αστρογένεσης των γαλαξιών.
Ο Pavel Kroupa (2023) [@haslbauer2023] υπολογίζει τις παραμέτρους του μοντέλου αυτού, αξιοποιώντας παρατηρησιακά δεδομένα του ρυθμού αστρογένεσης (star formation rate) και εφαρμόζοντας υπολογιστικές μεθόδους για τον προσδιορισμό της σταθεράς κανονικοποίησης και της χαρακτηριστικής χρονικής κλίμακας (time scale).

Η εξαγωγή αυτών των παραμέτρων επιτρέπει τη διερεύνηση του τρόπου με τον οποίο ο ρυθμός αστρογένεσης μεταβάλλεται με την πάροδο του χρόνου για διαφορετικούς γαλαξίες.
Ωστόσο, τα αποτελέσματα δείχνουν ότι το “delayed τ-model” παρουσιάζει ασυμφωνίες με καθιερωμένες κοσμολογικές θεωρίες και παρατηρησιακά δεδομένα, καθώς προβλέπει το μέγιστο του ρυθμού αστρογένεσης σε διαφορετικό κοσμολογικό χρόνο (δηλαδή σε χαμηλότερο redshift) από αυτόν που υποδεικνύουν οι παρατηρήσεις (z ≈ 2).
Επιπλέον, υποδηλώνει ότι το συγκεκριμένο μοντέλο είναι ικανοποιητικό μόνο για αρκετά μεγάλους γαλαξίες.
:::

# Lilly-Madau Plot

![@madauCosmicStarFormation2014](../images/lily-madau.png){fig-align="center"}

# Delayed-$τ$ model

::::: columns
$$
SFR_{del}(t_{sf})=A_{del}\frac{t_{sf}}{\tau^2}e^{-\frac{t_{sf}}{\tau}}\ \left[\frac{M_\odot}{yr} \right],\ 
$$

::: column
![](../images/delayed_tau_sfr.png){fig-align="center" width="500"} <!-- $$\int_0^{t_{sf}}\text{SFR(t)} \text{dt} = \zeta \cdot Μ_*$$ -->
:::

::: column
-   $t_{sf} = T_{\text{universe}} - t_{\text{start}}$
-   $\tau$ = timescale, ο χρόνος στον οποίο παρουσιάζει peak το SFR
-   $A_{del}$ = σταθερά κανονικοποίησης \[$M_\odot$\]
:::
:::::

::: notes
-   **Το delayed-**$\tau$ model περιγράφει την ιστορία σχηματισμού αστέρων (SFH) ενός γαλαξία, υποθέτοντας ότι οι ρυθμοί σχηματισμού αστέρων (SFRs) συνήθως αυξάνονται στην αρχική φάση εξέλιξης του γαλαξία και βαθμιαία μειώνονται.

-   Κρουπα χρησιμοποίησε δεδομένα για στο sfr kai M\_\* και υπολόγισε τις παραμέτρους του μοντέλου, για να δείξει την ασυμφωνία του με το lilly madau

-   **Speagle et al. (2014):**[@speagle2014] Το SFH γαλαξιών της κύρια ακολουθίας, μπορεί να παραμετροποιηθεί με ακρίβεια βάση αυτού του μοντέλου
:::

# Δεδομενα {.scrollable}

:::::: columns
::: {.column width="50%"}
Γαλαξίες του Local Cosmological Volume

-   $D \leq 10$ Mpc
-   Redshift: $z \approx 0$
:::

::: {.column width="50%"}
| Table  | Number of galaxies |
|:-------|-------------------:|
| UNGC   |               1321 |
| HECATE |               2901 |
| Join   |           **3934** |
:::

::: {.fragment .fade-in}
-   Για αυτούς τους γαλαξίες έχουμε:
    -   SFR από Hα, FUV και IR
    -   Αστρικές μάζες
    -   **1761** γαλαξίες με μετρήσεις SFR και $M_*$
:::
::::::

## FUV → IR

![](../compare/quickplots/SFR.png){fig-align="center"}

# Πρωτη προσεγγιση

-   Σύστημα 2 εξισώσεων και 2 μεταβλητών ($A_{del},\ \tau$), κρατώντας το $t_{sf} = 13.6$ Gyr σταθερό.
-   Λύση με υπολογιστικές μεθόδους
    -   Newton-Ramphson
-   Θα γίνει για *όλους* τους γαλαξίες του τελικού καταλόγου.

## Υπολογισμος $\tau$

::::: rows
::: row
![](../NR/tau_A_double_plot.png)
:::

::: row
![](../../../Pictures/Screenshots/Screenshot%20from%202025-03-10%2003-15-10.png)
:::
:::::

------------------------------------------------------------------------

::::::: rows
::: row
![$\text{sSFR}=\frac{\text{SFR}}{M_*}$](../NR/A-sSFR.png)
:::

::: row
![$A_{del}=M_*\frac{\zeta}{1-(x+1)e^{-x}},\ \zeta\approx1.3$](../NR/A-M_*-c_x.png)
:::

:::: row
::: incremental
-   **Προβλήματα Μεθόδου:**
    -   Επιτρέπει την ύπαρξη αρνητικών $\tau$
    -   $t_{sf} = 13.6\, \text{Gyr}$, αποκλείει την περίπτωση κάποιοι γαλαξίες να έχουν διαφορετικό $t_{sf}$
    -   Το εκθετικό προκαλεί αστάθεια στο σύστημα.
:::
::::
:::::::

# Markov Chain Monte Carlo {.scrollable}

Υπολογίζει και τις 3 μεταβλητές ταυτόχρονα, βάση κάποιας κατανομής

::: incremental
-   $t_{sf}\sim \text{uniform(1 Gyr, 13.8 Gyr)}$, <!-- -   $\zeta \sim \text{normal(mean=1.3, }\sigma = 0.01)$, within the limits $[1,2]$, -->
-   $\tau \sim \text{uniform(1 Gyr, 20 Gyr)}$,
-   $\tau \sim \text{normal}(\text{mean = 4 Gyr, } \sigma = 1)$,
:::

::: notes
Αλυσίδες Markov: Σειρές καταστάσεων όπου η επόμενη κατάσταση εξαρτάται μόνο από την τρέχουσα.

Δειγματοληψία Monte Carlo: Χρήση τυχαίων δειγμάτων για την εκτίμηση στατιστικών μεγεθών.

Συνδυασμός MCMC: Δημιουργία αλυσίδων Markov που παράγουν δείγματα από την επιθυμητή κατανομή.

-   Σύστημα 2 εξισώσεων και 3 μεταβλητών ($A_{del},\ \tau, t_{sf}$), δεν κρατάμε το $t_{sf} = 13.6$ Gyr σταθερό.
-   Mας δίνει σφάλματα για τα αποτελέσματα
-   Μπορούμε να περιορίσουμε το διάστημα των τιμών
:::

# Συγκριση Μεθοδων

![$\text{sSFR}=\frac{\text{SFR}}{M_*}$](../method_comparison/sSFR_A.png)

------------------------------------------------------------------------

![$A_{del}=M_*\frac{\zeta}{1-(x+1)e^{-x}},\ \zeta\approx1.3$](../method_comparison/A_M_MCMC_norm.png)

------------------------------------------------------------------------

::::: rows
::: row
![](../method_comparison/tau_hist.png)

-   N-R: $\tau\in [3,\infty]$,
-   MCMC uniform $\tau$ prior: 2 peak, ($\sim 2 Gyr,\sim 12 Gyr$),
-   MCMC normal $\tau$ prior: Τα αποτελέσματα είναι πιο κοντά στην βιβλιογραφία
:::

::: row
![](../method_comparison/tsf_hist.png)

Τα αποτελέσματα από το normal prior είναι πιο κοντά με την υπόθεση $t_{sf} = 13.6$ Gyr
:::
:::::

# SFRD reconstruction

::::: columns
::: column
![](../method_comparison/sfrd_comparison_custom_axes.png)
:::

::: column
![@haslbauerCosmologicalStarFormation2023](../method_comparison/hauslbauer_sfrd.png)
:::

MCMC έχει ίδια τάξη μεγέθους με το Lilly-Madau Plot
:::::

# Μελλοντικα σχεδια

-   Έλεγχος διαφορετικών priors για καλύτερα προσσέγγιση του Lilly-Madau Plot
-   Συνδιασμός με άλλα παραμετρικά μοντέλα
-   SFH reconstruction και σύγκριση με πειραματικά δεδομένα, ανά γαλαξία.

### 2025-03-16 thesis.qmd
cmd-ms comparison

@@
 
--   $\tau \sim \text{uniform(lower bound = 1 Gyr, upper bound = 13.8 Gyr)}$,
 -   $t_{sf}\sim \text{uniform(lower bound = 1 Gyr, upper bound = 13.8 Gyr)}$,
@@
 and the likelihood $\log(\text{SFR}_{obs}) \sim \text{normal}\left(\log(\text{SFR}_\text{MCMC}), \sigma = 0.1\right)$, while taking the Stellar Masses of the galaxies as they are, without any variance, and $A_{del}$ is calculated by @eq-A.
+For the $\tau$ we will consider two different priors, $\tau \sim \text{uniform(lower bound = 1 Gyr, upper bound = 13.8 Gyr)}$ and $\tau \sim \text{normal(mean = 4 Gyr, }\sigma  = 13.8 \text{Gyr)}$.
 The MCMC run consists of 6 chains with 8000 iterations each (2500 iterations for the burn-in phase).
@@
 The prior of the $\tau$ and $t_{sf}$ follow a uniform distribution, since we do not want to introduce any unwanted bias in the value selection of the MCMC sampler.
-While there is bibliography that could justify using a normal distribution for $\tau$, for example @speagleHighlyConsistentFramework2014 and @kroupaConstraintsStarFormation2020 explain that the galaxies of the Main Sequence are expected to have $3.5\lesssim\tau/\text{Gyr}\lesssim4.5$, this could significantly influence the results of galaxies with slow rising SFR's.
-In the same way a wrong prior for $t_{sf}$ could effect the results, especially of younger galaxies.
-While the choice of different priors is possible, for the aim of this thesis, the uniform distribution is the best choice.
+However, there is bibliography that could justify using a normal distribution for $\tau$, for example @speagleHighlyConsistentFramework2014 and @kroupaConstraintsStarFormation2020 explain that the galaxies of the Main Sequence are expected to have $3.5\lesssim\tau/\text{Gyr}\lesssim4.5$.
+The same prior will not apply for $t_{sf}$ since it could significatly effect the results, especially of younger galaxies.
 
@@
 
-![Comparison of the observed SFR with the predicted by the parameters given by the MCMC run.](r_mcmc/plots/sfr_diff_plot.png){#fig-comp-sfr-obs-pred}
+::: {#fig-comp-sfr-obs-pred layout-ncol="2"}
+
+![MCMC run for $\tau \sim \text{uniform}$ prior.](r_mcmc_uni/plots/sfr_diff_plot.png){#fig-comp-sfr-obs-pred-uni}
+
+![MCMC run $\tau \sim \text{normal}$ prior.](r_mcmc_normal/plots/sfr_diff_plot.png){#fig-comp-sfr-obs-pred-norm}
+
+Comparison of the observed SFR with the predicted by the parameters given by the MCMC run.
+:::
+
+::: {#fig-A-M-mcmc layout-nrow="2"}
 
 ![Linear fit for $A_{del}\sim M_*$, with a correlation of 94%.
-The black dashed line is the linear regression weighted by $x$, with a fit $\log(A_{del}) = 0.95\cdot\log(M_*)+0.60, with a corralation of 98\%$](method_comparison/A_M_MCMC.png){#fig-A-M-mcmc}
+The black dashed line is the linear regression weighted by $x$, with a fit $\log(A_{del}) = 0.95\cdot\log(M_*)+0.60, with a corralation of 98\%$](method_comparison/A_M_MCMC_uni.png){#fig-A-M-mcmc-uni}
+
+![Linear fit for $A_{del}\sim M_*$, with a correlation of 99%.
+The black dashed line is the linear regression weighted by $x$, with a fit $\log(A_{del}) = 0.97\cdot\log(M_*)+0.44, with a corralation of 99.5\%$](method_comparison/A_M_MCMC_norm.png){#fig-A-M-mcmc-norm}
+:::
 
@@
 ![$A_{del}-\text{sSFR}$ plot, where $A_{del}$ is calculated with different methods.
-In blue is the normalization constant as it is calculated by the MCMC method, while in red are results from Newton-Raphson.](method_comparison/sSFR_A.png){#fig-sSFR-A-both-methods}
+In blue and green are the normalization constant values as they calculated by the MCMC method with different priors, while in red are results from Newton-Raphson.](method_comparison/sSFR_A.png){#fig-sSFR-A-both-methods}
 

### 2025-03-16 method_comparison/joined_methods_table.sh

@@ -1,0 +1,14 @@
+stilts tmatchn nin=3 \
+  in1=/home/dp/Documents/Research_paper_SFR/r_mcmc_uni/joined_data.csv ifmt1=csv \
+  in2=/home/dp/Documents/Research_paper_SFR/r_mcmc_normal/joined_data.csv ifmt2=csv \
+  in3=/home/dp/Documents/Research_paper_SFR/NR/filled_with_NR.csv ifmt3=csv \
+  matcher=exact \
+  values1='ID' values2='ID' values3='ID' \
+  out=joined_output.csv ofmt=csv
+
+stilts tmatch2 \
+  in1=/home/dp/Documents/Research_paper_SFR/method_comparison/joined_output.csv ifmt1=csv \
+  in2=/home/dp/Documents/Research_paper_SFR/tables/filled.csv ifmt2=csv \
+  matcher=exact \
+  values1='ID_1' values2='ID' \
+  out=joined_output_HECATE.csv ofmt=csv

### 2025-03-16 method_comparison/plots.sh

@@ -6,14 +6,19 @@ topcat -stilts plot2plane \
    ifmt=CSV x=sSFR size=2 \
    layer_1=Mark \
       in_1=/home/dp/Documents/Research_paper_SFR/r_mcmc_uni/joined_data.csv \
-      y_1=A \
+      y_1=A_up \
       shading_1=auto color_1=blue \
-      leglabel_1=MCMC \
+      leglabel_1="MCMC\ with\ \tau \ \sim uniform(1,20)" \
    layer_2=Mark \
       in_2=/home/dp/Documents/Research_paper_SFR/NR/filled_with_NR.csv \
       y_2=A_n \
-      shading_2=translucent translevel_2=0.2 \
+      shading_2=translucent translevel_2=0.2 shape_2=filled_diamond\
       leglabel_2=N-R \
+   layer_3=Mark \
+      in_3=/home/dp/Documents/Research_paper_SFR/r_mcmc_normal/joined_data.csv \
+      y_3=A_np \
+      shading_3=auto color_3=green shape_3=cross\
+      leglabel_3="MCMC with\ \tau \sim normal(4,1)" \
    out=/home/dp/Documents/Research_paper_SFR/method_comparison/sSFR_A.png
 
 topcat -stilts plot2plane \
@@ -21,18 +26,36 @@ topcat -stilts plot2plane \
    xlabel='\tau\ [Gyr]' ylabel="Number of galaxies" grid=true texttype=latex \
    xmin=0 xmax=20 ymin=-2.0E-5 ymax=216 \
    legend=true legpos=0.9911,0.976 \
-   ifmt=CSV x=tau \
+   ifmt=CSV \
    layer_1=Histogram \
       in_1=/home/dp/Documents/Research_paper_SFR/r_mcmc_uni/joined_data.csv \
-      leglabel_1=MCMC color_1=blue\
+      x_1=tau_up \
+      leglabel_1="MCMC\ with\ \tau \ \sim uniform(1,20)" color_1=blue\
    layer_2=Histogram \
       in_2=/home/dp/Documents/Research_paper_SFR/NR/filled_with_NR.csv \
+      x_2=tau_n \
       color_2=red \
       leglabel_2=N-R \
    layer_3=Histogram \
       in_3=/home/dp/Documents/Research_paper_SFR/r_mcmc_normal/joined_data.csv \
[…]

### 2025-03-16 template/thesis_01_titlepage.tex

\begin{titlepage}
%
%
\begin{figure*}[ht]
\centering
\includegraphics[width=0.95\textwidth]{logo_header.png}
\end{figure*}

\vspace{10mm}
\hbox{ % Horizontal box
\hspace*{0.08\textwidth} % Whitespace to the left of the title page
\rule{1.5pt}{0.80\textheight} % Vertical line
\hspace*{0.02\textwidth} % Whitespace between the vertical line and title page text
\parbox[b]{0.90\textwidth}{ % Paragraph box which restricts text to less than the width of the page

{\large \textsc{Πτυχιακή Εργασία}}\\[\baselineskip] % Tagline or further description
{\noindent\Large\bfseries
title
}\\[2\baselineskip] % Title

{\Large Doctor Who}\\ % AUTHOR's name
{Α/Μ~201800142}\\[3\baselineskip] % Registrar number for the AUTHOR

{\em Επιβλέπων:}\\[0.25\baselineskip]
{\large Despina Hatzidimitriou}\\[0.25\baselineskip] % SUPERVISOR's name
{\large Professor} % SUPERVISOR's Title

\vspace{0.15\textheight} % Whitespace between the blocks
{\noindent Athens 2025}\\[\baselineskip] % Place / Year
}}
%
%
\end{titlepage}

\newpage
\thispagestyle{empty}
\phantom{~}
\vfill

### 2025-03-16 method_comparison/cmd_MS_plots.py
fixed labels

@@ -15,6 +15,9 @@ for d in plot_dirs:
 # Load dataset
 df = pd.read_csv("joined_output_HECATE.csv")
 
+# set ggplot style
+plt.style.use('ggplot')
+
 # Define function to create and save CMD plots
 def plot_cmd(df, x_col, y_col, xlabel, ylabel, title, filename, folder, hue=None, cmap=False, invert_y=True, clabel = "Morphological Type"):
     plt.figure(figsize=(8, 6), dpi=350)
@@ -28,6 +31,10 @@ def plot_cmd(df, x_col, y_col, xlabel, ylabel, title, filename, folder, hue=None
         sns.scatterplot(data=df, x=x_col, y=y_col, edgecolor="k", alpha=0.7, marker=".")
     if invert_y:
         plt.gca().invert_yaxis()
+    #add grid
+    plt.grid(True)
+    #remove title from legend
+    plt.legend(title=None)
     plt.xlabel(xlabel)
     plt.ylabel(ylabel)
     plt.title(title)
@@ -41,35 +48,35 @@ xlabel_bu = r"$B - U$ (mag)"
 ylabel_mb = r"$M_B$ (Absolute Magnitude in B-band)"
 xlabel_bv = r"$B - V$ (mag)"
 ylabel_mb = r"$M_B$ (Absolute Magnitude in B-band)"
-xlabel_ms = r"$\log M_{\mathrm{total}}$ ($M_\odot$)"
-ylabel_ms = r"$\log \mathrm{SFR}_{\mathrm{total}}$ ($M_\odot$ yr$^{-1}$)"
+xlabel_ms = r"$\log M_{*}/M_\odot$"
+ylabel_ms = r"$\log (\mathrm{SFR}_{\mathrm{total}} /(M_\odot$ yr$^{-1}$))"
 
 # Categorize tau_up and tau_np for color coding
-df["tau_up_category"] = pd.cut(df["tau_up"], bins=[-float("inf"), 5, 10, float("inf")], labels=[r"$\tau_{up} < 5$ Gyr", r"$5 \leq \tau_{up} \leq 10$ Gyr", r"$\tau_{up} > 10$ Gyr"])
[…]

### 2025-03-22 r_mcmc_uni/_targets.R
20 arcsecs

@@ -87,7 +87,7 @@ tar_plan(
     parallel_chains = 8,
     iter_sampling = 5500,
     iter_warmup = 2500,
-    init = init_function(6, 1761),
+    init = init_function(6, 1691),
   ),
 
   ######## summaries#######

### 2025-03-22 method_comparison/sfrd.py
bmh+colors

@@ -112,6 +112,11 @@ log_sfrd_lm = np.log10(sfrd_lilly_madau)
 
 
 # Plot
+## set theme for the plot
+plt.style.use('bmh')
+# Reset color cycle to default
+plt.rcParams["axes.prop_cycle"] = plt.matplotlib.rcParamsDefault["axes.prop_cycle"]
+
 fig, ax1 = plt.subplots(figsize=(8, 6))
 ax2 = ax1.twiny()
 ax3 = ax1.twiny()

### 2025-03-23 thesis.qmd
added results

@@
 
-  **Keywords:** Galaxies, Galaxy Evolution, Star Formation History (SFH), Star Formation Rate (SFR), Delayed-$\tau$, Local Cosmological Volume, Lilly-Madau Plot, Redshift, Markov Chain Monte Carlo (MCMC).
+  **Keywords:** Galaxies, Galaxy Evolution, Star Formation History (SFH), Star Formation Rate (SFR), Delayed-$\tau$, Local Cosmological Volume, Lilly-Madau Plot, Redshift, Newton-Ramphson, Markov Chain Monte Carlo (MCMC).
 ---
@@
 \text{SFRD} = \frac{1}{V}\sum^N_{i=1}\text{SFR}_{o,i},
-$$
+$$ {#eq-SFRD}
 
@@
 \quad \left[M_\odot \,\mathrm{yr}^{-1}\,\mathrm{Mpc}^{-3}\right],
-$$
+$$ {#eq-lilly-madau}
 
@@
 
-![Alt text](NR/A-sSFR.png){#fig-A-sSFR}
+![$A_{del}-\text{sSFR}$ plot, where $A_{del}$ is calculated with different methods.
+In blue and green are the normalization constant values as they calculated by the MCMC method with different priors, while in red are results from Newton-Raphson.](method_comparison/sSFR_A.png){#fig-sSFR-A}
 
@@
 ::: {#fig-comp-sfr-obs-pred layout-ncol="2"}
-
 ![MCMC run for $\tau \sim \text{uniform}$ prior.](r_mcmc_uni/plots/sfr_diff_plot.png){#fig-comp-sfr-obs-pred-uni}
@@
 
-::: {#fig-A-M-mcmc layout-nrow="2"}
+::: {#fig-A-M-mcmc layout-ncol="2"}
+![Uniform $\tau$ prior](method_comparison/A_M_MCMC_uni.png){#fig-A-M-mcmc-uni}
 
-![Linear fit for $A_{del}\sim M_*$, with a correlation of 94%.
-The black dashed line is the linear regression weighted by $x$, with a fit $\log(A_{del}) = 0.95\cdot\log(M_*)+0.60, with a corralation of 98\%$](method_comparison/A_M_MCMC_uni.png){#fig-A-M-mcmc-uni}
+![Normal $\tau$ prior](method_comparison/A_M_MCMC_norm.png){#fig-A-M-mcmc-norm}
 
-![Linear fit for $A_{del}\sim M_*$, with a correlation of 99%.
-The black dashed line is the linear regression weighted by $x$, with a fit $\log(A_{del}) = 0.97\cdot\log(M_*)+0.44, with a corralation of 99.5\%$](method_comparison/A_M_MCMC_norm.png){#fig-A-M-mcmc-norm}
+Linear regression for $A_{del}-M_*$ for the $A_{del}$ values from the two MCMC runs.
+The black dashed line represents the regresion weighted by $x$.
+For the left plot, the regression yields a correlation of 94%, while the weighted regression is the fit $\log(A_{del}) = 0.95\cdot\log(M_*)+0.60$, with a correlation of 98%.
+For the right plot, the correlation is higher, at 99%, with a weighted regression of $\log(A_{del}) = 0.97\cdot\log(M_*)+0.44$, with a correlation of 99.5%.
 :::
 
-In @fig-sSFR-A-both-methods, it can be seen that the MCMC run does not have the same inconsistancies with the NR method, and in @fig-tau-hist-both it seems that the MCMC method captures better both the galaxies with small timescales, and the galaxies with slow rising SFR's.
+In @fig-sSFR-A, it can be seen that the MCMC run does not have the same inconsistancies with the NR method, and @fig-tau-hist-both shows that the MCMC method captures better both the galaxies with small timescales, and the galaxies with slow rising SFR's.
 
-![$A_{del}-\text{sSFR}$ plot, where $A_{del}$ is calculated with different methods.
-In blue and green are the normalization constant values as they calculated by the MCMC method with different priors, while in red are results from Newton-Raphson.](method_comparison/sSFR_A.png){#fig-sSFR-A-both-methods}
+::: {#fig-distr-comparison layout-ncol="2"}
+![Distribution of $\tau$ values.](method_comparison/tau_hist.png){#fig-tau-hist-both}
 
-![Distribution of $\tau$ values, from the two methods.
-In blue is the timescale distribution as it is calculated by the MCMC method, while in red are results from Newton-Raphson.](method_comparison/tau_hist.png){#fig-tau-hist-both}
+![Distribution of $t_{sf}$ values.](method_comparison/tsf_hist.png){#fig-tsf-hist-both}
+
+Distribution of the results of $\tau$ and $t_{sf}$ from all the methods.
+In blue are the distributions as they are calculated by the MCMC method with the uniform $\tau$ prior, in green are the results from the MCMC run with the normal prior, while in red are results from Newton-Raphson.
+:::
+
+In @fig-tau-hist-both, the distribution of the $\tau$ from the MCMC run with the uniform prior, has two peaks, the first peak at $\sim 2$ Gyr and one at $\sim 12$ Gyr.
+As shown in @fig-MS-tau, the galaxies contributing in the two peaks are in different parts of the Main Sequence, while the MCMC run with the normal prior depicts the galaxies of the MS as they are predicted by @speagleHighlyConsistentFramework2014, since every galaxy reaches its peak SFR at the a timescale $\tau < 5$.
+Additionaly the MCMC run with the normal prior, predicts a peak of the $t_{sf}$ distribution around 12-12.5 Gyr, closer to assumed values in @kroupaConstraintsStarFormation2020 and @haslbauerCosmologicalStarFormation2023 (@fig-tsf-hist-both).
+
+![Main Sequence of of the galaxies, color coded by the timescale $\tau$, from the MCMC run from with the uniform prior for $\tau$.
+The galaxies with slow rising SFR's are the galaxies above the center of the MS, while galaxies with $\tau$ predicted from @speagleHighlyConsistentFramework2014 are in the lower part of the MS.
+In the center of the MS are the rest of the galaxies](method_comparison/ms_plots/ms_tau_up.png){#fig-MS-tau}
+
+Having calculated the model parameters, it is possible to recunstruct the SFH of the galaxies, and from the @eq-SFRD, it is possible to calculate the SFRD of the LCV and recreate the Lilly-Madau Plot.
+As seen from @fig-lilly-madau, the results from the MCMC method are more consistent with the theoretical line give by the [@eq-lilly-madau; @madauCosmicStarFormation2014], while the NR method underastimates the SFRD of the LCV, by a factor[^11] greater than $\sim 3$, up until $z \approx 3$.
+From the three methods, the MCMC with the prior $\tau\sim \text{normal}$ is systematicaly closer to universal SFRD, indicating that the assumption for the prior is better than the uniform prior, while the NR line can not approximate the expected line.
+Eventhough the MCMC method could approximate the SFRD for small redshifts, at greater $z$ the model can overestimate the SFRD by a factor of $\sim 2-3.2$.
+
+[^11]: The factor is calculated by the residuals, $\log(SFRD_\text{data})-\log(SFRD_{LM})=\log\left(\frac{SFRD_\text{data}}{SFRD_{LM}}\right)\Leftrightarrow \frac{SFRD_\text{data}}{SFRD_{LM}} = 10^{\log(SFRD_\text{data})-\log(SFRD_{LM})}$
+
+::: {#fig-lilly-madau layout-ncol="2"}
+![SFH Reconstruction of the Local Cosmological Volume](method_comparison/sfrd_comparison_custom_axes_log_values.png)
+
+![Residuals of the SFH reconstruction of the LCV based on the theoritical line given by @madauCosmicStarFormation2014](method_comparison/sfrd_residuals_vs_lm.png)
+
+SFH Reconstructions of the Local Cosmological Volume, based on the three different methods
+:::
 

### 2025-03-23 NR/NR_sfr.py
compare the sfr with the data

@@ -41,13 +41,13 @@ def solve_x_n(i):
         def f_prime(x):
            return (2*k*x -np.exp(x)+1)
 
-        sol = optimize.root_scalar(f, x0=3, fprime=f_prime, method="newton")
+        sol = optimize.root_scalar(f, x0=4, fprime=f_prime, method="newton")
         return sol.root if sol.converged else np.nan
     except ValueError:
         return np.nan
 
 # Run the solver in parallel
-num_cores = 4  # Use all CPU cores
+num_cores = 8  # Use all CPU cores
 x_n[:] = Parallel(n_jobs=num_cores)(delayed(solve_x_n)(i) for i in range(len(dt)))
 
 # Compute A_n for all valid x_n (same as original, but vectorized)
@@ -61,6 +61,20 @@ dt['tau_n'] = np.empty(len(dt))
 dt["tau_n"][valid_x] = (t_sf/dt["x_n"][valid_x])
 dt["tau_n"][~valid_x] = np.nan
 dt["A_n"] = A_n * u.solMass  # Add units to A_n
+
+#Calculate the SFR based on the delayed tau model
+dt["SFR"] = dt["A_n"]*tsf/(dt["tau_n"]*10**9)**2*np.exp(-dt['x_n'])
+#calculate the total SFRD
+sum_SFR = np.sum(dt["SFR"][~np.isnan(dt["SFR"])].value)
+V = (4/3 * np.pi * 11**3)
+SFRD = sum_SFR/V
+logSFRD = np.log10(SFRD)
+print(f"\nTotal SFRD: {logSFRD:.2e} M_sun/yr/Mpc^3\n")
+#calculate the total SFRD for the original SFR
+sum_SFR_total = np.sum(dt["SFR_total"][~np.isnan(dt["SFR_total"])].value)
+SFRD_total = sum_SFR_total/V
+logSFRD_total = np.log10(SFRD_total)
+print(f"\nTotal SFRD: {logSFRD_total:.2e} M_sun/yr/Mpc^3\n")
 
 # Print stats (same as original)
 print(dt["x_n", "A_n", "tau_n"].info("stats"))
@@ -101,9 +115,28 @@ plt.savefig("NR/tau_A_double_plot.png")
 # Show the plot
 plt.close()
 
+# Plot the original SFR vs. the new SFR
+plt.scatter(dt["SFR_total"], dt["SFR"])
+plt.xscale("log")
+plt.yscale("log")
[…]

### 2025-03-23 method_comparison/sfrd.py
SFRD function of T0

@@ -10,20 +10,36 @@ import astropy.units as u
 data_uni = pd.read_csv('r_mcmc_uni/joined_data.csv')
 data_norm = pd.read_csv('r_mcmc_normal/joined_data.csv')
 data_nr = pd.read_csv('NR/filled_with_NR.csv')
+T0 = 13.8*1e9  # Age of the Universe in years
 
 # Define the A and tau values for each dataset
 A_values_uni = data_uni['A_up'].values
 tau_values_uni = (data_uni['tau_up']*u.Gyr.to(u.yr)).values
+tsf_values_uni = (data_uni['t_sf_up']*u.Gyr.to(u.yr)).values
+tstart_values_uni = T0 - tsf_values_uni
 sigma_A_values_uni = data_uni['A_sigma_up'].values
 sigma_tau_values_uni = (data_uni['tau_sigma_up']*u.Gyr.to(u.yr)).values
+sigma_tsf_values_uni = (data_uni['t_sf_sigma_up']*u.Gyr.to(u.yr)).values
+sigma_tstart_values_uni = sigma_tsf_values_uni
+
 
 A_values_norm = data_norm['A_np'].values
 tau_values_norm = (data_norm['tau_np']*u.Gyr.to(u.yr)).values
+tsf_values_norm = (data_norm['t_sf_np']*u.Gyr.to(u.yr)).values
+tstart_values_norm = T0 - tsf_values_norm
 sigma_A_values_norm = data_norm['A_sigma_np'].values
 sigma_tau_values_norm = (data_norm['tau_sigma_np']*u.Gyr.to(u.yr)).values
+sigma_tsf_values_norm = (data_norm['t_sf_sigma_np']*u.Gyr.to(u.yr)).values
+sigma_tstart_values_norm = sigma_tsf_values_norm
 
 A_values_nr = data_nr['A_n'].values
 tau_values_nr = (data_nr['tau_n']*u.Gyr.to(u.yr)).values
+tsf_values_nr = 13.6*1e9  # Fixed value for NR
+tstart_values_nr = T0 - tsf_values_nr  # This is a scalar (e.g. 0.2 Gyr)
+# For NR, we want t_start to be an array with one value per galaxy:
+tstart_values_nr = np.full_like(A_values_nr, tstart_values_nr)
+# Similarly, we assume no uncertainty for t_start in NR:
+sigma_tstart_values_nr = np.zeros_like(A_values_nr)
 
 # Volume factor
[…]

### 2025-03-23 thesis.qmd
added the parameter results + plot labels

@@
 
-![Alt text](NR/tau_A_double_plot.png){#fig-A-tau}
+![Paramater distribution of the delayed-$\tau$ SFH for the galaxies of the LCV.
+The colourbar represents the present-day stellar mass of the galaxies.
+The left plot shows the whole parameter range of the model, including negative timescales and $A_{del}$ values that occur by instabilities.
+In the right plot, the region $\tau \in [0,16]$ and $A_{del}\in[0,10^{13}]$ is depicted.
+The majority of the galaxies have a timescale of about 3.5-4.5 Gyr as expected from @speagleHighlyConsistentFramework2014](NR/tau_A_double_plot.png){#fig-A-tau}
 
@@
 
-![](/NR/A-M_*-c_x.png){#fig-A-M}
-
 Since convergence can not occur for $x\ll 1$, this method should not be used for galaxies in the begging phases of their star formation [^10].
 If the assumption, $t_{sf}=13.6$ Gyr for all the galaxies is correct, then an inconstancy in the plot $A_{del}-\text{sSFR}$ should only be observed, for higher values of the sSFR, since, according to the delayed- $\tau$ model, higher sSFR values indicate a rising SFR, while lower SFR values indicate that the bulk of $M_*$ is already produced and the galaxy is in the declining SFR phase.
-However, as seen from @fig-A-sSFR, this inconsistency occurs in galaxies for both high and low sSFR's, meaning that the the model has convergence issues both for slow rising SFR and quenching galaxies, indicating an intrinsic problem with this approach.
+However, as seen from @fig-sSFR-A, this inconsistency occurs in galaxies for both high and low sSFR's, meaning that the the model has convergence issues both for slow rising SFR and quenching galaxies, indicating an intrinsic problem with this approach.
 
@@
 Using these priors, the metrics of the Stan programm give good results ($\hat{R}<1.001$ and $\text{ESS} >1000$), while the calculated values correspond to the data of the catalog.
-Specifically, we use the data to recalculate the SFR from the predicted parameters, using the delayed-$\tau$ model and compare it to the observational data (@fig-comp-sfr-obs-pred), and also compare the normalization constant to the stellar masses of the galaxies (@fig-A-M-mcmc).
+Specifically, we use the data to recalculate the SFR from the predicted parameters, using the delayed-$\tau$ model and compare the normalization constant to the stellar masses of the galaxies (@fig-A-M-mcmc).
 
-::: {#fig-comp-sfr-obs-pred layout-ncol="2"}
-![MCMC run for $\tau \sim \text{uniform}$ prior.](r_mcmc_uni/plots/sfr_diff_plot.png){#fig-comp-sfr-obs-pred-uni}
-
-![MCMC run $\tau \sim \text{normal}$ prior.](r_mcmc_normal/plots/sfr_diff_plot.png){#fig-comp-sfr-obs-pred-norm}
-
-Comparison of the observed SFR with the predicted by the parameters given by the MCMC run.
-:::
-
-::: {#fig-A-M-mcmc layout-ncol="2"}
+::: {#fig-A-M-mcmc layout="[[50,50],[70]]"}
 ![Uniform $\tau$ prior](method_comparison/A_M_MCMC_uni.png){#fig-A-M-mcmc-uni}
@@
 
-Linear regression for $A_{del}-M_*$ for the $A_{del}$ values from the two MCMC runs.
-The black dashed line represents the regresion weighted by $x$.
-For the left plot, the regression yields a correlation of 94%, while the weighted regression is the fit $\log(A_{del}) = 0.95\cdot\log(M_*)+0.60$, with a correlation of 98%.
-For the right plot, the correlation is higher, at 99%, with a weighted regression of $\log(A_{del}) = 0.97\cdot\log(M_*)+0.44$, with a correlation of 99.5%.
+![Newton-Raphson Method](/NR/A-M_*-c_x.png){#fig-A-M}
+
+Linear regression for $A_{del}-M_*$ for the $A_{del}$ values from the two MCMC runs and the Newton-Raphson method, with the colorbar repressenting the ratio $x=t_{sf}/\tau$.
+For the MCMC runs, the black dashed line represents the regresion weighted by $x$.
+For the upper left plot, the regression yields a correlation of 94%, while the weighted regression is the fit $\log(A_{del}) = 0.95\cdot\log(M_*)+0.60$, with a correlation of 98%.
+For the upper right plot, the correlation is higher, at 99%, with a weighted regression of $\log(A_{del}) = 0.97\cdot\log(M_*)+0.44$, with a correlation of 99.5%.
+For the N-R plot, we do two different regressions for the two distinct regions of $A_{del}$, with the upper region only having a correlation of 55\%, while the lower region closely relating the normalization constant with the Stellar Masses of the galaxies, as described in the MCMC plots.
 :::

### 2025-03-26 thesis.qmd
final results+conclusion

@@
 
-  @haslbauerCosmologicalStarFormation2023 argue that the Delayed-$\tau$ model is opposed to the Lilly-Madau plot ([@madauCosmicStarFormation2014]), which plots the observed SFR's of galaxies with the corresponding redshifts ($z$) and calculates a cosmic SFR peak at $z\approx 2$.
+  @haslbauerCosmologicalStarFormation2023 argue that the use of Delayed-$\tau$ model for the galaxies of the Local Cosmological Volume (LCV) is opposed to the Lilly-Madau plot ([@madauCosmicStarFormation2014]), which plots the observed SFR's of galaxies with the corresponding redshifts ($z$) and calculates a cosmic SFR peak at $z\approx 2$.
 The way they calculated this inconsistency is by using observatory data for SFR and Stellar Masses from the UNGC catalog (@karachentsevUPDATEDNEARBYGALAXY2013, @karachentsevSTARFORMATIONPROPERTIES2013) for calculating the parameters (the timescale $\tau$ and the normalization constant $A_{del}$) of the model.
@@
 
-where $\tau$ is the timescale, $t_{\text{sf}} = t - T_0$ is the star formation time, $t$ is the age of the Universe, and $T_0$ is the time when star formation began.
+where $\tau$ is the timescale, $t_{\text{sf}} = T_0 - t_\text{start}$ is the star formation time, $T_0$ is the age of the Universe, and $t_\text{start}$ is the time when star formation began.
 
@@
 $$
-\text{SFR}_0 = \text{SFR}(t_{sf}) = A_{del}\frac{t_{sf}}{\tau^2}e^{-t_{sf}/\tau}
+\text{SFR}_0 = \text{SFR}(t_{sf}) = A_{del}\frac{t_{sf}}{\tau^2}e^{-t_{sf}/\tau},\ t_{sf} = T_0-t_\text{start}
 $$ {#eq-delayed-current}
@@
 
-The specific-SFR (sSFR) describes the rate of change of the stellar mass in a galaxy. Assuming a function $g(x)$ and its derivative $g'(x)$ for the Newton-Raphson algorithm:
+The specific-SFR (sSFR) provides a normalized view of star formation intensity. Assuming a function $g(x)$ and its derivative $g'(x)$ for the Newton-Raphson algorithm:
 
@@
 ![Paramater distribution of the delayed-$\tau$ SFH for the galaxies of the LCV.
-The colourbar represents the present-day stellar mass of the galaxies.
+The colorbar represents the present-day stellar mass of the galaxies.
 The left plot shows the whole parameter range of the model, including negative timescales and $A_{del}$ values that occur by instabilities.
@@
 
-![$A_{del}-\text{sSFR}$ plot, where $A_{del}$ is calculated with different methods.
-In blue and green are the normalization constant values as they calculated by the MCMC method with different priors, while in red are results from Newton-Raphson.](method_comparison/sSFR_A.png){#fig-sSFR-A}
+![$A_{del}-\text{sSFR}$ plot, where $A_{del}$ is calculated with different methods.](method_comparison/sSFR_A.png){#fig-sSFR-A}
 
@@
 
-we can create a MCMC model to calculate the parameters, with the priors:
-
--   $t_{sf}\sim \text{uniform(lower bound = 1 Gyr, upper bound = 13.8 Gyr)}$,
--   $\zeta \sim \text{normal(mean=1.3, }\sigma = 0.01)$, within the limits $[1,2]$,
-
-and the likelihood $\log(\text{SFR}_{obs}) \sim \text{normal}\left(\log(\text{SFR}_\text{MCMC}), \sigma = 0.1\right)$, while taking the Stellar Masses of the galaxies as they are, without any variance, and $A_{del}$ is calculated by @eq-A.
+we can create a MCMC model to calculate the parameters, with the priors $t_{sf}\sim \text{uniform(lower bound = 1 Gyr, upper bound = 13.8 Gyr)}$, $\zeta \sim \text{normal(mean=1.3, }\sigma = 0.01)$, within the limits $[1,2]$ and the likelihood $\log(\text{SFR}_{obs}) \sim \text{normal}\left(\log(\text{SFR}_\text{MCMC}), \sigma = 0.1\right)$, while taking the Stellar Masses of the galaxies as they are, without any variance, and $A_{del}$ is calculated by @eq-A.
 For the $\tau$ we will consider two different priors, $\tau \sim \text{uniform(lower bound = 1 Gyr, upper bound = 13.8 Gyr)}$ and $\tau \sim \text{normal(mean = 4 Gyr, }\sigma  = 13.8 \text{Gyr)}$.
@@
 However, there is bibliography that could justify using a normal distribution for $\tau$, for example @speagleHighlyConsistentFramework2014 and @kroupaConstraintsStarFormation2020 explain that the galaxies of the Main Sequence are expected to have $3.5\lesssim\tau/\text{Gyr}\lesssim4.5$.
-The same prior will not apply for $t_{sf}$ since it could significatly effect the results, especially of younger galaxies.
+The same prior will not apply for $t_{sf}$ since it could significantly effect the results, especially of younger galaxies.
 
-Using these priors, the metrics of the Stan programm give good results ($\hat{R}<1.001$ and $\text{ESS} >1000$), while the calculated values correspond to the data of the catalog.
+Using these priors, the metrics of the Stan program give good results ($\hat{R}<1.001$ and $\text{ESS} >1000$), while the calculated values correspond to the data of the catalog.
 Specifically, we use the data to recalculate the SFR from the predicted parameters, using the delayed-$\tau$ model and compare the normalization constant to the stellar masses of the galaxies (@fig-A-M-mcmc).
 
-::: {#fig-A-M-mcmc layout="[[50,50],[70]]"}
-![Uniform $\tau$ prior](method_comparison/A_M_MCMC_uni.png){#fig-A-M-mcmc-uni}
-
-![Normal $\tau$ prior](method_comparison/A_M_MCMC_norm.png){#fig-A-M-mcmc-norm}
-
-![Newton-Raphson Method](/NR/A-M_*-c_x.png){#fig-A-M}
-
-Linear regression for $A_{del}-M_*$ for the $A_{del}$ values from the two MCMC runs and the Newton-Raphson method, with the colorbar repressenting the ratio $x=t_{sf}/\tau$.
-For the MCMC runs, the black dashed line represents the regresion weighted by $x$.
-For the upper left plot, the regression yields a correlation of 94%, while the weighted regression is the fit $\log(A_{del}) = 0.95\cdot\log(M_*)+0.60$, with a correlation of 98%.
-For the upper right plot, the correlation is higher, at 99%, with a weighted regression of $\log(A_{del}) = 0.97\cdot\log(M_*)+0.44$, with a correlation of 99.5%.
-For the N-R plot, we do two different regressions for the two distinct regions of $A_{del}$, with the upper region only having a correlation of 55\%, while the lower region closely relating the normalization constant with the Stellar Masses of the galaxies, as described in the MCMC plots.
-:::
-
-In @fig-sSFR-A, it can be seen that the MCMC run does not have the same inconsistancies with the NR method, and @fig-tau-hist-both shows that the MCMC method captures better both the galaxies with small timescales, and the galaxies with slow rising SFR's.
-
-::: {#fig-distr-comparison layout-ncol="2"}
+::: {#fig-distr-comparison layout-ncol="2" fig-pos="b"}
 ![Distribution of $\tau$ values.](method_comparison/tau_hist.png){#fig-tau-hist-both}
@@
 Distribution of the results of $\tau$ and $t_{sf}$ from all the methods.
-In blue are the distributions as they are calculated by the MCMC method with the uniform $\tau$ prior, in green are the results from the MCMC run with the normal prior, while in red are results from Newton-Raphson.
 :::
+
+In @fig-sSFR-A, it can be seen that the MCMC run does not have the same inconsistencies with the N-R method, and @fig-tau-hist-both shows that the MCMC method captures better both the galaxies with small timescales, and the galaxies with slow rising SFR's.
 
@@
 
+::: {#fig-A-M-mcmc layout="[[50,50],[1]]" fig-pos="hb"}
+![Uniform $\tau$ prior](method_comparison/A_M_MCMC_uni.png){#fig-A-M-mcmc-uni}
+
+![Normal $\tau$ prior](method_comparison/A_M_MCMC_norm.png){#fig-A-M-mcmc-norm}
+
+![Newton-Raphson Method](/NR/A-M_*-c_x.png){#fig-A-M width="60%"}
+
+Linear regression for $A_{del}-M_*$ for the $A_{del}$ values from the two MCMC runs and the Newton-Raphson method, with the colorbar representing the ratio $x=t_{sf}/\tau$.
+For the MCMC runs, the black dashed line represents the regression weighted by $x$.
+For the upper left plot, the regression yields a correlation of 94%, while the weighted regression is the fit $\log(A_{del}) = 0.95\cdot\log(M_*)+0.60$, with a correlation of 98%.
+For the upper right plot, the correlation is higher, at 99%, with a weighted regression of $\log(A_{del}) = 0.97\cdot\log(M_*)+0.44$, with a correlation of 99.5%.
+For the N-R plot, we do two different regressions for the two distinct regions of $A_{del}$, with the upper region only having a correlation of 55%, while the lower region closely relating the normalization constant with the Stellar Masses of the galaxies, as described in the MCMC plots.
+:::
+
 ![Main Sequence of of the galaxies, color coded by the timescale $\tau$, from the MCMC run from with the uniform prior for $\tau$.
@@
 
-Having calculated the model parameters, it is possible to recunstruct the SFH of the galaxies, and from the @eq-SFRD, it is possible to calculate the SFRD of the LCV and recreate the Lilly-Madau Plot.
-As seen from @fig-lilly-madau, the results from the MCMC method are more consistent with the theoretical line give by the [@eq-lilly-madau; @madauCosmicStarFormation2014], while the NR method underastimates the SFRD of the LCV, by a factor[^11] greater than $\sim 3$, up until $z \approx 3$.
-From the three methods, the MCMC with the prior $\tau\sim \text{normal}$ is systematicaly closer to universal SFRD, indicating that the assumption for the prior is better than the uniform prior, while the NR line can not approximate the expected line.
-Eventhough the MCMC method could approximate the SFRD for small redshifts, at greater $z$ the model can overestimate the SFRD by a factor of $\sim 2-3.2$.
+Having calculated the model parameters, it is possible to reconstruct the SFH of the galaxies, and from the @eq-SFRD, it is possible to calculate the SFRD of the LCV and recreate the Lilly-Madau Plot.
+Using the equations @eq-delayed-current and @eq-SFRD, we get the equation:
 
-[^11]: The factor is calculated by the residuals, $\log(SFRD_\text{data})-\log(SFRD_{LM})=\log\left(\frac{SFRD_\text{data}}{SFRD_{LM}}\right)\Leftrightarrow \frac{SFRD_\text{data}}{SFRD_{LM}} = 10^{\log(SFRD_\text{data})-\log(SFRD_{LM})}$
+$$
+\text{SFRD(T)} = \frac{1}{V}\sum^N_{i=1} A_{del}\frac{T-t_\text{start}}{\tau^2}\exp\left(-\frac{T-t_\text{start}}{\tau}\right),
+$$ {#eq-SFRD-delayed}
 
-::: {#fig-lilly-madau layout-ncol="2"}
+where $t_\text{start}$, is calculated by the computed $t_{sf}=T_0-t_\text{start}$, and $T$ is the age of the universe ($T_0$ is the current age=13.8 Gyr).
+Using this equation we can recreate the parameterized SFRD.
+
+<!-- ![Residuals of the SFH reconstruction of the LCV based on the theoritical line given by @madauCosmicStarFormation2014](method_comparison/sfrd_residuals_vs_lm.png) -->
+
+::: {#fig-lilly-madau-rec layout-ncol="2"}
 ![SFH Reconstruction of the Local Cosmological Volume](method_comparison/sfrd_comparison_custom_axes_log_values.png)
 
-![Residuals of the SFH reconstruction of the LCV based on the theoritical line given by @madauCosmicStarFormation2014](method_comparison/sfrd_residuals_vs_lm.png)
+![Ratio between the cosmic SFRD measured by @madauCosmicStarFormation2014 and the SFRD of the LCV](method_comparison/sfrd_ratio_vs_lm.png)
 
@@
 :::
+
+As seen from @fig-lilly-madau-rec, the MCMC method can approximate better the SFRD of the LCV up until $z\sim 2$ with a factor less than 2.
+At the peak of the cosmic SFRD, at $z=1.86$, the uniform and normal priors underestimate the SFRD by a factor of 1.82 and 1.53 respectively, while the N-R underestimates it by a factor of 3.6.
+In the paper, @haslbauerCosmologicalStarFormation2023, they estimate a factor of 2.16 at the peak, using the SFR's from the UNGC catalogs.
+However, the ratio of the MCMC grows with $z$, since many galaxies start forming stars at a lookback time of $\sim 12$ Gyr, as seen in @fig-tsf-hist-both (the mean value of the $t_{sf}$ of the galaxies is 10 Gyr for the uniform prior and 9.8 Gyr for the normal prior), resulting in extreme deviations from the cosmic SFRD.
+
+{{<pagebreak>}}
+
+# Conclusions
+
+With the use of IR data for the SFR of the LCV and with the use of different algorithms, we were able to reduce the divergence of the SFRD of the LCV from the cosmic SFRD from a factor of 2.16 to 1.53 at $z=1.86$.
+The N-R, can describe better the SFRD of the LCV compared to the MCMC for higher redshifts, but fails to approximate it for lower redshifts.
+The high divergence of the MCMC approximations, for $z>2$ is a result of the wrong prior of the $t_{sf}$.
+Using uniform priors for the time of star formations, severely underestimates the time in which most galaxies start the star forming process, meaning that most of the galaxies stop contributing at the SFRD at earlier lookback times than they should.
+
+A better assumption for the prior of $t_{sf}$, which pushes the mean $\overline{t_{start}}\approx0.2$ Gyr, could correct the model at higher redshifts, since it would approximate the assumption of the N-R, while also keeping the lower factor of the MCMC at the peak of the Lilly-Madau plot.
+A possible prior for the $t_{sf}$ could be a skewed normal distribution with a mean value $\overline{t_{sf}}\approx 13$ Gyr and with a large sigma to cover the younger galaxies of the LCV.
+Another possible distribution could be a log-normal distribution for the $t_{start}$.
+But since the choice of a prior can significantly affect the results and because of the lack of a bibliography for this model, for this undergraduate thesis, the choice of a uniform is the safest choice.
+
+Based on our results, we cannot safely assume that the model works for the galaxies of the LCV.
+Since parameterized SFH models do not account for bursty star formation, events characteristic of starburst galaxies, incorporating additional parameters who depend on $\text{SFR}_{H\alpha}$ and $\text{SFR}_\text{FUV}$ could increase the accuracy of the model.
+Additionaly, only examining one model ignores the intrinsic characteristics of the galaxies.
+@haslbauerCosmologicalStarFormation2023, introduce a combined SFH model depending on the mass of the galaxies, which can reduce the difference of the predicted model and the cosmic SFRD.
+
+In summary, the use of the MCMC and the data from the HECATE catalog proves that the delayed-$\tau$ model a better approximation of the SFH, as originally argued by @haslbauerCosmologicalStarFormation2023.
+However, more fine-tuning of the model is needed to be certain if the delayed-$\tau$ model is a robust approximation of the SFH of the galaxies of the Local Cosmological Volume.
 

### 2025-03-26 method_comparison/sfrd.py
added skew

@@ -9,6 +9,7 @@ import astropy.units as u
 # Import data
 data_uni = pd.read_csv('r_mcmc_uni/joined_data.csv')
 data_norm = pd.read_csv('r_mcmc_normal/joined_data.csv')
+data_skew = pd.read_csv('r_mcmc_skew/joined_data.csv')
 data_nr = pd.read_csv('NR/filled_with_NR.csv')
 T0 = 13.8*1e9  # Age of the Universe in years
 
@@ -31,6 +32,16 @@ sigma_A_values_norm = data_norm['A_sigma_np'].values
 sigma_tau_values_norm = (data_norm['tau_sigma_np']*u.Gyr.to(u.yr)).values
 sigma_tsf_values_norm = (data_norm['t_sf_sigma_np']*u.Gyr.to(u.yr)).values
 sigma_tstart_values_norm = sigma_tsf_values_norm
+
+#for skew
+A_values_skew = data_skew['A_np'].values
+tau_values_skew = (data_skew['tau_np']*u.Gyr.to(u.yr)).values
+tsf_values_skew = (data_skew['t_sf_np']*u.Gyr.to(u.yr)).values
+tstart_values_skew = T0 - tsf_values_skew
+sigma_A_values_skew = data_skew['A_sigma_np'].values
+sigma_tau_values_skew = (data_skew['tau_sigma_np']*u.Gyr.to(u.yr)).values
+sigma_tsf_values_skew = (data_skew['t_sf_sigma_np']*u.Gyr.to(u.yr)).values
+sigma_tstart_values_skew = sigma_tsf_values_skew
 
 A_values_nr = data_nr['A_n'].values
 tau_values_nr = (data_nr['tau_n']*u.Gyr.to(u.yr)).values
@@ -169,6 +180,17 @@ total_sfr_norm, total_sfr_error_norm = compute_total_sfr_and_error(
     sigma_tau_values=sigma_tau_values_norm
 )
 
+#Skew Prior Dataset
+total_sfr_skew, total_sfr_error_skew = compute_total_sfr_and_error(
+    z_array=redshifts,
+    t_start=tstart_values_skew,
+    sigma_t_start=sigma_tstart_values_skew,
+    A_values=A_values_skew,
+    tau_values=tau_values_skew,
+    sigma_A_values=sigma_A_values_skew,
+    sigma_tau_values=sigma_tau_values_skew
+)
+
 # NR Dataset (no uncertainties available)
[…]

### 2025-03-26 r_mcmc_skew/_targets.R
added skew

@@ -1,0 +1,297 @@
+# Created by use_targets().
+# Follow the comments below to fill in this target script.
+# Then follow the manual to check and run the pipeline:
+#   https://books.ropensci.org/targets/walkthrough.html#inspect-the-pipeline
+
+# Load packages required to define the pipeline:
+library(targets)
+library(tarchetypes) # Load other packages as needed.
+library(stantargets)
+library(crew)
+library(future)
+
+# Set target options:
+tar_option_set(
+  packages = c("readr", "tidyverse", "tibble", "stringr", "posterior", "bayesplot", "loo", "ggplot2", "scales", "latex2exp", "ggeasy"),
+  # format = "qs", # Optionally set the default storage format. qs is fast.
+  #
+  # Pipelines that take a long time to run may benefit from
+  # optional distributed computing. To use this capability
+  # in tar_make(), supply a {crew} controller
+  # as discussed at https://books.ropensci.org/targets/crew.html.
+  # Choose a controller that suits your needs. For example, the following
+  # sets a controller that scales up to a maximum of two workers
+  # which run as local R processes. Each worker launches when there is work
+  # to do and exits if 60 seconds pass with no tasks to run.
+  #
+  # controller = crew::crew_controller_local(workers = 6)
+  #
+  # Alternatively, if you want workers to run on a high-performance computing
+  # cluster, select a controller from the {crew.cluster} package.
+  # For the cloud, see plugin packages like {crew.aws.batch}.
+  # The following example is a controller for Sun Grid Engine (SGE).
+  #
+  #   controller = crew.cluster::crew_controller_sge(
+  #     # Number of workers that the pipeline can scale up to:
+  #     workers = 10,
+  #     # It is recommended to set an idle time so workers can shut themselves
+  #     # down if they are not running tasks.
+  #     seconds_idle = 120,
+  #     # Many clusters install R as an environment module, and you can load it
+  #     # with the script_lines argument. To select a specific verison of R,
+  #     # you may need to include a version string, e.g. "module load R/4.3.2".
[…]

### 2025-03-26 thesis.qmd
minor pdf fixes

@@
 This is why there are various theoretical models trying to describe the SFH of galaxies.
-One of those models is the Delayed-Tau model, which approximates the Star Formation Rates (SFR) of galaxies as a function with a rising SFR at the beginning, until it reaches a peak at a time $\tau$, unique for each galaxy, and then it drops at an exponential rate.
+One of those models is the Delayed-Tau model, which approximates the star formation of galaxies as a function with a rising Star Formation Rate (SFR) at the beginning, until it reaches a peak at a time $\tau$, unique for each galaxy, and then it drops at an exponential rate.
 
   @haslbauerCosmologicalStarFormation2023 argue that the use of Delayed-$\tau$ model for the galaxies of the Local Cosmological Volume (LCV) is opposed to the Lilly-Madau plot ([@madauCosmicStarFormation2014]), which plots the observed SFR's of galaxies with the corresponding redshifts ($z$) and calculates a cosmic SFR peak at $z\approx 2$.
-The way they calculated this inconsistency is by using observatory data for SFR and Stellar Masses from the UNGC catalog (@karachentsevUPDATEDNEARBYGALAXY2013, @karachentsevSTARFORMATIONPROPERTIES2013) for calculating the parameters (the timescale $\tau$ and the normalization constant $A_{del}$) of the model.
+The way they calculated this inconsistency is by using observational data for SFR and galaxy masses from the UNGC catalog (@karachentsevUPDATEDNEARBYGALAXY2013, @karachentsevSTARFORMATIONPROPERTIES2013) for calculating the parameters (the timescale $\tau$ and the normalization constant $A_{del}$) of the model.
 This calculation for the galaxies of the Local Cosmological Volume (LV), allows the investigation of the SFR throughout the life of each galaxy and so we can find the expected time of peak of the SFR.
@@
 
-# Galaxy Morphology and Star-Forming Regions
+# Galaxies and Galaxy Morphology
 
@@
 
-[^1]: The chain is homogeneous if $T \forall x^{(i)}$ remains invariant (the probability of moving from $x^{(i−1)}$ to $x^{(i)}$ does not depend on the iteration number $i$.) and $\sum_{x^{(i)}} T\bigl(x^{(j)} \mid x^{(i-1)}\bigr) = 1$.
+[^1]: For more information about the Great Debate, visit <https://apod.nasa.gov/debate/1920/cs_real.html>
 
@@
 
-    -   Assigned positive T-values , extending to +11 for extreme irregulars.
+    -   Assigned positive Numerical Morphological T-Types, extending to +11 for extreme irregulars.
 
@@
 
+# Star Formation
+
+The SFH of a galaxy describes the evolution of its star formation rate over time.
+By selecting an appropriate model for SFH, we can analyze stellar production, predict periods of active or quiescent star formation, and determine when SFR stabilizes.
+
+Understanding SFH models is crucial for interpreting internal and external processes affecting galaxies and identifying conditions for intense star formation in their early stages.
+
 ## Star-Forming Regions
@@
 
-# Star Formation History (SFH)
-
-The SFH of a galaxy describes the evolution of its star formation rate over time.
-By selecting an appropriate model for SFH, we can analyze stellar production, predict periods of active or quiescent star formation, and determine when SFR stabilizes.
-
-Understanding SFH models is crucial for interpreting internal and external processes affecting galaxies and identifying conditions for intense star formation in their early stages.
-
 ## Star Formation Rate
@@
 $$
-\int_0^{t_{sf}} \text{SFR}(t)dt = \zeta M_*(t_{sf}),\ t_{sf}=\text{Time of Star Formation,} 
+\int_{t_\text{start}}^{t_\text{final}} \text{SFR}(t)dt = \zeta M_*(t_{sf}),\ t_{sf}=\text{Time of Star Formation,} 
 $$ {#eq-sfr_int}
@@
 Dust can significantly affect observations.
+Since this estimator depends on young stars, it gives us information about the present day star formation (\~10 Myr).
 
--   **Far-Ultraviolet (FUV) Flux**: Mainly emitted by young, hot stars ( B-type stars, \~100 Myr). Dust presence can also significantly affect observations.
+-   **Far-Ultraviolet (FUV) Flux**: Mainly emitted by young, hot stars ( B-type stars, \~100 Myr).
+Dust presence can also significantly affect observations.
+Since this estimator depends on young stars, it gives us information about the present day star formation (\~100 Myr).
 
@@
 As a result, the total IR emission is age-agnostic and provides a more accurate approximation of the SFR because it accounts for contributions from both young and old stellar populations.
-
--   **Radio Continuum Emission**: Strongly correlated with IR. Its origin is complex, involving synchrotron radiation from relativistic electrons and thermal Bremsstrahlung from hot gas.
-
--   **X-Ray Emission**: In star-forming galaxies, X-rays arise from high-mass binary systems (neutron star or black hole with massive stellar companion) and hot gas from supernovae, correlating with SFR up to redshift $z \sim 4$.
-X-rays are dust-insensitive, enabling accurate high-redshift observations.
+Since this estimator is somewhat age agnostic, but is derived from the radiaton of heated dust, it is an estimator for the current star formation rate and not the present SFR (\~ 300 Myr).
 
@@
 
-where $\mathcal{K}_i$ is a constant specific to each $L_i$ ($i =$ H$\alpha$, IR, radio, FUV, X). In our analysis, we lack radio and X-ray data.
+where $\mathcal{K}_i$ is a constant specific to each $L_i$ ($i =$ H$\alpha$, IR, radio, FUV, X).
+
+![Plot showing the linear relation $\log\text{SFR}_{FUV} = \log\text{SFR}_{H\alpha}$, as well as their distributions, based on the data from UNGC](figure/log_SFR_FUV_Ha.png){#fig-SFR-Ha-FUV fig-align="center" width="400" fig-pos="t"}
 
@@
 where $L_{\text{FUV}}$ and $L_{\text{H}\alpha}$ are corrected for dust attenuation.
-
-![Plot showing the linear relation $\log\text{SFR}_{FUV} = \log\text{SFR}_{H\alpha}$, as well as their distributions, based on the data from UNGC](figure/log_SFR_FUV_Ha.png){#fig-SFR-Ha-FUV fig-align="center" width="500"}
 
@@
 
-where $\alpha(t)$ and $\beta(t)$ depend on time and redshift $z$ (@speagleHighlyConsistentFramework2014):
+where $\alpha(t)$ and $\beta(t)$ depend on time and redshift $z$ (@speagleHighlyConsistentFramework2014).
 
-### Star Formation History Models
+![The Main Sequence of the galaxies within the radius of 10 Mpc, with the colorbar representing their morphological type.
+From the linear fit we get $\alpha(T_0) = 0.86$ and $\beta(T_0)= 9.83$.
+Early types have lower Stellar Masses and SFR, while spiral galaxies have more intense SF](method_comparison/ms_plots/ms_morph.png){#fig-ms-Type width="60%"}
 
-![Star Formation Rate over the time of star formation, for different parametric models](images/sfr-models.png){fig-align="center" width="300"}
+## Star Formation History Models
 
@@
 This accounts for an initial growth phase followed by a decline. In this case, $\tau$ represents the time it takes for the galaxy to reach $\text{SFR}_{\text{max}}$.
+
+![Star Formation Rate over the time of star formation, for different parametric models](images/sfr-models.png){fig-align="center" width="500" fig-pos="ht"}
 
@@
 
-![The history of cosmic star formation as shown in @madauCosmicStarFormation2014](images/lily-madau.png){fig-align="center" width="450"}
-
 Using observational data from UV and IR traces for the SFR for galaxies of different redshifts ($z$) @madauCosmicStarFormation2014 where able to calculate the cosmic SFRD, at different ages of the universe, and reveals three periods of the universe.
@@
 
+![The history of cosmic star formation as shown in @madauCosmicStarFormation2014](images/lily-madau.png){fig-align="center" width="450" fig-pos="t"}
+
 ## Delayed-$\tau$ model
@@
 
-where $\text{SFR}_0$ is given in the catalogs.
+![The evolution of the SFR of a galaxy over the time of star formation, according to the delayed-$\tau$.
+The time need for the galaxy to reach the peak of its star formation is the timescale $\tau$ of the model](images/delayed_tau_sfr.png)
+
+where the current $\text{SFR}_0$ of the galaxies, at the current age of the universe $T_0=13.8$ Gyr, is given in the catalogs.
 According to these model the timescale, at which the SFR peaks, is around $3.5\lessapprox\tau\lessapprox 4.5$ [@speagleHighlyConsistentFramework2014].
@@
 $$
-\overline{\text{SFR}_\text{del}} = \frac{\zeta M_*}{t_sf}
+\overline{\text{SFR}_\text{del}} = \frac{\zeta M_*}{t_{sf}}
 $$ {#eq-averaged-SFR-M}
@@
 In our current analysis, we will use two different catalogs of galaxies, containing galaxies within the Local Cosmological Volume (LV), which is defined as a sphere with a radius of 11 Mpc centred around the Milky Way, to remain consistent with with the analysis of @kroupaConstraintsStarFormation2020 and @haslbauerCosmologicalStarFormation2023.
-The reason we focus on the LV and thus only at small distances is because we want to understand the SFR of the galaxies as they are today and since the redshift depends on distance, we can assume that the redshift of our galaxy sample is $z = 0 \Rightarrow t_\text{emitted}=T_0 = 13.8$ Gyr.
+The reason we focus on the LV and thus only at small distances is because we want to understand the SFR of the galaxies as they are today $z = 0 \Rightarrow t_\text{emitted}=T_0 = 13.8$ Gyr.
 
@@
 For galaxies with luminosities around $10^{10} L_{B,\odot}$, the catalog remains complete up to distances of 100 Mpc.
--   **Luminosity Density:** The catalog's completeness is also estimated based on the luminosity density in the B-band.
-Within 30 Mpc, the catalog is over 100% complete due to the high density of galaxies around the Milky Way.
-However, at distances around 170 Mpc, the completeness drops to approximately 50%, indicating that many galaxies are missing.
--   **Star Formation Rate and Stellar Mass:** The completeness of SFR is around 50% for distances between 30 and 150 Mpc, primarily due to limitations in the WISE survey coverage.
+-   **Star Formation Rate and Stellar Mass:** The percentage of the galaxies with measured SFR is around 50% for distances between 30 and 150 Mpc, primarily due to limitations in the WISE survey coverage.
 Similarly, the completeness of stellar mass estimates is comparable to that of the B-band luminosity, with overdensities at short distances and a sharp cutoff at larger distances.
@@
 In the Local Group ($D \leq 10 \, \text{Mpc}$) only half the galaxies have $M_B^c > -11^m$ and it is expected that for distances $\sim 9 \, \text{Mpc}$ more than half of the ultra-faint galaxies are missing.
-Specifically, it is estimated that around $10^3–10^4$ galaxies of the LV are not included in UNGC.
+Specifically, it is estimated that around $10^3–10^4$ galaxies of the LV are not included in UNG.
 
@@
 
-Since convergence can not occur for $x\ll 1$, this method should not be used for galaxies in the begging phases of their star formation [^10].
+Since convergence can not occur for $x\ll 1$, this method should not be used for galaxies in the begining phases of their star formation [^10].
 If the assumption, $t_{sf}=13.6$ Gyr for all the galaxies is correct, then an inconstancy in the plot $A_{del}-\text{sSFR}$ should only be observed, for higher values of the sSFR, since, according to the delayed- $\tau$ model, higher sSFR values indicate a rising SFR, while lower SFR values indicate that the bulk of $M_*$ is already produced and the galaxy is in the declining SFR phase.
@@
 
-Using these priors, the metrics of the Stan program give good results ($\hat{R}<1.001$ and $\text{ESS} >1000$), while the calculated values correspond to the data of the catalog.
-Specifically, we use the data to recalculate the SFR from the predicted parameters, using the delayed-$\tau$ model and compare the normalization constant to the stellar masses of the galaxies (@fig-A-M-mcmc).
+[^11]: For more information about the usage of Stan and its metrics can be found here: <https://mc-stan.org/>
 
-::: {#fig-distr-comparison layout-ncol="2" fig-pos="b"}
+::: {#fig-distr-comparison layout-ncol="2" fig-pos="h"}
 ![Distribution of $\tau$ values.](method_comparison/tau_hist.png){#fig-tau-hist-both}
@@
 
+Using these priors, the metrics of the Stan software[^11] give good results ($\hat{R}<1.001$ and $\text{ESS} >1000$), while the calculated values correspond to the data of the catalog.
+Specifically, we use the data to recalculate the SFR from the predicted parameters, using the delayed-$\tau$ model and compare the normalization constant to the stellar masses of the galaxies (@fig-A-M-mcmc).
+
 In @fig-sSFR-A, it can be seen that the MCMC run does not have the same inconsistencies with the N-R method, and @fig-tau-hist-both shows that the MCMC method captures better both the galaxies with small timescales, and the galaxies with slow rising SFR's.
+
+![Main Sequence of of the galaxies, color coded by the timescale $\tau$, from the MCMC run from with the uniform prior for $\tau$.
+The galaxies with slow rising SFR's are the galaxies above the center of the MS, while galaxies with $\tau$ predicted from @speagleHighlyConsistentFramework2014 are in the lower part of the MS.
+In the center of the MS are the rest of the galaxies](method_comparison/ms_plots/ms_tau_up.png){#fig-MS-tau width="60%" fig-pos="h"}
 
@@
 
-::: {#fig-A-M-mcmc layout="[[50,50],[1]]" fig-pos="hb"}
+::: {#fig-A-M-mcmc layout="[[50,50],[1]]" fig-pos="h"}
 ![Uniform $\tau$ prior](method_comparison/A_M_MCMC_uni.png){#fig-A-M-mcmc-uni}
@@
 :::
-
-![Main Sequence of of the galaxies, color coded by the timescale $\tau$, from the MCMC run from with the uniform prior for $\tau$.
-The galaxies with slow rising SFR's are the galaxies above the center of the MS, while galaxies with $\tau$ predicted from @speagleHighlyConsistentFramework2014 are in the lower part of the MS.
-In the center of the MS are the rest of the galaxies](method_comparison/ms_plots/ms_tau_up.png){#fig-MS-tau}
 
@@
 
-SFH Reconstructions of the Local Cosmological Volume, based on the three different methods
+SFH Reconstructions of the Local Cosmological Volume, based on the three different methods. Ignore the Skew prior (Red), is a proof of concept.
 :::
@@
 
-{{<pagebreak>}}
+<!-- {{<pagebreak>}} -->
 

### 2025-03-26 images/delayed.py

@@ -6,8 +6,11 @@ def delayed_tau_sfr(t_sf, A_del, tau):
 
 def plot_delayed_tau(A_del=1, taus=[1, 2, 3, 4, 5], t_max=10, num_points=1000):
     t_sf = np.linspace(0, t_max, num_points)  # Avoid t_sf = 0 for numerical stability
-    
-    plt.figure(figsize=(8, 6))
+    ## set theme for the plot
+    plt.style.use('bmh')
+    # Reset color cycle to default
+    plt.rcParams["axes.prop_cycle"] = plt.matplotlib.rcParamsDefault["axes.prop_cycle"]
+    plt.figure(figsize=(10, 6))
     for tau in taus:
         sfr = delayed_tau_sfr(t_sf, A_del, tau)
         plt.plot(t_sf, sfr, label=r"$\tau$ ="+f"{tau} Gyr")
@@ -18,7 +21,8 @@ def plot_delayed_tau(A_del=1, taus=[1, 2, 3, 4, 5], t_max=10, num_points=1000):
     plt.ylabel(r"$\text{SFR}_{del}(t_{sf})\ [M_\odot \cdot yr^{-1}]$")
     plt.title(r"Delayed-$\tau$ Model, for $A_{del} = 1\ M_\odot$")
     plt.legend()
-    plt.grid()
+    plt.tight_layout()
+    #plt.grid()
     plt.savefig("images/delayed_tau_sfr.png")
     plt.close()
 

### 2025-03-26 images/sfr-models.R

@@ -30,10 +30,10 @@ ggplot(data, aes(x = t, y = SFR, color = Model)) +
   labs(
     title = "Star Formation Rate Models",
     x = TeX("Star Formation time ( $t_{sf}$ ) [Gyr]"),
-    y = TeX("SFR($t_{sf}$) [ M$_*$/yr ]" ),
-    color = "Model"
+    y = TeX("SFR($t_{sf}$) [ M$_*$/yr ]"),
+    color = "Model",
   ) +
   scale_x_continuous(limits = c(0, 12)) +
   theme_minimal() +
   theme(plot.title = element_text(hjust = 0.5))
-ggsave("figure/sfr-models.png")
+ggsave("./images/sfr-models.png", width = 10, height = 6, dpi = 300)

### 2025-03-26 method_comparison/cmd_MS_plots.py

@@ -20,7 +20,7 @@ plt.style.use('ggplot')
 
 # Define function to create and save CMD plots
 def plot_cmd(df, x_col, y_col, xlabel, ylabel, title, filename, folder, hue=None, cmap=False, invert_y=True, clabel = "Morphological Type"):
-    plt.figure(figsize=(8, 6), dpi=350)
+    plt.figure(figsize=(11, 6), dpi=350)
     if hue:
         if cmap:
             scatter = plt.scatter(df[x_col], df[y_col], c=df[hue], cmap="viridis", alpha=0.7, marker=".")
@@ -38,6 +38,7 @@ def plot_cmd(df, x_col, y_col, xlabel, ylabel, title, filename, folder, hue=None
     plt.xlabel(xlabel)
     plt.ylabel(ylabel)
     plt.title(title)
+    plt.tight_layout()
     plt.savefig(os.path.join(folder, filename), dpi = 350)
     plt.close()
 

### 2025-04-14 thesis.qmd
final

@@
   title: "Analysis of observational data, to calculate the Delayed-Tau model parameters"
-author: "Dimitrios Papachristopoulos"
+  subtitle: "Undergraduate thesis"
+  author: 
+  - name: Dimitrios Papachristopoulos
+    role: sdf
+    affiliations:
+      - id: undgdt
+        department: ID number 1110 2018 00142 
+        name: Undergraduate student
+  - name: Despina Hatzidimitriou 
+    affiliations:
+      - id: sprvsr
+        name: Supervising professor 
+        department: National and Kapodistrian University of Athens
   fontfamily: fontenc
+  mainfont: "Times New Roman"
   format: 
-  pdf: default  
+    titlepage-pdf: 
+      titlepage: vline
+      titlepage-logo: "template/uoa_new_logo_red.png"
+      titlepage-footer: | # text
+        National and Kapodistrian University of Athens\
+        School of Science\
+        Faculty of Physics\
+        Department of Astrophysics, Astronomy and Mechanics\
+        April 2025
+      author-style: plain
+      author-sep: "\ --\ "
+      number-sections: true  
+      documentclass: scrartcl
+      classoption: ["oneside", "open=any"]
+
+    #pdf: default  
     # arxiv-pdf:
@@
 
-abstract: |
+---
+{{<pagebreak>}}
+
+# Abstract
+
+## English
+
 The Star Formation History (SFH) of a galaxy can offer many insights not only for the evolution and the future of the galaxy, but also for the evolution of the Universe.
@@
 **Keywords:** Galaxies, Galaxy Evolution, Star Formation History (SFH), Star Formation Rate (SFR), Delayed-$\tau$, Local Cosmological Volume, Lilly-Madau Plot, Redshift, Newton-Ramphson, Markov Chain Monte Carlo (MCMC).
----
+
+## Greek
+
+Οι γαλαξίες είναι τεράστια συστήματα από αστέρια, πλανήτες, αέρια και σκόνη που συγκρατούνται μαζί λόγω της βαρύτητας.
+Κάθε γαλαξίας αποτελεί ένα «κοσμικό νησί» με δισεκατομμύρια ή ακόμα και τρισεκατομμύρια αστέρια, πλανήτες, μαύρες τρύπες και άλλα αστρονομικά αντικείμενα.
+Κάθε γαλαξίας διαφέρει τόσο στο πόσο μαζικός είναι όσο και στην μορφολογία του.
+Συνεχώς, εντώς των γαλαξιών, νεφελώματα τα οποία αποτελούνται από αέρια και σκόνη, καταρρέουν λόγω της βαρύτητας τους και παράγουν αστέρια.
+Η παραγωγή των άστρων επιρρεάζεται από τα χαρακτηριστικά του εκάστοτε γαλαξία και μέσω της μελέτης της ιστορίας της αστρογέννεσης των γαλαξιών, μπορούμε να καταλάβουμε την προέλευση των αστρικών και πλανητικών συστημάτων αλλά και την εξέλιξη τόσο των γαλαξιών όσο και του σύμπαντος.
+
+Μέσω φασματοσκοπικών και φωτομετρικών μεθόδων μπορούμε να υπολογίσουμε των ρυθμό αστρογέννεσης (Star Formation Rate, SFR) των γαλαξίων σε διάφορες ηλικίες του γαλαξία (διαφορετικά φάσματα που χρησιμοποιούνται για τον υπολογισμό διαφορετικών αστρικών πληθυσμών), και με αυτών των τρόπο είναι δυνατόν να μάθουμε την ιστορία αστρογένεσης του κάθε γαλαξία (Star Formation History, SFH).
+Κάποια μοντέλα προσπαθούν να παραμετροποιήσουν την SFH, χρησιμοποιούντας συναρτήσεις της μορφής $\text{SFR} = f(t)$, προσπαθώντας να προσεγγίσουν την πραγματική SFH με μία ομαλή και εξιδινακευμένη εξίσωση που αγνοεί την ποικιλομορφία των γαλαξιών.
+
+{{<pagebreak>}}
 
@@
 # Star Formation
-
-The SFH of a galaxy describes the evolution of its star formation rate over time.
+ing professor
+The SFH of a galaxy describesution of its star formation rate over time.
 By selecting an appropriate model for SFH, we can analyze stellar production, predict periods of active or quiescent star formation, and determine when SFR stabilizes.
@@
 
-<!-- {{<pagebreak>}} -->
+{{<pagebreak>}}
 
